### 2017-10-07 draft1.tex
First Commit

%% Copyright (C) 2009 by Tobias Elze
%% Journal of Vision LaTeX template version 1.0
%% This document may be used freely for your own submissions.

\documentclass{jov}
\usepackage{graphicx} % needed for figures
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{comment}

\DeclareMathOperator*{\argmin}{arg\,min}

\begin{document}

\title{Lightness constancy under fixed geometry}
\abstract{Abstract goes here.}

\author{Singh}{Vijay}
 {Computational Neuroscience Initiative}
 {and Department of Physics, University of Pennsylvania, PA, USA}
 {}{vsin@sas.upenn.edu}

\keywords{color constancy, accuracy maximization analysis, supervised learning,
lightness}

\maketitle

\section{Introduction}
I am trying to add to git.
The color of an object has important behavioral implications. This important property of an object is perceived from the light reflected off the object surface. The reflected light depends not just on the properties intrinsic to the object, such as the object's surface reflectance, its texture, material properties and geometry (shape, size, orientation), but also on extrinsic factors that depend on the object's surround (Fig. \ref{fig:introSchematic}). The surround dependent extrinsic factors that affect the reflected light are: the surface reflectance, texture and material properties of the objects in the surround, the illumination spectrum of the sources of light illuminating the object, the geometry, relative position and pose of the objects and light sources in the surround, and the position of the observer. As these extrinsic factors vary considerably from scene to scene, the challenge faced by the visual system is to recover a stable perceptual representation of the object's surface reflectance, ignoring the  variations in the reflected light resulting from the extrinsic factors. The ability of the visual system to extract such a stable representation, its perceived color, is called color constancy. We are interested in identifying the computations that lead to such constancy.

In this work, we study a simpler analogue of color constancy called lightness constancy. Here, we consider the lightness component of the 3D color space. Lightness is the attribute that determines the brightness of a color. For achromatic objects, it is the property that changes from black to gray to white. A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color. We study the effects of variations in the reflected light on the perceived lightness of an object.

% Figure 1
\begin{figure}[h]
\centering
\begin{subfigure}{0.4 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{introSchematic.png}
        \caption{}
        \label{fig:introSchematic}
    \end{subfigure}
    \begin{subfigure}{0.45 \textwidth}   
        \includegraphics[width=\textwidth]{introExampleFigure.jpeg}
        \caption{}
        \label{fig:introExampleFigure}
    \end{subfigure}
    \label{introFigure}
    \caption{(a) {\bf Color Constancy:} The light reflected off an object and incident on our eyes, depends both on the surface reflectance of the object $\left( R(\lambda,x) \right)$ and the illumination spectrum of the light source $\left(E(\lambda,x)\right)$. Additionally, the reflected light also depends on context the object lies in. Thus a variation in the reflected light can result from either a change in the object surface reflectance, or a change in the illumination spectrum of the light source, or change in the context, or all of these. Color constancy refers to the ability of the human visual system to perceive the color of the object stably under variations coming from these factors. (b) {\bf Lightness Constancy Under Spectral Variations:} In this work we study lightness constancy under variations in the spectra of the light sources and the objects. In Fig.\ref{fig:introExampleFigure}, we show 5 images generated at three different lightness levels of the target object (spherical object in the center). Along the rows we have fixed the lightness level of the target object, while we vary the spectra of the target object, the background objects and the light sources. (For illustration, in fig.\ref{fig:introExampleFigure}, We have fixed the shape of the target object reflectance spectra along the column.) Our aim is to identify computations that can recover the target object lightness from such stimuli.} 
\end{figure}

The factors that lead to variations in the reflected light can broadly be categorized into two categories: geometrical (shape,size, relative position, etc.) and spectral (surface reflectance, diffusivity, etc.). Here we focus on spectral variations. Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness. We are interested in identifying the computations that should be performed on the visual signal to achieve lightness constancy (Fig.\ref{fig:introExampleFigure}).

\begin{comment}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{approach.png}
\caption{{\bf Approach:} We have employed a supervised learning approach to study color constancy. We first generate a large dataset of multi-spectral images labeled with the lightness level of the target object. We generate images at multiple lightness levels, with images at the same lightness level having variable object reflectance spectra and illumination spectra. These multi-spectral images are used to simulate the response of the visual system. We use isetbio toolbox to model the optics and physiology of early vision and produce the response of the cones in the retina. We use supervised computational learning methods on this labeled dataset of cone-responses to estimate the lightness of the target object. The performance of the supervised method is calculated using a separate test dataset.} 
\label{fig:approach}
\end{figure}
\end{comment}

Our approach involves generating a database of multi-spectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene. The label refers to the perceived lightness of the target object if it were placed under a standard light source ($D_{65}$ daylight spectrum). We generate hundreds of multi-spectral images at several fixed values of the target object standard lightness. At a particular lightness level, we allow variations in the surface reflectance spectra of the objects (both the target and surround) and the illumination spectra of the light sources (Fig. \ref{fig:introExampleFigure}. Here we show the results for three cases resulting from the combination of such spectral variations (Fig.\ref{fig:studiedCases}. These are: 1. Variations in target object spectra (Fig.\ref{fig:targetVarying}) with fixed illumination and background surface reflectance spectra, 2. Variations in target object spectra and the light source spectra, with fixed background surface reflectance spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3. Variations in all spectra (target object, background object and light source) (Fig.\ref{fig:allSpectraVarying}). The effects of other types of spectral variations can be explained in terms of one of these cases (see supplementary information).

% Figure 2
\begin{figure}
\centering
	\begin{subfigure}[b]{0.33 \textwidth}
		\includegraphics[width=\textwidth]{targetVarying.jpeg}
		\caption{Case 1}
 		\label{fig:targetVarying}
	\end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{targetIlluminantVarying.jpeg}
        \caption{Case 2}
        \label{fig:targetIlluminantVarying}
    \end{subfigure}
	\begin{subfigure}[b]{0.33 \textwidth}
        \includegraphics[width=\textwidth]{allSpectraVarying.jpeg}
        \caption{Case 3}
        \label{fig:allSpectraVarying}
    \end{subfigure}    
    \caption{{\bf Spectral Variations Studied:} sRGB rendition of images studied in our work. The numbers on the left are the standard lightness level of the target object. We show 5 images for each case at 3 lightness levels. The analysis was performed with images at 10 lightness levels. We studied three types of spectral variations. (a) Case 1: Target reflectance spectra variable, Background reflectance spectra fixed, illuminant spectra fixed (b) Case 2: Target reflectance spectra variable, Background reflectance spectra fixed, illuminant spectra variable (c) Case 3: Target reflectance spectra variable, Background reflectance spectra variable, illuminant spectra variable.}
\label{fig:studiedCases}
\end{figure}

Having generated the database of labeled multi-spectral images for each one of these cases, we simulate the retinal cone response to these images using an accurate model of the front end of the visual system. The cone-responses dataset, labeled with the standard lightness of the target object, are analyzed using supervised computational learning methods. We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, SVD-LDA regression and accuracy maximization analysis. These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness. Finally, we evaluate the performance of the computational methods on a test set of images.

In the following, we describe each one of these stages of our approach in detail. In the methods section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}). Next, we describe the steps to simulate the response of the visual system to these images (\nameref{method:Isetbio}). Finally, we describe the three learning methods we have used in our analysis (\nameref{method:SupervisedLearning}). In the results section, we first the show the estimates and performance of each one of the supervised methods for the three cases with different spectral variations. We show that for spectral variations that allow variation either only in the shape of the target surface reflectance or the background surface reflectance or the spectral power distribution of the source of light, the standard lightness, $Y_{65}$ can be recovered by simple manipulations of the reflected light captured by the visual system. For example, if the illumination spectra of the light sources and the background are held fixed, wile the target reflectance spectra change (case 1), $Y_{65}$ can be recovered directly from the light reflected off the target object. If  the surface reflectance of the target object  and the illumination spectra of the light sources are allowed to vary, with fixed background reflectance spectra (case 2), $Y_{65}$ can be recovered by from the contrast between the target and the background. When all the spectral features in the scene are allowed to change (case 3), $Y_{65}$ can not be recovered from a simple manipulations of the light captured by the visual system. Here, we have used a Bayesian supervised learning method called accuracy maximization analysis to estimate $Y_{65}$ of the target object. Using this method, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.

Finally, we compared the generality of the methods for lightness estimation by comparing the optimal receptive fields of one case to the others. The optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround. Additionally, the receptive fields give more weight to the L and M cone responses compared to S cone responses. We discuss the implications of such receptive fields on lightness constancy.

\section{Methods}
\subsection{Image database} \label{method:VirtualWorld}
In this section we briefly describe our image generation software, that we call Virtual world color constancy (VWCC). The details of the software are provided in the supplementary information section. To generate a virtual scene, we first select a 3D scene, a target object and a light source from the set of predefined scenes and objects of the VWCC software. The target object and the light source are inserted at predefined positions in the 3D scene. Fig.\ref{fig:3DScene} shows a 2D sRGB rendition of the 3D scene with the inserted target object (green sphere in the middle) used in our analysis. (The light source in not visible.) Next, we assign a surface reflectance spectrum and an illumination spectrum to each object and light source in the scene. The surface reflectance of the target object is assigned such that the perceived lightness of the target object under D65 daylight spectrum has a fixed value. Once these spectral properties have been assigned, we render a 320x240 pixel$^2$ 2d multi-spectral images of the scene at 31 frequencies (linearly spaced between 400nm - 700nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}. We generate hundreds of such scenes and corresponding multi-spectral images for at 10 linearly spaced lightness levels between 0.2 and 0.6. For the images at a fixed lightness level, the reflectance and illumination spectra are assigned according to the spectral variations allowed under each case. Next, we crop a 51x51 pixel$^2$ part of the multi-spectral image containing the target object for further analysis (\ref{fig:croppedImage}). Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this work.

% Figure 3
\begin{figure}
\centering
\begin{subfigure}[b]{0.25 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{3DScene.png}
        \caption{A typical 3D Scene}
        \label{fig:3DScene}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.19 \textwidth}   
    \hspace{0.1 \textwidth}
        \includegraphics[width=\textwidth]{croppedImage.png}
        \caption{Cropped Image}
        \label{fig:croppedImage}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.19 \textwidth}
    \hspace{0.1 \textwidth}
        \includegraphics[width=\textwidth]{croppedImageWithMosaic.png}
        \caption{Optical Image}
        \label{fig:croppedImageWithMosaic}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{coneContrast.png}
        \caption{LMS cone contrast}
        \label{fig:coneContrast}
    \end{subfigure}

    \label{fig:sceneWithCroppedImage}
    \caption{{\bf Generating labeled dataset for computational analysis:}  We employ a supervised learning approach in our study. We generate a database of visual system response to images labeled with the lightness of the target object. This is done as follows: (a) We define a 3D virtual scene where we can assign the geometrical and spectral properties of the objects. In this 3D scene, we place a target object (here the spherical object) in the camera field of view and assign a fixed reflectance spectrum to the target object. Then we render a hyperspectral image of the scene. (b) A part of the image, containing the target object, is cropped from the image. (c) Using an accurate model of the front end of the visual system, we generate the response of the retinal cones to the cropped image. Fig.\ref{fig:croppedImageWithMosaic} shows the optical image incident on the cone mosaic and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue). See text for the details of the model. (d) For each cone type, we interpolate the response to get the cone-response of all the three types at each location. These responses are contrast normalized (see text) to the get the input analysis.}
\end{figure}

\subsection{Model of Visual System} \label{method:Isetbio}
We simulate the visual system response using isetbio software toolbox. Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics. We use the multi-spectral cropped image (fig.\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina. The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m. The retinal cone mosaic is modeled as a square grid with 51x51 cones in the l:m:s ratio 0.6:0.3:0.1. The response of the cones are measured in terms of the number of isomerizations in the cone segment ({\it over what time ??}). Since, S cones response are much lower than of L and M cones, to mdoel the amplification of the s cone response downstream, we rescale the cone response functions by the total area under the response curves. This leads to comparable number of isomerizations in the L, M and S cone on the presentation of an image. We interpolate the responses of cones in each cone class to get a 51x51 cone response image for each cone class.  Further, the three 51x51 cone response matrix corresponding to each one of the L, M and S cones are then rescaled by the mean cone response to model contrast adaption in the retina. The mean is calculated over all the 3x51x51 cones in the de-mosaic response matrix.

\subsection{Supervised Learning methods} \label{method:SupervisedLearning}
\subsubsection*{Linear Regression}
\subsubsection*{SVD regression}
\subsubsection*{Accuracy maximization analysis}

\subsection{Types of spectral variations studied}
In this work we have studied the effects of spectral variations on perceived lightness. The spectral variations in the scene can be categorized into three types. The variations in the shape of target object reflectance spectra, the variations in the shape of background object reflectance spectra, and the variations in the shape of the spectral power distribution of light sources. Here, we present the results for three cases (fig.\ref{fig:studiedCases}): 1. effects of variations in target object spectra (fig.\ref{fig:targetVarying}), 2. effects of variations in target object spectra and the light source spectra (fig.\ref{fig:targetIlluminantVarying}), and 3. effects of variations in all three spectra (fig.\ref{fig:allSpectraVarying}). The rest of the cases are qualitatively similar to one of the cases discussed here, and are discussed in the supplementary materials.

\section{Results}
\subsection{Case 1}

% Figure 4
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{case9SVD.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case9SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{case9AMA.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case9AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{case9FiltersResponse.pdf}
        \caption{AMA RF Response}
        \label{fig:case9FiltersResponse}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{case9Results.pdf}
        \caption{Lightness Estimates}
        \label{fig:case9Results}
    \end{subfigure}    
    \caption{{\bf Receptive fields and lightness estimates. Case 1:} (a) First two receptive fields produced by the SVD method. Along the row we show the filters corresponding to the L cones, M cones and Scones (left to right). (c) First two receptive fields produced by the SVD method. (c) The response of the stimuli to the first two AMA filters. The responses are grouped with the label of the stimuli. As is clear, the response separate out quite well in this case, making the estimation easy (d) The estimates of the target object standard lightness. The naive method produces the mean value of the target luminance used in the analysis. The shaded region corresponds to 1 sigma standard deviation.}
\label{fig:case9AllResults}
\end{figure}

% Figure 5
\begin{figure}
\centering
\includegraphics[width=0.3\textwidth]{RMSEvsNFilters16.pdf}
\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs in our analysis.}
\label{fig:RMSEvsNFilters}
\end{figure}

% Figure 6
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{case10SVD.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case10SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{case10AMA.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case10AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{case10FiltersResponse.pdf}
        \caption{AMA RF Response}
        \label{fig:case10FiltersResponse}
    \end{subfigure}    
        \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{case10Results.pdf}
        \caption{Luminance Estimates}
        \label{fig:case10Results}
    \end{subfigure}
    \label{fig:case10AllResults}
    \caption{{\bf Receptive fields and lightness estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
\end{figure}

% Figure 7
\begin{figure}
\centering
\begin{subfigure}[b]{0.27 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{case12SVD.pdf}
        \caption{SVD First 2 RFs}
        \label{fig:case12SVD}
    \end{subfigure}
    \begin{subfigure}[b]{0.27 \textwidth}   
        \includegraphics[width=\textwidth]{case12AMA.pdf}
        \caption{AMA First 2 RFs}
        \label{fig:case12AMA}
    \end{subfigure}
        \begin{subfigure}[b]{0.20 \textwidth}
        \includegraphics[width=\textwidth]{case12FiltersResponse.pdf}
        \caption{AMA RF Response}
        \label{fig:case12FiltersResponse}
    \end{subfigure}    
        \begin{subfigure}[b]{0.2 \textwidth}
        \includegraphics[width=\textwidth]{case12Results.pdf}
        \caption{Luminance Estimates}
        \label{fig:case12Results}
    \end{subfigure}
    \label{fig:case12AllResults}
    \caption{{\bf Receptive fields and lightness estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
\end{figure}

\begin{comment}
% Figure 8
\begin{figure}
\centering
\begin{subfigure}[b]{0.3 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{case9AcrossCaseComparisonSVD.pdf}
        \caption{SVD RFs of Case 1}
        \label{fig:case9AcrossCaseComparisonSVD}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3 \textwidth}   
        \includegraphics[width=\textwidth]{case10AcrossCaseComparisonSVD.pdf}
        \caption{SVD RFs of Case 2}
        \label{fig:case10AcrossCaseComparisonSVD}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{case12AcrossCaseComparisonSVD.pdf}
        \caption{SVD RFs of Case 3}
        \label{fig:case12AcrossCaseComparisonSVD}
    \end{subfigure}
    \label{fig:SVDComparison}
    \caption{SVD Filter Comparison:}
\end{figure}

% Figure 9
\begin{figure}
\centering
\begin{subfigure}[b]{0.3 \textwidth}
		\centering
        \includegraphics[width=\textwidth]{case9AcrossCaseComparisonAMA.pdf}
        \caption{AMA RFs of Case 1}
        \label{fig:case9AcrossCaseComparisonAMA}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3 \textwidth}   
        \includegraphics[width=\textwidth]{case10AcrossCaseComparisonAMA.pdf}
        \caption{AMA RFs of Case 2}
        \label{fig:case10AcrossCaseComparisonAMA}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3 \textwidth}
        \includegraphics[width=\textwidth]{case12AcrossCaseComparisonAMA.pdf}
        \caption{AMA RFs of Case 3}
        \label{fig:case12AcrossCaseComparisonAMA}
    \end{subfigure}
    \label{fig:AMAComparison}
    \caption{AMA Filter Comparison:}
\end{figure}
\end{comment}

% Figure 10
\begin{figure}
\centering
\begin{subfigure}[b]{0.3 \textwidth}
	\includegraphics[width=\textwidth]{summaryBarGraph.pdf}
	\caption{Performance of methods}
	\label{fig:summaryBarGraph}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.3 \textwidth}   
	\includegraphics[width=\textwidth]{SVDSummaryBarGraph.pdf}
	\caption{SVD RF Performance}
	\label{fig:SVDBAR}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
        \begin{subfigure}[b]{0.3 \textwidth}
	\includegraphics[width=\textwidth]{AMASummaryBarGraph.pdf}
	\caption{AMA RF Performance}
	\label{fig:AMABAR}
    \end{subfigure}
\caption{{\bf Model and Filter Performance:} (a) Comparison of various methods on lightness estimations for the three cases studied here. For simple spectral variations, like where only the target reflectance varies (case 1) or only the target and illumination spectrum varies (Case 2), the lightness can be estimated well. This is so, because the lightness information can be estimated simply from the light reflected of the target( case 1) or from the contrast between the target and the {\it fixed} background (case 2). For more complex case, where the lightness information is confounded due to variations in target, background and illuminant (case 3), the estimation has higher variability. (b) Performance of the SVD receptive fields obtained from one case on the stimuli of others. The RFs obtained from any one of the three cases perform well on the stimuli from case 1. The RF of the most complicated case (case 3), has good performance on the stimuli of lower complexity. (c) Same as Fig.\ref{fig:SVDBAR} for AMA RFs.}
 \label{fig:barGraphs}
\end{figure}

\subsection{Lightness estimates and model performance}
Fig. ZZ gives the AMA lightness estimates for the three cases discussed above. We show the target object lightness estimates for there different methods: linear regression on center pixel, SVD regression and AMA. As is expected, when only the target object reflectance varies, it is easy to estimate the target object lightness. For case 2, where the light source spectra are allowed to vary, although the light captured by the cones vary from image to image, the contrast between the target and the background remains fixed and can be used to estimate the target object lightness. Thus, the SVD-LDA and AMA still provide good estimates of the target object lightness. In case 3, the most challenging case where all the spectra are allowed to change, AMA still does a reasonable job of estimating the target object lightness. AMA mean estimates lie close to the diagonal x=y line.

We compare the performance of these models using the relative root mean square estimator ($E_{\rm rel}$) defined as:

\begin{align}
E_{\rm rel} = \sqrt{\left\langle\left(\frac{Y_{\rm Est}-Y_{\rm Act}}{Y_{\rm Act}}\right)^2\right\rangle}
\end{align}

Fig. ZZZ shows $E_{\rm rel}$ for the various estimators used here.

\subsection{Explain the filters}

\section{Methods}
\subsection{Generating Virtual Images}
The light that reflects off an object and reaches our eyes depends on many factors. These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer. In natural scenes, these spectral and geometrical factors vary considerably. To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors. We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene. Under natural conditions it is difficult to control and quantify every such parameter in a scene. Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.

To overcome this  challenge, we have developed an image rendering software pipeline that allows us to specify a virtual, but naturalistic, statistical model of visual scenes with parametric control over factors in natural scenes. The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes. It then renders a multi-spectral 2D image of each modeled visual scene. Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes. In addition, our software simulates the responses of retinal cones to the rendered multi-spectral images using a realistic model of the early human visual system. Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images. Our software, which is written in MATLAB, is freely available through a public respository: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}. It builds on several other open source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}. Below we refer to the software pipeline as VWCC (for Virtual World Color Constancy).

The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}). The base scene is a 3D model that defines a rendering space.  It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position. VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses. We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly. We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene. Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).  The overall scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness. If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes. As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library. Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).

\begin{figure}[t]
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{baseSceneLibrary.png}
        \caption{Library }
        \label{fig:baseSceneLibrary}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{baseSceneMill.png}
        \caption{Mill}
        \label{fig:baseSceneMill}
    \end{subfigure}    
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{baseSceneTableChairs.png}
        \caption{Table-Chairs}
        \label{fig:baseSceneTableChairs}
    \end{subfigure}

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{baseSceneIndoorPlant.png}
        \caption{Indoor-plant}
        \label{fig:baseSceneIndoorPlant}
    \end{subfigure}    
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{baseSceneWarehouse.png}
        \caption{Warehouse}
        \label{fig:baseSceneWarehouse}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{baseSceneCheckerBoard.png}
        \caption{Checkerboard}
        \label{fig:baseSceneCheckerBoard}
    \end{subfigure}
    \caption{Example of base scenes.}\label{fig:baseScenes}
\end{figure}

VWCC provides an option for inserting 3D objects and lights sources into the base scene. Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted in the library base scene. The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from materials made available on the Internet. The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.

\begin{figure}[h]
\centering
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{libraryWithBigBall.png}
        \caption{Big-ball}
        \label{fig:libraryWithBigBall}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{libraryWithSmallBall.png}
        \caption{Small-ball}
        \label{fig:libraryWithSmallBall}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{libraryWithBarrel.png}
        \caption{Barrel}
        \label{fig:libraryWithBarrel}
    \end{subfigure}

    \begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{libraryWithXylophone.png}
        \caption{Xylophone}
        \label{fig:libraryWithXylophone}
    \end{subfigure}
    ~
	\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{libraryWithRingToy.png}
        \caption{Ring toy}
        \label{fig:libraryWithRingToy}
    \end{subfigure}
        ~
    	\begin{subfigure}[b]{0.22 \textwidth}
        \includegraphics[width=\textwidth]{libraryWithChampagneBottle.png}
        \caption{Champagne Bottle}
        \label{fig:libraryWithChampagneBottle}
    \end{subfigure}
\caption{Base scenes with inserted objects.}\label{fig:libraryWithTarget}
\end{figure}

The size, position and orientation of the inserted objects and lights may be specified programatically (Fig.~\ref{fig:objectTransformations}) or chosen randomly under constraints provided by the base scene meta-data. As with the base scene library, the object may be drawn at random from the VWCC object library.  Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.

Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene. We also assign the illuminant spectral power distribution to each light source in the scene. Objects in the VWCC library may contain more than one distinct surface, each of which may be assigned a different surface reflectance. As with object position, these may be specified programatically. In the present work, we use simple choices for texture (all surfaces spatially uniform) and material property (all surfaces matte) and focus on variation in surface spectral reflectance.

[GOT TO HERE.  DHB.]
\begin{figure}
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{targetVariation.png}
        \caption{Target spectra}
        \label{fig:targetVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{backgroundVariation.png}
        \caption{Background spectra}
        \label{fig:backGroundVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
    %(or a blank line to force the subfigure onto a new line)
    \begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{illuminationVariation.png}
        \caption{Illumination spectra}
        \label{fig:illuminationVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{targetPosition.png}
        \caption{Target position}
        \label{fig:targetPositionVariation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
	\begin{subfigure}[b]{0.18 \textwidth}
    \centering
        \includegraphics[width=\textwidth]{targetSizeOrientation.png}
        \caption{Target Size/Orientation}
        \label{fig:targetSizeOrientation}
    \end{subfigure}
    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
      %(or a blank line to force the subfigure onto a new line)
    \caption{{\bf Transformations of the scene:} (a-c) Spectral Transformations. (d-e) Geometrical transformations.}\label{fig:spectralTransformations}
\end{figure}

After specifying the geometry and spectra, one of the inserted objects is chosen as the target object in the scene. A camera is inserted at a user specified position and then pointed at the target object. We ensure that the target object is not completely occluded by another object in the line of sight of the camera. Next, a predefined surface reflectance spectrum is assigned to the target object. This target surface reflectance sets the label for the virtual scene image. The scene is now rendered using the Mitsuba rendering package. The renderer produces 2D hyper-spectral images of the scene at specified wavelengths. Finally, these multi-spectral images are used to simulate retinal cone responses using the \href{https://github.com/isetbio}{ISETBIO} software.

To generate the retinal response one needs to specify the retinal cone mosaic and the size of the retinal image. The retinal cone mosaic is specified in terms of the total number of cones and the proportion of the long(L), medium(M) and the short(S) cones in the mosaic. With these parameters, the software generates the specified number of LMS cones with random positions on a square grid. The size of the retinal image is specified in terms of the field of view and object distance from the eye.

For the images used in this work, we first selected the ``{\it Library}'' base scene from the VWCC base scene set. We inserted the spherical ``{\it Big Ball}'' object in the base scene and called it the target object. We also inserted a light source with the same spherical ``Big Ball'' shape. Also, a camera is inserted the scene and pointed at the target object. The position, and size of the inserted object, light source and the camera was held fixed for all the images analyzed in this work, i.e., no geometrical manipulations were performed between the images. Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene. The spectral manipulations for the various cases studied in this work are described below. Multi-spectral 2D images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$. Next, a $51 \times 51$ pixel$^2$ patch of the multi-spectral image was cropped around the target object and cone responses were calculated to these cropped images as described below.

\subsection{Illumination Spectrum}
The illumination spectrum is generated through a random statistical sampling of a natural illumination spectrum dataset. First, we decompose the spectra in the database as a linear sum using principle component analysis (PCA) basis vectors. This decomposition is approximated by taking a sum over the PCA basis vectors corresponding to the largest 6 eigenvalues. Random spectra are sampled from this low 6 dimensional PCA space assuming the spectral distribution to be a multivariate gaussian.

\begin{figure}
\centering
	\includegraphics[width=\textwidth]{illumination.pdf}
    \caption{Illumination Generation}
    \label{fig:illuminationGeneration}
\end{figure}
We have used the Granada natural daylight spectrum \href{http://colorimaginglab.ugr.es/pages/Data}{dataset} \cite{peyvandi2016colorimetric} to sample illuminants. Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset. Since the distribution varies over multiple order of magnitudes, we rescale each spectrum by dividing by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$. These rescaled spectra $(I_i^s(\lambda))$ are then mean centered for PCA by subtracting out the mean 
rescaled spectra, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
The resulting dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$, 
is decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
where $\hat{{\bf e}}_j^{PCA}$s are PCA basis vectors obtained using 
singular value decomposition (SVD). $w_{ij}$s are the projections 
of $I_i^{MC}(\lambda)$ along the PCA basis vectors. We approximate 
this decomposition by summing over the basis vectors corresponding to
the largest six SVD eigenvalues. For the Granada dataset, these six 
eigenvalues constitute more than $98\%$ of the variance. These steps
can be summarized as follows:
\begin{align}
I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}
\end{align}

To generate new illuminants $\tilde{I}_i(\lambda)$, random 
projection weights ($\tilde{w}_{ij}$) are generated using a multivariate 
gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. If the $\tilde{w}_{ij}$ are such that, $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, for all $\lambda$, then the new illuminant spectrum is given as 
\begin{align}
\tilde{I}(\lambda) = \left( \tilde{I}_{MC}(\lambda) + \bar{I}_{s}(\lambda)\right) 
\times \max\left(\langle I_{G}\rangle\right) .
\end{align}
Finally $\tilde{I}(\lambda)$ is rescaled by a uniform random number between [0, 300].

\subsection{Reflectance Spectrum}
\begin{figure}
\centering
	\includegraphics[width=\textwidth]{reflectance.pdf}
    \caption{Reflectance Generation}
    \label{fig:reflectanceGeneration}
\end{figure}

Similar to the illumination spectrum, the reflectance spectrum of the 
objects in the visual scene are generated through a random 
sampling of natural surface reflectance spectra. We have used 
the Munsell {(\it citation)} and vrhel {(\it citation)} surface reflectance 
datasets for such sampling. Let us denote the dataset of natural 
reflectance spectra as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
and $M$ is the total number of spectra in the dataset. To generate 
a random reflectance spectrum $\tilde{R}(\lambda)$, 
we first mean center the dataset by subtracting out the 
mean surface reflectance spectrum, $\bar{R}(\lambda)$,
from each surface reflectance spectrum.
$\bar{R}(\lambda)$ is obtained by taking the sample 
mean over all spectra in the dataset, i.e.,
$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. 
Thus we have the mean centered reflectance 
spectrum dataset as $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
We decompose this as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$. Here,
${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD 
and $w_{ij}$s are the projections of $R_i^{\rm MC}(\lambda)$ along the PCA eigenvectors 
$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. The 
decomposition is approximated by summing over the PCA basis 
vectors corresponding to the largest six SVD eigenvalues. These six eigenvalues capture 
more than $92\%$ of the variance in the combined Munsell and vhrel datasets. To generate 
a new reflectance spectrum, a point is sampled randomly in this 
six dimensional sub-space using a multivariate normal 
distribution, with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. If the randomly sampled projection, $\tilde{w}_{ij}$, is 
such that $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, the new surface reflectance 
is given as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.

\begin{figure}
\centering
	\includegraphics[width=\textwidth]{target.pdf}
    \caption{Target Reflectance Generation}
    \label{fig:targetGeneration}
\end{figure}

For generating the target object reflectance at a particular lightness $(Y_{\rm T})$, the values in the spectrum are 
rescaled by a scalar such that the perceived lightness of the 
target surface under standard daylight illuminant $(D_{65}(\lambda))$ 
equals a designated value. The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE luminosity (or luminous efficiency) function. 
$\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
perception of brightness. The target reflectance is given by: $\tilde{R}(\lambda) \cdot\left(\frac{Y}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.

\subsection{Cone response to hyper-spectral images}
Cone response to the hyper-spectral images are generated
using \href{https://github.com/isetbio}{ISETBIO}. The model incorporates several critical components of biological vision, including physiological optics, information about cornea, lens, pupil, etc. We simulate a model retinal mosaic with $51\times51$ cones having cone densities in the ratio [l,m,s]=[0.6 0.3 0.1]. The cone wavelength sensitivities are scaled such that the area under the sensitivity curve equals unity. A $51\times51$ pixel$^2$ patch of the image containing the target image is used to calculate the cone responses. The image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.

\subsection{Accuracy Maximization Analysis}
AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction. It finds the receptive fields that are optimal for performing a well defined behavioral task. Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task, which is implicitly defined in terms of the labels. The optimal filters are the ones whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set. The filters are learned via gradient descent with the aid of an optimal Bayesian decoder that is matched to the filters throughout the learning process.

Let us assume that there is a latent variable ($X$) that takes the values $\{X_k: k\in[1,N_{\nu}] \}$. The $l$'th stimuli corresponding to the the $k$'th category of the latent variable is $s_{kl}$. Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$. Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the latent variable ($X_k$) corresponding to the stimuli $s_{kl}$ as $\hat{X}_{kl}$. Given this estimate, one can define a cost function $C_{kl}(X_{kl},\hat{X}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and a mean cost $\bar{C}_{kl}(X_{kl},\hat{X}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.

Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}, l\in[1,N_k]\}$. $N_{\nu}$ is the total number of labels and $N_{k}$ is the number of stimuli corresponding to the label $X_k$. Thus,
\begin{align}
{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{kl} \bar{C}_{kl}.
\label{eq:fopt}
\end{align}

AMA employs the Bayes optimal decoder to estimate the optimal estimate. The Bayesian decoder computes the posterior probability of the latent variable $p(X|{\textbf {\textit R}})$ and reads out the optimal estimate $\hat{X}^{\rm opt}$ from the posterior as the value that minimizes the cost. By Bayes' theorem, the posterior probability can be written as:
\begin{align}
p(X_k|{\textbf {\textit R} }_{kl}) = \frac{p({\textbf {\textit R} }_{kl}|X_k)p(X_k)}{\sum\limits_{i=1}^{N_{\nu}}{p({\textbf {\textit R} }_{kl}|X_i)p(X_i)}}.
\label{eq:posterior}
\end{align}
As conditional probability of the filter response is:
\begin{align}
p({\textbf {\textit R} }_{kl}|X_k) = \sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|X_k),
\label{eq:condProb}
\end{align}
using Eq.\ref{eq:condProb} in Eq.\ref{eq:posterior} we get:
\begin{align}
p(X_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|X_k)\right]p(X_k)}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})p({\textbf {\textit s} }_{kj}|X_i)\right]p(X_i)}}
\label{eq:finalPosterior}
\end{align}
Since, $p({\textbf {\textit s} }_{km}|X_k) = \frac{1}{N_k}$, and $p(X_k)=\frac{N_k}{N}$, where $N = \sum\limits_{k=1}^{N_{\nu}}N_{k}$ is total number of samples in the training set, Eq.\ref{eq:finalPosterior} simplifies to
\begin{align}
p(X_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km}) \frac{1}{N_k}\right]\frac{N_k}{N}}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij}) \frac{1}{N_i}\right]\frac{N_i}{N}}} = \frac{\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})}{\sum\limits_{i=1}^{N_{\nu}}{\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})}}.
\label{eq:simplifiedPosterior}
\end{align}
Now if the cost associated with the latent variable $X_k$ and the estimate $\hat{X}_k$ is $\gamma (X_k,\hat{X}_k)$, we have  
\begin{align}
C_{kl} = \sum\limits_{u=1}^{N_{\nu}}\gamma(X_u,\hat{X}_u)p(X_u|{\textbf{\textit R}}_{kl}),
\end{align}
and the total cost associated with the training set is $\bar{C} = \frac{1}{N} \sum\limits_{k,l}\bar{C}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle C_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$. The optimal AMA filters are obtained by minimizing $\bar{C}$ over the filter set ${\textbf {\textit f} }$ (Eq.\ref{eq:fopt}). The filters are obtained using gradient descent.

In this work, we assume the noisy response model to be a multivariate gaussian. For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{kl,1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$. We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be zero mean contrast normalized, i.e., $\langle{s_{kl}}\rangle = 0$ \& ${|s_{kl}|=1}$.

\subsection{Data Analysis} We generate XX number of images with target objects at 10 standard luminance levels linearly spaced between 0.2 to 0.6. These limits were chosen because the luminance under the standard source ($D_{65}$) of more than $90\%$ of the natural surface reflectance spectra fell between them. Thus we had YY images at each target luminance level. We generated the cone responses to these images using ISETBIO. The cone response ($I$) were first converted in to weber contrast form using the transformation $\left(I \rightarrow I_{\rm web} = \frac{I}{\langle I \rangle}-1\right)$. The weber contrast responses and the target luminance levels were used as the input stimuli and the latent variable, respectively, for AMA. The AMA parameters were: $\alpha = xxx$ and $\sigma_0^2 = yyy$.

\subsection{Explanation of the various cases}
In this work we have labeled the images using the lightness of the target object under  standard daylight spectrum ($D_65$). The images are labeled such that the total light reflected from the target object equals a fixed value. At this fixed value, we generate multiple images with variations in the spectral properties of the objects and the light sources. At fixed target lightness (Y65), spectral variations can result from variations in the shape of: 1. Target surface reflectance spectrum, 2. Background object surface reflectance, and 3. Spectral power distribution of the light source. These give rise to 12 distinct cases (Fig. \ref{fig:caseIcons}). The icons on the left and the top represent the spectrum of the illuminant, the background and the target object. For the illuminant and background, only one curve in the represents fixed spectra from image to image. Two curve imply that the spectra were varied randomly from image to image. For the target object, we show the spectrum at two distinct lightness levels. At a particular level, the meaning of the curves is the same as that of illuminant and background icons. Additionally, same shape of the target reflectance spectrum at both the levels means that Y65 was changed by changing the mean value of the surface reflectance spectrum keeping the same shape.

\begin{figure}
\centering
	\includegraphics[width=0.6 \textwidth]{cases.pdf}
    \caption{\bf{Spectral variations considered in our analysis.} }
    \label{fig:casesIcons}
\end{figure}

To illustrate, in case 1 the spectral power distribution of the light source and the surface reflectance of the background objects are fixed from image to image. Further, the shape of the target object surface reflectance also remains the same from to image to image at the same standard lightness level, and only vary in their mean value between standard luminance levels. Thus in case 1, at one standard lightness, all images are identical (Fig. . This is the simplest possible scene variation considered here. Similarly, in the most complex case, case 12, all the spectra are allowed to vary from image to image.

\bibliography{references}
\bibliographystyle{jovcite}

\end{document}

### 2017-10-07 codeForFigures/CopyOverFigures.m
reorganizing figures

@@ -1,0 +1,107 @@
+% CopyOverFigures
+%
+% This script copies over figures made by the various analysis scripts and
+% renames them to match the figure numbers in the paper describing this
+% work.
+%
+% Oct 7 2017 VS wrote this 
+
+%% Get directory to fill up with the figure parts
+figuresStorageDirectory = '/Users/vijaysingh_local/Documents/LightnessPaper/codeForFigures/codeToMakeFigures/'; 
+            % point this to the directory where the figures are stored
+figureDir = '/Users/vijaysingh_local/Documents/LightnessPaper/Figures';
+
+
+% Figure4: Copy results for figure 4. These are the results for case 9
+copyCmd = ['cp ' fullfile(figuresStorageDirectory,'filters','case9SVD.pdf') ' ' fullfile(figureDir,'Figure4','Figure4_a.pdf')];
+unix(copyCmd);
+copyCmd = ['cp ' fullfile(figuresStorageDirectory,'filters','case9AMA.pdf') ' ' fullfile(figureDir,'Figure4','Figure4_b.pdf')];
+unix(copyCmd);
+copyCmd = ['cp ' fullfile(figuresStorageDirectory,'filterResponse','case9FiltersResponse.pdf') ' ' fullfile(figureDir,'Figure4','Figure4_c.pdf')];
+unix(copyCmd);
+copyCmd = ['cp ' fullfile(figuresStorageDirectory,'estimatesVsActual','Case9Results.pdf') ' ' fullfile(figureDir,'Figure4','Figure4_d.pdf')];
+unix(copyCmd);
+
+% Figure5: Copy results for figure 5.
+copyCmd = ['cp ' fullfile(figuresStorageDirectory,'RMSEvsNEigVals','RMSEvsNFilters16.pdf') ' ' fullfile(figureDir,'Figure5','Figure5.pdf')];
+unix(copyCmd);
+
+% Figure6: Copy results for figure 6. These are the results for case 10
+copyCmd = ['cp ' fullfile(figuresStorageDirectory,'filters','case10SVD.pdf') ' ' fullfile(figureDir,'Figure6','Figure6_a.pdf')];
+unix(copyCmd);
[…]

### 2017-10-07 codeForFigures/codeToMakeFigures/cmapBWR.m

@@ -1,0 +1,136 @@
+function newmap = cmapBWR(m)
+% function cmapBWR   
+% 
+%   Blue, white, and red color map.
+%   
+%   cmapBWR(M) returns an M-by-3 matrix containing a blue to white
+%   to red colormap, with white corresponding to the CAXIS value closest
+%   to zero.  This colormap is most useful for images and surface plots
+%   with positive and negative values.  cmapBWR, by itself, is the
+%   same length as the current colormap.
+%
+%   Examples:
+%   ------------------------------
+%   figure
+%   imagesc(peaks(250));
+%   colormap(cmapBWR(256)), colorbar
+% 
+%   figure
+%   imagesc(peaks(250), [0 8])
+%   colormap(cmapBWR), colorbar
+% 
+%   figure
+%   imagesc(peaks(250), [-6 0])
+%   colormap(cmapBWR), colorbar
+% 
+%   figure
+%   surf(peaks)
+%   colormap(cmapBWR)
+%   axis tight
+%
+%   See also HSV, HOT, COOL, BONE, COPPER, PINK, FLAG, 
+%   COLORMAP, RGBPLOT.
+
+
+if nargin < 1
+   m = size(get(gcf,'colormap'),1);
+end
+
+bottom    = [0.1 0.3 1.0];
+botmiddle = [0.5 0.6 0.75];
+middle    = [1.0 1.0 1.0];
+topmiddle = [0.75 0.6 .5];
+top       = [1.0 0.3 0.1];
+
+bottom    = [0.0 0.0 1.0];
+botmiddle = [0.0 0.5 1.0];
+middle    = [1.0 1.0 1.0];
+topmiddle = [1.0 0.5 0.0];
+top       = [1.0 0.0 0.0];
+
+bottom    = [0.0 0.0 0.6]; % USEFUL FOR RANGE STATS PLOTS
+botmiddle = [0.0 0.2 1.0];
+middle    = [1.0 1.0 1.0];
+topmiddle = [1.0 0.2 0.0];
+top       = [0.6 0.0 0.0];
+
+% Find middle
+lims = get(gca, 'CLim');
+
+% Find ratio of negative to positive
+if (lims(1) < 0) && (lims(2) > 0)
+    % It has both negative and positive
+    % Find ratio of negative to positive
+    ratio = abs(lims(1)) / (abs(lims(1)) + lims(2));
+    neglen = round(m*ratio);
+    poslen = m - neglen;
+    
+    % Just negative
+    new = [bottom; botmiddle; middle];
[…]

### 2017-10-07 codeForFigures/codeToMakeFigures/estimatesVsActual.m

@@ -1,0 +1,70 @@
+% This script plots the lightness estimates vs the actual lighteness for 
+% the linear, SVD and AMA methods.
+%
+% Case 9 - Variable Target shape Fixed Background Fixed Illuminant
+% Case 10 - Variable Target shape Fixed Background Variable Illuminant
+% Case 12 - Variable Target shape Variable Background Variable Illuminant
+%
+% VS wrote this Oct7 2017
+
+% Make the directory where the figures will be stored
+if (~exist('estimatesVsActual','dir'))
+    mkdir('estimatesVsActual');
+end
+
+% Choose a case
+for caseNo = [ 9 10 12]
+
+% load the files containing the estimates
+loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'.mat']);
+loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'.mat']);
+loadTheSVDFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SVD/case',num2str(caseNo),'.mat']);
+
+% Define the colors to be used for each method
+naiveColor  = 'm';
+linearColor = 'k';   
+SVDColor    = 'g';
+AMAColor    = 'r';
+
+% Plot the contrast estimates
+fig = figure;
+set(fig,'units','pixels', 'Position', [1 1 500 500]);
+hold on;
+% plot the linear and svd response
+lNaive = plot(unique(loadTheAMAFile.XTest)',0.4*ones(size(unique(loadTheAMAFile.XTest)')),naiveColor,'linewidth',2);
+lLinear = plot(unique(loadTheAMAFile.XTest)',loadTheLinearFile.cNormMeanEstimateTest,linearColor,'linewidth',2);
+% errorbar(unique(loadTheLinearFile.labelsTest)',loadTheLinearFile.cMeanSvdEstimateTest,loadTheLinearFile.cStdSvdEstimateTest,SVDColor,'linewidth',2);
+xlim([0.15 0.65]);
+ylim([0.15 0.65]);
+xlabel('$Y$','interpreter','latex');
+ylabel('$\hat{Y}$','interpreter','latex');
+box on;
+
[…]

### 2017-10-07 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m

@@ -1,0 +1,90 @@
+% filtersAndFilterResponses
+% This script can be used to plot AMA and SVD filters and filter responses.
+% This script first loads the results, plots the filters/response and saves
+% the figure as .pdf. The figures are made case by case. This is a really
+% dumb script. Everything needs to be typed manually.
+%
+% The data is stored in Johannes Burge's Ogle computer.
+%
+% VS wrote this Oct 7 2017
+
+% Make the directory where the figures will be stored
+if (~exist('filters','dir'))
+    mkdir('filters');
+end
+
+if (~exist('filterResponse','dir'))
+    mkdir('filterResponse');
+end
+
+
+% Load AMA results struct
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9.mat')
+plotFiltersJointResponsesModified(1,[1,2],case9Output.AMA.X,case9Output.AMA.s,case9Output.AMA.f,case9Output.AMA.ctgInd,[],[],[],[1:10])
+save2pdf('filterResponse/case9FiltersResponse.pdf',gcf,600);
+%%
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10.mat')
+plotFiltersJointResponsesModified(1,[1,2],case10Output.AMA.X,case10Output.AMA.s,case10Output.AMA.f,case10Output.AMA.ctgInd,[],[],[],[1:10]);
+save2pdf('filterResponse/case10FiltersResponse.pdf',gcf,600);
+%%
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12.mat')
+plotFiltersJointResponsesModified(1,[1,2],case12Output.AMA.X,case12Output.AMA.s,case12Output.AMA.f,case12Output.AMA.ctgInd,[],[],[],[1:10]);
+save2pdf('filterResponse/case12FiltersResponse.pdf',gcf,600);
+%% Plot SVD Filter Response
+% Load SVD results struct
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case9SVDResults.mat')
[…]

### 2017-10-07 codeForFigures/codeToMakeFigures/plotBarGraphs.m

@@ -1,0 +1,153 @@
+% This script plots the RMSE bar graphs for the linear, SVD and AMA 
+% methods. 
+% Three bar graphs are produced.
+% 1. Comparison of Naive, Linear, SVD and AMA methods for each case.
+% 2. Performance of SVD Filters from one case on stimuli of other cases.
+% 3. Performance of AMA Filters from one case on stimuli of other cases.
+%
+% VS wrote this Oct 7 2017
+
+
+% Load the results for all cases
+% SVD Results
+clear;
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case9SVDResults.mat']);
+results9SVD = results.case9Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case10SVDResults.mat']);
+results10SVD = results.case10Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12SVDResults.mat']);
+results12SVD = results.case12Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12RotatedSVDResults.mat']);
+results12RSVD = results.case12Rotated;
+
+% AMA Results
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9.mat']);
+results9AMA = results.case9Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10.mat']);
+results10AMA = results.case10Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12.mat']);
+results12AMA = results.case12Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12Rotated.mat']);
+results12RAMA = results.case12Rotated;
+
+% Linear Results
+
+linearCase9 = load('/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case9.mat');
[…]

### 2017-10-07 codeForFigures/codeToMakeFigures/plotFiltersColor2D.m

@@ -1,0 +1,62 @@
+function plotFiltersColor2D(f,fSmp,figh,overallTitle,bsmoothing)
+
+% function plotFilters_Defocus(f,fSmp,figh)
+%
+%   example call: plotFilters_Defocus(f)
+%
+% plot filters for defocus estimation
+%
+% f:          filter weights
+% fSmp:       values at which filter weights are sampled
+% figh:       figure handle
+
+if ~exist('fSmp','var') || isempty(fSmp) fSmp = [0:(size(f,1)/2-1)]; fSmp = fSmp-max(fSmp)/2-1;  end
+if ~exist('figh','var') || isempty(figh) figh = []; end
+
+% HANDLE FIGURE
+if isempty(figh); figure;
+else              figure(figh);
+end
+set(gcf,'position',[991 973 500 300]);
+
+% PLOT
+for i = 1:size(f,2)
+    % SUBPLOT ORGANIZATION: <= 3 plot each row, 1 row for each filter
+    if ~bsmoothing        
+        fSmooth = zeros(size(f,1),size(f,2));
+        fSmooth(:,i) = f(:,i);
+    else
+        sizeOfGrid = sqrt(size(f,1)/3);
+        [X,Y] = meshgrid((1:sizeOfGrid),(1:sizeOfGrid));
+        [XX,YY] = meshgrid((1:0.25:sizeOfGrid),(1:0.25:sizeOfGrid));
+        fSmooth = zeros(length(XX(:)),size(f,2));
+        for kk = 1:3
+            fSmooth((kk-1)*length(XX(:))+1:kk*length(XX(:)),i) = ...
+                griddata(X(:),Y(:),f((kk-1)*length(X(:))+1:kk*length(X(:)),i),XX(:),YY(:));
+        end
+    end
+    fSqr = reshape(fSmooth(:,i),[sqrt(size(fSmooth,1)/3) sqrt(size(fSmooth,1)/3) 3]); 
+    for j = 1:3, 
+        subplot(size(fSmooth,2),3,(i-1)*3+j);         
+        imagesc(fSqr(:,:,j));
+        set(gca, 'XTick', []);
+        set(gca, 'YTick', []);
+        axis square;
+        
+        colormap(cmapBWR);
+        caxis([-.04 .04]); colormap(cmapBWR);        
+        switch j
+            case 1
+                channelName = ' L';
+            case 2
+                channelName = ' M';
+            case 3
+                channelName = ' S';
+        end
[…]

### 2017-10-07 codeForFigures/codeToMakeFigures/plotFiltersJointResponsesModified.m

@@ -1,0 +1,113 @@
+function plotFiltersJointResponsesModified(bPltRsp,fPairs,X,sTrn,fTrn,ctgIndTrn,sTst,fTst,ctgIndTst,ctg2plt,rMax,fano,var0,axisLims,bPLOTellipse)
+
+% function plotFiltersJointResponses(bPltRsp,fPairs,X,sTrn,fTrn,ctgIndTrn,sTst,fTst,ctgIndTst,ctg2plt,rMax,fano,var0,axisLims,bPLOTellipse)
+%
+%   example call: plotFiltersJointResponses(1,[1 2; 3 4],X,s,f,ctgInd)
+%
+% plot joint filter responses for specified filter pairs
+%
+% bPltRsp:      boolean indicating whether to scatter plot responses or not
+%               1 -> scatter plot responses
+%               0 -> don't (plots only rsp ellipses)
+% fPairs:       filter pairs to plot                 [ nPairs  x    2    ]
+% X:            category values                      [ 1       x  nCtg   ]
+% sTrn:         stimuli           (training set)     [ d       x nStmTrn ]
+% fTrn:         filters           (training set)     [ d       x    q    ]
+% ctgIndTrn:    category indices  (training set)     [ nStmTrn x    1    ]
+%               having nCtg unique values
+% sTst:         stimuli           (  test   set)     [ d       x nStmTst ]
+%               default = sTrn
+% fTst:         filters           (  test   set)     [ d       x    q    ] 
+%               default = fTrn
+% ctgIndTst:    category indices  (  test   set)     [ nStmTst x    1    ]
+%               default = ctgIndTrn
+% rMax:         response max
+% fano:         response fano factor
+% var0:         response baseline variance
+% axisLims:     manual control over axis limits (e.g. rMax*[-1 1 -1 1])
+% bPLOTellipse: plot ellipse or not
+%               1 -> plot 
+%               0 -> not
+
+% INPUT HANDLING
+if ~exist('sTst',        'var') || isempty(sTst)         sTst      = sTrn;              end
[…]

### 2017-10-07 codeForFigures/codeToMakeFigures/plotRMSEvsEigValSVD.m

@@ -1,0 +1,83 @@
+% This script plots the RMES v/s the number of eigenvalues used for 
+% lightness estimation. We plot the RMSE for AMA and SVD cases together in
+% one figure.
+% The script first loads all data and then plots the RMSE.
+%
+% VS wrote this Oct 7 2017.
+
+% Load the files
+clear all;
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case9SVDResults.mat']);
+results9SVD = results.case9Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case10SVDResults.mat']);
+results10SVD = results.case10Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12SVDResults.mat']);
+results12SVD = results.case12Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12RotatedSVDResults.mat']);
+results12RSVD = results.case12Rotated;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9.mat']);
+results9AMA = results.case9Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10.mat']);
+results10AMA = results.case10Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12.mat']);
+results12AMA = results.case12Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12Rotated.mat']);
+results12RAMA = results.case12Rotated;
+
+%%
+% Make the directory where the figures will be stored
+if (~exist('RMSEvsNEigVals','dir'))
+    mkdir('RMSEvsNEigVals');
+end
+
+% Define the colors to be used for each method
+color9SVD  = '--k';
+color10SVD = '--b';
+color12SVD = '--r';
+color9AMA  = 'k';
+color10AMA = 'b';
+color12AMA = 'r';
+
[…]

### 2017-10-07 codeForFigures/CopyOverFigures.m
added CopyOverFigures

@@ -54,54 +54,3 @@ unix(copyCmd);
 copyCmd = ['cp ' fullfile(figuresStorageDirectory,'barGraphs','AMASummaryBarGraph.pdf') ' ' fullfile(figureDir,'Figure8','Figure8_c.pdf')];
 unix(copyCmd);
 
-% Figure2: Psychophysical data
-analysisOutputFigDir = fullfile(outputBaseDir,'xPsychoBasic','parametricConditions2','c32_pnt_rot0_shad4_blk40_cen40_vs_shd_rot0_shad4_blk40_cen40_t1/aqr/');
-copyCmd = ['cp ' fullfile(analysisOutputFigDir,'aqr-c32_pnt_rot0_shad4_blk40_cen40_vs_shd_rot0_shad4_blk40_cen40_t1-2_exampleOne.eps') ' ' fullfile(figureDir,'Figure2A_PsychometricFunctionExample.eps')];
-unix(copyCmd);
-copyCmd = ['cp ' fullfile(analysisOutputFigDir,'Summary_gain_aqr_32_example.eps') ' ' fullfile(figureDir,'Figure2B_PaintShadowEffectExample.eps')];
-unix(copyCmd);
-analysisOutputFigDir = fullfile(outputBaseDir,'xPsychoSummary','gain');
-copyCmd = ['cp ' fullfile(analysisOutputFigDir,'OriginalPaintShadowGainsWithControl.eps') ' ' fullfile(figureDir,'Figure2C_PaintShadowEffectSummary.eps')];
-unix(copyCmd);
-
-% Figure 5B: Average psychophyical probability correct figure
-analysisOutputFigDir = fullfile(outputBaseDir,'xPsychoSummary','Gain');
-copyCmd = ['cp ' fullfile(analysisOutputFigDir,'OriginalPaintShadowAverageProbCorrect.eps') ' ' fullfile(figureDir,'Figure5B_AveragePsychoProbCorrect.eps')];
-unix(copyCmd);
-
-%% Physiology
-%
-% Cd to popdecode.  Run ProprocessRunAll; ExtractedRunAll; SummarizeRunAll;
-
-% Figure 6: PCA projection example, panels B-D.  These are figures similar
-% to ones Marlene made, but hers are cross-validated and we used those in the 
-% paper.
-%
[…]

### 2017-10-10 Draft1/draft1.tex
restrucuturing
editing

--- 2017-10-07 draft1.tex
@@
 \section{Introduction}
-I am trying to add to git.
 The color of an object has important behavioral implications.
@@
 In this work, we study a simpler analogue of color constancy called lightness constancy.
-Here, we consider the lightness component of the 3D color space.
+Of the 3D human perceptual color space, we only consider the lightness component.
 Lightness is the attribute that determines the brightness of a color.
+A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color.
 For achromatic objects, it is the property that changes from black to gray to white.
-A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color.
 We study the effects of variations in the reflected light on the perceived lightness of an object.
 
-% Figure 1
+% Figure 1: Introduction
 \begin{figure}[h]
@@
 		\centering
-        \includegraphics[width=\textwidth]{introSchematic.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
         \caption{}
@@
     \begin{subfigure}{0.45 \textwidth}   
-        \includegraphics[width=\textwidth]{introExampleFigure.jpeg}
+        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
         \caption{}
@@
 
-The factors that lead to variations in the reflected light can broadly be categorized into two categories: geometrical (shape,size, relative position, etc.) and spectral (surface reflectance, diffusivity, etc.).
-Here we focus on spectral variations.
-Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness.
-We are interested in identifying the computations that should be performed on the visual signal to achieve lightness constancy (Fig.\ref{fig:introExampleFigure}).
+The variations in the reflected light can result from either geometrical factors (like shape, size, relative position of objects, etc.) or spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
+In this work, we focus on the spectral factors.
+Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness perception.
+We are interested in identifying the computations that can lead to stable lightness perception and constancy (Fig.\ref{fig:introExampleFigure}).
 
@@
 
-Our approach involves generating a database of multi-spectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene.
-The label refers to the perceived lightness of the target object if it were placed under a standard light source ($D_{65}$ daylight spectrum).
+We employ a supervised learning approach to understand this phenomenon.
+Our approach involves generating a database of multi-spectral images of naturalistic scenes.
+These images are labeled by the lightness of a specific target object in the scene.
+The image label depends on the reflectance of the target object.
+It refers to the perceived lightness of the target object if it were placed under a standard light source ($D_{65}$ daylight spectrum).
 We generate hundreds of multi-spectral images at several fixed values of the target object standard lightness.
-At a particular lightness level, we allow variations in the surface reflectance spectra of the objects (both the target and surround) and the illumination spectra of the light sources (Fig.
+At a particular lightness level, we allow variations in the surface reflectance spectra of the objects (both the target and the surround objects) and the illumination spectra of the light sources (Fig.
 \ref{fig:introExampleFigure}.
-Here we show the results for three cases resulting from the combination of such spectral variations (Fig.\ref{fig:studiedCases}.
-These are: 1.
+
+In this work, we study three cases resulting from the combination of such spectral variations (Fig.\ref{fig:studiedCases}.
+These cases are: 1.
 Variations in target object spectra (Fig.\ref{fig:targetVarying}) with fixed illumination and background surface reflectance spectra, 2.
@@
 
-% Figure 2
+% Figure 2: Cases Studied
 \begin{figure}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-		\includegraphics[width=\textwidth]{targetVarying.jpeg}
+		\includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_a.jpeg}
 		\caption{Case 1}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{targetIlluminantVarying.jpeg}
+        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_b.jpeg}
         \caption{Case 2}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{allSpectraVarying.jpeg}
+        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_c.jpeg}
         \caption{Case 3}
@@
     \end{subfigure}    
-    \caption{{\bf Spectral Variations Studied:} sRGB rendition of images studied in our work.
+    \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of images studied in our work.
 The numbers on the left are the standard lightness level of the target object.
@@
 
-Having generated the database of labeled multi-spectral images for each one of these cases, we simulate the retinal cone response to these images using an accurate model of the front end of the visual system.
-The cone-responses dataset, labeled with the standard lightness of the target object, are analyzed using supervised computational learning methods.
-We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, SVD-LDA regression and accuracy maximization analysis.
+Having generated the database of labeled multi-spectral images for each one of these cases, we simulate the retinal cone response to these images using an accurate model of the eye.
+These cone-responses datasets, that are labeled with the standard lightness of the target object, are analyzed using supervised computational learning methods.
+We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, a generalized SVD regression and accuracy maximization analysis.
 These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness.
@@
 In the methods section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}).
-Next, we describe the steps to simulate the response of the visual system to these images (\nameref{method:Isetbio}).
+Next, we describe the steps to simulate the response of the retinal cones to these images (\nameref{method:Isetbio}).
 Finally, we describe the three learning methods we have used in our analysis (\nameref{method:SupervisedLearning}).
-In the results section, we first the show the estimates and performance of each one of the supervised methods for the three cases with different spectral variations.
-We show that for spectral variations that allow variation either only in the shape of the target surface reflectance or the background surface reflectance or the spectral power distribution of the source of light, the standard lightness, $Y_{65}$ can be recovered by simple manipulations of the reflected light captured by the visual system.
-For example, if the illumination spectra of the light sources and the background are held fixed, wile the target reflectance spectra change (case 1), $Y_{65}$ can be recovered directly from the light reflected off the target object.
-If  the surface reflectance of the target object  and the illumination spectra of the light sources are allowed to vary, with fixed background reflectance spectra (case 2), $Y_{65}$ can be recovered by from the contrast between the target and the background.
+In the results section, we show the estimates and performance of each one of the supervised methods for the three cases with different spectral variations.
+
+We show that for spectral variations that allow variation either only in the target surface reflectance or the background surface reflectance or the spectral power distribution of the source of light, the standard lightness, $Y_{65}$ can be recovered by simple manipulations of the reflected light captured by the visual system.
+For example, if the illumination spectra of the light sources and the background are held fixed, while the target reflectance spectra change (case 1), $Y_{65}$ can be recovered directly from the light reflected off the target object.
+If the surface reflectance of the target object and the illumination spectra of the light sources are allowed to vary, but the background reflectance spectra is fixed (case 2), $Y_{65}$ can be recovered by from the contrast between the target and the background.
 When all the spectral features in the scene are allowed to change (case 3), $Y_{65}$ can not be recovered from a simple manipulations of the light captured by the visual system.
@@
 
-% Figure 3
+% Figure 3: Methods
 \begin{figure}
@@
 		\centering
-        \includegraphics[width=\textwidth]{3DScene.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_a.png}
         \caption{A typical 3D Scene}
@@
     \hspace{0.1 \textwidth}
-        \includegraphics[width=\textwidth]{croppedImage.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_b.png}
         \caption{Cropped Image}
@@
     \hspace{0.1 \textwidth}
-        \includegraphics[width=\textwidth]{croppedImageWithMosaic.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_c.png}
         \caption{Optical Image}
@@
     \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{coneContrast.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_d.png}
         \caption{LMS cone contrast}
@@
 		\centering
-        \includegraphics[width=\textwidth]{case9SVD.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_a.pdf}
         \caption{SVD First 2 RFs}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{case9AMA.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_b.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{case9FiltersResponse.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_c.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{case9Results.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_d.pdf}
         \caption{Lightness Estimates}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{RMSEvsNFilters16.pdf}
+\includegraphics[width=0.3\textwidth]{../Figures/Figure5/Figure5.pdf}
 \caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs in our analysis.}
@@
 		\centering
-        \includegraphics[width=\textwidth]{case10SVD.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_a.pdf}
         \caption{SVD First 2 RFs}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{case10AMA.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_b.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{case10FiltersResponse.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{case10Results.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
         \caption{Luminance Estimates}
@@
 		\centering
-        \includegraphics[width=\textwidth]{case12SVD.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_a.pdf}
         \caption{SVD First 2 RFs}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{case12AMA.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{case12FiltersResponse.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{case12Results.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_d.pdf}
         \caption{Luminance Estimates}
@@
 
-\begin{comment}
 % Figure 8
@@
 \begin{subfigure}[b]{0.3 \textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{case9AcrossCaseComparisonSVD.pdf}
-        \caption{SVD RFs of Case 1}
-        \label{fig:case9AcrossCaseComparisonSVD}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.3 \textwidth}   
-        \includegraphics[width=\textwidth]{case10AcrossCaseComparisonSVD.pdf}
-        \caption{SVD RFs of Case 2}
-        \label{fig:case10AcrossCaseComparisonSVD}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{case12AcrossCaseComparisonSVD.pdf}
-        \caption{SVD RFs of Case 3}
-        \label{fig:case12AcrossCaseComparisonSVD}
-    \end{subfigure}
-    \label{fig:SVDComparison}
-    \caption{SVD Filter Comparison:}
-\end{figure}
-
-% Figure 9
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.3 \textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{case9AcrossCaseComparisonAMA.pdf}
-        \caption{AMA RFs of Case 1}
-        \label{fig:case9AcrossCaseComparisonAMA}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.3 \textwidth}   
-        \includegraphics[width=\textwidth]{case10AcrossCaseComparisonAMA.pdf}
-        \caption{AMA RFs of Case 2}
-        \label{fig:case10AcrossCaseComparisonAMA}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{case12AcrossCaseComparisonAMA.pdf}
-        \caption{AMA RFs of Case 3}
-        \label{fig:case12AcrossCaseComparisonAMA}
-    \end{subfigure}
-    \label{fig:AMAComparison}
-    \caption{AMA Filter Comparison:}
-\end{figure}
-\end{comment}
-
-% Figure 10
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{summaryBarGraph.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
 	\caption{Performance of methods}
@@
     \begin{subfigure}[b]{0.3 \textwidth}   
-	\includegraphics[width=\textwidth]{SVDSummaryBarGraph.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
 	\caption{SVD RF Performance}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{AMASummaryBarGraph.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
 	\caption{AMA RF Performance}
@@
 
+% Figure 9
 \begin{figure}[t]
@@
 \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{baseSceneLibrary.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
         \caption{Library }
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{baseSceneMill.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.png}
         \caption{Mill}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{baseSceneTableChairs.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.png}
         \caption{Table-Chairs}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{baseSceneIndoorPlant.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
         \caption{Indoor-plant}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{baseSceneWarehouse.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_e.png}
         \caption{Warehouse}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{baseSceneCheckerBoard.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_f.png}
         \caption{Checkerboard}
@@
 
+% Figure 10
 \begin{figure}[h]
@@
 \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{libraryWithBigBall.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.png}
         \caption{Big-ball}
@@
 \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{libraryWithSmallBall.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.png}
         \caption{Small-ball}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{libraryWithBarrel.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.png}
         \caption{Barrel}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{libraryWithXylophone.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.png}
         \caption{Xylophone}
@@
 	\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{libraryWithRingToy.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_e.png}
         \caption{Ring toy}
@@
     	\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{libraryWithChampagneBottle.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_f.png}
         \caption{Champagne Bottle}
@@
 [GOT TO HERE.  DHB.]
+% Figure11
 \begin{figure}
@@
     \centering
-        \includegraphics[width=\textwidth]{targetVariation.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.png}
         \caption{Target spectra}
@@
     \centering
-        \includegraphics[width=\textwidth]{backgroundVariation.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.png}
         \caption{Background spectra}
@@
     \centering
-        \includegraphics[width=\textwidth]{illuminationVariation.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.png}
         \caption{Illumination spectra}
@@
     \centering
-        \includegraphics[width=\textwidth]{targetPosition.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_d.png}
         \caption{Target position}
@@
     \centering
-        \includegraphics[width=\textwidth]{targetSizeOrientation.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_e.png}
         \caption{Target Size/Orientation}
@@
 
+% Figure 12
 \begin{figure}
 \centering
-	\includegraphics[width=\textwidth]{illumination.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure12/Figure12.pdf}
     \caption{Illumination Generation}
@@
 
+% Figure 13
 \subsection{Reflectance Spectrum}
@@
 \centering
-	\includegraphics[width=\textwidth]{reflectance.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13.pdf}
     \caption{Reflectance Generation}
@@
 
+% Figure 14
 \begin{figure}
 \centering
-	\includegraphics[width=\textwidth]{target.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14.pdf}
     \caption{Target Reflectance Generation}
@@
 
-\begin{figure}
-\centering
-	\includegraphics[width=0.6 \textwidth]{cases.pdf}
-    \caption{\bf{Spectral variations considered in our analysis.} }
-    \label{fig:casesIcons}
-\end{figure}
+%\begin{figure}
+%\centering
+%	\includegraphics[width=0.6 \textwidth]{cases.pdf}
+%    \caption{\bf{Spectral variations considered in our analysis.} }
+%    \label{fig:casesIcons}
+% \end{figure}
 

### 2017-10-11 Draft1/draft1.tex
typed linaer regression

@@
 
-Having generated the database of labeled multi-spectral images for each one of these cases, we simulate the retinal cone response to these images using an accurate model of the eye.
-These cone-responses datasets, that are labeled with the standard lightness of the target object, are analyzed using supervised computational learning methods.
-We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, a generalized SVD regression and accuracy maximization analysis.
+After generating databases of labeled multi-spectral images for each one of these cases, we simulate the response of the cones in the retina cone using an accurate model of the eye.
+These cone-responses datasets, that are labeled with the standard lightness of the target object, are then analyzed using supervised computational learning methods.
+
+We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, a generalized SVD regression and accuracy maximization analysis (AMA).
+The linear regression has been performed on the cones corresponding to the center pixel of the target object.
+The other two methods take the response of all the cones in the model retina.
+While, SVD regression a linear transformation to estimate the lightness, AMA uses a non-linear transform of the data.
 These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness.
@@
 The response of the cones are measured in terms of the number of isomerizations in the cone segment ({\it over what time ??}).
-Since, S cones response are much lower than of L and M cones, to mdoel the amplification of the s cone response downstream, we rescale the cone response functions by the total area under the response curves.
+Since, S cones response are much lower than of L and M cones, to model the amplification of the S cone response downstream, we rescale the cone response functions by the total area under the response curves.
 This leads to comparable number of isomerizations in the L, M and S cone on the presentation of an image.
-We interpolate the responses of cones in each cone class to get a 51x51 cone response image for each cone class.
-Further, the three 51x51 cone response matrix corresponding to each one of the L, M and S cones are then rescaled by the mean cone response to model contrast adaption in the retina.
-The mean is calculated over all the 3x51x51 cones in the de-mosaic response matrix.
+We interpolate the responses of cones in each cone class to get a $51 \times 51$ cone response image for each cone class.
+
+The three $51 \times 51$ cone response matrix corresponding to each one of the L, M and S cones are then reshaped into a $7803 \times 1$ vector.
+To model the contrast adaptation in the visual system, we subtract the mean of the vector from each entry and divide by the mean.
+We further rescale the vector to have norm 1.
+The cone-response vectors corresponding to the N images for each case are concatenated into a $7803 \times N$ contrast normalized matrix $C$.
+The corresponding labels are represented by a $1 \times N$ row vector $Y$.
 
 \subsection{Supervised Learning methods} \label{method:SupervisedLearning}
-\subsubsection*{Linear Regression}
+\subsubsection*{Linear Regression} To estimate the target object lightness using linear regression, we solve the equation $A_{(1,3)}*C_{(3,N)} = Y_{(1,N)}$.
+Here, $Y_{(1,N)}$ corresponds to the row vector of the lightness labels for the N images in the dataset.
+$C_{(3,N)}$ corresponds to the matrix of cone responses corresponding to the central pixel.
+Each column represents the response to one image and the rows corresponds to the contrast normalized L, M and S cone response of the center pixel.
+The coefficient matrix $A$ can be obtained as $A = Y*C^{-1}$.
+
+The L, M and S response to the center pixel on the target object is calculate by taking the average of a 3x3 patch of cones near the center of the target.
+
 \subsubsection*{SVD regression}
+This 
 \subsubsection*{Accuracy maximization analysis}

### 2017-10-11 Draft1/draft1.tex
adding text

@@
 \usepackage{amsmath}
+\usepackage{bbm}
 \usepackage{amssymb}
@@
 \subsubsection*{SVD regression}
-This 
+This method is a generalization of principal component analysis for labeled data.
+Briefly, given a dataset $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds directions along which the projections of the data maximize the separation between the images with different labels, while clustering the images with similar labels together.
+Mathematically, the method searches for a direction $\hat{u}$ such that the cost function:
+
+\begin{align}
+S = \sum\limits_{j,j'}\left(\hat{u}^\intercal C(:,j) - \hat{u}^\intercal C(:,j')\right)^2 \left(Y(j)-Y(j') \right)^2,
+\end{align} 
+where $C(:,j)$ represents the $j$'th column of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the matrix:
+
+\begin{align}
+N C^\intercal Y_D^2 C - 2(Y*\mathbbm{1})C^\intercal Y_D C + (Y*Y^\intercal) (C^\intercal C)
+\end{align}
+
 \subsubsection*{Accuracy maximization analysis}
@@
 
-% Figure 8
+% Figure 8stimulusIntensities(1)-1
 \begin{figure}

### 2017-10-12 Draft1/draft1.tex
edits

@@
 \title{Lightness constancy under fixed geometry}
-\abstract{Abstract goes here.}
+\abstract{Color constancy is the ability of human visual system to stably perceive the color of an object under variations in the light reflected from the object.
+This is a very significant invariance detection ability with important behavioral implications.
+The light captured by our visual system depends not just on the object of interest, but also the lighting and other objects in the surround.
+In order to corectly identify the object color, the variations resulting from the surround related factors must be discarded.
+To understand the computational principles that can lead to color constancy, we study constancy of the lightness component of the 3D color space.
+Lightness is the attribute of the color space that determines the brightness of the color.
+We study the effects of spectral variations, specifically the variations in the object reflectance spectra and the light source illumination spectra, on the perceived lightness of an object.
+We have employed a supervised learning approach to study lightness constancy.
+We have developed a computational software that generates naturalistic hyper-spectral images of 3D scenes.
+The software allows precise control of the geometrical and spectral properties of the objects and lights in the scene.
+It takes into account the statistical structure of the spectral variations in natural scenes.
+It also produces the response of the retinal cones to the hyperspectral images through an accurate model of human visual system.
+We label the iamges generated by the software through the standard lightness (lighness under standard daylight spectrum D65) of a specific target object in the scene.
+We study the corresponsding dataset of labeled cone responses using supervised computational learning methods.
+Our analysis shows that under simple spectral variations, like the variation only in the spectrum of the target object, or of the background object, or of the light source, the standard lightness can be recovered by simple trasnformations of the reflected light.
+When all spectra vary simultaneously, while it is not easy to recover the lightess through simple transformations, a decoding cheme that compares the light from the target and the surround and properly adds the response of the L,M and S cones can recover the lightness within about 15\% RMSE.
+}
 
@@
 In this work, we study a simpler analogue of color constancy called lightness constancy.
-Of the 3D human perceptual color space, we only consider the lightness component.
 Lightness is the attribute that determines the brightness of a color.
@@
 For achromatic objects, it is the property that changes from black to gray to white.
-We study the effects of variations in the reflected light on the perceived lightness of an object.
+Here, we only consider the lightness component of the  3D human perceptual color space and study the effects of variations in the reflected light on the perceived lightness.
 
@@
 In this work, we focus on the spectral factors.
-Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness perception.
-We are interested in identifying the computations that can lead to stable lightness perception and constancy (Fig.\ref{fig:introExampleFigure}).
+Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness perception  (Fig.\ref{fig:introExampleFigure}).
+We are interested in identifying the computations that can lead to stable lightness perception.
 
@@
 \caption{{\bf Approach:} We have employed a supervised learning approach to study color constancy.
-We first generate a large dataset of multi-spectral images labeled with the lightness level of the target object.
+We first generate a large dataset of hyperspectral images labeled with the lightness level of the target object.
 We generate images at multiple lightness levels, with images at the same lightness level having variable object reflectance spectra and illumination spectra.
-These multi-spectral images are used to simulate the response of the visual system.
+These hyperspectral images are used to simulate the response of the visual system.
 We use isetbio toolbox to model the optics and physiology of early vision and produce the response of the cones in the retina.
@@
 We employ a supervised learning approach to understand this phenomenon.
-Our approach involves generating a database of multi-spectral images of naturalistic scenes.
-These images are labeled by the lightness of a specific target object in the scene.
-The image label depends on the reflectance of the target object.
-It refers to the perceived lightness of the target object if it were placed under a standard light source ($D_{65}$ daylight spectrum).
-We generate hundreds of multi-spectral images at several fixed values of the target object standard lightness.
+We generate a database of hyperspectral images of naturalistic scenes labeled by the lightness of a specific target object in the scene.
+The images are labeled with perceived lightness of a uniform surface having the target object reflectance placed under the standard daylight spectrum $D_{65}$.
+We generate hundreds of hyperspectral images at several fixed values of the target object standard lightness.
 At a particular lightness level, we allow variations in the surface reflectance spectra of the objects (both the target and the surround objects) and the illumination spectra of the light sources (Fig.
@@
 
-In this work, we study three cases resulting from the combination of such spectral variations (Fig.\ref{fig:studiedCases}.
+In this work, we study three cases resulting from the combination of such spectral variations (Fig.\ref{fig:studiedCases}).
 These cases are: 1.
@@
 
-After generating databases of labeled multi-spectral images for each one of these cases, we simulate the response of the cones in the retina cone using an accurate model of the eye.
+After generating databases of labeled hyperspectral images for each one of these cases, we simulate the response of the cones in the retina cone using an accurate model of the eye.
 These cone-responses datasets, that are labeled with the standard lightness of the target object, are then analyzed using supervised computational learning methods.
@@
 
-We show that for spectral variations that allow variation either only in the target surface reflectance or the background surface reflectance or the spectral power distribution of the source of light, the standard lightness, $Y_{65}$ can be recovered by simple manipulations of the reflected light captured by the visual system.
-For example, if the illumination spectra of the light sources and the background are held fixed, while the target reflectance spectra change (case 1), $Y_{65}$ can be recovered directly from the light reflected off the target object.
-If the surface reflectance of the target object and the illumination spectra of the light sources are allowed to vary, but the background reflectance spectra is fixed (case 2), $Y_{65}$ can be recovered by from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 3), $Y_{65}$ can not be recovered from a simple manipulations of the light captured by the visual system.
-Here, we have used a Bayesian supervised learning method called accuracy maximization analysis to estimate $Y_{65}$ of the target object.
-Using this method, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
+We show that for cases that allow variation either only in the target surface reflectance or the background surface reflectance or the spectral power distribution of the source of light, the standard lightness ($Y_{65}$) can be recovered by simple manipulations of the reflected light captured by the visual system.
+For case 1, (variations only in target obejct reflectance spectra), $Y_{65}$ can be recovered directly from the light reflected off the target object.
+For case 2, where both the target object reflectance and light source spectra vary, $Y_{65}$ can be recovered by from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered from a simple manipulations of the light captured by the visual system.
+Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
+Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
 
-Finally, we compared the generality of the methods for lightness estimation by comparing the optimal receptive fields of one case to the others.
-The optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, the receptive fields give more weight to the L and M cone responses compared to S cone responses.
+Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
+Additionally, lightness estimation invovles a weighted sum of the L, M and S cone responsese where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
+Comparing the performace of the receptive fields of one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
 We discuss the implications of such receptive fields on lightness constancy.
@@
 \subsection{Image database} \label{method:VirtualWorld}
-In this section we briefly describe our image generation software, that we call Virtual world color constancy (VWCC).
+In this section we briefly describe our image generation software that we call Virtual world color constancy (VWCC).
 The details of the software are provided in the supplementary information section.
@@
 (The light source in not visible.) Next, we assign a surface reflectance spectrum and an illumination spectrum to each object and light source in the scene.
-The surface reflectance of the target object is assigned such that the perceived lightness of the target object under D65 daylight spectrum has a fixed value.
-Once these spectral properties have been assigned, we render a 320x240 pixel$^2$ 2d multi-spectral images of the scene at 31 frequencies (linearly spaced between 400nm - 700nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}.
-We generate hundreds of such scenes and corresponding multi-spectral images for at 10 linearly spaced lightness levels between 0.2 and 0.6.
+For the target object the surface reflectance is assigned such that the perceived lightness of the target object under D65 daylight spectrum has a fixed value.
+Once these spectral properties have been assigned, we render a 320x240 pixel$^2$ 2d hyperspectral images of the scene at 31 frequencies (equal linear spacing between 400nm - 700nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}.
+We generate hundreds of such scenes and the corresponding hyperspectral images at 10 linearly spaced lightness levels between 0.2 and 0.6.
 For the images at a fixed lightness level, the reflectance and illumination spectra are assigned according to the spectral variations allowed under each case.
-Next, we crop a 51x51 pixel$^2$ part of the multi-spectral image containing the target object for further analysis (\ref{fig:croppedImage}).
+Next, we crop a 51x51 pixel$^2$ part of the hyperspectral image containing the target object for further analysis (\ref{fig:croppedImage}).
 Fig.
@@
 \subsection{Model of Visual System} \label{method:Isetbio}
-We simulate the visual system response using isetbio software toolbox.
+We simulate the visual system response using \href{http://isetbio.org}{Isetbio} software toolbox.
 Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics.
-We use the multi-spectral cropped image (fig.\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
+We use the hyperspectral cropped image (fig.\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
 The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
@@
 Since, S cones response are much lower than of L and M cones, to model the amplification of the S cone response downstream, we rescale the cone response functions by the total area under the response curves.
-This leads to comparable number of isomerizations in the L, M and S cone on the presentation of an image.
-We interpolate the responses of cones in each cone class to get a $51 \times 51$ cone response image for each cone class.
+This leads to comparable number of isomerizations in the L, M and S cones.
+Further, to get the response of each cone class at each poistion on the retinal mosaic, we interpolate the response of the cones for each cone class.
+Thus we get a $51 \times 51$ cone response image for each cone class.
 
@@
 \subsubsection*{Linear Regression} To estimate the target object lightness using linear regression, we solve the equation $A_{(1,3)}*C_{(3,N)} = Y_{(1,N)}$.
-Here, $Y_{(1,N)}$ corresponds to the row vector of the lightness labels for the N images in the dataset.
-$C_{(3,N)}$ corresponds to the matrix of cone responses corresponding to the central pixel.
-Each column represents the response to one image and the rows corresponds to the contrast normalized L, M and S cone response of the center pixel.
-The coefficient matrix $A$ can be obtained as $A = Y*C^{-1}$.
+$C_{(3,N)}$ corresponds to the matrix of LMS cone responses corresponding to the center pixel of the image.
+Each column represents the response to one image.
+The rows corresponds to the contrast normalized L, M and S cones response of the center pixel for the N images in the dataset.
+The (unknown) coefficient matrix $A$ can be obtained as $A = Y*C^{-1}$.
 
-The L, M and S response to the center pixel on the target object is calculate by taking the average of a 3x3 patch of cones near the center of the target.
+The L, M and S response to the center pixel on the target object is calculated by taking the average of a 3x3 patch of cones near the center of the target.
 
@@
 \begin{align}
-N C^\intercal Y_D^2 C - 2(Y*\mathbbm{1})C^\intercal Y_D C + (Y*Y^\intercal) (C^\intercal C)
+N C Y_D^2 C^\intercal - 2(Y*\mathbbm{1})C Y_D C^\intercal + (Y*Y^\intercal) (CC^\intercal)-C Y_{D}^2\mathbbm{1}\mathbbm{1}^\intercal C^\intercal +2 C Y_{D} \mathbbm{1}\mathbbm{1}^\intercal Y_{D} C^\intercal - C \mathbbm{1}\mathbbm{1}^\intercal Y_{D}^2 C^\intercal
 \end{align}
@@
 The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
-It then renders a multi-spectral 2D image of each modeled visual scene.
+It then renders a hyperspectral 2D image of each modeled visual scene.
 Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
-In addition, our software simulates the responses of retinal cones to the rendered multi-spectral images using a realistic model of the early human visual system.
+In addition, our software simulates the responses of retinal cones to the rendered hyperspectral images using a realistic model of the early human visual system.
 Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
@@
 The renderer produces 2D hyper-spectral images of the scene at specified wavelengths.
-Finally, these multi-spectral images are used to simulate retinal cone responses using the \href{https://github.com/isetbio}{ISETBIO} software.
+Finally, these hyperspectral images are used to simulate retinal cone responses using the \href{https://github.com/isetbio}{ISETBIO} software.
 
@@
 The spectral manipulations for the various cases studied in this work are described below.
-Multi-spectral 2D images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
-Next, a $51 \times 51$ pixel$^2$ patch of the multi-spectral image was cropped around the target object and cone responses were calculated to these cropped images as described below.
+hyperspectral 2D images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
+Next, a $51 \times 51$ pixel$^2$ patch of the hyperspectral image was cropped around the target object and cone responses were calculated to these cropped images as described below.
 

### 2017-10-13 Draft1/draft1.tex
more editing

@@
 \end{align} 
-where $C(:,j)$ represents the $j$'th column of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the matrix:
+where $C(:,j)$ represents the $j$'th column (image) of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the matrix:
 
 \begin{align}
-N C Y_D^2 C^\intercal - 2(Y*\mathbbm{1})C Y_D C^\intercal + (Y*Y^\intercal) (CC^\intercal)-C Y_{D}^2\mathbbm{1}\mathbbm{1}^\intercal C^\intercal +2 C Y_{D} \mathbbm{1}\mathbbm{1}^\intercal Y_{D} C^\intercal - C \mathbbm{1}\mathbbm{1}^\intercal Y_{D}^2 C^\intercal
+N C Y_D^2 C^\intercal - 2(Y*\mathbbm{1})C Y_D C^\intercal + (Y*Y^\intercal) (CC^\intercal)-C Y_{D}^2\mathbbm{1}\mathbbm{1}^\intercal C^\intercal +2 C Y_{D} \mathbbm{1}\mathbbm{1}^\intercal Y_{D} C^\intercal - C \mathbbm{1}\mathbbm{1}^\intercal Y_{D}^2 C^\intercal.
+\end{align}
+Here, $Y_{D}$ is a diagonal matrix with the elements of the labels vector $Y$ along the diagonal, and $\mathbbm{1}$ is a $N\times 1$ vector of ones.
+
+\subsubsection*{Accuracy maximization analysis}
+AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
+It finds the receptive fields that are optimal for performing a well defined behavioral task.
+Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task, which is implicitly defined in terms of the labels.
+The optimal filters are the ones whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
+The filters are learned via gradient descent with the aid of an optimal Bayesian decoder that is matched to the filters throughout the learning process.
+
+Let us assume that there is a latent variable ($Y$) that takes the values $\{Y_k: k\in[1,N_{\nu}] \}$.
+The $l$'th stimuli corresponding to the $k$'th category of the latent variable is $s_{kl}$.
+Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
+Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the latent variable ($Y_k$) corresponding to the stimuli $s_{kl}$ as $\hat{Y}_{kl}$.
+Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and a mean cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.
+
+Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}, l\in[1,N_k]\}$.
+$N_{\nu}$ is the total number of labels and $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
+Thus,
+\begin{align}
+{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{kl} \bar{\mathcal{C}}_{kl}.
+\label{eq:fopt}
 \end{align}
 
-\subsubsection*{Accuracy maximization analysis}
+AMA employs the Bayes optimal decoder to estimate the optimal estimate.
+The Bayesian decoder computes the posterior probability of the latent variable $p(X|{\textbf {\textit R}})$ and reads out the optimal estimate $\hat{Y}^{\rm opt}$ from the posterior as the value that minimizes the cost.
+By Bayes' theorem, the posterior probability can be written as:
+\begin{align}
+p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{p({\textbf {\textit R} }_{kl}|Y_k)p(Y_k)}{\sum\limits_{i=1}^{N_{\nu}}{p({\textbf {\textit R} }_{kl}|Y_i)p(Y_i)}}.
+\label{eq:posterior}
+\end{align}
+As conditional probability of the filter response is:
+\begin{align}
+p({\textbf {\textit R} }_{kl}|Y_k) = \sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|Y_k),
+\label{eq:condProb}
+\end{align}hat{Y}
+using Eq.\ref{eq:condProb} in Eq.\ref{eq:posterior} we get:
+\begin{align}
+p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|Y_k)\right]p(Y_k)}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})p({\textbf {\textit s} }_{kj}|Y_i)\right]p(Y_i)}}
+\label{eq:finalPosterior}
+\end{align}
+Since, $p({\textbf {\textit s} }_{km}|Y_k) = \frac{1}{N_k}$, and $p(Y_k)=\frac{N_k}{N}$, where $N = \sum\limits_{k=1}^{N_{\nu}}N_{k}$ is total number of samples in the training set, Eq.\ref{eq:finalPosterior} simplifies to
+\begin{align}
+p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km}) \frac{1}{N_k}\right]\frac{N_k}{N}}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij}) \frac{1}{N_i}\right]\frac{N_i}{N}}} = \frac{\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})}{\sum\limits_{i=1}^{N_{\nu}}{\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})}}.
+\label{eq:simplifiedPosterior}
+\end{align}
+Now if the cost associated with the latent variable $Y_k$ and the estimate $\hat{Y}_k$ is $\gamma (Y_k,\hat{Y}_k)$, we have  
+\begin{align}
+\mathcal{C}_{kl} = \sum\limits_{u=1}^{N_{\nu}}\gamma(X_u,\hat{Y}_u)p(X_u|{\textbf{\textit R}}_{kl}),
+\end{align}
+and the total cost associated with the training set is $\bar{\mathcal{C}} = \frac{1}{N} \sum\limits_{k,l}\bar{\mathcal{C}}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle \mathcal{C}_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$.
+The optimal AMA filters are obtained by minimizing $\bar{\mathcal{C}}$ over the filter set ${\textbf {\textit f} }$ (Eq.\ref{eq:fopt}).
+The filters are obtained using gradient descent.
+
+In this work, we assume the noisy response model to be a multivariate gaussian.
+For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{kl,1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$.
+We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be zero mean contrast normalized, i.e., $\langle{s_{kl}}\rangle = 0$ \& ${|s_{kl}|=1}$.
 
 \subsection{Types of spectral variations studied}
-In this work we have studied the effects of spectral variations on perceived lightness.
-The spectral variations in the scene can be categorized into three types.
-The variations in the shape of target object reflectance spectra, the variations in the shape of background object reflectance spectra, and the variations in the shape of the spectral power distribution of light sources.
-Here, we present the results for three cases (fig.\ref{fig:studiedCases}): 1.
-effects of variations in target object spectra (fig.\ref{fig:targetVarying}), 2.
-effects of variations in target object spectra and the light source spectra (fig.\ref{fig:targetIlluminantVarying}), and 3.
-effects of variations in all three spectra (fig.\ref{fig:allSpectraVarying}).
-The rest of the cases are qualitatively similar to one of the cases discussed here, and are discussed in the supplementary materials.
+We have studied the effects of spectral variations on perceived lightness.
+These can be categorized into three types: variations in the shape of target object reflectance spectra, variations in the shape of background object reflectance spectra, and the variations in the shape of the spectral power distribution of light sources.
+Here, we present the results for three cases (Fig.\ref{fig:studiedCases}): 1.
+effects of variations in target object spectra (Fig.\ref{fig:targetVarying}), 2.
+effects of variations in target object spectra and the light source spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
+effects of variations in all three spectra (Fig.\ref{fig:allSpectraVarying}).
+The cases with other types of variations are qualitatively similar to one of the three cases discussed here (see Discussion).
 
@@
 
-\subsection{Accuracy Maximization Analysis}
-AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
-It finds the receptive fields that are optimal for performing a well defined behavioral task.
-Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task, which is implicitly defined in terms of the labels.
-The optimal filters are the ones whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
-The filters are learned via gradient descent with the aid of an optimal Bayesian decoder that is matched to the filters throughout the learning process.
-
-Let us assume that there is a latent variable ($X$) that takes the values $\{X_k: k\in[1,N_{\nu}] \}$.
-The $l$'th stimuli corresponding to the the $k$'th category of the latent variable is $s_{kl}$.
-Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
-Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the latent variable ($X_k$) corresponding to the stimuli $s_{kl}$ as $\hat{X}_{kl}$.
-Given this estimate, one can define a cost function $C_{kl}(X_{kl},\hat{X}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and a mean cost $\bar{C}_{kl}(X_{kl},\hat{X}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.
-
-Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}, l\in[1,N_k]\}$.
-$N_{\nu}$ is the total number of labels and $N_{k}$ is the number of stimuli corresponding to the label $X_k$.
-Thus,
-\begin{align}
-{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{kl} \bar{C}_{kl}.
-\label{eq:fopt}
-\end{align}
-
-AMA employs the Bayes optimal decoder to estimate the optimal estimate.
-The Bayesian decoder computes the posterior probability of the latent variable $p(X|{\textbf {\textit R}})$ and reads out the optimal estimate $\hat{X}^{\rm opt}$ from the posterior as the value that minimizes the cost.
-By Bayes' theorem, the posterior probability can be written as:
-\begin{align}
-p(X_k|{\textbf {\textit R} }_{kl}) = \frac{p({\textbf {\textit R} }_{kl}|X_k)p(X_k)}{\sum\limits_{i=1}^{N_{\nu}}{p({\textbf {\textit R} }_{kl}|X_i)p(X_i)}}.
-\label{eq:posterior}
-\end{align}
-As conditional probability of the filter response is:
-\begin{align}
-p({\textbf {\textit R} }_{kl}|X_k) = \sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|X_k),
-\label{eq:condProb}
-\end{align}
-using Eq.\ref{eq:condProb} in Eq.\ref{eq:posterior} we get:
-\begin{align}
-p(X_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|X_k)\right]p(X_k)}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})p({\textbf {\textit s} }_{kj}|X_i)\right]p(X_i)}}
-\label{eq:finalPosterior}
-\end{align}
-Since, $p({\textbf {\textit s} }_{km}|X_k) = \frac{1}{N_k}$, and $p(X_k)=\frac{N_k}{N}$, where $N = \sum\limits_{k=1}^{N_{\nu}}N_{k}$ is total number of samples in the training set, Eq.\ref{eq:finalPosterior} simplifies to
-\begin{align}
-p(X_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km}) \frac{1}{N_k}\right]\frac{N_k}{N}}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij}) \frac{1}{N_i}\right]\frac{N_i}{N}}} = \frac{\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})}{\sum\limits_{i=1}^{N_{\nu}}{\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})}}.
-\label{eq:simplifiedPosterior}
-\end{align}
-Now if the cost associated with the latent variable $X_k$ and the estimate $\hat{X}_k$ is $\gamma (X_k,\hat{X}_k)$, we have  
-\begin{align}
-C_{kl} = \sum\limits_{u=1}^{N_{\nu}}\gamma(X_u,\hat{X}_u)p(X_u|{\textbf{\textit R}}_{kl}),
-\end{align}
-and the total cost associated with the training set is $\bar{C} = \frac{1}{N} \sum\limits_{k,l}\bar{C}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle C_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$.
-The optimal AMA filters are obtained by minimizing $\bar{C}$ over the filter set ${\textbf {\textit f} }$ (Eq.\ref{eq:fopt}).
-The filters are obtained using gradient descent.
-
-In this work, we assume the noisy response model to be a multivariate gaussian.
-For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{kl,1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$.
-We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be zero mean contrast normalized, i.e., $\langle{s_{kl}}\rangle = 0$ \& ${|s_{kl}|=1}$.
-
-\subsection{Data Analysis} We generate XX number of images with target objects at 10 standard luminance levels linearly spaced between 0.2 to 0.6.
-These limits were chosen because the luminance under the standard source ($D_{65}$) of more than $90\%$ of the natural surface reflectance spectra fell between them.
-Thus we had YY images at each target luminance level.
-We generated the cone responses to these images using ISETBIO.
-The cone response ($I$) were first converted in to weber contrast form using the transformation $\left(I \rightarrow I_{\rm web} = \frac{I}{\langle I \rangle}-1\right)$.
-The weber contrast responses and the target luminance levels were used as the input stimuli and the latent variable, respectively, for AMA.
-The AMA parameters were: $\alpha = xxx$ and $\sigma_0^2 = yyy$.
-
-\subsection{Explanation of the various cases}
-In this work we have labeled the images using the lightness of the target object under  standard daylight spectrum ($D_65$).
-The images are labeled such that the total light reflected from the target object equals a fixed value.
-At this fixed value, we generate multiple images with variations in the spectral properties of the objects and the light sources.
-At fixed target lightness (Y65), spectral variations can result from variations in the shape of: 1.
-Target surface reflectance spectrum, 2.
-Background object surface reflectance, and 3.
-Spectral power distribution of the light source.
-These give rise to 12 distinct cases (Fig.
-\ref{fig:caseIcons}).
-The icons on the left and the top represent the spectrum of the illuminant, the background and the target object.
-For the illuminant and background, only one curve in the represents fixed spectra from image to image.
-Two curve imply that the spectra were varied randomly from image to image.
-For the target object, we show the spectrum at two distinct lightness levels.
-At a particular level, the meaning of the curves is the same as that of illuminant and background icons.
-Additionally, same shape of the target reflectance spectrum at both the levels means that Y65 was changed by changing the mean value of the surface reflectance spectrum keeping the same shape.
-
-%\begin{figure}
-%\centering
-%	\includegraphics[width=0.6 \textwidth]{cases.pdf}
-%    \caption{\bf{Spectral variations considered in our analysis.} }
-%    \label{fig:casesIcons}
-% \end{figure}
-
-To illustrate, in case 1 the spectral power distribution of the light source and the surface reflectance of the background objects are fixed from image to image.
-Further, the shape of the target object surface reflectance also remains the same from to image to image at the same standard lightness level, and only vary in their mean value between standard luminance levels.
-Thus in case 1, at one standard lightness, all images are identical (Fig.
-.
-This is the simplest possible scene variation considered here.
-Similarly, in the most complex case, case 12, all the spectra are allowed to vary from image to image.
-
 \bibliography{references}

### 2017-10-14 Draft1/draft1.tex
edit abstract

@@
 \title{Lightness constancy under fixed geometry}
-\abstract{Color constancy is the ability of human visual system to stably perceive the color of an object under variations in the light reflected from the object.
-This is a very significant invariance detection ability with important behavioral implications.
-The light captured by our visual system depends not just on the object of interest, but also the lighting and other objects in the surround.
-In order to corectly identify the object color, the variations resulting from the surround related factors must be discarded.
-To understand the computational principles that can lead to color constancy, we study constancy of the lightness component of the 3D color space.
-Lightness is the attribute of the color space that determines the brightness of the color.
-We study the effects of spectral variations, specifically the variations in the object reflectance spectra and the light source illumination spectra, on the perceived lightness of an object.
-We have employed a supervised learning approach to study lightness constancy.
-We have developed a computational software that generates naturalistic hyper-spectral images of 3D scenes.
-The software allows precise control of the geometrical and spectral properties of the objects and lights in the scene.
-It takes into account the statistical structure of the spectral variations in natural scenes.
-It also produces the response of the retinal cones to the hyperspectral images through an accurate model of human visual system.
-We label the iamges generated by the software through the standard lightness (lighness under standard daylight spectrum D65) of a specific target object in the scene.
-We study the corresponsding dataset of labeled cone responses using supervised computational learning methods.
-Our analysis shows that under simple spectral variations, like the variation only in the spectrum of the target object, or of the background object, or of the light source, the standard lightness can be recovered by simple trasnformations of the reflected light.
-When all spectra vary simultaneously, while it is not easy to recover the lightess through simple transformations, a decoding cheme that compares the light from the target and the surround and properly adds the response of the L,M and S cones can recover the lightness within about 15\% RMSE.
-}
+\abstract{Human visual system has the ability to stably perceive the color of an object under variations in the reflected light due to surround factors.
+This is a behaviorally significant invariance detection ability whose biological mechanism remains unknown.
+To understand the computational principles that can lead to such invariant perception, here we study the perception of object lightness under spectral variations.
+Lightness is the attribute of the 3D color space that determines the brightness of a color.
+Specifically, we study the effects of variations in reflectance and illumination spectra of the objects and lights sources in a scene on the perceived lightness of an object.
+We have developed a software to generate naturalistic hyper-spectral images of 3D scenes with precise control over the geometrical and spectral properties of the objects and lights in the scene.
+The software also produces the response of the early visual system to these hyper-spectral images.
+We label the images with the lightness of a specific object in the scene and use supervised learning methods to identify the computations that lead to stable lightness perception.
+Our analysis shows that for simple spectral variations, like the ones that allow variations only in the spectrum of the target object, or of the background object, or of the light source, the standard lightness can be recovered by through transformations of the reflected light.
+When all spectra are allowed to vary simultaneously, while it is not easy to recover the lightness through simple transformations, a decoding sheme that compares the light from the target and the surround, and properly adds the response of the L,M and S cones can recover the lightness within about 15\% RMSE.}
 
@@
 \ref{fig:introSchematic}).
-The surround dependent extrinsic factors that affect the reflected light are: the surface reflectance, texture and material properties of the objects in the surround, the illumination spectrum of the sources of light illuminating the object, the geometry, relative position and pose of the objects and light sources in the surround, and the position of the observer.
-As these extrinsic factors vary considerably from scene to scene, the challenge faced by the visual system is to recover a stable perceptual representation of the object's surface reflectance, ignoring the  variations in the reflected light resulting from the extrinsic factors.
+These extrinsic factors are: the surface reflectance, texture and material properties of the objects in the surround, the illumination spectrum of the sources of light illuminating the object, the geometry, relative position and pose of the objects and light sources in the surround, and the position of the observer.
+As these extrinsic factors vary considerably from scene to scene, the challenge faced by the visual system is to recover a stable perceptual representation of the object's surface reflectance, invariant of the extrinsic factors.
 The ability of the visual system to extract such a stable representation, its perceived color, is called color constancy.
@@
 
-In this work, we study a simpler analogue of color constancy called lightness constancy.
+In this work, we identify the computations that lead to stable lightness perception.
 Lightness is the attribute that determines the brightness of a color.
 A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color.
-For achromatic objects, it is the property that changes from black to gray to white.
-Here, we only consider the lightness component of the  3D human perceptual color space and study the effects of variations in the reflected light on the perceived lightness.
+For achromatic objects, lightness is the property that changes from black to gray to white.
+We study the effects of variations in the reflected light on the perceived lightness.
 
@@
 The variations in the reflected light can result from either geometrical factors (like shape, size, relative position of objects, etc.) or spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
-In this work, we focus on the spectral factors.
+Here, we focus on the spectral factors.
 Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness perception  (Fig.\ref{fig:introExampleFigure}).
@@
 \subsection{Case 1}
+Fig.~\ref{fig:case9AllResults} shows the receptive fields and the the AMA lightness estimates for the three cases discussed above.
+We show the target object lightness estimates for there different methods: linear regression on center pixel, SVD regression and AMA.
+As is expected, when only the target object reflectance varies, it is easy to estimate the target object lightness.
+For case 2, where the light source spectra are allowed to vary, although the light captured by the cones vary from image to image, the contrast between the target and the background remains fixed and can be used to estimate the target object lightness.
+Thus, the SVD-LDA and AMA still provide good estimates of the target object lightness.
+In case 3, the most challenging case where all the spectra are allowed to change, AMA still does a reasonable job of estimating the target object lightness.
+AMA mean estimates lie close to the diagonal x=y line.
 
@@
 \end{figure}
-
-\subsection{Lightness estimates and model performance}
-Fig.
-ZZ gives the AMA lightness estimates for the three cases discussed above.
-We show the target object lightness estimates for there different methods: linear regression on center pixel, SVD regression and AMA.
-As is expected, when only the target object reflectance varies, it is easy to estimate the target object lightness.
-For case 2, where the light source spectra are allowed to vary, although the light captured by the cones vary from image to image, the contrast between the target and the background remains fixed and can be used to estimate the target object lightness.
-Thus, the SVD-LDA and AMA still provide good estimates of the target object lightness.
-In case 3, the most challenging case where all the spectra are allowed to change, AMA still does a reasonable job of estimating the target object lightness.
-AMA mean estimates lie close to the diagonal x=y line.
 

### 2017-10-15 Draft1/draft1.tex
more edits

@@
 \title{Lightness constancy under fixed geometry}
-\abstract{Human visual system has the ability to stably perceive the color of an object under variations in the reflected light due to surround factors.
-This is a behaviorally significant invariance detection ability whose biological mechanism remains unknown.
-To understand the computational principles that can lead to such invariant perception, here we study the perception of object lightness under spectral variations.
-Lightness is the attribute of the 3D color space that determines the brightness of a color.
-Specifically, we study the effects of variations in reflectance and illumination spectra of the objects and lights sources in a scene on the perceived lightness of an object.
-We have developed a software to generate naturalistic hyper-spectral images of 3D scenes with precise control over the geometrical and spectral properties of the objects and lights in the scene.
-The software also produces the response of the early visual system to these hyper-spectral images.
-We label the images with the lightness of a specific object in the scene and use supervised learning methods to identify the computations that lead to stable lightness perception.
-Our analysis shows that for simple spectral variations, like the ones that allow variations only in the spectrum of the target object, or of the background object, or of the light source, the standard lightness can be recovered by through transformations of the reflected light.
-When all spectra are allowed to vary simultaneously, while it is not easy to recover the lightness through simple transformations, a decoding sheme that compares the light from the target and the surround, and properly adds the response of the L,M and S cones can recover the lightness within about 15\% RMSE.}
+\abstract{The light that reflects off an object surface and is captured by our eyes varies significantly with its context.
+But, the human visual system has the ability stably perceive the object's color invariant of the context.
+The mechanism of this behaviorally significant invariance detection ability remains largely unknown.
+To understand the computational principles that lead to such invariant perception, we study the perception of object lightness under spectral variations in 3D scenes.
+Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the perceived lightness of an object.
+We have developed a software that generates naturalistic hyper-spectral images of 3D scenes with precise control over the geometrical and spectral properties of the constituents that make a scene.
+We label these images with the lightness of a specific object in the scene.
+Next, we simulate the response of the retinal cones to these hyper-spectral images using an accurate model of the early visual system.
+Using supervised learning methods on these labeled cone response we identify the computations that lead to accurate lightness estimation.
+We show that if only target, or background, or illumination spectra are allowed to vary, the standard lightness can be estimated through simple transformations of the cone responses.
+When all the spectra vary simultaneously, while it is not easy to recover the lightness through simple transformations, a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and S cones can recover the lightness within about 15\% RMSE.}
 
@@
 \ref{fig:introSchematic}).
-These extrinsic factors are: the surface reflectance, texture and material properties of the objects in the surround, the illumination spectrum of the sources of light illuminating the object, the geometry, relative position and pose of the objects and light sources in the surround, and the position of the observer.
-As these extrinsic factors vary considerably from scene to scene, the challenge faced by the visual system is to recover a stable perceptual representation of the object's surface reflectance, invariant of the extrinsic factors.
+These extrinsic factors, such as the surface reflectance, texture and material properties of the objects in the surround, the illumination spectrum of the sources of light illuminating the object, the geometry, relative position and pose of the objects and light sources in the surround, and the position of the observer, vary considerably from scene to scene.
+The challenge faced by the visual system is to recover a stable perceptual representation of the object's surface reflectance invariant of the extrinsic factors.
 The ability of the visual system to extract such a stable representation, its perceived color, is called color constancy.
@@
 
-In this work, we identify the computations that lead to stable lightness perception.
+In this work, we study lightness estimation of objects in naturalistic scenes using supervised learning methods.
 Lightness is the attribute that determines the brightness of a color.
@@
 For achromatic objects, lightness is the property that changes from black to gray to white.
-We study the effects of variations in the reflected light on the perceived lightness.
+Here, we study the effects of variations in the reflected light on the perceived lightness.
+These variations can result either due to geometrical factors (like shape, size, relative position of objects, etc.) or due to spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
+We focus on spectral factors, specifically the effects of variations in the surface reflectance spectra and the illumination spectra (Fig.\ref{fig:introExampleFigure}).
+Our aim is to identify the computations that lead to accurate lightness estimation.
 
 % Figure 1: Introduction
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
     \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light reflected off an object and incident on our eyes, depends both on the surface reflectance of the object $\left( R(\lambda,x) \right)$ and the illumination spectrum of the light source $\left(E(\lambda,x)\right)$.
-Additionally, the reflected light also depends on context the object lies in.
-Thus a variation in the reflected light can result from either a change in the object surface reflectance, or a change in the illumination spectrum of the light source, or change in the context, or all of these.
-Color constancy refers to the ability of the human visual system to perceive the color of the object stably under variations coming from these factors.
-(b) {\bf Lightness Constancy Under Spectral Variations:} In this work we study lightness constancy under variations in the spectra of the light sources and the objects.
-In Fig.\ref{fig:introExampleFigure}, we show 5 images generated at three different lightness levels of the target object (spherical object in the center).
-Along the rows we have fixed the lightness level of the target object, while we vary the spectra of the target object, the background objects and the light sources.
-(For illustration, in fig.\ref{fig:introExampleFigure}, We have fixed the shape of the target object reflectance spectra along the column.) Our aim is to identify computations that can recover the target object lightness from such stimuli.}
+    \caption{(a) {\bf Color Constancy:} The light coming from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,x)$, and the illumination spectrum of the light source, $E(\lambda,x)$.
+Additionally, it depends on the context in which the object lies.
+The human visual system has the ability to discard any variations in the captured light due to extrinsic factors, and stably perceive the color of the object.
+Such invariant color perception is called color constancy.
+(b) {\bf Lightness Constancy Under Spectral Variations:} In this work we study lightness estimation.
+Fig.\ref{fig:introExampleFigure} shows images of an object (spherical object in the center) at three lightness levels.
+We show 5 images at each lightness level which vary in the spectra of the target object (sphere), the background objects and the light sources.
+(For illustration, in fig.\ref{fig:introExampleFigure}, we have fixed the shape of the target object reflectance spectra along the column.) Our aim is to identify computations that can accurately estimate the object lightness under such variations.}
 \end{figure}
-
-The variations in the reflected light can result from either geometrical factors (like shape, size, relative position of objects, etc.) or spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
-Here, we focus on the spectral factors.
-Specifically, we study the effects of variations in the surface reflectance spectra and the illumination spectra on lightness perception  (Fig.\ref{fig:introExampleFigure}).
-We are interested in identifying the computations that can lead to stable lightness perception.
 
@@
 \caption{{\bf Approach:} We have employed a supervised learning approach to study color constancy.
-We first generate a large dataset of hyperspectral images labeled with the lightness level of the target object.
+We first generate a large dataset of hyper-spectral images labeled with the lightness level of the target object.
 We generate images at multiple lightness levels, with images at the same lightness level having variable object reflectance spectra and illumination spectra.
-These hyperspectral images are used to simulate the response of the visual system.
+These hyper-spectral images are used to simulate the response of the visual system.
 We use isetbio toolbox to model the optics and physiology of early vision and produce the response of the cones in the retina.
@@
 We employ a supervised learning approach to understand this phenomenon.
-We generate a database of hyperspectral images of naturalistic scenes labeled by the lightness of a specific target object in the scene.
-The images are labeled with perceived lightness of a uniform surface having the target object reflectance placed under the standard daylight spectrum $D_{65}$.
-We generate hundreds of hyperspectral images at several fixed values of the target object standard lightness.
-At a particular lightness level, we allow variations in the surface reflectance spectra of the objects (both the target and the surround objects) and the illumination spectra of the light sources (Fig.
-\ref{fig:introExampleFigure}.
-
-In this work, we study three cases resulting from the combination of such spectral variations (Fig.\ref{fig:studiedCases}).
+We generate a database of hyper-spectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene.
+These images are labeled with the perceived lightness of the target object under standard daylight spectrum $D_{65}$ (see Methods).
+We generate hundreds of images with variations in the surface reflectance spectra of the objects and the illumination spectra of the light sources (Fig.~\ref{fig:introExampleFigure}).
+We study three cases resulting from the combination of such spectral variations (Fig.~\ref{fig:studiedCases}).
 These cases are: 1.
-Variations in target object spectra (Fig.\ref{fig:targetVarying}) with fixed illumination and background surface reflectance spectra, 2.
-Variations in target object spectra and the light source spectra, with fixed background surface reflectance spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
-Variations in all spectra (target object, background object and light source) (Fig.\ref{fig:allSpectraVarying}).
-The effects of other types of spectral variations can be explained in terms of one of these cases (see supplementary information).
+Variation in target object spectrum (Fig.\ref{fig:targetVarying}) with fixed illumination and background, 2.
+Variations in both the target object spectrum and the light source spectra, with fixed background spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
+Variations in all three spectra (target, background and light source) (Fig.\ref{fig:allSpectraVarying}).
+The effects of other types of spectral variations can be explained in terms of one of these cases (see Discussion/Supplementary information).
+Next, we simulate the response of the cones in the retina to these hyper-spectral images using an accurate model of the early visual system.
+Such labeled cone-responses datasets are then analyzed using supervised computational learning methods.
+We use three methods: linear regression, generalized SVD regression and accuracy maximization analysis (AMA) in our analysis.
+These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness.
+These methods identify the receptive fields (RFs) that optimal for lightness estimation.
+We evaluate the performance of the learnt RFs on a test set of images.
 
@@
     \end{subfigure}    
-    \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of images studied in our work.
-The numbers on the left are the standard lightness level of the target object.
-We show 5 images for each case at 3 lightness levels.
-The analysis was performed with images at 10 lightness levels.
+    \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of hyper-spectral images similar to ones studied in our work.
+The numbers on the left indicate the standard lightness level of the target object.
+5 images are shown at each lightness level.
 We studied three types of spectral variations.
-(a) Case 1: Target reflectance spectra variable, Background reflectance spectra fixed, illuminant spectra fixed (b) Case 2: Target reflectance spectra variable, Background reflectance spectra fixed, illuminant spectra variable (c) Case 3: Target reflectance spectra variable, Background reflectance spectra variable, illuminant spectra variable.}
+(a) Case 1: Target reflectance spectrum variable, illumination spectra fixed, background spectra fixed, (b) Case 2: Target spectrum variable, Illumination spectra variable, Background spectra fixed, (c) Case 3: Target spectrum variable, Illumination spectra variable, Background spectra variable.}
 \label{fig:studiedCases}
 \end{figure}
-
-After generating databases of labeled hyperspectral images for each one of these cases, we simulate the response of the cones in the retina cone using an accurate model of the eye.
-These cone-responses datasets, that are labeled with the standard lightness of the target object, are then analyzed using supervised computational learning methods.
-
-We have employed three supervised computational learning methods for estimating the target object lightness: linear regression, a generalized SVD regression and accuracy maximization analysis (AMA).
-The linear regression has been performed on the cones corresponding to the center pixel of the target object.
-The other two methods take the response of all the cones in the model retina.
-While, SVD regression a linear transformation to estimate the lightness, AMA uses a non-linear transform of the data.
-These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness.
-Finally, we evaluate the performance of the computational methods on a test set of images.
 
@@
 
-We show that for cases that allow variation either only in the target surface reflectance or the background surface reflectance or the spectral power distribution of the source of light, the standard lightness ($Y_{65}$) can be recovered by simple manipulations of the reflected light captured by the visual system.
-For case 1, (variations only in target obejct reflectance spectra), $Y_{65}$ can be recovered directly from the light reflected off the target object.
-For case 2, where both the target object reflectance and light source spectra vary, $Y_{65}$ can be recovered by from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered from a simple manipulations of the light captured by the visual system.
+We show that for cases that have spectral variation only in target reflectance or background reflectance or the illuminant, the standard lightness ($Y_{65}$) can be estimated by simple transformations of the cone responses.
+For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
+For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
 Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
@@
 Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, lightness estimation invovles a weighted sum of the L, M and S cone responsese where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
-Comparing the performace of the receptive fields of one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
+Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
+Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
 We discuss the implications of such receptive fields on lightness constancy.
@@
 The details of the software are provided in the supplementary information section.
-To generate a virtual scene, we first select a 3D scene, a target object and a light source from the set of predefined scenes and objects of the VWCC software.
+We first select a 3D scene, a target object and a light source from the set of predefined scenes and objects of the VWCC software.
 The target object and the light source are inserted at predefined positions in the 3D scene.
-Fig.\ref{fig:3DScene} shows a 2D sRGB rendition of the 3D scene with the inserted target object (green sphere in the middle) used in our analysis.
-(The light source in not visible.) Next, we assign a surface reflectance spectrum and an illumination spectrum to each object and light source in the scene.
+Fig.\ref{fig:3DScene} shows a 2D sRGB rendition of the 3D scene used in our analysis.
+The green sphere in the middle is the target object.
+The light source is not in the camera field of view.
+Next, we assign a surface reflectance spectrum and an illumination spectrum to each object and light source in the scene.
 For the target object the surface reflectance is assigned such that the perceived lightness of the target object under D65 daylight spectrum has a fixed value.
-Once these spectral properties have been assigned, we render a 320x240 pixel$^2$ 2d hyperspectral images of the scene at 31 frequencies (equal linear spacing between 400nm - 700nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}.
-We generate hundreds of such scenes and the corresponding hyperspectral images at 10 linearly spaced lightness levels between 0.2 and 0.6.
-For the images at a fixed lightness level, the reflectance and illumination spectra are assigned according to the spectral variations allowed under each case.
-Next, we crop a 51x51 pixel$^2$ part of the hyperspectral image containing the target object for further analysis (\ref{fig:croppedImage}).
+Now we render a $320\times 240$ pixel$^2$ 2d hyper-spectral images of the scene at 31 frequencies (equal linear spacing between 400 nm - 700 nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}.
+For each of the three case, We generate hundreds of such scenes and corresponding hyper-spectral images at 10 linearly spaced lightness levels between 0.2 and 0.6 (see below).
+We crop a 51x51 pixel$^2$ part of the hyper-spectral image containing the target object for further analysis (\ref{fig:croppedImage}).
 Fig.
@@
     \end{subfigure}
-
     \label{fig:sceneWithCroppedImage}
-    \caption{{\bf Generating labeled dataset for computational analysis:}  We employ a supervised learning approach in our study.
-We generate a database of visual system response to images labeled with the lightness of the target object.
-This is done as follows: (a) We define a 3D virtual scene where we can assign the geometrical and spectral properties of the objects.
-In this 3D scene, we place a target object (here the spherical object) in the camera field of view and assign a fixed reflectance spectrum to the target object.
-Then we render a hyperspectral image of the scene.
+    \caption{{\bf Generating labeled dataset for computational analysis:}  For the supervised approach employed in this work, the labeled database is generated as follows: (a) A 3D virtual scene, a target object and a light source is selected from the VWCC library.
+The target object is placed in the camera field of view and assigned a reflectance spectrum with a specific lightness.
+After assigning spectra to other objects and lights sources in the scene, a hyper-spectral image of the scene is rendered using Mitsuba graphics rendering software.
 (b) A part of the image, containing the target object, is cropped from the image.
-(c) Using an accurate model of the front end of the visual system, we generate the response of the retinal cones to the cropped image.
+(c) The response of the retinal cones to the cropped image is simulated using a model of the visual system.
 Fig.\ref{fig:croppedImageWithMosaic} shows the optical image incident on the cone mosaic and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
 See text for the details of the model.
-(d) For each cone type, we interpolate the response to get the cone-response of all the three types at each location.
-These responses are contrast normalized (see text) to the get the input analysis.}
+(d) The cone response are interpolated to get the response of all the three types at each location (demosaicing).
+Finally, the demosaic response is contrast normalized (see text).}
 \end{figure}
@@
 Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics.
-We use the hyperspectral cropped image (fig.\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
+We use the hyper-spectral cropped image (fig.\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
 The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
@@
 The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
-It then renders a hyperspectral 2D image of each modeled visual scene.
+It then renders a hyper-spectral 2D image of each modeled visual scene.
 Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
-In addition, our software simulates the responses of retinal cones to the rendered hyperspectral images using a realistic model of the early human visual system.
+In addition, our software simulates the responses of retinal cones to the rendered hyper-spectral images using a realistic model of the early human visual system.
 Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
@@
 The renderer produces 2D hyper-spectral images of the scene at specified wavelengths.
-Finally, these hyperspectral images are used to simulate retinal cone responses using the \href{https://github.com/isetbio}{ISETBIO} software.
+Finally, these hyper-spectral images are used to simulate retinal cone responses using the \href{https://github.com/isetbio}{ISETBIO} software.
 
@@
 The spectral manipulations for the various cases studied in this work are described below.
-hyperspectral 2D images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
-Next, a $51 \times 51$ pixel$^2$ patch of the hyperspectral image was cropped around the target object and cone responses were calculated to these cropped images as described below.
+hyper-spectral 2D images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
+Next, a $51 \times 51$ pixel$^2$ patch of the hyper-spectral image was cropped around the target object and cone responses were calculated to these cropped images as described below.
 

### 2017-10-16 Draft1/draft1.tex
added some text in the methods section

@@
 We generate a database of hyper-spectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene.
-These images are labeled with the perceived lightness of the target object under standard daylight spectrum $D_{65}$ (see Methods).
+These images are labeled with the perceived lightness of the target object under standard daylight spectrum $D_{65}$ (see SI).
 We generate hundreds of images with variations in the surface reflectance spectra of the objects and the illumination spectra of the light sources (Fig.~\ref{fig:introExampleFigure}).
@@
 \subsection{Image database} \label{method:VirtualWorld}
-In this section we briefly describe our image generation software that we call Virtual world color constancy (VWCC).
+We called our image generation software Virtual world color constancy (VWCC).
 The details of the software are provided in the supplementary information section.
-We first select a 3D scene, a target object and a light source from the set of predefined scenes and objects of the VWCC software.
-The target object and the light source are inserted at predefined positions in the 3D scene.
+To generate an image, we first select a 3D scene, a target object and a light source from the set of predefined scenes and objects in VWCC.
+The target object and the light source are inserted in the 3D scene.
 Fig.\ref{fig:3DScene} shows a 2D sRGB rendition of the 3D scene used in our analysis.
@@
 Now we render a $320\times 240$ pixel$^2$ 2d hyper-spectral images of the scene at 31 frequencies (equal linear spacing between 400 nm - 700 nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}.
-For each of the three case, We generate hundreds of such scenes and corresponding hyper-spectral images at 10 linearly spaced lightness levels between 0.2 and 0.6 (see below).
+For each of the three case, we generate hundreds of such scenes and corresponding hyper-spectral images at 10 linearly spaced lightness levels between 0.2 and 0.6 (see below).
 We crop a 51x51 pixel$^2$ part of the hyper-spectral image containing the target object for further analysis (\ref{fig:croppedImage}).
@@
 \subsection{Model of Visual System} \label{method:Isetbio}
-We simulate the visual system response using \href{http://isetbio.org}{Isetbio} software toolbox.
+We simulate visual system response using \href{http://isetbio.org}{Isetbio} software toolbox.
 Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics.
-We use the hyper-spectral cropped image (fig.\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
+We use the hyper-spectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
 The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
 The retinal cone mosaic is modeled as a square grid with 51x51 cones in the l:m:s ratio 0.6:0.3:0.1.
-The response of the cones are measured in terms of the number of isomerizations in the cone segment ({\it over what time ??}).
-Since, S cones response are much lower than of L and M cones, to model the amplification of the S cone response downstream, we rescale the cone response functions by the total area under the response curves.
-This leads to comparable number of isomerizations in the L, M and S cones.
-Further, to get the response of each cone class at each poistion on the retinal mosaic, we interpolate the response of the cones for each cone class.
+The response of the cones are measured as the number of isomerizations in the cone segment ({\it over what time ??}).
+The cone response functions are normalized by the total area under the response curves to model the amplification of the S cone response downstream and thus have comparable number if isomerizations in L, M and S cones.
+Further, to get the response of each cone class at each position on the retinal mosaic, we interpolate the response of each cone class.
 Thus we get a $51 \times 51$ cone response image for each cone class.
 
-The three $51 \times 51$ cone response matrix corresponding to each one of the L, M and S cones are then reshaped into a $7803 \times 1$ vector.
-To model the contrast adaptation in the visual system, we subtract the mean of the vector from each entry and divide by the mean.
+The three $51 \times 51$ cone response matrix corresponding to L, M and S cones are then reshaped into a $7803 \times 1$ vector.
+To model the contrast adaptation in the visual system, we perform a contrast normalization of the vector by subtracting and dividing by the mean.
 We further  rescale the vector to have norm 1.
-The cone-response vectors corresponding to the N images for each case are concatenated into a $7803 \times N$ contrast normalized matrix $C$.
-The corresponding labels are represented by a $1 \times N$ row vector $Y$.
+The cone-response vectors corresponding to the N images for each case are concatenated into a column-wise contrast normalized matrix $C_{7803\times N}$.
+The corresponding labels are represented by the row vector $Y_{1\times N}$.
 
 \subsection{Supervised Learning methods} \label{method:SupervisedLearning}
-\subsubsection*{Linear Regression} To estimate the target object lightness using linear regression, we solve the equation $A_{(1,3)}*C_{(3,N)} = Y_{(1,N)}$.
-$C_{(3,N)}$ corresponds to the matrix of LMS cone responses corresponding to the center pixel of the image.
-Each column represents the response to one image.
-The rows corresponds to the contrast normalized L, M and S cones response of the center pixel for the N images in the dataset.
-The (unknown) coefficient matrix $A$ can be obtained as $A = Y*C^{-1}$.
-
-The L, M and S response to the center pixel on the target object is calculated by taking the average of a 3x3 patch of cones near the center of the target.
+\subsubsection*{Linear Regression} For linear regression, we solve the equation $A_{(1,3)}*C_{(3,N)} = Y_{(1,N)}$ for the regression parameters $A_{(1,3)}$.
+Here, $C_{(3,N)}$ has the contrast normalized matrix of LMS cone responses of the center pixel.
+Each column corresponds to the N images in the dataset.
+The rows correspond to the contrast normalized L, M and S cones response of the center pixel for each image.
+The L, M and S response to the center pixel on the target object is calculated by taking the average of a 3x3 patch of cones near the center of the target.The (unknown) regression parameters $A$ are obtained using Matlab linear regression function.
 
 \subsubsection*{SVD regression}
-This method is a generalization of principal component analysis for labeled data.
-Briefly, given a dataset $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds directions along which the projections of the data maximize the separation between the images with different labels, while clustering the images with similar labels together.
-Mathematically, the method searches for a direction $\hat{u}$ such that the cost function:
-
+SVD regression is a generalization of principal component analysis for labeled data \cite{ranganNotes}.
+Briefly, given an image dataset $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds directions that maximize the separation of the images with different labels, while clustering the images with similar labels together.
+Mathematically, the method searches for a direction $\hat{u}$ such that minimize the cost function:
 \begin{align}
@@
 \end{align} 
-where $C(:,j)$ represents the $j$'th column (image) of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the matrix:
-
+where $C(:,j)$ represents the $j$'th column/image of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the matrix:
 \begin{align}
@@
 AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
-It finds the receptive fields that are optimal for performing a well defined behavioral task.
-Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task, which is implicitly defined in terms of the labels.
+Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task.
+The task is implicitly defined in terms of the labels.
 The optimal filters are the ones whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
@@
 
-Let us assume that there is a latent variable ($Y$) that takes the values $\{Y_k: k\in[1,N_{\nu}] \}$.
-The $l$'th stimuli corresponding to the $k$'th category of the latent variable is $s_{kl}$.
+Let us assume that there is a latent variable ($Y$) that takes one of the $N_{\nu}$ possible values $\{Y_k: k\in[1,N_{\nu}] \}$.
+Let's represent the $l$'th stimuli corresponding to the $k$'th category of the latent variable as $s_{kl}$.
 Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
@@
 
-Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}, l\in[1,N_k]\}$.
+Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$.
 $N_{\nu}$ is the total number of labels and $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
@@
 \label{eq:condProb}
-\end{align}hat{Y}
+\end{align}
 using Eq.\ref{eq:condProb} in Eq.\ref{eq:posterior} we get:
@@
 We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be zero mean contrast normalized, i.e., $\langle{s_{kl}}\rangle = 0$ \& ${|s_{kl}|=1}$.
-
-\subsection{Types of spectral variations studied}
-We have studied the effects of spectral variations on perceived lightness.
-These can be categorized into three types: variations in the shape of target object reflectance spectra, variations in the shape of background object reflectance spectra, and the variations in the shape of the spectral power distribution of light sources.
-Here, we present the results for three cases (Fig.\ref{fig:studiedCases}): 1.
-effects of variations in target object spectra (Fig.\ref{fig:targetVarying}), 2.
-effects of variations in target object spectra and the light source spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
-effects of variations in all three spectra (Fig.\ref{fig:allSpectraVarying}).
-The cases with other types of variations are qualitatively similar to one of the three cases discussed here (see Discussion).
 

### 2017-10-16 Draft1/draft1.tex
Added text in results

@@
 SVD regression is a generalization of principal component analysis for labeled data \cite{ranganNotes}.
-Briefly, given an image dataset $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds directions that maximize the separation of the images with different labels, while clustering the images with similar labels together.
+Briefly, given an image dataset matrix $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds unit vectors such that the projection of the data along this vector maximizes the separation of the images with different labels, while clustering the images with similar labels together.
 Mathematically, the method searches for a direction $\hat{u}$ such that minimize the cost function:
@@
 \subsubsection*{Accuracy maximization analysis}
-AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
+ \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
 Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task.
@@
 The optimal filters are the ones whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
-The filters are learned via gradient descent with the aid of an optimal Bayesian decoder that is matched to the filters throughout the learning process.
 
-Let us assume that there is a latent variable ($Y$) that takes one of the $N_{\nu}$ possible values $\{Y_k: k\in[1,N_{\nu}] \}$.
-Let's represent the $l$'th stimuli corresponding to the $k$'th category of the latent variable as $s_{kl}$.
+Let us assume that the labels ($Y$) take one of the $N_{\nu}$ possible values $\{Y_k: k\in[1,N_{\nu}] \}$ and the $l$'th stimuli corresponding to the $k$'th category of the labels is represented as $s_{kl}$.
 Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
@@
 
-AMA employs the Bayes optimal decoder to estimate the optimal estimate.
+AMA employs the Bayes optimal decoder ($g$) to estimate the optimal estimate.
 The Bayesian decoder computes the posterior probability of the latent variable $p(X|{\textbf {\textit R}})$ and reads out the optimal estimate $\hat{Y}^{\rm opt}$ from the posterior as the value that minimizes the cost.
@@
 \end{align}
-As conditional probability of the filter response is:
+As the conditional probability of the filter response is:
 \begin{align}
@@
 \end{align}
-using Eq.\ref{eq:condProb} in Eq.\ref{eq:posterior} we get:
+using Eq.~\ref{eq:condProb} in Eq.~\ref{eq:posterior} we get:
 \begin{align}
@@
 \end{align}
-and the total cost associated with the training set is $\bar{\mathcal{C}} = \frac{1}{N} \sum\limits_{k,l}\bar{\mathcal{C}}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle \mathcal{C}_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$.
+and the mean cost associated with the training set is $\bar{\mathcal{C}} = \frac{1}{N} \sum\limits_{k,l}\bar{\mathcal{C}}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle \mathcal{C}_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$.
 The optimal AMA filters are obtained by minimizing $\bar{\mathcal{C}}$ over the filter set ${\textbf {\textit f} }$ (Eq.\ref{eq:fopt}).
@@
 \section{Results}
-\subsection{Case 1}
-Fig.~\ref{fig:case9AllResults} shows the receptive fields and the the AMA lightness estimates for the three cases discussed above.
-We show the target object lightness estimates for there different methods: linear regression on center pixel, SVD regression and AMA.
-As is expected, when only the target object reflectance varies, it is easy to estimate the target object lightness.
-For case 2, where the light source spectra are allowed to vary, although the light captured by the cones vary from image to image, the contrast between the target and the background remains fixed and can be used to estimate the target object lightness.
-Thus, the SVD-LDA and AMA still provide good estimates of the target object lightness.
-In case 3, the most challenging case where all the spectra are allowed to change, AMA still does a reasonable job of estimating the target object lightness.
-AMA mean estimates lie close to the diagonal x=y line.
+\subsection{Optimal receptive fields show a center surround structure}
+Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults}) shows the RFs, the linear response of these RFs training dataset and the lightness estimates of the test data for the three cases described above.
+We show the first two RFs for SVD and AMA methods (Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(a-b)).
+The RFs are ranked in ascending order of the value of the cost function.
+Thus the first RF corresponds to the direction along which the projection of the data gives the minimum cost.
+The L, M and S components give the weights for the linear sum of the cone responses for the three cone types.
+The salient features are the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.
+
+For case 1, since the illuminant and the background are fixed, all the information is in the central target object reflectance.
+Thus, the RFs weights are mostly concentrated around the center.
+For case 2, while the target and the illuminant spectra varies, the background object spectra is fixed.
+Hence, the lightness can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background.
+Thus, while the RFs show a trend of weights concentrated at the center similar to case 1, there is large negative contribution from the surround.
+The spatial features of the RFs are due the stereotypical geometry of the images (see SI).
+For case 3, has a similar center surround structure with more prominent features of the background as we also vary the spectra of the background objects.
+Again, the spatial features are a result of the stereotypical geometry of the images.
 
@@
 \centering
-\includegraphics[width=0.3\textwidth]{../Figures/Figure5/Figure5.pdf}
-\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs in our analysis.}
-\label{fig:RMSEvsNFilters}
-\end{figure}
-
-% Figure 6
-\begin{figure}
-\centering
 \begin{subfigure}[b]{0.27 \textwidth}
@@
     \end{subfigure}
+    \caption{{\bf Receptive fields and lightness estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
     \label{fig:case10AllResults}
-    \caption{{\bf Receptive fields and lightness estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
 \end{figure}
 
-% Figure 7
+% Figure 6
 \begin{figure}
@@
     \end{subfigure}
+    \caption{{\bf Receptive fields and lightness estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
     \label{fig:case12AllResults}
-    \caption{{\bf Receptive fields and lightness estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
 \end{figure}
 
+\subsection{Lightness can be well estimated using a bayesian decoder with gaussian priors.}
+We estimate the lightness of the target object in the images using the receptive field response of the corresponding contrast normalized cone responses.
+Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(c) shows the response of the first two RFs to the stimuli set for the three cases.
+For the training images at each lightness level, we approximate the receptive response of the contrast normalized cone responses by a multivariate gaussian.
+The target object lightness of an image in the test set is estimated using Bayesian decoder.
+We measure the estimation performance in terms of the relative root mean square ($E_{\rm rel}$) defined as:
+\begin{align}
+E_{\rm rel} = \sqrt{\left\langle\left(\frac{\hat{Y}-Y}{Y}\right)^2\right\rangle},
+\end{align}
+where $\hat{Y}$ corresponds to the estimated lightness and $Y$ to the assigned lightness. We use the first 8 RFs for lightness estimation ( see Fig.~\ref{fig:RMSEvsNFilters}).
+
+% Figure 7
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{../Figures/Figure5/Figure5.pdf}
+\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the lightness.}
+\label{fig:RMSEvsNFilters}
+\end{figure}
+
+Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(d) shows the lightness estimates and the RMSE for the three methods (Linear regression on center pixel, AMA and SVD).
+Additionally we show the estimate of a naive model that reports the mean value of the lightness labels used in the dataset.
+The diagonal x=y line is shown for reference.
+The shaded regions show $E_{\rm rel}$ for each method.
+
+(Fig.~\ref{fig:summaryBarGraph}) compares the $E_{\rm rel}$ for the different methods for the three cases.
+Both AMA and SVD methods, which use the information from the entire image estimate the lightness better compared to linear regression which only uses the information from the center pixel.
+This shows the importance of context information for lightness estimation.
+
+\subsection{The RFs of complex case perform well on simpler cases}
 % Figure 8stimulusIntensities(1)-1
@@
 \centering
-\begin{subfigure}[b]{0.3 \textwidth}
+\begin{subfigure}{0.3 \textwidth}
 	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
@@
       %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.3 \textwidth}   
+    \begin{subfigure}{0.3 \textwidth}   
 	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
@@
     %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}[b]{0.3 \textwidth}
+        \begin{subfigure}{0.3 \textwidth}
 	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
@@
 \end{figure}
+Fig.~\ref{fig:SVDBAR} and Fig~\ref{fig:AMABAR} show the performance of the receptive fields learnt using the stimuli of one case on the stimuli of other cases.
+The RFs of case 3, (the most complex case) perform well on stimuli of case 1 and case 2.
+Similarly, the RFs of case 2 performs well on the stimuli of case 1.
+Thus, the receptive fields leant on the complex case generalize for lightness estimation of stimuli for simpler cases.
 
-We compare the performance of these models using the relative root mean square estimator ($E_{\rm rel}$) defined as:
-
-\begin{align}
-E_{\rm rel} = \sqrt{\left\langle\left(\frac{Y_{\rm Est}-Y_{\rm Act}}{Y_{\rm Act}}\right)^2\right\rangle}
-\end{align}
-
-Fig. ZZZ shows $E_{\rm rel}$ for the various estimators used here.
-
-\subsection{Explain the filters}
-
-\section{Methods}
+\section{Supplementary Information}
 \subsection{Generating Virtual Images}

### 2017-10-18 Draft1/draft1.tex
more edits

@@
 Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the perceived lightness of an object.
-We have developed a software that generates naturalistic hyper-spectral images of 3D scenes with precise control over the geometrical and spectral properties of the constituents that make a scene.
+We have developed a software that generates naturalistic multispectral images of 3D scenes with precise control over the geometrical and spectral properties of the constituents that make a scene.
 We label these images with the lightness of a specific object in the scene.
-Next, we simulate the response of the retinal cones to these hyper-spectral images using an accurate model of the early visual system.
+Next, we simulate the response of the retinal cones to these multispectral images using an accurate model of the early visual system.
 Using supervised learning methods on these labeled cone response we identify the computations that lead to accurate lightness estimation.
@@
 \caption{{\bf Approach:} We have employed a supervised learning approach to study color constancy.
-We first generate a large dataset of hyper-spectral images labeled with the lightness level of the target object.
+We first generate a large dataset of multispectral images labeled with the lightness level of the target object.
 We generate images at multiple lightness levels, with images at the same lightness level having variable object reflectance spectra and illumination spectra.
-These hyper-spectral images are used to simulate the response of the visual system.
+These multispectral images are used to simulate the response of the visual system.
 We use isetbio toolbox to model the optics and physiology of early vision and produce the response of the cones in the retina.
@@
 We employ a supervised learning approach to understand this phenomenon.
-We generate a database of hyper-spectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene.
+We generate a database of multispectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene.
 These images are labeled with the perceived lightness of the target object under standard daylight spectrum $D_{65}$ (see SI).
@@
 The effects of other types of spectral variations can be explained in terms of one of these cases (see Discussion/Supplementary information).
-Next, we simulate the response of the cones in the retina to these hyper-spectral images using an accurate model of the early visual system.
+Next, we simulate the response of the cones in the retina to these multispectral images using an accurate model of the early visual system.
 Such labeled cone-responses datasets are then analyzed using supervised computational learning methods.
@@
     \end{subfigure}    
-    \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of hyper-spectral images similar to ones studied in our work.
+    \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of multispectral images similar to ones studied in our work.
 The numbers on the left indicate the standard lightness level of the target object.
@@
 For the target object the surface reflectance is assigned such that the perceived lightness of the target object under D65 daylight spectrum has a fixed value.
-Now we render a $320\times 240$ pixel$^2$ 2d hyper-spectral images of the scene at 31 frequencies (equal linear spacing between 400 nm - 700 nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}.
-For each of the three case, we generate hundreds of such scenes and corresponding hyper-spectral images at 10 linearly spaced lightness levels between 0.2 and 0.6 (see below).
-We crop a 51x51 pixel$^2$ part of the hyper-spectral image containing the target object for further analysis (\ref{fig:croppedImage}).
+Now we render a $320\times 240$ pixel$^2$ 2d multispectral images of the scene at 31 frequencies (equal linear spacing between 400 nm - 700 nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}.
+For each of the three case, we generate hundreds of such scenes and corresponding multispectral images at 10 linearly spaced lightness levels between 0.2 and 0.6 (see below).
+We crop a 51x51 pixel$^2$ part of the multispectral image containing the target object for further analysis (\ref{fig:croppedImage}).
 Fig.
@@
 The target object is placed in the camera field of view and assigned a reflectance spectrum with a specific lightness.
-After assigning spectra to other objects and lights sources in the scene, a hyper-spectral image of the scene is rendered using Mitsuba graphics rendering software.
+After assigning spectra to other objects and lights sources in the scene, a multispectral image of the scene is rendered using Mitsuba graphics rendering software.
 (b) A part of the image, containing the target object, is cropped from the image.
@@
 Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics.
-We use the hyper-spectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
+We use the multispectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
 The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
@@
 
-\subsection{The RFs of complex case perform well on simpler cases}
+\subsection{The RFs of complex case generalize on simpler cases}
 % Figure 8stimulusIntensities(1)-1
@@
 
+\section{Discussion}
+
 \section{Supplementary Information}
-\subsection{Generating Virtual Images}
+\subsection{Virtual World Color Constancy}
 The light that reflects off an object and reaches our eyes depends on many factors.
@@
 The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
-It then renders a hyper-spectral 2D image of each modeled visual scene.
+It then renders a multispectral 2D image of each modeled visual scene.
 Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
-In addition, our software simulates the responses of retinal cones to the rendered hyper-spectral images using a realistic model of the early human visual system.
+In addition, our software simulates the responses of retinal cones to the rendered multispectral images using a realistic model of the early human visual system.
 Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
@@
 
-After specifying the geometry and spectra, one of the inserted objects is chosen as the target object in the scene.
-A camera is inserted at a user specified position and then pointed at the target object.
-We ensure that the target object is not completely occluded by another object in the line of sight of the camera.
-Next, a predefined surface reflectance spectrum is assigned to the target object.
-This target surface reflectance sets the label for the virtual scene image.
-The scene is now rendered using the Mitsuba rendering package.
-The renderer produces 2D hyper-spectral images of the scene at specified wavelengths.
-Finally, these hyper-spectral images are used to simulate retinal cone responses using the \href{https://github.com/isetbio}{ISETBIO} software.
+One of the inserted objects is chosen as the target object in the scene.
+A camera is inserted at a user specified position and pointed at the target object.
+We ensure that the target object is not completely occluded by other objects in the line of sight of the camera.
+A predefined surface reflectance spectrum is assigned to the target object.
+This target surface reflectance also sets the label for the virtual scene image.
+The image label is defined as the perceived lightness of a uniform object with the surface reflectance same as that of the the target object when viewed under uniform standard daylight spectrum D65.
+The scene is rendered using the Mitsuba rendering package.
+The renderer produces 2D multispectral images of the scene at specified wavelengths.
+Finally, these multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
 
@@
 
-For the images used in this work, we first selected the ``{\it Library}'' base scene from the VWCC base scene set.
-We inserted the spherical ``{\it Big Ball}'' object in the base scene and called it the target object.
-We also inserted a light source with the same spherical ``Big Ball'' shape.
-Also, a camera is inserted the scene and pointed at the target object.
-The position, and size of the inserted object, light source and the camera was held fixed for all the images analyzed in this work, i.e., no geometrical manipulations were performed between the images.
+For the images used in this work, we have used the ``{\it Library}'' base scene from the VWCC  as the and the ``{\it Big Ball}'' object as the target object.
+We also inserted a spherical light source with the same ``{\it Big Ball}'' shape.
+The position, and size of the inserted object, light source and the camera was held fixed for all the images analyzed in this work, i.e., the images were identical in their geometry.
 Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene.
-The spectral manipulations for the various cases studied in this work are described below.
-hyper-spectral 2D images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
-Next, a $51 \times 51$ pixel$^2$ patch of the hyper-spectral image was cropped around the target object and cone responses were calculated to these cropped images as described below.
+The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:studiedCases}).
+2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
+A $51 \times 51$ pixel$^2$ patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
 
-\subsection{Illumination Spectrum}
+\subsection{Generating Spectrum for VWCC}
+\subsubsection{Illumination Spectrum}
 The illumination spectrum is generated through a random statistical sampling of a natural illumination spectrum dataset.
-First, we decompose the spectra in the database as a linear sum using principle component analysis (PCA) basis vectors.
-This decomposition is approximated by taking a sum over the PCA basis vectors corresponding to the largest 6 eigenvalues.
-Random spectra are sampled from this low 6 dimensional PCA space assuming the spectral distribution to be a multivariate gaussian.
+First, we approximate the spectra in the dataset using principle component analysis (PCA).
+We decompose the spectra as a linear sum over the PCA basis vectors corresponding to the largest 6 PCA eigenvalues.
+Next, we sample random spectra from this low 6 dimensional PCA space assuming the spectral distribution to be a multivariate gaussian.
 
@@
 These rescaled spectra $(I_i^s(\lambda))$ are then mean centered for PCA by subtracting out the mean
-rescaled spectra, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
-The resulting dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$, 
+rescaled spectra, $\bar{I}^{s}(\lambda)$. The mean is obtained
+by taking the sample mean over all spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
+The resulting mean subtracted dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$, 
 is decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
 where $\hat{{\bf e}}_j^{PCA}$s are PCA basis vectors obtained using 
-singular value decomposition (SVD). $w_{ij}$s are the projections 
-of $I_i^{MC}(\lambda)$ along the PCA basis vectors. We approximate 
+singular value decomposition (SVD). $w_{ij}$'s are the projections 
+of $I_i^{MC}(\lambda)$ along the PCA basis vectors $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. We approximate 
 this decomposition by summing over the basis vectors corresponding to
@@
 \begin{align}
-\tilde{I}(\lambda) = \left( \tilde{I}_{MC}(\lambda) + \bar{I}_{s}(\lambda)\right) 
-\times \max\left(\langle I_{G}\rangle\right) .
+\tilde{I}(\lambda) = \left( \tilde{I}_{MC}(\lambda) + \bar{I}_{s}(\lambda)\right).
 \end{align}
-Finally $\tilde{I}(\lambda)$ is rescaled by a uniform random number between [0, 300].
+Finally $\tilde{I}(\lambda)$ is rescaled by a random number generated uniformly in the range [0, 100].
 
 % Figure 13
-\subsection{Reflectance Spectrum}
+\subsubsection{Reflectance Spectrum}
 \begin{figure}
@@
 
-Similar to the illumination spectrum, the reflectance spectrum of the 
-objects in the visual scene are generated through a random 
-sampling of natural surface reflectance spectra. We have used 
-the Munsell {(\it citation)} and vrhel {(\it citation)} surface reflectance 
-datasets for such sampling. Let us denote the dataset of natural 
+The reflectance spectrum are generated similar to illumination spectrum. 
+We have used the Munsell {(\it citation)} and vrhel {(\it citation)} surface reflectance 
+datasets for sampling the reflectance. Let us denote the dataset of natural 
 reflectance spectra as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
@@
 $\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
-perception of brightness. The target reflectance is given by: $\tilde{R}(\lambda) \cdot\left(\frac{Y}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
+perception of brightness.
+The target reflectance is given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
 
-\subsection{Cone response to hyper-spectral images}
-Cone response to the hyper-spectral images are generated
-using \href{https://github.com/isetbio}{ISETBIO}.
+\subsection{Cone response to multispectral images}
+Cone response to the multispectral images are generated
+using \href{https://github.com/isetbio}{Isetbio}.
 The model incorporates several critical components of biological vision, including physiological optics, information about cornea, lens, pupil, etc.

### 2017-11-01 codeForFigures/codeToMakeFigures/plotRMSEvsEigValSVD.m
changed label names

@@ -63,14 +63,14 @@ l10AMA = plot([1:nEigVecs],results10AMA.error(1:nEigVecs),color10AMA,'linewidth'
 l12AMA = plot([1:nEigVecs],results12AMA.error(1:nEigVecs),color12AMA,'linewidth',2);
 
 xlim([1 nEigVecs])
-xlabel('N Filters Used');
-ylabel('Relative RMSE');
+xlabel('N RFs Used');
+ylabel('E_{rel}');
 box on;
 
 set(gca, 'fontsize', 20);
 legend([l9SVD l9AMA l10SVD l10AMA l12SVD l12AMA],{'Case 1 SVD', 'Case 2 SVD', 'Case 3 SVD', ...
     'Case 1 AMA', 'Case 2 AMA', 'Case 3 AMA'});
-set(gca,'FontName','TimesNewRoman','FontSize',24);
+set(gca,'FontSize',24);
 
 save2pdf('RMSEvsNEigVals/RMSEvsNFilters16.pdf',fig,600);
 

### 2017-11-01 Draft1/draft1.tex
edited the last three figures

@@
 \abstract{The light that reflects off an object surface and is captured by our eyes varies significantly with its context.
-But, the human visual system has the ability stably perceive the object's color invariant of the context.
+But, the human visual system has the ability to stably perceive the object's color invariant of the context variations.
 The mechanism of this behaviorally significant invariance detection ability remains largely unknown.
@@
 Next, we simulate the response of the retinal cones to these multispectral images using an accurate model of the early visual system.
-Using supervised learning methods on these labeled cone response we identify the computations that lead to accurate lightness estimation.
-We show that if only target, or background, or illumination spectra are allowed to vary, the standard lightness can be estimated through simple transformations of the cone responses.
+Using supervised learning methods on these labeled cone response, we identify the computations that lead to accurate lightness estimation.
+We show that if only either target, or background, or illumination spectra are allowed to vary, the standard lightness can be estimated through simple transformations of the cone responses.
 When all the spectra vary simultaneously, while it is not easy to recover the lightness through simple transformations, a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and S cones can recover the lightness within about 15\% RMSE.}
@@
 The color of an object has important behavioral implications.
-This important property of an object is perceived from the light reflected off the object surface.
+This important property of an object is perceived from the light reflected off its surface.
 The reflected light depends not just on the properties intrinsic to the object, such as the object's surface reflectance, its texture, material properties and geometry (shape, size, orientation), but also on extrinsic factors that depend on the object's surround (Fig.
@@
 Here, we study the effects of variations in the reflected light on the perceived lightness.
-These variations can result either due to geometrical factors (like shape, size, relative position of objects, etc.) or due to spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
-We focus on spectral factors, specifically the effects of variations in the surface reflectance spectra and the illumination spectra (Fig.\ref{fig:introExampleFigure}).
+These variations can result both due to geometrical factors (like shape, size, relative position of objects, etc.) or  spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
+In this work, we focus on spectral factors, specifically the effects of variations in the surface reflectance spectra and the illumination spectra (Fig.\ref{fig:introExampleFigure}).
 Our aim is to identify the computations that lead to accurate lightness estimation.
@@
 \begin{figure}
+\centering
 	\begin{subfigure}[b]{0.18 \textwidth}
@@
 \centering
-	\includegraphics[width=\textwidth]{../Figures/Figure12/Figure12.pdf}
-    \caption{Illumination Generation}
-    \label{fig:illuminationGeneration}
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
+        \caption{Granada natural daylight dataset}
+        \label{fig:granadaSpectra}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
+        \caption{Rescaled Granada dataset}
+        \label{fig:rescaledGranada}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
+        \caption{Randomly generated samples}
+        \label{fig:randomIlluminant}
+    \end{subfigure}
+
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_d.pdf}
+        \caption{xy chromaticity diagram}
+        \label{fig:xyDiagram}
+    \end{subfigure}
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_e.pdf}
+        \caption{Normalized PCA eigenvalues}
+        \label{fig:granadaEV}
+    \end{subfigure}
+      	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_f.pdf}
+        \caption{sRGB rendition of samples from Fig.\ref{fig:randomIlluminant}}
+        \label{fig:sRGBIlluminant}
+    \end{subfigure}
+    \caption{{\bf Generating random illumination spectrum:} The illumination spectra are generated by random sampling of Granada daylight spectra assuming a multivariate gaussian distribution.
+The mean and variance of the gaussian are chosen by projecting the dataset along PCA directions and taking the mean and covariance of the projections.
+(a) Granada natural daylight dataset.
+(b) Rescaled Granada dataset.
+Each spectra is rescaled by its mean illumination over frequency.
+(c) Randomly generated samples.
+(d) xy chromaticity diagram of the rescaled dataset (Fig.
+\ref{fig:rescaledGranada}) and the randomly generated samples (Fig.\ref{fig:randomIlluminant}).
+(e) Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
+The eigenvalues have been normalized by the sum over all eigenvalues.
+The dotted line (= 0.9) is for reference.
+We choose the first six eigenvectors in ur analysis.
+(f) The sRGB renditions of the random samples generated in \ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
 \end{figure}
+
 We have used the Granada natural daylight spectrum \href{http://colorimaginglab.ugr.es/pages/Data}{dataset} \cite{peyvandi2016colorimetric} to sample illuminants.
@@
 \centering
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13.pdf}
-    \caption{Reflectance Generation}
-    \label{fig:reflectanceGeneration}
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+        \caption{Natural surface reflectance spectra}
+        \label{fig:naturalSurface}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+        \caption{Randomly generated samples}
+        \label{fig:randomSurface}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+        \caption{sRGB rendition of samples from \ref{fig:randomSurface}}
+        \label{fig:sRGBSurface}
+    \end{subfigure}
+    \caption{{\bf Generating random surface reflectance spectrum:} The surface reflectance spectra are generated by random sampling of natural surface reflectance spectra assuming a multivariate gaussian distribution.
+The mean and variance of the gaussian are chosen by projecting the natural dataset along PCA directions and taking the mean and covariance of the projections.
+(a) Natural surface reflectance spectra.
+(b) Randomly generated samples.
+(c) The sRGB renditions of the random samples generated in \ref{fig:randomSurface}.}\label{fig:surfaceReflectanceGeneration}
 \end{figure}
@@
 \centering
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14.pdf}
-    \caption{Target Reflectance Generation}
-    \label{fig:targetGeneration}
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
+        \caption{Natural surface reflectance spectra}
+        \label{fig:naturalSurfaceTarget}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
+        \caption{Randomly generated target samples}
+        \label{fig:randomSurfaceTarget}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
+        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
+        \label{fig:sRGBSurfaceTarget}
+    \end{subfigure}
+    \caption{{\bf Target object surface reflectance spectrum:} For getting the target object surface reflectance, we first generate the spectra similar to that of other objects and then rescale them appropriately to get the required perceived lightness.
+(a) Natural surface reflectance spectra.
+(b) Randomly generated samples for target reflectance.
+(c) The sRGB renditions of the random samples generated in Fig.~\ref{fig:randomSurfaceTarget}.
+We show 10 samples at 1 lightness levels.}\label{fig:targetSurfaceReflectance}
 \end{figure}

### 2017-12-13 Draft1/draft1.tex
Working with Vijay on the text

@@
 \section{Introduction}
-The color of an object has important behavioral implications.
-This important property of an object is perceived from the light reflected off its surface.
-The reflected light depends not just on the properties intrinsic to the object, such as the object's surface reflectance, its texture, material properties and geometry (shape, size, orientation), but also on extrinsic factors that depend on the object's surround (Fig.
-\ref{fig:introSchematic}).
-These extrinsic factors, such as the surface reflectance, texture and material properties of the objects in the surround, the illumination spectrum of the sources of light illuminating the object, the geometry, relative position and pose of the objects and light sources in the surround, and the position of the observer, vary considerably from scene to scene.
-The challenge faced by the visual system is to recover a stable perceptual representation of the object's surface reflectance invariant of the extrinsic factors.
-The ability of the visual system to extract such a stable representation, its perceived color, is called color constancy.
-We are interested in identifying the computations that lead to such constancy.
+The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties (REF Jacobs, Mollon).
+%@article{RN11757,
+%   author = {Mollon, J. D.},
+%   title = {"Tho' she kneel'd in that place where they grew..." The uses and origins of primate colour vision},
+%   journal = {Journal of Experimental Biology},
+%   volume = {146},
+%   pages = {21-38},
+%   url = {http://jeb.biologists.org/content/146/1/21.full.pdf},
+%   year = {1989},
+%   type = {Journal Article}
+%}
+%@book{RN4724,
+%   author = {Jacobs, G. H.},
+%   title = {Comparative Color Vision},
+%   publisher = {Academic Press},
+%   address = {New York},
+%   year = {1981},
+%   type = {Book}
+%}
+Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of light reflected from the object to the eye.
+The challenge of object color perception is that this reflected light depends not just on the intrinsic properties of the object (e.g., its surface reflectance)
+Indeed, the light reflected from an object depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose,
+and the position of the observer (Fig. \ref{fig:introSchematic}.
+Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
+The ability of a visual system to extract such a stable representation is called color constancy.
+Although human color constancy is by no means perfect, it is often very good (REFS: Foster, Brainard and Radonjic).
+%@article{RN13987,
+%   author = {Foster, D. H.},
+%   title = {Color constancy},
+%   journal = {Vision Research},
+%   volume = {51},
+%   number = {7},
+%   pages = {674-700},
+%   ISSN = {1878-5646 (Electronic)
+%0042-6989 (Linking)},
+%   DOI = {10.1016/j.visres.2010.09.006},
+%   url = {http://www.ncbi.nlm.nih.gov/pubmed/20849875
+%http://ac.els-cdn.com/S0042698910004402/1-s2.0-S0042698910004402-main.pdf?_tid=9f194810-0789-11e4-8bf9-00000aab0f26&acdnat=1404925019_749d71db2edf9d07b6323195f5a519dc},
+%   year = {2011},
+%   type = {Journal Article}
+%}
+%@inbook{RN14002,
+%   author = {Brainard, D. H. and Radonji?, A.},
+%   title = {Color constancy},
+%   booktitle = {The New Visual Neurosciences},
+%   editor = {Chalupa, L. M. and Werner, J. S.},
+%   publisher = {MIT Press},
+%   address = {Cambridge, MA},
+%   pages = {545-556},
+%   year = {2014},
+%   type = {Book Section}
+%}
+In this paper, we consider the computational problem of color constancy, that is how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.
+
+There is a considerable literature on computational color constancy.
+Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover either descriptor correlated with object surface reflectance (e.g.
+REF Land) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., REFS Buchsbaum; Maloney and Wandell).
+%@article{RN12797,
+%   author = {Land, E. H.},
+%   title = {The retinex theory of color vision},
+%   journal = {Scientific American},
+%   volume = {237},
+%   number = {6},
+%   pages = {108-128},
+%   ISSN = {0036-8733 (Print)
+%0036-8733 (Linking)},
+%   url = {http://www.ncbi.nlm.nih.gov/pubmed/929159},
+%   year = {1977},
+%   type = {Journal Article}
+%}
+%@article{RN12790,
+%   author = {Buchsbaum, G.},
+%   title = {A spatial processor model for object colour perception},
+%   journal = {Journal of the Franklin Institute},
+%   volume = {310},
+%   number = {1},
+%   pages = {1-26},
+%   ISSN = {0016-0032},
+%   DOI = {Doi 10.1016/0016-0032(80)90058-7},
+%   url = {<Go to ISI>://WOS:A1980KH89600001},
+%   year = {1980},
+%   type = {Journal Article}
+%}
+%@article{RN12792,
+%   author = {Maloney, L.T. and Wandell, B. A.},
+%   title = {Color constancy: a method for recovering surface spectral reflectances},
+%   journal = {Journal of the Optical Society of America A},
+%   volume = {3},
+%   pages = {29-33},
+%   url = {http://www.opticsinfobase.org/DirectPDFAccess/0C84AF25-A90E-B3D5-AED2308AF33196BF_2286/josaa-3-1-29.pdf?da=1&id=2286&seq=0&mobile=no},
+%   year = {1986},
+%   type = {Journal Article}
+%}
+An important insight clarified by this line of research is that to account for variation in illumination, it was necessary to consider the light reflected from the entire scene.
+That is, although good constancy cannot be achieved in the face of illuminant variation if one considers only the light reflected from a single target object, when one considers the entire image it is possible to use the joint variation in light reflected from many objects to obtain (either implicitly or explicitly) an estimate of the illuminant common across the objects, and in turn to use this estimate to produce a stabilized representation of object color.
+At the same time, this processing introduces an additional dependence.
+Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image (REF Brainard and Wandell).
+Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
+%@article{RN12810,
+%   author = {Brainard, D. H. and Wandell, B. A.},
+%   title = {Analysis of the retinex theory of color vision},
+%   journal = {Journal of the Optical Society of America A},
+%   volume = {3},
+%   number = {10},
+%   pages = {1651-1661},
+%   ISSN = {0740-3232 (Print)
+%0740-3232 (Linking)},
+%   url = {http://www.opticsinfobase.org/DirectPDFAccess/0D4EF4BB-D483-C92D-5D5F36D660104411_2473/josaa-3-10-1651.pdf?da=1&id=2473&seq=0&mobile=no},
+%   year = {1986},
+%   type = {Journal Article}
+%}
+Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes (REFS Funt and Drew; D'Zmura and Iverson; D'Zmura, Iverson, and Singer; Barron and Malik; Brainard and Freeman; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
+%@inproceedings{RN3265,
+%   author = {Funt, B. V. and Drew, M. S.},
+%   title = {Color constancy computation in near-Mondrian scenes using a finite dimensional linear model},
+%   type = {Conference Proceedings}
+%}
+%@article{RN12796,
+%   author = {D'Zmura, M. and Iverson, G.},
+%   title = {Color constancy . III. General linear recovery of spectral descriptions for lights and surfaces},
+%   journal = {Journal Of The Optical Society Of America A},
+%   volume = {11},
+%   number = {9},
+%   pages = {2389-2400},
+%   ISSN = {1084-7529 (Print)
+%1084-7529 (Linking)},
+%   url = {http://www.opticsinfobase.org/DirectPDFAccess/3991999B-F1A4-66F5-1F0CA009799B4F7B_806/josaa-11-9-2389.pdf?da=1&id=806&seq=0&mobile=no},
+%   year = {1994},
+%   type = {Journal Article}
+%}
+%@inproceedings{RN143,
+%   author = {Barron, J. T. and Malik, J.},
+%   title = {Color constancy, intrinsic images, and shape estimation},
+%   booktitle = {ECCV},
+%   type = {Conference Proceedings}
+%}
+%@inbook{RN2224,
+%   author = {D'Zmura, M. and Iverson, G. and Singer, B.},
+%   title = {Probabilistic color constancy},
+%   booktitle = {Geometric Representations of Perceptual Phenomena: Papers in Honor of Tarow Indow's 70th Birthday},
+%   editor = {Luce, R. D. and D'Zmura, M. and Hoffman, D. and Iverson, G. and Romney, A. K.},
+%   publisher = {Lawrence Erlbaum Associates},
+%   address = {Mahwah, NJ},
+%   pages = {187-202},
+%   year = {1995},
+%   type = {Book Section}
+%}
+%@article{RN12793,
+%   author = {Brainard, D. H. and Freeman, W. T.},
+%   title = {Bayesian color constancy},
+%   journal = {Journal of the Optical Society of America A},
+%   volume = {14},
+%   number = {7},
+%   pages = {1393-1411},
+%   ISSN = {1084-7529 (Print)
+%1084-7529 (Linking)},
+%   url = {http://www.opticsinfobase.org/DirectPDFAccess/0D4A73DE-BFFB-35F6-AA30000149C16461_1807/josaa-14-7-1393.pdf?da=1&id=1807&seq=0&mobile=no},
+%   year = {1997},
+%   type = {Journal Article}
+%}
+
+% NEED TO SAY SOMETHING ABOUT THE LITERATURE ON COMP. COLOR CONSTANCY
+% NEED TO MOTIVATE WHAT WE'RE GOING TO DO.  SUPERVISED LEARNING APPROACH USING VIRTUAL WORLD DATA TO GET LABELLED TRAINING DATA.
+
+% IN THIS PAPER, WILL APPLY OUR APPROACH TO A REDUCED VERSION OF THE PROBLEM, AS A FIRST STEP
 
@@
     \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light coming from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,x)$, and the illumination spectrum of the light source, $E(\lambda,x)$.
-Additionally, it depends on the context in which the object lies.
-The human visual system has the ability to discard any variations in the captured light due to extrinsic factors, and stably perceive the color of the object.
+    \caption{(a) {\bf Color Constancy:} The light reflected from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,\vec{x})$, and the illumination spectrum of the light source, $E(\lambda,\vec{x})$.
+Additionally, it depends on geometric factors, such as the object's shape and pose as well as the position of the observer.
+The human visual system is able to account for, at least partially, variations in the reflected light due to such extrinsic factors, and produce a percept of object color that is relatively stable with respect to such variations.
 Such invariant color perception is called color constancy.
-(b) {\bf Lightness Constancy Under Spectral Variations:} In this work we study lightness estimation.
-Fig.\ref{fig:introExampleFigure} shows images of an object (spherical object in the center) at three lightness levels.
-We show 5 images at each lightness level which vary in the spectra of the target object (sphere), the background objects and the light sources.
-(For illustration, in fig.\ref{fig:introExampleFigure}, we have fixed the shape of the target object reflectance spectra along the column.) Our aim is to identify computations that can accurately estimate the object lightness under such variations.}
+(b) {\bf Lightness Constancy Under Spectral Variations:} In this paper we consider the special case of lightness constancy.
+Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance.
+Within each row, the surface reflectance of the spheres has the same luminance, when illuminated by a standard reference illuminant, CIE D65.
+The three rows differ in this value, as can be seen by the fact that the lightness of the spheres generally decreases as we move down the rows.
+Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.
+Within each column, this relative surface reflectance is held fixed.
+In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
  \end{figure}

### 2017-12-14 Draft1/draft1.tex
added references

--- 2017-11-01 Draft1/draft1.tex
@@
 \section{Introduction}
-The color of an object has important behavioral implications.
-This important property of an object is perceived from the light reflected off its surface.
-The reflected light depends not just on the properties intrinsic to the object, such as the object's surface reflectance, its texture, material properties and geometry (shape, size, orientation), but also on extrinsic factors that depend on the object's surround (Fig.
-\ref{fig:introSchematic}).
-These extrinsic factors, such as the surface reflectance, texture and material properties of the objects in the surround, the illumination spectrum of the sources of light illuminating the object, the geometry, relative position and pose of the objects and light sources in the surround, and the position of the observer, vary considerably from scene to scene.
-The challenge faced by the visual system is to recover a stable perceptual representation of the object's surface reflectance invariant of the extrinsic factors.
-The ability of the visual system to extract such a stable representation, its perceived color, is called color constancy.
-We are interested in identifying the computations that lead to such constancy.
-
-In this work, we study lightness estimation of objects in naturalistic scenes using supervised learning methods.
-Lightness is the attribute that determines the brightness of a color.
-A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color.
-For achromatic objects, lightness is the property that changes from black to gray to white.
-Here, we study the effects of variations in the reflected light on the perceived lightness.
-These variations can result both due to geometrical factors (like shape, size, relative position of objects, etc.) or  spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
-In this work, we focus on spectral factors, specifically the effects of variations in the surface reflectance spectra and the illumination spectra (Fig.\ref{fig:introExampleFigure}).
-Our aim is to identify the computations that lead to accurate lightness estimation.
+The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
+Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of light reflected from the object to the eye.
+The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose,
+and the position of the observer (Fig. \ref{fig:introSchematic}).
+Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
+The ability of a visual system to extract such a stable representation is called color constancy.
+Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}.
+In this paper, we consider the computational problem of color constancy, that is how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.
 
@@
     \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light coming from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,x)$, and the illumination spectrum of the light source, $E(\lambda,x)$.
-Additionally, it depends on the context in which the object lies.
-The human visual system has the ability to discard any variations in the captured light due to extrinsic factors, and stably perceive the color of the object.
+    \caption{(a) {\bf Color Constancy:} The light reflected from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,\vec{x})$, and the illumination spectrum of the light source, $E(\lambda,\vec{x})$.
+Additionally, it depends on geometric factors, such as the object's shape and pose as well as the position of the observer.
+The human visual system is able to account for, at least partially, variations in the reflected light due to such extrinsic factors, and produce a percept of object color that is relatively stable with respect to such variations.
 Such invariant color perception is called color constancy.
-(b) {\bf Lightness Constancy Under Spectral Variations:} In this work we study lightness estimation.
-Fig.\ref{fig:introExampleFigure} shows images of an object (spherical object in the center) at three lightness levels.
-We show 5 images at each lightness level which vary in the spectra of the target object (sphere), the background objects and the light sources.
-(For illustration, in fig.\ref{fig:introExampleFigure}, we have fixed the shape of the target object reflectance spectra along the column.) Our aim is to identify computations that can accurately estimate the object lightness under such variations.}
+(b) {\bf Lightness Constancy Under Spectral Variations:} In this paper we consider the special case of lightness constancy.
+Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance.
+Within each row, the surface reflectance of the spheres has the same luminance, when illuminated by a standard reference illuminant, CIE D65.
+The three rows differ in this value, as can be seen by the fact that the lightness of the spheres generally decreases as we move down the rows.
+Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.
+Within each column, this relative surface reflectance is held fixed.
+In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
  \end{figure}
+
+There is a considerable literature on computational color constancy.
+Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
+\cite{LandRetinex}) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
+An important insight of this line of research was that to account for variation in illumination, it was necessary to consider the light reflected from the entire scene.
+That is, although good constancy cannot be achieved in the face of illuminant variation if one considers only the light reflected from a single target object, when one considers the entire image it is possible to use the joint variation in light reflected from many objects to obtain (either implicitly or explicitly) an estimate of the illuminant common across the objects, and in turn to use this estimate to produce a stabilized representation of object color.
+At the same time, this processing introduces an additional dependence.
+Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image \cite{BrainardWandellRetinex}.
+Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
+Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
+
+% NEED TO MOTIVATE WHAT WE'RE GOING TO DO.  SUPERVISED LEARNING APPROACH USING VIRTUAL WORLD DATA TO GET LABELLED TRAINING DATA.
+
+% IN THIS PAPER, WILL APPLY OUR APPROACH TO A REDUCED VERSION OF THE PROBLEM, AS A FIRST STEP
+
+In this work, we study lightness estimation of objects in naturalistic scenes using supervised learning methods.
+Lightness is the attribute that determines the brightness of a color.
+A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color.
+For achromatic objects, lightness is the property that changes from black to gray to white.
+Here, we study the effects of variations in the reflected light on the perceived lightness.
+These variations can result both due to geometrical factors (like shape, size, relative position of objects, etc.) or  spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
+In this work, we focus on spectral factors, specifically the effects of variations in the surface reflectance spectra and the illumination spectra (Fig.\ref{fig:introExampleFigure}).
+Our aim is to identify the computations that lead to accurate lightness estimation.
 

### 2017-12-14 Draft1/draft1.tex
Today’s work

@@
 Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
+None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.
 
-% NEED TO MOTIVATE WHAT WE'RE GOING TO DO.  SUPERVISED LEARNING APPROACH USING VIRTUAL WORLD DATA TO GET LABELLED TRAINING DATA.
+The computational work reviewed above is based on formulating an explicit model of the image formation process and the statistical properties of natural images, and leveraging these formulations to obtain an appropriate "inverse optics" algorithm.
+An alternative approach, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors.
+Along these lines, Barron (REF, that color balancing deep learning paper) recently developed a color balancing algorithm based on training a neural network ...
+(better go back and re-understand that paper so we can describe it here).
+The use of supervised learning to understand human perceptual capabilities has enjoyed success in domains outside of color vision.
+Geisler and colleagues, for example, have developed a technique they refer to as accuracy maximization analysis (AMA, REFS), which learns linear filters whose output carries information that is optimized for particular perceptual tasks.
+This technique has provided computations that efficiently estimate [depth, focus, whatever]  from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
+In this paper, we apply AMA to a special case of the color constancy problem (lightness constancy) and evaluate how well it performs for naturalistic image input.
 
-% IN THIS PAPER, WILL APPLY OUR APPROACH TO A REDUCED VERSION OF THE PROBLEM, AS A FIRST STEP
+A difficulty in using machine learning approaches for color constancy is that these approaches require training sets where images of scenes containing objects with known surface reflectances and/or illuminated with known illuminations.
+Such data sets are not readily available.
+Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth (REFS,  McGill Database, UPENN database, Foster hyperspectal, Chakrabati hyperspectral, Parraga hyperspectral).
+Generating databases with both the images and the ground truth scene information is not trivial.
+One approach has been to acquire mages where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations (REFS, Foster).
+This is somewhat painstaking, however, and in any case provides information about the illumination only at a small number of selected locations, so that generalizing across the image requires strong assumptions.
+Some progress is being made on characterizing how illumination varies over space in natural scenes (REF, Pont), which in the longer run may guide how information from reference objects can be used to provide reasonable estimates.
+Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene (REFS, UCSB hyperspectral, Funt, look in Barron paper for more).
+These data sets have been useful for evaluating computational color constancy algorithms, but the use of posed scenes does not scale well when the need is for large training sets to use with supervised learning.
 
-In this work, we study lightness estimation of objects in naturalistic scenes using supervised learning methods.
-Lightness is the attribute that determines the brightness of a color.
-A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color.
-For achromatic objects, lightness is the property that changes from black to gray to white.
-Here, we study the effects of variations in the reflected light on the perceived lightness.
-These variations can result both due to geometrical factors (like shape, size, relative position of objects, etc.) or  spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
-In this work, we focus on spectral factors, specifically the effects of variations in the surface reflectance spectra and the illumination spectra (Fig.\ref{fig:introExampleFigure}).
-Our aim is to identify the computations that lead to accurate lightness estimation.
+Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as \em{virtual natural scenes}.
+We describe this approach in detail below, but the key advantage is that we can produce large numbers of naturalistic images where all of the underlying properties are well-specified.
+This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
+This general approach has been adopted by other labs for the study of computational estimation of optical flow (REF, Black) and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception (REFS: Many -- go to Boynton lecture slides for some).
+Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the discussion.
+
+In this initial work, we do not tackle the full problem of color constancy.
+Rather, as a point of departure, we consider the computational problem of estimating a single attribute of object surface reflectance, which we refer to as surface luminance.
+We compute object luminance from an object's surface reflectance function as follows.
+We compute the light that would be reflected to the eye from a flat matte object with that surface reflectance, when the object is diffusely illuminated by the standard CIE daylight spectrum D65 (REF, CIE).
+We then compute the luminance of this reflected light, using the CIE 1931 photopic luminosity function (REF, CIE), and divide this by the luminance of a perfectly reflecting diffuser (surface reflectance of one at all wavelengths) when that is computed in the same way.
+%@techreport{RN1912,
+%   author = {CIE},
+%   title = {Colorimetry, second edition},
+%   institution = {Bureau Central de la CIE},
+%   number = {15.2},
+%   year = {1986},
+%   type = {Report}
+%}
+This procedure allows us to assign to any surface reflectance a single surface luminance value.
+Because the perceived lightness of an object is approximately (but by no means exactly, see REF Wyszecki) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of lightness constancy.
+%@inbook{RN10709,
+%   author = {Wyszecki, G.},
+%   title = {Color appearance},
+%   booktitle = {Handbook of Perception and Human Performance: Sensory Processes and Perception},
+%   publisher = {John Wiley & Sons},
+%   address = {New York},
+%   pages = {9.1-9.56},
+%   year = {1986},
+%   type = {Book Section}
+%}
+This is a generalization of the way this term is often used, where it refers more specifically to the stability of perceived lightness across images of scenes where all objects and illuminants are achromatic (REF, GILCHRIST BOOK).
+%@book{RN3427,
+%   author = {Gilchrist, A. L.},
+%   title = {Seeing Black and White},
+%   publisher = {Oxford University Press},
+%   address = {Oxford},
+%   year = {2006},
+%   type = {Book}
+%}
+Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (se  Fig.~\ref{fig:introExampleFigure}).
+A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimeted.
+
+The rest of this paper is organized as follows. [WRITE AN OUTLINE HERE.]  We conclude that [GIVE THE RESULT].
+
+%@article{RN130,
+%   author = {Nascimento, S. M. and Amano, K. and Foster, D. H.},
+%   title = {Spatial distributions of local illumination color in natural scenes},
+%   journal = {Vision Res},
+%   volume = {120},
+%   pages = {39-44},
+%   ISSN = {1878-5646 (Electronic)
+%0042-6989 (Linking)},
+%   DOI = {10.1016/j.visres.2015.07.005},
+%   url = {http://www.ncbi.nlm.nih.gov/pubmed/26291072},
+%   year = {2016},
+%   type = {Journal Article}
+%}
+%@inproceedings{RN134,
+%   author = {Chakrabarti, A. and Zickler, T.},
+%   title = {Statistics of real-world hyperspectral images},
+%   booktitle = {Proceedings of the IEEE Computer Society Conference on Computer Vision and Pattern Recognition},
+%   pages = {193-200},
+%   type = {Conference Proceedings}
+%}
+%@article{RN7450,
+%   author = {Parraga, C. A. and Brelstaff, G. and Troscianko, T. and Moorehead, I. R.},
+%   title = {Color and luminance information in natural scenes},
+%   journal = {Journal of The Optical Society of America A},
+%   volume = {15},
+%   pages = {563-569},
+%   year = {1998},
+%   type = {Journal Article}
+%}
+%@article{RN9554,
+%   author = {Tkacik, G. and Garrigan, P. and Ratliff, C. and Milcinski, G. and Klein, J. M. and Sterling, P. and Brainard, D. H. and Balasubramanian, V.},
+%   title = {Natural images from the birthplace of the human eye},
+%   journal = {PLoS ONE},
+%   volume = {6},
+%   number = {6:e20409},
+%   DOI = {doi:10.1371/journal.pone.0020409},
+%   url = {http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0020409},
+%   year = {2011},
+%   type = {Journal Article}
+%}
 

### 2017-12-18 Draft1/draft1.tex
Worked on intro

@@
 This technique has provided computations that efficiently estimate [depth, focus, whatever]  from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
-In this paper, we apply AMA to a special case of the color constancy problem (lightness constancy) and evaluate how well it performs for naturalistic image input.
+In this paper, we apply AMA as well as comparison supervised learning algorithms to a special case of the color constancy problem (lightness constancy) and evaluate how well it performs for naturalistic image input.
+% [CHECK WHETHER ANY OF THIS NEEDS TO BE MELDED INTO THE PARAGRAPH ABOVE]
+%We employ a supervised learning approach to understand this phenomenon.
+We generate a database of multispectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene.
+These images are labeled with the perceived lightness of the target object under standard daylight spectrum $D_{65}$ (see SI).
+We generate hundreds of images with variations in the surface reflectance spectra of the objects and the illumination spectra of the light sources (Fig.~\ref{fig:introExampleFigure}).
+We study three cases resulting from the combination of such spectral variations
 
@@
 
-Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as \em{virtual natural scenes}.
-We describe this approach in detail below, but the key advantage is that we can produce large numbers of naturalistic images where all of the underlying properties are well-specified.
+Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as {\em virtual natural scenes}.
+In addition to employing computer graphics to render the light reaching the eye from specified scenes, we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
+We describe this approach in detail below, but the key advantage is that we can produce large numbers of naturalistic images and corresponding cone mosaic responses, where all of the underlying scene properties are well-specified.
 This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
 This general approach has been adopted by other labs for the study of computational estimation of optical flow (REF, Black) and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception (REFS: Many -- go to Boynton lecture slides for some).
-Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the discussion.
+Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \ref{Discussion}.
 
@@
 This procedure allows us to assign to any surface reflectance a single surface luminance value.
-Because the perceived lightness of an object is approximately (but by no means exactly, see REF Wyszecki) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of lightness constancy.
+Because the perceived lightness of an object is approximately (but by no means exactly, see REF Wyszecki) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of {\em lightness constancy}.
 %@inbook{RN10709,
@@
 %}
-Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (se  Fig.~\ref{fig:introExampleFigure}).
-A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimeted.
+Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (see  Fig.~\ref{fig:introExampleFigure}).
+A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimated.
+
+Even within the special case of lightness constancy, there are many scene manipulations that could be considered.
+The set of manipulations we focus on here are illustrated by the three panels of (Fig.~\ref{fig:studiedCases}).
+These cases are: 1.
+variation in target object spectrum (Fig.\ref{fig:targetVarying}) with fixed light source and background objects spectra, 2.
+variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
+variations in all three types of spectra (target object, light source, and background objects) (Fig.\ref{fig:allSpectraVarying}).
+Across real scenes, there will also be variations in the shape of the target object, its pose, eye position, etc.
+(see \ref{Methods}).
+In this paper, we focus on the problem of lightness constancy within scene ensembles where these geometric factors are held fixed.
 
 The rest of this paper is organized as follows. [WRITE AN OUTLINE HERE.]  We conclude that [GIVE THE RESULT].
+%EDIT THIS IN HERE.
+%In the following, we describe each one of these stages of our approach in detail.
+In the methods section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}).
+Next, we describe the steps to simulate the response of the retinal cones to these images (\nameref{method:Isetbio}).
+Finally, we describe the three learning methods we have used in our analysis (\nameref{method:SupervisedLearning}).
+In the results section, we show the estimates and performance of each one of the supervised methods for the three cases with different spectral variations.
+%
+%We show that for cases that have spectral variation only in target reflectance or background reflectance or the illuminant, the standard lightness ($Y_{65}$) can be estimated by simple transformations of the cone responses.
+For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
+For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
+Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
+Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
+%
+%Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
+Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
+Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
+We discuss the implications of such receptive fields on lightness constancy.
 
@@
 
-\begin{comment}
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{approach.png}
-\caption{{\bf Approach:} We have employed a supervised learning approach to study color constancy.
-We first generate a large dataset of multispectral images labeled with the lightness level of the target object.
-We generate images at multiple lightness levels, with images at the same lightness level having variable object reflectance spectra and illumination spectra.
-These multispectral images are used to simulate the response of the visual system.
-We use isetbio toolbox to model the optics and physiology of early vision and produce the response of the cones in the retina.
-We use supervised computational learning methods on this labeled dataset of cone-responses to estimate the lightness of the target object.
-The performance of the supervised method is calculated using a separate test dataset.}
-\label{fig:approach}
-\end{figure}
-\end{comment}
-
-We employ a supervised learning approach to understand this phenomenon.
-We generate a database of multispectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene.
-These images are labeled with the perceived lightness of the target object under standard daylight spectrum $D_{65}$ (see SI).
-We generate hundreds of images with variations in the surface reflectance spectra of the objects and the illumination spectra of the light sources (Fig.~\ref{fig:introExampleFigure}).
-We study three cases resulting from the combination of such spectral variations (Fig.~\ref{fig:studiedCases}).
-These cases are: 1.
-Variation in target object spectrum (Fig.\ref{fig:targetVarying}) with fixed illumination and background, 2.
-Variations in both the target object spectrum and the light source spectra, with fixed background spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
-Variations in all three spectra (target, background and light source) (Fig.\ref{fig:allSpectraVarying}).
-The effects of other types of spectral variations can be explained in terms of one of these cases (see Discussion/Supplementary information).
-Next, we simulate the response of the cones in the retina to these multispectral images using an accurate model of the early visual system.
-Such labeled cone-responses datasets are then analyzed using supervised computational learning methods.
-We use three methods: linear regression, generalized SVD regression and accuracy maximization analysis (AMA) in our analysis.
-These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness.
-These methods identify the receptive fields (RFs) that optimal for lightness estimation.
-We evaluate the performance of the learnt RFs on a test set of images.
-
 % Figure 2: Cases Studied
@@
 We studied three types of spectral variations.
-(a) Case 1: Target reflectance spectrum variable, illumination spectra fixed, background spectra fixed, (b) Case 2: Target spectrum variable, Illumination spectra variable, Background spectra fixed, (c) Case 3: Target spectrum variable, Illumination spectra variable, Background spectra variable.}
+(a) Case 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed, (b) Case 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Case 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
+This panel is reproduced from \ref{fig:introExampleFigure}.
+As in \ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
+Moreover, across the three panels of this figure, spheres in corresponding locations have the same surface reflectance.
+In all three panels, the overall lights source spectra scale factors (see \ref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+[CHECK THAT THIS WORKS FOR A NICE FIGURE].
+The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
 \label{fig:studiedCases}
 \end{figure}
-
-In the following, we describe each one of these stages of our approach in detail.
-In the methods section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}).
-Next, we describe the steps to simulate the response of the retinal cones to these images (\nameref{method:Isetbio}).
-Finally, we describe the three learning methods we have used in our analysis (\nameref{method:SupervisedLearning}).
-In the results section, we show the estimates and performance of each one of the supervised methods for the three cases with different spectral variations.
-
-We show that for cases that have spectral variation only in target reflectance or background reflectance or the illuminant, the standard lightness ($Y_{65}$) can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
-For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
-Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
-Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
-
-Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
-Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
-We discuss the implications of such receptive fields on lightness constancy.
 

### 2017-12-19 Draft1/draft1.tex
more edits

--- 2017-12-14 Draft1/draft1.tex
@@
 \section{Introduction}
-The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
+The perceived color of an object has important behavioral implications, since color helps us identify objects and their properties \cite{Mollon89, Jacobs81}.
 Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of light reflected from the object to the eye.
@@
 Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}.
-In this paper, we consider the computational problem of color constancy, that is how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.
+In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.
 
@@
     \caption{(a) {\bf Color Constancy:} The light reflected from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,\vec{x})$, and the illumination spectrum of the light source, $E(\lambda,\vec{x})$.
-Additionally, it depends on geometric factors, such as the object's shape and pose as well as the position of the observer.
+Additionally, it depends on geometric factors, such as the object's shape and pose, as well as the position of the observer.
 The human visual system is able to account for, at least partially, variations in the reflected light due to such extrinsic factors, and produce a percept of object color that is relatively stable with respect to such variations.
@@
 Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
-\cite{LandRetinex}) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
+\citeNP{LandRetinex}) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
 An important insight of this line of research was that to account for variation in illumination, it was necessary to consider the light reflected from the entire scene.
@@
 Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
+None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.
 
-% NEED TO MOTIVATE WHAT WE'RE GOING TO DO.  SUPERVISED LEARNING APPROACH USING VIRTUAL WORLD DATA TO GET LABELLED TRAINING DATA.
+The computational work reviewed above is based on formulating an explicit model of the image formation process and the statistical properties of natural images, and leveraging these formulations to obtain an appropriate ``inverse optics" algorithm.
+An alternative approach, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors.
+Along these lines, Barron \cite{barron2015convolutional} recently developed a color balancing algorithm based on training a neural network to detect a uniform illuminant in an image by matching image templates in the chromaticity space.
+The use of supervised learning to understand human perceptual capabilities has enjoyed success in domains outside of color vision.
+Geisler and colleagues, for example, have developed a technique they refer to as accuracy maximization analysis (AMA, \citeNP{geisler2009optimal}), which learns linear filters whose output carries information that is optimized for particular perceptual tasks.
+This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus \cite{burge2011optimal} and disparity \cite{burge2014optimal} from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
+In this paper, we apply AMA, as well as comparison supervised learning algorithms to a special case of the color constancy problem (lightness constancy) and evaluate how well it performs for naturalistic image input.
 
-% IN THIS PAPER, WILL APPLY OUR APPROACH TO A REDUCED VERSION OF THE PROBLEM, AS A FIRST STEP
+A difficulty in using machine learning approaches for color constancy is that these approaches require large training sets with images of scenes containing objects with known surface reflectances illuminated with known illuminations.
+Such data sets are not readily available.
+Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection},  ( ADD McGill Database).
+Generating databases with both the images and the ground truth scene information is not trivial.
+One approach has been to acquire mages where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations (\cite{NascimentoFoster2016}).
+This is somewhat painstaking, however, and in any case provides information about the illumination only at a small number of selected locations, so that generalizing across the image requires strong assumptions.
+Some progress is being made on characterizing how illumination varies over space in natural scenes \cite{mury2007spatial}, which in the longer run may guide how information from reference objects can be used to provide reasonable estimates.
+Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene \cite{funt1988color,ciurea2003large} (ADD UCSB hyperspectral).
+These data sets have been useful for evaluating computational color constancy algorithms, but the use of posed scenes does not scale well for use with supervised learning methods which needs large training sets.
 
-In this work, we study lightness estimation of objects in naturalistic scenes using supervised learning methods.
-Lightness is the attribute that determines the brightness of a color.
-A color with a low lightness is nearly black, while one with a high lightness is the pure, saturated color.
-For achromatic objects, lightness is the property that changes from black to gray to white.
-Here, we study the effects of variations in the reflected light on the perceived lightness.
-These variations can result both due to geometrical factors (like shape, size, relative position of objects, etc.) or  spectral factors (such as the illumination spectra, surface reflectance, diffusivity, etc.).
-In this work, we focus on spectral factors, specifically the effects of variations in the surface reflectance spectra and the illumination spectra (Fig.\ref{fig:introExampleFigure}).
-Our aim is to identify the computations that lead to accurate lightness estimation.
+Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as {\em virtual natural scenes}.
+Here, in addition to employing computer graphics to render the light reaching the eye from specified scenes, we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
+We describe this approach in detail below, but the key advantage is that we can produce large numbers of naturalistic images and the corresponding cone mosaic responses, where all of the underlying scene properties are well-specified.
+This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
+This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception (REFS: Many -- go to Boynton lecture slides for some).
+Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.
 
-\begin{comment}
-\begin{figure}
-\centering
-\includegraphics[width=\textwidth]{approach.png}
-\caption{{\bf Approach:} We have employed a supervised learning approach to study color constancy.
-We first generate a large dataset of multispectral images labeled with the lightness level of the target object.
-We generate images at multiple lightness levels, with images at the same lightness level having variable object reflectance spectra and illumination spectra.
-These multispectral images are used to simulate the response of the visual system.
-We use isetbio toolbox to model the optics and physiology of early vision and produce the response of the cones in the retina.
-We use supervised computational learning methods on this labeled dataset of cone-responses to estimate the lightness of the target object.
-The performance of the supervised method is calculated using a separate test dataset.}
-\label{fig:approach}
-\end{figure}
-\end{comment}
+In this initial work, we do not tackle the full problem of color constancy.
+Rather, as a point of departure, we consider the computational problem of estimating a single attribute of object surface reflectance, which we refer to as surface luminance.
+We compute object luminance from an object's surface reflectance function as follows.
+We compute the light that would be reflected to the eye from a flat matte object with that surface reflectance, when the object is diffusely illuminated by the standard CIE daylight spectrum D65 (\cite{CIE86}).
+We then compute the luminance of this reflected light, using the CIE 1931 photopic luminosity function (\cite{CIE86}), and divide this by the luminance of a perfectly reflecting diffuser (surface reflectance of one at all wavelengths) when that is computed in the same way.
+This procedure allows us to assign to any surface reflectance a single surface luminance value.
+Because the perceived lightness of an object is approximately (but by no means exactly, see \cite{wyszecki1986color}) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of {\em lightness constancy}.
+This is a generalization of the way this term is often used, where it refers more specifically to the stability of perceived lightness across images of scenes where all objects and illuminants are achromatic \cite{gilchrist2006seeing}.
+Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (see  Fig.~\ref{fig:introExampleFigure}).
+A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimated.
 
-We employ a supervised learning approach to understand this phenomenon.
-We generate a database of multispectral images of naturalistic scenes, labeled by the lightness of a specific target object in the scene.
-These images are labeled with the perceived lightness of the target object under standard daylight spectrum $D_{65}$ (see SI).
-We generate hundreds of images with variations in the surface reflectance spectra of the objects and the illumination spectra of the light sources (Fig.~\ref{fig:introExampleFigure}).
-We study three cases resulting from the combination of such spectral variations (Fig.~\ref{fig:studiedCases}).
+Even within the special case of lightness constancy, there are many scene manipulations that could be considered.
+The set of manipulations we focus on here are illustrated by the three panels of (Fig.~\ref{fig:studiedCases}).
 These cases are: 1.
-Variation in target object spectrum (Fig.\ref{fig:targetVarying}) with fixed illumination and background, 2.
-Variations in both the target object spectrum and the light source spectra, with fixed background spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
-Variations in all three spectra (target, background and light source) (Fig.\ref{fig:allSpectraVarying}).
-The effects of other types of spectral variations can be explained in terms of one of these cases (see Discussion/Supplementary information).
-Next, we simulate the response of the cones in the retina to these multispectral images using an accurate model of the early visual system.
-Such labeled cone-responses datasets are then analyzed using supervised computational learning methods.
-We use three methods: linear regression, generalized SVD regression and accuracy maximization analysis (AMA) in our analysis.
-These methods identify the computations that need to be performed on the cone-responses to estimate the target object lightness.
-These methods identify the receptive fields (RFs) that optimal for lightness estimation.
-We evaluate the performance of the learnt RFs on a test set of images.
+variation in target object spectrum (Fig.\ref{fig:targetVarying}) with fixed light source and background objects spectra, 2.
+variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
+variations in all three types of spectra (target object, light source, and background objects) (Fig.\ref{fig:allSpectraVarying}).
+Across real scenes, there will also be variations in the shape of the target object, its pose, eye position, etc.
+(see \nameref{Methods}).
+In this paper, we focus on the problem of lightness constancy within scene ensembles where these geometric factors are held fixed.
+
+The rest of this paper is organized as follows.
+In the \nameref{Methods} section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}).
+Next, we describe the steps to simulate the response of the retinal cones to these images (\nameref{method:Isetbio}).
+Finally, we describe the supervised learning methods used in our analysis (\nameref{method:SupervisedLearning}).
+In the \nameref{Results} section, we show the estimates and performance of the supervised methods for the three cases mentioned above.
+
+We show that for cases that have spectral variation only in target reflectance or background reflectance or the illuminant the lightness can be estimated by simple transformations of the cone responses.
+For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
+For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
+Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
+Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
+
+Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
+Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
+Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
+We discuss the implications of such receptive fields on lightness constancy.
 
@@
 We studied three types of spectral variations.
-(a) Case 1: Target reflectance spectrum variable, illumination spectra fixed, background spectra fixed, (b) Case 2: Target spectrum variable, Illumination spectra variable, Background spectra fixed, (c) Case 3: Target spectrum variable, Illumination spectra variable, Background spectra variable.}
+(a) Case 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed, (b) Case 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Case 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
+This panel is reproduced from \ref{fig:introExampleFigure}.
+As in \ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
+Moreover, across the three panels of this figure, spheres in corresponding locations have the same surface reflectance.
+In all three panels, the overall lights source spectra scale factors (see \ref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+[CHECK THAT THIS WORKS FOR A NICE FIGURE].
+The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
 \label{fig:studiedCases}
@@
 
-In the following, we describe each one of these stages of our approach in detail.
-In the methods section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}).
-Next, we describe the steps to simulate the response of the retinal cones to these images (\nameref{method:Isetbio}).
-Finally, we describe the three learning methods we have used in our analysis (\nameref{method:SupervisedLearning}).
-In the results section, we show the estimates and performance of each one of the supervised methods for the three cases with different spectral variations.
-
-We show that for cases that have spectral variation only in target reflectance or background reflectance or the illuminant, the standard lightness ($Y_{65}$) can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
-For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
-Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
-Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
-
-Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
-Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
-We discuss the implications of such receptive fields on lightness constancy.
-
-\section{Methods}
+\section*{Methods} \label{Methods}
 \subsection{Image database} \label{method:VirtualWorld}
-We called our image generation software Virtual world color constancy (VWCC).
+We call our image generation software Virtual world color constancy (VWCC).
 The details of the software are provided in the supplementary information section.
@@
 
-\section{Results}
+\section{Results} \label{Results}
 \subsection{Optimal receptive fields show a center surround structure}
@@
 
-\section{Discussion}
-
+\section{Discussion} \label{Discussion}
 \section{Supplementary Information}

### 2017-12-19 Draft1/draft1.tex
Today’s editing

@@
 \section*{Methods} \label{Methods}
-\subsection{Image database} \label{method:VirtualWorld}
-We call our image generation software Virtual world color constancy (VWCC).
+\subsection{Overview}
+
+There are four key parts to our methods.
+The first is how we generate a labelled set of training data for our supervised learning algorithms.
+The second is how we model the transformations applied by the early visual system to generate modeled responses of the cone photoreceptor mosaic.
+The third is the details of the supervised learning methods we apply to the labelled training data.
+And the fourth is how we evaluate the performance of the algorithms.
+We describe each of these in the sections below.
+
+\subsection{Labelled image database} \label{method:VirtualWorld}
+
+\subsubsection{Virtual naturalistic scenes}
+
+The light that reflects off an object and reaches our eyes depends on many factors.
+These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer.
+In natural scenes, these spectral and geometrical factors vary considerably.
+To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors.
+We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene.
+Under natural conditions it is difficult to control and quantify every such parameter in a scene.
+Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.
+
+To overcome this  challenge, we have developed an image rendering software pipeline that allows us to specify a virtual, but naturalistic, statistical model of visual scenes with parametric control over factors in natural scenes.
+The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
+It then renders a multispectral 2D image of each modeled visual scene.
+Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
+In addition, our software simulates the responses of retinal cones to the rendered multispectral images using a realistic model of the early human visual system.
+Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
+Our software, which is written in MATLAB, is freely available through a public respository: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
+It builds on several other open source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
+Below we refer to the software pipeline as VWCC (for Virtual World Color Constancy).
+
+The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}).
+The base scene is a 3D model that defines a rendering space.
+It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position.
+VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses.
+We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly.
+We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene.
+Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).
+The overall spatial scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness.
+If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes.
+As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library.
+Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).
+
+% Figure 9
+\begin{figure}[t]
+\centering
+\begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
+        \caption{Library }
+        \label{fig:baseSceneLibrary}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.png}
+        \caption{Mill}
+        \label{fig:baseSceneMill}
+    \end{subfigure}    
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+    %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.png}
+        \caption{Table-Chairs}
+        \label{fig:baseSceneTableChairs}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
+        \caption{Indoor-plant}
+        \label{fig:baseSceneIndoorPlant}
+    \end{subfigure}    
+    ~
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_e.png}
+        \caption{Warehouse}
+        \label{fig:baseSceneWarehouse}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_f.png}
+        \caption{Checkerboard}
+        \label{fig:baseSceneCheckerBoard}
+    \end{subfigure}
+    \caption{{Example of base scenes form the VWCC library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.
+The reflectance spectra of the distinct surfaces in each scene has been assigned randomly (see below) using the VWCC software.
+The light source spectra were also assigned randomly to the default light source for each scene.
+[CHECK THAT THIS IS CORRET] }\label{fig:baseScenes}
+\end{figure}
+
+VWCC provides an option for inserting 3D objects and lights sources into the base scene.
+Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted into the library base scene.
+The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from object descriptions made available on the Internet.
+The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.
+
+% Figure 10
+\begin{figure}[h]
+\centering
+\begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.png}
+        \caption{Big-ball}
+        \label{fig:libraryWithBigBall}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+\begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.png}
+        \caption{Small-ball}
+        \label{fig:libraryWithSmallBall}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.png}
+        \caption{Barrel}
+        \label{fig:libraryWithBarrel}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.png}
+        \caption{Xylophone}
+        \label{fig:libraryWithXylophone}
+    \end{subfigure}
+    ~
+	\begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_e.png}
+        \caption{Ring toy}
+        \label{fig:libraryWithRingToy}
+    \end{subfigure}
+        ~
+    	\begin{subfigure}[b]{0.22 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_f.png}
+        \caption{Champagne Bottle}
+        \label{fig:libraryWithChampagneBottle}
+    \end{subfigure}
+\caption{{Library base scene with inserted objects.} The VWCC software was used to insert different objects into the library base scene, with each panel showing a different object.
+The objects were inserted at a location in the image and then the camera was pointed at the object, so that the object's image is at the center of the rendered image.
+In the figure panels, the full rendered image is cropped so that the inserted object is more visually salient.
+We use this capability of our software pipeline to insert target objects into scenes.}\label{fig:libraryWithTarget}
+\end{figure}
+
+The size, position and orientation of the inserted objects and lights may be specified programatically (Fig.~\ref{fig:objectTransformations}) or chosen randomly under constraints provided by the base scene meta-data.
+Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.
+
+Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene.
+We also assign an illuminant spectral power distribution to each light source in the scene.
+Objects in the VWCC library may contain more than one distinct surface, each of which may be assigned a different surface reflectance.
+As with object position, these may be specified programatically.
+In the present work, we use simple choices for texture (all surfaces spatially uniform) and material property (all surfaces matte) and focus on variation in surface spectral reflectance.
+
+% Figure11
+\begin{figure}
+\centering
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.png}
+        \caption{Target spectra}
+        \label{fig:targetVariation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.png}
+        \caption{Background spectra}
+        \label{fig:backGroundVariation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+    %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.png}
+        \caption{Illumination spectra}
+        \label{fig:illuminationVariation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_d.png}
+        \caption{Target position}
+        \label{fig:targetPositionVariation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_e.png}
+        \caption{Target Size/Orientation}
+        \label{fig:targetSizeOrientation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \caption{{\bf Transformations of the scene.} Each column illustrates transformations of a scene that are under software control.
+(a-c) Spectral Transformations.
+(d-e) Geometrical transformations.
+EXPAND OUT AND SAY WHAT EACH COLUMN IS, INDIVIDUALLY}\label{fig:spectralTransformations}
+\end{figure}
+
+In the present work, we insert one target object and one additional light source into a fixed base scene, and vary reflectance and illuminant spectra.
+We then insert a camera for rendering at a user specified position and point this camera at the target object.
+We ensure that a N by N pixel [CHECK ACTUAL SIZE] region at the center of the image corresponds to light reflected from the target object, which amounts to verifying that the target object at its inserted position was not occluded by other objects in the line of sight from camera.
+For each rendered scene, we specify the surface reflectance of the target object, which allows us to control both its surface luminance as well as its relative surface reflectance.
+The specified surface luminance provides the requisite label for the scene and resultant cone mosaic responses.
+
+We render scenes using the \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba} rendering package, driven by our \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3} rendering pipeline.
+
+For the images used for the primary results reported in this paper, we used the ``{\it Library}'' base scene from the VWCC  and the ``{\it Big Ball}'' object as the target object.
+We also inserted a spherical light source with the same ``{\it Big Ball}'' shape.
+The position, and size of the inserted object, light source and the camera were held fixed for all the images analyzed in this work, i.e., the scene geometry did not vary.
+Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene.
+The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:studiedCases}).
+2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
+A $51 \times 51$ pixel$^2$ patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
+
+[GOT TO HERE]
+\subsubsection{Illumination Spectra}
+The illumination spectrum is generated through a random statistical sampling of a natural illumination spectrum dataset.
+First, we approximate the spectra in the dataset using principle component analysis (PCA).
+We decompose the spectra as a linear sum over the PCA basis vectors corresponding to the largest 6 PCA eigenvalues.
+Next, we sample random spectra from this low 6 dimensional PCA space assuming the spectral distribution to be a multivariate gaussian.
+
+% Figure 12
+\begin{figure}
+\centering
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
+        \caption{Granada natural daylight dataset}
+        \label{fig:granadaSpectra}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
+        \caption{Rescaled Granada dataset}
+        \label{fig:rescaledGranada}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
+        \caption{Randomly generated samples}
+        \label{fig:randomIlluminant}
+    \end{subfigure}
+
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_d.pdf}
+        \caption{xy chromaticity diagram}
+        \label{fig:xyDiagram}
+    \end{subfigure}
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_e.pdf}
+        \caption{Normalized PCA eigenvalues}
+        \label{fig:granadaEV}
+    \end{subfigure}
+      	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_f.pdf}
+        \caption{sRGB rendition of samples from Fig.\ref{fig:randomIlluminant}}
+        \label{fig:sRGBIlluminant}
+    \end{subfigure}
+    \caption{{\bf Generating random illumination spectrum:} The illumination spectra are generated by random sampling of Granada daylight spectra assuming a multivariate gaussian distribution.
+The mean and variance of the gaussian are chosen by projecting the dataset along PCA directions and taking the mean and covariance of the projections.
+(a) Granada natural daylight dataset.
+(b) Rescaled Granada dataset.
+Each spectra is rescaled by its mean illumination over frequency.
+(c) Randomly generated samples.
+(d) xy chromaticity diagram of the rescaled dataset (Fig.
+\ref{fig:rescaledGranada}) and the randomly generated samples (Fig.\ref{fig:randomIlluminant}).
+(e) Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
+The eigenvalues have been normalized by the sum over all eigenvalues.
+The dotted line (= 0.9) is for reference.
+We choose the first six eigenvectors in ur analysis.
+(f) The sRGB renditions of the random samples generated in \ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
+\end{figure}
+
+We have used the Granada natural daylight spectrum \href{http://colorimaginglab.ugr.es/pages/Data}{dataset} \cite{peyvandi2016colorimetric} to sample illuminants.
+Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset.
+Since the distribution varies over multiple order of magnitudes, we rescale each spectrum by dividing by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$.
+These rescaled spectra $(I_i^s(\lambda))$ are then mean centered for PCA by subtracting out the mean
+rescaled spectra, $\bar{I}^{s}(\lambda)$. The mean is obtained
+by taking the sample mean over all spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
+The resulting mean subtracted dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$, 
+is decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
+where $\hat{{\bf e}}_j^{PCA}$s are PCA basis vectors obtained using 
+singular value decomposition (SVD). $w_{ij}$'s are the projections 
+of $I_i^{MC}(\lambda)$ along the PCA basis vectors $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. We approximate 
+this decomposition by summing over the basis vectors corresponding to
+the largest six SVD eigenvalues. For the Granada dataset, these six 
+eigenvalues constitute more than $98\%$ of the variance. These steps
+can be summarized as follows:
+\begin{align}
+I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}
+\end{align}
+
+To generate new illuminants $\tilde{I}_i(\lambda)$, random 
+projection weights ($\tilde{w}_{ij}$) are generated using a multivariate 
+gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
+and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
+If the $\tilde{w}_{ij}$ are such that, $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, for all $\lambda$, then the new illuminant spectrum is given as
+\begin{align}
+\tilde{I}(\lambda) = \left( \tilde{I}_{MC}(\lambda) + \bar{I}_{s}(\lambda)\right).
+\end{align}
+Finally $\tilde{I}(\lambda)$ is rescaled by a random number generated uniformly in the range [0, 100].
+
+% Figure 13
+\subsubsection{Reflectance Spectrum}
+\begin{figure}
+\centering
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+        \caption{Natural surface reflectance spectra}
+        \label{fig:naturalSurface}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+        \caption{Randomly generated samples}
+        \label{fig:randomSurface}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+        \caption{sRGB rendition of samples from \ref{fig:randomSurface}}
+        \label{fig:sRGBSurface}
+    \end{subfigure}
+    \caption{{\bf Generating random surface reflectance spectrum:} The surface reflectance spectra are generated by random sampling of natural surface reflectance spectra assuming a multivariate gaussian distribution.
+The mean and variance of the gaussian are chosen by projecting the natural dataset along PCA directions and taking the mean and covariance of the projections.
+(a) Natural surface reflectance spectra.
+(b) Randomly generated samples.
+(c) The sRGB renditions of the random samples generated in \ref{fig:randomSurface}.}\label{fig:surfaceReflectanceGeneration}
+\end{figure}
+
+The reflectance spectrum are generated similar to illumination spectrum. 
+We have used the Munsell {(\it citation)} and vrhel {(\it citation)} surface reflectance 
+datasets for sampling the reflectance. Let us denote the dataset of natural 
+reflectance spectra as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
+and $M$ is the total number of spectra in the dataset. To generate 
+a random reflectance spectrum $\tilde{R}(\lambda)$, 
+we first mean center the dataset by subtracting out the 
+mean surface reflectance spectrum, $\bar{R}(\lambda)$,
+from each surface reflectance spectrum.
+$\bar{R}(\lambda)$ is obtained by taking the sample 
+mean over all spectra in the dataset, i.e.,
+$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. 
+Thus we have the mean centered reflectance 
+spectrum dataset as $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
+We decompose this as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$. Here,
+${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD 
+and $w_{ij}$s are the projections of $R_i^{\rm MC}(\lambda)$ along the PCA eigenvectors 
+$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. The 
+decomposition is approximated by summing over the PCA basis 
+vectors corresponding to the largest six SVD eigenvalues. These six eigenvalues capture 
+more than $92\%$ of the variance in the combined Munsell and vhrel datasets. To generate 
+a new reflectance spectrum, a point is sampled randomly in this 
+six dimensional sub-space using a multivariate normal 
+distribution, with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
+and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. If the randomly sampled projection, $\tilde{w}_{ij}$, is 
+such that $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, the new surface reflectance 
+is given as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.
+
+% Figure 14
+\begin{figure}
+\centering
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
+        \caption{Natural surface reflectance spectra}
+        \label{fig:naturalSurfaceTarget}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
+        \caption{Randomly generated target samples}
+        \label{fig:randomSurfaceTarget}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
+        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
+        \label{fig:sRGBSurfaceTarget}
+    \end{subfigure}
+    \caption{{\bf Target object surface reflectance spectrum:} For getting the target object surface reflectance, we first generate the spectra similar to that of other objects and then rescale them appropriately to get the required perceived lightness.
+(a) Natural surface reflectance spectra.
+(b) Randomly generated samples for target reflectance.
+(c) The sRGB renditions of the random samples generated in Fig.~\ref{fig:randomSurfaceTarget}.
+We show 10 samples at 1 lightness levels.}\label{fig:targetSurfaceReflectance}
+\end{figure}
+
+For generating the target object reflectance at a particular lightness $(Y_{\rm T})$, the values in the spectrum are 
+rescaled by a scalar such that the perceived lightness of the 
+target surface under standard daylight illuminant $(D_{65}(\lambda))$ 
+equals a designated value.
+The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE luminosity (or luminous efficiency) function.
+$\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
+perception of brightness.
+The target reflectance is given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
+
+% NEED TO DECIDE PRECISELY WHERE TO USE THIS PROSE AND  FIGURE
+%Figure~\ref{sceneWithCroppedImage} illustrates the steps in this process for one scene.  We start with how we generate a single labeled set of cone responses
+%We call our image generation software Virtual world color constancy (VWCC).
 The details of the software are provided in the supplementary information section.
@@
 \subsection{Model of Visual System} \label{method:Isetbio}
+
+Finally, these multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
+
+To generate the retinal response one needs to specify the retinal cone mosaic and the size of the retinal image.
+The retinal cone mosaic is specified in terms of the total number of cones and the proportion of the long(L), medium(M) and the short(S) cones in the mosaic.
+With these parameters, the software generates the specified number of LMS cones with random positions on a square grid.
+The size of the retinal image is specified in terms of the field of view and object distance from the eye.
+
 We simulate visual system response using \href{http://isetbio.org}{Isetbio} software toolbox.
@@
 \section{Supplementary Information}
-\subsection{Virtual World Color Constancy}
-The light that reflects off an object and reaches our eyes depends on many factors.
-These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer.
-In natural scenes, these spectral and geometrical factors vary considerably.
-To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors.
-We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene.
-Under natural conditions it is difficult to control and quantify every such parameter in a scene.
-Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.
-
-To overcome this  challenge, we have developed an image rendering software pipeline that allows us to specify a virtual, but naturalistic, statistical model of visual scenes with parametric control over factors in natural scenes.
-The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
-It then renders a multispectral 2D image of each modeled visual scene.
-Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
-In addition, our software simulates the responses of retinal cones to the rendered multispectral images using a realistic model of the early human visual system.
-Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
-Our software, which is written in MATLAB, is freely available through a public respository: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
-It builds on several other open source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
-Below we refer to the software pipeline as VWCC (for Virtual World Color Constancy).
-
-The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}).
-The base scene is a 3D model that defines a rendering space.
-It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position.
-VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses.
-We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly.
-We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene.
-Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).
-The overall scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness.
-If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes.
-As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library.
-Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).
-
-% Figure 9
-\begin{figure}[t]
-\centering
-\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
-        \caption{Library }
-        \label{fig:baseSceneLibrary}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.png}
-        \caption{Mill}
-        \label{fig:baseSceneMill}
-    \end{subfigure}    
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.png}
-        \caption{Table-Chairs}
-        \label{fig:baseSceneTableChairs}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
-        \caption{Indoor-plant}
-        \label{fig:baseSceneIndoorPlant}
-    \end{subfigure}    
-    ~
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_e.png}
-        \caption{Warehouse}
-        \label{fig:baseSceneWarehouse}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_f.png}
-        \caption{Checkerboard}
-        \label{fig:baseSceneCheckerBoard}
-    \end{subfigure}
-    \caption{Example of base scenes.}\label{fig:baseScenes}
-\end{figure}
-
-VWCC provides an option for inserting 3D objects and lights sources into the base scene.
-Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted in the library base scene.
-The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from materials made available on the Internet.
-The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.
-
-% Figure 10
-\begin{figure}[h]
-\centering
-\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.png}
-        \caption{Big-ball}
-        \label{fig:libraryWithBigBall}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.png}
-        \caption{Small-ball}
-        \label{fig:libraryWithSmallBall}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.png}
-        \caption{Barrel}
-        \label{fig:libraryWithBarrel}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.png}
-        \caption{Xylophone}
-        \label{fig:libraryWithXylophone}
-    \end{subfigure}
-    ~
-	\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_e.png}
-        \caption{Ring toy}
-        \label{fig:libraryWithRingToy}
-    \end{subfigure}
-        ~
-    	\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_f.png}
-        \caption{Champagne Bottle}
-        \label{fig:libraryWithChampagneBottle}
-    \end{subfigure}
-\caption{Base scenes with inserted objects.}\label{fig:libraryWithTarget}
-\end{figure}
-
-The size, position and orientation of the inserted objects and lights may be specified programatically (Fig.~\ref{fig:objectTransformations}) or chosen randomly under constraints provided by the base scene meta-data.
-As with the base scene library, the object may be drawn at random from the VWCC object library.
-Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.
-
-Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene.
-We also assign the illuminant spectral power distribution to each light source in the scene.
-Objects in the VWCC library may contain more than one distinct surface, each of which may be assigned a different surface reflectance.
-As with object position, these may be specified programatically.
-In the present work, we use simple choices for texture (all surfaces spatially uniform) and material property (all surfaces matte) and focus on variation in surface spectral reflectance.
-
-[GOT TO HERE.  DHB.]
-% Figure11
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.png}
-        \caption{Target spectra}
-        \label{fig:targetVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.png}
-        \caption{Background spectra}
-        \label{fig:backGroundVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.png}
-        \caption{Illumination spectra}
-        \label{fig:illuminationVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_d.png}
-        \caption{Target position}
-        \label{fig:targetPositionVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_e.png}
-        \caption{Target Size/Orientation}
-        \label{fig:targetSizeOrientation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \caption{{\bf Transformations of the scene:} (a-c) Spectral Transformations. (d-e) Geometrical transformations.}\label{fig:spectralTransformations}
-\end{figure}
-
-One of the inserted objects is chosen as the target object in the scene.
-A camera is inserted at a user specified position and pointed at the target object.
-We ensure that the target object is not completely occluded by other objects in the line of sight of the camera.
-A predefined surface reflectance spectrum is assigned to the target object.
-This target surface reflectance also sets the label for the virtual scene image.
-The image label is defined as the perceived lightness of a uniform object with the surface reflectance same as that of the the target object when viewed under uniform standard daylight spectrum D65.
-The scene is rendered using the Mitsuba rendering package.
-The renderer produces 2D multispectral images of the scene at specified wavelengths.
-Finally, these multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
-
-To generate the retinal response one needs to specify the retinal cone mosaic and the size of the retinal image.
-The retinal cone mosaic is specified in terms of the total number of cones and the proportion of the long(L), medium(M) and the short(S) cones in the mosaic.
-With these parameters, the software generates the specified number of LMS cones with random positions on a square grid.
-The size of the retinal image is specified in terms of the field of view and object distance from the eye.
-
-For the images used in this work, we have used the ``{\it Library}'' base scene from the VWCC  as the and the ``{\it Big Ball}'' object as the target object.
-We also inserted a spherical light source with the same ``{\it Big Ball}'' shape.
-The position, and size of the inserted object, light source and the camera was held fixed for all the images analyzed in this work, i.e., the images were identical in their geometry.
-Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene.
-The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:studiedCases}).
-2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
-A $51 \times 51$ pixel$^2$ patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
-
-\subsection{Generating Spectrum for VWCC}
-\subsubsection{Illumination Spectrum}
-The illumination spectrum is generated through a random statistical sampling of a natural illumination spectrum dataset.
-First, we approximate the spectra in the dataset using principle component analysis (PCA).
-We decompose the spectra as a linear sum over the PCA basis vectors corresponding to the largest 6 PCA eigenvalues.
-Next, we sample random spectra from this low 6 dimensional PCA space assuming the spectral distribution to be a multivariate gaussian.
-
-% Figure 12
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
-        \caption{Granada natural daylight dataset}
-        \label{fig:granadaSpectra}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
-        \caption{Rescaled Granada dataset}
-        \label{fig:rescaledGranada}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
-        \caption{Randomly generated samples}
-        \label{fig:randomIlluminant}
-    \end{subfigure}
-
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_d.pdf}
-        \caption{xy chromaticity diagram}
-        \label{fig:xyDiagram}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_e.pdf}
-        \caption{Normalized PCA eigenvalues}
-        \label{fig:granadaEV}
-    \end{subfigure}
-      	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_f.pdf}
-        \caption{sRGB rendition of samples from Fig.\ref{fig:randomIlluminant}}
-        \label{fig:sRGBIlluminant}
-    \end{subfigure}
-    \caption{{\bf Generating random illumination spectrum:} The illumination spectra are generated by random sampling of Granada daylight spectra assuming a multivariate gaussian distribution.
-The mean and variance of the gaussian are chosen by projecting the dataset along PCA directions and taking the mean and covariance of the projections.
-(a) Granada natural daylight dataset.
-(b) Rescaled Granada dataset.
-Each spectra is rescaled by its mean illumination over frequency.
-(c) Randomly generated samples.
-(d) xy chromaticity diagram of the rescaled dataset (Fig.
-\ref{fig:rescaledGranada}) and the randomly generated samples (Fig.\ref{fig:randomIlluminant}).
-(e) Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
-The eigenvalues have been normalized by the sum over all eigenvalues.
-The dotted line (= 0.9) is for reference.
-We choose the first six eigenvectors in ur analysis.
-(f) The sRGB renditions of the random samples generated in \ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
-\end{figure}
-
-We have used the Granada natural daylight spectrum \href{http://colorimaginglab.ugr.es/pages/Data}{dataset} \cite{peyvandi2016colorimetric} to sample illuminants.
-Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset.
-Since the distribution varies over multiple order of magnitudes, we rescale each spectrum by dividing by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$.
-These rescaled spectra $(I_i^s(\lambda))$ are then mean centered for PCA by subtracting out the mean
-rescaled spectra, $\bar{I}^{s}(\lambda)$. The mean is obtained
-by taking the sample mean over all spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
-The resulting mean subtracted dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$, 
-is decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
-where $\hat{{\bf e}}_j^{PCA}$s are PCA basis vectors obtained using 
-singular value decomposition (SVD). $w_{ij}$'s are the projections 
-of $I_i^{MC}(\lambda)$ along the PCA basis vectors $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. We approximate 
-this decomposition by summing over the basis vectors corresponding to
-the largest six SVD eigenvalues. For the Granada dataset, these six 
-eigenvalues constitute more than $98\%$ of the variance. These steps
-can be summarized as follows:
-\begin{align}
-I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}
-\end{align}
-
-To generate new illuminants $\tilde{I}_i(\lambda)$, random 
-projection weights ($\tilde{w}_{ij}$) are generated using a multivariate 
-gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
-If the $\tilde{w}_{ij}$ are such that, $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, for all $\lambda$, then the new illuminant spectrum is given as
-\begin{align}
-\tilde{I}(\lambda) = \left( \tilde{I}_{MC}(\lambda) + \bar{I}_{s}(\lambda)\right).
-\end{align}
-Finally $\tilde{I}(\lambda)$ is rescaled by a random number generated uniformly in the range [0, 100].
-
-% Figure 13
-\subsubsection{Reflectance Spectrum}
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
-        \caption{Natural surface reflectance spectra}
-        \label{fig:naturalSurface}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
-        \caption{Randomly generated samples}
-        \label{fig:randomSurface}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
-        \caption{sRGB rendition of samples from \ref{fig:randomSurface}}
-        \label{fig:sRGBSurface}
-    \end{subfigure}
-    \caption{{\bf Generating random surface reflectance spectrum:} The surface reflectance spectra are generated by random sampling of natural surface reflectance spectra assuming a multivariate gaussian distribution.
-The mean and variance of the gaussian are chosen by projecting the natural dataset along PCA directions and taking the mean and covariance of the projections.
-(a) Natural surface reflectance spectra.
-(b) Randomly generated samples.
-(c) The sRGB renditions of the random samples generated in \ref{fig:randomSurface}.}\label{fig:surfaceReflectanceGeneration}
-\end{figure}
-
-The reflectance spectrum are generated similar to illumination spectrum. 
-We have used the Munsell {(\it citation)} and vrhel {(\it citation)} surface reflectance 
-datasets for sampling the reflectance. Let us denote the dataset of natural 
-reflectance spectra as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
-and $M$ is the total number of spectra in the dataset. To generate 
-a random reflectance spectrum $\tilde{R}(\lambda)$, 
-we first mean center the dataset by subtracting out the 
-mean surface reflectance spectrum, $\bar{R}(\lambda)$,
-from each surface reflectance spectrum.
-$\bar{R}(\lambda)$ is obtained by taking the sample 
-mean over all spectra in the dataset, i.e.,
-$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. 
-Thus we have the mean centered reflectance 
-spectrum dataset as $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
-We decompose this as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$. Here,
-${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD 
-and $w_{ij}$s are the projections of $R_i^{\rm MC}(\lambda)$ along the PCA eigenvectors 
-$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. The 
-decomposition is approximated by summing over the PCA basis 
-vectors corresponding to the largest six SVD eigenvalues. These six eigenvalues capture 
-more than $92\%$ of the variance in the combined Munsell and vhrel datasets. To generate 
-a new reflectance spectrum, a point is sampled randomly in this 
-six dimensional sub-space using a multivariate normal 
-distribution, with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. If the randomly sampled projection, $\tilde{w}_{ij}$, is 
-such that $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, the new surface reflectance 
-is given as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.
-
-% Figure 14
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
-        \caption{Natural surface reflectance spectra}
-        \label{fig:naturalSurfaceTarget}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
-        \caption{Randomly generated target samples}
-        \label{fig:randomSurfaceTarget}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
-        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
-        \label{fig:sRGBSurfaceTarget}
-    \end{subfigure}
-    \caption{{\bf Target object surface reflectance spectrum:} For getting the target object surface reflectance, we first generate the spectra similar to that of other objects and then rescale them appropriately to get the required perceived lightness.
-(a) Natural surface reflectance spectra.
-(b) Randomly generated samples for target reflectance.
-(c) The sRGB renditions of the random samples generated in Fig.~\ref{fig:randomSurfaceTarget}.
-We show 10 samples at 1 lightness levels.}\label{fig:targetSurfaceReflectance}
-\end{figure}
-
-For generating the target object reflectance at a particular lightness $(Y_{\rm T})$, the values in the spectrum are 
-rescaled by a scalar such that the perceived lightness of the 
-target surface under standard daylight illuminant $(D_{65}(\lambda))$ 
-equals a designated value.
-The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE luminosity (or luminous efficiency) function.
-$\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
-perception of brightness.
-The target reflectance is given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
 

### 2017-12-20 Draft1/draft1.tex
mostly figure renaming

@@
 \section{Introduction}
-The perceived color of an object has important behavioral implications, since color helps us identify objects and their properties \cite{Mollon89, Jacobs81}.
+The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
 Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of light reflected from the object to the eye.
@@
 In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.
+
+There is a considerable literature on computational color constancy.
+Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
+\citeNP{LandRetinex}) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
+An important insight of this line of research was that, to account for variation in illumination, it was necessary to consider the light reflected from the entire scene.
+That is, although good constancy cannot be achieved in the face of illuminant variation if one considers only the light reflected from a single target object, when one considers the entire image it is possible to use the joint variation in light reflected from many objects to obtain (either implicitly or explicitly) an estimate of the illuminant common across the objects, and in turn to use this estimate to produce a stabilized representation of object color.
+At the same time, this processing introduces an additional dependence.
+Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image \cite{BrainardWandellRetinex}.
+Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
+Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
+None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.
 
@@
 Within each row, the surface reflectance of the spheres has the same luminance, when illuminated by a standard reference illuminant, CIE D65.
-The three rows differ in this value, as can be seen by the fact that the lightness of the spheres generally decreases as we move down the rows.
+The three rows differ in this value, as can be seen by the fact that the lightness of the spheres generally decreases as we move down the columns.
 Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.
 Within each column, this relative surface reflectance is held fixed.
+For illustration, we have kept the light source and the background obejcts fixed across the panels.
+See Fig.~\ref{fig:studiedCases} for images with such variations.
 In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
  \end{figure}
-
-There is a considerable literature on computational color constancy.
-Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
-\citeNP{LandRetinex}) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
-An important insight of this line of research was that to account for variation in illumination, it was necessary to consider the light reflected from the entire scene.
-That is, although good constancy cannot be achieved in the face of illuminant variation if one considers only the light reflected from a single target object, when one considers the entire image it is possible to use the joint variation in light reflected from many objects to obtain (either implicitly or explicitly) an estimate of the illuminant common across the objects, and in turn to use this estimate to produce a stabilized representation of object color.
-At the same time, this processing introduces an additional dependence.
-Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image \cite{BrainardWandellRetinex}.
-Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
-Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
-None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.
 
@@
 Generating databases with both the images and the ground truth scene information is not trivial.
-One approach has been to acquire mages where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations (\cite{NascimentoFoster2016}).
+One approach has been to acquire mages where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations \cite{NascimentoFoster2016}.
 This is somewhat painstaking, however, and in any case provides information about the illumination only at a small number of selected locations, so that generalizing across the image requires strong assumptions.
@@
 These data sets have been useful for evaluating computational color constancy algorithms, but the use of posed scenes does not scale well for use with supervised learning methods which needs large training sets.
-
-Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as {\em virtual natural scenes}.
-Here, in addition to employing computer graphics to render the light reaching the eye from specified scenes, we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
-We describe this approach in detail below, but the key advantage is that we can produce large numbers of naturalistic images and the corresponding cone mosaic responses, where all of the underlying scene properties are well-specified.
-This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
-This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception (REFS: Many -- go to Boynton lecture slides for some).
-Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.
-
-In this initial work, we do not tackle the full problem of color constancy.
-Rather, as a point of departure, we consider the computational problem of estimating a single attribute of object surface reflectance, which we refer to as surface luminance.
-We compute object luminance from an object's surface reflectance function as follows.
-We compute the light that would be reflected to the eye from a flat matte object with that surface reflectance, when the object is diffusely illuminated by the standard CIE daylight spectrum D65 (\cite{CIE86}).
-We then compute the luminance of this reflected light, using the CIE 1931 photopic luminosity function (\cite{CIE86}), and divide this by the luminance of a perfectly reflecting diffuser (surface reflectance of one at all wavelengths) when that is computed in the same way.
-This procedure allows us to assign to any surface reflectance a single surface luminance value.
-Because the perceived lightness of an object is approximately (but by no means exactly, see \cite{wyszecki1986color}) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of {\em lightness constancy}.
-This is a generalization of the way this term is often used, where it refers more specifically to the stability of perceived lightness across images of scenes where all objects and illuminants are achromatic \cite{gilchrist2006seeing}.
-Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (see  Fig.~\ref{fig:introExampleFigure}).
-A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimated.
-
-Even within the special case of lightness constancy, there are many scene manipulations that could be considered.
-The set of manipulations we focus on here are illustrated by the three panels of (Fig.~\ref{fig:studiedCases}).
-These cases are: 1.
-variation in target object spectrum (Fig.\ref{fig:targetVarying}) with fixed light source and background objects spectra, 2.
-variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.\ref{fig:targetIlluminantVarying}), and 3.
-variations in all three types of spectra (target object, light source, and background objects) (Fig.\ref{fig:allSpectraVarying}).
-Across real scenes, there will also be variations in the shape of the target object, its pose, eye position, etc.
-(see \nameref{Methods}).
-In this paper, we focus on the problem of lightness constancy within scene ensembles where these geometric factors are held fixed.
-
-The rest of this paper is organized as follows.
-In the \nameref{Methods} section, we first describe the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}).
-Next, we describe the steps to simulate the response of the retinal cones to these images (\nameref{method:Isetbio}).
-Finally, we describe the supervised learning methods used in our analysis (\nameref{method:SupervisedLearning}).
-In the \nameref{Results} section, we show the estimates and performance of the supervised methods for the three cases mentioned above.
-
-We show that for cases that have spectral variation only in target reflectance or background reflectance or the illuminant the lightness can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
-For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
-Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
-Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
-
-Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
-Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
-We discuss the implications of such receptive fields on lightness constancy.
 
@@
 
+Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as {\em virtual natural scenes}.
+Here, in addition to employing computer graphics to render the light reaching the eye from specified scenes, we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
+We describe this approach in detail below, but the key advantage is that we can produce large numbers of naturalistic images and the corresponding cone mosaic responses, where all of the underlying scene properties are well-specified.
+This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
+This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception (REFS: Many -- go to Boynton lecture slides for some).
+Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.
+
+In this initial work, we do not tackle the full problem of color constancy.
+Rather, as a point of departure, we consider the computational problem of estimating a single attribute of object surface reflectance, which we refer to as surface luminance.
+We compute object luminance from an object's surface reflectance function as follows.
+We compute the light that would be reflected to the eye from a flat matte object with that surface reflectance, when the object is diffusely illuminated by the standard CIE daylight spectrum D65 \cite{CIE86}.
+We then compute the luminance of this reflected light, using the CIE 1931 photopic luminosity function \cite{CIE86}, and divide this by the luminance of a perfectly reflecting diffuser (surface reflectance of one at all wavelengths) when that is computed in the same way.
+This procedure allows us to assign to any surface reflectance a single surface luminance value.
+Because the perceived lightness of an object is approximately (but by no means exactly, see \citeNP{wyszecki1986color}) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of {\em lightness constancy}.
+This is a generalization of the way this term is often used, where it refers more specifically to the stability of perceived lightness across images of scenes where all objects and illuminants are achromatic \cite{gilchrist2006seeing}.
+Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (see  Fig.~\ref{fig:introExampleFigure}).
+A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimated.
+
+Even within the special case of lightness constancy, there are many scene manipulations that could be considered.
+The set of manipulations we focus on here are illustrated by the three panels of Fig.~\ref{fig:studiedCases}.
+These cases are: 1.
+variation in target object spectrum with fixed light source and background objects spectra (Fig.~\ref{fig:targetVarying}), 2.
+variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.~\ref{fig:targetIlluminantVarying}), and 3.
+variations in all three types of spectra (target object, light source, and background objects) (Fig.~\ref{fig:allSpectraVarying}).
+Across real scenes, there will also be variations in the shape of the target object, its pose, eye position, etc.
+(see \nameref{Methods}).
+In this paper, we focus on the problem of lightness constancy within scene ensembles where these geometric factors are held fixed.
+
+We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, lightness can be estimated by simple transformations of the cone responses.
+For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
+For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
+Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
+Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
+Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
+Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
+Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
+We discuss the implications of such receptive fields on lightness constancy.
+
+The rest of this paper is organized as follows.
+In the \nameref{Methods} section, we describe in detail the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}) using our software pipeline {\rm Virtual world color constancy}, the process to simulate the response of retinal cone photoreceptors to these images using a standard model of the early visual system (\nameref{method:Isetbio}) and the supervised learning methods used in our analysis (\nameref{method:SupervisedLearning}).
+In the \nameref{Results} section, we show the estimates and performance of the supervised methods for the three cases mentioned above.
+We conclude the paper with the implication of our results in the \nameref{Discussion} section.
+
 \section*{Methods} \label{Methods}
 \subsection{Overview}
-
 There are four key parts to our methods.
@@
 \subsubsection{Virtual naturalistic scenes}
-
 The light that reflects off an object and reaches our eyes depends on many factors.
@@
 
-% Figure 9
+% Figure 3
 \begin{figure}[t]
@@
 \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_a.png}
         \caption{Library }
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_b.png}
         \caption{Mill}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_c.png}
         \caption{Table-Chairs}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_d.png}
         \caption{Indoor-plant}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_e.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_e.png}
         \caption{Warehouse}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_f.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_f.png}
         \caption{Checkerboard}
@@
     \end{subfigure}
-    \caption{{Example of base scenes form the VWCC library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.
+    \caption{{\bf Example of base scenes form the VWCC library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.
 The reflectance spectra of the distinct surfaces in each scene has been assigned randomly (see below) using the VWCC software.
-The light source spectra were also assigned randomly to the default light source for each scene.
-[CHECK THAT THIS IS CORRET] }\label{fig:baseScenes}
+The light source spectra were also assigned randomly to the default and inserted light source.}\label{fig:baseScenes}
 \end{figure}
@@
 The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.
+The position (Fig.~\ref{fig:targetPositionVariation}), size and orientation (Fig.~\ref{fig:targetSizeOrientation})of the inserted objects and lights may be specified programatically or chosen randomly under constraints provided by the base scene meta-data.
+Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.
 
-% Figure 10
+% Figure 4
 \begin{figure}[h]
 \centering
-\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.png}
+\begin{subfigure}[b]{0.14 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_a.png}
         \caption{Big-ball}
@@
       %(or a blank line to force the subfigure onto a new line)
-\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.png}
+\begin{subfigure}[b]{0.14 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_b.png}
         \caption{Small-ball}
@@
       %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.png}
+    \begin{subfigure}[b]{0.14 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_c.png}
         \caption{Barrel}
@@
     \end{subfigure}
-
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.png}
+    \begin{subfigure}[b]{0.14 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_d.png}
         \caption{Xylophone}
@@
     ~
-	\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_e.png}
+	\begin{subfigure}[b]{0.14 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_e.png}
         \caption{Ring toy}
@@
         ~
-    	\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_f.png}
-        \caption{Champagne Bottle}
+    	\begin{subfigure}[b]{0.14 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_f.png}
+        \caption{Bottle}
         \label{fig:libraryWithChampagneBottle}
     \end{subfigure}
-\caption{{Library base scene with inserted objects.} The VWCC software was used to insert different objects into the library base scene, with each panel showing a different object.
+\caption{{\bf Library base scene with inserted objects.} The VWCC software was used to insert different objects into the library base scene, with each panel showing a different object.
 The objects were inserted at a location in the image and then the camera was pointed at the object, so that the object's image is at the center of the rendered image.
@@
 
-The size, position and orientation of the inserted objects and lights may be specified programatically (Fig.~\ref{fig:objectTransformations}) or chosen randomly under constraints provided by the base scene meta-data.
-Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.
+% Figure5
+\begin{figure}
+\centering
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_a.png}
+        \caption{Target spectra}
+        \label{fig:targetVariation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_b.png}
+        \caption{Background spectra}
+        \label{fig:backGroundVariation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+    %(or a blank line to force the subfigure onto a new line)
+    \begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_c.png}
+        \caption{Illumination spectra}
+        \label{fig:illuminationVariation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_d.png}
+        \caption{Target position}
+        \label{fig:targetPositionVariation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_e.png}
+        \caption{Target Size/Orientation}
+        \label{fig:targetSizeOrientation}
+    \end{subfigure}
+    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
+      %(or a blank line to force the subfigure onto a new line)
+    \caption{{\bf Transformations of the scene.} The possible transformations of the properties of a scene can broadly be classified into two groups: Spectral (a-c) and Geometrical (d-e).
+VWCC provides control over such transformation as illustrated by the columns.
+(a) The target object surface reflectance varies across the three panels of the column.
+(b) The surface reflectance of the background objects varies across the three panels.
+In each panel, the reflectances were assigned randomly.
+(c) The power spectrum of the light sources were assigned randomly in the three panels.
+(d) The three panels in the column have the target object at three different positions.
+The camera points to the center of the pixel.
+}\label{fig:VWCCTransformations}
+\end{figure}
 
@@
 
-% Figure11
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.png}
-        \caption{Target spectra}
-        \label{fig:targetVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.png}
-        \caption{Background spectra}
-        \label{fig:backGroundVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.png}
-        \caption{Illumination spectra}
-        \label{fig:illuminationVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_d.png}
-        \caption{Target position}
-        \label{fig:targetPositionVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_e.png}
-        \caption{Target Size/Orientation}
-        \label{fig:targetSizeOrientation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \caption{{\bf Transformations of the scene.} Each column illustrates transformations of a scene that are under software control.
-(a-c) Spectral Transformations.
-(d-e) Geometrical transformations.
-EXPAND OUT AND SAY WHAT EACH COLUMN IS, INDIVIDUALLY}\label{fig:spectralTransformations}
-\end{figure}
-
 In the present work, we insert one target object and one additional light source into a fixed base scene, and vary reflectance and illuminant spectra.
 We then insert a camera for rendering at a user specified position and point this camera at the target object.
-We ensure that a N by N pixel [CHECK ACTUAL SIZE] region at the center of the image corresponds to light reflected from the target object, which amounts to verifying that the target object at its inserted position was not occluded by other objects in the line of sight from camera.
+We ensure that a 9 pixel by 9 pixel region at the center of the image corresponds to light reflected from the target object, which amounts to verifying that the target object at its inserted position was not occluded by other objects in the line of sight from camera.
 For each rendered scene, we specify the surface reflectance of the target object, which allows us to control both its surface luminance as well as its relative surface reflectance.
@@
 
-% Figure 12
+% Figure 6
 \begin{figure}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_a.pdf}
         \caption{Granada natural daylight dataset}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_b.pdf}
         \caption{Rescaled Granada dataset}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
         \caption{Randomly generated samples}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_d.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
         \caption{xy chromaticity diagram}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_e.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_e.pdf}
         \caption{Normalized PCA eigenvalues}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_f.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_f.pdf}
         \caption{sRGB rendition of samples from Fig.\ref{fig:randomIlluminant}}
@@
 
-% Figure 13
+% Figure 7
 \subsubsection{Reflectance Spectrum}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_a.pdf}
         \caption{Natural surface reflectance spectra}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
         \caption{Randomly generated samples}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
         \caption{sRGB rendition of samples from \ref{fig:randomSurface}}
@@
 
-% Figure 14
+% Figure 8
 \begin{figure}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
         \caption{Natural surface reflectance spectra}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
         \caption{Randomly generated target samples}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
         \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
@@
 
-% Figure 3: Methods
+% Figure 9: Methods
 \begin{figure}
@@
 		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_a.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
         \caption{A typical 3D Scene}
@@
     \hspace{0.1 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_b.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.png}
         \caption{Cropped Image}
@@
     \hspace{0.1 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_c.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.png}
         \caption{Optical Image}
@@
     \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_d.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
         \caption{LMS cone contrast}
@@
 
-% Figure 4
+%% Figure 10
 \begin{figure}
@@
 		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_a.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.pdf}
         \caption{SVD First 2 RFs}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_d.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.pdf}
         \caption{Lightness Estimates}
@@
 
-% Figure 5
+%% Figure 11
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
+\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the lightness.}
+\label{fig:RMSEvsNFilters}
+\end{figure}
+
+% Figure 12
 \begin{figure}
@@
 		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_a.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
         \caption{SVD First 2 RFs}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_d.pdf}
         \caption{Luminance Estimates}
@@
 
-% Figure 6
+% Figure 13
 \begin{figure}
@@
 		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_a.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
         \caption{SVD First 2 RFs}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_d.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
         \caption{Luminance Estimates}
@@
 
-% Figure 7
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{../Figures/Figure5/Figure5.pdf}
-\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the lightness.}
-\label{fig:RMSEvsNFilters}
-\end{figure}
-
 Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(d) shows the lightness estimates and the RMSE for the three methods (Linear regression on center pixel, AMA and SVD).
@@
 \subsection{The RFs of complex case generalize on simpler cases}
-% Figure 8stimulusIntensities(1)-1
+% Figure 8
 \begin{figure}
@@
 \begin{subfigure}{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
 	\caption{Performance of methods}
@@
     \begin{subfigure}{0.3 \textwidth}   
-	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
 	\caption{SVD RF Performance}
@@
         \begin{subfigure}{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
 	\caption{AMA RF Performance}

### 2017-12-20 Draft1/draft1.tex
Today’s writing

@@
 
-[GOT TO HERE]
 \subsubsection{Illumination Spectra}
-The illumination spectrum is generated through a random statistical sampling of a natural illumination spectrum dataset.
+We generate illumination spectra  through random statistical sampling of a dataset of naturally occurring illuminants, the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{peyvandi2016colorimetric}.
 First, we approximate the spectra in the dataset using principle component analysis (PCA).
-We decompose the spectra as a linear sum over the PCA basis vectors corresponding to the largest 6 PCA eigenvalues.
-Next, we sample random spectra from this low 6 dimensional PCA space assuming the spectral distribution to be a multivariate gaussian.
+We then decompose the spectra in terms of the PCA basis vectors corresponding to the 6 largest PCA eigenvalues.
+Next, we sample random spectra from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a multivariate gaussian whose mean and covariance matrix match the sample mean and covariance obtained from the daylight dataset.
+This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman (1997).
+Details of the process we used are provided below.
+% ADD BRAINARD/FREEMAN BAYESIAN COLOR CONSTANCY REF
 
@@
     \end{subfigure}
-    \caption{{\bf Generating random illumination spectrum:} The illumination spectra are generated by random sampling of Granada daylight spectra assuming a multivariate gaussian distribution.
-The mean and variance of the gaussian are chosen by projecting the dataset along PCA directions and taking the mean and covariance of the projections.
-(a) Granada natural daylight dataset.
-(b) Rescaled Granada dataset.
-Each spectra is rescaled by its mean illumination over frequency.
-(c) Randomly generated samples.
-(d) xy chromaticity diagram of the rescaled dataset (Fig.
-\ref{fig:rescaledGranada}) and the randomly generated samples (Fig.\ref{fig:randomIlluminant}).
+    \caption{{\bf Generating random illumination spectra:} The illumination spectra are generated by random sampling based on the Granada daylight measurements, assuming a multivariate Gaussian distribution of weights in a 6-dimensional PCA representation.
+The mean and covariance matrix of the Gaussian are chosen by projecting the dataset along the first six PCA directions and taking the mean and covariance matrix of the resulting basis vector weights.
+(a) The XXX spectra from the Granada natural daylight dataset.
+(b) Rescaled version of the Granada dataset.
+Each spectrum is rescaled so that it has a mean value (over wavelength) of one illumination.
+(c) Randomly generated spectra.
+(d) CIE xy chromaticity plot of the rescaled dataset (Fig.~\ref{fig:rescaledGranada}) and randomly generated spectra (Fig.~\ref{fig:randomIlluminant}).
 (e) Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
 The eigenvalues have been normalized by the sum over all eigenvalues.
-The dotted line (= 0.9) is for reference.
-We choose the first six eigenvectors in ur analysis.
-(f) The sRGB renditions of the random samples generated in \ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
+The dotted line at 0.9 on the y-axis is for reference.
+We used the first six eigenvectors in our analysis.
+(f) sRGB renditions of the random illuminant samples shown in \ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
 \end{figure}
+% CHECK SCALING THAT WENT INTO A, AND DESCRIBE IN CAPTION.  ADD IN NUMBER OF SPECTRA SHOWN IN PANELS a and b (XXX ABOVE).  TRY LOG SCALE FOR A.
 
-We have used the Granada natural daylight spectrum \href{http://colorimaginglab.ugr.es/pages/Data}{dataset} \cite{peyvandi2016colorimetric} to sample illuminants.
 Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset.
-Since the distribution varies over multiple order of magnitudes, we rescale each spectrum by dividing by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$.
-These rescaled spectra $(I_i^s(\lambda))$ are then mean centered for PCA by subtracting out the mean
-rescaled spectra, $\bar{I}^{s}(\lambda)$. The mean is obtained
-by taking the sample mean over all spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
-The resulting mean subtracted dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$, 
-is decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
-where $\hat{{\bf e}}_j^{PCA}$s are PCA basis vectors obtained using 
-singular value decomposition (SVD). $w_{ij}$'s are the projections 
-of $I_i^{MC}(\lambda)$ along the PCA basis vectors $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. We approximate 
-this decomposition by summing over the basis vectors corresponding to
-the largest six SVD eigenvalues. For the Granada dataset, these six 
-eigenvalues constitute more than $98\%$ of the variance. These steps
+Since the measured spectra vary over several orders of magnitude in overall intensity, we rescale each spectrum by dividing it by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$.
+For simplicity of notation, we denote wavelength $\lambda$ as a continuous variable; in the actual calculations wavelength is discretely sampled and integrals are approximated by sums.
+The Granada dataset was measured at X nm sampling intervals between YY and ZZ nm.
+We performed our calculations at this sampling, and then subsampled to the 400-700 nm interval, 10 nm spacing representation used for rendering.
+% CHECK DETAILS AND MAKE THIS TRUE.
+The rescaled spectra $I_i^s(\lambda)$ were then mean centered for PCA by subtracting out the mean 
+rescaled spectrum, $\bar{I}^{s}(\lambda)$. That mean was obtained
+by taking the sample mean over all rescaled spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
+The resulting mean subtracted dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$
+was decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
+where the $\hat{{\bf e}}_j^{PCA}$ are the PCA basis vectors obtained using the
+singular value decomposition (SVD) applied to the $I_i^{MC}(\lambda)$ and
+the $w_{ij}$ are the weights obtained by projecting each of $I_i^{MC}(\lambda)$ onto the  $\hat{{\bf e}}_j^{PCA}$ $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$.
+We used the basis vectors corresponding to
+the largest six SVD eigenvalues, so that $\{j \in [16]\}$.
+For the rescaled Granada dataset, these six  eigenvalues account for more than $98\%$ of the variance.
+These steps
 can be summarized as follows:
 \begin{align}
-I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}
+I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) \approx \sum_{j = 1}^6 w_{ij}\hat{{\bf e}}_j^{PCA}.
 \end{align}
 
-To generate new illuminants $\tilde{I}_i(\lambda)$, random 
-projection weights ($\tilde{w}_{ij}$) are generated using a multivariate 
-gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
+To generate random illuminant spectra $\tilde{I}_i(\lambda)$, we generate weights $\tilde{w}_{ij}$ drawn from random 
+the multivariate 
+Gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
 and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
-If the $\tilde{w}_{ij}$ are such that, $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, for all $\lambda$, then the new illuminant spectrum is given as
+From these weights, the corresponding spectrum $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right)$ is generated.
+This spectrum can sometimes have values that are less than zero.  In such cases, the weights are discarded and a new draw obtained, until
+the condition $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, for all $\lambda$, is satisifed.
+The random illuminant spectrum is then given as
 \begin{align}
@@
 \end{align}
-Finally $\tilde{I}(\lambda)$ is rescaled by a random number generated uniformly in the range [0, 100].
+Finally, to model the fact that illumination spectra can vary in overall intensity, we draw a random number uniformly from the range [$I_{min}$ and $I_{max}$] and scale $\tilde{I}(\lambda)$ by this number.
+In most of our calculations, we set $I_{min} = 0$ and $I_{max} = 100$.
 
 % Figure 7
-\subsubsection{Reflectance Spectrum}
+\subsubsection{Reflectance Spectra}
 \begin{figure}
@@
 
-The reflectance spectrum are generated similar to illumination spectrum. 
+We generated random reflecta spctra using the same principles we applied to generate random illuminant spectra.
 We have used the Munsell {(\it citation)} and vrhel {(\it citation)} surface reflectance 

### 2017-12-20 Draft1/draft1.tex
moer edits

@@
 Next, we sample random spectra from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a multivariate gaussian whose mean and covariance matrix match the sample mean and covariance obtained from the daylight dataset.
-This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman (1997).
+This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman \cite{BrainardFreeman}.
 Details of the process we used are provided below.
-% ADD BRAINARD/FREEMAN BAYESIAN COLOR CONSTANCY REF
 
@@
 The mean and covariance matrix of the Gaussian are chosen by projecting the dataset along the first six PCA directions and taking the mean and covariance matrix of the resulting basis vector weights.
-(a) The XXX spectra from the Granada natural daylight dataset.
+(a) The 2600 spectra from the Granada natural daylight dataset.
 (b) Rescaled version of the Granada dataset.
 Each spectrum is rescaled so that it has a mean value (over wavelength) of one illumination.
-(c) Randomly generated spectra.
-(d) CIE xy chromaticity plot of the rescaled dataset (Fig.~\ref{fig:rescaledGranada}) and randomly generated spectra (Fig.~\ref{fig:randomIlluminant}).
+(c) Randomly samples generated using the rescaled spectra from Fig.~\ref{fig:rescaledGranada}.
+(d) CIE xy chromaticity plot of the rescaled dataset (Fig.~\ref{fig:rescaledGranada}) and randomly generated samples from Fig.~\ref{fig:randomIlluminant}.
 (e) Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
@@
 \end{figure}
+
 % CHECK SCALING THAT WENT INTO A, AND DESCRIBE IN CAPTION.  ADD IN NUMBER OF SPECTRA SHOWN IN PANELS a and b (XXX ABOVE).  TRY LOG SCALE FOR A.
@@
 For simplicity of notation, we denote wavelength $\lambda$ as a continuous variable; in the actual calculations wavelength is discretely sampled and integrals are approximated by sums.
-The Granada dataset was measured at X nm sampling intervals between YY and ZZ nm.
-We performed our calculations at this sampling, and then subsampled to the 400-700 nm interval, 10 nm spacing representation used for rendering.
-% CHECK DETAILS AND MAKE THIS TRUE.
+The Granada dataset was measured at 5 nm sampling intervals between 300 and 1100 nm.
+We subsampled the spectra to the 400-700 nm interval, 10 nm spacing representation used for rendering, and performed our calculations at this sampling.
+
 The rescaled spectra $I_i^s(\lambda)$ were then mean centered for PCA by subtracting out the mean 
@@
 the largest six SVD eigenvalues, so that $\{j \in [16]\}$.
-For the rescaled Granada dataset, these six  eigenvalues account for more than $98\%$ of the variance.
+For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance.
 These steps
@@
 \end{align}
-Finally, to model the fact that illumination spectra can vary in overall intensity, we draw a random number uniformly from the range [$I_{min}$ and $I_{max}$] and scale $\tilde{I}(\lambda)$ by this number.
-In most of our calculations, we set $I_{min} = 0$ and $I_{max} = 100$.
+To get a scaling similar to the original Granada spectrum set, we multiply the randomly sampled spectrum with a random number generated uniformly from the interval [0, $\bar{I}_{\rm max}$], where $\bar{I}_{\rm max}$ is the maximum of the 2600 mean values   obtained from the Granada spectra.
+Finally, to model the fact that illumination spectra can vary in overall intensity, we draw a random number distributed logarithmically in the range [$I_{min}$ and $I_{max}$] and scale the generated spectrum by this number.
+In most of our calculations, we set $I_{min} = 1$ and $I_{max} = 300$.
+
+\subsubsection{Reflectance Spectra}
 
 % Figure 7
-\subsubsection{Reflectance Spectra}
 \begin{figure}
@@
     \end{subfigure}
-    \caption{{\bf Generating random surface reflectance spectrum:} The surface reflectance spectra are generated by random sampling of natural surface reflectance spectra assuming a multivariate gaussian distribution.
-The mean and variance of the gaussian are chosen by projecting the natural dataset along PCA directions and taking the mean and covariance of the projections.
-(a) Natural surface reflectance spectra.
-(b) Randomly generated samples.
+    \caption{{\bf Generating random surface reflectance spectra:} The surface reflectance spectra are generated by random sampling of natural surface reflectance spectra, similar to the principles used to generate random illuminant spectra.
+(a) The 632 surface reflectance spectra from the Munsell and Vrhel dataset.
+(b) Randomly generated samples of reflectance spectra.
 (c) The sRGB renditions of the random samples generated in \ref{fig:randomSurface}.}\label{fig:surfaceReflectanceGeneration}
@@
 
-We generated random reflecta spctra using the same principles we applied to generate random illuminant spectra.
-We have used the Munsell {(\it citation)} and vrhel {(\it citation)} surface reflectance 
-datasets for sampling the reflectance. Let us denote the dataset of natural 
-reflectance spectra as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
-and $M$ is the total number of spectra in the dataset. To generate 
-a random reflectance spectrum $\tilde{R}(\lambda)$, 
-we first mean center the dataset by subtracting out the 
-mean surface reflectance spectrum, $\bar{R}(\lambda)$,
-from each surface reflectance spectrum.
-$\bar{R}(\lambda)$ is obtained by taking the sample 
-mean over all spectra in the dataset, i.e.,
-$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. 
-Thus we have the mean centered reflectance 
-spectrum dataset as $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
-We decompose this as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$. Here,
-${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD 
-and $w_{ij}$s are the projections of $R_i^{\rm MC}(\lambda)$ along the PCA eigenvectors 
-$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. The 
-decomposition is approximated by summing over the PCA basis 
-vectors corresponding to the largest six SVD eigenvalues. These six eigenvalues capture 
-more than $92\%$ of the variance in the combined Munsell and vhrel datasets. To generate 
-a new reflectance spectrum, a point is sampled randomly in this 
-six dimensional sub-space using a multivariate normal 
-distribution, with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. If the randomly sampled projection, $\tilde{w}_{ij}$, is 
-such that $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, the new surface reflectance 
-is given as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.
+We generated random reflectance spectra using the same principles we applied to generate random illuminant spectra.
+We used the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
+datasets for sampling the reflectance. 
+Let us denote the reflectance dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
+and $M$ is the total number of spectra in the dataset. 
+We calculated the mean reflectance spectrum,
+$\bar{R}(\lambda)$, by taking the sample mean over all spectra in the dataset, i.e.,
+$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. Then, we mean centered 
+the reflectance dataset by subtracting the mean spectrum, $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
+We decomposed this mean centered dataset as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$, where
+${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
+and $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
+$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. 
+We used the basis vectors corresponding to the largest six SVD eigenvalues. 
+For the combined Munsell and Vrhel datasets, these six eigenvalues account for 
+more than $90\%$ of the variance. 
+To generate random reflectance spectra, we generate samples of weights ($\tilde{w}_{ij}$) drawn from the multivariate Gaussian 
+distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
+and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
+If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, we use them to give the random reflectance spectrum as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.
 
@@
 
-For generating the target object reflectance at a particular lightness $(Y_{\rm T})$, the values in the spectrum are 
+For generating the target object reflectance at a particular luminance $(Y_{\rm T})$, the values in the spectrum are 
 rescaled by a scalar such that the perceived lightness of the 

### 2017-12-21 Draft1/draft1.tex
December 21 (Winter Solstice) editing

@@
 We generate illumination spectra  through random statistical sampling of a dataset of naturally occurring illuminants, the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{peyvandi2016colorimetric}.
-First, we approximate the spectra in the dataset using principle component analysis (PCA).
+These spectra are shown on a log intensity scale in Fig.~\ref{fig:granadaSpectra}, which illustrates that the overall intensity of natural daylights varies over several orders of magnitude, and in normalized format in Fig.~\ref{fig:rescaledGranada}, which illustrates that the relative spectra also vary considerably.
+In our procedure, we first approximate the spectra in the dataset using principle component analysis (PCA).
 We then decompose the spectra in terms of the PCA basis vectors corresponding to the 6 largest PCA eigenvalues.
-Next, we sample random spectra from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a multivariate gaussian whose mean and covariance matrix match the sample mean and covariance obtained from the daylight dataset.
+Next, we sample from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a multivariate gaussian whose mean and covariance matrix match the sample mean and covariance obtained from the daylight dataset.
+Finallly, we use the sampled weights to reconstruct sampled spectra.
 This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman \cite{BrainardFreeman}.
-Details of the process we used are provided below.
+Details of the procedure we used are provided below.
 
@@
 The mean and covariance matrix of the Gaussian are chosen by projecting the dataset along the first six PCA directions and taking the mean and covariance matrix of the resulting basis vector weights.
-(a) The 2600 spectra from the Granada natural daylight dataset.
+(a) The 2600 spectra from the Granada natural daylight dataset, plotted on a log intensity scale in arbitrary units.
 (b) Rescaled version of the Granada dataset.
@@
 the largest six SVD eigenvalues, so that $\{j \in [16]\}$.
-For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance.
+For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance (Fig.~\ref{fig:granadaEV}).
 These steps
@@
 \end{align}
+Fig.~\ref{fig:randomIlluminant} shows a set of 100 spectra sampled in this manner, and may be compared with Fig.~\ref{fig:rescaledGranada}.
+Fig.~\ref{fig:xyDiagram} shows the CIE xy chromaticities of these samples and compares these with the chromaticities in the Granada dataset.
+Finally, Fig.~\ref{fig:sRGBIlluminant} provides an sRGB rendering of each spectrum in Fig.~\ref{fig:rescaledGranada}, to provide a visual sense of the chromatic variation in the sampled spectra.
+
+Because our multivariate Gaussian model is based on the rescaled spectra, it does not embody the large variation in overall intensity of natural daylights.
 To get a scaling similar to the original Granada spectrum set, we multiply the randomly sampled spectrum with a random number generated uniformly from the interval [0, $\bar{I}_{\rm max}$], where $\bar{I}_{\rm max}$ is the maximum of the 2600 mean values obtained from the Granada spectra.
@@
 In most of our calculations, we set $I_{min} = 1$ and $I_{max} = 300$.
+% WE NEED TO RETHINK THIS SCALING.  CERTAINLY SHOULD JUST BE ONE STEP.  ONE APPROACH WOULD BE TO DRAW UNIFORMLY FROM THE DISTRIBUTION OF SCALE FACTORS OBTAINED FROM THE 2600 
+% GRANADA MEASUREMENTS.
 
-\subsubsection{Reflectance Spectra}
+\subsubsection{Surface Reflectance Spectra}
 
@@
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
-        \caption{Randomly generated samples}
+        \caption{Randomly generated spectra}
         \label{fig:randomSurface}
@@
     \end{subfigure}
-    \caption{{\bf Generating random surface reflectance spectra:} The surface reflectance spectra are generated by random sampling of natural surface reflectance spectra, similar to the principles used to generate random illuminant spectra.
-(a) The 632 surface reflectance spectra from the Munsell and Vrhel dataset.
+    \caption{{\bf Generating random surface reflectance spectra:} Surface reflectance spectra are generated by random sampling based on measured surface reflectance spectra, using principles similar to those used to generate random illuminant spectra.
+(a) The 632 surface reflectance spectra from the Munsell and Vrhel datasets.
 (b) Randomly generated samples of reflectance spectra.
-(c) The sRGB renditions of the random samples generated in \ref{fig:randomSurface}.}\label{fig:surfaceReflectanceGeneration}
+(c) sRGB renderings (under CIE D65) of the random samples generated in \ref{fig:randomSurface}.}\label{fig:surfaceReflectanceGeneration}
 \end{figure}
@@
 We generated random reflectance spectra using the same principles we applied to generate random illuminant spectra.
-We used the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
-datasets for sampling the reflectance. 
+We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
+measurements to create a reflectance database containing 632 reflectances. 
+% SAY SOMETHING ABOUT SPECTRAL SAMPLING
 Let us denote the reflectance dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
@@
 We decomposed this mean centered dataset as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$, where
-${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
-and $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
+the ${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
+and the $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the basis vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
 $\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. 
@@
 If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, we use them to give the random reflectance spectrum as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.
+Otherwise the draw is discarded and a new set of weights is drawn.
 
@@
 
-For generating the target object reflectance at a particular luminance $(Y_{\rm T})$, the values in the spectrum are 
-rescaled by a scalar such that the perceived lightness of the 
-target surface under standard daylight illuminant $(D_{65}(\lambda))$ 
-equals a designated value.
-The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE luminosity (or luminous efficiency) function.
+For generating the target object reflectance at a particular luminance $(Y_{\rm T})$, the values in a generated spectrum were 
+rescaled such that the surface luminance (as defined above) had the desired value.
+The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE photopic luminosity (or luminous efficiency) function. 
 $\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
 perception of brightness.
-The target reflectance is given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
-
-% NEED TO DECIDE PRECISELY WHERE TO USE THIS PROSE AND  FIGURE
-%Figure~\ref{sceneWithCroppedImage} illustrates the steps in this process for one scene.  We start with how we generate a single labeled set of cone responses
-%We call our image generation software Virtual world color constancy (VWCC).
-The details of the software are provided in the supplementary information section.
-To generate an image, we first select a 3D scene, a target object and a light source from the set of predefined scenes and objects in VWCC.
-The target object and the light source are inserted in the 3D scene.
-Fig.\ref{fig:3DScene} shows a 2D sRGB rendition of the 3D scene used in our analysis.
-The green sphere in the middle is the target object.
-The light source is not in the camera field of view.
-Next, we assign a surface reflectance spectrum and an illumination spectrum to each object and light source in the scene.
-For the target object the surface reflectance is assigned such that the perceived lightness of the target object under D65 daylight spectrum has a fixed value.
-Now we render a $320\times 240$ pixel$^2$ 2d multispectral images of the scene at 31 frequencies (equal linear spacing between 400 nm - 700 nm) using a graphics rendering system called Mitsuba \cite{jakob2015mitsuba}.
-For each of the three case, we generate hundreds of such scenes and corresponding multispectral images at 10 linearly spaced lightness levels between 0.2 and 0.6 (see below).
-We crop a 51x51 pixel$^2$ part of the multispectral image containing the target object for further analysis (\ref{fig:croppedImage}).
-Fig.
-\ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this work.
+The target reflectance is then given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
 
@@
         \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
-        \caption{A typical 3D Scene}
+        \caption{Rendered image of a randomly drawn scene}
         \label{fig:3DScene}
@@
     \label{fig:sceneWithCroppedImage}
-    \caption{{\bf Generating labeled dataset for computational analysis:}  For the supervised approach employed in this work, the labeled database is generated as follows: (a) A 3D virtual scene, a target object and a light source is selected from the VWCC library.
-The target object is placed in the camera field of view and assigned a reflectance spectrum with a specific lightness.
-After assigning spectra to other objects and lights sources in the scene, a multispectral image of the scene is rendered using Mitsuba graphics rendering software.
-(b) A part of the image, containing the target object, is cropped from the image.
-(c) The response of the retinal cones to the cropped image is simulated using a model of the visual system.
-Fig.\ref{fig:croppedImageWithMosaic} shows the optical image incident on the cone mosaic and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
-See text for the details of the model.
-(d) The cone response are interpolated to get the response of all the three types at each location (demosaicing).
-Finally, the demosaic response is contrast normalized (see text).}
+    \caption{{\bf Generating labeled dataset for computational analysis:}  For the supervised approach employed in this work, the labeled database is generated as follows: (a) A 3D virtual scene, containing a target object of known surface luminance is created.
+The target object is placed in the camera field of view.
+After assigning spectra to the light sources and other other objects in the scene, a multispectral image of the scene is rendered using the Mitsuba software package.
+(b) The central portion of the rendered image, which contains the target object, is cropped from the image.
+(c) The response of retinal cones to the cropped image is simulated using the isetbio software package to model early vision.
+The software models optical blurring and foveal spatial sampling by the trichromatic cone mosaic.
+Fig.\ref{fig:croppedImageWithMosaic} shows the retinal image incident on the cone mosaic and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
+(d) The cone responses are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
+Finally, the demosaiced images are contrast normalized separately for each cone type.}
 \end{figure}
 
-\subsection{Model of Visual System} \label{method:Isetbio}
+\subsection{Model of Early Visual System} \label{method:Isetbio}
 
-Finally, these multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
+The sampling and rendering steps described above allow us to generate images from scenes that contain an image of a target object of known surface luminance at the center pixel, and where the illuminant spectra and spectra of the other surfaces in the scene are drawn randomly from models of naturally occurring spectra.
+One such image is shown in Fig.~\ref{fig:3DScene}, where the green sphere in the middle is the target object and the light sources are not within the camera field of view.
+We model the encoding of such images by the early visual system, to generate {\em neural images} that provide an abstracted representation of the information available to the brain for producing perceptual representations of the external world.
+It is this information for each image, together with the known surface luminance of the corresponding target object, that we will provide to our supervised learning algorithms.
+Our training datasets correspond to % SAY WHAT WE DID ONCE WE FINISH EVERYTHING OFF.
 
+In this work, we are interested in how well lightness constancy may be achieved using reasonably information that is local to the image region containing the target patch.
+% MAYBE SAY A LITTLE MORE ABOUT WHY - THIS IS A PRINCIPLED STANCE TAKEN IN MOST OF JOHANNES WORK.  OR MAYBE DEFER THAT TO THE DISCUSSION.
+To this end, we crop a 51x51 pixel portion of the full rendreed multispectral image that contains the target object and use this for further analysis (\ref{fig:croppedImage}).
+Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this paper.
+
+Next, the cropped multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
+The key steps we model are optical blurring, including axial chromatic aberration, in the formation of the retinal image, spatial sampling by an interleaved mosaic of L, M and S cones, and the Poisson nature of photopigment isomerization.
+% NEED TO WRITE IN THE KEY PARAMETERS USED.
+PROBABLY MARIMONT AND WANDELL OPTICS, STOCKMAN-SHARPE LMS CONE SPECTRAL SENSITIVITIES, THE L, M, S CONE RATIO IN THE MOSAIC, RECTANGULAR AND REGULAR CONE PACKING, SOME IMPLIED SPATIAL SCALE, AND SOME OVERALL SCALING THAT DRIVES THE MEAN LUMINANCE OF THE RETINAL IMAGES AND THUS THE AMOUNT OF POISSON NOISE.
+
+% WE GOT TO HERE ON DECEMBER 21.
 To generate the retinal response one needs to specify the retinal cone mosaic and the size of the retinal image.

### 2017-12-27 Draft1/draft1.tex
small edits

@@
 The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose,
-and the position of the observer (Fig. \ref{fig:introSchematic}).
+and the position of the observer (Fig.~\ref{fig:introSchematic}).
 Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
@@
 Within each column, this relative surface reflectance is held fixed.
-For illustration, we have kept the light source and the background obejcts fixed across the panels.
+For illustration, we have kept the light source and the background objects fixed across the panels.
 See Fig.~\ref{fig:studiedCases} for images with such variations.
@@
 Generating databases with both the images and the ground truth scene information is not trivial.
-One approach has been to acquire mages where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations \cite{NascimentoFoster2016}.
+One approach has been to acquire images where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations \cite{NascimentoFoster2016}.
 This is somewhat painstaking, however, and in any case provides information about the illumination only at a small number of selected locations, so that generalizing across the image requires strong assumptions.
@@
 Moreover, across the three panels of this figure, spheres in corresponding locations have the same surface reflectance.
-In all three panels, the overall lights source spectra scale factors (see \ref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
-[CHECK THAT THIS WORKS FOR A NICE FIGURE].
+In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
 The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
@@
 This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
-This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception (REFS: Many -- go to Boynton lecture slides for some).
+This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception \cite{boyaci2003effect}(REFS: Many -- go to Boynton lecture slides for some).
 Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.
@@
 
-\subsubsection{Virtual naturalistic scenes}
-The light that reflects off an object and reaches our eyes depends on many factors.
-These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer.
-In natural scenes, these spectral and geometrical factors vary considerably.
-To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors.
-We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene.
-Under natural conditions it is difficult to control and quantify every such parameter in a scene.
-Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.
-
-To overcome this  challenge, we have developed an image rendering software pipeline that allows us to specify a virtual, but naturalistic, statistical model of visual scenes with parametric control over factors in natural scenes.
-The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
-It then renders a multispectral 2D image of each modeled visual scene.
-Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
-In addition, our software simulates the responses of retinal cones to the rendered multispectral images using a realistic model of the early human visual system.
-Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
-Our software, which is written in MATLAB, is freely available through a public respository: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
-It builds on several other open source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
-Below we refer to the software pipeline as VWCC (for Virtual World Color Constancy).
-
-The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}).
-The base scene is a 3D model that defines a rendering space.
-It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position.
-VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses.
-We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly.
-We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene.
-Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).
-The overall spatial scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness.
-If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes.
-As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library.
-Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).
-
 % Figure 3
@@
 
-VWCC provides an option for inserting 3D objects and lights sources into the base scene.
-Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted into the library base scene.
-The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from object descriptions made available on the Internet.
-The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.
-The position (Fig.~\ref{fig:targetPositionVariation}), size and orientation (Fig.~\ref{fig:targetSizeOrientation})of the inserted objects and lights may be specified programatically or chosen randomly under constraints provided by the base scene meta-data.
-Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.
+\subsubsection{Virtual naturalistic scenes}
+The light that reflects off an object and reaches our eyes depends on many factors.
+These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer.
+In natural scenes, these spectral and geometrical factors vary considerably.
+To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors.
+We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene.
+Under natural conditions it is difficult to control and quantify every such parameter in a scene.
+Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.
+
+To overcome this  challenge, we have developed an image rendering software pipeline that allows us to specify a virtual, but naturalistic, statistical model of visual scenes with parametric control over factors in natural scenes.
+The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
+It then renders a multispectral 2D image of each modeled visual scene.
+Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
+In addition, our software simulates the responses of retinal cones to the rendered multispectral images using a realistic model of the early human visual system.
+Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
+Our software, which is written in MATLAB, is freely available through a public respository: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
+It builds on several other open source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
+Below we refer to the software pipeline as VWCC (for Virtual World Color Constancy).
 
 % Figure 4
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 \end{figure}
+
+The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}).
+The base scene is a 3D model that defines a rendering space.
+It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position.
+VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses.
+We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly.
+We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene.
+Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).
+The overall spatial scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness.
+If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes.
+As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library.
+Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).
+
+VWCC provides an option for inserting 3D objects and lights sources into the base scene.
+Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted into the library base scene.
+The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from object descriptions made available on the Internet.
+The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.
+The position (Fig.~\ref{fig:targetPositionVariation}), size and orientation (Fig.~\ref{fig:targetSizeOrientation})of the inserted objects and lights may be specified programatically or chosen randomly under constraints provided by the base scene meta-data.
+Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.
 
@@
 The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:studiedCases}).
-2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel$^2$.
-A $51 \times 51$ pixel$^2$ patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
+2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel.
+A $51 \times 51$ pixel patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
 
 \subsubsection{Illumination Spectra}
-We generate illumination spectra  through random statistical sampling of a dataset of naturally occurring illuminants, the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{peyvandi2016colorimetric}.
-These spectra are shown on a log intensity scale in Fig.~\ref{fig:granadaSpectra}, which illustrates that the overall intensity of natural daylights varies over several orders of magnitude, and in normalized format in Fig.~\ref{fig:rescaledGranada}, which illustrates that the relative spectra also vary considerably.
-In our procedure, we first approximate the spectra in the dataset using principle component analysis (PCA).
-We then decompose the spectra in terms of the PCA basis vectors corresponding to the 6 largest PCA eigenvalues.
-Next, we sample from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a multivariate gaussian whose mean and covariance matrix match the sample mean and covariance obtained from the daylight dataset.
-Finallly, we use the sampled weights to reconstruct sampled spectra.
-This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman \cite{BrainardFreeman}.
-Details of the procedure we used are provided below.
-
 % Figure 6
@@
     \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_e.pdf}
+        \caption{Normalized PCA eigenvalues}
+        \label{fig:granadaEV}
+    \end{subfigure}
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
         \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_e.pdf}
-        \caption{Normalized PCA eigenvalues}
-        \label{fig:granadaEV}
-    \end{subfigure}
-      	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
         \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_f.pdf}
-        \caption{sRGB rendition of samples from Fig.\ref{fig:randomIlluminant}}
+        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomIlluminant}}
         \label{fig:sRGBIlluminant}
@@
 
-% CHECK SCALING THAT WENT INTO A, AND DESCRIBE IN CAPTION.  ADD IN NUMBER OF SPECTRA SHOWN IN PANELS a and b (XXX ABOVE).  TRY LOG SCALE FOR A.
+We generate illumination spectra  through random statistical sampling of a dataset of naturally occurring illuminants, the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{peyvandi2016colorimetric}.
+These spectra are shown on a log intensity scale in Fig.~\ref{fig:granadaSpectra}, which illustrates that the overall intensity of natural daylights varies over several orders of magnitude, and in normalized format in Fig.~\ref{fig:rescaledGranada}, which illustrates that the relative spectra also vary considerably.
+In our procedure, we first approximate the spectra in the dataset using principle component analysis (PCA).
+We then decompose the spectra in terms of the PCA basis vectors corresponding to the 6 largest PCA eigenvalues.
+Next, we sample from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a multivariate gaussian whose mean and covariance matrix match the sample mean and covariance obtained from the daylight dataset.
+Finallly, we use the sampled weights to reconstruct sampled spectra.
+This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman \cite{BrainardFreeman}.
+Details of the procedure we used are provided below.
 
@@
     \end{subfigure}
-    \caption{{\bf Generating random surface reflectance spectra:} Surface reflectance spectra are generated by random sampling based on measured surface reflectance spectra, using principles similar to those used to generate random illuminant spectra.
+
+    \centering
+	\begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
+        \caption{Natural surface reflectance spectra}
+        \label{fig:naturalSurfaceTarget}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
+        \caption{Randomly generated target samples}
+        \label{fig:randomSurfaceTarget}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
+        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
+        \label{fig:sRGBSurfaceTarget}
+    \end{subfigure}
+    \caption{{\bf Target object surface reflectance spectrum:} For getting the target object surface reflectance, we first generate the spectra similar to that of other objects and then rescale them appropriately to get the required perceived lightness.
+(a) Natural surface reflectance spectra.
+(b) Randomly generated samples for target reflectance.
+(c) The sRGB renditions of the random samples generated in Fig.~\ref{fig:randomSurfaceTarget}.
+We show 10 samples at 1 lightness levels.
+\newline
+{\bf Generating random surface reflectance spectra:} Surface reflectance spectra are generated by random sampling based on measured surface reflectance spectra, using principles similar to those used to generate random illuminant spectra.
 (a) The 632 surface reflectance spectra from the Munsell and Vrhel datasets.
@@
 % Figure 8
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
-        \caption{Natural surface reflectance spectra}
-        \label{fig:naturalSurfaceTarget}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
-        \caption{Randomly generated target samples}
-        \label{fig:randomSurfaceTarget}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
-        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
-        \label{fig:sRGBSurfaceTarget}
-    \end{subfigure}
-    \caption{{\bf Target object surface reflectance spectrum:} For getting the target object surface reflectance, we first generate the spectra similar to that of other objects and then rescale them appropriately to get the required perceived lightness.
+%\begin{figure}
+%\centering
+%	\begin{subfigure}[b]{0.3 \textwidth}
+%    \centering
+%        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
+%        \caption{Natural surface reflectance spectra}
+%        \label{fig:naturalSurfaceTarget}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.3\textwidth}
+%    \centering
+%        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
+%        \caption{Randomly generated target samples}
+%        \label{fig:randomSurfaceTarget}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.3 \textwidth}
+%    \centering
+%        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
+%        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
+%        \label{fig:sRGBSurfaceTarget}
+%    \end{subfigure}
+%    \caption{{\bf Target object surface reflectance spectrum:} For getting the target object surface reflectance, we first generate the spectra similar to that of other objects and then rescale them appropriately to get the required perceived lightness.
 (a) Natural surface reflectance spectra.
@@
 We show 10 samples at 1 lightness levels.}\label{fig:targetSurfaceReflectance}
-\end{figure}
+%\end{figure}
 
@@
         \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
-        \caption{Rendered image of a randomly drawn scene}
+        \caption{sRGB rendering of a 3D scene}
         \label{fig:3DScene}

### 2017-12-27 Draft1/draft1.tex
more edits

@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_e.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
         \caption{Normalized PCA eigenvalues}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_e.pdf}
         \caption{xy chromaticity diagram}
@@
 (c) Randomly samples generated using the rescaled spectra from Fig.~\ref{fig:rescaledGranada}.
-(d) CIE xy chromaticity plot of the rescaled dataset (Fig.~\ref{fig:rescaledGranada}) and randomly generated samples from Fig.~\ref{fig:randomIlluminant}.
-(e) Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
+(d)Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
 The eigenvalues have been normalized by the sum over all eigenvalues.
@@
 We used the first six eigenvectors in our analysis.
+(e) CIE xy chromaticity plot of the rescaled dataset (Fig.~\ref{fig:rescaledGranada}) and randomly generated samples from Fig.~\ref{fig:randomIlluminant}.
 (f) sRGB renditions of the random illuminant samples shown in \ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_d.pdf}
         \caption{Natural surface reflectance spectra}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_e.pdf}
         \caption{Randomly generated target samples}
@@
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
-        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_f.pdf}
+        \caption{sRGB rendition of target reflectance}
         \label{fig:sRGBSurfaceTarget}
     \end{subfigure}
-    \caption{{\bf Target object surface reflectance spectrum:} For getting the target object surface reflectance, we first generate the spectra similar to that of other objects and then rescale them appropriately to get the required perceived lightness.
-(a) Natural surface reflectance spectra.
-(b) Randomly generated samples for target reflectance.
-(c) The sRGB renditions of the random samples generated in Fig.~\ref{fig:randomSurfaceTarget}.
-We show 10 samples at 1 lightness levels.
-\newline
-{\bf Generating random surface reflectance spectra:} Surface reflectance spectra are generated by random sampling based on measured surface reflectance spectra, using principles similar to those used to generate random illuminant spectra.
+    \caption{{\bf Generating surface reflectance spectra:} Surface reflectance spectra are generated by random sampling based on measured surface reflectance spectra, using principles similar to those used to generate random illuminant spectra.
 (a) The 632 surface reflectance spectra from the Munsell and Vrhel datasets.
 (b) Randomly generated samples of reflectance spectra.
-(c) sRGB renderings (under CIE D65) of the random samples generated in \ref{fig:randomSurface}.}\label{fig:surfaceReflectanceGeneration}
+(c) sRGB renderings (under CIE D65) of the random samples generated in \ref{fig:randomSurface}.
+(d)Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues for the mean centered surface reflectance dataset.
+The eigenvalues have been normalized by the sum over all eigenvalues.
+The dotted line at 0.9 on the y-axis is for reference.
+We used the first six eigenvectors in our analysis.
+(e) CIE xy chromaticity plot of the surface reflectance dataset (Fig.~\ref{fig:naturalSurface}), randomly generated samples of surface reflectance (Fig.~\ref{fig:randomSurface}) and randomly generated samples of target surface.
+(f) The sRGB renditions of the randomly generated sample of target object surface reflectance.
+The figure shows 10 randomly generated samples at 10 levels of the target object surface luminance.
+The range of luminance levels [0.2, 0.6] (indicated on the Y axis), captures the luminance of more than 90\% of the natural surface reflectances.}
+\label{fig:surfaceReflectanceGeneration}
 \end{figure}
@@
 
-% Figure 8
-%\begin{figure}
-%\centering
-%	\begin{subfigure}[b]{0.3 \textwidth}
-%    \centering
-%        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.pdf}
-%        \caption{Natural surface reflectance spectra}
-%        \label{fig:naturalSurfaceTarget}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.3\textwidth}
-%    \centering
-%        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.pdf}
-%        \caption{Randomly generated target samples}
-%        \label{fig:randomSurfaceTarget}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.3 \textwidth}
-%    \centering
-%        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.pdf}
-%        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomSurfaceTarget}}
-%        \label{fig:sRGBSurfaceTarget}
-%    \end{subfigure}
-%    \caption{{\bf Target object surface reflectance spectrum:} For getting the target object surface reflectance, we first generate the spectra similar to that of other objects and then rescale them appropriately to get the required perceived lightness.
-(a) Natural surface reflectance spectra.
-(b) Randomly generated samples for target reflectance.
-(c) The sRGB renditions of the random samples generated in Fig.~\ref{fig:randomSurfaceTarget}.
-We show 10 samples at 1 lightness levels.}\label{fig:targetSurfaceReflectance}
-%\end{figure}
-
 For generating the target object reflectance at a particular luminance $(Y_{\rm T})$, the values in a generated spectrum were 
@@
 
-% Figure 9: Methods
+% Figure 8: Methods
 \begin{figure}
@@
 		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.png}
         \caption{sRGB rendering of a 3D scene}
@@
     \hspace{0.1 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.png}
         \caption{Cropped Image}
@@
     \hspace{0.1 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.png}
         \caption{Optical Image}
@@
     \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_d.png}
+        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_d.png}
         \caption{LMS cone contrast}
@@
 The software models optical blurring and foveal spatial sampling by the trichromatic cone mosaic.
-Fig.\ref{fig:croppedImageWithMosaic} shows the retinal image incident on the cone mosaic and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
+Fig.~\ref{fig:croppedImageWithMosaic} shows the retinal image incident on the cone mosaic and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
 (d) The cone responses are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).

### 2017-12-27 Draft1/draft1.tex
more edits

@@
 measurements to create a reflectance database containing 632 reflectances.
-% SAY SOMETHING ABOUT SPECTRAL SAMPLING
+
+ SAY SOMETHING ABOUT SPECTRAL SAMPLING
+
 Let us denote the reflectance dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
@@
 We model the encoding of such images by the early visual system, to generate {\em neural images} that provide an abstracted representation of the information available to the brain for producing perceptual representations of the external world.
-It is this information for each image, together with the known surface luminance of the corresponding target object, that we will provide to our supervised learning algorithms.
-Our training datasets correspond to % SAY WHAT WE DID ONCE WE FINISH EVERYTHING OFF.
+For each image, it is this information together with the known surface luminance of the corresponding target object that we will provide to our supervised learning algorithms.
+Our training datasets correspond to ...
+% SAY WHAT WE DID ONCE WE FINISH EVERYTHING OFF.
 
-In this work, we are interested in how well lightness constancy may be achieved using reasonably information that is local to the image region containing the target patch.
+In this work, we are interested in how well lightness constancy may be achieved using reasonable information that is local to the image region containing the target patch. 
 % MAYBE SAY A LITTLE MORE ABOUT WHY - THIS IS A PRINCIPLED STANCE TAKEN IN MOST OF JOHANNES WORK.  OR MAYBE DEFER THAT TO THE DISCUSSION.
-To this end, we crop a 51x51 pixel portion of the full rendreed multispectral image that contains the target object and use this for further analysis (\ref{fig:croppedImage}).
+To this end, we crop a 51x51 pixel portion of the full rendered multispectral image that contains the target object and use this for further analysis (\ref{fig:croppedImage}).
 Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this paper.
@@
 \subsection{Supervised Learning methods} \label{method:SupervisedLearning}
-\subsubsection*{Linear Regression} For linear regression, we solve the equation $A_{(1,3)}*C_{(3,N)} = Y_{(1,N)}$ for the regression parameters $A_{(1,3)}$.
-Here, $C_{(3,N)}$ has the contrast normalized matrix of LMS cone responses of the center pixel.
-Each column corresponds to the N images in the dataset.
-The rows correspond to the contrast normalized L, M and S cones response of the center pixel for each image.
-The L, M and S response to the center pixel on the target object is calculated by taking the average of a 3x3 patch of cones near the center of the target.The (unknown) regression parameters $A$ are obtained using Matlab linear regression function.
+We used three supervised learning methods in out analysis. Linear regression, SVD regression and accuracy maximization analysis.
+
+\subsubsection*{Linear Regression} For linear regression, we solve the equation $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
+Here, $C_{3\times N}$ is a matrix containing the contrast normalized L, M and S cone responses of the central patch of each image.
+The columns corresponds to the N images in the dataset.
+The rows correspond to the contrast normalized L, M and S cones responses averaged over a 3$\times$3 pixel central region of the image containing the target object.
+The (unknown) regression parameters $A$ are obtained using Matlab linear regression function.
 
@@
 Briefly, given an image dataset matrix $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds unit vectors such that the projection of the data along this vector maximizes the separation of the images with different labels, while clustering the images with similar labels together.
-Mathematically, the method searches for a direction $\hat{u}$ such that minimize the cost function:
+Mathematically, the method searches for a direction $\hat{u}$ that minimize the cost function:
 \begin{align}
@@
 \end{align} 
-where $C(:,j)$ represents the $j$'th column/image of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the matrix:
+where $C(:,j)$ represents the $j$'th column/image of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the following matrix:
 \begin{align}
@@
 \end{align}
-Here, $Y_{D}$ is a diagonal matrix with the elements of the labels vector $Y$ along the diagonal, and $\mathbbm{1}$ is a $N\times 1$ vector of ones.
+Here, $Y_{D}$ is a diagonal matrix with the elements of the labels vector $Y$ along the diagonal, and $\mathbbm{1}$ is a $N\times 1$ vector with each element equal to one.
 
@@
 \section{Discussion} \label{Discussion}
-\section{Supplementary Information}
+In this paper, we studied luminance constancy using naturalistic images.
+We generated a dataset of multispectral images labeled by the reflectance of a target object in each image.
+These images were generated by a software pipeline developed for this work, that we call Virtual world color constancy (VWCC).
+This software creates 3D scene descriptors based on programatic information provided by the user.
+Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc.
+We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances.
+Thus, we generate a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image.
+Such databases are near to be impossible to generate using other means as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab.
 
-\subsection{Cone response to multispectral images}
-Cone response to the multispectral images are generated
-using \href{https://github.com/isetbio}{Isetbio}.
-The model incorporates several critical components of biological vision, including physiological optics, information about cornea, lens, pupil, etc.
-We simulate a model retinal mosaic with $51\times51$ cones having cone densities in the ratio [l,m,s]=[0.6 0.3 0.1].
-The cone wavelength sensitivities are scaled such that the area under the sensitivity curve equals unity.
-A $51\times51$ pixel$^2$ patch of the image containing the target image is used to calculate the cone responses.
-The image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
+In this paper, as a first step towards understanding color constancy using supervised methods on labeled dataset, we studied a simpler analogue: luminance constancy.
+We generated images labeled with the luminance of a target object in the scene.
+We performed three types of spectral manipulations in the scene while generating the images (Fig.~\ref{fig:studiedCases}).
+1.
+Allow variations in the spectral shape of the target object surface reflectance spectrum, while keeping the background object surface reflectance and the illumination spectra of the light sources fixed.
+2.
+Allow variations in the shape of the target object surface reflectance and the illumination spectra of the light sources, while keeping the surface reflectance spectra of the background objects fixed.
+3.
+Allow variations in all three types of spectra.
+We generated hundreds of images at multiple luminance level of the target object for each of these three cases.
+Then using a model of the early visual system, we generated the response of the cones in the retina for each image in our database.
+These model retinal responses, along with the luminance label of the images, are then used as the input to supervised learning algorithms.
+Using our supervised methods, we leant that the target object luminance can be obtained from simple manipulation of the cone response for case where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, the light source illumination spectra.
+In these cases, the luminance can be obtained by comparing the response of the cones corresponding to the target and the background objects.
+When all these three types of spectral variations are allowed simultaneously, one needs additional information to obtain the luminance of the target object.
 

### 2017-12-28 Draft1/draft1.tex
more edits

@@
 \subsubsection*{Accuracy maximization analysis}
- \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
+AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
 Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task.
 The task is implicitly defined in terms of the labels.
-The optimal filters are the ones whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
+The optimal filters that are returned by AMA are filters whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
 
-Let us assume that the labels ($Y$) take one of the $N_{\nu}$ possible values $\{Y_k: k\in[1,N_{\nu}] \}$ and the $l$'th stimuli corresponding to the $k$'th category of the labels is represented as $s_{kl}$.
+Let us assume that there are $N_{\nu}$ possible values of the labels (luminance levels $\{Y_k: k\in[1,N_{\nu}] \}$).
+The image labels take one of these $N_{\nu}$ possible values.
+The $l$'th stimuli corresponding to the $k$'th category of the labels is represented as $s_{kl}$.
 Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
-Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the latent variable ($Y_k$) corresponding to the stimuli $s_{kl}$ as $\hat{Y}_{kl}$.
+Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the label ($Y_k$) corresponding to the stimuli $s_{kl}$ as $\hat{Y}_{kl}$.
 Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and a mean cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.
@@
 Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$.
-$N_{\nu}$ is the total number of labels and $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
+$N_{\nu}$ is the total number of values that labels can take and $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
 Thus,
@@
 AMA employs the Bayes optimal decoder ($g$) to estimate the optimal estimate.
-The Bayesian decoder computes the posterior probability of the latent variable $p(X|{\textbf {\textit R}})$ and reads out the optimal estimate $\hat{Y}^{\rm opt}$ from the posterior as the value that minimizes the cost.
+The Bayesian decoder computes the posterior probability of the label $p(Y|{\textbf {\textit R}})$ and reads out the optimal estimate $\hat{Y}^{\rm opt}$ from the posterior as the value that minimizes the cost.
 By Bayes' theorem, the posterior probability can be written as:
@@
 \section{Results} \label{Results}
-\subsection{Optimal receptive fields show a center surround structure}
-Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults}) shows the RFs, the linear response of these RFs training dataset and the lightness estimates of the test data for the three cases described above.
-We show the first two RFs for SVD and AMA methods (Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(a-b)).
+\subsection{Optimal receptive fields for luminance estimation have a center surround structure}
+We used two supervised learning methods to learn the optimal receptive fields (RFs) for lightness estimation for the three types of variations in the spectral properties of the scene as discuss earlier.
+Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults}) shows the optimal RFs, the linear response of these RFs to the training dataset, and the estimates of the luminance of the target object in the test dataset for the three cases.
+We show the first two RFs obtained using the SVD and AMA methods (Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(a-b)).
 The RFs are ranked in ascending order of the value of the cost function.
@@
 The L, M and S components give the weights for the linear sum of the cone responses for the three cone types.
-The salient features are the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.
+The salient features are: the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.
 
@@
 Thus, while the RFs show a trend of weights concentrated at the center similar to case 1, there is large negative contribution from the surround.
-The spatial features of the RFs are due the stereotypical geometry of the images (see SI).
-For case 3, has a similar center surround structure with more prominent features of the background as we also vary the spectra of the background objects.
+The spatial features of the RFs are due the stereotypical geometry of the images (see \nameref{Methods}).
+For case 3, has a similar center surround structure with more prominent features of the background, as we also vary the spectra of the background objects.
 Again, the spatial features are a result of the stereotypical geometry of the images.
@@
 Case 1:} (a) First two receptive fields produced by the SVD method.
-Along the row we show the filters corresponding to the L cones, M cones and Scones (left to right).
-(c) First two receptive fields produced by the SVD method.
+Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right).
+(b) First two receptive fields produced by the AMA method.
 (c) The response of the stimuli to the first two AMA filters.
 The responses are grouped with the label of the stimuli.
-As is clear, the response separate out quite well in this case, making the estimation easy (d) The estimates of the target object standard lightness.
+As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance.
+(d) The estimates of the target object standard luminance.
 The naive method produces the mean value of the target luminance used in the analysis.

### 2018-01-04 Draft1/draft1.tex
Today’s work

@@
 Such data sets are not readily available.
-Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection},  ( ADD McGill Database).
+Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection}.
+%http://tabby.vision.mcgill.ca, Olmos, A., Kingdom, F. A. A. (2004). A biologically inspired algorithm for the recovery of shading and reflectance images, Perception, 33, 1463 - 1473.
  Generating databases with both the images and the ground truth scene information is not trivial.
@@
 Some progress is being made on characterizing how illumination varies over space in natural scenes \cite{mury2007spatial}, which in the longer run may guide how information from reference objects can be used to provide reasonable estimates.
-Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene \cite{funt1988color,ciurea2003large} (ADD UCSB hyperspectral).
+Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene \cite{funt1988color,ciurea2003large}
+%http://color.psych.upenn.edu/hyperspectral/
 These data sets have been useful for evaluating computational color constancy algorithms, but the use of posed scenes does not scale well for use with supervised learning methods which needs large training sets.
@@
 This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
-This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception \cite{boyaci2003effect}(REFS: Many -- go to Boynton lecture slides for some).
+This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS),
+% Kavita Bale at Cornell, Check her website
+% Autonmous vehicle work - ask BAW
+as well as for the generation of stimuli for the study of human perception \cite{boyaci2003effect}(REFS: Many -- go to Boynton lecture slides for some).
+% Add "e.g." in front of citation list, however you do that in BibTex
+%@article{todd1983perception,
+%  title={Perception of surface curvature and direction of illumination from patterns of shading.},
+%  author={Todd, James T and Mingolla, Ennio},
+%  journal={Journal of Experimental Psychology: Human perception and performance},
+%  volume={9},
+%  number={4},
+%  pages={583},
+%  year={1983},
+%  publisher={American Psychological Association}
+%}
+%@article{RN456,
+%   author = {Arend, L and Reeves, A},
+%   title = {Simultaneous color constancy},
+%   journal = {Journal Of The Optical Society Of America A},
+%   volume = {3},
+%   number = {10},
+%   pages = {1743-1751},
+%   DOI = {10.1364/josaa.3.001743},
+%   url = {http://josaa.osa.org/abstract.cfm?URI=josaa-3-10-1743},
+%   year = {1986},
+%   type = {Journal Article}
+%}
+%@article{johnston1993integration,
+%  title={Integration of depth modules: Stereopsis and texture},
+%  author={Johnston, Elizabeth B and Cumming, Bruce G and Parker, Andrew J},
+%  journal={Vision research},
+%  volume={33},
+%  number={5},
+%  pages={813--826},
+%  year={1993},
+%  publisher={Elsevier}
+%}
 Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.
@@
 Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this paper.
+Next, the cropped multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
+The key steps we model are the size of the pupil, optical blurring (including axial chromatic aberration) in the formation of the retinal image, spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones, and the Poisson nature of photopigment isomerization.
+We use the multispectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
+The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
+The retinal cone mosaic is modeled as a square grid with $51 \times 51$ cones in the L:M:S ratio 0.6:0.3:0.1.
+The response of the cones are taken as the number of isomerizations in the cone segment ({\it over what time ??}).
 
-Next, the cropped multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
-The key steps we model are optical blurring, including axial chromatic aberration, in the formation of the retinal image, spatial sampling by an interleaved mosaic of L, M and S cones, and the Poisson nature of photopigment isomerization.
 % NEED TO WRITE IN THE KEY PARAMETERS USED.
 PROBABLY MARIMONT AND WANDELL OPTICS, STOCKMAN-SHARPE LMS CONE SPECTRAL SENSITIVITIES, THE L, M, S CONE RATIO IN THE MOSAIC, RECTANGULAR AND REGULAR CONE PACKING, SOME IMPLIED SPATIAL SCALE, AND SOME OVERALL SCALING THAT DRIVES THE MEAN LUMINANCE OF THE RETINAL IMAGES AND THUS THE AMOUNT OF POISSON NOISE.
+ALSO INTEGRATION TIME.
+The cone response functions are normalized by the total area under the response curves to model the amplification of the S cone response downstream and thus have comparable number if isomerizations in L, M and S cones.
+% NEED TO UNDERSTAND THIS.  WHEN WAS THE GAIN, BEFORE OR AFTER NOISE ADDED, AND LET'S REMEMBER WHY WE DID IT.
 
-% WE GOT TO HERE ON DECEMBER 21.
-To generate the retinal response one needs to specify the retinal cone mosaic and the size of the retinal image.
-The retinal cone mosaic is specified in terms of the total number of cones and the proportion of the long(L), medium(M) and the short(S) cones in the mosaic.
-With these parameters, the software generates the specified number of LMS cones with random positions on a square grid.
-The size of the retinal image is specified in terms of the field of view and object distance from the eye.
-
-We simulate visual system response using \href{http://isetbio.org}{Isetbio} software toolbox.
-Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics.
-We use the multispectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
-The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
-The retinal cone mosaic is modeled as a square grid with 51x51 cones in the l:m:s ratio 0.6:0.3:0.1.
-The response of the cones are measured as the number of isomerizations in the cone segment ({\it over what time ??}).
-The cone response functions are normalized by the total area under the response curves to model the amplification of the S cone response downstream and thus have comparable number if isomerizations in L, M and S cones.
-Further, to get the response of each cone class at each position on the retinal mosaic, we interpolate the response of each cone class.
-Thus we get a $51 \times 51$ cone response image for each cone class.
-
-The three $51 \times 51$ cone response matrix corresponding to L, M and S cones are then reshaped into a $7803 \times 1$ vector.
-To model the contrast adaptation in the visual system, we perform a contrast normalization of the vector by subtracting and dividing by the mean.
-We further  rescale the vector to have norm 1.
-The cone-response vectors corresponding to the N images for each case are concatenated into a column-wise contrast normalized matrix $C_{7803\times N}$.
+The isomerizations of the cones in the retinal mosaic represent the first steps of visual processing.
+To capture key properties of post-receptoral processing, contrast coding (REFS) and contrast normalization (REFS),
+% Ask Johannes what he'd use as references for these broad principles
+we processed the isomerations as follows:
+First, we created a representation for each cone class on the full $51 \times 51$ pixel grid, we interpolated the responses of the cones in each class across the grid, using bilinear interpolation separately for each cone class.
+% DOUBLE CHECK THAT THIS WAS DONE WITH SOMETHING LIKE INTERP2 WITH THE LINEAR OPTION.
+This gives us a $51 \times 51$ cone response image for each cone class.
+The three $51 \times 51$ sets of cone responses corresponding to the L, M and S cones were then reshaped into a single $7803 \times 1$ vector (7803 = 51 \times 51 \times 3).
+To model the contrast coding and contrast adaptation, we convert this vector to a contrast representation by subtracting out the mean and then dividing by it (contrast coding), followed by normalizing the vector to have unit length (contrast normalization).
+The cone-response vectors corresponding to the N images for each case are concatenated column-wise to form a contrast normalized matrix $C_{7803\times N}$.
 The corresponding labels are represented by the row vector $Y_{1\times N}$.
@@
 \subsubsection*{Linear Regression} For linear regression, we solve the equation $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
-Here, $C_{3\times N}$ is a matrix containing the contrast normalized L, M and S cone responses of the central patch of each image.
+Here, $C_{3\times N}$ is a matrix containing the contrast normalized L, M and S cone responses of the central patch of each image, extracted from $C_{7803\times N}$.
 The columns corresponds to the N images in the dataset.
@@
 The (unknown) regression parameters $A$ are obtained using Matlab linear regression function.
+This model provides a baseline performance measure, which does not take the context in which the target image is seen into account.
 
 \subsubsection*{SVD regression}
-SVD regression is a generalization of principal component analysis for labeled data \cite{ranganNotes}.
-Briefly, given an image dataset matrix $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds unit vectors such that the projection of the data along this vector maximizes the separation of the images with different labels, while clustering the images with similar labels together.
+SVD regression is a generalization of principal component analysis that may be applied to labelled data \cite{ranganNotes}.
+Briefly, given an image dataset matrix $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds unit vectors such that the projection of the data along these vectors maximizes the separation of the vectors with different labels, while clustering vectores with similar labels together.
 Mathematically, the method searches for a direction $\hat{u}$ that minimize the cost function:
@@
 Here, $Y_{D}$ is a diagonal matrix with the elements of the labels vector $Y$ along the diagonal, and $\mathbbm{1}$ is a $N\times 1$ vector with each element equal to one.
+%% NEED TO DECIDE WHETHER WE ARE KEEPING THIS.  IF SO, NEED TO CLARIFY THAT WE CAN PROJECT ONTO MULTIPLE VECTORS AND THAT HAVING DONE SO, WE THEN DO BAYESIAN DECODING AS WITH AMA
 
+% MAYBE ADD SOME INTRO TEXT THAT SAYS THAT FIRST ONE FINDS THE FILTERS AND THEN PROJECTS ONTO THEM, THEN DOES BAYESIAN DECODING OF THE RESPONSES.  BREAK INTO TWO SUBSECTIONS FOR CLARITY.
 \subsubsection*{Accuracy maximization analysis}

### 2018-01-05 Draft2/draft2.tex
restructuring

--- 2018-01-04 Draft1/draft1.tex
@@
 
-\title{Lightness constancy under fixed geometry}
+\title{Luminance constancy under fixed geometry}
 \abstract{The light that reflects off an object surface and is captured by our eyes varies significantly with its context.
@@
 The mechanism of this behaviorally significant invariance detection ability remains largely unknown.
-To understand the computational principles that lead to such invariant perception, we study the perception of object lightness under spectral variations in 3D scenes.
-Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the perceived lightness of an object.
+To understand the computational principles that lead to such invariant perception, we study the perception of object luminance under spectral variations in 3D scenes.
+Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the perceived luminance of an object.
 We have developed a software that generates naturalistic multispectral images of 3D scenes with precise control over the geometrical and spectral properties of the constituents that make a scene.
-We label these images with the lightness of a specific object in the scene.
+We label these images with the luminance of a specific object in the scene.
 Next, we simulate the response of the retinal cones to these multispectral images using an accurate model of the early visual system.
-Using supervised learning methods on these labeled cone response, we identify the computations that lead to accurate lightness estimation.
-We show that if only either target, or background, or illumination spectra are allowed to vary, the standard lightness can be estimated through simple transformations of the cone responses.
-When all the spectra vary simultaneously, while it is not easy to recover the lightness through simple transformations, a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and S cones can recover the lightness within about 15\% RMSE.}
+Using supervised learning methods on these labeled cone response, we identify the computations that lead to accurate luminance estimation.
+We show that if only either target, or background, or illumination spectra are allowed to vary, the standard luminance can be estimated through simple transformations of the cone responses.
+When all the spectra vary simultaneously, while it is not easy to recover the luminance through simple transformations, a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and S cones can recover the luminance within about 15\% RMSE.}
 
@@
 \keywords{color constancy, accuracy maximization analysis, supervised learning,
-lightness}
+luminance}
 
@@
 Such invariant color perception is called color constancy.
-(b) {\bf Lightness Constancy Under Spectral Variations:} In this paper we consider the special case of lightness constancy.
+(b) {\bf Luminance Constancy Under Spectral Variations:} In this paper we consider the special case of luminance constancy.
 Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance.
 Within each row, the surface reflectance of the spheres has the same luminance, when illuminated by a standard reference illuminant, CIE D65.
-The three rows differ in this value, as can be seen by the fact that the lightness of the spheres generally decreases as we move down the columns.
+The three rows differ in this value, as can be seen by the fact that the luminance of the spheres generally decreases as we move down the columns.
 Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.
@@
 This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus \cite{burge2011optimal} and disparity \cite{burge2014optimal} from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
-In this paper, we apply AMA, as well as comparison supervised learning algorithms to a special case of the color constancy problem (lightness constancy) and evaluate how well it performs for naturalistic image input.
+In this paper, we apply AMA, as well as comparison supervised learning algorithms to a special case of the color constancy problem (luminance constancy) and evaluate how well it performs for naturalistic image input.
 
@@
 Such data sets are not readily available.
-Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection}.
-%http://tabby.vision.mcgill.ca, Olmos, A., Kingdom, F. A. A. (2004). A biologically inspired algorithm for the recovery of shading and reflectance images, Perception, 33, 1463 - 1473.
+Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
 Generating databases with both the images and the ground truth scene information is not trivial.
@@
 Some progress is being made on characterizing how illumination varies over space in natural scenes \cite{mury2007spatial}, which in the longer run may guide how information from reference objects can be used to provide reasonable estimates.
-Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene \cite{funt1988color,ciurea2003large}
-%http://color.psych.upenn.edu/hyperspectral/
+Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene \cite{funt1988color,ciurea2003large, davidPennHyperspectral}.
+% REMOVE NO DATE (n.d.) FROM THE CITATION
 These data sets have been useful for evaluating computational color constancy algorithms, but the use of posed scenes does not scale well for use with supervised learning methods which needs large training sets.
@@
     \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of multispectral images similar to ones studied in our work.
-The numbers on the left indicate the standard lightness level of the target object.
-5 images are shown at each lightness level.
+The numbers on the left indicate the standard luminance level of the target object.
+5 images are shown at each luminance level.
 We studied three types of spectral variations.
@@
 Here, in addition to employing computer graphics to render the light reaching the eye from specified scenes, we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
-We describe this approach in detail below, but the key advantage is that we can produce large numbers of naturalistic images and the corresponding cone mosaic responses, where all of the underlying scene properties are well-specified.
+We describe this approach in detail below.
+The key advantage of this approach is that we can produce large numbers of naturalistic images and the corresponding cone mosaic responses where all of the underlying scene properties are well-specified.
 This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
-This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS),
-% Kavita Bale at Cornell, Check her website
+This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular \cite{kovacs17shading},
 % Autonmous vehicle work - ask BAW
-as well as for the generation of stimuli for the study of human perception \cite{boyaci2003effect}(REFS: Many -- go to Boynton lecture slides for some).
-% Add "e.g." in front of citation list, however you do that in BibTex
-%@article{todd1983perception,
-%  title={Perception of surface curvature and direction of illumination from patterns of shading.},
-%  author={Todd, James T and Mingolla, Ennio},
-%  journal={Journal of Experimental Psychology: Human perception and performance},
-%  volume={9},
-%  number={4},
-%  pages={583},
-%  year={1983},
-%  publisher={American Psychological Association}
-%}
-%@article{RN456,
-%   author = {Arend, L and Reeves, A},
-%   title = {Simultaneous color constancy},
-%   journal = {Journal Of The Optical Society Of America A},
-%   volume = {3},
-%   number = {10},
-%   pages = {1743-1751},
-%   DOI = {10.1364/josaa.3.001743},
-%   url = {http://josaa.osa.org/abstract.cfm?URI=josaa-3-10-1743},
-%   year = {1986},
-%   type = {Journal Article}
-%}
-%@article{johnston1993integration,
-%  title={Integration of depth modules: Stereopsis and texture},
-%  author={Johnston, Elizabeth B and Cumming, Bruce G and Parker, Andrew J},
-%  journal={Vision research},
-%  volume={33},
-%  number={5},
-%  pages={813--826},
-%  year={1993},
-%  publisher={Elsevier}
-%}
+as well as for the generation of stimuli for the study of human perception (e.g., \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}). 
 Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.
@@
 This procedure allows us to assign to any surface reflectance a single surface luminance value.
-Because the perceived lightness of an object is approximately (but by no means exactly, see \citeNP{wyszecki1986color}) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of {\em lightness constancy}.
-This is a generalization of the way this term is often used, where it refers more specifically to the stability of perceived lightness across images of scenes where all objects and illuminants are achromatic \cite{gilchrist2006seeing}.
+Because the perceived luminance of an object is approximately (but by no means exactly, see \citeNP{wyszecki1986color}) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of {\em luminance constancy}.
+This is a generalization of the way this term is often used, where it refers more specifically to the stability of perceived luminance across images of scenes where all objects and illuminants are achromatic \cite{gilchrist2006seeing}.
 Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (see  Fig.~\ref{fig:introExampleFigure}).
@@
 
-Even within the special case of lightness constancy, there are many scene manipulations that could be considered.
+Even within the special case of luminance constancy, there are many scene manipulations that could be considered.
 The set of manipulations we focus on here are illustrated by the three panels of Fig.~\ref{fig:studiedCases}.
@@
 (see \nameref{Methods}).
-In this paper, we focus on the problem of lightness constancy within scene ensembles where these geometric factors are held fixed.
+In this paper, we focus on the problem of luminance constancy within scene ensembles where these geometric factors are held fixed.
 
-We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, lightness can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
-For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
-Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
-Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
-Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
+We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
+For variations only in target object reflectance spectra (case 1), object luminance can be recovered directly from the light reflected off the target object.
+For case 2, where both the target object reflectance and light source spectra vary, object luminance can be recovered from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (case 3), the standard luminance can not be recovered simply from the cone response or the contrast.
+We have used AMA with a Bayesian estimator to estimate standard luminance of the target object.
+Using this method, we can recover the luminance of the target object with $\sim 15\%$ relative root mean square error.
+Our analysis shows that the optimal receptive fields for estimating the luminance of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
+Additionally, luminance estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
 Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
-We discuss the implications of such receptive fields on lightness constancy.
+We discuss the implications of such receptive fields on luminance constancy.
 
 The rest of this paper is organized as follows.
-In the \nameref{Methods} section, we describe in detail the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}) using our software pipeline {\rm Virtual world color constancy}, the process to simulate the response of retinal cone photoreceptors to these images using a standard model of the early visual system (\nameref{method:Isetbio}) and the supervised learning methods used in our analysis (\nameref{method:SupervisedLearning}).
+In the \nameref{Methods} section, we describe in detail the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}) using our software pipeline {\rm Virtual world color constancy}, the process to simulate the response of retinal cone photoreceptors to these images using a standard model of the early visual system (\nameref{method:Isetbio}) and the supervised learning method (AMA) used in our analysis (\nameref{method:SupervisedLearning}).
 In the \nameref{Results} section, we show the estimates and performance of the supervised methods for the three cases mentioned above.
@@
 The second is how we model the transformations applied by the early visual system to generate modeled responses of the cone photoreceptor mosaic.
-The third is the details of the supervised learning methods we apply to the labelled training data.
+The third is the details of the supervised learning method (AMA) we apply to the labelled training data.
 And the fourth is how we evaluate the performance of the algorithms.
@@
 measurements to create a reflectance database containing 632 reflectances.
-
- SAY SOMETHING ABOUT SPECTRAL SAMPLING
+The Munsell database contains 462 samples of surface reflectance spectra each measured at 5nm sampling intervals between 380nm and 780nm.
+The Vrhel dataset has 170 samples measured at 2nm sampling between 390nm and 730 nm.
+We subsampled these spectra in the 400-700nm interval, 10 nm apart, for rendering images used in this work.
 
@@
 $\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
-perception of brightness.
+perception of bruminance.
 The target reflectance is then given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
@@
 
-In this work, we are interested in how well lightness constancy may be achieved using reasonable information that is local to the image region containing the target patch. 
+In this work, we are interested in how well luminance constancy may be achieved using reasonable information that is local to the image region containing the target patch. 
 % MAYBE SAY A LITTLE MORE ABOUT WHY - THIS IS A PRINCIPLED STANCE TAKEN IN MOST OF JOHANNES WORK.  OR MAYBE DEFER THAT TO THE DISCUSSION.
 To this end, we crop a 51x51 pixel portion of the full rendered multispectral image that contains the target object and use this for further analysis (\ref{fig:croppedImage}).
-Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this paper.
+Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 luminance levels for the three cases considered in this paper.
 Next, the cropped multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
@@
 % NEED TO UNDERSTAND THIS.  WHEN WAS THE GAIN, BEFORE OR AFTER NOISE ADDED, AND LET'S REMEMBER WHY WE DID IT.  
+% First we add noise, then we do the scaling.
+The reason this was done is to make sure that in the normalization process each of the cone class have the same contribution.
+Otherwise, the S cone contribution would be very low.
 
@@
 % Ask Johannes what he'd use as references for these broad principles
-we processed the isomerations as follows:
+we processed the isomerizations as follows:
 First, we created a representation for each cone class on the full $51 \times 51$ pixel grid, we interpolated the responses of the cones in each class across the grid, using bilinear interpolation separately for each cone class.
@@
 This gives us a $51 \times 51$ cone response image for each cone class.
-The three $51 \times 51$ sets of cone responses corresponding to the L, M and S cones were then reshaped into a single $7803 \times 1$ vector (7803 = 51 \times 51 \times 3).
+The three $51 \times 51$ sets of cone responses corresponding to the L, M and S cones were then reshaped into a single $7803 \times 1$ vector ($7803 = 51 \times 51 \times 3$).
 To model the contrast coding and contrast adaptation, we convert this vector to a contrast representation by subtracting out the mean and then dividing by it (contrast coding), followed by normalizing the vector to have unit length (contrast normalization).
@@
 \subsection{Supervised Learning methods} \label{method:SupervisedLearning}
-We used three supervised learning methods in out analysis. Linear regression, SVD regression and accuracy maximization analysis.
+We have two supervised learning methods in our work: Linear regression and Accuracy maximization analysis. While, our main focus is on AMA, linear regression provides a baseline performance measure.
 
@@
 
-\subsubsection*{SVD regression}
-SVD regression is a generalization of principal component analysis that may be applied to labelled data \cite{ranganNotes}.
-Briefly, given an image dataset matrix $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds unit vectors such that the projection of the data along these vectors maximizes the separation of the vectors with different labels, while clustering vectores with similar labels together.
-Mathematically, the method searches for a direction $\hat{u}$ that minimize the cost function:
-\begin{align}
-S = \sum\limits_{j,j'}\left(\hat{u}^\intercal C(:,j) - \hat{u}^\intercal C(:,j')\right)^2 \left(Y(j)-Y(j') \right)^2,
-\end{align} 
-where $C(:,j)$ represents the $j$'th column/image of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the following matrix:
-\begin{align}
-N C Y_D^2 C^\intercal - 2(Y*\mathbbm{1})C Y_D C^\intercal + (Y*Y^\intercal) (CC^\intercal)-C Y_{D}^2\mathbbm{1}\mathbbm{1}^\intercal C^\intercal +2 C Y_{D} \mathbbm{1}\mathbbm{1}^\intercal Y_{D} C^\intercal - C \mathbbm{1}\mathbbm{1}^\intercal Y_{D}^2 C^\intercal.
-\end{align}
-Here, $Y_{D}$ is a diagonal matrix with the elements of the labels vector $Y$ along the diagonal, and $\mathbbm{1}$ is a $N\times 1$ vector with each element equal to one.
-%% NEED TO DECIDE WHETHER WE ARE KEEPING THIS.  IF SO, NEED TO CLARIFY THAT WE CAN PROJECT ONTO MULTIPLE VECTORS AND THAT HAVING DONE SO, WE THEN DO BAYESIAN DECODING AS WITH AMA
+\subsubsection*{Accuracy maximization analysis}
+% MAYBE ADD SOME INTRO TEXT THAT SAYS THAT FIRST ONE FINDS THE FILTERS AND THEN PROJECTS ONTO THEM, THEN DOES BAYESIAN DECODING OF THE RESPONSES.  BREAK INTO TWO SUBSECTIONS FOR CLARITY.
 
-% MAYBE ADD SOME INTRO TEXT THAT SAYS THAT FIRST ONE FINDS THE FILTERS AND THEN PROJECTS ONTO THEM, THEN DOES BAYESIAN DECODING OF THE RESPONSES.  BREAK INTO TWO SUBSECTIONS FOR CLARITY.
-\subsubsection*{Accuracy maximization analysis}
 AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
@@
 The task is implicitly defined in terms of the labels.
-The optimal filters that are returned by AMA are filters whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
+The optimal filters that are returned by AMA are the filters whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
+Once these filters have been identified, a suitable decoding method (in this case a Bayesian decoding scheme) is used to estimate the label on a test set.
 
-Let us assume that there are $N_{\nu}$ possible values of the labels (luminance levels $\{Y_k: k\in[1,N_{\nu}] \}$).
-The image labels take one of these $N_{\nu}$ possible values.
-The $l$'th stimuli corresponding to the $k$'th category of the labels is represented as $s_{kl}$.
+{\bf Learning AMA Filters:} Let us assume that there are $N_{\nu}$ possible values of the labels.
+In our analysis, it means that the luminance level of the target object in an image can take one of the possible $N_{\nu}$ values ($\{Y_k: k\in[1,N_{\nu}] \}$).
+We represent the $l$'th image corresponding to the $k$'th category of the labels as $s_{kl}$.
 Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
@@
 Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$.
-$N_{\nu}$ is the total number of values that labels can take and $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
+Here $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
 Thus,
@@
 \end{align}
-As the conditional probability of the filter response is:
+Since, the conditional probability of the filter response is:
 \begin{align}
@@
 \end{align}
-Since, $p({\textbf {\textit s} }_{km}|Y_k) = \frac{1}{N_k}$, and $p(Y_k)=\frac{N_k}{N}$, where $N = \sum\limits_{k=1}^{N_{\nu}}N_{k}$ is total number of samples in the training set, Eq.\ref{eq:finalPosterior} simplifies to
+Since, $p({\textbf {\textit s} }_{km}|Y_k) = \frac{1}{N_k}$, and $p(Y_k)=\frac{N_k}{N}$, where $N = \sum\limits_{k=1}^{N_{\nu}}N_{k}$ is total number of samples in the training set, Eq.~\ref{eq:finalPosterior} simplifies to
 \begin{align}
@@
 \begin{align}
-\mathcal{C}_{kl} = \sum\limits_{u=1}^{N_{\nu}}\gamma(X_u,\hat{Y}_u)p(X_u|{\textbf{\textit R}}_{kl}),
+\mathcal{C}_{kl} = \sum\limits_{u=1}^{N_{\nu}}\gamma(Y_u,\hat{Y}_u)p(X_u|{\textbf{\textit R}}_{kl}).
 \end{align}
-and the mean cost associated with the training set is $\bar{\mathcal{C}} = \frac{1}{N} \sum\limits_{k,l}\bar{\mathcal{C}}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle \mathcal{C}_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$.
+The mean cost associated with the training set is $\bar{\mathcal{C}} = \frac{1}{N} \sum\limits_{k,l}\bar{\mathcal{C}}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle \mathcal{C}_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$.
 The optimal AMA filters are obtained by minimizing $\bar{\mathcal{C}}$ over the filter set ${\textbf {\textit f} }$ (Eq.\ref{eq:fopt}).
@@
 
+{\bf Estimating labels:} The image labels are estimated using the Bayesian decoder as described above.
+First, we use the AMA optimal filters and the training dataset to find the conditional distribution of the AMA filter response $p({\textbf {\textit R} }|Y_i)$.
+We then approximate this distribution with multivariate normal distribution $p({\textbf {\textit R} }|Y_i) = \mathcal{N}\left(\mu(Y_i),\Sigma(Y_i) \right)$.
+To estimate the label of an image from the test set, we use Byes' rule to obtain the posterior distribution $p(Y_i|{\textbf {\textit R} })$.
+The estimates value is the one that optimizes the cost function.
+
 \section{Results} \label{Results}
 \subsection{Optimal receptive fields for luminance estimation have a center surround structure}
-We used two supervised learning methods to learn the optimal receptive fields (RFs) for lightness estimation for the three types of variations in the spectral properties of the scene as discuss earlier.
+We used two supervised learning methods to learn the optimal receptive fields (RFs) for luminance estimation for the three types of variations in the spectral properties of the scene as discuss earlier.
 Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults}) shows the optimal RFs, the linear response of these RFs to the training dataset, and the estimates of the luminance of the target object in the test dataset for the three cases.
@@
 For case 2, while the target and the illuminant spectra varies, the background object spectra is fixed.
-Hence, the lightness can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background.
+Hence, the luminance can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background.
 Thus, while the RFs show a trend of weights concentrated at the center similar to case 1, there is large negative contribution from the surround.
@@
 \centering
-\begin{subfigure}[b]{0.27 \textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.pdf}
-        \caption{SVD First 2 RFs}
-        \label{fig:case9SVD}
-    \end{subfigure}
     \begin{subfigure}[b]{0.27 \textwidth}   
@@
         \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.pdf}
-        \caption{Lightness Estimates}
+        \caption{Luminance Estimates}
         \label{fig:case9Results}
     \end{subfigure}    
-    \caption{{\bf Receptive fields and lightness estimates.
+    \caption{{\bf Receptive fields and luminance estimates.
 Case 1:} (a) First two receptive fields produced by the SVD method.
@@
 \includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
-\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the lightness.}
+\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the luminance.}
 \label{fig:RMSEvsNFilters}
@@
     \end{subfigure}
-    \caption{{\bf Receptive fields and lightness estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
+    \caption{{\bf Receptive fields and luminance estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
     \label{fig:case10AllResults}
@@
     \end{subfigure}
-    \caption{{\bf Receptive fields and lightness estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
+    \caption{{\bf Receptive fields and luminance estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
     \label{fig:case12AllResults}
@@
 
-\subsection{Lightness can be well estimated using a bayesian decoder with gaussian priors.}
-We estimate the lightness of the target object in the images using the receptive field response of the corresponding contrast normalized cone responses.
+\subsection{Luminance can be well estimated using a bayesian decoder with gaussian priors.}
+We estimate the luminance of the target object in the images using the receptive field response of the corresponding contrast normalized cone responses.
 Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(c) shows the response of the first two RFs to the stimuli set for the three cases.
-For the training images at each lightness level, we approximate the receptive response of the contrast normalized cone responses by a multivariate gaussian.
-The target object lightness of an image in the test set is estimated using Bayesian decoder.
+For the training images at each luminance level, we approximate the receptive response of the contrast normalized cone responses by a multivariate gaussian.
+The target object luminance of an image in the test set is estimated using Bayesian decoder.
 We measure the estimation performance in terms of the relative root mean square ($E_{\rm rel}$) defined as:
@@
 \end{align}
-where $\hat{Y}$ corresponds to the estimated lightness and $Y$ to the assigned lightness. We use the first 8 RFs for lightness estimation ( see Fig.~\ref{fig:RMSEvsNFilters}).
+where $\hat{Y}$ corresponds to the estimated luminance and $Y$ to the assigned luminance. We use the first 8 RFs for luminance estimation ( see Fig.~\ref{fig:RMSEvsNFilters}).
 
-Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(d) shows the lightness estimates and the RMSE for the three methods (Linear regression on center pixel, AMA and SVD).
-Additionally we show the estimate of a naive model that reports the mean value of the lightness labels used in the dataset.
+Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(d) shows the luminance estimates and the RMSE for the three methods (Linear regression on center pixel, AMA and SVD).
+Additionally we show the estimate of a naive model that reports the mean value of the luminance labels used in the dataset.
 The diagonal x=y line is shown for reference.
@@
 (Fig.~\ref{fig:summaryBarGraph}) compares the $E_{\rm rel}$ for the different methods for the three cases.
-Both AMA and SVD methods, which use the information from the entire image estimate the lightness better compared to linear regression which only uses the information from the center pixel.
-This shows the importance of context information for lightness estimation.
+Both AMA and SVD methods, which use the information from the entire image estimate the luminance better compared to linear regression which only uses the information from the center pixel.
+This shows the importance of context information for luminance estimation.
 
@@
     \end{subfigure}
-\caption{{\bf Model and Filter Performance:} (a) Comparison of various methods on lightness estimations for the three cases studied here.
-For simple spectral variations, like where only the target reflectance varies (case 1) or only the target and illumination spectrum varies (Case 2), the lightness can be estimated well.
-This is so, because the lightness information can be estimated simply from the light reflected of the target( case 1) or from the contrast between the target and the {\it fixed} background (case 2).
-For more complex case, where the lightness information is confounded due to variations in target, background and illuminant (case 3), the estimation has higher variability.
+\caption{{\bf Model and Filter Performance:} (a) Comparison of various methods on luminance estimations for the three cases studied here.
+For simple spectral variations, like where only the target reflectance varies (case 1) or only the target and illumination spectrum varies (Case 2), the luminance can be estimated well.
+This is so, because the luminance information can be estimated simply from the light reflected of the target( case 1) or from the contrast between the target and the {\it fixed} background (case 2).
+For more complex case, where the luminance information is confounded due to variations in target, background and illuminant (case 3), the estimation has higher variability.
 (b) Performance of the SVD receptive fields obtained from one case on the stimuli of others.
@@
 Similarly, the RFs of case 2 performs well on the stimuli of case 1.
-Thus, the receptive fields leant on the complex case generalize for lightness estimation of stimuli for simpler cases.
+Thus, the receptive fields leant on the complex case generalize for luminance estimation of stimuli for simpler cases.
 

### 2018-01-05 codeForFigures/codeToMakeFigures/estimatesVsActualAMAOnly.m
more figures

@@ -1,0 +1,59 @@
+% This script plots the lightness estimates vs the actual lighteness for 
+% the linear, SVD and AMA methods.
+%
+% Case 9 - Variable Target shape Fixed Background Fixed Illuminant
+% Case 10 - Variable Target shape Fixed Background Variable Illuminant
+% Case 12 - Variable Target shape Variable Background Variable Illuminant
+%
+% VS wrote this Oct7 2017
+
+% Make the directory where the figures will be stored
+if (~exist('estimatesVsActualAMA','dir'))
+    mkdir('estimatesVsActualAMA');
+end
+
+% Choose a case
+for caseNo = [ 9 10 12]
+
+% load the files containing the estimates
+loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'.mat']);
+loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'.mat']);
+loadTheSVDFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SVD/case',num2str(caseNo),'.mat']);
+
+% Define the colors to be used for each method
+naiveColor  = 'g';
+linearColor = 'k';   
+AMAColor    = 'r';
+
+% Plot the contrast estimates
+fig = figure;
+set(fig,'units','pixels', 'Position', [1 1 500 500]);
+hold on;
+% plot the linear and svd response
+lNaive = plot(unique(loadTheAMAFile.XTest)',0.4*ones(size(unique(loadTheAMAFile.XTest)')),naiveColor,'linewidth',2);
+lLinear = plot(unique(loadTheAMAFile.XTest)',loadTheLinearFile.cNormMeanEstimateTest,linearColor,'linewidth',2);
+% errorbar(unique(loadTheLinearFile.labelsTest)',loadTheLinearFile.cMeanSvdEstimateTest,loadTheLinearFile.cStdSvdEstimateTest,SVDColor,'linewidth',2);
+xlim([0.15 0.65]);
+ylim([0.15 0.65]);
+xlabel('$Y$','interpreter','latex');
+ylabel('$\hat{Y}$','interpreter','latex');
+box on;
+
+%% This part is for AMA SGD
[…]

### 2018-01-05 codeForFigures/codeToMakeFigures/plotRMSEvsEigValSVD.m

@@ -53,12 +53,12 @@ axis square
 
 nEigVecs = 16;
 % SVD Results
-l9SVD = plot([1:nEigVecs],results9SVD.Case9error(1:nEigVecs),color9SVD,'linewidth',2);
-l10SVD = plot([1:nEigVecs],results10SVD.Case10error(1:nEigVecs),color10SVD,'linewidth',2);
-l12SVD = plot([1:nEigVecs],results12SVD.Case12error(1:nEigVecs),color12SVD,'linewidth',2);
+% l9SVD = plot([1:nEigVecs],results9SVD.Case9error(1:nEigVecs),color9SVD,'linewidth',2);
+% l10SVD = plot([1:nEigVecs],results10SVD.Case10error(1:nEigVecs),color10SVD,'linewidth',2);
+% l12SVD = plot([1:nEigVecs],results12SVD.Case12error(1:nEigVecs),color12SVD,'linewidth',2);
 
 % AMA Results
-l9AMA = plot([1:8],results9AMA.error(1:8),color9AMA,'linewidth',2);
+l9AMA = plot([1:nEigVecs],results9AMA.error(1:nEigVecs),color9AMA,'linewidth',2);
 l10AMA = plot([1:nEigVecs],results10AMA.error(1:nEigVecs),color10AMA,'linewidth',2);
 l12AMA = plot([1:nEigVecs],results12AMA.error(1:nEigVecs),color12AMA,'linewidth',2);
 
@@ -68,16 +68,16 @@ ylabel('E_{rel}');
 box on;
 
 set(gca, 'fontsize', 20);
-legend([l9SVD l9AMA l10SVD l10AMA l12SVD l12AMA],{'Case 1 SVD', 'Case 2 SVD', 'Case 3 SVD', ...
+legend([l9AMA l10AMA l12AMA],{ ...
     'Case 1 AMA', 'Case 2 AMA', 'Case 3 AMA'});
 set(gca,'FontSize',24);
 
-save2pdf('RMSEvsNEigVals/RMSEvsNFilters16.pdf',fig,600);
+save2pdf('RMSEvsNEigVals/RMSEvsNFilters16AMA.pdf',fig,600);
 
 %% Figure upto the 8th eigenvalue
 nEigVecs = 8;
 
 xlim([1 nEigVecs])
 
-save2pdf('RMSEvsNEigVals/RMSEvsNFilters8.pdf',fig,600);
[…]

### 2018-01-05 Draft2/draft2.tex
restrucutreing and editing

@@
 
-%% Figure 10
+%% Figure 9
 \begin{figure}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
         \caption{Luminance Estimates}
@@
     \caption{{\bf Receptive fields and luminance estimates.
-Case 1:} (a) First two receptive fields produced by the SVD method.
+Case 1:} (a) First two receptive fields produced by the AMA.
 Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right).
-(b) First two receptive fields produced by the AMA method.
-(c) The response of the stimuli to the first two AMA filters.
+(b) The response of the stimuli to the first two AMA filters.
 The responses are grouped with the label of the stimuli.
 As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance.
-(d) The estimates of the target object standard luminance.
+(c) The estimates of the target object standard luminance.
 The naive method produces the mean value of the target luminance used in the analysis.
@@
 
-%% Figure 11
+%% Figure 10
 \begin{figure}
 \centering
-\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
+\includegraphics[width=0.3\textwidth]{../Figures/Figure10/Figure10.pdf}
 \caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the luminance.}
@@
 \end{figure}
+% GET RID OF AMA FROM THE CAPTION
 
-% Figure 12
+% Figure 11
 \begin{figure}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
-        \caption{SVD First 2 RFs}
-        \label{fig:case10SVD}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_d.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.pdf}
         \caption{Luminance Estimates}
@@
 
-% Figure 13
+% Figure 12
 \begin{figure}
@@
     \begin{subfigure}[b]{0.27 \textwidth}   
-		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
-        \caption{SVD First 2 RFs}
-        \label{fig:case12SVD}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
         \caption{AMA First 2 RFs}
@@
         \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
         \caption{Luminance Estimates}
@@
 \subsection{The RFs of complex case generalize on simpler cases}
-% Figure 8
+% Figure 13
 \begin{figure}
@@
 \begin{subfigure}{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
-	\caption{Performance of methods}
-	\label{fig:summaryBarGraph}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+	\caption{Case 1}
+	\label{fig:case1Bar}
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
+    ~ 
     \begin{subfigure}{0.3 \textwidth}   
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
-	\caption{SVD RF Performance}
-	\label{fig:SVDBAR}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+	\caption{Case 2}
+	\label{fig:case2Bar}
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
+    ~ 
         \begin{subfigure}{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
-	\caption{AMA RF Performance}
-	\label{fig:AMABAR}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+	\caption{Case 3}
+	\label{fig:case3Bar}
     \end{subfigure}
-\caption{{\bf Model and Filter Performance:} (a) Comparison of various methods on luminance estimations for the three cases studied here.
-For simple spectral variations, like where only the target reflectance varies (case 1) or only the target and illumination spectrum varies (Case 2), the luminance can be estimated well.
-This is so, because the luminance information can be estimated simply from the light reflected of the target( case 1) or from the contrast between the target and the {\it fixed} background (case 2).
-For more complex case, where the luminance information is confounded due to variations in target, background and illuminant (case 3), the estimation has higher variability.
-(b) Performance of the SVD receptive fields obtained from one case on the stimuli of others.
-The RFs obtained from any one of the three cases perform well on the stimuli from case 1.
-The RF of the most complicated case (case 3), has good performance on the stimuli of lower complexity.
-(c) Same as Fig.\ref{fig:SVDBAR} for AMA RFs.}
+\caption{{\bf Model and Filter Performance:} Comparison of optimal AMA RFs from one case on the images of other cases.
+(a) RMSE of luminance estimates on images from the training set of case 1.
+Each bar represents RMSE of the filter obtained using the optimal RFs corresponding to the model.
+(b) (c)}
  \label{fig:barGraphs}

### 2018-01-06 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m
figures for case 1 and 2

@@ -17,7 +17,19 @@ if (~exist('filterResponse','dir'))
     mkdir('filterResponse');
 end
 
+%% Load AMA results struct
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case1.mat')
+plotFiltersJointResponsesModified(1,[1,2],case1Output.AMA.X,case1Output.AMA.s,case1Output.AMA.f,case1Output.AMA.ctgInd,[],[],[],[1:10])
+% save2pdf('filterResponse/case1FiltersResponse.pdf',gcf,600);
 
+%% Load AMA results struct
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case2.mat')
+plotFiltersJointResponsesModified(1,[1,2],case2Output.AMA.X,case2Output.AMA.s,case2Output.AMA.f,case2Output.AMA.ctgInd,[],[],[],[1:10])
+% save2pdf('filterResponse/case2FiltersResponse.pdf',gcf,600);
+
+%%
 % Load AMA results struct
 clear;
 load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9.mat')

### 2018-01-07 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m
no noise

@@ -19,10 +19,15 @@ end
 
 %% Load AMA results struct
 clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case1_NoIsomerizationNoise.mat')
+plotFiltersJointResponsesModified(1,[1,2],case1Output.AMA.X,case1Output.AMA.s,case1Output.AMA.f,case1Output.AMA.ctgInd,[],[],[],[1:10])
+% save2pdf('filterResponse/case1FiltersResponse_NoIsomerizationNoise.pdf',gcf,600);
+
+%% Load AMA results struct
+clear;
 load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case1.mat')
 plotFiltersJointResponsesModified(1,[1,2],case1Output.AMA.X,case1Output.AMA.s,case1Output.AMA.f,case1Output.AMA.ctgInd,[],[],[],[1:10])
 % save2pdf('filterResponse/case1FiltersResponse.pdf',gcf,600);
-
 %% Load AMA results struct
 clear;
 load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case2.mat')

### 2018-01-16 Draft2/draft2.tex
Today
small edits

@@
 
+% THINGS TO THINK ABOUT:
+%  1) Putting error bars on performance.  Particularly want to be sure that Fig 13 feature that Case 3 RFs do better than Case 1 RFs for Case 1 is just statistical sampling.
+%  2) What exactly do we want to run for final version.  How much illuminant intensity variation?  Should we make this match psychophysics so we could imagine these images displayed on a monitor?
+%  3) Do we just want to look at results for contrast normalized, or do we want to pick them off separately for isomerizations, contrast, and contrast normalized?
+%  4) What is driving the response variability in Case 1, where the stimulus is basically deterministic up to noise.
+There are three sources of noise: 1) Rendering noise, 2) Isomerization noise, 3) AMA noise introduced for some unknown reason, 4) Variation in target color.
+
+% WHAT STORY DO WE WANT TO TELL ABOUT THE RESULTS
+%  1) Case 0 -- work out effect of sources of internal noise - isomerization and AMA -- without any external "noise", where external "noise" is the effect of variability in object extrinsic scene factors (illumination, surrounding objects).
+%                      Also establish the rendering noise is einsy relative to whatever else we're doing.
+%  2) Move to Case 1 -- what happens when we introduce color variability into the target.
+This may not be of interest to the psychophysics, but none-the-less seems interesting to know as one ponders lightness constancy.
+%  3) On to Case 2 -- here the question is, do we keep varying target color, or do we fix target color and vary illumination?
+In any case, this isn't too hard a case if the other objects remain fixed, because then contrast coding basically normalizes out a lot of the variation, and it's only the spectral variation that might screw things up.
+But, that's why we run case 3.
+%  4) Do we run a case where the relative spectrum of the illuminant stays fixed and we only vary intensity?
+%  4) On to Case 3 --
 \section{Results} \label{Results}
+\begin{itemize}  
+\item Show the minimal model (to describe the sources and magnitude of error). This can go in supplement.
+\begin{itemize}  
+\item rendering error
+\item isomerization error
+\item ama error
+\end{itemize}
+\item Case 1. Only the target object color changes. AMA on isomerization
+\item Case 2. Background color changes too, AMA on isomerization
+\item Case 3. Background fixed, illuminant changes, AMA on isomerization fails, but the contrast version works
+\item Case 4. Change all three and show that both ismerization fails, constrast does better, but not perfectly better
+
+\end{itemize}
+
 \subsection{Optimal receptive fields for luminance estimation have a center surround structure}

### 2018-01-16 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m
more figures

@@ -17,6 +17,19 @@ if (~exist('filterResponse','dir'))
     mkdir('filterResponse');
 end
 
+
+%% Load AMA results struct
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10_AMAIsomerization.mat')
+plotFiltersJointResponsesModified(1,[1,2],case10Output.AMA.X,case10Output.AMA.s,case10Output.AMA.f,case10Output.AMA.ctgInd,[],[],[],[1:10])
+% save2pdf('filterResponse/case10FiltersResponse_AMAIsomerization.pdf',gcf,600);
+
+%% Load AMA results struct
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case1_NoIsomerizationNoise_AMAIsomerization.mat')
+plotFiltersJointResponsesModified(1,[1,2],case1Output.AMA.X,case1Output.AMA.s,case1Output.AMA.f,case1Output.AMA.ctgInd,[],[],[],[1:10])
+% save2pdf('filterResponse/case1FiltersResponse_NoIsomerizationNoise_AMAIsomerization.pdf',gcf,600);
+
 %% Load AMA results struct
 clear;
 load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case1_NoIsomerizationNoise_AMANoiseTenTimesLower.mat')

### 2018-01-16 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m
more edits

@@ -17,6 +17,11 @@ if (~exist('filterResponse','dir'))
     mkdir('filterResponse');
 end
 
+%% Load AMA results struct
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat')
+plotFiltersJointResponsesModified(1,[1,2],case9Output.AMA.X,case9Output.AMA.s,case9Output.AMA.f,case9Output.AMA.ctgInd,[],[],[],[1:10])
+% save2pdf('filterResponse/case9FiltersResponse_AMAIsomerization.pdf',gcf,600);
 
 %% Load AMA results struct
 clear;

### 2018-01-16 Draft2/draft2.tex
small edits
more edits

@@
 \item Case 1. Only the target object color changes. AMA on isomerization
-\item Case 2. Background color changes too, AMA on isomerization
+\item Case 2.
+Background color changes too, AMA on isomerization.
+(This is not giving good results.
+The filters are giving weights to the background which they should not.
+Maybe more samples would help.)
 \item Case 3. Background fixed, illuminant changes, AMA on isomerization fails, but the contrast version works
@@
 \end{itemize}
+
+%% Figure Results
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.33 \textwidth}   
+        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
+        \caption{Rendering noise}
+        \label{fig:renderingNoise}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.33 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingAndIsomerization.pdf}
+        \caption{Rendering and isomerization noise}
+        \label{fig:renderingAndIsomerization}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.33 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
+        \caption{Target color variation}
+        \label{fig:renderingIsomerizationTargetColor}
+    \end{subfigure}    
+    \caption{Different sources of noise}
+\label{fig:sourcesOfNoise}
+\end{figure}
 
@@
 \centering
-    \begin{subfigure}[b]{0.27 \textwidth}   
+    \begin{subfigure}[b]{0.4 \textwidth}   
         \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
@@
     \end{subfigure}
-        \begin{subfigure}[b]{0.20 \textwidth}
+        \begin{subfigure}[b]{0.27 \textwidth}
         \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
@@
     \end{subfigure}
-        \begin{subfigure}[b]{0.20 \textwidth}
+        \begin{subfigure}[b]{0.27 \textwidth}
         \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
@@
 \label{fig:case9AllResults}
+\end{figure}
+
+%% Figure Isomerization Fails
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.3	 \textwidth}   
+        \includegraphics[width=\textwidth]{../Figures/resultsFigure/isomerizationFails.pdf}
+        \caption{AMA on isomerization fails in case of variation in illuminant}
+        \label{fig:isomerizationFails}
+    \end{subfigure}
+    ~
+        \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/resultsFigure/constrastWorks.pdf}
+        \caption{Converting signal to contrast solves the problem}
+        \label{fig:constrastWorks}
+    \end{subfigure}
+    \caption{Need for contrast conversion.}
+\label{fig:importanceOfConstrast}
 \end{figure}

### 2018-01-27 Draft2/draft2.tex
edits

@@
 \item Case 4. Change all three and show that both ismerization fails, constrast does better, but not perfectly better
-
 \end{itemize}
 
+\subsection{In the absence of illuminant and background variation, object lightness can be estimated directly from the photoreceptor response}
+
+We used AMA to learn a set of linear receptive fields that are optimal for target object lightness estimation for images of case 1. 
+Fig. \ref{fig:renderingIsomerizationTargetColor} shows the projection of the photoreceptor response along the first two receptive fields. 
+Clearly, there exists a subspace along which the photoresponse response separates according to the luminance level assigned to the target object. 
+The target object luminance of the images in the test set can thus be obtained by projecting the corresponding photoreceptor response along these AMA receptive fields. 
+Fig.\ref{fig:case9Results} shows the estimated luminance for the test images in case 1 v/s the actual lightness assigned to the target object for AMA. 
+We also show the estimates of two null models: a naive method that assigns the average luminance across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object.
+As expected, in the absence of any external source of variation, the photoreceptor response is proportional to the luminance of the target object, and hence can be easily estimated by both AMA and linear regression.
+
+Each cloud in Fig.\ref{fig:renderingIsomerizationTargetColor} corresponds to the photoreceptor response to the images with target luminance level at a fixed value. 
+The variation within the cloud results due to the difference in shape of the target object reflectance spectra at the same luminance. 
+This variation dominates any variation coming from the noise in photoreceptor response or the noisy rendering of the images by the software. 
+Fig.\ref{fig:renderingAndIsomerization} shows the projection of photoreceptor response corresponding to 1000 images where, in addition to the illumination and background spectra, we also fixed the relative shape of the target object surface reflectance.
+Thus, for these images the target object had the same hue and chroma at all luminance levels.
+Any variation resulting from the poisson nature of the photoreceptor response or due the image rendering software is negligible, and can be ignored.
+(DO WE WANT TO GET AN ESTIMATE OF THE CLOUD SIZE FROM THE ALLOWED VARIATION IN THE SPECTRAL SHAPE?)
+
 %% Figure Results
@@
 \centering
-    \begin{subfigure}[b]{0.33 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
-        \caption{Rendering noise}
-        \label{fig:renderingNoise}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.33 \textwidth}
+        \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
+        \caption{Target color variation}
+        \label{fig:renderingIsomerizationTargetColor}
+    \end{subfigure}    
+%    \begin{subfigure}[b]{0.33 \textwidth}   
+ %       \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
+%        \caption{Rendering noise}
+%        \label{fig:renderingNoise}
+%    \end{subfigure}
+            \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
+        \caption{Luminance Estimates}
+        \label{fig:case9Results}
+    \end{subfigure}    
+        \begin{subfigure}[b]{0.3 \textwidth}
         \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingAndIsomerization.pdf}
@@
         \label{fig:renderingAndIsomerization}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
-        \caption{Target color variation}
-        \label{fig:renderingIsomerizationTargetColor}
     \end{subfigure}
@@
         \label{fig:case9FiltersResponse}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.27 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
-        \caption{Luminance Estimates}
-        \label{fig:case9Results}
     \end{subfigure}

### 2018-01-28 Draft2/draft2.tex
todays work

@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
         \caption{Target color variation}
@@
             \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
         \caption{Luminance Estimates}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingAndIsomerization.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
         \caption{Rendering and isomerization noise}
@@
 
-%% Figure 9
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.4 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
-        \caption{AMA First 2 RFs}
-        \label{fig:case9AMA}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.27 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
-        \caption{AMA RF Response}
-        \label{fig:case9FiltersResponse}
-    \end{subfigure}
-    \caption{{\bf Receptive fields and luminance estimates.
-Case 1:} (a) First two receptive fields produced by the AMA.
-Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right).
-(b) The response of the stimuli to the first two AMA filters.
-The responses are grouped with the label of the stimuli.
-As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance.
-(c) The estimates of the target object standard luminance.
-The naive method produces the mean value of the target luminance used in the analysis.
-The shaded region corresponds to 1 sigma standard deviation.}
-\label{fig:case9AllResults}
-\end{figure}
-
 %% Figure Isomerization Fails
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/constrastWorks.pdf}
+        \includegraphics[width=\textwidth]{../Figures/resultsFigure/contrastWorks.pdf}
         \caption{Converting signal to contrast solves the problem}
         \label{fig:constrastWorks}
+    \end{subfigure}
+            \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.pdf}
+        \caption{Luminance Estimates}
+        \label{fig:case10Results}
     \end{subfigure}

### 2018-01-28 codeForFigures/codeToMakeFigures/estimatesVsActualAMAOnly.m

@@ -13,10 +13,14 @@ if (~exist('estimatesVsActualAMA','dir'))
 end
 
 % Choose a case
-for caseNo = [ 9 10 12]
+for caseNo = [10]
 
 % load the files containing the estimates
-loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'.mat']);
+if (caseNo==9)
+    loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'_AMAIsomerization.mat']);
+else
+    loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'.mat']);
+end
 loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'.mat']);
 loadTheSVDFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SVD/case',num2str(caseNo),'.mat']);
 
@@ -35,9 +39,10 @@ lLinear = plot(unique(loadTheAMAFile.XTest)',loadTheLinearFile.cNormMeanEstimate
 % errorbar(unique(loadTheLinearFile.labelsTest)',loadTheLinearFile.cMeanSvdEstimateTest,loadTheLinearFile.cStdSvdEstimateTest,SVDColor,'linewidth',2);
 xlim([0.15 0.65]);
 ylim([0.15 0.65]);
-xlabel('$Y$','interpreter','latex');
-ylabel('$\hat{Y}$','interpreter','latex');
+xlabel('$Y$','interpreter','latex','FontSize',20);
+ylabel('$\hat{Y}$','interpreter','latex','FontSize',20);
 box on;
+set(gca,'FontSize',22)
 
 %% This part is for AMA SGD
 estimatedL = loadTheAMAFile.XHATi;
@@ -52,8 +57,8 @@ plotfillederror(linspace(0.2,0.6,10),loadTheLinearFile.cNormMeanEstimateTest-loa
 
 lDiagonal = plot([0.15 0.65],[0.15 0.65],'b--','linewidth',2);
 legend([lNaive, lLinear, lAMA, lDiagonal],...
[…]

### 2018-01-28 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m

@@ -21,19 +21,20 @@ end
 clear;
 load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat')
 plotFiltersJointResponsesModified(1,[1,2],case9Output.AMA.X,case9Output.AMA.s,case9Output.AMA.f,case9Output.AMA.ctgInd,[],[],[],[1:10])
-% save2pdf('filterResponse/case9FiltersResponse_AMAIsomerization.pdf',gcf,600);
+% save2pdf('/Users/vijaysingh_local/Documents/LightnessPaper/codeForFigures/codeToMakeFigures/filterResponse/case9FiltersResponse_AMAIsomerization.pdf',gcf,600);
 
 %% Load AMA results struct
 clear;
 load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10_AMAIsomerization.mat')
 plotFiltersJointResponsesModified(1,[1,2],case10Output.AMA.X,case10Output.AMA.s,case10Output.AMA.f,case10Output.AMA.ctgInd,[],[],[],[1:10])
-% save2pdf('filterResponse/case10FiltersResponse_AMAIsomerization.pdf',gcf,600);
+% save2pdf('/Users/vijaysingh_local/Documents/LightnessPaper/codeForFigures/codeToMakeFigures/filterResponse/case10FiltersResponse_AMAIsomerization.pdf',gcf,600);
 
 %% Load AMA results struct
 clear;
-load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case1_NoIsomerizationNoise_AMAIsomerization.mat')
-plotFiltersJointResponsesModified(1,[1,2],case1Output.AMA.X,case1Output.AMA.s,case1Output.AMA.f,case1Output.AMA.ctgInd,[],[],[],[1:10])
-% save2pdf('filterResponse/case1FiltersResponse_NoIsomerizationNoise_AMAIsomerization.pdf',gcf,600);
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case1_AMAIsomerization.mat')
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat')
[…]

### 2018-01-29 codeForFigures/codeToMakeFigures/estimatesVsActualAMAOnly.m
more edits

@@ -13,7 +13,7 @@ if (~exist('estimatesVsActualAMA','dir'))
 end
 
 % Choose a case
-for caseNo = [10]
+for caseNo = [12]
 
 % load the files containing the estimates
 if (caseNo==9)

### 2018-01-29 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m

@@ -80,7 +80,7 @@ plotFiltersJointResponsesModified(1,[1,2],case10Output.AMA.X,case10Output.AMA.s,
 clear;
 load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12.mat')
 plotFiltersJointResponsesModified(1,[1,2],case12Output.AMA.X,case12Output.AMA.s,case12Output.AMA.f,case12Output.AMA.ctgInd,[],[],[],[1:10]);
-% save2pdf('filterResponse/case12FiltersResponseNoLegend.pdf',gcf,600);
+% save2pdf('/Users/vijaysingh_local/Documents/LightnessPaper/codeForFigures/codeToMakeFigures/filterResponse/case12FiltersResponseNoLegend.pdf',gcf,600);
 %% Plot SVD Filter Response
 % Load SVD results struct
 clear;

### 2018-01-29 codeForFigures/codeToMakeFigures/plotFiltersJointResponsesModified.m

@@ -68,7 +68,7 @@ for t = 1:size(fPairs,1)
         if bPLOTellipse
             h(c) = plotEllipse(MU(ctg2plt(c),:),COV(:,:,ctg2plt(c)),90,fPairs(t,:),2,colors(ctg2plt(c),:));
             legendIndicator(c) = h(c);
-            legendName{c} = num2str(X(c),4);
+            legendName{c} = num2str(X(c),2);
         end
         % SCATTER PLOT RESPONSES
         if bPltRsp, 
@@ -106,7 +106,7 @@ end
 set(gca,'FontSize',22)
 xlabel(['RF' num2str(fPairs(t,1)) ' response'],'FontSize',26);
 ylabel(['RF' num2str(fPairs(t,2)) ' response'],'FontSize',26);
-legend(legendIndicator,legendName,'Location','southwest');
+legend(legendIndicator,legendName,'Location','southwest','FontSize',18);
 
 % try   legend(h,legendLabel('Y = ', X(ctg2plt),1,4),'Location','NorthEast');
 % catch legend(legendLabel('X=',X(ctg2plt),1,4),'Location','NorthEast');

### 2018-01-29 Draft2/draft2.tex
more edits
lost of edits

--- 2018-01-16 Draft2/draft2.tex
@@
 \item Case 4. Change all three and show that both ismerization fails, constrast does better, but not perfectly better
-
 \end{itemize}
 
-%% Figure Results
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.33 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
-        \caption{Rendering noise}
-        \label{fig:renderingNoise}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingAndIsomerization.pdf}
-        \caption{Rendering and isomerization noise}
-        \label{fig:renderingAndIsomerization}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingIsomerizationTargetColor.pdf}
-        \caption{Target color variation}
-        \label{fig:renderingIsomerizationTargetColor}
-    \end{subfigure}    
-    \caption{Different sources of noise}
+\subsection{Case 1: Target luminance can be estimated directly from the photoreceptor response}
+We used AMA to learn a set of linear receptive fields that are optimal for estimating target object luminance using stimuli in the training set of case 1. 
+Fig.~\ref{fig:case1RFResponse} shows the projection of the photoreceptor response along the first two AMA receptive fields. 
+Clearly, there exists a subspace along which the photoreceptor response separates according to the luminance level assigned to the target object. 
+Thus, the target object luminance can be obtained by projecting photoreceptor responses along these AMA receptive fields. 
+Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test images in case 1. 
+We show the estimates obtained by AMA and two null models: a naive method that assigns the average target object luminance across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object (see Methods).
+As expected, in the absence of any external source of variation, the photoreceptor response is proportional to the luminance of the target object, and hence can be easily estimated by both AMA and linear regression.
+
+Each cloud in Fig.~\ref{fig:case1RFResponse} corresponds to the photoreceptor response to the images with target luminance level at a fixed value. 
+The variation within the cloud, between images that have the target object at same luminance values, results due to the difference in the relative shape of the target object reflectance spectra (difference in hue and saturation).
+The resulting variation dominates any variation coming from the noise in photoreceptor response or the noisy rendering of the images by the software.
+Fig.~\ref{fig:case0RFResponse} shows the projection of photoreceptor response corresponding to 1000 images where, in addition to the illumination and background spectra, we also fixed the relative shape of the target object surface reflectance.
+Any variation resulting from the poisson nature of the photoreceptor response or due the image rendering software is negligible, and can be ignored.
+
+(DO WE WANT TO GET AN ESTIMATE OF THE CLOUD SIZE FROM THE ALLOWED VARIATION IN THE SPECTRAL SHAPE?)
+
+%% Figure 9
+\begin{figure}
+\centering
+        \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
+        \caption{RF response Case 1}
+        \label{fig:case1RFResponse}
+    \end{subfigure}    
+%    \begin{subfigure}[b]{0.33 \textwidth}   
+ %       \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
+%        \caption{Rendering noise}
+%        \label{fig:renderingNoise}
+%    \end{subfigure}
+            \begin{subfigure}[b]{0.297 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
+        \caption{Luminance Estimates}
+        \label{fig:case9Results}
+    \end{subfigure}    
+        \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
+        \caption{Images with fixed relative spectrum}
+        \label{fig:case0RFResponse}
+    \end{subfigure}
+    \caption{{\bf Case 1: RF response and luminance estimates:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of case 1.
+We show the response for the images in the training set.
+Each response cloud represents the response of images corresponding to one luminance level.
+The response clouds are approximated by a multinormal Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
+(b) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA.
+The estimates fall along the diagonal unit slope line for both linear regression and AMA.
+The standard deviations are too small to be visible.
+(c) Photoreceptor response for images with fixed relative shape of the target object reflectance spectrum projected along the first two case 1 AMA receptive fields.
+The variation coming from the poisson nature of the photoreceptor isomerization is small compared to the variation due to shape of target object reflectance spectrum.}
 \label{fig:sourcesOfNoise}
 \end{figure}
+
+\subsection{Case 1a: This will be the case of background variation with fixed luminance}
+
+\subsection{Case 2: Luminance can be estimated from contrast between target and background}
+The AMA receptive fields learnt using the photoreceptor response does a very poor job in predicting the target object luminance (Fig.~\ref{fig:isomerizationFails}) for images of case 2. 
+This is because, since the illuminant spectra varies in this case, the photoreceptor response is not directly proportional to the target object surface anymore. 
+But, since the background surfaces are fixed in this case, the ratio between the response of  photoreceptors corresponding to the target object and the background remains proportional to the target object luminance.
+This is because a change in illuminant spectra produces the same effect in both the target object and the background object. 
+Thus, the AMA receptive fields learnt on the contrast normalized photoreceptor response (see Methods) can be used to predicts the target object luminance (Fig.~\ref{fig:constrastWorks}). 
+Fig.~\ref{fig:case10Results} shows the estimated target object luminance v/s the assigned luminance for the images in case 2 obtained using the contrast normalized representation. 
+AMA receptive fields provide excellent predictions of the target object luminance. 
+The predictions are much better compared to that of a linear model that only considers the (contrast normalized) response of the photoreceptors corresponding to the center pixel of the target object.
+
+%% Figure Isomerization Fails
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.3	 \textwidth}   
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.pdf}
+        \caption{RFs learnt using photoreceptor response}
+        \label{fig:isomerizationFails}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.pdf}
+        \caption{RFs learnt using contrast signal}
+        \label{fig:constrastWorks}
+    \end{subfigure}
+            \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.pdf}
+        \caption{Luminance estimates}
+        \label{fig:case10Results}
+    \end{subfigure}
+    \caption{{\bf Case 2: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
+(b) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
+The receptive fields were calculated using the contrast normalized stimuli.
+The response at each luminance level separates much better in this representation.
+(c) Estimated v/s assigned target object luminance for the image in case 2.
+Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
+AMA estimates are much better compared to the null models.}
+\label{fig:importanceOfConstrast}
+\end{figure}
+
+While, the projection along the first two receptive fields shows an overlap between the stimuli at higher luminance values (Fig.~\ref{fig:constrastWorks}), the stimuli are better separated if the projection is considered within a subspace that has more receptive fields.
+Fig.~\ref{fig:RMSEvsNFilters} shows the relative error (Methods) of estimates as a function of the of the number of receptive fields considered for luminance estimation for the cases considered in this work.
+As expected, relative error reduces with increasing number of receptive fields.
+
+%% Figure 11
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
+\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the luminance.}
+\label{fig:RMSEvsNFilters}
+\end{figure}
+% GET RID OF AMA FROM THE CAPTION
+
+\subsection{Case 3}
+% Figure 12
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.3 \textwidth}   
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
+        \caption{AMA RF Response}
+        \label{fig:case12FiltersResponse}
+    \end{subfigure}    
+        \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
+        \caption{Luminance Estimates}
+        \label{fig:case12Results}
+    \end{subfigure}
+    \caption{{\bf Case 3:} (a) Contrast normalized photoreceptor response projected along the first two AMA receptive fields.
+(b) Target object luminance estimates v/s assigned luminance for images in case 3.
+The AMA estimates are unbiased and have smaller relative error compared to linear model.}
+    \label{fig:case12AllResults}
+\end{figure}
+
+Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 3. 
+We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:RMSEvsNFilters}). 
+The AMA receptive fields do an excellent job of predicting the target object luminance.
+The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}).
+The relative error of estimation is ~17\%, which low compared to that of the naive model (~42\%) or the linear model on center pixel (~21\%).
 
@@
 
-%% Figure 9
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.4 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
-        \caption{AMA First 2 RFs}
-        \label{fig:case9AMA}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.27 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
-        \caption{AMA RF Response}
-        \label{fig:case9FiltersResponse}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.27 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
-        \caption{Luminance Estimates}
-        \label{fig:case9Results}
-    \end{subfigure}    
-    \caption{{\bf Receptive fields and luminance estimates.
-Case 1:} (a) First two receptive fields produced by the AMA.
-Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right).
-(b) The response of the stimuli to the first two AMA filters.
-The responses are grouped with the label of the stimuli.
-As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance.
-(c) The estimates of the target object standard luminance.
-The naive method produces the mean value of the target luminance used in the analysis.
-The shaded region corresponds to 1 sigma standard deviation.}
-\label{fig:case9AllResults}
-\end{figure}
-
-%% Figure Isomerization Fails
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.3	 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/isomerizationFails.pdf}
-        \caption{AMA on isomerization fails in case of variation in illuminant}
-        \label{fig:isomerizationFails}
+\subsection{The RFs of complex case generalize on simpler cases}
+Fig.~\ref{fig:barGraphs} shows the relative error for the estimates of the target object luminance obtained using the linear model and AMA.
+We show the relative error of the estimates obtained using the AMA receptive fields from all cases.
+The receptive fields from a more complex case perform at par on the stimuli from a simpler case.
+The optimal AMA estimates are better than that of the linear model.
+
+% Figure 13
+\begin{figure}
+\centering
+\begin{subfigure}{0.3 \textwidth}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+	\caption{Case 1}
+	\label{fig:case1Bar}
     \end{subfigure}
     ~ 
-        \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/resultsFigure/constrastWorks.pdf}
-        \caption{Converting signal to contrast solves the problem}
-        \label{fig:constrastWorks}
-    \end{subfigure}
-    \caption{Need for contrast conversion.}
-\label{fig:importanceOfConstrast}
-\end{figure}
-
-%% Figure 10
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{../Figures/Figure10/Figure10.pdf}
-\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the luminance.}
-\label{fig:RMSEvsNFilters}
-\end{figure}
-% GET RID OF AMA FROM THE CAPTION
-
-% Figure 11
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.pdf}
-        \caption{AMA First 2 RFs}
-        \label{fig:case10AMA}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.pdf}
-        \caption{AMA RF Response}
-        \label{fig:case10FiltersResponse}
-    \end{subfigure}    
-        \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.pdf}
-        \caption{Luminance Estimates}
-        \label{fig:case10Results}
-    \end{subfigure}
-    \caption{{\bf Receptive fields and luminance estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
-    \label{fig:case10AllResults}
-\end{figure}
-
-% Figure 12
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
-        \caption{AMA First 2 RFs}
-        \label{fig:case12AMA}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
-        \caption{AMA RF Response}
-        \label{fig:case12FiltersResponse}
-    \end{subfigure}    
-        \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
-        \caption{Luminance Estimates}
-        \label{fig:case12Results}
-    \end{subfigure}
-    \caption{{\bf Receptive fields and luminance estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
-    \label{fig:case12AllResults}
+    \begin{subfigure}{0.3 \textwidth}   
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+	\caption{Case 2}
+	\label{fig:case2Bar}
+    \end{subfigure}
+    ~ 
+        \begin{subfigure}{0.3 \textwidth}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+	\caption{Case 3}
+	\label{fig:case3Bar}
+    \end{subfigure}
+\caption{{\bf Error comparison across models:} Comparison of optimal AMA receptive fields from one case on the images of other cases.
+(a) Relative error of the estimates obtained using the linear model and AMA.
+The AMA receptive fields of case 1, 2 and 3 are used to estimate the target object luminance of the test images from case 1.
+The AMA receptive fields from all three cases perform well in this case.
+(b) Relative error for images of case 2.
+As expected, the error of the linear model on the center pixel is higher than AMA.
+AMA receptive fields from case 1 do worse than the receptive fields from case 2 and 3.
+(c) Relative error for images of case 3.
+The best predictions are from the receptive learnt using the images of case 3.}
+ \label{fig:barGraphs}
 \end{figure}
@@
 This shows the importance of context information for luminance estimation.
-
-\subsection{The RFs of complex case generalize on simpler cases}
-% Figure 13
-\begin{figure}
-\centering
-\begin{subfigure}{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
-	\caption{Case 1}
-	\label{fig:case1Bar}
-    \end{subfigure}
-    ~ 
-    \begin{subfigure}{0.3 \textwidth}   
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
-	\caption{Case 2}
-	\label{fig:case2Bar}
-    \end{subfigure}
-    ~ 
-        \begin{subfigure}{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
-	\caption{Case 3}
-	\label{fig:case3Bar}
-    \end{subfigure}
-\caption{{\bf Model and Filter Performance:} Comparison of optimal AMA RFs from one case on the images of other cases.
-(a) RMSE of luminance estimates on images from the training set of case 1.
-Each bar represents RMSE of the filter obtained using the optimal RFs corresponding to the model.
-(b) (c)}
- \label{fig:barGraphs}
-\end{figure}
-Fig.~\ref{fig:SVDBAR} and Fig~\ref{fig:AMABAR} show the performance of the receptive fields learnt using the stimuli of one case on the stimuli of other cases.
-The RFs of case 3, (the most complex case) perform well on stimuli of case 1 and case 2.
-Similarly, the RFs of case 2 performs well on the stimuli of case 1.
-Thus, the receptive fields leant on the complex case generalize for luminance estimation of stimuli for simpler cases.
 

### 2018-02-06 Draft2/draft2.tex
added the 4th case

@@
 (b) {\bf Luminance Constancy Under Spectral Variations:} In this paper we consider the special case of luminance constancy.
-Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance.
+Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance (indicated on the left).
 Within each row, the surface reflectance of the spheres has the same luminance, when illuminated by a standard reference illuminant, CIE D65.
@@
 		\includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_a.jpeg}
-		\caption{Case 1}
- 		\label{fig:targetVarying}
+		\caption{Case 2}
+ 		\label{fig:backgroundVarying}
 	\end{subfigure}
@@
         \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_b.jpeg}
-        \caption{Case 2}
+        \caption{Case 3}
         \label{fig:targetIlluminantVarying}
@@
         \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_c.jpeg}
-        \caption{Case 3}
+        \caption{Case 4}
         \label{fig:allSpectraVarying}
@@
 5 images are shown at each luminance level.
-We studied three types of spectral variations.
-(a) Case 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed, (b) Case 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Case 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
-This panel is reproduced from \ref{fig:introExampleFigure}.
+We studied four types of spectral variations.
+Case 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed, (Fig.~\ref{fig:introExampleFigure}).
+(a) Case 2: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable, (b) Case 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Case 4: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
 As in \ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
@@
 Even within the special case of luminance constancy, there are many scene manipulations that could be considered.
-The set of manipulations we focus on here are illustrated by the three panels of Fig.~\ref{fig:studiedCases}.
+The set of manipulations we focus on here are illustrated by Fig.~\ref{fig:introExampleFigure} and the three panels of Fig.~\ref{fig:studiedCases}.
 These cases are: 1.
-variation in target object spectrum with fixed light source and background objects spectra (Fig.~\ref{fig:targetVarying}), 2.
+variation in target object spectrum with fixed light source and background objects spectra (Fig.~\ref{fig:introExampleFigure}), 2.
+variation in target object spectrum and background objects spectra, with fixed light source  (Fig.~\ref{fig:backgroundVarying}), 3.
 variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.~\ref{fig:targetIlluminantVarying}), and 3.
@@
 We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (case 1), object luminance can be recovered directly from the light reflected off the target object.
-For case 2, where both the target object reflectance and light source spectra vary, object luminance can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 3), the standard luminance can not be recovered simply from the cone response or the contrast.
+For variations only in target object reflectance spectra (case 1) or just the target and background objects reflectance spectra (case 2), object luminance can be recovered directly from the light reflected off the target object.
+For case 3, where both the target object reflectance and light source spectra vary, object luminance can be recovered from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (case 4), the standard luminance can not be recovered simply from the cone response or the contrast.
 We have used AMA with a Bayesian estimator to estimate standard luminance of the target object.

### 2018-02-06 codeForFigures/codeToMakeFigures/estimatesVsActualAMAOnly.m
added more figures

@@ -13,16 +13,17 @@ if (~exist('estimatesVsActualAMA','dir'))
 end
 
 % Choose a case
-for caseNo = [12]
+for caseNo = [9]
 
 % load the files containing the estimates
-if (caseNo==9)
+if (caseNo==9 || caseNo==11)
     loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'_AMAIsomerization.mat']);
+    loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'_AMAIsomerization.mat']);
 else
     loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'.mat']);
+    loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'.mat']);
 end
-loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'.mat']);
-loadTheSVDFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SVD/case',num2str(caseNo),'.mat']);
+% loadTheSVDFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SVD/case',num2str(caseNo),'.mat']);
 
 % Define the colors to be used for each method
 naiveColor  = 'g';

### 2018-02-06 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m

@@ -19,13 +19,19 @@ end
 
 %% Load AMA results struct
 clear;
-load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat')
-plotFiltersJointResponsesModified(1,[1,2],case9Output.AMA.X,case9Output.AMA.s,case9Output.AMA.f,case9Output.AMA.ctgInd,[],[],[],[1:10])
-% save2pdf('/Users/vijaysingh_local/Documents/LightnessPaper/codeForFigures/codeToMakeFigures/filterResponse/case9FiltersResponse_AMAIsomerization.pdf',gcf,600);
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case11_AMAIsomerization.mat')
+plotFiltersJointResponsesModified(1,[1,2],case11Output.AMA.X,case11Output.AMA.s,case11Output.AMA.f,case11Output.AMA.ctgInd,[],[],[],[1:10])
+% save2pdf('/Users/vijaysingh_local/Documents/LightnessPaper/codeForFigures/codeToMakeFigures/filterResponse/case11FiltersResponse_AMAIsomerization.pdf',gcf,600);
 
 %% Load AMA results struct
 clear;
-load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10_AMAIsomerization.mat')
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat')
+plotFiltersJointResponsesModified(1,[1,2],case9Output.AMA.X,case9Output.AMA.s,case9Output.AMA.f,case9Output.AMA.ctgInd,[],[],[],[1:10])
+% Case11_AMAIsomerization
+
+%% Load AMA results struct
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10_contrast.mat')
 plotFiltersJointResponsesModified(1,[1,2],case10Output.AMA.X,case10Output.AMA.s,case10Output.AMA.f,case10Output.AMA.ctgInd,[],[],[],[1:10])
 % save2pdf('/Users/vijaysingh_local/Documents/LightnessPaper/codeForFigures/codeToMakeFigures/filterResponse/case10FiltersResponse_AMAIsomerization.pdf',gcf,600);
 

### 2018-02-06 codeForFigures/codeToMakeFigures/plotBarGraphsAMAOnly.m

@@ -11,42 +11,46 @@
 % Load the results for all cases
 % SVD Results
 clear;
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case9SVDResults.mat']);
-results9SVD = results.case9Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case10SVDResults.mat']);
-results10SVD = results.case10Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12SVDResults.mat']);
-results12SVD = results.case12Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12RotatedSVDResults.mat']);
-results12RSVD = results.case12Rotated;
+% results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case9SVDResults.mat']);
+% results9SVD = results.case9Output;
+% 
+% results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case10SVDResults.mat']);
+% results10SVD = results.case10Output;
+% 
+% results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12SVDResults.mat']);
+% results12SVD = results.case12Output;
+% 
+% results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12RotatedSVDResults.mat']);
+% results12RSVD = results.case12Rotated;
 
 % AMA Results
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9.mat']);
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD2/Case9.mat']);
 results9AMA = results.case9Output;
 
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10.mat']);
[…]

### 2018-02-06 codeForFigures/codeToMakeFigures/plotRMSEvsEigValSVD.m

@@ -19,11 +19,14 @@ results12SVD = results.case12Output;
 results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12RotatedSVDResults.mat']);
 results12RSVD = results.case12Rotated;
 
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9.mat']);
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat']);
 results9AMA = results.case9Output;
 
 results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10.mat']);
 results10AMA = results.case10Output;
+
+results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case11_AMAIsomerization.mat']);
+results11AMA = results.case11Output;
 
 results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12.mat']);
 results12AMA = results.case12Output;
@@ -43,6 +46,7 @@ color10SVD = '--b';
 color12SVD = '--r';
 color9AMA  = 'k';
 color10AMA = 'b';
+color11AMA = 'g';
 color12AMA = 'r';
 
 % Plot the contrast estimates
@@ -58,20 +62,22 @@ nEigVecs = 16;
 % l12SVD = plot([1:nEigVecs],results12SVD.Case12error(1:nEigVecs),color12SVD,'linewidth',2);
 
 % AMA Results
-l9AMA = plot([1:nEigVecs],results9AMA.error(1:nEigVecs),color9AMA,'linewidth',2);
+l9AMA = plot([1:8],results9AMA.error(1:8),color9AMA,'linewidth',2);
+l11AMA = plot([1:12],results11AMA.error(1:12),color11AMA,'linewidth',2);
 l10AMA = plot([1:nEigVecs],results10AMA.error(1:nEigVecs),color10AMA,'linewidth',2);
 l12AMA = plot([1:nEigVecs],results12AMA.error(1:nEigVecs),color12AMA,'linewidth',2);
 
 xlim([1 nEigVecs])
-xlabel('N RFs Used');
-ylabel('E_{rel}');
[…]

### 2018-02-06 Draft2/draft2.tex
added more figures
more edits

@@
 Next, we simulate the response of the retinal cones to these multispectral images using an accurate model of the early visual system.
-Using supervised learning methods on these labeled cone response, we identify the computations that lead to accurate luminance estimation.
+We then use supervised learning methods on these labeled cone response to identify the computations that lead to accurate luminance estimation.
 We show that if only either target, or background, or illumination spectra are allowed to vary, the standard luminance can be estimated through simple transformations of the cone responses.
@@
 Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
-\citeNP{LandRetinex}) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
+\citeNP{LandRetinex}) or produce explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
 An important insight of this line of research was that, to account for variation in illumination, it was necessary to consider the light reflected from the entire scene.
@@
 Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance (indicated on the left).
-Within each row, the surface reflectance of the spheres has the same luminance, when illuminated by a standard reference illuminant, CIE D65.
+Within each row, the surface reflectance of the spheres has the same luminance when illuminated by a standard reference illuminant, CIE D65.
 The three rows differ in this value, as can be seen by the fact that the luminance of the spheres generally decreases as we move down the columns.
@@
 Geisler and colleagues, for example, have developed a technique they refer to as accuracy maximization analysis (AMA, \citeNP{geisler2009optimal}), which learns linear filters whose output carries information that is optimized for particular perceptual tasks.
-This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus \cite{burge2011optimal} and disparity \cite{burge2014optimal} from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
+This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus \cite{burge2011optimal} and disparity \cite{burge2014optimal}
+% JOHANNES ARE THERE ANY OTHER PAPERS YOU WOULD LIKE TO CITE
+from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
 In this paper, we apply AMA, as well as comparison supervised learning algorithms to a special case of the color constancy problem (luminance constancy) and evaluate how well it performs for naturalistic image input.
@@
     \end{subfigure}    
-    \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of multispectral images similar to ones studied in our work.
+    \caption{{\bf Types of spectral variations studied in this work:} sRGB rendition of multispectral images similar to ones studied in our work.
 The numbers on the left indicate the standard luminance level of the target object.
@@
 As in \ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
-Moreover, across the three panels of this figure, spheres in corresponding locations have the same surface reflectance.
-In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+Moreover, across the four panels (Fig.~\ref{fig:introExampleFigure} \& Fig.~\ref{fig:studiedCases}), spheres in corresponding locations have the same surface reflectance.
+In all four panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
 The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
@@
 In the \nameref{Methods} section, we describe in detail the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}) using our software pipeline {\rm Virtual world color constancy}, the process to simulate the response of retinal cone photoreceptors to these images using a standard model of the early visual system (\nameref{method:Isetbio}) and the supervised learning method (AMA) used in our analysis (\nameref{method:SupervisedLearning}).
-In the \nameref{Results} section, we show the estimates and performance of the supervised methods for the three cases mentioned above.
+In the \nameref{Results} section, we show the estimates and performance of the supervised methods for the four cases mentioned above.
 We conclude the paper with the implication of our results in the \nameref{Discussion} section.
@@
 The second is how we model the transformations applied by the early visual system to generate modeled responses of the cone photoreceptor mosaic.
-The third is the details of the supervised learning method (AMA) we apply to the labelled training data.
-And the fourth is how we evaluate the performance of the algorithms.
+The third is the details of the supervised learning method (AMA) that we apply to the labelled training data.
+And the fourth is how we evaluate the performance of the algorithm.
 We describe each of these in the sections below.
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
+    ~
     \begin{subfigure}[b]{0.22 \textwidth}
@@
     \end{subfigure}    
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
+    ~
     \begin{subfigure}[b]{0.22 \textwidth}
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
+    ~ 
 \begin{subfigure}[b]{0.14 \textwidth}
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
+    ~ 
     \begin{subfigure}[b]{0.14 \textwidth}
@@
 We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene.
-Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).
+Tame base scenes may also be created {\it de novo} using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).
 The overall spatial scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness.
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
+    ~
     \begin{subfigure}[b]{0.18 \textwidth}
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
+    ~
     \begin{subfigure}[b]{0.18 \textwidth}
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
+    ~
 	\begin{subfigure}[b]{0.18 \textwidth}
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
+    ~
     \caption{{\bf Transformations of the scene.} The possible transformations of the properties of a scene can broadly be classified into two groups: Spectral (a-c) and Geometrical (d-e).
@@
 Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene.
-The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:studiedCases}).
+The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:introExampleFigure} \& Fig.~\ref{fig:studiedCases}).
 2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel.
@@
 The dotted line at 0.9 on the y-axis is for reference.
-We used the first six eigenvectors in our analysis.
-(e) CIE xy chromaticity plot of the rescaled dataset (Fig.~\ref{fig:rescaledGranada}) and randomly generated samples from Fig.~\ref{fig:randomIlluminant}.
-(f) sRGB renditions of the random illuminant samples shown in \ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
+We used the eigenvectors corresponding to the first six eigenvalues in our analysis.
+(e) CIE xy chromaticity plot of the rescaled dataset (in Fig.~\ref{fig:rescaledGranada}) and randomly generated samples from Fig.~\ref{fig:randomIlluminant}.
+(f) sRGB renditions of the random illuminant samples shown in Fig.~\ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
 \end{figure}
@@
 by taking the sample mean over all rescaled spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
-The resulting mean subtracted dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$
+The resulting mean centered dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$
 was decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
@@
 We used the basis vectors corresponding to
-the largest six SVD eigenvalues, so that $\{j \in [16]\}$.
+the largest six SVD eigenvalues, so that $\{j \in [1,6]\}$.
 For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance (Fig.~\ref{fig:granadaEV}).
@@
 This spectrum can sometimes have values that are less than zero.  In such cases, the weights are discarded and a new draw obtained, until
-the condition $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, for all $\lambda$, is satisifed.
+the condition $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, is satisfied for all $\lambda$.
 The random illuminant spectrum is then given as
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
+    ~ 
     \begin{subfigure}[b]{0.19 \textwidth}   
@@
     \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
+    ~ 
     \begin{subfigure}[b]{0.19 \textwidth}
@@
 The three $51 \times 51$ sets of cone responses corresponding to the L, M and S cones were then reshaped into a single $7803 \times 1$ vector ($7803 = 51 \times 51 \times 3$).
-To model the contrast coding and contrast adaptation, we convert this vector to a contrast representation by subtracting out the mean and then dividing by it (contrast coding), followed by normalizing the vector to have unit length (contrast normalization).
+For case 1 and 3 we used this as the input for the supervised methods.
+For case 3 and 4, to model the contrast coding and contrast adaptation, we convert this vector to a contrast representation by subtracting out the mean and then dividing by it (contrast coding), followed by normalizing the vector to have unit length (contrast normalization).
 The cone-response vectors corresponding to the N images for each case are concatenated column-wise to form a contrast normalized matrix $C_{7803\times N}$.
@@
 \subsubsection*{Linear Regression} For linear regression, we solve the equation $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
-Here, $C_{3\times N}$ is a matrix containing the contrast normalized L, M and S cone responses of the central patch of each image, extracted from $C_{7803\times N}$.
+Here, $C_{3\times N}$ is a matrix containing either the L, M and S cone responses (for case 1 and 2) or contrast normalized responses (for case 3 and 4) of the central patch of each image, extracted from $C_{7803\times N}$.
 The columns corresponds to the N images in the dataset.
@@
 AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
-Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task.
+When provided with a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task.
 The task is implicitly defined in terms of the labels.
@@
 In our analysis, it means that the luminance level of the target object in an image can take one of the possible $N_{\nu}$ values ($\{Y_k: k\in[1,N_{\nu}] \}$).
-We represent the $l$'th image corresponding to the $k$'th category of the labels as $s_{kl}$.
+We represent the $l$'th image corresponding to the $k$'th label as $s_{kl}$.
 Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
 Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the label ($Y_k$) corresponding to the stimuli $s_{kl}$ as $\hat{Y}_{kl}$.
-Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and a mean cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.
+Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and an avearge cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.
 
@@
 %  4) On to Case 3 --
+
 \section{Results} \label{Results}
-\begin{itemize}
-\item Show the minimal model (to describe the sources and magnitude of error). This can go in supplement.
-\begin{itemize}  
-\item rendering error
-\item isomerization error
-\item ama error
-\end{itemize}
-\item Case 1. Only the target object color changes. AMA on isomerization
-\item Case 2.
-Background color changes too, AMA on isomerization.
-(This is not giving good results.
-The filters are giving weights to the background which they should not.
-Maybe more samples would help.)
-\item Case 3. Background fixed, illuminant changes, AMA on isomerization fails, but the contrast version works
-\item Case 4. Change all three and show that both ismerization fails, constrast does better, but not perfectly better
-\end{itemize}
-
 \subsection{Case 1: Target luminance can be estimated directly from the photoreceptor response}
@@
 Fig.~\ref{fig:case0RFResponse} shows the projection of photoreceptor response corresponding to 1000 images where, in addition to the illumination and background spectra, we also fixed the relative shape of the target object surface reflectance.
-Any variation resulting from the poisson nature of the photoreceptor response or due the image rendering software is negligible, and can be ignored.
-
-(DO WE WANT TO GET AN ESTIMATE OF THE CLOUD SIZE FROM THE ALLOWED VARIATION IN THE SPECTRAL SHAPE?)
+The variation resulting from the poisson nature of the photoreceptor response or due the image rendering software is small and can be ignored.
 
@@
 
-\subsection{Case 1a: This will be the case of background variation with fixed luminance}
-
-\subsection{Case 2: Luminance can be estimated from contrast between target and background}
-The AMA receptive fields learnt using the photoreceptor response does a very poor job in predicting the target object luminance (Fig.~\ref{fig:isomerizationFails}) for images of case 2. 
+\subsection{Case 2}
+Fig.~{\ref{fig:case2RFResponse}} shows the projection of the photoreceptor response for case 2 along the first two AMA receptive fields.
+The naive expectation would be that variations in background objects surface reflectance would have minimal effect on the isomerizations of the cones corresponding to the target object.
+Hence, the luminance can be estimated directly from the isomerization of these cones.
+But projection of the cone response along the AMA RFs shows that the background variation has significant effect on the cone isomerizations.
+The response clouds at different luminance levels along the first two receptive fields do not separate as well compared to case 1.
+The overlap is lower if the projection is considered in subspaces that have more AMA receptive fields.
+Fig.~\ref{fig:ErrorVsNFilters} shows the relative error of luminance estimate as a function of the number of AMA receptive fields used for luminance estimation.
+As expected, the relative error decreases with the number of receptive fields and converges to the minimum value around 8 receptive fields.
+Fig.~\ref{fig:case2Estimates} shows the luminance estimates for the learning methods used in this work.
+The mean estimates fall along the diagonal x=y line.
+The variance in the estimates increases with assigned luminance.
+This is because the isomerization noise is directly proportional to the light reflected from the target object and is higher at higher values of the target object luminance.
+
+%% Figure Case 2
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.3	 \textwidth}   
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.pdf}
+        \caption{RF response Case 2}
+        \label{fig:case2RFResponse}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.pdf}
+        \caption{Luminance Estimates}
+        \label{fig:case2Estimates}
+    \end{subfigure}
+            \begin{subfigure}[b]{0.3 \textwidth}
+        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.pdf}
+        \caption{Error v/s number of RFs}
+        \label{fig:ErrorVsNFilters}
+    \end{subfigure}
+    \caption{{\bf Case 2:} (a) Photoreceptor response projected along the first two AMA receptive fields.
+(b) Estimated v/s assigned target object luminance for the image in case 2.
+Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
+(c) Relative error as a function of number of AMA receptive fields used for luminance estimation.
+The relative error reduces if more receptive fields are used for estimation.}
+\label{fig:case2Results}
+\end{figure}
+
+\subsection{Case 3: Luminance can be estimated from contrast between target and background}
+For images of case 2, the AMA receptive fields learnt using the photoreceptor response does a very poor job in predicting the target object luminance (Fig.~\ref{fig:isomerizationFails}). 
 This is because, since the illuminant spectra varies in this case, the photoreceptor response is not directly proportional to the target object surface anymore. 
@@
     \begin{subfigure}[b]{0.3	 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.pdf}
         \caption{RFs learnt using photoreceptor response}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.pdf}
         \caption{RFs learnt using contrast signal}
@@
             \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.pdf}
         \caption{Luminance estimates}
@@
 
-While, the projection along the first two receptive fields shows an overlap between the stimuli at higher luminance values (Fig.~\ref{fig:constrastWorks}), the stimuli are better separated if the projection is considered within a subspace that has more receptive fields.
-Fig.~\ref{fig:RMSEvsNFilters} shows the relative error (Methods) of estimates as a function of the of the number of receptive fields considered for luminance estimation for the cases considered in this work.
-As expected, relative error reduces with increasing number of receptive fields.
-
-%% Figure 11
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
-\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the luminance.}
-\label{fig:RMSEvsNFilters}
-\end{figure}
+Again, similar to case 2, the projection along the first two receptive fields shows an overlap between the stimuli at higher luminance values (Fig.~\ref{fig:constrastWorks}).
+But, the stimuli are better separated if the projection is considered within a subspace that has more receptive fields (Fig.~\ref{fig:ErrorVsNFilters}).
+
+%%% Figure 11
+%\begin{figure}
+%\centering
+%\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
+%\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the luminance.}
+%\label{fig:RMSEvsNFilters}
+%\end{figure}
 % GET RID OF AMA FROM THE CAPTION
 
-\subsection{Case 3}
+\subsection{Case 4}
 % Figure 12
@@
 Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 3. 
-We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:RMSEvsNFilters}). 
+We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:ErrorVsNFilters}). 
 The AMA receptive fields do an excellent job of predicting the target object luminance.
 The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}).
-The relative error of estimation is ~17\%, which low compared to that of the naive model (~42\%) or the linear model on center pixel (~21\%).
+The relative error of estimation is ~15\%, which low compared to that of the naive model (~42\%) or the linear model on center pixel (~21\%).
 
@@
 \centering
-\begin{subfigure}{0.3 \textwidth}
+\begin{subfigure}{0.22 \textwidth}
 	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
@@
     ~ 
-    \begin{subfigure}{0.3 \textwidth}   
+    \begin{subfigure}{0.22 \textwidth}   
 	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
@@
     ~ 
-        \begin{subfigure}{0.3 \textwidth}
+        \begin{subfigure}{0.22 \textwidth}
 	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
@@
 	\label{fig:case3Bar}
+    \end{subfigure}
+    ~ 
+        \begin{subfigure}{0.22 \textwidth}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
+	\caption{Case 4}
+	\label{fig:case4Bar}
     \end{subfigure}
@@
 
-\subsection{Luminance can be well estimated using a bayesian decoder with gaussian priors.}
-We estimate the luminance of the target object in the images using the receptive field response of the corresponding contrast normalized cone responses.
-Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(c) shows the response of the first two RFs to the stimuli set for the three cases.
-For the training images at each luminance level, we approximate the receptive response of the contrast normalized cone responses by a multivariate gaussian.
-The target object luminance of an image in the test set is estimated using Bayesian decoder.
-We measure the estimation performance in terms of the relative root mean square ($E_{\rm rel}$) defined as:
 \begin{align}
@@
 where $\hat{Y}$ corresponds to the estimated luminance and $Y$ to the assigned luminance. We use the first 8 RFs for luminance estimation ( see Fig.~\ref{fig:RMSEvsNFilters}).
-
-Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(d) shows the luminance estimates and the RMSE for the three methods (Linear regression on center pixel, AMA and SVD).
-Additionally we show the estimate of a naive model that reports the mean value of the luminance labels used in the dataset.
-The diagonal x=y line is shown for reference.
-The shaded regions show $E_{\rm rel}$ for each method.
-
-(Fig.~\ref{fig:summaryBarGraph}) compares the $E_{\rm rel}$ for the different methods for the three cases.
-Both AMA and SVD methods, which use the information from the entire image estimate the luminance better compared to linear regression which only uses the information from the center pixel.
-This shows the importance of context information for luminance estimation.
 

### 2018-02-06 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m
more figures

@@ -106,7 +106,7 @@ save2pdf('filterResponse/case9FiltersResponseSVD.pdf',gcf,600);
 
 %% PLOT AMA first two Filters 
 clear;
-load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9.mat')
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat')
 plotFiltersColor2D(case9Output.AMA.f(:,1:2),[],[],[],1);
 save2pdf('filters/case9AMA.pdf',gcf,600);
 
@@ -115,6 +115,12 @@ clear;
 load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10.mat')
 plotFiltersColor2D(case10Output.AMA.f(:,1:2),[],[],[],1);
 save2pdf('filters/case10AMA.pdf',gcf,600);
+
+%%
+clear;
+load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case11_AMAIsomerization.mat')
+plotFiltersColor2D(case11Output.AMA.f(:,1:2),[],[],[],1);
+save2pdf('filters/case11AMA.pdf',gcf,600);
 
 %%
 clear;

### 2018-02-06 Draft2/draft2.tex
more edits

@@
 
+{\bf Error estimation:}
+The error of the luminance estimates are quantified in terms of the relative error ($E_{\rm rel}$), defined as follows:
+\begin{align}
+E_{\rm rel} = \sqrt{\left\langle\left(\frac{\hat{Y}-Y}{Y}\right)^2\right\rangle},
+\end{align}
+where $\hat{Y}$ corresponds to the estimated luminance and $Y$ to the assigned luminance.
+
 % THINGS TO THINK ABOUT:
@@
 \subsection{Optimal receptive fields for luminance estimation have a center surround structure}
-We used two supervised learning methods to learn the optimal receptive fields (RFs) for luminance estimation for the three types of variations in the spectral properties of the scene as discuss earlier.
-Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults}) shows the optimal RFs, the linear response of these RFs to the training dataset, and the estimates of the luminance of the target object in the test dataset for the three cases.
-We show the first two RFs obtained using the SVD and AMA methods (Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(a-b)).
-The RFs are ranked in ascending order of the value of the cost function.
+% Figure 14
+\begin{figure}
+\centering
+\begin{subfigure}{0.21 \textwidth}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+	\caption{Case 1}
+	\label{fig:case1Filter}
+    \end{subfigure}
+    ~ ~ ~
+    \begin{subfigure}{0.21 \textwidth}   
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+	\caption{Case 2}
+	\label{fig:case2Filter}
+    \end{subfigure}
+    ~ ~ ~
+        \begin{subfigure}{0.21 \textwidth}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+	\caption{Case 3}
+	\label{fig:case3Filter}
+    \end{subfigure}
+    ~ ~ ~
+        \begin{subfigure}{0.21 \textwidth}
+	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
+	\caption{Case 4}
+	\label{fig:case4Filter}
+    \end{subfigure}
+\caption{{\bf AMA receptive fields:} The first two AMA receptive fields for the four cases studied in this work.
+The receptive fields show a center surround structure.
+The L and M filters have larger weight as luminance is essentially a function of the L and M cone isomerizations.
+The stereotypical pattern in the receptive fields of case 4 is due to the fixed geometry of the images.}
+ \label{fig:AMAFilters}
+\end{figure}
+
+Fig.~{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for luminance estimation for the spectral variations studied in this work.
+The receptive fields are ranked in ascending order of the value of the cost function associated with them.
 Thus the first RF corresponds to the direction along which the projection of the data gives the minimum cost.
@@
 Thus, the RFs weights are mostly concentrated around the center.
-For case 2, while the target and the illuminant spectra varies, the background object spectra is fixed.
+For case 2, where the target and the background spectra varies, most of the luminance information is still concentrated around the central target object.
+For case 3, while the target and the illuminant spectra varies, the background object spectra is fixed.
 Hence, the luminance can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background.
@@
 The spatial features of the RFs are due the stereotypical geometry of the images (see \nameref{Methods}).
-For case 3, has a similar center surround structure with more prominent features of the background, as we also vary the spectra of the background objects.
+Case 4 has a similar center surround structure, but with more prominent features of the background since the spectra of the background objects are also varying.
 Again, the spatial features are a result of the stereotypical geometry of the images.
@@
 
-% Figure 13
+% Figure 14
 \begin{figure}
@@
 \begin{subfigure}{0.22 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
 	\caption{Case 1}
@@
     \begin{subfigure}{0.22 \textwidth}   
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
 	\caption{Case 2}
@@
         \begin{subfigure}{0.22 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
 	\caption{Case 3}
@@
         \begin{subfigure}{0.22 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_d.pdf}
 	\caption{Case 4}
@@
 \end{figure}
-
-\begin{align}
-E_{\rm rel} = \sqrt{\left\langle\left(\frac{\hat{Y}-Y}{Y}\right)^2\right\rangle},
-\end{align}
-where $\hat{Y}$ corresponds to the estimated luminance and $Y$ to the assigned luminance. We use the first 8 RFs for luminance estimation ( see Fig.~\ref{fig:RMSEvsNFilters}).
 

### 2018-02-07 Draft2/draft2.tex
more edits

@@
 
-\keywords{color constancy, accuracy maximization analysis, supervised learning,
-luminance}
+\keywords{color constancy, luminance constancy, supervised learning}
 
@@
 The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
-Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of light reflected from the object to the eye.
-The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose,
-and the position of the observer (Fig.~\ref{fig:introSchematic}).
+Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
+The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose and the position of the observer (Fig.~\ref{fig:introSchematic}).
 Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
@@
 In this work, we assume the noisy response model to be a multivariate gaussian.
-For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{kl,1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$.
-We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be zero mean contrast normalized, i.e., $\langle{s_{kl}}\rangle = 0$ \& ${|s_{kl}|=1}$.
+For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$.
+We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be contrast normalized, i.e., ${|s_{kl}|=1}$.
 
@@
 To estimate the label of an image from the test set, we use Byes' rule to obtain the posterior distribution $p(Y_i|{\textbf {\textit R} })$.
-The estimates value is the one that optimizes the cost function.
-
-{\bf Error estimation:}
-The error of the luminance estimates are quantified in terms of the relative error ($E_{\rm rel}$), defined as follows:
-\begin{align}
-E_{\rm rel} = \sqrt{\left\langle\left(\frac{\hat{Y}-Y}{Y}\right)^2\right\rangle},
-\end{align}
-where $\hat{Y}$ corresponds to the estimated luminance and $Y$ to the assigned luminance.
+The estimated value is the one that optimizes the cost function.
+
+\subsection{Error estimation}
+If $\hat{Y}$ is the estimated luminance corresponding to the assigned luminance $Y$, the error of the luminance estimates is quantified as the relative error ($E_{\rm rel}$) defined as: $E_{\rm rel}^2 = \left\langle\left((\hat{Y}-Y)/Y\right)^2\right\rangle$.
 
@@
 The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}).
-The relative error of estimation is ~15\%, which low compared to that of the naive model (~42\%) or the linear model on center pixel (~21\%).
+The relative error of estimation is $\sim15\%$, which low compared to that of the naive model ($\sim42\%$) or the linear model on center pixel ($\sim21\%$).
 
@@
 We generated a dataset of multispectral images labeled by the reflectance of a target object in each image.
-These images were generated by a software pipeline developed for this work, that we call Virtual world color constancy (VWCC).
+These images were generated by a software pipeline developed for this work that we call Virtual world color constancy (VWCC).
 This software creates 3D scene descriptors based on programatic information provided by the user.

### 2018-02-07 Draft2/draft2.tex
more edits

@@
 
-AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
-When provided with a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task.
-The task is implicitly defined in terms of the labels.
-The optimal filters that are returned by AMA are the filters whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
-Once these filters have been identified, a suitable decoding method (in this case a Bayesian decoding scheme) is used to estimate the label on a test set.
-
-{\bf Learning AMA Filters:} Let us assume that there are $N_{\nu}$ possible values of the labels.
-In our analysis, it means that the luminance level of the target object in an image can take one of the possible $N_{\nu}$ values ($\{Y_k: k\in[1,N_{\nu}] \}$).
-We represent the $l$'th image corresponding to the $k$'th label as $s_{kl}$.
+To construct an ideal observer model for our task, two steps are required.
+First, we use AMA to learn the filters that are optimal for the task.
+Second, we determine how to optimally decode the task relevant variable from the filter responses to arbitrary stimuli.
+
+{\bf Learning optimal filters:} AMA \cite{geisler2009optimal,burge2017accuracy} is a task specific Bayesian method for dimensionality reduction.
+When provided with a labeled training set, a response noise model, and a cost function, AMA returns the linear receptive fields in rank order that are optimal for performing a task.
+The optimal filters that are returned by AMA are the filters whose noisy responses to the stimuli, as given by the specified response model, minimizes the cost function over the training set when optimally decoded.
+
+Let us assume that there are $N_{\nu}$ possible values of the target object luminance levels ($\{Y_k: k\in[1,N_{\nu}] \}$).
+We represent the $l$'th image corresponding to the $k$'th level as $s_{kl}$.
 Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
-Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the label ($Y_k$) corresponding to the stimuli $s_{kl}$ as $\hat{Y}_{kl}$.
+Let's say we have a decoder $g$, that uses the information of the response noise model, to return the Bayes optimal estimate of the luminance level ($\hat{Y}_k$) corresponding to the stimuli $s_{kl}$.
 Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and an avearge cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.
@@
 
-{\bf Estimating labels:} The image labels are estimated using the Bayesian decoder as described above.
+{\bf Estimating labels:}
+
+Once these filters have been learned, a suitable decoding method (in this case a Bayesian decoding scheme) is used to estimate the label on a test set.
+
+The image labels are estimated using the Bayesian decoder as described above.
 First, we use the AMA optimal filters and the training dataset to find the conditional distribution of the AMA filter response $p({\textbf {\textit R} }|Y_i)$.

### 2018-02-08 Draft2/draft2.tex
more edits

@@
 Geisler and colleagues, for example, have developed a technique they refer to as accuracy maximization analysis (AMA, \citeNP{geisler2009optimal}), which learns linear filters whose output carries information that is optimized for particular perceptual tasks.
-This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus \cite{burge2011optimal} and disparity \cite{burge2014optimal}
-% JOHANNES ARE THERE ANY OTHER PAPERS YOU WOULD LIKE TO CITE
+This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus error \cite{burge2011optimal}, and disparity \cite{burge2014optimal}
 from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
@@
 
-In this work, we are interested in how well luminance constancy may be achieved using reasonable information that is local to the image region containing the target patch. 
-% MAYBE SAY A LITTLE MORE ABOUT WHY - THIS IS A PRINCIPLED STANCE TAKEN IN MOST OF JOHANNES WORK.  OR MAYBE DEFER THAT TO THE DISCUSSION.
-To this end, we crop a 51x51 pixel portion of the full rendered multispectral image that contains the target object and use this for further analysis (\ref{fig:croppedImage}).
+In this work, we are interested in how well luminance constancy may be achieved using information that is local to the image region containing the target object. 
+To analyze the local image information, we cropped and processed the image in the immediate neighborhood of the target object such that each patch represented a one degree of visual angle, approximately the size of a receptive field in early visual cortex (\ref{fig:croppedImage}).
 Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 luminance levels for the three cases considered in this paper.
@@
 
-The isomerizations of the cones in the retinal mosaic represent the first steps of visual processing.
-To capture key properties of post-receptoral processing, contrast coding (REFS) and contrast normalization (REFS),
-% Ask Johannes what he'd use as references for these broad principles
+The cone isomerizations represent the first step of visual processing.  To capture key properties of post-receptoral processing, such as contrast normalization (REFS),
+% Heeger 1992, Albrecht and Geisler 1991 (contrast normalization)
+% Carindini Heeger 2012 (Review on contrast norm)
 we processed the isomerizations as follows:
@@
 \subsubsection*{Accuracy maximization analysis}
-% MAYBE ADD SOME INTRO TEXT THAT SAYS THAT FIRST ONE FINDS THE FILTERS AND THEN PROJECTS ONTO THEM, THEN DOES BAYESIAN DECODING OF THE RESPONSES.  BREAK INTO TWO SUBSECTIONS FOR CLARITY.
-
-To construct an ideal observer model for our task, two steps are required.
-First, we use AMA to learn the filters that are optimal for the task.
-Second, we determine how to optimally decode the task relevant variable from the filter responses to arbitrary stimuli.
-
-{\bf Learning optimal filters:} AMA \cite{geisler2009optimal,burge2017accuracy} is a task specific Bayesian method for dimensionality reduction.
-When provided with a labeled training set, a response noise model, and a cost function, AMA returns the linear receptive fields in rank order that are optimal for performing a task.
-The optimal filters that are returned by AMA are the filters whose noisy responses to the stimuli, as given by the specified response model, minimizes the cost function over the training set when optimally decoded.
-
-Let us assume that there are $N_{\nu}$ possible values of the target object luminance levels ($\{Y_k: k\in[1,N_{\nu}] \}$).
-We represent the $l$'th image corresponding to the $k$'th level as $s_{kl}$.
-Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
-Let's say we have a decoder $g$, that uses the information of the response noise model, to return the Bayes optimal estimate of the luminance level ($\hat{Y}_k$) corresponding to the stimuli $s_{kl}$.
-Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and an avearge cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.
-
-Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$.
-Here $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
+We perform two steps to decode the luminance of the target object from the cone isomerization.
+First, we use AMA to learn the linear filters that are optimal for estimating the target object luminance.
+Second, we determine how to optimally decode the luminance from the response of these filters to arbitrary stimuli.
+
+{\bf Learning optimal filters using AMA:} AMA \cite{geisler2009optimal,burge2017accuracy}
+% add Jaini burge 2017
+is a task specific Bayesian method for dimensionality reduction.
+When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns the linear receptive fields (in rank order) that are optimal for performing a task.
+The optimal receptive fields that are returned by AMA are those whose responses to the stimuli minimizes the cost function over the training set when optimally decoded.
+
+More concretely, let us assume that there are $N_{\nu}$ possible values of the target object luminance levels ($\{Y_k: k\in[1,N_{\nu}] \}$) and the $l$'th image corresponding to the $k$'th luminance level is represented as $s_{kl}$.
+Also, assume that there is a set of linear receptive fields {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
+Also assume there is a decoder $g$, with the knowledge of the response model and of every stimulus in the training set, that returns the Bayes' optimal estimate of the luminance level ($\hat{Y}_k$) of the target object in each stimulus $s_{kl}$.
+The crux computation for obtaining this estimate is the computation of the posterior probability of the luminance given an observed response, $P(Y|\textbf{R}_{kl})$ \cite{geisler2009optimal,burge2017accuracy}
+% add Jaini burge 2017
+.
+With this luminance estimate, we calculate the cost given the cost function $\mathcal{C}_{kl} = \gamma(Y_{kl},\hat{Y}_{kl})$.
+Finally, AMA searches for the set of optimal receptive fields ${\textbf{\textit f}}^{\rm opt}$ that minimize the cost over the entire training set $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$ where $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
 Thus,
 \begin{align}
-{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{kl} \bar{\mathcal{C}}_{kl}.
+{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{k=1}^{N_{\nu}}  \sum_{l=1}^{N_k} {\mathcal{C}}_{kl}.
 \label{eq:fopt}
@@
 
-AMA employs the Bayes optimal decoder ($g$) to estimate the optimal estimate.
-The Bayesian decoder computes the posterior probability of the label $p(Y|{\textbf {\textit R}})$ and reads out the optimal estimate $\hat{Y}^{\rm opt}$ from the posterior as the value that minimizes the cost.
-By Bayes' theorem, the posterior probability can be written as:
-\begin{align}
-p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{p({\textbf {\textit R} }_{kl}|Y_k)p(Y_k)}{\sum\limits_{i=1}^{N_{\nu}}{p({\textbf {\textit R} }_{kl}|Y_i)p(Y_i)}}.
-\label{eq:posterior}
-\end{align}
-Since, the conditional probability of the filter response is:
-\begin{align}
-p({\textbf {\textit R} }_{kl}|Y_k) = \sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|Y_k),
-\label{eq:condProb}
-\end{align}
-using Eq.~\ref{eq:condProb} in Eq.~\ref{eq:posterior} we get:
-\begin{align}
-p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|Y_k)\right]p(Y_k)}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})p({\textbf {\textit s} }_{kj}|Y_i)\right]p(Y_i)}}
-\label{eq:finalPosterior}
-\end{align}
-Since, $p({\textbf {\textit s} }_{km}|Y_k) = \frac{1}{N_k}$, and $p(Y_k)=\frac{N_k}{N}$, where $N = \sum\limits_{k=1}^{N_{\nu}}N_{k}$ is total number of samples in the training set, Eq.~\ref{eq:finalPosterior} simplifies to
-\begin{align}
-p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km}) \frac{1}{N_k}\right]\frac{N_k}{N}}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij}) \frac{1}{N_i}\right]\frac{N_i}{N}}} = \frac{\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})}{\sum\limits_{i=1}^{N_{\nu}}{\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})}}.
-\label{eq:simplifiedPosterior}
-\end{align}
-Now if the cost associated with the latent variable $Y_k$ and the estimate $\hat{Y}_k$ is $\gamma (Y_k,\hat{Y}_k)$, we have  
-\begin{align}
-\mathcal{C}_{kl} = \sum\limits_{u=1}^{N_{\nu}}\gamma(Y_u,\hat{Y}_u)p(X_u|{\textbf{\textit R}}_{kl}).
-\end{align}
-The mean cost associated with the training set is $\bar{\mathcal{C}} = \frac{1}{N} \sum\limits_{k,l}\bar{\mathcal{C}}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle \mathcal{C}_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$.
-The optimal AMA filters are obtained by minimizing $\bar{\mathcal{C}}$ over the filter set ${\textbf {\textit f} }$ (Eq.\ref{eq:fopt}).
-The filters are obtained using gradient descent.
-
-In this work, we assume the noisy response model to be a multivariate gaussian.
-For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$.
-We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be contrast normalized, i.e., ${|s_{kl}|=1}$.
+{\bf Estimating luminance:} 
+Once the optimal receptive fields have been learned, a general decoder must be used to estimate the luminance.
+Recall that the decoder used to learn the receptive fields required the knowledge of every stimulus in the training set.
+To obtain the general decoder, first we use the AMA optimal receptive fields and the training dataset to find the conditional distributions of the AMA receptive field responses $P({\textbf {\textit R} }|Y_i)$.
+Then, we approximate these with multivariate Gaussian distributions $P({\textbf {\textit R} }|Y_i) = \mathcal{N}\left(\mu(Y_i),\Sigma(Y_i) \right)$.
+To estimate the luminance of the target object in the test stimulus, we use Bayes' rule to obtain the posterior distribution $P(Y|{\textbf {\textit R} })$.
+The optimal estimate is the luminance value that minimizes the cost function.
 

### 2018-02-09 Draft2/draft2.tex
more edits

@@
 \section{Results} \label{Results}
-\subsection{Case 1: Target luminance can be estimated directly from the photoreceptor response}
-We used AMA to learn a set of linear receptive fields that are optimal for estimating target object luminance using stimuli in the training set of case 1. 
-Fig.~\ref{fig:case1RFResponse} shows the projection of the photoreceptor response along the first two AMA receptive fields. 
+In this section, we discuss the results of supervised learning to estimate the luminance of the target object on the the various cases we described previously.
+We describe the computations that need to be performed on the cone photoreceptor responses to estimate the luminance.
+We start with case 1, where only the reflectance spectrum of the target object is allowed to vary, and show that in this case the luminance can be estimated directly from the photoreceptor response.
+We then progressively increase the complexity of the spectral conditions and explain the correspondingly complex computations that are required to estimate the target object luminance.
+Next, we show the optimal AMA receptive fields for each one of the spectral cases discussed in this work.
+We show that the optimal receptive fields for target luminance estimation have a center surround structure and they give more weights to the response of L and M cones than S cones.
+We finally show that, as expected, the receptive fields for the complex spectral cases generalize to the simple cases.
+Hence, one requires only one set of optimal receptive fields for estimating the target luminance, not separate receptive fields for each spectral case.
+
+\subsection{Luminance estimates for each spectral case}
+\subsubsection{Case 1: Target object relative surface reflectance spectrum variable, light source and background object spectra fixed}
+We started our analysis with the simplest case, where only the target object relative spectrum is allowed to change. 
+We used AMA to learn a set of linear receptive fields that are optimal for estimating target object luminance for the stimuli in this case. 
+Fig.~\ref{fig:case1RFResponse} shows the projection of the photoreceptor response along the first two optimal AMA receptive fields. 
 Clearly, there exists a subspace along which the photoreceptor response separates according to the luminance level assigned to the target object. 
 Thus, the target object luminance can be obtained by projecting photoreceptor responses along these AMA receptive fields. 
-Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test images in case 1. 
+We used such projections and a generalized decoder Bayes' decoder (see methods) to estimate the luminance of the target objects in the test set stimuli.
+Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test stimulus in case 1. 
 We show the estimates obtained by AMA and two null models: a naive method that assigns the average target object luminance across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object (see Methods).
@@
 
-\subsection{Case 2}
+\subsubsection{Case 2: Target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable}
 Fig.~{\ref{fig:case2RFResponse}} shows the projection of the photoreceptor response for case 2 along the first two AMA receptive fields.
@@
 
-\subsection{Case 3: Luminance can be estimated from contrast between target and background}
-For images of case 2, the AMA receptive fields learnt using the photoreceptor response does a very poor job in predicting the target object luminance (Fig.~\ref{fig:isomerizationFails}). 
+It has previously been assumed that the surface reflectance spectra of the background objects have no direct effect on the light reflected by the target object \cite{BrainardWandellRetinex}.
+This would suggest that the response of the photoreceptors corresponding to the target object would only depend on the surface reflectance spectrum of the target object.
+But our results show that the effects of change in background object surface reflectances are significant.
+The secondary reflections from the target object, of the light coming indirectly after being reflected from the background objects, contribute to response of the photoreceptors corresponding to the target object.
+
+\subsubsection{Case 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed}
+For images of case 3, the AMA receptive fields learnt using the photoreceptor response does a very poor job in predicting the target object luminance (Fig.~\ref{fig:isomerizationFails}). 
 This is because, since the illuminant spectra varies in this case, the photoreceptor response is not directly proportional to the target object surface anymore. 
@@
 
-\subsection{Case 4}
+\subsubsection{Case 4: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
 % Figure 12
@@
 
-\subsection{The RFs of complex case generalize on simpler cases}
+\subsection{The receptive fields of complex case generalize on simpler cases}
 Fig.~\ref{fig:barGraphs} shows the relative error for the estimates of the target object luminance obtained using the linear model and AMA.

### 2018-02-12 Draft2/draft2.tex
more edits

@@
 Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
-The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose and the position of the observer (Fig.~\ref{fig:introSchematic}).
+The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
 Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
@@
 
-Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 3. 
+Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 4. 
 We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:ErrorVsNFilters}). 
@@
 
-Fig.~{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for luminance estimation for the spectral variations studied in this work.
+Fig.~\ref{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for luminance estimation for the spectral variations studied in this work.
 The receptive fields are ranked in ascending order of the value of the cost function associated with them.
@@
 \caption{{\bf Error comparison across models:} Comparison of optimal AMA receptive fields from one case on the images of other cases.
-(a) Relative error of the estimates obtained using the linear model and AMA.
-The AMA receptive fields of case 1, 2 and 3 are used to estimate the target object luminance of the test images from case 1.
+Each panel shows the relative error of the estimates obtained using the linear model and the AMA receptive fields of case 1-4.
+(a) Relative error of estimates of the target object luminance of images from case 1.
 The AMA receptive fields from all three cases perform well in this case.
@@
 As expected, the error of the linear model on the center pixel is higher than AMA.
-AMA receptive fields from case 1 do worse than the receptive fields from case 2 and 3.
+As expected, the best estimates are provided by the receptive fields of case 2.
 (c) Relative error for images of case 3.
-The best predictions are from the receptive learnt using the images of case 3.}
+(d) Relative error for test images of case 4.}
  \label{fig:barGraphs}
@@
 In this paper, we studied luminance constancy using naturalistic images.
-We generated a dataset of multispectral images labeled by the reflectance of a target object in each image.
-These images were generated by a software pipeline developed for this work that we call Virtual world color constancy (VWCC).
-This software creates 3D scene descriptors based on programatic information provided by the user.
+We generated datasets of multispectral images labeled by the reflectance of a target object in each image.
+The images were generated using a software pipeline developed for this work that we call Virtual world color constancy (VWCC).
+The software creates 3D scene descriptors based on programatic information provided by the user.
 Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc.
 We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances.
-Thus, we generate a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image.
-Such databases are near to be impossible to generate using other means as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab.
-
-In this paper, as a first step towards understanding color constancy using supervised methods on labeled dataset, we studied a simpler analogue: luminance constancy.
-We generated images labeled with the luminance of a target object in the scene.
-We performed three types of spectral manipulations in the scene while generating the images (Fig.~\ref{fig:studiedCases}).
+Thus, we generated a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image.
+Such databases are nearly impossible to generate for natural scenes as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab.
+We used these labeled images in a supervised manner to understand the computations required for estimating the luminance of an object under spectral variations in the scene.
+
+In this work, as a first step towards understanding luminance constancy, we generated images labeled with the luminance of a target object.
+We performed four types of spectral manipulations in the scene while generating the images (Fig.~\ref{fig:introExampleFigure}-\ref{fig:studiedCases}).
 1.
-Allow variations in the spectral shape of the target object surface reflectance spectrum, while keeping the background object surface reflectance and the illumination spectra of the light sources fixed.
-2.
-Allow variations in the shape of the target object surface reflectance and the illumination spectra of the light sources, while keeping the surface reflectance spectra of the background objects fixed.
-3.
-Allow variations in all three types of spectra.
-We generated hundreds of images at multiple luminance level of the target object for each of these three cases.
+variations in the surface reflectance spectrum of the target object, 2.
+variations in surface reflectance spectrum of both target and the background objects, 3.
+variations in the surface reflectance spectrum of the target and the emission spectrum of the light source, and 4.
+variation is surface reflectance spectrum of the target and the background objects and the emission spectrum of the light source.
+We generated hundreds of images at multiple luminance level of the target object for each of these cases.
 Then using a model of the early visual system, we generated the response of the cones in the retina for each image in our database.
-These model retinal responses, along with the luminance label of the images, are then used as the input to supervised learning algorithms.
+These model retinal responses, along with the luminance label of the images, were then used as the input to supervised learning algorithms.
 Using our supervised methods, we leant that the target object luminance can be obtained from simple manipulation of the cone response for case where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, the light source illumination spectra.
@@
 
+Summary
+
+Effect of background. multiple reflection
+
+center surround RFs
+
+LM
+
 \bibliography{references}

### 2018-02-12 Draft2/draft2.tex
more edits

@@
 \subsection{Labelled image database} \label{method:VirtualWorld}
-
 % Figure 3
@@
 \subsubsection{Surface Reflectance Spectra}
-
 % Figure 7
@@
 
-The cone isomerizations represent the first step of visual processing.  To capture key properties of post-receptoral processing, such as contrast normalization (REFS),
-% Heeger 1992, Albrecht and Geisler 1991 (contrast normalization)
-% Carindini Heeger 2012 (Review on contrast norm)
+The cone isomerizations represent the first step of visual processing.
+To capture key properties of post-receptoral processing, such as contrast normalization \cite{heeger1992normalization,albrecht1991motion,carandini2012normalization},
 we processed the isomerizations as follows:
@@
 
-{\bf Learning optimal filters using AMA:} AMA \cite{geisler2009optimal,burge2017accuracy}
-% add Jaini burge 2017
+{\bf Learning optimal filters using AMA:} AMA \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
 is a task specific Bayesian method for dimensionality reduction.
@@
 Also assume there is a decoder $g$, with the knowledge of the response model and of every stimulus in the training set, that returns the Bayes' optimal estimate of the luminance level ($\hat{Y}_k$) of the target object in each stimulus $s_{kl}$.
-The crux computation for obtaining this estimate is the computation of the posterior probability of the luminance given an observed response, $P(Y|\textbf{R}_{kl})$ \cite{geisler2009optimal,burge2017accuracy}
-% add Jaini burge 2017
+The crux computation for obtaining this estimate is the computation of the posterior probability of the luminance given an observed response, $P(Y|\textbf{R}_{kl})$ \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
 .
@@
 %  1) Putting error bars on performance.  Particularly want to be sure that Fig 13 feature that Case 3 RFs do better than Case 1 RFs for Case 1 is just statistical sampling.
-%  2) What exactly do we want to run for final version.  How much illuminant intensity variation?  Should we make this match psychophysics so we could imagine these images displayed on a monitor?
-%  3) Do we just want to look at results for contrast normalized, or do we want to pick them off separately for isomerizations, contrast, and contrast normalized?
-%  4) What is driving the response variability in Case 1, where the stimulus is basically deterministic up to noise.
-There are three sources of noise: 1) Rendering noise, 2) Isomerization noise, 3) AMA noise introduced for some unknown reason, 4) Variation in target color.
-
-% WHAT STORY DO WE WANT TO TELL ABOUT THE RESULTS
-%  1) Case 0 -- work out effect of sources of internal noise - isomerization and AMA -- without any external "noise", where external "noise" is the effect of variability in object extrinsic scene factors (illumination, surrounding objects).
-%                      Also establish the rendering noise is einsy relative to whatever else we're doing.
-%  2) Move to Case 1 -- what happens when we introduce color variability into the target.
-This may not be of interest to the psychophysics, but none-the-less seems interesting to know as one ponders lightness constancy.
-%  3) On to Case 2 -- here the question is, do we keep varying target color, or do we fix target color and vary illumination?
-In any case, this isn't too hard a case if the other objects remain fixed, because then contrast coding basically normalizes out a lot of the variation, and it's only the spectral variation that might screw things up.
-But, that's why we run case 3.
-%  4) Do we run a case where the relative spectrum of the illuminant stays fixed and we only vary intensity?
-%  4) On to Case 3 --
 
@@
 \subsubsection{Case 1: Target object relative surface reflectance spectrum variable, light source and background object spectra fixed}
-We started our analysis with the simplest case, where only the target object relative spectrum is allowed to change. 
-We used AMA to learn a set of linear receptive fields that are optimal for estimating target object luminance for the stimuli in this case. 
+We start with the results of the simplest type of spectral variation where only the target object relative surface reflectance spectrum is allowed to change. 
+We used AMA to learn a set of linear receptive fields that are optimal for estimating target object luminance from the model cone photoreceptor response to the images from this case.
 Fig.~\ref{fig:case1RFResponse} shows the projection of the photoreceptor response along the first two optimal AMA receptive fields. 
 Clearly, there exists a subspace along which the photoreceptor response separates according to the luminance level assigned to the target object. 
-Thus, the target object luminance can be obtained by projecting photoreceptor responses along these AMA receptive fields. 
-We used such projections and a generalized decoder Bayes' decoder (see methods) to estimate the luminance of the target objects in the test set stimuli.
-Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test stimulus in case 1. 
+Thus, the target object luminance can be obtained by projecting the photoreceptor response along these AMA receptive fields. 
+We used such projections and a generalized Bayes' decoder (see methods) to estimate the luminance of the target objects in the test set stimuli. 
+Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test stimuli in case 1. 
 We show the estimates obtained by AMA and two null models: a naive method that assigns the average target object luminance across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object (see Methods).
@@
 Each cloud in Fig.~\ref{fig:case1RFResponse} corresponds to the photoreceptor response to the images with target luminance level at a fixed value. 
-The variation within the cloud, between images that have the target object at same luminance values, results due to the difference in the relative shape of the target object reflectance spectra (difference in hue and saturation).
+The variation within the cloud, between images that have the target object at same luminance values, is due to the difference in the relative shape of the target object reflectance spectra (difference in hue and saturation).
 The resulting variation dominates any variation coming from the noise in photoreceptor response or the noisy rendering of the images by the software.
@@
 \subsubsection{Case 2: Target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable}
-Fig.~{\ref{fig:case2RFResponse}} shows the projection of the photoreceptor response for case 2 along the first two AMA receptive fields.
-The naive expectation would be that variations in background objects surface reflectance would have minimal effect on the isomerizations of the cones corresponding to the target object.
-Hence, the luminance can be estimated directly from the isomerization of these cones.
-But projection of the cone response along the AMA RFs shows that the background variation has significant effect on the cone isomerizations.
-The response clouds at different luminance levels along the first two receptive fields do not separate as well compared to case 1.
-The overlap is lower if the projection is considered in subspaces that have more AMA receptive fields.
+When the light source emission spectrum is fixed, the naive expectation would be that the luminance of the target object would depend only on the surface reflectance of the target object. 
+Indeed, it is believed that the variation in the surface reflectance of the background has little effect on the reflected light from the target object  \cite{BrainardWandellRetinex}. 
+But our analysis shows that the secondary reflections from the target object, of the light coming indirectly after being reflected from the background objects, have a significant effect on the response of the photoreceptors corresponding to the target object.
+Fig.~{\ref{fig:case2RFResponse}} shows the projection of the photoreceptor response for the stimuli in case 2 along the first two AMA receptive fields. 
+These receptive fields were learnt using the stimuli from the same case 2. 
+The response projected along the first two optimal receptive fields do not separate as well compared to case 1. 
+But the overlap is lower if the projection is considered in subspaces that have more AMA receptive fields. 
 Fig.~\ref{fig:ErrorVsNFilters} shows the relative error of luminance estimate as a function of the number of AMA receptive fields used for luminance estimation. 
@@
 
-It has previously been assumed that the surface reflectance spectra of the background objects have no direct effect on the light reflected by the target object \cite{BrainardWandellRetinex}.
-This would suggest that the response of the photoreceptors corresponding to the target object would only depend on the surface reflectance spectrum of the target object.
-But our results show that the effects of change in background object surface reflectances are significant.
-The secondary reflections from the target object, of the light coming indirectly after being reflected from the background objects, contribute to response of the photoreceptors corresponding to the target object.
-
 \subsubsection{Case 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed}
-For images of case 3, the AMA receptive fields learnt using the photoreceptor response does a very poor job in predicting the target object luminance (Fig.~\ref{fig:isomerizationFails}). 
+For the spectral variations of case 3, the AMA receptive fields learnt on the photoreceptor response to the images does a very poor job in predicting the target object luminance (Fig.~\ref{fig:isomerizationFails}).
 This is because, since the illuminant spectra varies in this case, the photoreceptor response is not directly proportional to the target object surface anymore. 
@@
 This is because a change in illuminant spectra produces the same effect in both the target object and the background object. 
-Thus, the AMA receptive fields learnt on the contrast normalized photoreceptor response (see Methods) can be used to predicts the target object luminance (Fig.~\ref{fig:constrastWorks}). 
-Fig.~\ref{fig:case10Results} shows the estimated target object luminance v/s the assigned luminance for the images in case 2 obtained using the contrast normalized representation. 
+Thus, the AMA receptive fields learnt on the contrast normalized photoreceptor response (see Methods) can be used to predict the target object luminance (Fig.~\ref{fig:constrastWorks}). 
+Fig.~\ref{fig:case10Results} shows the estimated target object luminance v/s the assigned luminance for the images in case 3 obtained using the contrast normalized representation. 
 AMA receptive fields provide excellent predictions of the target object luminance. 
@@
     \end{subfigure}
-    \caption{{\bf Case 2: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
+    \caption{{\bf Case 3: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
 (b) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
@@
 The response at each luminance level separates much better in this representation.
-(c) Estimated v/s assigned target object luminance for the image in case 2.
+(c) Estimated v/s assigned target object luminance for the image in case 3.
 Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
@@
 
+Case 4 is the most complex type of variation that we consider in this work.
+Here we allow all three types of spectra to change from image to image.
+In this case, neither the photoreceptor response (as in Case 1 and 2), nor any simple transformation of the response (case 3) can provide the target object luminance.We used AMA to learn the receptive fields using the contrast normalized cone photoreceptor response from stimuli in case 4.
 Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 4.
@@
 
-Fig.~\ref{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for luminance estimation for the spectral variations studied in this work.
+Fig.~\ref{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for estimating the target object luminance for the four types of spectral variations studied in this work.
 The receptive fields are ranked in ascending order of the value of the cost function associated with them.

### 2018-02-13 Draft2/draft2.tex
discussion

@@
 In this paper, we studied luminance constancy using naturalistic images.
-We generated datasets of multispectral images labeled by the reflectance of a target object in each image.
-The images were generated using a software pipeline developed for this work that we call Virtual world color constancy (VWCC).
-The software creates 3D scene descriptors based on programatic information provided by the user.
-Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc.
-We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances.
-Thus, we generated a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image.
-Such databases are nearly impossible to generate for natural scenes as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab.
-We used these labeled images in a supervised manner to understand the computations required for estimating the luminance of an object under spectral variations in the scene.
-
-In this work, as a first step towards understanding luminance constancy, we generated images labeled with the luminance of a target object.
-We performed four types of spectral manipulations in the scene while generating the images (Fig.~\ref{fig:introExampleFigure}-\ref{fig:studiedCases}).
-1.
-variations in the surface reflectance spectrum of the target object, 2.
-variations in surface reflectance spectrum of both target and the background objects, 3.
-variations in the surface reflectance spectrum of the target and the emission spectrum of the light source, and 4.
-variation is surface reflectance spectrum of the target and the background objects and the emission spectrum of the light source.
-We generated hundreds of images at multiple luminance level of the target object for each of these cases.
-Then using a model of the early visual system, we generated the response of the cones in the retina for each image in our database.
-These model retinal responses, along with the luminance label of the images, were then used as the input to supervised learning algorithms.
-Using our supervised methods, we leant that the target object luminance can be obtained from simple manipulation of the cone response for case where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, the light source illumination spectra.
-In these cases, the luminance can be obtained by comparing the response of the cones corresponding to the target and the background objects.
-When all these three types of spectral variations are allowed simultaneously, one needs additional information to obtain the luminance of the target object.
+We used a software pipeline called  Virtual world color constancy (VWCC), which was developed for this work, to generate datasets of multispectral images labeled by the luminance of a target object in each image.
+VWCC creates 2D multispectral images of 3D scenes based on information provided by the user.
+Such information include the shape of the 3D space, the shape, size, position and material properties of the objects and light sources in the scene.
+In our work, we assigned these geometrical and spectral properties using random sampling from available databases of natural objects and light sources.
+Thus, we generated a large database of labeled hyper-spectral images, with naturalistic scene properties, where we have the ground truth information about every surface and light source.
+Such databases, of even a few images, are nearly impossible to obtain for natural scenes.
+This is because it is very hard to measure the surface reflectance and the illumination spectrum at every point in a scene, even for well controlled lab environments.
+
+We used the software generated labeled images in a supervised manner to understand luminance constancy under four types of spectral manipulations (Fig.~\ref{fig:introExampleFigure}-Fig.~\ref{fig:studiedCases}).
+We found that target object luminance can be recovered through simple manipulation of the retinal cone responses for cases where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, or the light source illumination spectra.
+When variations are allowed only in the target object surface reflectance spectrum, or only the target object and the background objects surface reflectance spectra, the luminance can be estimated directly from the response of retinal cone photoreceptors.
+If the background spectra is fixed, but the target object reflectance spectrum and the light source illumination spectra are varying, the luminance can be obtained from the contrast between the cone response corresponding to the target and the background.
+When all three spectral variations are allowed simultaneously, one needs additional information to obtain the target object luminance.
 

### 2018-03-05 Draft2/draft2.tex
DB and JB editing today

@@
 \section{Introduction}
-The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
-Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
-The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
-Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
+The perceived color of an object has important behavioral implications, since color helps to identify objects and their properties \cite{Mollon89, Jacobs81}.
+Perceived object color is not sensed directly. Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
+The computational challenge underlying object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
+To produce a stable perceptual representation correlated with an object's surface reflectance the brain must account for these intrinsic factors on the reflected light.
 The ability of a visual system to extract such a stable representation is called color constancy.
 Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}.
-In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.
-
-There is a considerable literature on computational color constancy.
-Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
-\citeNP{LandRetinex}) or produce explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
-An important insight of this line of research was that, to account for variation in illumination, it was necessary to consider the light reflected from the entire scene.
-That is, although good constancy cannot be achieved in the face of illuminant variation if one considers only the light reflected from a single target object, when one considers the entire image it is possible to use the joint variation in light reflected from many objects to obtain (either implicitly or explicitly) an estimate of the illuminant common across the objects, and in turn to use this estimate to produce a stabilized representation of object color.
+In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eye to produce percepts well-correlated with object surface reflectance.
+
+Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
+A key insight from this work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.
+But, it is possible to obtain such descriptors by analyzing jointly the light reflected from all of the objects in the scene.
+As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant.
+Thus evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects.
+
+*** HERE ***
+
 At the same time, this processing introduces an additional dependence.
-Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image \cite{BrainardWandellRetinex}.
+Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image
+
 Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
-Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
-None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.
+
+***
+Subsequent work, which extended the analysis to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS), confirmed this basic insight.
+
+Seminal computational color constancy algorithms applied to a  considered a simplified case in which flat matte surfaces are illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
+\citeNP{LandRetinex}) or produce explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., .
+Subsequent computational constancy work sought to generalize both the image formation model   None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.
 
@@
     \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light reflected from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,\vec{x})$, and the illumination spectrum of the light source, $E(\lambda,\vec{x})$.
-Additionally, it depends on geometric factors, such as the object's shape and pose, as well as the position of the observer.
-The human visual system is able to account for, at least partially, variations in the reflected light due to such extrinsic factors, and produce a percept of object color that is relatively stable with respect to such variations.
+    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and the illumination spectrum of the light source.
+It also depends on geometric factors, such as the object's shape, pose, and position relative to the observer.
+The human visual system is able to account for variations in the reflected light due to such extrinsic factors and produce a percept of object color that is relatively stable with respect to such variations.
 Such invariant color perception is called color constancy.
@@
  \end{figure}
+ % REMOVE EQUATION FROM 1a. IT'S NOT DOING ANY WORK AND IT ISN'T ACCURATE IN 3D WHERE EVERYTHING IS MORE COMPLICATED.
 

### 2018-03-07 Draft2/draft2.tex
Through the intro.  May need to meld some prose into methods, we’ll see.

@@
 Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
-A key insight from this work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.
+Subsequent computational considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
+A key insight from this computational work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.
 But, it is possible to obtain such descriptors by analyzing jointly the light reflected from all of the objects in the scene.
 As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant.
-Thus evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects.
-
-*** HERE ***
-
-At the same time, this processing introduces an additional dependence.
-Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image
-
-Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
-
-***
-Subsequent work, which extended the analysis to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS), confirmed this basic insight.
-
-Seminal computational color constancy algorithms applied to a  considered a simplified case in which flat matte surfaces are illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
-\citeNP{LandRetinex}) or produce explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., .
-Subsequent computational constancy work sought to generalize both the image formation model   None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.
+Thus evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects \cite{BrainardWandellRetinex,BrainardFreeman}.
 
@@
     \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and the illumination spectrum of the light source.
+    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the object's surface reflectance of the object and the illumination.
 It also depends on geometric factors, such as the object's shape, pose, and position relative to the observer.
-The human visual system is able to account for variations in the reflected light due to such extrinsic factors and produce a percept of object color that is relatively stable with respect to such variations.
-Such invariant color perception is called color constancy.
-(b) {\bf Luminance Constancy Under Spectral Variations:} In this paper we consider the special case of luminance constancy.
-Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance (indicated on the left).
-Within each row, the surface reflectance of the spheres has the same luminance when illuminated by a standard reference illuminant, CIE D65.
-The three rows differ in this value, as can be seen by the fact that the luminance of the spheres generally decreases as we move down the columns.
-Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.
-Within each column, this relative surface reflectance is held fixed.
-For illustration, we have kept the light source and the background objects fixed across the panels.
-See Fig.~\ref{fig:studiedCases} for images with such variations.
-In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
+The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable, an ability called color constancy.
+(b) {\bf Luminance Constancy:} Images of a sphere under a fixed illuminant.
+Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance spectrum held fixed.
+The relative spectrum (shape of reflectance spectrum) varies across each row.
+Within each row, the object luminance of the spheres is constant; we define object luminance as the luminance of the light that would be reflected by the object's surface under standard illuminant CIE D65.
+The values on the left of each row provide the corresponding object luminance.
+We cast the problem of computational luminance constancy to be that of estimating object luminance from the image, across variation in other scene factors: variation in relative surface reflectance, variation in illumination, and variation in the reflectance of the other objects in the scene.}
  \end{figure}
  % REMOVE EQUATION FROM 1a. IT'S NOT DOING ANY WORK AND IT ISN'T ACCURATE IN 3D WHERE EVERYTHING IS MORE COMPLICATED.
-
-The computational work reviewed above is based on formulating an explicit model of the image formation process and the statistical properties of natural images, and leveraging these formulations to obtain an appropriate ``inverse optics" algorithm.
-An alternative approach, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors.
-Along these lines, Barron \cite{barron2015convolutional} recently developed a color balancing algorithm based on training a neural network to detect a uniform illuminant in an image by matching image templates in the chromaticity space.
-The use of supervised learning to understand human perceptual capabilities has enjoyed success in domains outside of color vision.
-Geisler and colleagues, for example, have developed a technique they refer to as accuracy maximization analysis (AMA, \citeNP{geisler2009optimal}), which learns linear filters whose output carries information that is optimized for particular perceptual tasks.
-This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus error \cite{burge2011optimal}, and disparity \cite{burge2014optimal}
-from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
-In this paper, we apply AMA, as well as comparison supervised learning algorithms to a special case of the color constancy problem (luminance constancy) and evaluate how well it performs for naturalistic image input.
-
-A difficulty in using machine learning approaches for color constancy is that these approaches require large training sets with images of scenes containing objects with known surface reflectances illuminated with known illuminations.
-Such data sets are not readily available.
-Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
-Generating databases with both the images and the ground truth scene information is not trivial.
-One approach has been to acquire images where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations \cite{NascimentoFoster2016}.
-This is somewhat painstaking, however, and in any case provides information about the illumination only at a small number of selected locations, so that generalizing across the image requires strong assumptions.
-Some progress is being made on characterizing how illumination varies over space in natural scenes \cite{mury2007spatial}, which in the longer run may guide how information from reference objects can be used to provide reasonable estimates.
-Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene \cite{funt1988color,ciurea2003large, davidPennHyperspectral}.
-% REMOVE NO DATE (n.d.) FROM THE CITATION
-These data sets have been useful for evaluating computational color constancy algorithms, but the use of posed scenes does not scale well for use with supervised learning methods which needs large training sets.
+ % MOVE (a) and (b) to upper left of each panel.
+ % DELETE NUMBERS 1 to 5 at bottom of each row.
+
+An alternative approach to computational color constancy, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors \cite{barron2015convolutional}.
+The use of supervised learning to understand perceptual capabilities for natural stimuli has enjoyed success in domains outside of color vision.
+For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \citeNP{geisler2009optimal}.
+It has been used to develop ideal observers for speed, focus error, and disparity estimation that provide excellent models of human performance \cite{burge2015optimal, burge2011optimal, burge2014optimal}.
+In this paper, we apply AMA to a special case of computational color constancy.
+
+Supervised learning requires large labelled data sets.
+Such data sets are not readily available for the study of color constancy.
+Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
+There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually \cite{funt1988color,ciurea2003large, davidPennHyperspectral}, but these are not large enough to drive supervised learning.
 
@@
 
-Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as {\em virtual natural scenes}.
-Here, in addition to employing computer graphics to render the light reaching the eye from specified scenes, we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
-We describe this approach in detail below.
-The key advantage of this approach is that we can produce large numbers of naturalistic images and the corresponding cone mosaic responses where all of the underlying scene properties are well-specified.
-This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
-This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular \cite{kovacs17shading},
+In this paper, we use high-quality computer graphics to generate large data sets of naturalistic images where the surface reflectance and illumination corresponding to each image pixel are known. 
+This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants.
+Here, we use this approach to tackle luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
+
+% MOVE ALL THIS TO DICUSSION
+%This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
+Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the Discussion.
+% \cite{baker2011database}  \cite{kovacs17shading} \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}
 % Autonmous vehicle work - ask BAW
-as well as for the generation of stimuli for the study of human perception (e.g., \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}). 
-Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.
+
+ {\em virtual natural scenes}.
+
+ we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
 

### 2018-03-15 Draft2/draft2.tex
Edited the figures

@@
 (b) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA.
-The estimates fall along the diagonal unit slope line for both linear regression and AMA.
+The estimates fall along the diagonal unit slope (blue dotted) line for both linear regression and AMA.
 The standard deviations are too small to be visible.
@@
     \end{subfigure}
-            \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.pdf}
-        \caption{Error v/s number of RFs}
-        \label{fig:ErrorVsNFilters}
-    \end{subfigure}
     \caption{{\bf Case 2:} (a) Photoreceptor response projected along the first two AMA receptive fields.
 (b) Estimated v/s assigned target object luminance for the image in case 2.
-Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
-(c) Relative error as a function of number of AMA receptive fields used for luminance estimation.
-The relative error reduces if more receptive fields are used for estimation.}
+Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.}
 \label{fig:case2Results}
+\end{figure}
+
+%%% Figure 11: RMSE vs N Filters
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
+\caption{{\bf Performance with number of RFs used for estimation:} Relative error as a function of number of AMA receptive fields used for luminance estimation.
+While most of the information is captured by the first two filters, the relative error reduces as the number of receptive fields used for luminance estimation are increased.
+We have used the first 8 RFs for estimating the luminance.}
+\label{fig:ErrorVsNFilters}
 \end{figure}
@@
 
-%% Figure Isomerization Fails
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.3	 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_a.pdf}
+%% Figure Case 3: Isomerization Fails
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.3	 \textwidth}   
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
         \caption{RFs learnt using photoreceptor response}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
         \caption{RFs learnt using contrast signal}
@@
             \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure11/Figure11_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
         \caption{Luminance estimates}
@@
 
-%%% Figure 11
-%\begin{figure}
-%\centering
-%\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
-%\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the luminance.}
-%\label{fig:RMSEvsNFilters}
-%\end{figure}
-% GET RID OF AMA FROM THE CAPTION
-
 \subsubsection{Case 4: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
-% Figure 12
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.3 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
+% Figure Case 4
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.3 \textwidth}   
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
         \caption{AMA RF Response}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
         \caption{Luminance Estimates}
@@
 \subsection{Optimal receptive fields for luminance estimation have a center surround structure}
-% Figure 14
+% Figure RFs 
 \begin{figure}
@@
 \begin{subfigure}{0.21 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
 	\caption{Case 1}
@@
     \begin{subfigure}{0.21 \textwidth}   
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
 	\caption{Case 2}
@@
         \begin{subfigure}{0.21 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
 	\caption{Case 3}
@@
         \begin{subfigure}{0.21 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_d.pdf}
 	\caption{Case 4}
@@
 
-% Figure 14
+% Figure Error Bar Graphs
 \begin{figure}
@@
 \begin{subfigure}{0.22 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_a.pdf}
 	\caption{Case 1}
@@
     \begin{subfigure}{0.22 \textwidth}   
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_b.pdf}
 	\caption{Case 2}
@@
         \begin{subfigure}{0.22 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_c.pdf}
 	\caption{Case 3}
@@
         \begin{subfigure}{0.22 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_d.pdf}
+	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_d.pdf}
 	\caption{Case 4}
@@
     \end{subfigure}
-\caption{{\bf Error comparison across models:} Comparison of optimal AMA receptive fields from one case on the images of other cases.
-Each panel shows the relative error of the estimates obtained using the linear model and the AMA receptive fields of case 1-4.
-(a) Relative error of estimates of the target object luminance of images from case 1.
+\caption{{\bf Comparison of optimal RFs across cases:} Comparison of optimal AMA receptive fields from one case on the images of other cases.
+Each panel shows the relative error estimates on the same set of images obtained using the receptive fields of the four cases (case 1-4).
+(a) Error estimates for images of case 1.
 The AMA receptive fields from all three cases perform well in this case.
-(b) Relative error for images of case 2.
-As expected, the error of the linear model on the center pixel is higher than AMA.
+(b) Error estimates for images of case 2.
 As expected, the best estimates are provided by the receptive fields of case 2.
-(c) Relative error for images of case 3.
-(d) Relative error for test images of case 4.}
+(c) Error estimates for images of case 3.
+(d) Error estimates for images of case 4.}
  \label{fig:barGraphs}

### 2018-03-15 codeForFigures/codeToMakeFigures/estimatesVsActualAMAOnly.m

@@ -13,7 +13,7 @@ if (~exist('estimatesVsActualAMA','dir'))
 end
 
 % Choose a case
-for caseNo = [9]
+for caseNo = [12]
 
 % load the files containing the estimates
 if (caseNo==9 || caseNo==11)
@@ -35,8 +35,13 @@ fig = figure;
 set(fig,'units','pixels', 'Position', [1 1 500 500]);
 hold on;
 % plot the linear and svd response
+lDiagonal = plot([0.15 0.65],[0.15 0.65],'b:','linewidth',1);
 lNaive = plot(unique(loadTheAMAFile.XTest)',0.4*ones(size(unique(loadTheAMAFile.XTest)')),naiveColor,'linewidth',2);
-lLinear = plot(unique(loadTheAMAFile.XTest)',loadTheLinearFile.cNormMeanEstimateTest,linearColor,'linewidth',2);
+if (caseNo==9 || caseNo==11)
+    lLinear = plot(unique(loadTheAMAFile.XTest)',loadTheLinearFile.MeanEstimateTest,linearColor,'linewidth',2);
+else
+    lLinear = plot(unique(loadTheAMAFile.XTest)',loadTheLinearFile.cNormMeanEstimateTest,linearColor,'linewidth',2);
+end
 % errorbar(unique(loadTheLinearFile.labelsTest)',loadTheLinearFile.cMeanSvdEstimateTest,loadTheLinearFile.cStdSvdEstimateTest,SVDColor,'linewidth',2);
 xlim([0.15 0.65]);
 ylim([0.15 0.65]);
@@ -53,12 +58,17 @@ stdEstimatedL = std(estimatedL);
 lAMA = plot(linspace(0.2,0.6,10),meanEstimatedL,AMAColor,'linewidth',2);
 axis square;
 plotfillederror(linspace(0.2,0.6,10),meanEstimatedL-stdEstimatedL,meanEstimatedL+stdEstimatedL,AMAColor);
-plotfillederror(linspace(0.2,0.6,10),loadTheLinearFile.cNormMeanEstimateTest-loadTheLinearFile.cNormStdEstimateTest,...
-    loadTheLinearFile.cNormMeanEstimateTest+loadTheLinearFile.cNormStdEstimateTest,linearColor);
+if (caseNo==9 || caseNo==11)
+    plotfillederror(linspace(0.2,0.6,10),loadTheLinearFile.MeanEstimateTest-loadTheLinearFile.StdEstimateTest,...
[…]

### 2018-03-15 codeForFigures/codeToMakeFigures/plotBarGraphsAMAOnly.m

@@ -82,12 +82,12 @@ set(h5,'FaceColor',AMAColor3);
 set(h6,'FaceColor',AMAColor4);
 
 ylim([0 0.5]);
-xlim([0.5 5.5]);
+xlim([1.5 5.5]);
 ylabel('$E_{\rm rel}$','interpreter','latex');
 % set(gca, 'XTick',[1 2 3 4],'XTickLabels', {'Naive', 'Linear Regression Center Pixel', 'SVD-LDA', 'AMA'},'TickLabelInterpreter','latex');
 set(gca, 'XTick',[1 2 3 4 5],'XTickLabels', {'Linear', 'Case 1', 'Case 2', 'Case 3', 'Case 4'},'TickLabelInterpreter','latex');
-set(gca,'FontSize',20);
-% title('Case 1');
+set(gca,'FontSize',25);
+% title('Images of case 1');
 box on;
 axis square;
 save2pdf('barGraphs2/AMAComparisionCase1.pdf',fig2,600);
@@ -114,11 +114,11 @@ set(h5,'FaceColor',AMAColor3);
 set(h6,'FaceColor',AMAColor4);
 
 ylim([0 0.5]);
-xlim([0.5 5.5]);
+xlim([1.5 5.5]);
 ylabel('$E_{\rm rel}$','interpreter','latex');
 % set(gca, 'XTick',[1 2 3 4],'XTickLabels', {'Naive', 'Linear Regression Center Pixel', 'SVD-LDA', 'AMA'},'TickLabelInterpreter','latex');
 set(gca, 'XTick',[1 2 3 4 5],'XTickLabels', {'Linear', 'Case 1', 'Case 2', 'Case 3', 'Case 4'},'TickLabelInterpreter','latex');
-set(gca,'FontSize',20);
+set(gca,'FontSize',25);
 % title('Case 1');
 box on;
 axis square;
@@ -146,11 +146,11 @@ set(h5,'FaceColor',AMAColor3);
 set(h6,'FaceColor',AMAColor4);
 
 ylim([0 0.5]);
-xlim([0.5 5.5]);
+xlim([1.5 5.5]);
 ylabel('$E_{\rm rel}$','interpreter','latex');
 % set(gca, 'XTick',[1 2 3 4],'XTickLabels', {'Naive', 'Linear Regression Center Pixel', 'SVD-LDA', 'AMA'},'TickLabelInterpreter','latex');
[…]

### 2018-03-16 Draft2/draft2.tex
small edits

@@
 
-Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
-Subsequent computational considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
+Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
+Subsequent computational work considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
 A key insight from this computational work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.
@@
     \end{subfigure}
-    \begin{subfigure}{0.45 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
+    \begin{subfigure}{0.55 \textwidth}   
+        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.png}
         \caption{}
@@
  \end{figure}
- % REMOVE EQUATION FROM 1a. IT'S NOT DOING ANY WORK AND IT ISN'T ACCURATE IN 3D WHERE EVERYTHING IS MORE COMPLICATED.
- % MOVE (a) and (b) to upper left of each panel.
- % DELETE NUMBERS 1 to 5 at bottom of each row.
 
@@
 The use of supervised learning to understand perceptual capabilities for natural stimuli has enjoyed success in domains outside of color vision.
-For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \citeNP{geisler2009optimal}.
-It has been used to develop ideal observers for speed, focus error, and disparity estimation that provide excellent models of human performance \cite{burge2015optimal, burge2011optimal, burge2014optimal}.
+For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal}.
+It has been used to develop ideal observers for speed, focus error, and disparity estimation that provide excellent models of human performance \cite{burge2011optimal, burge2014optimal, burge2015optimal}.
 In this paper, we apply AMA to a special case of computational color constancy.
@@
 Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
-There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually \cite{funt1988color,ciurea2003large, davidPennHyperspectral}, but these are not large enough to drive supervised learning.
+There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}; \citeauthor{davidPennHyperspectral}), but these are not large enough to drive supervised learning.
 
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-		\includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_a.jpeg}
+		\includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_a.png}
 		\caption{Case 2}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_b.jpeg}
+        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_b.png}
         \caption{Case 3}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_c.jpeg}
+        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_c.png}
         \caption{Case 4}
@@
 (a) Case 2: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable, (b) Case 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Case 4: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
-As in \ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
+As in Fig.~\ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
 Moreover, across the four panels (Fig.~\ref{fig:introExampleFigure} \& Fig.~\ref{fig:studiedCases}), spheres in corresponding locations have the same surface reflectance.

### 2018-03-21 Draft2/draft2.tex
Today’s edits

@@
 Next, we simulate the response of the retinal cones to these multispectral images using an accurate model of the early visual system.
-We then use supervised learning methods on these labeled cone response to identify the computations that lead to accurate luminance estimation.
+We then use supervised learning methods on these labeled cone responses to identify the computations that lead to accurate luminance estimation.
 We show that if only either target, or background, or illumination spectra are allowed to vary, the standard luminance can be estimated through simple transformations of the cone responses.
@@
 
-Supervised learning requires large labelled data sets.
+Supervised learning requires large labeled data sets.
 Such data sets are not readily available for the study of color constancy.
@@
 There are four key parts to our methods.
-The first is how we generate a labelled set of training data for our supervised learning algorithms.
-The second is how we model the transformations applied by the early visual system to generate modeled responses of the cone photoreceptor mosaic.
-The third is the details of the supervised learning method (AMA) that we apply to the labelled training data.
-And the fourth is how we evaluate the performance of the algorithm.
-We describe each of these in the sections below.
-
-\subsection{Labelled image database} \label{method:VirtualWorld}
+First we generate a labeled set of training images.
+Second we model the responses of the cone photoreceptor mosaic to the labeled images.
+Third we apply AMA to the cone responses to learn task-optimal receptive fields (RFs).
+Fourth we evaluate how well the responses of the RFs may be decoded to achieve luminance constancy.
+
+\subsection{Labeled training data} \label{method:VirtualWorld}
 % Figure 3
@@
 \subsubsection{Virtual naturalistic scenes}
-The light that reflects off an object and reaches our eyes depends on many factors.
-These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer.
-In natural scenes, these spectral and geometrical factors vary considerably.
-To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors.
-We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene.
-Under natural conditions it is difficult to control and quantify every such parameter in a scene.
-Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.
-
-To overcome this  challenge, we have developed an image rendering software pipeline that allows us to specify a virtual, but naturalistic, statistical model of visual scenes with parametric control over factors in natural scenes.
-The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
-It then renders a multispectral 2D image of each modeled visual scene.
-Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
-In addition, our software simulates the responses of retinal cones to the rendered multispectral images using a realistic model of the early human visual system.
-Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
-Our software, which is written in MATLAB, is freely available through a public respository: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
-It builds on several other open source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
-Below we refer to the software pipeline as VWCC (for Virtual World Color Constancy).
+The light that reflects from objects to the eyes depends on many factors.
+These include the surface reflectance, texture, material and geometry of the objects, the spectra of the illuminants, and the position of the observer.
+We developed a rendering pipeline that allows us to specify models of naturalistic scenes.
+The pipeline harnesses computer graphics to render, for each scene, a corresponding image.
+The renderer traces the flow of light through the scene as it interacts with object surfaces, so that the images are physically accurate.
+Because each image is rendered from a known scene description, each image pixel can be labeled with the surface reflectance of the corresponding scene object.
+By incorporating statistical models of the variation of object surface reflectance and daylight illumination, the pipeline allows us to produce large labeled sets of images that capture much of the task-relevant statistical structure of natural scenes.
+
+We refer to the software pipeline as Virtual World Color Constancy (VWCC).
+It is written in Matlab and is freely available: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
+VWCC builds on other open-source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
 
@@
 
-The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}).
-The base scene is a 3D model that defines a rendering space.
-It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position.
-VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses.
-We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly.
-We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene.
-Tame base scenes may also be created {\it de novo} using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).
-The overall spatial scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness.
-If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes.
-As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library.
-Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).
-
-VWCC provides an option for inserting 3D objects and lights sources into the base scene.
-Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted into the library base scene.
-The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from object descriptions made available on the Internet.
-The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.
-The position (Fig.~\ref{fig:targetPositionVariation}), size and orientation (Fig.~\ref{fig:targetSizeOrientation})of the inserted objects and lights may be specified programatically or chosen randomly under constraints provided by the base scene meta-data.
+The purpose of VWCC is to allow us to specify and render a large set of diverse scenes.
+
+VWCC includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
+Base scenes specify an arrangment of objects and light sources, and provide a starting point for constructing more complex scenes via the placement of additional objects and light sources.
+To guide where to put such additional objects and light sources, base scenes are annotated with meta data.
+To render an image of a scene, it is necessary to specify a viewpoint.
+The meta data also includes information to guide selection of the viewpoint.
+
+VWCC contains a collection of objects that may be inserted into base scenes (Fig.~\ref{fig:libraryWithTarget}).
+It also allows positioning of additional point and area lights.
+In addition, VWCC provides the user with control over key scene properties.
+These include the position, size and pose of inserted objects, the reflectance of surfaces, and the spectra of illuminants (Fig.~\ref{fig:targetPositionVariation}).
+% REORDER FIGURE 5 COLUMNS d -> e -> a -> b -> c.
+
 Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.

### 2018-03-22 Draft2/draft2.tex
Today’s edits

@@
 
-% MOVE ALL THIS TO DICUSSION
-%This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
-Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the Discussion.
-% \cite{baker2011database}  \cite{kovacs17shading} \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}
-% Autonmous vehicle work - ask BAW
-
- {\em virtual natural scenes}.
-
- we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
-
-In this initial work, we do not tackle the full problem of color constancy.
-Rather, as a point of departure, we consider the computational problem of estimating a single attribute of object surface reflectance, which we refer to as surface luminance.
-We compute object luminance from an object's surface reflectance function as follows.
-We compute the light that would be reflected to the eye from a flat matte object with that surface reflectance, when the object is diffusely illuminated by the standard CIE daylight spectrum D65 \cite{CIE86}.
+We define the computational problem of luminance constancy as that of estimating what we call surface luminance. 
+Surface luminance is a measure of the overall amount of light that a surface reflects.
+We define
+
+A surface' luminance is the luminance of the light that would be reflected to the eye from a flat matte object with that surface reflectance, when the object is diffusely illuminated by the standard CIE daylight spectrum D65 \cite{CIE86}.
 We then compute the luminance of this reflected light, using the CIE 1931 photopic luminosity function \cite{CIE86}, and divide this by the luminance of a perfectly reflecting diffuser (surface reflectance of one at all wavelengths) when that is computed in the same way.
@@
 A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimated.
+
+% MOVE ALL THIS TO DICUSSION
+%This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
+Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the Discussion.
+% \cite{baker2011database}  \cite{kovacs17shading} \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}
+% Autonmous vehicle work - ask BAW
+
+ {\em virtual natural scenes}.
+
+ we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
 
@@
 \subsubsection{Virtual naturalistic scenes}
+
 The light that reflects from objects to the eyes depends on many factors.
 These include the surface reflectance, texture, material and geometry of the objects, the spectra of the illuminants, and the position of the observer.
-We developed a rendering pipeline that allows us to specify models of naturalistic scenes.
-The pipeline harnesses computer graphics to render, for each scene, a corresponding image.
-The renderer traces the flow of light through the scene as it interacts with object surfaces, so that the images are physically accurate.
-Because each image is rendered from a known scene description, each image pixel can be labeled with the surface reflectance of the corresponding scene object.
+We developed a rendering package that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
+The package harnesses an open-source computer graphics renderer  \cite{jakob2015mitsuba} to produce physically-accurate images from the scene models.
+Because each image is rendered from a known scene model, each image pixel can be labeled with the surface reflectance of the corresponding scene object.
 By incorporating statistical models of the variation of object surface reflectance and daylight illumination, the pipeline allows us to produce large labeled sets of images that capture much of the task-relevant statistical structure of natural scenes.
-
-We refer to the software pipeline as Virtual World Color Constancy (VWCC).
-It is written in Matlab and is freely available: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
-VWCC builds on other open-source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
 
@@
 
-The purpose of VWCC is to allow us to specify and render a large set of diverse scenes.
-
-VWCC includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
-Base scenes specify an arrangment of objects and light sources, and provide a starting point for constructing more complex scenes via the placement of additional objects and light sources.
-To guide where to put such additional objects and light sources, base scenes are annotated with meta data.
-To render an image of a scene, it is necessary to specify a viewpoint.
-The meta data also includes information to guide selection of the viewpoint.
-
-VWCC contains a collection of objects that may be inserted into base scenes (Fig.~\ref{fig:libraryWithTarget}).
-It also allows positioning of additional point and area lights.
-In addition, VWCC provides the user with control over key scene properties.
-These include the position, size and pose of inserted objects, the reflectance of surfaces, and the spectra of illuminants (Fig.~\ref{fig:targetPositionVariation}).
+Our software package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
+Base scenes specify an arrangement of objects and light sources.
+Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}).
+Once the position, size and pose of the inserted objects has been set, our package allows the assignment of a surface reflectance function to each object in the scene and a spectral power distribution to each light source (Fig.~\ref{fig:VWCCTransformations}).
+This provides a complete scene model which can be rendered from any specified viewpoint.
 % REORDER FIGURE 5 COLUMNS d -> e -> a -> b -> c.
 
-Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.
+In the present work, we used our package to generate datasets of naturalistic scenes and corresponding images.
+We used one fixed base scene and inserted a target object of fixed shape and size into this scene.
+Across scenes, we systematically varied the reflectance of the target object, and randomly varied the reflectance of the other objects and the spectral power distributions of the light sources.
+
+The variation within our datasets captures the essence of the computational problem of lightness constancy.
+
+ fixed target object, but varied the surface reflectance of the objects in the scene and the spectra of the light sources.
+The target object
+
+In the present work, we insert one target object and one additional light source into a fixed base scene, and vary object reflectance and illuminant spectra.
+We then insert a camera for rendering at a user specified position and point this camera at the target object.
+We ensure that a 9 pixel by 9 pixel region at the center of the image corresponds to light reflected from the target object, which amounts to verifying that the target object is not occluded along the camera's line of sight.
+For each rendered scene, we specify the surface reflectance of the target object, which allows us to control both its surface luminance as well as its relative surface reflectance.
+The specified surface luminance provides the requisite label for the scene and resultant cone mosaic responses.
+
+We render scenes using the \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba} rendering package, driven by our \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3} rendering pipeline.
+
+For the images used for the primary results reported in this paper, we used the ``{\it Library}'' base scene from the VWCC  and the ``{\it Big Ball}'' object as the target object.
+We also inserted a spherical light source with the same ``{\it Big Ball}'' shape.
+The position, and size of the inserted object, light source and the camera were held fixed for all the images analyzed in this work, i.e., the scene geometry did not vary.
+Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene.
+The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:introExampleFigure} \& Fig.~\ref{fig:studiedCases}).
+2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel.
+A $51 \times 51$ pixel patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
+
+It is written in Matlab and is freely available: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
+VWCC builds on other open-source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
 
@@
 The camera points to the center of the pixel.
-}\label{fig:VWCCTransformations}
-\end{figure}
-
-Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene.
+\label{fig:VWCCTransformations}}
+\end{figure}
+
+%Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene.
 We also assign an illuminant spectral power distribution to each light source in the scene.
@@
 In the present work, we use simple choices for texture (all surfaces spatially uniform) and material property (all surfaces matte) and focus on variation in surface spectral reflectance.
-
-In the present work, we insert one target object and one additional light source into a fixed base scene, and vary reflectance and illuminant spectra.
-We then insert a camera for rendering at a user specified position and point this camera at the target object.
-We ensure that a 9 pixel by 9 pixel region at the center of the image corresponds to light reflected from the target object, which amounts to verifying that the target object at its inserted position was not occluded by other objects in the line of sight from camera.
-For each rendered scene, we specify the surface reflectance of the target object, which allows us to control both its surface luminance as well as its relative surface reflectance.
-The specified surface luminance provides the requisite label for the scene and resultant cone mosaic responses.
-
-We render scenes using the \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba} rendering package, driven by our \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3} rendering pipeline.
-
-For the images used for the primary results reported in this paper, we used the ``{\it Library}'' base scene from the VWCC  and the ``{\it Big Ball}'' object as the target object.
-We also inserted a spherical light source with the same ``{\it Big Ball}'' shape.
-The position, and size of the inserted object, light source and the camera were held fixed for all the images analyzed in this work, i.e., the scene geometry did not vary.
-Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene.
-The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:introExampleFigure} \& Fig.~\ref{fig:studiedCases}).
-2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel.
-A $51 \times 51$ pixel patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
 

### 2018-03-24 Draft2/draft2.tex
Luminous reflectance factor

@@
 
-We define the computational problem of luminance constancy as that of estimating what we call surface luminance. 
-Surface luminance is a measure of the overall amount of light that a surface reflects.
-We define
+We define the computational problem of luminance constancy as that of estimating the luminous reflectance factor of the diffuse component of an object's surface reflectance function.
+The luminous reflectance factor is a measure of the overall amount of light reflected by a matte surface.
+More precisely, the luminous reflectance factor is the normalized luminance of the light that would
+be reflected to the eye from a flat matte object with that the specified surface reflectance function, when the object is diffusely illuminated by a reference illuminant.
+The normalization factor is 100 divided by the luminance of the reference illuminant, so that luminous reflectance factors range between 0 and 100.
+Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance  \cite{CIE86}.
 
-A surface' luminance is the luminance of the light that would be reflected to the eye from a flat matte object with that surface reflectance, when the object is diffusely illuminated by the standard CIE daylight spectrum D65 \cite{CIE86}.
-We then compute the luminance of this reflected light, using the CIE 1931 photopic luminosity function \cite{CIE86}, and divide this by the luminance of a perfectly reflecting diffuser (surface reflectance of one at all wavelengths) when that is computed in the same way.
-This procedure allows us to assign to any surface reflectance a single surface luminance value.
-Because the perceived luminance of an object is approximately (but by no means exactly, see \citeNP{wyszecki1986color}) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of {\em luminance constancy}.
-This is a generalization of the way this term is often used, where it refers more specifically to the stability of perceived luminance across images of scenes where all objects and illuminants are achromatic \cite{gilchrist2006seeing}.
-Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (see  Fig.~\ref{fig:introExampleFigure}).
-A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimated.
-
-% MOVE ALL THIS TO DICUSSION
+% MOVE THIS TO DICUSSION
 %This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
@@
 
- {\em virtual natural scenes}.
-
- we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
-
-Even within the special case of luminance constancy, there are many scene manipulations that could be considered.
+% NOT SURE WE NEED ANY OF THIS.  PROBABLY NOT HERE IF WE DO
+%Even within the special case of luminance constancy, there are many scene manipulations that could be considered.
 The set of manipulations we focus on here are illustrated by Fig.~\ref{fig:introExampleFigure} and the three panels of Fig.~\ref{fig:studiedCases}.
@@
 In this paper, we focus on the problem of luminance constancy within scene ensembles where these geometric factors are held fixed.
-
-We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
+%
+%We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
 For variations only in target object reflectance spectra (case 1) or just the target and background objects reflectance spectra (case 2), object luminance can be recovered directly from the light reflected off the target object.
@@
 We discuss the implications of such receptive fields on luminance constancy.
-
-The rest of this paper is organized as follows.
-In the \nameref{Methods} section, we describe in detail the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}) using our software pipeline {\rm Virtual world color constancy}, the process to simulate the response of retinal cone photoreceptors to these images using a standard model of the early visual system (\nameref{method:Isetbio}) and the supervised learning method (AMA) used in our analysis (\nameref{method:SupervisedLearning}).
-In the \nameref{Results} section, we show the estimates and performance of the supervised methods for the four cases mentioned above.
-We conclude the paper with the implication of our results in the \nameref{Discussion} section.
 

### 2018-03-26 Draft2/draft2.tex
Today’s edits

@@
 The mechanism of this behaviorally significant invariance detection ability remains largely unknown.
-To understand the computational principles that lead to such invariant perception, we study the perception of object luminance under spectral variations in 3D scenes.
+To understand the computational principles that lead to such invariant perception, we study the perception of LRV under spectral variations in 3D scenes.
 Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the perceived luminance of an object.
@@
 The relative spectrum (shape of reflectance spectrum) varies across each row.
-Within each row, the object luminance of the spheres is constant; we define object luminance as the luminance of the light that would be reflected by the object's surface under standard illuminant CIE D65.
-The values on the left of each row provide the corresponding object luminance.
-We cast the problem of computational luminance constancy to be that of estimating object luminance from the image, across variation in other scene factors: variation in relative surface reflectance, variation in illumination, and variation in the reflectance of the other objects in the scene.}
+Within each row, the light reflectance value (LRV) of the spheres is constant.
+The values on the left of each row provide the corresponding LRV.
+We cast the problem of computational luminance constancy to be that of estimating LRV from the image, across variation in other scene factors: variation in relative surface reflectance, variation in illumination, and variation in the reflectance of the other objects in the scene.}
  \end{figure}
@@
 
-We define the computational problem of luminance constancy as that of estimating the luminous reflectance factor of the diffuse component of an object's surface reflectance function.
-The luminous reflectance factor is a measure of the overall amount of light reflected by a matte surface.
-More precisely, the luminous reflectance factor is the normalized luminance of the light that would
-be reflected to the eye from a flat matte object with that the specified surface reflectance function, when the object is diffusely illuminated by a reference illuminant.
-The normalization factor is 100 divided by the luminance of the reference illuminant, so that luminous reflectance factors range between 0 and 100.
-Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance  \cite{CIE86}.
-
-% MOVE THIS TO DICUSSION
+% I found the definition of light reflectance value on the web, sort of.  Need to find the right citable reference and or a term for the same thing that
+% we can find a reference for.
+We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of an object's surface reflectance function.
+The LRV is a measure of the overall amount of light reflected by surface.
+More precisely, the LRV is the luminance of the light that would
+be reflected to the eye from an object with the specified surface reflectance function when the object is illuminated by a reference illuminant,
+normalized by the luminance of the reference illuminant itself.
+Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function \cite{CIE86}.
+LRVs are typically expressed in percent, so that they range from 0 to 100.
+
+% MOVE THIS TO DISCUSSION
 %This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
@@
 %We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (case 1) or just the target and background objects reflectance spectra (case 2), object luminance can be recovered directly from the light reflected off the target object.
-For case 3, where both the target object reflectance and light source spectra vary, object luminance can be recovered from the contrast between the target and the background.
+For variations only in target object reflectance spectra (case 1) or just the target and background objects reflectance spectra (case 2), LRV can be recovered directly from the light reflected off the target object.
+For case 3, where both the target object reflectance and light source spectra vary, LRV can be recovered from the contrast between the target and the background.
 When all the spectral features in the scene are allowed to change (case 4), the standard luminance can not be recovered simply from the cone response or the contrast.
@@
 Across scenes, we systematically varied the reflectance of the target object, and randomly varied the reflectance of the other objects and the spectral power distributions of the light sources.
+We generated five distinct datasets.
+Across these datasets, the luminance constancy problem is progressively more difficult (Fig.~\ref{fig:studiedCases}).
+In the first dataset (Condition 0), the only source of stimulus variation was in the task relevant quantity, the LRV.
+Here, we fixed the relative reflectance spectrum of the target object, the reflectance spectra of the other objects in the scene, and the spectral power distribution of the light sources fixed.
+We used 10 LRV values, equally spaced between 20 and 60.
+Condition 0 provides a baseline.
+
+In the remaining conditions, we systematically introduced variation in scene factors other than the LRV.
+
+In the second dataset (Condition 1), we introduced variation in the relative reflectance spectrum of the target object.
+In essence, this condition introduces color variation across target objects that have the same LRV.
+
+Conditions 2 and 3 each increase the variation relative to Condition 1.
+
+In Condition 2, in addition to the relative reflectance spectrum of the target
+we varied the reflectance spectra of the background objects,
+while holding the the spectral power distribution of the light sources
+constant.
+
+In Condition 3, in addition to the relative reflectance spectrum of the target
+we varied the spectral power distribution of the light sources,
+while holding the reflectance spectra of the background objects constant.
+
+Finally, in Condition 4 we varied all three factors (relative reflectance spectrum,
+reflectance spectra of the background objects, spectral power distribution of the light sources).
+
+Condition 0: Baseline
+Condition 1: Target Color Only
+Condition 2: Target Color and Background
 
@@
 We perform two steps to decode the luminance of the target object from the cone isomerization.
-First, we use AMA to learn the linear filters that are optimal for estimating the target object luminance.
+First, we use AMA to learn the linear filters that are optimal for estimating the target LRV.
 Second, we determine how to optimally decode the luminance from the response of these filters to arbitrary stimuli.
@@
 
-More concretely, let us assume that there are $N_{\nu}$ possible values of the target object luminance levels ($\{Y_k: k\in[1,N_{\nu}] \}$) and the $l$'th image corresponding to the $k$'th luminance level is represented as $s_{kl}$.
+More concretely, let us assume that there are $N_{\nu}$ possible values of the target LRV levels ($\{Y_k: k\in[1,N_{\nu}] \}$) and the $l$'th image corresponding to the $k$'th luminance level is represented as $s_{kl}$.
 Also, assume that there is a set of linear receptive fields {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
@@
 We start with case 1, where only the reflectance spectrum of the target object is allowed to vary, and show that in this case the luminance can be estimated directly from the photoreceptor response.
-We then progressively increase the complexity of the spectral conditions and explain the correspondingly complex computations that are required to estimate the target object luminance.
+We then progressively increase the complexity of the spectral conditions and explain the correspondingly complex computations that are required to estimate the target LRV.
 Next, we show the optimal AMA receptive fields for each one of the spectral cases discussed in this work.
@@
 We start with the results of the simplest type of spectral variation where only the target object relative surface reflectance spectrum is allowed to change. 
-We used AMA to learn a set of linear receptive fields that are optimal for estimating target object luminance from the model cone photoreceptor response to the images from this case.
+We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV from the model cone photoreceptor response to the images from this case.
 Fig.~\ref{fig:case1RFResponse} shows the projection of the photoreceptor response along the first two optimal AMA receptive fields. 
 Clearly, there exists a subspace along which the photoreceptor response separates according to the luminance level assigned to the target object. 
-Thus, the target object luminance can be obtained by projecting the photoreceptor response along these AMA receptive fields. 
+Thus, the target LRV can be obtained by projecting the photoreceptor response along these AMA receptive fields. 
 We used such projections and a generalized Bayes' decoder (see methods) to estimate the luminance of the target objects in the test set stimuli. 
 Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test stimuli in case 1. 
-We show the estimates obtained by AMA and two null models: a naive method that assigns the average target object luminance across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object (see Methods).
+We show the estimates obtained by AMA and two null models: a naive method that assigns the average target LRV across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object (see Methods).
 As expected, in the absence of any external source of variation, the photoreceptor response is proportional to the luminance of the target object, and hence can be easily estimated by both AMA and linear regression.
@@
 The variance in the estimates increases with assigned luminance. 
-This is because the isomerization noise is directly proportional to the light reflected from the target object and is higher at higher values of the target object luminance.
+This is because the isomerization noise is directly proportional to the light reflected from the target object and is higher at higher values of the target LRV.
 
@@
     \caption{{\bf Case 2:} (a) Photoreceptor response projected along the first two AMA receptive fields.
-(b) Estimated v/s assigned target object luminance for the image in case 2.
+(b) Estimated v/s assigned target LRV for the image in case 2.
 Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.}
@@
 \subsubsection{Case 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed}
-For the spectral variations of case 3, the AMA receptive fields learnt on the photoreceptor response to the images does a very poor job in predicting the target object luminance (Fig.~\ref{fig:isomerizationFails}).
+For the spectral variations of case 3, the AMA receptive fields learnt on the photoreceptor response to the images does a very poor job in predicting the target LRV (Fig.~\ref{fig:isomerizationFails}).
 This is because, since the illuminant spectra varies in this case, the photoreceptor response is not directly proportional to the target object surface anymore. 
-But, since the background surfaces are fixed in this case, the ratio between the response of  photoreceptors corresponding to the target object and the background remains proportional to the target object luminance.
+But, since the background surfaces are fixed in this case, the ratio between the response of  photoreceptors corresponding to the target object and the background remains proportional to the target LRV.
 This is because a change in illuminant spectra produces the same effect in both the target object and the background object. 
-Thus, the AMA receptive fields learnt on the contrast normalized photoreceptor response (see Methods) can be used to predict the target object luminance (Fig.~\ref{fig:constrastWorks}). 
-Fig.~\ref{fig:case10Results} shows the estimated target object luminance v/s the assigned luminance for the images in case 3 obtained using the contrast normalized representation. 
-AMA receptive fields provide excellent predictions of the target object luminance. 
+Thus, the AMA receptive fields learnt on the contrast normalized photoreceptor response (see Methods) can be used to predict the target LRV (Fig.~\ref{fig:constrastWorks}). 
+Fig.~\ref{fig:case10Results} shows the estimated target LRV v/s the assigned luminance for the images in case 3 obtained using the contrast normalized representation. 
+AMA receptive fields provide excellent predictions of the target LRV. 
 The predictions are much better compared to that of a linear model that only considers the (contrast normalized) response of the photoreceptors corresponding to the center pixel of the target object.
@@
 The response at each luminance level separates much better in this representation.
-(c) Estimated v/s assigned target object luminance for the image in case 3.
+(c) Estimated v/s assigned target LRV for the image in case 3.
 Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
@@
     \caption{{\bf Case 3:} (a) Contrast normalized photoreceptor response projected along the first two AMA receptive fields.
-(b) Target object luminance estimates v/s assigned luminance for images in case 3.
+(b) Target LRV estimates v/s assigned luminance for images in case 3.
 The AMA estimates are unbiased and have smaller relative error compared to linear model.}
@@
 Here we allow all three types of spectra to change from image to image.
-In this case, neither the photoreceptor response (as in Case 1 and 2), nor any simple transformation of the response (case 3) can provide the target object luminance.We used AMA to learn the receptive fields using the contrast normalized cone photoreceptor response from stimuli in case 4.
+In this case, neither the photoreceptor response (as in Case 1 and 2), nor any simple transformation of the response (case 3) can provide the target LRV.We used AMA to learn the receptive fields using the contrast normalized cone photoreceptor response from stimuli in case 4.
 Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 4.
 We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:ErrorVsNFilters}). 
-The AMA receptive fields do an excellent job of predicting the target object luminance. 
+The AMA receptive fields do an excellent job of predicting the target LRV. 
 The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}). 
@@
 
-Fig.~\ref{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for estimating the target object luminance for the four types of spectral variations studied in this work.
+Fig.~\ref{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for estimating the target LRV for the four types of spectral variations studied in this work.
 The receptive fields are ranked in ascending order of the value of the cost function associated with them.
@@
 \subsection{The receptive fields of complex case generalize on simpler cases}
-Fig.~\ref{fig:barGraphs} shows the relative error for the estimates of the target object luminance obtained using the linear model and AMA.
+Fig.~\ref{fig:barGraphs} shows the relative error for the estimates of the target LRV obtained using the linear model and AMA.
 We show the relative error of the estimates obtained using the AMA receptive fields from all cases.
@@
 We used the software generated labeled images in a supervised manner to understand luminance constancy under four types of spectral manipulations (Fig.~\ref{fig:introExampleFigure}-Fig.~\ref{fig:studiedCases}).
-We found that target object luminance can be recovered through simple manipulation of the retinal cone responses for cases where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, or the light source illumination spectra.
+We found that target LRV can be recovered through simple manipulation of the retinal cone responses for cases where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, or the light source illumination spectra.
 When variations are allowed only in the target object surface reflectance spectrum, or only the target object and the background objects surface reflectance spectra, the luminance can be estimated directly from the response of retinal cone photoreceptors.
 If the background spectra is fixed, but the target object reflectance spectrum and the light source illumination spectra are varying, the luminance can be obtained from the contrast between the cone response corresponding to the target and the background.
-When all three spectral variations are allowed simultaneously, one needs additional information to obtain the target object luminance.
+When all three spectral variations are allowed simultaneously, one needs additional information to obtain the target LRV.
 

### 2018-03-28 Draft2/draft2.tex
Today’s edits

@@
 First we generate a labeled set of training images.
-Second we model the responses of the cone photoreceptor mosaic to the labeled images.
+Second we use a model of the early visual system the compute the responses of the cone photoreceptor mosaic to the labeled images.
 Third we apply AMA to the cone responses to learn task-optimal receptive fields (RFs).
@@
 By incorporating statistical models of the variation of object surface reflectance and daylight illumination, the pipeline allows us to produce large labeled sets of images that capture much of the task-relevant statistical structure of natural scenes.
+% Reference RTB and VWCC where we say "We developed a rendering package".
+% \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}.
+%\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}
 
@@
     \end{subfigure}
-\caption{{\bf Library base scene with inserted objects.} The VWCC software was used to insert different objects into the library base scene, with each panel showing a different object.
+\caption{{\bf Library base scene with inserted objects.} The rendering package was used to insert different objects into the library base scene, with each panel showing a different object.
 The objects were inserted at a location in the image and then the camera was pointed at the object, so that the object's image is at the center of the rendered image.
@@
 
-Our software package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
+Our rendering package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
 Base scenes specify an arrangement of objects and light sources.
@@
 We used one fixed base scene and inserted a target object of fixed shape and size into this scene.
-Across scenes, we systematically varied the reflectance of the target object, and randomly varied the reflectance of the other objects and the spectral power distributions of the light sources.
-We generated five distinct datasets.
-Across these datasets, the luminance constancy problem is progressively more difficult (Fig.~\ref{fig:studiedCases}).
-In the first dataset (Condition 0), the only source of stimulus variation was in the task relevant quantity, the LRV.
-Here, we fixed the relative reflectance spectrum of the target object, the reflectance spectra of the other objects in the scene, and the spectral power distribution of the light sources fixed.
+We generated five distinct datasets: Conditions 0 through 4.
+Across these datasets the luminance constancy problem, estimating the target object LRV,
+becomes progressively more difficult (Fig.~\ref{fig:studiedCases}).
+
+In Condition 0, the only source of stimulus variation was in the task relevant quantity, the target object LRV.
+Here, we fixed target object color (i.e. the relative reflectance spectrum of the target object),
+the reflectance spectra of the background objects, and the spectral power distributions of the light sources.
 We used 10 LRV values, equally spaced between 20 and 60.
-Condition 0 provides a baseline.
-
-In the remaining conditions, we systematically introduced variation in scene factors other than the LRV.
-
-In the second dataset (Condition 1), we introduced variation in the relative reflectance spectrum of the target object.
-In essence, this condition introduces color variation across target objects that have the same LRV.
-
-Conditions 2 and 3 each increase the variation relative to Condition 1.
-
-In Condition 2, in addition to the relative reflectance spectrum of the target
-we varied the reflectance spectra of the background objects,
+Condition 0 defines a baseline. In this condition, all images with the the same value of the LRV are identical.
+
+In the remaining conditions, we systematically introduced variation in scene factors other than the target object LRV.
+In Condition 1, we introduced variation in target object color but held the other factors fixed.
+
+Conditions 2, 3 and 4 each increase the variation relative to Condition 1.
+In Condition 2, in addition to the color of the target object,
+we varied the reflectance spectra of the background objects
 while holding the the spectral power distribution of the light sources
 constant.
-
-In Condition 3, in addition to the relative reflectance spectrum of the target
-we varied the spectral power distribution of the light sources,
+In Condition 3, in addition to the color of the target object,
+we varied the spectral power distribution of the light sources
 while holding the reflectance spectra of the background objects constant.
-
-Finally, in Condition 4 we varied all three factors (relative reflectance spectrum,
+Finally, in Condition 4 we varied all three factors (target object color,
 reflectance spectra of the background objects, spectral power distribution of the light sources).
-
-Condition 0: Baseline
-Condition 1: Target Color Only
-Condition 2: Target Color and Background
-
-The variation within our datasets captures the essence of the computational problem of lightness constancy.
-
- fixed target object, but varied the surface reflectance of the objects in the scene and the spectra of the light sources.
-The target object
-
-In the present work, we insert one target object and one additional light source into a fixed base scene, and vary object reflectance and illuminant spectra.
-We then insert a camera for rendering at a user specified position and point this camera at the target object.
-We ensure that a 9 pixel by 9 pixel region at the center of the image corresponds to light reflected from the target object, which amounts to verifying that the target object is not occluded along the camera's line of sight.
-For each rendered scene, we specify the surface reflectance of the target object, which allows us to control both its surface luminance as well as its relative surface reflectance.
-The specified surface luminance provides the requisite label for the scene and resultant cone mosaic responses.
-
-We render scenes using the \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba} rendering package, driven by our \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3} rendering pipeline.
-
-For the images used for the primary results reported in this paper, we used the ``{\it Library}'' base scene from the VWCC  and the ``{\it Big Ball}'' object as the target object.
+The variation within our datasets captures the essence of the computational problem of lightness constancy
+up to effects of scene geometry, an additional richness that we do not address in this paper.
+
+%Condition 0: Baseline
+%Condition 1: Target Color Only Variation
+%Condition 2: Target Color and Background
+%Condition 3: Target Color and Illuminant
+%Condition 4: Everything
+
+For the primary results we used the ``{\it Library}'' base scene and a sphere as the target object.
 We also inserted a spherical light source with the same ``{\it Big Ball}'' shape.
-The position, and size of the inserted object, light source and the camera were held fixed for all the images analyzed in this work, i.e., the scene geometry did not vary.
-Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene.
-The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:introExampleFigure} \& Fig.~\ref{fig:studiedCases}).
-2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel.
-A $51 \times 51$ pixel patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
-
-It is written in Matlab and is freely available: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
-VWCC builds on other open-source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
+The position and size of the inserted object, light source and the camera were held fixed.
+Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra.
+We describe these models below.
+Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
+A $51 \times 51$ pixel patch was cropped around the target object for further analysis.
+This corresponded to $1 \times 1$ degrees of visual angle for the model of the early visual system, also described below.
 
@@
 
-We generate illumination spectra  through random statistical sampling of a dataset of naturally occurring illuminants, the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{peyvandi2016colorimetric}.
-These spectra are shown on a log intensity scale in Fig.~\ref{fig:granadaSpectra}, which illustrates that the overall intensity of natural daylights varies over several orders of magnitude, and in normalized format in Fig.~\ref{fig:rescaledGranada}, which illustrates that the relative spectra also vary considerably.
+To generate illumination spectra, we developed a statistical model of the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{peyvandi2016colorimetric} and sample randomly from the model.
+The overall intensity of the measurements spans approximately three orders of magnitude.
+Figure~\ref{fig:rescaledGranada} plots the measurements in normalized form to make apparent the variation in the relative spectra.
+
+Our statistical model approximates these normalized shapes using their first 6 principle components, and models the variation in these components with
+a 6-dimensional Gaussian whose mean and covariance matrix match the dataset's sample mean and covariance of the weights on these components.
+To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
+Figure~ref{ENTER REF} .....
+and reconstruct t
+obtained from the daylight dataset.
  In our procedure, we first approximate the spectra in the dataset using principle component analysis (PCA).
 We then decompose the spectra in terms of the PCA basis vectors corresponding to the 6 largest PCA eigenvalues.
-Next, we sample from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a multivariate gaussian whose mean and covariance matrix match the sample mean and covariance obtained from the daylight dataset.
-Finallly, we use the sampled weights to reconstruct sampled spectra.
+Next, we sample from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a  Finallly, we use the sampled weights to reconstruct sampled spectra.
 This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman \cite{BrainardFreeman}.

### 2018-03-28 Draft2/draft2.tex
added references and rordered figures

@@
 These include the surface reflectance, texture, material and geometry of the objects, the spectra of the illuminants, and the position of the observer.
-We developed a rendering package that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
+We developed a rendering package (\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}, \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}) that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
 The package harnesses an open-source computer graphics renderer  \cite{jakob2015mitsuba} to produce physically-accurate images from the scene models.
@@
 By incorporating statistical models of the variation of object surface reflectance and daylight illumination, the pipeline allows us to produce large labeled sets of images that capture much of the task-relevant statistical structure of natural scenes.
-% Reference RTB and VWCC where we say "We developed a rendering package".
-% \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}.
-%\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}
 
@@
 This provides a complete scene model which can be rendered from any specified viewpoint.
-% REORDER FIGURE 5 COLUMNS d -> e -> a -> b -> c.
+
+% Figure5
+\begin{figure}
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_d.png}
+        \caption{Target position}
+        \label{fig:targetPositionVariation}
+    \end{subfigure}
+    ~
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_e.png}
+        \caption{Target Size/Orientation}
+        \label{fig:targetSizeOrientation}
+    \end{subfigure}
+~
+\centering
+	\begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_a.png}
+        \caption{Target spectra}
+        \label{fig:targetVariation}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_b.png}
+        \caption{Background spectra}
+        \label{fig:backGroundVariation}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.18 \textwidth}
+    \centering
+        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_c.png}
+        \caption{Illumination spectra}
+        \label{fig:illuminationVariation}
+    \end{subfigure}
+    \caption{{\bf Transformations of the scene.} The possible transformations of the properties of a scene can broadly be classified into two groups: Geometrical (a-b) and Spectral (c-e).
+VWCC provides control over such transformation as illustrated by the columns.
+(a) The three panels in the column have the target object at three different positions.
+The camera points to the center of the pixel.
+(b) The target object in the three panels are at different orientations.
+(c) The target object surface reflectance varies across the three panels of the column.
+(d) The surface reflectance of the background objects varies across the three panels.
+In each panel, the reflectances were assigned randomly.
+(e) The power spectrum of the light sources were assigned randomly in the three panels.
+\label{fig:VWCCTransformations}}
+\end{figure}
 
@@
 This corresponded to $1 \times 1$ degrees of visual angle for the model of the early visual system, also described below.
-
-% Figure5
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_a.png}
-        \caption{Target spectra}
-        \label{fig:targetVariation}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_b.png}
-        \caption{Background spectra}
-        \label{fig:backGroundVariation}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_c.png}
-        \caption{Illumination spectra}
-        \label{fig:illuminationVariation}
-    \end{subfigure}
-    ~
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_d.png}
-        \caption{Target position}
-        \label{fig:targetPositionVariation}
-    \end{subfigure}
-    ~
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_e.png}
-        \caption{Target Size/Orientation}
-        \label{fig:targetSizeOrientation}
-    \end{subfigure}
-    ~
-    \caption{{\bf Transformations of the scene.} The possible transformations of the properties of a scene can broadly be classified into two groups: Spectral (a-c) and Geometrical (d-e).
-VWCC provides control over such transformation as illustrated by the columns.
-(a) The target object surface reflectance varies across the three panels of the column.
-(b) The surface reflectance of the background objects varies across the three panels.
-In each panel, the reflectances were assigned randomly.
-(c) The power spectrum of the light sources were assigned randomly in the three panels.
-(d) The three panels in the column have the target object at three different positions.
-The camera points to the center of the pixel.
-\label{fig:VWCCTransformations}}
-\end{figure}
 

### 2018-03-30 Draft2/draft2.tex
added one reference for the LRV
Today’s edits, charging along!

@@
 We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of an object's surface reflectance function.
-The LRV is a measure of the overall amount of light reflected by surface.
+The LRV is a measure of the overall amount of light reflected by surface (\citeauthor{astm1121477}).
 More precisely, the LRV is the luminance of the light that would
@@
 becomes progressively more difficult (Fig.~\ref{fig:studiedCases}).
+Each dataset consisted of 1000 scenes and corresponding images.
 
@@
 
+% 1000 each case
 %Condition 0: Baseline
@@
 %Condition 3: Target Color and Illuminant
+%Condition 3a: Target Color and Relative Illuminant
 %Condition 4: Everything
@@
 
+% REMOVE PANELS A AND D AND FIX CAPTION AND REFERENCES TO THIS FIGURE.
 \subsubsection{Illumination Spectra}
@@
 Our statistical model approximates these normalized shapes using their first 6 principle components, and models the variation in these components with
-a 6-dimensional Gaussian whose mean and covariance matrix match the dataset's sample mean and covariance of the weights on these components.
+a 6-dimensional Gaussian whose mean and covariance matrix match the dataset's sample mean and covariance of the weights on these components \cite{BrainardFreeman}.
 To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
-Figure~ref{ENTER REF} .....
-and reconstruct t
-obtained from the daylight dataset.
- In our procedure, we first approximate the spectra in the dataset using principle component analysis (PCA).
-We then decompose the spectra in terms of the PCA basis vectors corresponding to the 6 largest PCA eigenvalues.
-Next, we sample from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a  Finallly, we use the sampled weights to reconstruct sampled spectra.
-This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman \cite{BrainardFreeman}.
-Details of the procedure we used are provided below.
-
-Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset.
+Figure~ref{ENTER REF FIG} illustrates the relative spectra of draws obtained using this procedure.
+Details of the statistical model for illumination are provided in the appendix.
+
+Because our multivariate Gaussian model is based on the rescaled spectra, it does not embody the large variation in overall intensity of natural daylights.
+To obtain illuminant spectra with intensity variation similar to the Granada dataset, we scaled each randomly generated relative spectrum.
+We obtained each scale factor by randomly sampling (with replacement) a spectrum from the Granda dataset and taking its mean.
+
+% MOVE THIS TO AN APPENDEX.
+%Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset.
 Since the measured spectra vary over several orders of magnitude in overall intensity, we rescale each spectrum by dividing it by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$.
@@
 We subsampled the spectra to the 400-700 nm interval, 10 nm spacing representation used for rendering, and performed our calculations at this sampling.
-
-The rescaled spectra $I_i^s(\lambda)$ were then mean centered for PCA by subtracting out the mean 
-rescaled spectrum, $\bar{I}^{s}(\lambda)$. That mean was obtained
-by taking the sample mean over all rescaled spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
-The resulting mean centered dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$
-was decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
-where the $\hat{{\bf e}}_j^{PCA}$ are the PCA basis vectors obtained using the
-singular value decomposition (SVD) applied to the $I_i^{MC}(\lambda)$ and
-the $w_{ij}$ are the weights obtained by projecting each of $I_i^{MC}(\lambda)$ onto the  $\hat{{\bf e}}_j^{PCA}$ $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$.
-We used the basis vectors corresponding to
-the largest six SVD eigenvalues, so that $\{j \in [1,6]\}$.
-For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance (Fig.~\ref{fig:granadaEV}).
-These steps
-can be summarized as follows:
-\begin{align}
-I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) \approx \sum_{j = 1}^6 w_{ij}\hat{{\bf e}}_j^{PCA}.
-\end{align}
-
-To generate random illuminant spectra $\tilde{I}_i(\lambda)$, we generate weights $\tilde{w}_{ij}$ drawn from random 
-the multivariate 
-Gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
-From these weights, the corresponding spectrum $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right)$ is generated.
-This spectrum can sometimes have values that are less than zero.  In such cases, the weights are discarded and a new draw obtained, until
-the condition $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, is satisfied for all $\lambda$.
-The random illuminant spectrum is then given as
-\begin{align}
-\tilde{I}(\lambda) = \left( \tilde{I}_{MC}(\lambda) + \bar{I}_{s}(\lambda)\right).
-\end{align}
-Fig.~\ref{fig:randomIlluminant} shows a set of 100 spectra sampled in this manner, and may be compared with Fig.~\ref{fig:rescaledGranada}.
+%
+%The rescaled spectra $I_i^s(\lambda)$ were then mean centered for PCA by subtracting out the mean 
+%rescaled spectrum, $\bar{I}^{s}(\lambda)$. That mean was obtained
+%by taking the sample mean over all rescaled spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
+%The resulting mean centered dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$
+%was decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
+%where the $\hat{{\bf e}}_j^{PCA}$ are the PCA basis vectors obtained using the
+%singular value decomposition (SVD) applied to the $I_i^{MC}(\lambda)$ and
+%the $w_{ij}$ are the weights obtained by projecting each of $I_i^{MC}(\lambda)$ onto the  $\hat{{\bf e}}_j^{PCA}$ $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$.
+%We used the basis vectors corresponding to
+%the largest six SVD eigenvalues, so that $\{j \in [1,6]\}$.
+%For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance (Fig.~\ref{fig:granadaEV}).
+%These steps
+%can be summarized as follows:
+%\begin{align}
+%I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) \approx \sum_{j = 1}^6 w_{ij}\hat{{\bf e}}_j^{PCA}.
+%\end{align}
+%
+%To generate random illuminant spectra $\tilde{I}_i(\lambda)$, we generate weights $\tilde{w}_{ij}$ drawn from random 
+%the multivariate 
+%Gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
+%and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
+%From these weights, the corresponding spectrum $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right)$ is generated.
+%This spectrum can sometimes have values that are less than zero.  In such cases, the weights are discarded and a new draw obtained, until
+%the condition $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, is satisfied for all $\lambda$.
+%The random illuminant spectrum is then given as
+%\begin{align}
+%\tilde{I}(\lambda) = \left( \tilde{I}_{MC}(\lambda) + \bar{I}_{s}(\lambda)\right).
+%\end{align}
+%Fig.~\ref{fig:randomIlluminant} shows a set of 100 spectra sampled in this manner, and may be compared with Fig.~\ref{fig:rescaledGranada}.
 Fig.~\ref{fig:xyDiagram} shows the CIE xy chromaticities of these samples and compares these with the chromaticities in the Granada dataset.
 Finally, Fig.~\ref{fig:sRGBIlluminant} provides an sRGB rendering of each spectrum in Fig.~\ref{fig:rescaledGranada}, to provide a visual sense of the chromatic variation in the sampled spectra.
-
-Because our multivariate Gaussian model is based on the rescaled spectra, it does not embody the large variation in overall intensity of natural daylights.
-To get a scaling similar to the original Granada spectrum set, we multiply the randomly sampled spectrum with a random number generated uniformly from the interval [0, $\bar{I}_{\rm max}$], where $\bar{I}_{\rm max}$ is the maximum of the 2600 mean values obtained from the Granada spectra.
-Finally, to model the fact that illumination spectra can vary in overall intensity, we draw a random number distributed logarithmically in the range [$I_{min}$ and $I_{max}$] and scale the generated spectrum by this number.
-In most of our calculations, we set $I_{min} = 1$ and $I_{max} = 300$.
-% WE NEED TO RETHINK THIS SCALING.  CERTAINLY SHOULD JUST BE ONE STEP.  ONE APPROACH WOULD BE TO DRAW UNIFORMLY FROM THE DISTRIBUTION OF SCALE FACTORS OBTAINED FROM THE 2600 
-% GRANADA MEASUREMENTS.
 
@@
 We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
-measurements to create a reflectance database containing 632 reflectances.
-The Munsell database contains 462 samples of surface reflectance spectra each measured at 5nm sampling intervals between 380nm and 780nm.
-The Vrhel dataset has 170 samples measured at 2nm sampling between 390nm and 730 nm.
-We subsampled these spectra in the 400-700nm interval, 10 nm apart, for rendering images used in this work.
-
-Let us denote the reflectance dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
-and $M$ is the total number of spectra in the dataset. 
-We calculated the mean reflectance spectrum,
-$\bar{R}(\lambda)$, by taking the sample mean over all spectra in the dataset, i.e.,
-$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. Then, we mean centered 
-the reflectance dataset by subtracting the mean spectrum, $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
-We decomposed this mean centered dataset as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$, where
-the ${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
-and the $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the basis vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
-$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. 
-We used the basis vectors corresponding to the largest six SVD eigenvalues. 
-For the combined Munsell and Vrhel datasets, these six eigenvalues account for 
-more than $90\%$ of the variance. 
-To generate random reflectance spectra, we generate samples of weights ($\tilde{w}_{ij}$) drawn from the multivariate Gaussian 
-distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
+measurements to create a database containing 632 reflectance spectra.
+The Munsell database contains 462 spectra each measured at 5nm sampling intervals between 380nm and 780nm.
+The Vrhel dataset contains 170 spectra measured at 2nm sampling between 390nm and 730 nm.
+We resampled these spectra to 31 evenly-spaced wavelengths between $400$nm and $700$nm.
+Figure~ref{ENTER REF FIG} illustrates the spectra of draws obtained using this procedure.
+Details of the statistical model for surface reflectance spectra are provided in the appendix.
+
+% THIS GOES TO THE SAME APPENDIX AS THE ILLUMINANT MATH.
+%Let us denote the reflectance dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
+%and $M$ is the total number of spectra in the dataset. 
+%We calculated the mean reflectance spectrum,
+%$\bar{R}(\lambda)$, by taking the sample mean over all spectra in the dataset, i.e.,
+%$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. Then, we mean centered 
+%the reflectance dataset by subtracting the mean spectrum, $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
+%We decomposed this mean centered dataset as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$, where
+%the ${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
+%and the $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the basis vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
+%$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. 
+%We used the basis vectors corresponding to the largest six SVD eigenvalues. 
+%For the combined Munsell and Vrhel datasets, these six eigenvalues account for 
+%more than $90\%$ of the variance. 
+%To generate random reflectance spectra, we generate samples of weights ($\tilde{w}_{ij}$) drawn from the multivariate Gaussian 
+%distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
+%and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
 If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, we use them to give the random reflectance spectrum as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.
@@
 
+% MAKE TARGET SWATCHES ITS OWN FIGURE.
 For generating the target object reflectance at a particular luminance $(Y_{\rm T})$, the values in a generated spectrum were 
-rescaled such that the surface luminance (as defined above) had the desired value.
-The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE photopic luminosity (or luminous efficiency) function. 
-$\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
-perception of bruminance.
+scaled such that the LRV had the desired value (see appendix).
+Figure \ref{TARGET FIG} shows color swatches of target reflectance spectra rendered under CIE illuminant D65, for evenly spaced LRV values.
+
+%The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE photopic luminosity (or luminous efficiency) function. 
+%$\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
+%perception of bruminance.
 The target reflectance is then given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.

### 2018-03-30 Draft3/appendix.tex
new draft, new figures

--- 2017-12-28 Draft1/draft1.tex
@@
-%% Copyright (C) 2009 by Tobias Elze
-%% Journal of Vision LaTeX template version 1.0
-%% This document may be used freely for your own submissions.
+\documentclass[10pt,english]{article}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{lmodern}
+\renewcommand{\sfdefault}{lmss}
+\renewcommand{\ttdefault}{lmtt}
+\usepackage[T1]{fontenc}
+\usepackage[latin9]{inputenc}
+\usepackage{amstext}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{babel}
+\usepackage{mathtools}
+%\usepackage{subfigure}
+\usepackage{subcaption}
 
-\documentclass{jov}
-\usepackage{graphicx} % needed for figures
-\usepackage{subcaption}
-\usepackage{hyperref}
-\usepackage{amsmath}
-\usepackage{bbm}
-\usepackage{amssymb}
-\usepackage{comment}
-
-\DeclareMathOperator*{\argmin}{arg\,min}
+   \usepackage{multirow}
+   \topmargin 0.0cm
+   \oddsidemargin 0.5cm
+   \evensidemargin 0.5cm
+   \textwidth 16cm 
+   \textheight 21cm
 
 \begin{document}
+\title{Appendix: Luminance constancy under fixed geometry}
 
-\title{Lightness constancy under fixed geometry}
-\abstract{The light that reflects off an object surface and is captured by our eyes varies significantly with its context.
-But, the human visual system has the ability to stably perceive the object's color invariant of the context variations.
-The mechanism of this behaviorally significant invariance detection ability remains largely unknown.
-To understand the computational principles that lead to such invariant perception, we study the perception of object lightness under spectral variations in 3D scenes.
-Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the perceived lightness of an object.
-We have developed a software that generates naturalistic multispectral images of 3D scenes with precise control over the geometrical and spectral properties of the constituents that make a scene.
-We label these images with the lightness of a specific object in the scene.
-Next, we simulate the response of the retinal cones to these multispectral images using an accurate model of the early visual system.
-Using supervised learning methods on these labeled cone response, we identify the computations that lead to accurate lightness estimation.
-We show that if only either target, or background, or illumination spectra are allowed to vary, the standard lightness can be estimated through simple transformations of the cone responses.
-When all the spectra vary simultaneously, while it is not easy to recover the lightness through simple transformations, a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and S cones can recover the lightness within about 15\% RMSE.}
-
-\author{Singh}{Vijay}
- {Computational Neuroscience Initiative}
- {and Department of Physics, University of Pennsylvania, PA, USA}
- {}{vsin@sas.upenn.edu}
-
-\keywords{color constancy, accuracy maximization analysis, supervised learning,
-lightness}
-
+\author{Vijay Singh, Benjamin Heasly, Nicolas Cottaris, David Brainard, Johannes Burge}
 \maketitle
 
-\section{Introduction}
-The perceived color of an object has important behavioral implications, since color helps us to identify objects and their properties \cite{Mollon89, Jacobs81}.
-Perceived object color is not sensed directly, rather it is computed by the brain starting with the retinal image of light reflected from the object to the eye.
-The challenge of object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose,
-and the position of the observer (Fig.~\ref{fig:introSchematic}).
-Thus, to produce a stable perceptual representation of an object's surface reflectance in the face of variation in these extrinsic factors, the brain must account for their influence on the reflected light.
-The ability of a visual system to extract such a stable representation is called color constancy.
-Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}.
-In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eyes to produce percepts well-correlated with object surface reflectance.
+\date
+\begin{abstract}
+\end{abstract}
 
-There is a considerable literature on computational color constancy.
-Seminal work considered a reduced scene model in which flat matte surfaces were illuminated by a single spatially diffuse illuminant and explored algorithms that could either recover a descriptor correlated with object surface reflectance (e.g.
-\citeNP{LandRetinex}) or explicit estimates of object surface reflectance and/or illuminant spectral power distribution (e.g., \citeNP{LandRetinex,Buchsbaum80,MaloneyWandell86}).
-An important insight of this line of research was that, to account for variation in illumination, it was necessary to consider the light reflected from the entire scene.
-That is, although good constancy cannot be achieved in the face of illuminant variation if one considers only the light reflected from a single target object, when one considers the entire image it is possible to use the joint variation in light reflected from many objects to obtain (either implicitly or explicitly) an estimate of the illuminant common across the objects, and in turn to use this estimate to produce a stabilized representation of object color.
-At the same time, this processing introduces an additional dependence.
-Although the reflectance of the objects surrounding an object of interest has little direct effect on the light reflected from the object of interest, variation in the reflectance of the surrounding objects can have a large effect on the output of constancy algorithms that process the entire image \cite{BrainardWandellRetinex}.
-Thus, a key aspect evaluating computational constancy algorithms is not only to ask about target object color stability with respect to variation in illumination, but also to ask about target object color stability with respect to the surface reflectance of other objects in the scene.
-Subsequent computational constancy work sought to generalize both the image formation model to include richer geometric descriptions and to incorporate probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
-None-the-less, it is not known how best to estimate stable object descriptors from images of the natural scenes we view in daily life.
-
-% Figure 1: Introduction
-\begin{figure}
-\centering
-\begin{subfigure}{0.4 \textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
-        \caption{}
-        \label{fig:introSchematic}
-    \end{subfigure}
-    \begin{subfigure}{0.45 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.jpeg}
-        \caption{}
-        \label{fig:introExampleFigure}
-    \end{subfigure}
-    \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light reflected from an object to our eyes depends both on the surface reflectance of the object, $R(\lambda,\vec{x})$, and the illumination spectrum of the light source, $E(\lambda,\vec{x})$.
-Additionally, it depends on geometric factors, such as the object's shape and pose, as well as the position of the observer.
-The human visual system is able to account for, at least partially, variations in the reflected light due to such extrinsic factors, and produce a percept of object color that is relatively stable with respect to such variations.
-Such invariant color perception is called color constancy.
-(b) {\bf Lightness Constancy Under Spectral Variations:} In this paper we consider the special case of lightness constancy.
-Fig.~\ref{fig:introExampleFigure} shows images of an object (the sphere in the center of each image) at three levels of object luminance.
-Within each row, the surface reflectance of the spheres has the same luminance, when illuminated by a standard reference illuminant, CIE D65.
-The three rows differ in this value, as can be seen by the fact that the lightness of the spheres generally decreases as we move down the columns.
-Within each row, the relative surface reflectance of the spheres varies, as can be seen by the variation in color appearance across the each row.
-Within each column, this relative surface reflectance is held fixed.
-For illustration, we have kept the light source and the background objects fixed across the panels.
-See Fig.~\ref{fig:studiedCases} for images with such variations.
-In this paper, we seek to identify computations that accurately estimate object luminance across variations in relative surface reflectance, variations in illumination, and variation in the reflectance of other objects in the scene.}
- \end{figure}
-
-The computational work reviewed above is based on formulating an explicit model of the image formation process and the statistical properties of natural images, and leveraging these formulations to obtain an appropriate ``inverse optics" algorithm.
-An alternative approach, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors.
-Along these lines, Barron \cite{barron2015convolutional} recently developed a color balancing algorithm based on training a neural network to detect a uniform illuminant in an image by matching image templates in the chromaticity space.
-The use of supervised learning to understand human perceptual capabilities has enjoyed success in domains outside of color vision.
-Geisler and colleagues, for example, have developed a technique they refer to as accuracy maximization analysis (AMA, \citeNP{geisler2009optimal}), which learns linear filters whose output carries information that is optimized for particular perceptual tasks.
-This technique has provided computations that efficiently estimate speed \cite{burge2015optimal}, focus \cite{burge2011optimal} and disparity \cite{burge2014optimal} from image patches taken from natural scenes, and that in addition provide excellent models of human's ability to make corresponding estimates from the same stimuli.
-In this paper, we apply AMA, as well as comparison supervised learning algorithms to a special case of the color constancy problem (lightness constancy) and evaluate how well it performs for naturalistic image input.
-
-A difficulty in using machine learning approaches for color constancy is that these approaches require large training sets with images of scenes containing objects with known surface reflectances illuminated with known illuminations.
-Such data sets are not readily available.
-Although there are several databases of calibrated color natural images, these do not generally provide the corresponding information about surface and illuminant ground truth \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection},  ( ADD McGill Database).
-Generating databases with both the images and the ground truth scene information is not trivial.
-One approach has been to acquire images where objects of known reflectance have been inserted into the scene, and to use the image of these reference objects to provide an estimate of the illumination impinging at various scene locations \cite{NascimentoFoster2016}.
-This is somewhat painstaking, however, and in any case provides information about the illumination only at a small number of selected locations, so that generalizing across the image requires strong assumptions.
-Some progress is being made on characterizing how illumination varies over space in natural scenes \cite{mury2007spatial}, which in the longer run may guide how information from reference objects can be used to provide reasonable estimates.
-Another approach is to acquire images of posed scenes, where the surface reflectances of objects are measured individually for many of the objects in the scene \cite{funt1988color,ciurea2003large} (ADD UCSB hyperspectral).
-These data sets have been useful for evaluating computational color constancy algorithms, but the use of posed scenes does not scale well for use with supervised learning methods which needs large training sets.
-
-% Figure 2: Cases Studied
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.33 \textwidth}
-		\includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_a.jpeg}
-		\caption{Case 1}
- 		\label{fig:targetVarying}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_b.jpeg}
-        \caption{Case 2}
-        \label{fig:targetIlluminantVarying}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.33 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_c.jpeg}
-        \caption{Case 3}
-        \label{fig:allSpectraVarying}
-    \end{subfigure}    
-    \caption{{\bf Three types of spectral variations studied in this work:} sRGB rendition of multispectral images similar to ones studied in our work.
-The numbers on the left indicate the standard lightness level of the target object.
-5 images are shown at each lightness level.
-We studied three types of spectral variations.
-(a) Case 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed, (b) Case 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Case 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
-This panel is reproduced from \ref{fig:introExampleFigure}.
-As in \ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
-Moreover, across the three panels of this figure, spheres in corresponding locations have the same surface reflectance.
-In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
-The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
-\label{fig:studiedCases}
-\end{figure}
-
-Because of the difficulty in obtaining large labelled data sets of natural images for use in developing and evaluating computational color constancy algorithms, in this paper we adopt the approach of using high-quality computer graphics to render images of what we refer to as {\em virtual natural scenes}.
-Here, in addition to employing computer graphics to render the light reaching the eye from specified scenes, we also model the initial steps of the human visual system, so that our supervised learning methods are applied not to image pixels but rather to modeled responses of the foveal cone photoreceptor mosaic.
-We describe this approach in detail below, but the key advantage is that we can produce large numbers of naturalistic images and the corresponding cone mosaic responses, where all of the underlying scene properties are well-specified.
-This allows us to explore and evaluate computational color constancy with rich stimuli, while retaining the ability to precisely control and manipulate the intrinsic properties of the objects and illuminants that comprise the scene.
-This general approach has been adopted by other labs for the study of computational estimation of optical flow \cite{baker2011database} and is becoming increasingly popular (OTHER REFS: Cornell graphics person, Gallant, Yamins, Autonomous vehicle work), as well as for the generation of stimuli for the study of human perception \cite{boyaci2003effect}(REFS: Many -- go to Boynton lecture slides for some).
-Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the \nameref{Discussion}.
-
-In this initial work, we do not tackle the full problem of color constancy.
-Rather, as a point of departure, we consider the computational problem of estimating a single attribute of object surface reflectance, which we refer to as surface luminance.
-We compute object luminance from an object's surface reflectance function as follows.
-We compute the light that would be reflected to the eye from a flat matte object with that surface reflectance, when the object is diffusely illuminated by the standard CIE daylight spectrum D65 \cite{CIE86}.
-We then compute the luminance of this reflected light, using the CIE 1931 photopic luminosity function \cite{CIE86}, and divide this by the luminance of a perfectly reflecting diffuser (surface reflectance of one at all wavelengths) when that is computed in the same way.
-This procedure allows us to assign to any surface reflectance a single surface luminance value.
-Because the perceived lightness of an object is approximately (but by no means exactly, see \citeNP{wyszecki1986color}) correlated with surface luminance across a range of viewing conditions, we refer to the computational problem we study as that of {\em lightness constancy}.
-This is a generalization of the way this term is often used, where it refers more specifically to the stability of perceived lightness across images of scenes where all objects and illuminants are achromatic \cite{gilchrist2006seeing}.
-Here, we aim to estimate surface luminance, but do so for images where both the luminance and the chromaticity of the surfaces and illuminants varies (see  Fig.~\ref{fig:introExampleFigure}).
-A particularly important feature of our treatment is that we consider scene variations where not only the spectrum of the illumination varies, but also the surface reflectance of objects in the scene other than the object whose surface luminance is being estimated.
-
-Even within the special case of lightness constancy, there are many scene manipulations that could be considered.
-The set of manipulations we focus on here are illustrated by the three panels of Fig.~\ref{fig:studiedCases}.
-These cases are: 1.
-variation in target object spectrum with fixed light source and background objects spectra (Fig.~\ref{fig:targetVarying}), 2.
-variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.~\ref{fig:targetIlluminantVarying}), and 3.
-variations in all three types of spectra (target object, light source, and background objects) (Fig.~\ref{fig:allSpectraVarying}).
-Across real scenes, there will also be variations in the shape of the target object, its pose, eye position, etc.
-(see \nameref{Methods}).
-In this paper, we focus on the problem of lightness constancy within scene ensembles where these geometric factors are held fixed.
-
-We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, lightness can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (case 1), object lightness can be recovered directly from the light reflected off the target object.
-For case 2, where both the target object reflectance and light source spectra vary, object lightness can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 3), the standard lightness can not be recovered simply from the cone response or the contrast.
-Here, we have used two supervised learning methods with Bayesian estimators to estimate standard lightness of the target object.
-Using these methods, we can recover the lightness of the target object with $\sim 15\%$ relative root mean square error.
-Our analysis shows that the optimal receptive fields for estimating the lightness of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, lightness estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
-Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
-We discuss the implications of such receptive fields on lightness constancy.
-
-The rest of this paper is organized as follows.
-In the \nameref{Methods} section, we describe in detail the process to generate naturalistic labeled images (\nameref{method:VirtualWorld}) using our software pipeline {\rm Virtual world color constancy}, the process to simulate the response of retinal cone photoreceptors to these images using a standard model of the early visual system (\nameref{method:Isetbio}) and the supervised learning methods used in our analysis (\nameref{method:SupervisedLearning}).
-In the \nameref{Results} section, we show the estimates and performance of the supervised methods for the three cases mentioned above.
-We conclude the paper with the implication of our results in the \nameref{Discussion} section.
-
-\section*{Methods} \label{Methods}
-\subsection{Overview}
-There are four key parts to our methods.
-The first is how we generate a labelled set of training data for our supervised learning algorithms.
-The second is how we model the transformations applied by the early visual system to generate modeled responses of the cone photoreceptor mosaic.
-The third is the details of the supervised learning methods we apply to the labelled training data.
-And the fourth is how we evaluate the performance of the algorithms.
-We describe each of these in the sections below.
-
-\subsection{Labelled image database} \label{method:VirtualWorld}
-
-% Figure 3
-\begin{figure}[t]
-\centering
-\begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_a.png}
-        \caption{Library }
-        \label{fig:baseSceneLibrary}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_b.png}
-        \caption{Mill}
-        \label{fig:baseSceneMill}
-    \end{subfigure}    
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_c.png}
-        \caption{Table-Chairs}
-        \label{fig:baseSceneTableChairs}
-    \end{subfigure}
-
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_d.png}
-        \caption{Indoor-plant}
-        \label{fig:baseSceneIndoorPlant}
-    \end{subfigure}    
-    ~
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_e.png}
-        \caption{Warehouse}
-        \label{fig:baseSceneWarehouse}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_f.png}
-        \caption{Checkerboard}
-        \label{fig:baseSceneCheckerBoard}
-    \end{subfigure}
-    \caption{{\bf Example of base scenes form the VWCC library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.
-The reflectance spectra of the distinct surfaces in each scene has been assigned randomly (see below) using the VWCC software.
-The light source spectra were also assigned randomly to the default and inserted light source.}\label{fig:baseScenes}
-\end{figure}
-
-\subsubsection{Virtual naturalistic scenes}
-The light that reflects off an object and reaches our eyes depends on many factors.
-These factors include: the surface reflectance of the object, the surface reflectance, texture, material and geometry of the objects in its surround, the spectrum of the sources of light illuminating the object, and the position of the observer.
-In natural scenes, these spectral and geometrical factors vary considerably.
-To study the effect of these factors on color perception, we need a system that can generate natural scenes with precise control over all such factors.
-We need a system that can produce natural scenes at a fixed perceived color of a target object, while having a representative, but precisely quantified, sampling of the variations in the scene.
-Under natural conditions it is difficult to control and quantify every such parameter in a scene.
-Thus generating such a dataset, with a representative sampling of natural variations, is considerably time and labor intensive.
-
-To overcome this  challenge, we have developed an image rendering software pipeline that allows us to specify a virtual, but naturalistic, statistical model of visual scenes with parametric control over factors in natural scenes.
-The software uses a physically-based image rendering system that accurately accounts for the interactions of light with matter in 3D scenes.
-It then renders a multispectral 2D image of each modeled visual scene.
-Wherever possible, we have incorporated statistical models of the variation of specific scene parameters based on observed data in natural scenes.
-In addition, our software simulates the responses of retinal cones to the rendered multispectral images using a realistic model of the early human visual system.
-Below we provide the details of the software and the choices made to generate ensembles of scenes with corresponding images.
-Our software, which is written in MATLAB, is freely available through a public respository: \href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}.
-It builds on several other open source projects, including \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}, \href{http://isetbio.org}{Isetbio} and \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba}.
-Below we refer to the software pipeline as VWCC (for Virtual World Color Constancy).
-
-% Figure 4
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.14 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_a.png}
-        \caption{Big-ball}
-        \label{fig:libraryWithBigBall}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-\begin{subfigure}[b]{0.14 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_b.png}
-        \caption{Small-ball}
-        \label{fig:libraryWithSmallBall}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.14 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_c.png}
-        \caption{Barrel}
-        \label{fig:libraryWithBarrel}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.14 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_d.png}
-        \caption{Xylophone}
-        \label{fig:libraryWithXylophone}
-    \end{subfigure}
-    ~
-	\begin{subfigure}[b]{0.14 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_e.png}
-        \caption{Ring toy}
-        \label{fig:libraryWithRingToy}
-    \end{subfigure}
-        ~
-    	\begin{subfigure}[b]{0.14 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_f.png}
-        \caption{Bottle}
-        \label{fig:libraryWithChampagneBottle}
-    \end{subfigure}
-\caption{{\bf Library base scene with inserted objects.} The VWCC software was used to insert different objects into the library base scene, with each panel showing a different object.
-The objects were inserted at a location in the image and then the camera was pointed at the object, so that the object's image is at the center of the rendered image.
-In the figure panels, the full rendered image is cropped so that the inserted object is more visually salient.
-We use this capability of our software pipeline to insert target objects into scenes.}\label{fig:libraryWithTarget}
-\end{figure}
-
-The process of generating an individual virtual scene begins with the selection of a \textit{base scene} (Fig.~\ref{fig:baseScenes}).
-The base scene is a 3D model that defines a rendering space.
-It typically includes the specification of a number of 3D objects and light sources, and is annotated with meta-data that may be used to guide the placement of additional objects and light sources, as well as the specification of camera position.
-VWCC includes a library of base scenes obtained from materials made available on the Internet under various Creative Commons licenses.
-We have found that there is sufficient variation in how nominally-standard graphics interchange file formats are used in practice that each base scene obtained from the Internet (which we refer to as \textit{wild scenes}) requires a certain amount of hand editing before it renders properly.
-We refer to this process, along with adding meta-data about the scene, as \textit{taming} a wild scene.
-Tame base scenes may also be created de novo using a 3D modeling software (e.g., \href{https://www.blender.org/}{Blender}).
-The overall spatial scale of the base scene may be adjusted under programmatic control or chosen randomly, adding to the available statistical richness.
-If one chooses to draw entries from the base scene library at random for each virtual scene, the base scene library then provides a simple statistical model of the gross layout of natural scenes.
-As time progresses, we plan to tame more wild scenes so as to increase the number of entries in the base scene library.
-Currently the library contains 6 base scenes: Library (Fig.~\ref{fig:baseSceneLibrary}), Mill (Fig.~\ref{fig:baseSceneMill}), Table-Chairs (Fig.~\ref{fig:baseSceneTableChairs}), Indoor plant (Fig.~\ref{fig:baseSceneIndoorPlant}), Checkerboard (Fig.~\ref{fig:baseSceneWarehouse}) and Warehouse (Fig.~\ref{fig:baseSceneCheckerBoard}).
-
-VWCC provides an option for inserting 3D objects and lights sources into the base scene.
-Fig.~\ref{fig:libraryWithTarget} shows examples of objects inserted into the library base scene.
-The object shapes may be selected from a VWCC library that, similar to the VWCC library of base scenes, has been tamed from object descriptions made available on the Internet.
-The light sources may be chosen as point lights, area lights, or as shapes selected from the object library.
-The position (Fig.~\ref{fig:targetPositionVariation}), size and orientation (Fig.~\ref{fig:targetSizeOrientation})of the inserted objects and lights may be specified programatically or chosen randomly under constraints provided by the base scene meta-data.
-Thus, along with distributions that characterize parameters such as the number, size, shape and orientation of the inserted objects and light sources, we have a simple statistical model of the object and light source geometry of natural scenes.
-
-% Figure5
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_a.png}
-        \caption{Target spectra}
-        \label{fig:targetVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_b.png}
-        \caption{Background spectra}
-        \label{fig:backGroundVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_c.png}
-        \caption{Illumination spectra}
-        \label{fig:illuminationVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_d.png}
-        \caption{Target position}
-        \label{fig:targetPositionVariation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_e.png}
-        \caption{Target Size/Orientation}
-        \label{fig:targetSizeOrientation}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \caption{{\bf Transformations of the scene.} The possible transformations of the properties of a scene can broadly be classified into two groups: Spectral (a-c) and Geometrical (d-e).
-VWCC provides control over such transformation as illustrated by the columns.
-(a) The target object surface reflectance varies across the three panels of the column.
-(b) The surface reflectance of the background objects varies across the three panels.
-In each panel, the reflectances were assigned randomly.
-(c) The power spectrum of the light sources were assigned randomly in the three panels.
-(d) The three panels in the column have the target object at three different positions.
-The camera points to the center of the pixel.
-}\label{fig:VWCCTransformations}
-\end{figure}
-
-Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene.
-We also assign an illuminant spectral power distribution to each light source in the scene.
-Objects in the VWCC library may contain more than one distinct surface, each of which may be assigned a different surface reflectance.
-As with object position, these may be specified programatically.
-In the present work, we use simple choices for texture (all surfaces spatially uniform) and material property (all surfaces matte) and focus on variation in surface spectral reflectance.
-
-In the present work, we insert one target object and one additional light source into a fixed base scene, and vary reflectance and illuminant spectra.
-We then insert a camera for rendering at a user specified position and point this camera at the target object.
-We ensure that a 9 pixel by 9 pixel region at the center of the image corresponds to light reflected from the target object, which amounts to verifying that the target object at its inserted position was not occluded by other objects in the line of sight from camera.
-For each rendered scene, we specify the surface reflectance of the target object, which allows us to control both its surface luminance as well as its relative surface reflectance.
-The specified surface luminance provides the requisite label for the scene and resultant cone mosaic responses.
-
-We render scenes using the \href{https://www.mitsuba-renderer.org}{Mitsuba} \cite{jakob2015mitsuba} rendering package, driven by our \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3} rendering pipeline.
-
-For the images used for the primary results reported in this paper, we used the ``{\it Library}'' base scene from the VWCC  and the ``{\it Big Ball}'' object as the target object.
-We also inserted a spherical light source with the same ``{\it Big Ball}'' shape.
-The position, and size of the inserted object, light source and the camera were held fixed for all the images analyzed in this work, i.e., the scene geometry did not vary.
-Next, we assigned illumination and surface reflectance spectra to the lights and objects in the scene.
-The spectral manipulations for the various cases studied in this work have been described in the main text (Fig.~\ref{fig:studiedCases}).
-2D multispectral images were rendered at 31 wavelengths from $400$nm to $700$nm spaced $10$nm apart at an image size $320\times 240$ pixel.
-A $51 \times 51$ pixel patch of the multispectral image was cropped around the target object and cone responses were calculated to these cropped images.
-
-\subsubsection{Illumination Spectra}
-% Figure 6
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_a.pdf}
-        \caption{Granada natural daylight dataset}
-        \label{fig:granadaSpectra}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_b.pdf}
-        \caption{Rescaled Granada dataset}
-        \label{fig:rescaledGranada}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
-        \caption{Randomly generated samples}
-        \label{fig:randomIlluminant}
-    \end{subfigure}
-
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
-        \caption{Normalized PCA eigenvalues}
-        \label{fig:granadaEV}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_e.pdf}
-        \caption{xy chromaticity diagram}
-        \label{fig:xyDiagram}
-    \end{subfigure}
-      	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_f.pdf}
-        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomIlluminant}}
-        \label{fig:sRGBIlluminant}
-    \end{subfigure}
-    \caption{{\bf Generating random illumination spectra:} The illumination spectra are generated by random sampling based on the Granada daylight measurements, assuming a multivariate Gaussian distribution of weights in a 6-dimensional PCA representation.
-The mean and covariance matrix of the Gaussian are chosen by projecting the dataset along the first six PCA directions and taking the mean and covariance matrix of the resulting basis vector weights.
-(a) The 2600 spectra from the Granada natural daylight dataset, plotted on a log intensity scale in arbitrary units.
-(b) Rescaled version of the Granada dataset.
-Each spectrum is rescaled so that it has a mean value (over wavelength) of one illumination.
-(c) Randomly samples generated using the rescaled spectra from Fig.~\ref{fig:rescaledGranada}.
-(d)Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
-The eigenvalues have been normalized by the sum over all eigenvalues.
-The dotted line at 0.9 on the y-axis is for reference.
-We used the first six eigenvectors in our analysis.
-(e) CIE xy chromaticity plot of the rescaled dataset (Fig.~\ref{fig:rescaledGranada}) and randomly generated samples from Fig.~\ref{fig:randomIlluminant}.
-(f) sRGB renditions of the random illuminant samples shown in \ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
-\end{figure}
-
-We generate illumination spectra  through random statistical sampling of a dataset of naturally occurring illuminants, the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{peyvandi2016colorimetric}.
-These spectra are shown on a log intensity scale in Fig.~\ref{fig:granadaSpectra}, which illustrates that the overall intensity of natural daylights varies over several orders of magnitude, and in normalized format in Fig.~\ref{fig:rescaledGranada}, which illustrates that the relative spectra also vary considerably.
-In our procedure, we first approximate the spectra in the dataset using principle component analysis (PCA).
-We then decompose the spectra in terms of the PCA basis vectors corresponding to the 6 largest PCA eigenvalues.
-Next, we sample from this low 6 dimensional PCA weight space assuming that the distribution of the basis vector weights is a multivariate gaussian whose mean and covariance matrix match the sample mean and covariance obtained from the daylight dataset.
-Finallly, we use the sampled weights to reconstruct sampled spectra.
-This general method for modeling the statistical structure of daylight was introduced by Brainard \& Freeman \cite{BrainardFreeman}.
-Details of the procedure we used are provided below.
-
+\section{Illumination Spectra}
 Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset.
@@
 We used the basis vectors corresponding to
-the largest six SVD eigenvalues, so that $\{j \in [16]\}$.
-For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance (Fig.~\ref{fig:granadaEV}).
+the largest six SVD eigenvalues, so that $\{j \in [1,6]\}$.
+For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance.
 These steps
@@
 \end{align}
-Fig.~\ref{fig:randomIlluminant} shows a set of 100 spectra sampled in this manner, and may be compared with Fig.~\ref{fig:rescaledGranada}.
-Fig.~\ref{fig:xyDiagram} shows the CIE xy chromaticities of these samples and compares these with the chromaticities in the Granada dataset.
-Finally, Fig.~\ref{fig:sRGBIlluminant} provides an sRGB rendering of each spectrum in Fig.~\ref{fig:rescaledGranada}, to provide a visual sense of the chromatic variation in the sampled spectra.
 
-Because our multivariate Gaussian model is based on the rescaled spectra, it does not embody the large variation in overall intensity of natural daylights.
-To get a scaling similar to the original Granada spectrum set, we multiply the randomly sampled spectrum with a random number generated uniformly from the interval [0, $\bar{I}_{\rm max}$], where $\bar{I}_{\rm max}$ is the maximum of the 2600 mean values obtained from the Granada spectra.
-Finally, to model the fact that illumination spectra can vary in overall intensity, we draw a random number distributed logarithmically in the range [$I_{min}$ and $I_{max}$] and scale the generated spectrum by this number.
-In most of our calculations, we set $I_{min} = 1$ and $I_{max} = 300$.
-% WE NEED TO RETHINK THIS SCALING.  CERTAINLY SHOULD JUST BE ONE STEP.  ONE APPROACH WOULD BE TO DRAW UNIFORMLY FROM THE DISTRIBUTION OF SCALE FACTORS OBTAINED FROM THE 2600 
-% GRANADA MEASUREMENTS.
-
-\subsubsection{Surface Reflectance Spectra}
-
-% Figure 7
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_a.pdf}
-        \caption{Natural surface reflectance spectra}
-        \label{fig:naturalSurface}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
-        \caption{Randomly generated spectra}
-        \label{fig:randomSurface}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
-        \caption{sRGB rendition of samples from \ref{fig:randomSurface}}
-        \label{fig:sRGBSurface}
-    \end{subfigure}
-
-    \centering
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_d.pdf}
-        \caption{Natural surface reflectance spectra}
-        \label{fig:naturalSurfaceTarget}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_e.pdf}
-        \caption{Randomly generated target samples}
-        \label{fig:randomSurfaceTarget}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_f.pdf}
-        \caption{sRGB rendition of target reflectance}
-        \label{fig:sRGBSurfaceTarget}
-    \end{subfigure}
-    \caption{{\bf Generating surface reflectance spectra:} Surface reflectance spectra are generated by random sampling based on measured surface reflectance spectra, using principles similar to those used to generate random illuminant spectra.
-(a) The 632 surface reflectance spectra from the Munsell and Vrhel datasets.
-(b) Randomly generated samples of reflectance spectra.
-(c) sRGB renderings (under CIE D65) of the random samples generated in \ref{fig:randomSurface}.
-(d)Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues for the mean centered surface reflectance dataset.
-The eigenvalues have been normalized by the sum over all eigenvalues.
-The dotted line at 0.9 on the y-axis is for reference.
-We used the first six eigenvectors in our analysis.
-(e) CIE xy chromaticity plot of the surface reflectance dataset (Fig.~\ref{fig:naturalSurface}), randomly generated samples of surface reflectance (Fig.~\ref{fig:randomSurface}) and randomly generated samples of target surface.
-(f) The sRGB renditions of the randomly generated sample of target object surface reflectance.
-The figure shows 10 randomly generated samples at 10 levels of the target object surface luminance.
-The range of luminance levels [0.2, 0.6] (indicated on the Y axis), captures the luminance of more than 90\% of the natural surface reflectances.}
-\label{fig:surfaceReflectanceGeneration}
-\end{figure}
-
-We generated random reflectance spectra using the same principles we applied to generate random illuminant spectra.
-We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
-measurements to create a reflectance database containing 632 reflectances.
-
- SAY SOMETHING ABOUT SPECTRAL SAMPLING
-
+\section{Surface Reflectance Spectra}
 Let us denote the reflectance dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
@@
 For generating the target object reflectance at a particular luminance $(Y_{\rm T})$, the values in a generated spectrum were 
-rescaled such that the surface luminance (as defined above) had the desired value.
+scaled such that the LRV had the desired value.
 The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE photopic luminosity (or luminous efficiency) function. 
 $\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
-perception of brightness.
-The target reflectance is then given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
-
-% Figure 8: Methods
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.25 \textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.png}
-        \caption{sRGB rendering of a 3D scene}
-        \label{fig:3DScene}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.19 \textwidth}   
-    \hspace{0.1 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.png}
-        \caption{Cropped Image}
-        \label{fig:croppedImage}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}[b]{0.19 \textwidth}
-    \hspace{0.1 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.png}
-        \caption{Optical Image}
-        \label{fig:croppedImageWithMosaic}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_d.png}
-        \caption{LMS cone contrast}
-        \label{fig:coneContrast}
-    \end{subfigure}
-    \label{fig:sceneWithCroppedImage}
-    \caption{{\bf Generating labeled dataset for computational analysis:}  For the supervised approach employed in this work, the labeled database is generated as follows: (a) A 3D virtual scene, containing a target object of known surface luminance is created.
-The target object is placed in the camera field of view.
-After assigning spectra to the light sources and other other objects in the scene, a multispectral image of the scene is rendered using the Mitsuba software package.
-(b) The central portion of the rendered image, which contains the target object, is cropped from the image.
-(c) The response of retinal cones to the cropped image is simulated using the isetbio software package to model early vision.
-The software models optical blurring and foveal spatial sampling by the trichromatic cone mosaic.
-Fig.~\ref{fig:croppedImageWithMosaic} shows the retinal image incident on the cone mosaic and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
-(d) The cone responses are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
-Finally, the demosaiced images are contrast normalized separately for each cone type.}
-\end{figure}
-
-\subsection{Model of Early Visual System} \label{method:Isetbio}
-
-The sampling and rendering steps described above allow us to generate images from scenes that contain an image of a target object of known surface luminance at the center pixel, and where the illuminant spectra and spectra of the other surfaces in the scene are drawn randomly from models of naturally occurring spectra.
-One such image is shown in Fig.~\ref{fig:3DScene}, where the green sphere in the middle is the target object and the light sources are not within the camera field of view.
-We model the encoding of such images by the early visual system, to generate {\em neural images} that provide an abstracted representation of the information available to the brain for producing perceptual representations of the external world.
-For each image, it is this information together with the known surface luminance of the corresponding target object that we will provide to our supervised learning algorithms.
-Our training datasets correspond to ...
-% SAY WHAT WE DID ONCE WE FINISH EVERYTHING OFF.
-
-In this work, we are interested in how well lightness constancy may be achieved using reasonable information that is local to the image region containing the target patch. 
-% MAYBE SAY A LITTLE MORE ABOUT WHY - THIS IS A PRINCIPLED STANCE TAKEN IN MOST OF JOHANNES WORK.  OR MAYBE DEFER THAT TO THE DISCUSSION.
-To this end, we crop a 51x51 pixel portion of the full rendered multispectral image that contains the target object and use this for further analysis (\ref{fig:croppedImage}).
-Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 lightness levels for the three cases considered in this paper.
-
-Next, the cropped multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
-The key steps we model are optical blurring, including axial chromatic aberration, in the formation of the retinal image, spatial sampling by an interleaved mosaic of L, M and S cones, and the Poisson nature of photopigment isomerization.
-% NEED TO WRITE IN THE KEY PARAMETERS USED.
-PROBABLY MARIMONT AND WANDELL OPTICS, STOCKMAN-SHARPE LMS CONE SPECTRAL SENSITIVITIES, THE L, M, S CONE RATIO IN THE MOSAIC, RECTANGULAR AND REGULAR CONE PACKING, SOME IMPLIED SPATIAL SCALE, AND SOME OVERALL SCALING THAT DRIVES THE MEAN LUMINANCE OF THE RETINAL IMAGES AND THUS THE AMOUNT OF POISSON NOISE.
-
-% WE GOT TO HERE ON DECEMBER 21.
-To generate the retinal response one needs to specify the retinal cone mosaic and the size of the retinal image.
-The retinal cone mosaic is specified in terms of the total number of cones and the proportion of the long(L), medium(M) and the short(S) cones in the mosaic.
-With these parameters, the software generates the specified number of LMS cones with random positions on a square grid.
-The size of the retinal image is specified in terms of the field of view and object distance from the eye.
-
-We simulate visual system response using \href{http://isetbio.org}{Isetbio} software toolbox.
-Isetbio simulates a model of the visual system accounting for cornea, pupil size, lens and physiological optics.
-We use the multispectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
-The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
-The retinal cone mosaic is modeled as a square grid with 51x51 cones in the l:m:s ratio 0.6:0.3:0.1.
-The response of the cones are measured as the number of isomerizations in the cone segment ({\it over what time ??}).
-The cone response functions are normalized by the total area under the response curves to model the amplification of the S cone response downstream and thus have comparable number if isomerizations in L, M and S cones.
-Further, to get the response of each cone class at each position on the retinal mosaic, we interpolate the response of each cone class.
-Thus we get a $51 \times 51$ cone response image for each cone class.
-
-The three $51 \times 51$ cone response matrix corresponding to L, M and S cones are then reshaped into a $7803 \times 1$ vector.
-To model the contrast adaptation in the visual system, we perform a contrast normalization of the vector by subtracting and dividing by the mean.
-We further  rescale the vector to have norm 1.
-The cone-response vectors corresponding to the N images for each case are concatenated into a column-wise contrast normalized matrix $C_{7803\times N}$.
-The corresponding labels are represented by the row vector $Y_{1\times N}$.
-
-\subsection{Supervised Learning methods} \label{method:SupervisedLearning}
-We used three supervised learning methods in out analysis. Linear regression, SVD regression and accuracy maximization analysis.
-
-\subsubsection*{Linear Regression} For linear regression, we solve the equation $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
-Here, $C_{3\times N}$ is a matrix containing the contrast normalized L, M and S cone responses of the central patch of each image.
-The columns corresponds to the N images in the dataset.
-The rows correspond to the contrast normalized L, M and S cones responses averaged over a 3$\times$3 pixel central region of the image containing the target object.
-The (unknown) regression parameters $A$ are obtained using Matlab linear regression function.
-
-\subsubsection*{SVD regression}
-SVD regression is a generalization of principal component analysis for labeled data \cite{ranganNotes}.
-Briefly, given an image dataset matrix $C_{M \times N}$ and labels $Y_{1\times N}$, the method finds unit vectors such that the projection of the data along this vector maximizes the separation of the images with different labels, while clustering the images with similar labels together.
-Mathematically, the method searches for a direction $\hat{u}$ that minimize the cost function:
+perception of bruminance. The target reflectance is then given by: 
 \begin{align}
-S = \sum\limits_{j,j'}\left(\hat{u}^\intercal C(:,j) - \hat{u}^\intercal C(:,j')\right)^2 \left(Y(j)-Y(j') \right)^2,
-\end{align} 
-where $C(:,j)$ represents the $j$'th column/image of the data matrix $C$. The direction of minimum cost is given by the eigenvector corresponding to the largest eigenvalue of the following matrix:
-\begin{align}
-N C Y_D^2 C^\intercal - 2(Y*\mathbbm{1})C Y_D C^\intercal + (Y*Y^\intercal) (CC^\intercal)-C Y_{D}^2\mathbbm{1}\mathbbm{1}^\intercal C^\intercal +2 C Y_{D} \mathbbm{1}\mathbbm{1}^\intercal Y_{D} C^\intercal - C \mathbbm{1}\mathbbm{1}^\intercal Y_{D}^2 C^\intercal.
-\end{align}
-Here, $Y_{D}$ is a diagonal matrix with the elements of the labels vector $Y$ along the diagonal, and $\mathbbm{1}$ is a $N\times 1$ vector with each element equal to one.
-
-\subsubsection*{Accuracy maximization analysis}
-AMA \cite{geisler2009optimal,burge2017accuracy} is a Bayesian ideal observer model for task specific dimensionality reduction.
-Given a labeled training set, a noisy response model, and a cost function, AMA returns a set of linear receptive fields that are optimal for performing a task.
-The task is implicitly defined in terms of the labels.
-The optimal filters that are returned by AMA are filters whose noisy response to the stimuli, as given by the specified response model, minimizes the cost function over the training set.
-
-Let us assume that there are $N_{\nu}$ possible values of the labels (luminance levels $\{Y_k: k\in[1,N_{\nu}] \}$).
-The image labels take one of these $N_{\nu}$ possible values.
-The $l$'th stimuli corresponding to the $k$'th category of the labels is represented as $s_{kl}$.
-Let us assume that there is a set of linear filters {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
-Let's say we have a decoder $g$ that takes ${\textbf{\textit R}}_{kl}$ as the input and returns an estimate of the label ($Y_k$) corresponding to the stimuli $s_{kl}$ as $\hat{Y}_{kl}$.
-Given this estimate, one can define a cost function $\mathcal{C}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to specific response ${\textbf{\textit R}}_{kl}$ and a mean cost $\bar{\mathcal{C}}_{kl}(Y_{kl},\hat{Y}_{kl})$ corresponding to the average response $r_{kl} = \langle{\textbf{\textit R}}_{kl}\rangle$.
-
-Accuracy maximization analysis (AMA) finds the set of optimal filters ${\textbf{\textit f}}^{\rm opt}$ that minimize the average cost function over the entire dataset $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$.
-$N_{\nu}$ is the total number of values that labels can take and $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
-Thus,
-\begin{align}
-{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{kl} \bar{\mathcal{C}}_{kl}.
-\label{eq:fopt}
+\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right).
 \end{align}
 
-AMA employs the Bayes optimal decoder ($g$) to estimate the optimal estimate.
-The Bayesian decoder computes the posterior probability of the label $p(Y|{\textbf {\textit R}})$ and reads out the optimal estimate $\hat{Y}^{\rm opt}$ from the posterior as the value that minimizes the cost.
-By Bayes' theorem, the posterior probability can be written as:
-\begin{align}
-p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{p({\textbf {\textit R} }_{kl}|Y_k)p(Y_k)}{\sum\limits_{i=1}^{N_{\nu}}{p({\textbf {\textit R} }_{kl}|Y_i)p(Y_i)}}.
-\label{eq:posterior}
-\end{align}
-As the conditional probability of the filter response is:
-\begin{align}
-p({\textbf {\textit R} }_{kl}|Y_k) = \sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|Y_k),
-\label{eq:condProb}
-\end{align}
-using Eq.~\ref{eq:condProb} in Eq.~\ref{eq:posterior} we get:
-\begin{align}
-p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})p({\textbf {\textit s} }_{km}|Y_k)\right]p(Y_k)}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})p({\textbf {\textit s} }_{kj}|Y_i)\right]p(Y_i)}}
-\label{eq:finalPosterior}
-\end{align}
-Since, $p({\textbf {\textit s} }_{km}|Y_k) = \frac{1}{N_k}$, and $p(Y_k)=\frac{N_k}{N}$, where $N = \sum\limits_{k=1}^{N_{\nu}}N_{k}$ is total number of samples in the training set, Eq.\ref{eq:finalPosterior} simplifies to
-\begin{align}
-p(Y_k|{\textbf {\textit R} }_{kl}) = \frac{\left[\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km}) \frac{1}{N_k}\right]\frac{N_k}{N}}{\sum\limits_{i=1}^{N_{\nu}}{\left[\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij}) \frac{1}{N_i}\right]\frac{N_i}{N}}} = \frac{\sum\limits_{m=1}^{N_k}p({\textbf {\textit R} }_{kl}|{\textbf {\textit s} }_{km})}{\sum\limits_{i=1}^{N_{\nu}}{\sum\limits_{j=1}^{N_j}p({\textbf {\textit R} }_{il}|{\textbf {\textit s} }_{ij})}}.
-\label{eq:simplifiedPosterior}
-\end{align}
-Now if the cost associated with the latent variable $Y_k$ and the estimate $\hat{Y}_k$ is $\gamma (Y_k,\hat{Y}_k)$, we have  
-\begin{align}
-\mathcal{C}_{kl} = \sum\limits_{u=1}^{N_{\nu}}\gamma(X_u,\hat{Y}_u)p(X_u|{\textbf{\textit R}}_{kl}),
-\end{align}
-and the mean cost associated with the training set is $\bar{\mathcal{C}} = \frac{1}{N} \sum\limits_{k,l}\bar{\mathcal{C}}_{kl} = \frac{1}{N} \sum\limits_{k,l}\langle \mathcal{C}_{kl}\rangle_{{\textbf{\textit R}}_{kl}}$.
-The optimal AMA filters are obtained by minimizing $\bar{\mathcal{C}}$ over the filter set ${\textbf {\textit f} }$ (Eq.\ref{eq:fopt}).
-The filters are obtained using gradient descent.
-
-In this work, we assume the noisy response model to be a multivariate gaussian.
-For a stimuli $s_{kl}$, the noisy response vector ${\textbf{\textit R}}_{kl} = \left[{\textbf{\textit R}}_{kl,1},{\textbf{\textit R}}_{kl,2},\dots,{\textbf{\textit R}}_{kl,q}\right]$ to the set of filters ${\textbf{\textit f}} = \left[{\textbf{\textit f}}_{kl,1},{\textbf{\textit f}}_{2},\dots,{\textbf{\textit f}}_{q}\right]$ is given by $\mathcal{N}({\textbf{\textit r}}_{kl}, \Sigma)$, with mean response vector ${\textbf{\textit r}}_{kl} = \left[{\textbf{\textit r}}_{kl,1},{\textbf{\textit r}}_{kl,2},\dots,{\textbf{\textit r}}_{kl,q}\right] = \left[{\textbf{\textit f}}_{1}\cdot s_{kl},{\textbf{\textit f}}_{2}\cdot s_{kl}\dots,{\textbf{\textit f}}_{q}\cdot s_{kl}\right]$ and the covariance matrix as the diagonal matrix $\Sigma$ with variances $\left(\sigma_1^2, \sigma_2^2,\dots, \sigma_q^2 \right)$.
-We assume $\sigma_i^2 = \alpha |r_i| + \sigma_0^2$, $|{\textbf{\textit f}}_{kl,i}|=1$ and $s_{kl}$ to be zero mean contrast normalized, i.e., $\langle{s_{kl}}\rangle = 0$ \& ${|s_{kl}|=1}$.
-
-\section{Results} \label{Results}
-\subsection{Optimal receptive fields for luminance estimation have a center surround structure}
-We used two supervised learning methods to learn the optimal receptive fields (RFs) for lightness estimation for the three types of variations in the spectral properties of the scene as discuss earlier.
-Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults}) shows the optimal RFs, the linear response of these RFs to the training dataset, and the estimates of the luminance of the target object in the test dataset for the three cases.
-We show the first two RFs obtained using the SVD and AMA methods (Fig.~(\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(a-b)).
-The RFs are ranked in ascending order of the value of the cost function.
-Thus the first RF corresponds to the direction along which the projection of the data gives the minimum cost.
-The L, M and S components give the weights for the linear sum of the cone responses for the three cone types.
-The salient features are: the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.
-
-For case 1, since the illuminant and the background are fixed, all the information is in the central target object reflectance.
-Thus, the RFs weights are mostly concentrated around the center.
-For case 2, while the target and the illuminant spectra varies, the background object spectra is fixed.
-Hence, the lightness can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background.
-Thus, while the RFs show a trend of weights concentrated at the center similar to case 1, there is large negative contribution from the surround.
-The spatial features of the RFs are due the stereotypical geometry of the images (see \nameref{Methods}).
-For case 3, has a similar center surround structure with more prominent features of the background, as we also vary the spectra of the background objects.
-Again, the spatial features are a result of the stereotypical geometry of the images.
-
-%% Figure 10
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.27 \textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.pdf}
-        \caption{SVD First 2 RFs}
-        \label{fig:case9SVD}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.pdf}
-        \caption{AMA First 2 RFs}
-        \label{fig:case9AMA}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_c.pdf}
-        \caption{AMA RF Response}
-        \label{fig:case9FiltersResponse}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_d.pdf}
-        \caption{Lightness Estimates}
-        \label{fig:case9Results}
-    \end{subfigure}    
-    \caption{{\bf Receptive fields and lightness estimates.
-Case 1:} (a) First two receptive fields produced by the SVD method.
-Along the row we show the filters corresponding to the L cones, M cones and S cones (left to right).
-(b) First two receptive fields produced by the AMA method.
-(c) The response of the stimuli to the first two AMA filters.
-The responses are grouped with the label of the stimuli.
-As is clear, the response distributions at each luminance level separate out well in this case, resulting in good estimates of the target object luminance.
-(d) The estimates of the target object standard luminance.
-The naive method produces the mean value of the target luminance used in the analysis.
-The shaded region corresponds to 1 sigma standard deviation.}
-\label{fig:case9AllResults}
-\end{figure}
-
-%% Figure 11
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
-\caption{{\bf Performance with number of RFs used for estimation:} Most of the information is captured by the first two filters. We have used the first 8 RFs for estimating the lightness.}
-\label{fig:RMSEvsNFilters}
-\end{figure}
-
-% Figure 12
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.27 \textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
-        \caption{SVD First 2 RFs}
-        \label{fig:case10SVD}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
-        \caption{AMA First 2 RFs}
-        \label{fig:case10AMA}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
-        \caption{AMA RF Response}
-        \label{fig:case10FiltersResponse}
-    \end{subfigure}    
-        \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_d.pdf}
-        \caption{Luminance Estimates}
-        \label{fig:case10Results}
-    \end{subfigure}
-    \caption{{\bf Receptive fields and lightness estimates. Case 2:} Same as Fig. \ref{fig:case9AllResults}.}
-    \label{fig:case10AllResults}
-\end{figure}
-
-% Figure 13
-\begin{figure}
-\centering
-\begin{subfigure}[b]{0.27 \textwidth}
-		\centering
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
-        \caption{SVD First 2 RFs}
-        \label{fig:case12SVD}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.27 \textwidth}   
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
-        \caption{AMA First 2 RFs}
-        \label{fig:case12AMA}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.20 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_c.pdf}
-        \caption{AMA RF Response}
-        \label{fig:case12FiltersResponse}
-    \end{subfigure}    
-        \begin{subfigure}[b]{0.2 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_d.pdf}
-        \caption{Luminance Estimates}
-        \label{fig:case12Results}
-    \end{subfigure}
-    \caption{{\bf Receptive fields and lightness estimates. Case 3:}  Same as Fig. \ref{fig:case9AllResults}.}
-    \label{fig:case12AllResults}
-\end{figure}
-
-\subsection{Lightness can be well estimated using a bayesian decoder with gaussian priors.}
-We estimate the lightness of the target object in the images using the receptive field response of the corresponding contrast normalized cone responses.
-Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(c) shows the response of the first two RFs to the stimuli set for the three cases.
-For the training images at each lightness level, we approximate the receptive response of the contrast normalized cone responses by a multivariate gaussian.
-The target object lightness of an image in the test set is estimated using Bayesian decoder.
-We measure the estimation performance in terms of the relative root mean square ($E_{\rm rel}$) defined as:
-\begin{align}
-E_{\rm rel} = \sqrt{\left\langle\left(\frac{\hat{Y}-Y}{Y}\right)^2\right\rangle},
-\end{align}
-where $\hat{Y}$ corresponds to the estimated lightness and $Y$ to the assigned lightness. We use the first 8 RFs for lightness estimation ( see Fig.~\ref{fig:RMSEvsNFilters}).
-
-Fig.~ (\ref{fig:case9AllResults}-\ref{fig:case12AllResults})(d) shows the lightness estimates and the RMSE for the three methods (Linear regression on center pixel, AMA and SVD).
-Additionally we show the estimate of a naive model that reports the mean value of the lightness labels used in the dataset.
-The diagonal x=y line is shown for reference.
-The shaded regions show $E_{\rm rel}$ for each method.
-
-(Fig.~\ref{fig:summaryBarGraph}) compares the $E_{\rm rel}$ for the different methods for the three cases.
-Both AMA and SVD methods, which use the information from the entire image estimate the lightness better compared to linear regression which only uses the information from the center pixel.
-This shows the importance of context information for lightness estimation.
-
-\subsection{The RFs of complex case generalize on simpler cases}
-% Figure 8
-\begin{figure}
-\centering
-\begin{subfigure}{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
-	\caption{Performance of methods}
-	\label{fig:summaryBarGraph}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-      %(or a blank line to force the subfigure onto a new line)
-    \begin{subfigure}{0.3 \textwidth}   
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
-	\caption{SVD RF Performance}
-	\label{fig:SVDBAR}
-    \end{subfigure}
-    ~ %add desired spacing between images, e. g. ~, \quad, \qquad, \hfill etc. 
-    %(or a blank line to force the subfigure onto a new line)
-        \begin{subfigure}{0.3 \textwidth}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
-	\caption{AMA RF Performance}
-	\label{fig:AMABAR}
-    \end{subfigure}
-\caption{{\bf Model and Filter Performance:} (a) Comparison of various methods on lightness estimations for the three cases studied here.
-For simple spectral variations, like where only the target reflectance varies (case 1) or only the target and illumination spectrum varies (Case 2), the lightness can be estimated well.
-This is so, because the lightness information can be estimated simply from the light reflected of the target( case 1) or from the contrast between the target and the {\it fixed} background (case 2).
-For more complex case, where the lightness information is confounded due to variations in target, background and illuminant (case 3), the estimation has higher variability.
-(b) Performance of the SVD receptive fields obtained from one case on the stimuli of others.
-The RFs obtained from any one of the three cases perform well on the stimuli from case 1.
-The RF of the most complicated case (case 3), has good performance on the stimuli of lower complexity.
-(c) Same as Fig.\ref{fig:SVDBAR} for AMA RFs.}
- \label{fig:barGraphs}
-\end{figure}
-Fig.~\ref{fig:SVDBAR} and Fig~\ref{fig:AMABAR} show the performance of the receptive fields learnt using the stimuli of one case on the stimuli of other cases.
-The RFs of case 3, (the most complex case) perform well on stimuli of case 1 and case 2.
-Similarly, the RFs of case 2 performs well on the stimuli of case 1.
-Thus, the receptive fields leant on the complex case generalize for lightness estimation of stimuli for simpler cases.
-
-\section{Discussion} \label{Discussion}
-In this paper, we studied luminance constancy using naturalistic images.
-We generated a dataset of multispectral images labeled by the reflectance of a target object in each image.
-These images were generated by a software pipeline developed for this work, that we call Virtual world color constancy (VWCC).
-This software creates 3D scene descriptors based on programatic information provided by the user.
-Such information include the shape of the 3D rendering space, the shape, size, position and material properties of the objects and light sources in the scene, the location of the observer, etc.
-We assign these geometrical and spectral properties (the power spectrum of the light sources and the surface reflectance of the objects) using random sampling from available databases of naturally occurring objects, light sources and surface reflectances.
-Thus, we generate a large database of labeled hyper-spectral images, with naturalistic scene properties, but with the information about the surface reflectance and illumination at every pixel in the image.
-Such databases are near to be impossible to generate using other means as it is very hard to measure the surface reflectance of every object and the illumination at every point, even for well controlled scenes in a lab.
-
-In this paper, as a first step towards understanding color constancy using supervised methods on labeled dataset, we studied a simpler analogue: luminance constancy.
-We generated images labeled with the luminance of a target object in the scene.
-We performed three types of spectral manipulations in the scene while generating the images (Fig.~\ref{fig:studiedCases}).
-1.
-Allow variations in the spectral shape of the target object surface reflectance spectrum, while keeping the background object surface reflectance and the illumination spectra of the light sources fixed.
-2.
-Allow variations in the shape of the target object surface reflectance and the illumination spectra of the light sources, while keeping the surface reflectance spectra of the background objects fixed.
-3.
-Allow variations in all three types of spectra.
-We generated hundreds of images at multiple luminance level of the target object for each of these three cases.
-Then using a model of the early visual system, we generated the response of the cones in the retina for each image in our database.
-These model retinal responses, along with the luminance label of the images, are then used as the input to supervised learning algorithms.
-Using our supervised methods, we leant that the target object luminance can be obtained from simple manipulation of the cone response for case where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, the light source illumination spectra.
-In these cases, the luminance can be obtained by comparing the response of the cones corresponding to the target and the background objects.
-When all these three types of spectral variations are allowed simultaneously, one needs additional information to obtain the luminance of the target object.
-
 \bibliography{references}
-\bibliographystyle{jovcite}
 

### 2018-03-30 Draft3/draft3.tex
new draft, new figures

--- 2018-03-30 Draft2/draft2.tex
@@
 	\centering
+	\caption{}
         \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
-        \caption{}
         \label{fig:introSchematic}
@@
     \begin{subfigure}{0.55 \textwidth}   
+        \caption{}    
         \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.png}
-        \caption{}
         \label{fig:introExampleFigure}
@@
 
-% Figure 2: Cases Studied
+% Figure 2: Conditions Studied
 \begin{figure}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
+		\caption{Condition 2}
 		\includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_a.png}
-		\caption{Case 2}
  		\label{fig:backgroundVarying}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
+        \caption{Condition 3}	
         \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_b.png}
-        \caption{Case 3}
         \label{fig:targetIlluminantVarying}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
+	\caption{Condition 4}	
         \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_c.png}        
-        \caption{Case 4}
         \label{fig:allSpectraVarying}
@@
 We studied four types of spectral variations.
-Case 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed, (Fig.~\ref{fig:introExampleFigure}).
-(a) Case 2: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable, (b) Case 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Case 4: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
+Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed, (Fig.~\ref{fig:introExampleFigure}).
+(a) Condition 2: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable, (b) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 4: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
 As in Fig.~\ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
@@
 The set of manipulations we focus on here are illustrated by Fig.~\ref{fig:introExampleFigure} and the three panels of Fig.~\ref{fig:studiedCases}.
-These cases are: 1.
+These conditions are: 1.
 variation in target object spectrum with fixed light source and background objects spectra (Fig.~\ref{fig:introExampleFigure}), 2.
@@
 %
-%We show that for cases that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (case 1) or just the target and background objects reflectance spectra (case 2), LRV can be recovered directly from the light reflected off the target object.
-For case 3, where both the target object reflectance and light source spectra vary, LRV can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (case 4), the standard luminance can not be recovered simply from the cone response or the contrast.
+%We show that for conditions that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
+For variations only in target object reflectance spectra (Condition 1) or just the target and background objects reflectance spectra (Condition 2), LRV can be recovered directly from the light reflected off the target object.
+For Condition 3, where both the target object reflectance and light source spectra vary, LRV can be recovered from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (Condition 4), the standard luminance can not be recovered simply from the cone response or the contrast.
 We have used AMA with a Bayesian estimator to estimate standard luminance of the target object.
@@
 Additionally, luminance estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
-Comparing the performance of the RFs learnt using  one case on the cone response of other cases shows that the receptive field of the complex cases perform well on images of simpler cases.
+Comparing the performance of the RFs learnt using  one condition on the cone response of other conditions shows that the receptive field of the complex conditions perform well on images of simpler conditions.
 We discuss the implications of such receptive fields on luminance constancy.
@@
 \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Library }
         \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_a.png}
-        \caption{Library }
         \label{fig:baseSceneLibrary}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Mill}    
         \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_b.png}
-        \caption{Mill}
         \label{fig:baseSceneMill}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Table-Chairs}    
         \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_c.png}
-        \caption{Table-Chairs}
         \label{fig:baseSceneTableChairs}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Indoor-plant}    
         \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_d.png}
-        \caption{Indoor-plant}
         \label{fig:baseSceneIndoorPlant}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Warehouse}    
         \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_e.png}
-        \caption{Warehouse}
         \label{fig:baseSceneWarehouse}
@@
     \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Checkerboard}    
         \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_f.png}
-        \caption{Checkerboard}
         \label{fig:baseSceneCheckerBoard}
@@
 \begin{subfigure}[b]{0.14 \textwidth}
+        \caption{Big-ball}
         \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_a.png}
-        \caption{Big-ball}
         \label{fig:libraryWithBigBall}
@@
 \begin{subfigure}[b]{0.14 \textwidth}
+        \caption{Small-ball}
         \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_b.png}
-        \caption{Small-ball}
         \label{fig:libraryWithSmallBall}
@@
     \begin{subfigure}[b]{0.14 \textwidth}
+        \caption{Barrel}
         \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_c.png}
-        \caption{Barrel}
         \label{fig:libraryWithBarrel}
@@
     \begin{subfigure}[b]{0.14 \textwidth}
+        \caption{Xylophone}
         \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_d.png}
-        \caption{Xylophone}
         \label{fig:libraryWithXylophone}
@@
 	\begin{subfigure}[b]{0.14 \textwidth}
+        \caption{Ring toy}
         \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_e.png}
-        \caption{Ring toy}
         \label{fig:libraryWithRingToy}
@@
     	\begin{subfigure}[b]{0.14 \textwidth}
+        \caption{Bottle}
         \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_f.png}
-        \caption{Bottle}
         \label{fig:libraryWithChampagneBottle}
@@
     \centering
+        \caption{Target position}
         \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_d.png}
-        \caption{Target position}
         \label{fig:targetPositionVariation}
@@
     \centering
+        \caption{Target Size/Orientation}
         \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_e.png}
-        \caption{Target Size/Orientation}
         \label{fig:targetSizeOrientation}
@@
     \centering
+        \caption{Target spectra}
         \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_a.png}
-        \caption{Target spectra}
         \label{fig:targetVariation}
@@
     \centering
+        \caption{Background spectra}
         \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_b.png}
-        \caption{Background spectra}
         \label{fig:backGroundVariation}
@@
     \centering
+        \caption{Illumination spectra}
         \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_c.png}
-        \caption{Illumination spectra}
         \label{fig:illuminationVariation}
@@
 
-% 1000 each case
+% 1000 each Condition
 %Condition 0: Baseline
@@
 \centering
-	\begin{subfigure}[b]{0.3 \textwidth}
+    \begin{subfigure}[b]{0.24 \textwidth}
     \centering
+	\caption{}
         \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_a.pdf}
-        \caption{Granada natural daylight dataset}
-        \label{fig:granadaSpectra}
+        \label{fig:illuminantSpectra}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+	\begin{subfigure}[b]{0.24 \textwidth}
     \centering
+        \caption{}
         \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_b.pdf}
-        \caption{Rescaled Granada dataset}
-        \label{fig:rescaledGranada}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
-        \caption{Randomly generated samples}
-        \label{fig:randomIlluminant}
-    \end{subfigure}
-
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
-        \caption{Normalized PCA eigenvalues}
-        \label{fig:granadaEV}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_e.pdf}
-        \caption{xy chromaticity diagram}
         \label{fig:xyDiagram}
     \end{subfigure}
-      	\begin{subfigure}[b]{0.3 \textwidth}
+      	\begin{subfigure}[b]{0.24 \textwidth}
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_f.pdf}
-        \caption{sRGB rendition of samples from Fig.~\ref{fig:randomIlluminant}}
+        \caption{}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
         \label{fig:sRGBIlluminant}
         \end{subfigure}
-    \caption{{\bf Generating random illumination spectra:} The illumination spectra are generated by random sampling based on the Granada daylight measurements, assuming a multivariate Gaussian distribution of weights in a 6-dimensional PCA representation.
-The mean and covariance matrix of the Gaussian are chosen by projecting the dataset along the first six PCA directions and taking the mean and covariance matrix of the resulting basis vector weights.
-(a) The 2600 spectra from the Granada natural daylight dataset, plotted on a log intensity scale in arbitrary units.
-(b) Rescaled version of the Granada dataset.
-Each spectrum is rescaled so that it has a mean value (over wavelength) of one illumination.
-(c) Randomly samples generated using the rescaled spectra from Fig.~\ref{fig:rescaledGranada}.
-(d)Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues.
-The eigenvalues have been normalized by the sum over all eigenvalues.
-The dotted line at 0.9 on the y-axis is for reference.
-We used the eigenvectors corresponding to the first six eigenvalues in our analysis.
-(e) CIE xy chromaticity plot of the rescaled dataset (in Fig.~\ref{fig:rescaledGranada}) and randomly generated samples from Fig.~\ref{fig:randomIlluminant}.
-(f) sRGB renditions of the random illuminant samples shown in Fig.~\ref{fig:randomIlluminant}.}\label{fig:illluminationGeneration}
+      	\begin{subfigure}[b]{0.24 \textwidth}
+    \centering
+        \caption{}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
+        \label{fig:sRGBIlluminant}
+    \end{subfigure}
+    \caption{{\bf Illumination spectra:} (a) Mean scaled Granada dataset (red, 2600 samples) and 100 randomly generated samples using the rescaled spectra (black).
+(b) CIE xy chromaticity diagram of the mean scaled dataset and the random samples.
+(c) sRGB renditions of 100 random samples before scaling.
+(d) sRGB renditions of the samples after scaling.}
 \end{figure}
@@
 To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
-Figure~ref{ENTER REF FIG} illustrates the relative spectra of draws obtained using this procedure.
+Figure~ref{fig:illuminantSpectra} illustrates the relative spectra of draws obtained using this procedure.
 Details of the statistical model for illumination are provided in the appendix.
@@
 
-% MOVE THIS TO AN APPENDEX.
-%Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset.
-Since the measured spectra vary over several orders of magnitude in overall intensity, we rescale each spectrum by dividing it by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$.
-For simplicity of notation, we denote wavelength $\lambda$ as a continuous variable; in the actual calculations wavelength is discretely sampled and integrals are approximated by sums.
-The Granada dataset was measured at 5 nm sampling intervals between 300 and 1100 nm.
-We subsampled the spectra to the 400-700 nm interval, 10 nm spacing representation used for rendering, and performed our calculations at this sampling.
-%
-%The rescaled spectra $I_i^s(\lambda)$ were then mean centered for PCA by subtracting out the mean 
-%rescaled spectrum, $\bar{I}^{s}(\lambda)$. That mean was obtained
-%by taking the sample mean over all rescaled spectra in the dataset, $\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}$. 
-%The resulting mean centered dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$
-%was decomposed as $I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA}$, 
-%where the $\hat{{\bf e}}_j^{PCA}$ are the PCA basis vectors obtained using the
-%singular value decomposition (SVD) applied to the $I_i^{MC}(\lambda)$ and
-%the $w_{ij}$ are the weights obtained by projecting each of $I_i^{MC}(\lambda)$ onto the  $\hat{{\bf e}}_j^{PCA}$ $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$.
-%We used the basis vectors corresponding to
-%the largest six SVD eigenvalues, so that $\{j \in [1,6]\}$.
-%For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance (Fig.~\ref{fig:granadaEV}).
-%These steps
-%can be summarized as follows:
-%\begin{align}
-%I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) \approx \sum_{j = 1}^6 w_{ij}\hat{{\bf e}}_j^{PCA}.
-%\end{align}
-%
-%To generate random illuminant spectra $\tilde{I}_i(\lambda)$, we generate weights $\tilde{w}_{ij}$ drawn from random 
-%the multivariate 
-%Gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-%and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
-%From these weights, the corresponding spectrum $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right)$ is generated.
-%This spectrum can sometimes have values that are less than zero.  In such cases, the weights are discarded and a new draw obtained, until
-%the condition $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, is satisfied for all $\lambda$.
-%The random illuminant spectrum is then given as
-%\begin{align}
-%\tilde{I}(\lambda) = \left( \tilde{I}_{MC}(\lambda) + \bar{I}_{s}(\lambda)\right).
-%\end{align}
-%Fig.~\ref{fig:randomIlluminant} shows a set of 100 spectra sampled in this manner, and may be compared with Fig.~\ref{fig:rescaledGranada}.
-Fig.~\ref{fig:xyDiagram} shows the CIE xy chromaticities of these samples and compares these with the chromaticities in the Granada dataset.
-Finally, Fig.~\ref{fig:sRGBIlluminant} provides an sRGB rendering of each spectrum in Fig.~\ref{fig:rescaledGranada}, to provide a visual sense of the chromatic variation in the sampled spectra.
-
 \subsubsection{Surface Reflectance Spectra}
@@
 \centering
-	\begin{subfigure}[b]{0.3 \textwidth}
+	\begin{subfigure}[b]{0.24 \textwidth}
     \centering
+            \caption{}
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_a.pdf}
-        \caption{Natural surface reflectance spectra}
         \label{fig:naturalSurface}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.24 \textwidth}
     \centering
+        \caption{}
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
-        \caption{Randomly generated spectra}
         \label{fig:randomSurface}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
+    \begin{subfigure}[b]{0.24 \textwidth}
     \centering
+    \caption{}
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
-        \caption{sRGB rendition of samples from \ref{fig:randomSurface}}
         \label{fig:sRGBSurface}
     \end{subfigure}    
-
     \centering
-	\begin{subfigure}[b]{0.3 \textwidth}
+	\begin{subfigure}[b]{0.24 \textwidth}
     \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_d.pdf}
-        \caption{Natural surface reflectance spectra}
+        \caption{}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure8.pdf}
         \label{fig:naturalSurfaceTarget}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_e.pdf}
-        \caption{Randomly generated target samples}
-        \label{fig:randomSurfaceTarget}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.3 \textwidth}
-    \centering
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_f.pdf}
-        \caption{sRGB rendition of target reflectance}
-        \label{fig:sRGBSurfaceTarget}
-    \end{subfigure}
-    \caption{{\bf Generating surface reflectance spectra:} Surface reflectance spectra are generated by random sampling based on measured surface reflectance spectra, using principles similar to those used to generate random illuminant spectra.
-(a) The 632 surface reflectance spectra from the Munsell and Vrhel datasets.
-(b) Randomly generated samples of reflectance spectra.
-(c) sRGB renderings (under CIE D65) of the random samples generated in \ref{fig:randomSurface}.
-(d)Normalized PCA eigenvalues and cumulative sum of the normalized eigenvalues for the mean centered surface reflectance dataset.
-The eigenvalues have been normalized by the sum over all eigenvalues.
-The dotted line at 0.9 on the y-axis is for reference.
-We used the first six eigenvectors in our analysis.
-(e) CIE xy chromaticity plot of the surface reflectance dataset (Fig.~\ref{fig:naturalSurface}), randomly generated samples of surface reflectance (Fig.~\ref{fig:randomSurface}) and randomly generated samples of target surface.
-(f) The sRGB renditions of the randomly generated sample of target object surface reflectance.
-The figure shows 10 randomly generated samples at 10 levels of the target object surface luminance.
-The range of luminance levels [0.2, 0.6] (indicated on the Y axis), captures the luminance of more than 90\% of the natural surface reflectances.}
+    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets (red, 632 samples) and randomly generated samples for background objects (black, 100 samples).
+(b) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (red) and a representative sample of 100 background object surface reflectances (black) and 100 target object surface reflectances (green).
+(c) sRGB renditions of the 100 random samples of background object surface reflectance.
+(d) sRGB renditions of the target object surface reflectance.
+random samples after rescaling.
+The figure shows 10 randomly generated samples at 10 levels of the target object LRV.
+The LRV range of [0.2, 0.6], captures more than 90\% of the natural surface reflectances.}
 \label{fig:surfaceReflectanceGeneration}
@@
 		\centering
+        \caption{sRGB rendering of a 3D scene}
         \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.png}
-        \caption{sRGB rendering of a 3D scene}
         \label{fig:3DScene}
@@
     \hspace{0.1 \textwidth}
+        \caption{Cropped Image}
+        \vspace{1.5mm}
         \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.png}
-        \caption{Cropped Image}
         \label{fig:croppedImage}
@@
     \hspace{0.1 \textwidth}
+        \caption{Optical Image}
+        \vspace{1.5mm}
         \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.png}
-        \caption{Optical Image}
         \label{fig:croppedImageWithMosaic}
@@
     \begin{subfigure}[b]{0.2 \textwidth}
+        \caption{LMS cone contrast}
         \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_d.png}
-        \caption{LMS cone contrast}
         \label{fig:coneContrast}
@@
 To analyze the local image information, we cropped and processed the image in the immediate neighborhood of the target object such that each patch represented a one degree of visual angle, approximately the size of a receptive field in early visual cortex (\ref{fig:croppedImage}).
-Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 luminance levels for the three cases considered in this paper.
+Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 luminance levels for the three conditions considered in this paper.
 Next, the cropped multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
@@
 The three $51 \times 51$ sets of cone responses corresponding to the L, M and S cones were then reshaped into a single $7803 \times 1$ vector ($7803 = 51 \times 51 \times 3$).
-For case 1 and 3 we used this as the input for the supervised methods.
-For case 3 and 4, to model the contrast coding and contrast adaptation, we convert this vector to a contrast representation by subtracting out the mean and then dividing by it (contrast coding), followed by normalizing the vector to have unit length (contrast normalization).
-The cone-response vectors corresponding to the N images for each case are concatenated column-wise to form a contrast normalized matrix $C_{7803\times N}$.
+For Condition 1 and 3 we used this as the input for the supervised methods.
+For Condition 3 and 4, to model the contrast coding and contrast adaptation, we convert this vector to a contrast representation by subtracting out the mean and then dividing by it (contrast coding), followed by normalizing the vector to have unit length (contrast normalization).
+The cone-response vectors corresponding to the N images for each condition are concatenated column-wise to form a contrast normalized matrix $C_{7803\times N}$.
 The corresponding labels are represented by the row vector $Y_{1\times N}$.
@@
 \subsubsection*{Linear Regression} For linear regression, we solve the equation $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
-Here, $C_{3\times N}$ is a matrix containing either the L, M and S cone responses (for case 1 and 2) or contrast normalized responses (for case 3 and 4) of the central patch of each image, extracted from $C_{7803\times N}$.
+Here, $C_{3\times N}$ is a matrix containing either the L, M and S cone responses (for Condition 1 and 2) or contrast normalized responses (for Condition 3 and 4) of the central patch of each image, extracted from $C_{7803\times N}$.
 The columns corresponds to the N images in the dataset.
@@
 % THINGS TO THINK ABOUT:
-%  1) Putting error bars on performance.  Particularly want to be sure that Fig 13 feature that Case 3 RFs do better than Case 1 RFs for Case 1 is just statistical sampling.
+%  1) Putting error bars on performance.  Particularly want to be sure that Fig 13 feature that Condition 3 RFs do better than Condition 1 RFs for Condition 1 is just statistical sampling.
 
 \section{Results} \label{Results}
-In this section, we discuss the results of supervised learning to estimate the luminance of the target object on the the various cases we described previously.
+In this section, we discuss the results of supervised learning to estimate the luminance of the target object on the the various conditions we described previously.
 We describe the computations that need to be performed on the cone photoreceptor responses to estimate the luminance.
-We start with case 1, where only the reflectance spectrum of the target object is allowed to vary, and show that in this case the luminance can be estimated directly from the photoreceptor response.
+We start with condition 1, where only the reflectance spectrum of the target object is allowed to vary, and show that in this condition the luminance can be estimated directly from the photoreceptor response.
 We then progressively increase the complexity of the spectral conditions and explain the correspondingly complex computations that are required to estimate the target LRV.
-Next, we show the optimal AMA receptive fields for each one of the spectral cases discussed in this work.
+Next, we show the optimal AMA receptive fields for each one of the spectral conditions discussed in this work.
 We show that the optimal receptive fields for target luminance estimation have a center surround structure and they give more weights to the response of L and M cones than S cones.
-We finally show that, as expected, the receptive fields for the complex spectral cases generalize to the simple cases.
-Hence, one requires only one set of optimal receptive fields for estimating the target luminance, not separate receptive fields for each spectral case.
+We finally show that, as expected, the receptive fields for the complex spectral conditions generalize to the simple conditions.
+Hence, one requires only one set of optimal receptive fields for estimating the target luminance, not separate receptive fields for each spectral condition.
 
-\subsection{Luminance estimates for each spectral case}
-\subsubsection{Case 1: Target object relative surface reflectance spectrum variable, light source and background object spectra fixed}
+\subsection{Luminance estimates for each spectral condition}
+\subsubsection{Condition 1: Target object relative surface reflectance spectrum variable, light source and background object spectra fixed}
 We start with the results of the simplest type of spectral variation where only the target object relative surface reflectance spectrum is allowed to change. 
-We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV from the model cone photoreceptor response to the images from this case.
+We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV from the model cone photoreceptor response to the images from this condition.
 Fig.~\ref{fig:case1RFResponse} shows the projection of the photoreceptor response along the first two optimal AMA receptive fields. 
@@
 We used such projections and a generalized Bayes' decoder (see methods) to estimate the luminance of the target objects in the test set stimuli. 
-Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test stimuli in case 1. 
+Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test stimuli in condition 1. 
 We show the estimates obtained by AMA and two null models: a naive method that assigns the average target LRV across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object (see Methods).
@@
         \begin{subfigure}[b]{0.3 \textwidth}
+        \caption{RF response condition 0}
+        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
+        \label{fig:case0RFResponse}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.3 \textwidth}
+        \caption{RF response condition 1}
         \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
-        \caption{RF response Case 1}
         \label{fig:case1RFResponse}
@@
             \begin{subfigure}[b]{0.297 \textwidth}
+        \caption{Luminance Estimates}
         \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
-        \caption{Luminance Estimates}
         \label{fig:case9Results}
     \end{subfigure}    
-        \begin{subfigure}[b]{0.3 \textwidth}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
-        \caption{Images with fixed relative spectrum}
-        \label{fig:case0RFResponse}
-    \end{subfigure}
-    \caption{{\bf Case 1: RF response and luminance estimates:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of case 1.
+    \caption{{\bf RF response and luminance estimates for condition 0 (baseline) and condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 0.
 We show the response for the images in the training set.
 Each response cloud represents the response of images corresponding to one luminance level.
-The response clouds are approximated by a multinormal Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(b) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA.
+The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
+(b) Photoreceptor response for images of condition 1.
+(c) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA.
 The estimates fall along the diagonal unit slope (blue dotted) line for both linear regression and AMA.
-The standard deviations are too small to be visible.
-(c) Photoreceptor response for images with fixed relative shape of the target object reflectance spectrum projected along the first two case 1 AMA receptive fields.
-The variation coming from the poisson nature of the photoreceptor isomerization is small compared to the variation due to shape of target object reflectance spectrum.}
+The standard deviations are too small to be visible.}
 \label{fig:sourcesOfNoise}
@@
 
-\subsubsection{Case 2: Target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable}
+\subsubsection{Condition 2: Target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable}
 When the light source emission spectrum is fixed, the naive expectation would be that the luminance of the target object would depend only on the surface reflectance of the target object. 
@@
 But our analysis shows that the secondary reflections from the target object, of the light coming indirectly after being reflected from the background objects, have a significant effect on the response of the photoreceptors corresponding to the target object.
-Fig.~{\ref{fig:case2RFResponse}} shows the projection of the photoreceptor response for the stimuli in case 2 along the first two AMA receptive fields. 
-These receptive fields were learnt using the stimuli from the same case 2. 
-The response projected along the first two optimal receptive fields do not separate as well compared to case 1. 
+Fig.~{\ref{fig:case2RFResponse}} shows the projection of the photoreceptor response for the stimuli in condition 2 along the first two AMA receptive fields. 
+These receptive fields were learnt using the stimuli from the same condition (Condition 2). 
+The response projected along the first two optimal receptive fields do not separate as well compared to condition 1. 
 But the overlap is lower if the projection is considered in subspaces that have more AMA receptive fields. 
@@
 
-%% Figure Case 2
+%% Figure condition 2
 \begin{figure}
@@
     \begin{subfigure}[b]{0.3	 \textwidth}   
+        \caption{RF response condition 2}
         \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.pdf}
-        \caption{RF response Case 2}
         \label{fig:case2RFResponse}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
+        \caption{Luminance Estimates}
         \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.pdf}
-        \caption{Luminance Estimates}
         \label{fig:case2Estimates}
     \end{subfigure}
-    \caption{{\bf Case 2:} (a) Photoreceptor response projected along the first two AMA receptive fields.
-(b) Estimated v/s assigned target LRV for the image in case 2.
+    \caption{{\bf Condition 2:} (a) Photoreceptor response projected along the first two AMA receptive fields.
+(b) Estimated v/s assigned target LRV for the image in condition 2.
 Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.}
@@
 
-\subsubsection{Case 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed}
-For the spectral variations of case 3, the AMA receptive fields learnt on the photoreceptor response to the images does a very poor job in predicting the target LRV (Fig.~\ref{fig:isomerizationFails}).
-This is because, since the illuminant spectra varies in this case, the photoreceptor response is not directly proportional to the target object surface anymore. 
-But, since the background surfaces are fixed in this case, the ratio between the response of  photoreceptors corresponding to the target object and the background remains proportional to the target LRV.
+\subsubsection{Condition 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed}
+For the spectral variations of condition 3, the AMA receptive fields learnt on the photoreceptor response to the images does a very poor job in predicting the target LRV (Fig.~\ref{fig:isomerizationFails}).
+This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
+But, since the background surfaces are fixed in this condition, the ratio between the response of  photoreceptors corresponding to the target object and the background remains proportional to the target LRV.
 This is because a change in illuminant spectra produces the same effect in both the target object and the background object. 
 Thus, the AMA receptive fields learnt on the contrast normalized photoreceptor response (see Methods) can be used to predict the target LRV (Fig.~\ref{fig:constrastWorks}). 
-Fig.~\ref{fig:case10Results} shows the estimated target LRV v/s the assigned luminance for the images in case 3 obtained using the contrast normalized representation. 
+Fig.~\ref{fig:case10Results} shows the estimated target LRV v/s the assigned luminance for the images in condition 3 obtained using the contrast normalized representation. 
 AMA receptive fields provide excellent predictions of the target LRV. 
@@
 
-%% Figure Case 3: Isomerization Fails
+%% Figure condition 3: Isomerization Fails
 \begin{figure}
@@
     \begin{subfigure}[b]{0.3	 \textwidth}   
+        \caption{RFs learnt using photoreceptor response}
         \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
-        \caption{RFs learnt using photoreceptor response}
         \label{fig:isomerizationFails}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
+        \caption{RFs learnt using contrast signal}
         \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
-        \caption{RFs learnt using contrast signal}
         \label{fig:constrastWorks}
@@
             \begin{subfigure}[b]{0.3 \textwidth}
+        \caption{Luminance estimates}
         \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
-        \caption{Luminance estimates}
         \label{fig:case10Results}
     \end{subfigure}
-    \caption{{\bf Case 3: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
+    \caption{{\bf Condition 3: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
 (b) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
@@
 The response at each luminance level separates much better in this representation.
-(c) Estimated v/s assigned target LRV for the image in case 3.
+(c) Estimated v/s assigned target LRV for the image in condition 3.
 Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
@@
 
-Again, similar to case 2, the projection along the first two receptive fields shows an overlap between the stimuli at higher luminance values (Fig.~\ref{fig:constrastWorks}).
+Again, similar to condition 2, the projection along the first two receptive fields shows an overlap between the stimuli at higher luminance values (Fig.~\ref{fig:constrastWorks}).
 But, the stimuli are better separated if the projection is considered within a subspace that has more receptive fields (Fig.~\ref{fig:ErrorVsNFilters}).
 
-\subsubsection{Case 4: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
-% Figure Case 4
+\subsubsection{Condition 4: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
+% Figure condition 4
 \begin{figure}
@@
     \begin{subfigure}[b]{0.3 \textwidth}   
+        \caption{AMA RF Response}
         \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
-        \caption{AMA RF Response}
         \label{fig:case12FiltersResponse}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
+        \caption{Luminance Estimates}
         \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
-        \caption{Luminance Estimates}
         \label{fig:case12Results}
     \end{subfigure}
-    \caption{{\bf Case 3:} (a) Contrast normalized photoreceptor response projected along the first two AMA receptive fields.
-(b) Target LRV estimates v/s assigned luminance for images in case 3.
+    \caption{{\bf Condition 3:} (a) Contrast normalized photoreceptor response projected along the first two AMA receptive fields.
+(b) Target LRV estimates v/s assigned luminance for images in condition 3.
 The AMA estimates are unbiased and have smaller relative error compared to linear model.}
@@
 
-Case 4 is the most complex type of variation that we consider in this work.
+Condition 4 is the most complex type of variation that we consider in this work.
 Here we allow all three types of spectra to change from image to image.
-In this case, neither the photoreceptor response (as in Case 1 and 2), nor any simple transformation of the response (case 3) can provide the target LRV.We used AMA to learn the receptive fields using the contrast normalized cone photoreceptor response from stimuli in case 4.
-Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in case 4.
-We have used the first 8 receptive fields to estimate the luminance in this case (see Fig.\ref{fig:ErrorVsNFilters}). 
+In this condition, neither the photoreceptor response (as in condition 1 and 2), nor any simple transformation of the response (condition 3) can provide the target LRV.We used AMA to learn the receptive fields using the contrast normalized cone photoreceptor response from stimuli in condition 4.
+Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in condition 4.
+We have used the first 8 receptive fields to estimate the luminance in this condition (see Fig.\ref{fig:ErrorVsNFilters}). 
 The AMA receptive fields do an excellent job of predicting the target LRV. 
@@
 \begin{subfigure}{0.21 \textwidth}
+	\caption{Condition 1}
 	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
-	\caption{Case 1}
 	\label{fig:case1Filter}
@@
     \begin{subfigure}{0.21 \textwidth}   
+	\caption{Condition 2}
 	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
-	\caption{Case 2}
 	\label{fig:case2Filter}
@@
         \begin{subfigure}{0.21 \textwidth}
+	\caption{Condition 3}
 	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
-	\caption{Case 3}
 	\label{fig:case3Filter}
@@
         \begin{subfigure}{0.21 \textwidth}
+	\caption{Condition 4}
 	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_d.pdf}
-	\caption{Case 4}
 	\label{fig:case4Filter}
     \end{subfigure}
-\caption{{\bf AMA receptive fields:} The first two AMA receptive fields for the four cases studied in this work.
+\caption{{\bf AMA receptive fields:} The first two AMA receptive fields for the four conditions studied in this work.
 The receptive fields show a center surround structure.
 The L and M filters have larger weight as luminance is essentially a function of the L and M cone isomerizations.
-The stereotypical pattern in the receptive fields of case 4 is due to the fixed geometry of the images.}
+The stereotypical pattern in the receptive fields of condition 4 is due to the fixed geometry of the images.}
  \label{fig:AMAFilters}
@@
 
-For case 1, since the illuminant and the background are fixed, all the information is in the central target object reflectance.
+For condition 1, since the illuminant and the background are fixed, all the information is in the central target object reflectance.
 Thus, the RFs weights are mostly concentrated around the center.
-For case 2, where the target and the background spectra varies, most of the luminance information is still concentrated around the central target object.
-For case 3, while the target and the illuminant spectra varies, the background object spectra is fixed.
+For condition 2, where the target and the background spectra varies, most of the luminance information is still concentrated around the central target object.
+For condition 3, while the target and the illuminant spectra varies, the background object spectra is fixed.
 Hence, the luminance can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background.
-Thus, while the RFs show a trend of weights concentrated at the center similar to case 1, there is large negative contribution from the surround.
+Thus, while the RFs show a trend of weights concentrated at the center similar to condition 1, there is large negative contribution from the surround.
 The spatial features of the RFs are due the stereotypical geometry of the images (see \nameref{Methods}).
-Case 4 has a similar center surround structure, but with more prominent features of the background since the spectra of the background objects are also varying.
+Condition 4 has a similar center surround structure, but with more prominent features of the background since the spectra of the background objects are also varying.
 Again, the spatial features are a result of the stereotypical geometry of the images.
 
-\subsection{The receptive fields of complex case generalize on simpler cases}
+\subsection{The receptive fields of complex condition generalize on simpler conditions}
 Fig.~\ref{fig:barGraphs} shows the relative error for the estimates of the target LRV obtained using the linear model and AMA.
-We show the relative error of the estimates obtained using the AMA receptive fields from all cases.
-The receptive fields from a more complex case perform at par on the stimuli from a simpler case.
+We show the relative error of the estimates obtained using the AMA receptive fields from all conditions.
+The receptive fields from a more complex condition perform at par on the stimuli from a simpler condition.
 The optimal AMA estimates are better than that of the linear model.
@@
 \begin{subfigure}{0.22 \textwidth}
+	\caption{Condition 1}
 	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_a.pdf}
-	\caption{Case 1}
 	\label{fig:case1Bar}
@@
     \begin{subfigure}{0.22 \textwidth}   
+	\caption{Condition 2}
 	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_b.pdf}
-	\caption{Case 2}
 	\label{fig:case2Bar}
@@
         \begin{subfigure}{0.22 \textwidth}
+	\caption{Condition 3}
 	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_c.pdf}
-	\caption{Case 3}
 	\label{fig:case3Bar}
@@
         \begin{subfigure}{0.22 \textwidth}
+	\caption{Condition 4}
 	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_d.pdf}
-	\caption{Case 4}
 	\label{fig:case4Bar}
     \end{subfigure}
-\caption{{\bf Comparison of optimal RFs across cases:} Comparison of optimal AMA receptive fields from one case on the images of other cases.
-Each panel shows the relative error estimates on the same set of images obtained using the receptive fields of the four cases (case 1-4).
-(a) Error estimates for images of case 1.
+\caption{{\bf Comparison of optimal RFs across cases:} Comparison of optimal AMA receptive fields from one condition on the images of other cases.
+Each panel shows the relative error estimates on the same set of images obtained using the receptive fields of the four cases (condition 1-4).
+(a) Error estimates for images of condition 1.
 The AMA receptive fields from all three cases perform well in this case.
-(b) Error estimates for images of case 2.
-As expected, the best estimates are provided by the receptive fields of case 2.
-(c) Error estimates for images of case 3.
-(d) Error estimates for images of case 4.}
+(b) Error estimates for images of condition 2.
+As expected, the best estimates are provided by the receptive fields of condition 2.
+(c) Error estimates for images of condition 3.
+(d) Error estimates for images of condition 4.}
  \label{fig:barGraphs}

### 2018-03-30 Draft3/appendix.tex
edits to the figure captions

@@
 Let us denote the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset.
-Since the measured spectra vary over several orders of magnitude in overall intensity, we rescale each spectrum by dividing it by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$.
+Since the measured spectra vary over several orders of magnitude in overall intensity, we normalize each spectrum by dividing it by its mean $I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}$.
 For simplicity of notation, we denote wavelength $\lambda$ as a continuous variable; in the actual calculations wavelength is discretely sampled and integrals are approximated by sums.
@@
 Gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
+and co-variance $\Sigma$ given as:
+\begin{align}
+\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right).
+\end{align}
 From these weights, the corresponding spectrum $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right)$ is generated.
@@
 and $M$ is the total number of spectra in the dataset. 
-We calculated the mean reflectance spectrum,
+We first calculated the mean reflectance spectrum,
 $\bar{R}(\lambda)$, by taking the sample mean over all spectra in the dataset, i.e.,
-$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. Then, we mean centered 
-the reflectance dataset by subtracting the mean spectrum, $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
-We decomposed this mean centered dataset as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$, where
-the ${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
+\begin{align}
+\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda).\end{align} 
+The reflectance dataset is mean centered by subtracting the mean spectrum, $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
+This mean centered dataset as:
+\begin{align}
+R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}},
+\end{align} 
+where the ${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
 and the $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the basis vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
 $\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$.
+
 We used the basis vectors corresponding to the largest six SVD eigenvalues. 
@@
 and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
-If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, we use them to give the random reflectance spectrum as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.
+
+If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, we use them to give the random reflectance spectrum as:
+\begin{align}
+\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda).
+\end{align}
 Otherwise the draw is discarded and a new set of weights is drawn.

### 2018-03-30 Draft3/draft3.tex
edits to the figure captions

@@
         \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
-        \label{fig:sRGBIlluminant}
+        \label{fig:sRGBIlluminantScaled}
     \end{subfigure}
-    \caption{{\bf Illumination spectra:} (a) Mean scaled Granada dataset (red, 2600 samples) and 100 randomly generated samples using the rescaled spectra (black).
-(b) CIE xy chromaticity diagram of the mean scaled dataset and the random samples.
+    \caption{{\bf Illumination spectra:} (a) Normalized Granada dataset (red, 2600 samples of Granada dataset) and 100 randomly generated samples using the rescaled spectra (black).
+(b) CIE xy chromaticity diagram of the normalized dataset and the random samples.
 (c) sRGB renditions of 100 random samples before scaling.
 (d) sRGB renditions of the samples after scaling.}
+\label{fig:illuminant}
 \end{figure}
@@
 The overall intensity of the measurements spans approximately three orders of magnitude.
-Figure~\ref{fig:rescaledGranada} plots the measurements in normalized form to make apparent the variation in the relative spectra.
+Figure~\ref{fig:illuminantSpectra} plots the measurements in normalized form (red) to make apparent the variation in the relative spectra. The spectra are normalized by their mean over wavelength.
 
@@
 To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
-Figure~ref{fig:illuminantSpectra} illustrates the relative spectra of draws obtained using this procedure.
+Figure~\ref{fig:illuminantSpectra} also illustrates the relative spectra of draws obtained using this procedure (black).
 Details of the statistical model for illumination are provided in the appendix.
@@
 We obtained each scale factor by randomly sampling (with replacement) a spectrum from the Granda dataset and taking its mean. 
+Color swatches of samples of illuminant spectra are shown in Figure~\ref{fig:illuminant}.
 
@@
 \centering
-	\begin{subfigure}[b]{0.24 \textwidth}
+	\begin{subfigure}{0.24 \textwidth}
     \centering
@@
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_a.pdf}
-        \label{fig:naturalSurface}
+        \label{fig:reflectanceSpectra}
     \end{subfigure}
-    \begin{subfigure}[b]{0.24 \textwidth}
+    \begin{subfigure}{0.24 \textwidth}
     \centering
@@
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
-        \label{fig:randomSurface}
+        \label{fig:xyChroReflectance}
     \end{subfigure}
-    \begin{subfigure}[b]{0.24 \textwidth}
+    \begin{subfigure}{0.24 \textwidth}
     \centering
@@
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
-        \label{fig:sRGBSurface}
+        \label{fig:backgroundSwatches}
     \end{subfigure}    
     \centering
-	\begin{subfigure}[b]{0.24 \textwidth}
+	\begin{subfigure}{0.24 \textwidth}
     \centering
@@
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure8.pdf}
-        \label{fig:naturalSurfaceTarget}
+        \label{fig:targetSwatches}
     \end{subfigure}
-    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets (red, 632 samples) and randomly generated samples for background objects (black, 100 samples).
-(b) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (red) and a representative sample of 100 background object surface reflectances (black) and 100 target object surface reflectances (green).
+    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets (red, 632 samples), representative samples of background object surface reflectances (black, 100 samples) and target object surface reflectances (green, 100 samples).
+(b) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (red) and randomly generated samples of surface reflectances for background objects (black) and target objects (green).
 (c) sRGB renditions of the 100 random samples of background object surface reflectance.
 (d) sRGB renditions of the target object surface reflectance.
-random samples after rescaling.
 The figure shows 10 randomly generated samples at 10 levels of the target object LRV.
@@
 We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
-measurements to create a database containing 632 reflectance spectra.
+measurements to create a database containing 632 reflectance spectra Figure~\ref{fig:reflectanceSpectra}.
 The Munsell database contains 462 spectra each measured at 5nm sampling intervals between 380nm and 780nm.
@@
 We resampled these spectra to 31 evenly-spaced wavelengths between $400$nm and $700$nm.
-Figure~ref{ENTER REF FIG} illustrates the spectra of draws obtained using this procedure.
+Figure~\ref{fig:reflectanceSpectra} illustrates the spectra of draws obtained using this procedure.
 Details of the statistical model for surface reflectance spectra are provided in the appendix.
-
-% THIS GOES TO THE SAME APPENDIX AS THE ILLUMINANT MATH.
-%Let us denote the reflectance dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
-%and $M$ is the total number of spectra in the dataset. 
-%We calculated the mean reflectance spectrum,
-%$\bar{R}(\lambda)$, by taking the sample mean over all spectra in the dataset, i.e.,
-%$\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda)$. Then, we mean centered 
-%the reflectance dataset by subtracting the mean spectrum, $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$. 
-%We decomposed this mean centered dataset as $R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}}$, where
-%the ${\bf \hat{e}}_j^{\rm PCA}$s are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
-%and the $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the basis vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
-%$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. 
-%We used the basis vectors corresponding to the largest six SVD eigenvalues. 
-%For the combined Munsell and Vrhel datasets, these six eigenvalues account for 
-%more than $90\%$ of the variance. 
-%To generate random reflectance spectra, we generate samples of weights ($\tilde{w}_{ij}$) drawn from the multivariate Gaussian 
-%distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-%and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $.
-If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, we use them to give the random reflectance spectrum as: $\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)$.
-Otherwise the draw is discarded and a new set of weights is drawn.
 
@@
 scaled such that the LRV had the desired value (see appendix).
-Figure \ref{TARGET FIG} shows color swatches of target reflectance spectra rendered under CIE illuminant D65, for evenly spaced LRV values.
-
-%The scaling equals $\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}$, with $\bar{y}(\lambda)$ being the CIE photopic luminosity (or luminous efficiency) function. 
-%$\bar{y}(\lambda)$ describes the average spectral sensitivity of human visual 
-%perception of bruminance.
-The target reflectance is then given by: $\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right)$.
+Figure \ref{fig:targetSwatches} shows color swatches of target reflectance spectra rendered under CIE illuminant D65, for evenly spaced LRV values.
 

### 2018-04-02 Draft3/draft3.tex
small edits

@@
 The perceived color of an object has important behavioral implications, since color helps to identify objects and their properties \cite{Mollon89, Jacobs81}.
+[THIS PERCEIVED COLOR DEPENDS ON THE SURFACE REFLECTANCE OF THE OBJECT.]
 Perceived object color is not sensed directly. Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
@@
 The ability of a visual system to extract such a stable representation is called color constancy. 
-Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}.
+[DO WE NEED THIS LINE -] Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
 In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eye to produce percepts well-correlated with object surface reflectance.
@@
 We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of an object's surface reflectance function.
-The LRV is a measure of the overall amount of light reflected by surface (\citeauthor{astm1121477}).
+The LRV is a measure of the overall amount of light reflected by a surface (\citeauthor{astm1121477}).
 More precisely, the LRV is the luminance of the light that would
@@
 %Condition 3: Target Color and Illuminant
-%Condition 3a: Target Color and Relative Illuminant
+%Condition 4a: Target Color, Background and Relative Illuminant
 %Condition 4: Everything
 
-For the primary results we used the ``{\it Library}'' base scene and a sphere as the target object.
-We also inserted a spherical light source with the same ``{\it Big Ball}'' shape.
+For the primary results, we used the ``{\it Library}'' base scene and the spherical ``{\it Big Ball}'' shape as the target object.
+We also inserted an additional spherical light source with the same ``{\it Big Ball}'' shape.
 The position and size of the inserted object, light source and the camera were held fixed.
@@
 The overall intensity of the measurements spans approximately three orders of magnitude.
-Figure~\ref{fig:illuminantSpectra} plots the measurements in normalized form (red) to make apparent the variation in the relative spectra. The spectra are normalized by their mean over wavelength.
+Figure~\ref{fig:illuminantSpectra} plots the measurements in normalized form to make apparent the variation in the relative spectra. The spectra are normalized by their mean over wavelength.
 
@@
 To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
-Figure~\ref{fig:illuminantSpectra} also illustrates the relative spectra of draws obtained using this procedure (black).
+Figure~\ref{fig:illuminantSpectra} also illustrates the relative spectra of draws obtained using this procedure.
 Details of the statistical model for illumination are provided in the appendix.
@@
 \subsection{Supervised Learning methods} \label{method:SupervisedLearning}
-We have two supervised learning methods in our work: Linear regression and Accuracy maximization analysis. While, our main focus is on AMA, linear regression provides a baseline performance measure.
+We have used two supervised learning methods in our work: Linear regression and Accuracy maximization analysis.
+While, our main focus is on AMA, linear regression provides a baseline performance measure.
 

### 2018-04-02 Draft3/draft3.tex
Today’s work

@@
 
-For the primary results, we used the ``{\it Library}'' base scene and the spherical ``{\it Big Ball}'' shape as the target object.
-We also inserted an additional spherical light source with the same ``{\it Big Ball}'' shape.
-The position and size of the inserted object, light source and the camera were held fixed.
+For the primary results, we used the ``{\it Library}'' base scene and a spherical target object .
+The library base scene contains X area lights. We inserted one additional spherical spherical light source into the scene.
+The position and size of the inserted object, inserted light source and viewpoint were held fixed across all scenes in the database,
+as shown in Figure (REF 8a).
 Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra.
@@
 Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
-A $51 \times 51$ pixel patch was cropped around the target object for further analysis.
-This corresponded to $1 \times 1$ degrees of visual angle for the model of the early visual system, also described below.
 
@@
 (b) The central portion of the rendered image, which contains the target object, is cropped from the image.
-(c) The response of retinal cones to the cropped image is simulated using the isetbio software package to model early vision.
-The software models optical blurring and foveal spatial sampling by the trichromatic cone mosaic.
-Fig.~\ref{fig:croppedImageWithMosaic} shows the retinal image incident on the cone mosaic and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
+(c) The retinal image incident on the cone mosaic after optical blurring and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
 (d) The cone responses are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
@@
 
-The sampling and rendering steps described above allow us to generate images from scenes that contain an image of a target object of known surface luminance at the center pixel, and where the illuminant spectra and spectra of the other surfaces in the scene are drawn randomly from models of naturally occurring spectra.
+The light entering the eye is blurred by the eye's optics.
+The resulting retinal image is sampled by a mosaic of cone photoreceptors.
+The responses of these photoreceptors provide the information about the scene that is available to the neural visual system for further processing.
+Because we are interested in how well luminance constancy may be achieved by the human visual system, we simulated the cone responses
+to our scenes using a model of the early visual system.
+
+We focussed our analysis on regions of the image local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; REF 8b).
+This choice is motivated by the observation that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
+In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle (REFS).
+% Johannes to provide his favorite citation or two.  Some review.
+
+We modeled a visual system with a pupil diameter of XX mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image (REF whatever optics model), spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (Brainard mosaic review; Fig.~\ref{fig:croppedImageWithMosaic}).
+The cone mosaic contained  L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological stanard (REF).
+Cone isomerizations were computed assuming an integration time of XX msec, and we modeled the Poisson nature of photopigment isomerization (REF Hecht et al).
+This modeling was implemented using the software infratstructure provided by ISETBio (REF).
+
+The cone isomerizations represent the first step of visual processing.
+To capture key properties of post-receptoral processing, such as contrast normalization \cite{heeger1992normalization,albrecht1991motion,carandini2012normalization},
+we processed the isomerizations as follows:
+First, we generated a response for each cone class at the each pixel in the sampled retinal image, using bilinear interpolation separately for each cone class.
+This step does not add information.
+% DOUBLE CHECK THAT THIS WAS DONE WITH SOMETHING LIKE INTERP2 WITH THE LINEAR OPTION.
+This gives us a cone response image for each cone class.
+We then convert each cone image to a contrast representation by subtracting and dividing by the mean.
+Finally  followed by normalizing the vector to have unit length (contrast normalization).
+
+The three $51 \times 51$ sets of cone responses corresponding to the L, M and S cones were then reshaped into a single $7803 \times 1$ vector ($7803 = 51 \times 51 \times 3$).
+For Condition 1 and 3 we used this as the input for the supervised methods.
+For Condition 3 and 4,
+The cone-response vectors corresponding to the N images for each condition are concatenated column-wise to form a contrast normalized matrix $C_{7803\times N}$.
+The corresponding labels are represented by the row vector $Y_{1\times N}$.
+
+%The sampling and rendering steps described above allow us to generate images from scenes that contain an image of a target object of known surface luminance at the center pixel, and where the illuminant spectra and spectra of the other surfaces in the scene are drawn randomly from models of naturally occurring spectra.
 One such image is shown in Fig.~\ref{fig:3DScene}, where the green sphere in the middle is the target object and the light sources are not within the camera field of view.
@@
 
-In this work, we are interested in how well luminance constancy may be achieved using information that is local to the image region containing the target object. 
-To analyze the local image information, we cropped and processed the image in the immediate neighborhood of the target object such that each patch represented a one degree of visual angle, approximately the size of a receptive field in early visual cortex (\ref{fig:croppedImage}).
-Fig. \ref{fig:studiedCases} shows examples of such cropped image at 3 luminance levels for the three conditions considered in this paper.
-Next, the cropped multispectral images are used to simulate retinal cone responses using \href{https://github.com/isetbio}{Isetbio} software.
 The key steps we model are the size of the pupil, optical blurring (including axial chromatic aberration) in the formation of the retinal image, spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones, and the Poisson nature of photopigment isomerization.
@@
 The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
-The retinal cone mosaic is modeled as a square grid with $51 \times 51$ cones in the L:M:S ratio 0.6:0.3:0.1.
+The retinal cone mosaic is modeled as a square grid with $51 \times 51$ cones in the.
 The response of the cones are taken as the number of isomerizations in the cone segment ({\it over what time ??}).
@@
 Otherwise, the S cone contribution would be very low.
-
-The cone isomerizations represent the first step of visual processing.
-To capture key properties of post-receptoral processing, such as contrast normalization \cite{heeger1992normalization,albrecht1991motion,carandini2012normalization},
-we processed the isomerizations as follows:
-First, we created a representation for each cone class on the full $51 \times 51$ pixel grid, we interpolated the responses of the cones in each class across the grid, using bilinear interpolation separately for each cone class.
-% DOUBLE CHECK THAT THIS WAS DONE WITH SOMETHING LIKE INTERP2 WITH THE LINEAR OPTION.
-This gives us a $51 \times 51$ cone response image for each cone class.
-The three $51 \times 51$ sets of cone responses corresponding to the L, M and S cones were then reshaped into a single $7803 \times 1$ vector ($7803 = 51 \times 51 \times 3$).
-For Condition 1 and 3 we used this as the input for the supervised methods.
-For Condition 3 and 4, to model the contrast coding and contrast adaptation, we convert this vector to a contrast representation by subtracting out the mean and then dividing by it (contrast coding), followed by normalizing the vector to have unit length (contrast normalization).
-The cone-response vectors corresponding to the N images for each condition are concatenated column-wise to form a contrast normalized matrix $C_{7803\times N}$.
-The corresponding labels are represented by the row vector $Y_{1\times N}$.
 

### 2018-04-02 Draft3/draft3.tex
fixed figures

@@
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
-        \label{fig:xyChroReflectance}
+        \label{fig:reflectanceSamples}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
-        \label{fig:backgroundSwatches}
+        \label{fig:xyChroReflectance}
     \end{subfigure}    
@@
         \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure8.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_d.pdf}
+        \label{fig:backgroundSwatches}
+    \end{subfigure}
+    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.(b) Representative samples of object surface reflectances.
+(c) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (black) and samples of surface reflectances (red).
+(d) sRGB renditions of the samples of object surface reflectance.}
+\label{fig:surfaceReflectanceGeneration}
+\end{figure}
+
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{../Figures/Figure7/Figure8.pdf}
+\caption{{\bf Target surface reflectance spectra:} sRGB renditions of the target object surface reflectance.
+The figure shows 10 random samples at 10 equally spaced LRV levels in the range [0.2, 0.6].
+This range captures more than 90\% of the natural surface reflectances.}
 \label{fig:targetSwatches}
-    \end{subfigure}
-    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets (red, 632 samples), representative samples of background object surface reflectances (black, 100 samples) and target object surface reflectances (green, 100 samples).
-(b) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (red) and randomly generated samples of surface reflectances for background objects (black) and target objects (green).
-(c) sRGB renditions of the 100 random samples of background object surface reflectance.
-(d) sRGB renditions of the target object surface reflectance.
-The figure shows 10 randomly generated samples at 10 levels of the target object LRV.
-The LRV range of [0.2, 0.6], captures more than 90\% of the natural surface reflectances.}
-\label{fig:surfaceReflectanceGeneration}
 \end{figure}

### 2018-04-03 Draft3/draft3.tex
small edits

@@
 The position and size of the inserted object, inserted light source and viewpoint were held fixed across all scenes in the database,
-as shown in Figure (REF 8a).
+as shown in Figure~\ref{fig:3DScene}.
 Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra.
@@
 
-We focussed our analysis on regions of the image local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; REF 8b).
+We focussed our analysis on regions of the image local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
 This choice is motivated by the observation that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
@@
 
-We modeled a visual system with a pupil diameter of XX mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image (REF whatever optics model), spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (Brainard mosaic review; Fig.~\ref{fig:croppedImageWithMosaic}).
-The cone mosaic contained  L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological stanard (REF).
-Cone isomerizations were computed assuming an integration time of XX msec, and we modeled the Poisson nature of photopigment isomerization (REF Hecht et al).
-This modeling was implemented using the software infratstructure provided by ISETBio (REF).
+We modeled a visual system with a pupil diameter of 3 mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image (REF whatever optics model), spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (Brainard mosaic review; Fig.~\ref{fig:croppedImageWithMosaic}).
+The cone mosaic contained  L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard (REF).
+Cone isomerizations were computed assuming an integration time of 5 msec, and we modeled the Poisson nature of photopigment isomerization (REF Hecht et al).
+This modeling was implemented using the software infrastructure provided by ISETBio (REF).
 
@@
 
-The key steps we model are the size of the pupil, optical blurring (including axial chromatic aberration) in the formation of the retinal image, spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones, and the Poisson nature of photopigment isomerization.
-We use the multispectral cropped image (Fig.~\ref{fig:croppedImage}) as the optical stimulus to simulate the response of the cones in the retina.
-The cropped image patch is assumed to cover a $1^{\circ}$ field of view at a distance of 1 m.
-The retinal cone mosaic is modeled as a square grid with $51 \times 51$ cones in the.
-The response of the cones are taken as the number of isomerizations in the cone segment ({\it over what time ??}).
-
 % NEED TO WRITE IN THE KEY PARAMETERS USED.
@@
 ALSO INTEGRATION TIME.
+
 The cone response functions are normalized by the total area under the response curves to model the amplification of the S cone response downstream and thus have comparable number if isomerizations in L, M and S cones.
@@
 
-\subsubsection*{Linear Regression} For linear regression, we solve the equation $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
-Here, $C_{3\times N}$ is a matrix containing either the L, M and S cone responses (for Condition 1 and 2) or contrast normalized responses (for Condition 3 and 4) of the central patch of each image, extracted from $C_{7803\times N}$.
-The columns corresponds to the N images in the dataset.
-The rows correspond to the contrast normalized L, M and S cones responses averaged over a 3$\times$3 pixel central region of the image containing the target object.
-The (unknown) regression parameters $A$ are obtained using Matlab linear regression function.
-This model provides a baseline performance measure, which does not take the context in which the target image is seen into account.
+\subsubsection*{Linear Regression} Linear regression gives us a baseline estimate of the performance.
+We use this method to estimate the target object LRV using cone responses corresponding to the central pixel of the cropped image.
+Thus, getting an estimate for a condition that does not take into account the context in the scene.
+
+For for linear regression, we solve the set of linear equations given by $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
+Here, $C_{3\times N}$ is a matrix containing the average L, M and S stimulus of a central  3$\times$3 pixel patch of the image.
+We use Matlab to obtain the (unknown) regression parameters $A$.
 
@@
 
-{\bf Estimating labels:}
-
-Once these filters have been learned, a suitable decoding method (in this case a Bayesian decoding scheme) is used to estimate the label on a test set.
-
-The image labels are estimated using the Bayesian decoder as described above.
-First, we use the AMA optimal filters and the training dataset to find the conditional distribution of the AMA filter response $p({\textbf {\textit R} }|Y_i)$.
-We then approximate this distribution with multivariate normal distribution $p({\textbf {\textit R} }|Y_i) = \mathcal{N}\left(\mu(Y_i),\Sigma(Y_i) \right)$.
-To estimate the label of an image from the test set, we use Byes' rule to obtain the posterior distribution $p(Y_i|{\textbf {\textit R} })$.
-The estimated value is the one that optimizes the cost function.
-
 \subsection{Error estimation}
@@
 \section{Results} \label{Results}
-In this section, we discuss the results of supervised learning to estimate the luminance of the target object on the the various conditions we described previously.
+In this section, we discuss the results of supervised learning to estimate the luminance of the target object on the conditions we described previously.
 We describe the computations that need to be performed on the cone photoreceptor responses to estimate the luminance.

### 2018-04-03 Draft3/draft3.tex
Today’s editing

@@
 \end{figure}
+% Axis labels: Normalized Irradiance, Wavelength (nm), CIE x chromaticity, CIE y chromaticity.  In caption, make sure a, b, c are right.  Add titles on a, b: Granada Data, Statistical Model
 
@@
 
+% Fix case in headers to sentence style, here and elsewhere
 \subsubsection{Surface Reflectance Spectra}
@@
 \end{figure}
+% Axis labels etc as with illumination
 
@@
 \end{figure}
+% Y axis label LRV.  x axis, maybe "Example Number"  Expand caption.
 
@@
 This modeling was implemented using the software infrastructure provided by ISETBio (REF).
+% Add in Nicolas REFS on some details.
 
@@
 we processed the isomerizations as follows:
-First, we generated a response for each cone class at the each pixel in the sampled retinal image, using bilinear interpolation separately for each cone class.
-This step does not add information.
+First, we generated a response for each cone class at each pixel in the sampled retinal image, using bilinear interpolation separately for each cone class.
+This gives us a cone response image for each cone class.
+We also normalized each cone response image by the total area under the corresponding cone spectral sensitivity.
+This makes the magnitude of the cone response images similar across cone classes.
+These two processing steps do not alter the information in the cone response images. 
 % DOUBLE CHECK THAT THIS WAS DONE WITH SOMETHING LIKE INTERP2 WITH THE LINEAR OPTION.
-This gives us a cone response image for each cone class.
-We then convert each cone image to a contrast representation by subtracting and dividing by the mean.
-Finally  followed by normalizing the vector to have unit length (contrast normalization).
 
-The three $51 \times 51$ sets of cone responses corresponding to the L, M and S cones were then reshaped into a single $7803 \times 1$ vector ($7803 = 51 \times 51 \times 3$).
-For Condition 1 and 3 we used this as the input for the supervised methods.
-For Condition 3 and 4,
-The cone-response vectors corresponding to the N images for each condition are concatenated column-wise to form a contrast normalized matrix $C_{7803\times N}$.
-The corresponding labels are represented by the row vector $Y_{1\times N}$.
+To model contrast coding, we converted each cone response image to a corresponding cone contrast image.
+This was accomplished by computing the mean response over the three cone contrast images, and then subtracting off and dividing by this mean.
+To model contrast normalization, we divided by the sum of squared contrasts over image pixels and cone classes.
 
@@
 
-The cone response functions are normalized by the total area under the response curves to model the amplification of the S cone response downstream and thus have comparable number if isomerizations in L, M and S cones.
 % NEED TO UNDERSTAND THIS.  WHEN WAS THE GAIN, BEFORE OR AFTER NOISE ADDED, AND LET'S REMEMBER WHY WE DID IT.  
@@
 
-\subsection{Supervised Learning methods} \label{method:SupervisedLearning}
-We have used two supervised learning methods in our work: Linear regression and Accuracy maximization analysis.
-While, our main focus is on AMA, linear regression provides a baseline performance measure.
+\subsection{Computational luminance constancy} \label{method:SupervisedLearning}
+We used our datasets to determine how well target object LRV can be estimated from cone responses and from normalized cone contrasts.
+Studying both representations allows us to understand how early contrast coding and normalization affect how well luminance constancy can be achieved.
+We applied accuracy maximization analysis (AMA) to learn the optimal receptive fields for estimating LRV,
+and evaluated the performance obtained when the output of these filters was optimally decoded.
 
-\subsubsection*{Linear Regression} Linear regression gives us a baseline estimate of the performance.
-We use this method to estimate the target object LRV using cone responses corresponding to the central pixel of the cropped image.
-Thus, getting an estimate for a condition that does not take into account the context in the scene.
+\subsubsection*{Learning optimal filters}
 
-For for linear regression, we solve the set of linear equations given by $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
-Here, $C_{3\times N}$ is a matrix containing the average L, M and S stimulus of a central  3$\times$3 pixel patch of the image.
-We use Matlab to obtain the (unknown) regression parameters $A$.
-
-\subsubsection*{Accuracy maximization analysis}
-We perform two steps to decode the luminance of the target object from the cone isomerization.
-First, we use AMA to learn the linear filters that are optimal for estimating the target LRV.
-Second, we determine how to optimally decode the luminance from the response of these filters to arbitrary stimuli.
-
-{\bf Learning optimal filters using AMA:} AMA \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
+AMA \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
 is a task specific Bayesian method for dimensionality reduction.
-When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns the linear receptive fields (in rank order) that are optimal for performing a task.
-The optimal receptive fields that are returned by AMA are those whose responses to the stimuli minimizes the cost function over the training set when optimally decoded.
+When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of linear receptive fields.
+These receptive fields have the property that the  expected estimation cost is minimized when their responses are optimally decoded.
 
@@
 
-{\bf Estimating luminance:} 
+\subsubsection*{Decoding optimal filters}
+
 Once the optimal receptive fields have been learned, a general decoder must be used to estimate the luminance.
@@
 
-\subsection{Error estimation}
+\subsubsection*{Baseline performance measure}
+
+We used linear regression to provide a baseline performance measure.
+
+Linear regression gives us a baseline estimate of the performance.
+We use this method to estimate the target object LRV using cone responses corresponding to the central pixel of the cropped image.
+Thus, getting an estimate for a condition that does not take into account the context in the scene.
+
+For for linear regression, we solve the set of linear equations given by $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
+Here, $C_{3\times N}$ is a matrix containing the average L, M and S stimulus of a central  3$\times$3 pixel patch of the image.
+We use Matlab to obtain the (unknown) regression parameters $A$.
+
+\subsection{Performance metric}
 If $\hat{Y}$ is the estimated luminance corresponding to the assigned luminance $Y$, the error of the luminance estimates is quantified as the relative error ($E_{\rm rel}$) defined as: $E_{\rm rel}^2 = \left\langle\left((\hat{Y}-Y)/Y\right)^2\right\rangle$.

### 2018-04-03 Draft3/draft3.tex
MORE EDITS

@@
 % REMOVE PANELS A AND D AND FIX CAPTION AND REFERENCES TO THIS FIGURE.
-\subsubsection{Illumination Spectra}
+\subsubsection{Illumination spectra}
 % Figure 6
@@
         \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_a.pdf}
-        \label{fig:illuminantSpectra}
+        \label{fig:granadaData}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_b.pdf}
+        \label{fig:illuminantSamples}
+    \end{subfigure}
+      	\begin{subfigure}[b]{0.24 \textwidth}
+    \centering
+        \caption{}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
         \label{fig:xyDiagram}
@@
         \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
+        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
         \label{fig:sRGBIlluminant}
     \end{subfigure}
-      	\begin{subfigure}[b]{0.24 \textwidth}
-    \centering
-        \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
-        \label{fig:sRGBIlluminantScaled}
-    \end{subfigure}
-    \caption{{\bf Illumination spectra:} (a) Normalized Granada dataset (red, 2600 samples of Granada dataset) and 100 randomly generated samples using the rescaled spectra (black).
-(b) CIE xy chromaticity diagram of the normalized dataset and the random samples.
-(c) sRGB renditions of 100 random samples before scaling.
-(d) sRGB renditions of the samples after scaling.}
+    \caption{{\bf Illumination spectra:} (a) Granada dataset.
+The spectra are normalized by the mean over wavelength.
+(b) A representative sample of spectra generated using normalized Granada dataset.
+(c) CIE xy chromaticity diagram of the normalized dataset and the random samples.
+(d) sRGB renditions of the samples from Figure~\ref{fig:illuminantSamples}.}
 \label{fig:illuminant}
 \end{figure}
-% Axis labels: Normalized Irradiance, Wavelength (nm), CIE x chromaticity, CIE y chromaticity.  In caption, make sure a, b, c are right.  Add titles on a, b: Granada Data, Statistical Model
 
@@
 The overall intensity of the measurements spans approximately three orders of magnitude.
-Figure~\ref{fig:illuminantSpectra} plots the measurements in normalized form to make apparent the variation in the relative spectra. The spectra are normalized by their mean over wavelength.
+Figure~\ref{fig:granadaData} plots the measurements in normalized form to make apparent the variation in the relative spectra. The spectra are normalized by their mean over wavelength.
 
@@
 To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
-Figure~\ref{fig:illuminantSpectra} also illustrates the relative spectra of draws obtained using this procedure.
+Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
 Details of the statistical model for illumination are provided in the appendix.
@@
 We obtained each scale factor by randomly sampling (with replacement) a spectrum from the Granda dataset and taking its mean. 
-Color swatches of samples of illuminant spectra are shown in Figure~\ref{fig:illuminant}.
+Color swatches of samples of illuminant spectra are shown in Figure~\ref{fig:sRGBIlluminant}.
 
 % Fix case in headers to sentence style, here and elsewhere
-\subsubsection{Surface Reflectance Spectra}
+\subsubsection{Surface reflectance spectra}
 % Figure 7
@@
 (c) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (black) and samples of surface reflectances (red).
-(d) sRGB renditions of the samples of object surface reflectance.}
+(d) sRGB renditions of the samples of object surface reflectance under CIE D65 daylight.}
 \label{fig:surfaceReflectanceGeneration}
 \end{figure}
-% Axis labels etc as with illumination
 
@@
 \includegraphics[width=0.3\textwidth]{../Figures/Figure7/Figure8.pdf}
-\caption{{\bf Target surface reflectance spectra:} sRGB renditions of the target object surface reflectance.
+\caption{{\bf Target surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
 The figure shows 10 random samples at 10 equally spaced LRV levels in the range [0.2, 0.6].
-This range captures more than 90\% of the natural surface reflectances.}
+This range captures more than 90\% of the natural surface reflectances.
+Each row contains 10 random samples of reflectance spectra generated at the LRV shown on the left.}
 \label{fig:targetSwatches}
 \end{figure}
-% Y axis label LRV.  x axis, maybe "Example Number"  Expand caption.
 
@@
 
-\subsection{Model of Early Visual System} \label{method:Isetbio}
+\subsection{Model of early visual system} \label{method:Isetbio}
 
@@
 This modeling was implemented using the software infrastructure provided by ISETBio (REF).
-% Add in Nicolas REFS on some details.
+
+% Details from Nicolas (TEXT IN CAPS IS FROM VIJAY)
+% Scene: 
+%- the default mean luminance was set to 200, but there is a key-value param that could have overriden this value. 
+%  I do not know if this were the case.
+%
+% % MEAN LUMINANCE = 0, NO SCALING
+
+%- The default FOV was 1 deg, but there is a key-value param that could have overriden this value.
+%  I do not know if this were the case.
+%
+% % HORIZONTAL FOV = 1
+
+%- Distance default is 1 meter, but there is  a key-value param that could have overriden this value.
+%  I do not know if this were the case.
+%
+%% DISTANCE 1M
+
+%
+%Optics: 
+%- 3 mm pupil, 17 mm focal length, with a spectro-spatial OTF described in  
+%  (Marimont & Wandell (1994) J. Opt. Soc. Amer. A,  v. 11, p. 3113-3122), 
+%   which includes axial chromatic aberration. However, there is key-value param o skip the OTF. 
+%   Not sure if this was used.  It it was used, the optics was set to diffraction limited.
+%
+% % SKIP OTF OFF:  'skipOTF', false ...
+
+%
+%Lens: 
+%- not sure if the optical density is from Wyszecki&Stiles or from Stockman-Sharpe. 
+%  The isetbio file commend only says it is from PTB. David do you know, or should I check
+%  the data?
+%
+%Cone Mosaic: 
+%- rectangular cone mosaic with 0.6:0.3:0.1 LMS densities
+%- FOV was a key-value param, so I do not know what was used.
+%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
+%but there is a key-value param that could have overriden this value. I do not know what that parameter value was.
+%
+% CONE STRIDE = 3 'coneStride', 3, ...
+
+%
+%- There is a key-value pair to also low-pass the optical image with default value to not do so.
+%  If that was user-overriden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
+%
+% LOW PASS FILTER = MATCH CONE STRIDE : lowPassFilter = 'matchConeStride';
+
+%- IntegrationTime was not specified, so it was the default which is 5 msec.
+%  The cone isomerization maps were also demosaiced using linear interpolation.
+%- The default isomerization noise was set to none, but there is a key-value parameter
+%  that can override it. I do not know what the value of that was.
+%
+% ISOMERIZATION NOISE = FROZEN, 'isomerizationNoise', 'frozen'
+
+%-  Finally, there is a key-value param named 'coneEfficiencyBasedReponseScaling', which by default is set to 'none'
+%   But if it was user-set to non 'none' the code scaled the responses to simulate equal quantal efficiencies 
+%   for L , M and S coneEfficiencyBasedReponseScaling by undoing filtering by the lens and the macular pigment.
+%   I do not know if this was used.
+% 
+% coneEfficiencyBasedReponseScaling = 'area'
 
@@
 These two processing steps do not alter the information in the cone response images.
-% DOUBLE CHECK THAT THIS WAS DONE WITH SOMETHING LIKE INTERP2 WITH THE LINEAR OPTION.
 

### 2018-04-04 Draft3/draft3.tex
Today’s editing

@@
 
-AMA \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
+AMA 
 is a task specific Bayesian method for dimensionality reduction.
 When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of linear receptive fields.
-These receptive fields have the property that the  expected estimation cost is minimized when their responses are optimally decoded.
+Given a set of linear receptive fields and an explicit cost function, it is possible to determine the minimum-expected-cost estimator that maps responses to stimulus labels given the training set and the
+assumption that all images in the training set are equally likely.
+Moreover, the corresponding expected estimation cost may be explicitly computed.
+AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
+Here we used squared error as the cost function and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e. Poisson-like noise with a fano factor of 1.3).
+Details of how AMA learns filters and the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
 
-More concretely, let us assume that there are $N_{\nu}$ possible values of the target LRV levels ($\{Y_k: k\in[1,N_{\nu}] \}$) and the $l$'th image corresponding to the $k$'th luminance level is represented as $s_{kl}$.
+% VIJAY make this work
+%Let a set of linear receptive fields be represented by the matrix $\textbf{f} = [\textbf{f_1} \hdots \textbf{f_N}]$, where each $\textbf{f_q}$ is a column vector providing the weights defining a single filter's receptive field.
+%Once we have a set of receptive fields and a labelled training set, we can find the decoder that minimizes the expected estimation cost on the assumption that all images in the training set are equally likely to occur.
+%
+%The learning goal is to find a set of receptive fields ${\textbf{f}}^{\rm opt}$ that have the following property.
+%Represent a set of linear receptive fields by a matrix 
+%Assume that there are $n_{\nu}$ possible values of the target LRV levels ($\{y_k: k\in[1,n_{\nu}] \}$) and the $l$'th image corresponding to the $k$'th luminance level is represented as $s_{kl}$.
 Also, assume that there is a set of linear receptive fields {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
-Also assume there is a decoder $g$, with the knowledge of the response model and of every stimulus in the training set, that returns the Bayes' optimal estimate of the luminance level ($\hat{Y}_k$) of the target object in each stimulus $s_{kl}$.
+Also assume there is a decoder $g$, with the knowledge of the response model and of every stimulus in the training set, that returns the Bayes' optimal estimate of the luminance level ($\hat{y}_k$) of the target object in each stimulus $s_{kl}$.
 The crux computation for obtaining this estimate is the computation of the posterior probability of the luminance given an observed response, $P(Y|\textbf{R}_{kl})$ \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
-.
-With this luminance estimate, we calculate the cost given the cost function $\mathcal{C}_{kl} = \gamma(Y_{kl},\hat{Y}_{kl})$.
-Finally, AMA searches for the set of optimal receptive fields ${\textbf{\textit f}}^{\rm opt}$ that minimize the cost over the entire training set $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$ where $N_{k}$ is the number of stimuli corresponding to the label $Y_k$.
+%.
+With this luminance estimate, we calculate the cost given the cost function $\mathcal{C}_{kl} = \gamma(y_{kl},\hat{y}_{kl})$.
+Finally, AMA searches for the set of optimal receptive fields ${\textbf{\textit f}}^{\rm opt}$ that minimize the cost over the entire training set $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$ where $N_{k}$ is the number of stimuli corresponding to the label $y_k$.
 Thus,
-\begin{align}
-{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{k=1}^{N_{\nu}}  \sum_{l=1}^{N_k} {\mathcal{C}}_{kl}.
-\label{eq:fopt}
-\end{align}
+%\begin{align}
+%{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{k=1}^{N_{\nu}}  \sum_{l=1}^{N_k} {\mathcal{C}}_{kl}.
+%\label{eq:fopt}
+%\end{align}
 

### 2018-04-06 Draft3/draft3.tex
Today’s work

@@
 
-Once the optimal receptive fields have been learned, a general decoder must be used to estimate the luminance.
-Recall that the decoder used to learn the receptive fields required the knowledge of every stimulus in the training set.
-To obtain the general decoder, first we use the AMA optimal receptive fields and the training dataset to find the conditional distributions of the AMA receptive field responses $P({\textbf {\textit R} }|Y_i)$.
-Then, we approximate these with multivariate Gaussian distributions $P({\textbf {\textit R} }|Y_i) = \mathcal{N}\left(\mu(Y_i),\Sigma(Y_i) \right)$.
-To estimate the luminance of the target object in the test stimulus, we use Bayes' rule to obtain the posterior distribution $P(Y|{\textbf {\textit R} })$.
-The optimal estimate is the luminance value that minimizes the cost function.
-
-\subsubsection*{Baseline performance measure}
-
-We used linear regression to provide a baseline performance measure.
-
-Linear regression gives us a baseline estimate of the performance.
-We use this method to estimate the target object LRV using cone responses corresponding to the central pixel of the cropped image.
-Thus, getting an estimate for a condition that does not take into account the context in the scene.
-
-For for linear regression, we solve the set of linear equations given by $A_{1\times3}*C_{3\times N} = Y_{1\times N}$ for the regression parameters $A_{1\times3}$.
-Here, $C_{3\times N}$ is a matrix containing the average L, M and S stimulus of a central  3$\times$3 pixel patch of the image.
-We use Matlab to obtain the (unknown) regression parameters $A$.
-
-\subsection{Performance metric}
-If $\hat{Y}$ is the estimated luminance corresponding to the assigned luminance $Y$, the error of the luminance estimates is quantified as the relative error ($E_{\rm rel}$) defined as: $E_{\rm rel}^2 = \left\langle\left((\hat{Y}-Y)/Y\right)^2\right\rangle$.
+Once the optimal receptive fields have been learned, we need to develop a general decoder that can be applied to arbitrary test stimuli.
+A general decoder is necessary because the decoder used to learn the receptive fields requires the response mean and response variance of the filters to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
+To proceed, first we use the AMA optimal receptive fields and the training dataset to find the conditional distributions of the receptive field responses, conditioned on the labelled target object LRVs.
+Then, we approximate these with multivariate Gaussian distributions.
+With the Gaussian approximation in hand, 
+to estimate the LRV of the target object in a test image, we use Bayes' rule to obtain the posterior distribution over LRV values given the filter responses.
+The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
+
+\subsubsection*{Baseline methods}
+
+To provide baselines for evaluation of the estimation method described above, we used linear regression.
+First, we solved for the weights on the average L, M and S cone responses target object that best predicted the target LRV values.
+We took the average cone respones from a $3 \times 3$ region at the center of the target object.
+This baseline method disregards information carried the image regions corresponding to the background objects.
+We also performed regression on the contrast normalized version of the cone responses.
+This baseline method indirectly incorporates information carried the image regions corresponding to the background objects,
+through their effect on the contrast normalized responses from the target object. 
+We also evaluated the performance of a naive model that estimate the mean of the LRV values in the training set, irrespective
+of the image data.
+
+%\subsection{Performance evaluation}
+%
+%To evaluate the performance of our luminance constancy methods, we generated test sets as new random draws from our statistical models.
+%For each test image, we quant we summarized performance as the relative mean squared estimation error.
+%If $\hat{Y}$ is the estimated luminance corresponding to the assigned luminance $Y$, the error of the luminance estimates is quantified as the relative error ($E_{\rm rel}$) defined as: $E_{\rm rel}^2 = \left\langle\left((\hat{Y}-Y)/Y\right)^2\right\rangle$.
 
@@
 \section{Results} \label{Results}
-In this section, we discuss the results of supervised learning to estimate the luminance of the target object on the conditions we described previously.
-We describe the computations that need to be performed on the cone photoreceptor responses to estimate the luminance.
-We start with condition 1, where only the reflectance spectrum of the target object is allowed to vary, and show that in this condition the luminance can be estimated directly from the photoreceptor response.
+
+%We start with Condition 1, where only the reflectance spectrum of the target object is allowed to vary, and show that in this condition the luminance can be estimated directly from the photoreceptor response.
 We then progressively increase the complexity of the spectral conditions and explain the correspondingly complex computations that are required to estimate the target LRV.
@@
 Hence, one requires only one set of optimal receptive fields for estimating the target luminance, not separate receptive fields for each spectral condition.
+
+We first learned filters for Condition 0, where the only scene variation was in the target object LRV.  Performance in this condition is limited by response noise.
+
+Figure ~\ref{fig:case1RFResponse} (ADD A)
 

### 2018-04-13 Draft3/draft3.tex
Today’s figures

@@
 
-%We start with Condition 1, where only the reflectance spectrum of the target object is allowed to vary, and show that in this condition the luminance can be estimated directly from the photoreceptor response.
+We start with Condition 1, where only the LRV and relative reflectance spectrum of the target object vary across scenes.
+For this condition, estimating LRV should be easy because the variation in target object reflectance that we introduced
+preserved LRV (which is calculated using a CIE D65 as the illumination.
+This in turn means that for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will
+vary minimally.
+In Condition 1, we used an illumination draw form our daylight sample and thus expect a reasonable degree of similarity to D65.
+
+We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
+For this condition, we trained and evaluated AMA on the cone responses to the image patches.
+Fig.~\ref{fig:case1RFResponse} shows the responses of the first two receptive fields to all the image patches in the training set.
+Each individual point represents the receptive field responses to a single image patch.
+Each point is color coded according to the LRV corresponding to the target object in the patch.
+The responses segregate according to the target LRV.
+This means that the responses may be used to accurately decode LRV, confirming the intuition that computational
+luminance constancy is readily achieved for Condition 1.
+
+Decoding performance for the test set is shown in Figure (WHATSI).
+As expected, the LRV estimates obtained by decoding the AMA receptive field responses are veridical.
+Figure (WHATSI) also shows the performance of the baseline linear regression method, again trained
+on the training set and evaluated on the test set.
+For this condition, linear regression on the target object cone responses also leads to veridical LRV estimates.
+
+%ont along the first two optimal AMA receptive fields. 
+%Clearly, there exists a subspace along which the photoreceptor response separates according to the luminance level assigned to the target object. 
+%Thus, the target LRV can be obtained by projecting the photoreceptor response along these AMA receptive fields. 
+%We used such projections and a generalized Bayes' decoder (see methods) to estimate the luminance of the target objects in the test set stimuli. 
+% shows the estimated luminance v/s the actual luminance assigned to the target object for the test stimuli in condition 1. 
+%We show the estimates obtained by AMA and two null models: a naive method that assigns the average target LRV across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object (see Methods).
+%As expected, in the absence of any external source of variation, the photoreceptor response is proportional to the luminance of the target object, and hence can be easily estimated by both AMA and linear regression.
+%Figure (WHATSI)  and it provides a use and thus it illustrates how AMA op
+%
+% because (as we will see below) the only source of variation other
+%than the LRV does not have a large effect on cone responses to the target object.  there is just one source of variation.
+%
+%This is an instructive case to begin with, because it allows us to illustrate the action of AMA
+
+%, and show that in this condition the luminance can be estimated directly from the photoreceptor response.
 We then progressively increase the complexity of the spectral conditions and explain the correspondingly complex computations that are required to estimate the target LRV.
@@
 Hence, one requires only one set of optimal receptive fields for estimating the target luminance, not separate receptive fields for each spectral condition.
-
-We first learned filters for Condition 0, where the only scene variation was in the target object LRV.  Performance in this condition is limited by response noise.
-
-Figure ~\ref{fig:case1RFResponse} (ADD A)
+%
+%We first learned filters for Condition 0, where the only scene variation was in the target object LRV.  Performance in this condition is limited by response noise.
+
+%Figure ~\ref{fig:case1RFResponse} (ADD A)
 
@@
 We start with the results of the simplest type of spectral variation where only the target object relative surface reflectance spectrum is allowed to change.
+
 We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV from the model cone photoreceptor response to the images from this condition.

### 2018-04-15 Draft4/draft4.tex
draft 4, removed commented text
small edits

--- 2018-04-06 Draft3/draft3.tex
@@
 
-% I found the definition of light reflectance value on the web, sort of.  Need to find the right citable reference and or a term for the same thing that
-% we can find a reference for.
 We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of an object's surface reflectance function.
@@
 LRVs are typically expressed in percent, so that they range from 0 to 100.
-
-% MOVE THIS TO DISCUSSION
-%This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
-Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the Discussion.
-% \cite{baker2011database}  \cite{kovacs17shading} \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}
-% Autonmous vehicle work - ask BAW
-
-% NOT SURE WE NEED ANY OF THIS.  PROBABLY NOT HERE IF WE DO
-%Even within the special case of luminance constancy, there are many scene manipulations that could be considered.
-The set of manipulations we focus on here are illustrated by Fig.~\ref{fig:introExampleFigure} and the three panels of Fig.~\ref{fig:studiedCases}.
-These conditions are: 1.
-variation in target object spectrum with fixed light source and background objects spectra (Fig.~\ref{fig:introExampleFigure}), 2.
-variation in target object spectrum and background objects spectra, with fixed light source  (Fig.~\ref{fig:backgroundVarying}), 3.
-variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.~\ref{fig:targetIlluminantVarying}), and 3.
-variations in all three types of spectra (target object, light source, and background objects) (Fig.~\ref{fig:allSpectraVarying}).
-Across real scenes, there will also be variations in the shape of the target object, its pose, eye position, etc.
-(see \nameref{Methods}).
-In this paper, we focus on the problem of luminance constancy within scene ensembles where these geometric factors are held fixed.
-%
-%We show that for conditions that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (Condition 1) or just the target and background objects reflectance spectra (Condition 2), LRV can be recovered directly from the light reflected off the target object.
-For Condition 3, where both the target object reflectance and light source spectra vary, LRV can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (Condition 4), the standard luminance can not be recovered simply from the cone response or the contrast.
-We have used AMA with a Bayesian estimator to estimate standard luminance of the target object.
-Using this method, we can recover the luminance of the target object with $\sim 15\%$ relative root mean square error.
-Our analysis shows that the optimal receptive fields for estimating the luminance of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, luminance estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
-Comparing the performance of the RFs learnt using  one condition on the cone response of other conditions shows that the receptive field of the complex conditions perform well on images of simpler conditions.
-We discuss the implications of such receptive fields on luminance constancy.
 
@@
 
-%Once a base scene has been chosen and objects and light sources inserted, we assign spectral surface reflectance, texture, and material property to each object surface in the scene.
-We also assign an illuminant spectral power distribution to each light source in the scene.
-Objects in the VWCC library may contain more than one distinct surface, each of which may be assigned a different surface reflectance.
-As with object position, these may be specified programatically.
-In the present work, we use simple choices for texture (all surfaces spatially uniform) and material property (all surfaces matte) and focus on variation in surface spectral reflectance.
-
-% REMOVE PANELS A AND D AND FIX CAPTION AND REFERENCES TO THIS FIGURE.
 \subsubsection{Illumination spectra}
@@
 
-% Fix case in headers to sentence style, here and elsewhere
 \subsubsection{Surface reflectance spectra}
@@
 
-% MAKE TARGET SWATCHES ITS OWN FIGURE.
 For generating the target object reflectance at a particular luminance $(Y_{\rm T})$, the values in a generated spectrum were 
@@
 
-%The sampling and rendering steps described above allow us to generate images from scenes that contain an image of a target object of known surface luminance at the center pixel, and where the illuminant spectra and spectra of the other surfaces in the scene are drawn randomly from models of naturally occurring spectra.
-One such image is shown in Fig.~\ref{fig:3DScene}, where the green sphere in the middle is the target object and the light sources are not within the camera field of view.
-We model the encoding of such images by the early visual system, to generate {\em neural images} that provide an abstracted representation of the information available to the brain for producing perceptual representations of the external world.
-For each image, it is this information together with the known surface luminance of the corresponding target object that we will provide to our supervised learning algorithms.
-Our training datasets correspond to ...
-% SAY WHAT WE DID ONCE WE FINISH EVERYTHING OFF.
-
-% NEED TO WRITE IN THE KEY PARAMETERS USED.
-PROBABLY MARIMONT AND WANDELL OPTICS, STOCKMAN-SHARPE LMS CONE SPECTRAL SENSITIVITIES, THE L, M, S CONE RATIO IN THE MOSAIC, RECTANGULAR AND REGULAR CONE PACKING, SOME IMPLIED SPATIAL SCALE, AND SOME OVERALL SCALING THAT DRIVES THE MEAN LUMINANCE OF THE RETINAL IMAGES AND THUS THE AMOUNT OF POISSON NOISE.
-ALSO INTEGRATION TIME.
-
-% NEED TO UNDERSTAND THIS.  WHEN WAS THE GAIN, BEFORE OR AFTER NOISE ADDED, AND LET'S REMEMBER WHY WE DID IT.  
-% First we add noise, then we do the scaling.
-The reason this was done is to make sure that in the normalization process each of the cone class have the same contribution.
-Otherwise, the S cone contribution would be very low.
-
 \subsection{Computational luminance constancy} \label{method:SupervisedLearning}
@@
 Details of how AMA learns filters and the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
-
-% VIJAY make this work
-%Let a set of linear receptive fields be represented by the matrix $\textbf{f} = [\textbf{f_1} \hdots \textbf{f_N}]$, where each $\textbf{f_q}$ is a column vector providing the weights defining a single filter's receptive field.
-%Once we have a set of receptive fields and a labelled training set, we can find the decoder that minimizes the expected estimation cost on the assumption that all images in the training set are equally likely to occur.
-%
-%The learning goal is to find a set of receptive fields ${\textbf{f}}^{\rm opt}$ that have the following property.
-%Represent a set of linear receptive fields by a matrix 
-%Assume that there are $n_{\nu}$ possible values of the target LRV levels ($\{y_k: k\in[1,n_{\nu}] \}$) and the $l$'th image corresponding to the $k$'th luminance level is represented as $s_{kl}$.
-Also, assume that there is a set of linear receptive fields {\textbf{\textit f}} which when acting on $s_{kl}$ gives the response ${\textbf{\textit R}}_{kl}$.
-Also assume there is a decoder $g$, with the knowledge of the response model and of every stimulus in the training set, that returns the Bayes' optimal estimate of the luminance level ($\hat{y}_k$) of the target object in each stimulus $s_{kl}$.
-The crux computation for obtaining this estimate is the computation of the posterior probability of the luminance given an observed response, $P(Y|\textbf{R}_{kl})$ \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}
-%.
-With this luminance estimate, we calculate the cost given the cost function $\mathcal{C}_{kl} = \gamma(y_{kl},\hat{y}_{kl})$.
-Finally, AMA searches for the set of optimal receptive fields ${\textbf{\textit f}}^{\rm opt}$ that minimize the cost over the entire training set $\{s_{kl}: k\in[1,N_{\nu}], l\in[1,N_k]\}$ where $N_{k}$ is the number of stimuli corresponding to the label $y_k$.
-Thus,
-%\begin{align}
-%{\textbf {\textit f} }^{\rm opt} = \argmin_{\textbf {\textit f} } \sum_{k=1}^{N_{\nu}}  \sum_{l=1}^{N_k} {\mathcal{C}}_{kl}.
-%\label{eq:fopt}
-%\end{align}
 
@@
 
-% THINGS TO THINK ABOUT:
-%  1) Putting error bars on performance.  Particularly want to be sure that Fig 13 feature that Condition 3 RFs do better than Condition 1 RFs for Condition 1 is just statistical sampling.
-
 \section{Results} \label{Results}
 
-%We start with Condition 1, where only the reflectance spectrum of the target object is allowed to vary, and show that in this condition the luminance can be estimated directly from the photoreceptor response.
-We then progressively increase the complexity of the spectral conditions and explain the correspondingly complex computations that are required to estimate the target LRV.
-Next, we show the optimal AMA receptive fields for each one of the spectral conditions discussed in this work.
-We show that the optimal receptive fields for target luminance estimation have a center surround structure and they give more weights to the response of L and M cones than S cones.
-We finally show that, as expected, the receptive fields for the complex spectral conditions generalize to the simple conditions.
-Hence, one requires only one set of optimal receptive fields for estimating the target luminance, not separate receptive fields for each spectral condition.
+We start with Condition 1, where only the LRV and relative reflectance spectrum of the target object vary across scenes.
+For this condition, estimating LRV should be easy because the variation in target object reflectance that we introduced
+preserved LRV (which is calculated using a CIE D65 as the illumination.
+This in turn means that for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will
+vary minimally.
+In Condition 1, we used an illumination draw form our daylight sample and thus expect a reasonable degree of similarity to D65.
 
-We first learned filters for Condition 0, where the only scene variation was in the target object LRV.  Performance in this condition is limited by response noise.
+We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
+For this condition, we trained and evaluated AMA on the cone responses to the image patches.
+Figure~\ref{fig:case1RFResponse} shows the responses of the first two receptive fields to all the image patches in the training set.
+Each individual point represents the receptive field responses to a single image patch.
+Each point is color coded according to the LRV corresponding to the target object in the patch.
+The responses segregate according to the target LRV.
+This means that the responses may be used to accurately decode LRV, confirming the intuition that computational
+luminance constancy is readily achieved for Condition 1.
 
-Figure ~\ref{fig:case1RFResponse} (ADD A)
-
-\subsection{Luminance estimates for each spectral condition}
-\subsubsection{Condition 1: Target object relative surface reflectance spectrum variable, light source and background object spectra fixed}
-We start with the results of the simplest type of spectral variation where only the target object relative surface reflectance spectrum is allowed to change. 
-We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV from the model cone photoreceptor response to the images from this condition.
-Fig.~\ref{fig:case1RFResponse} shows the projection of the photoreceptor response along the first two optimal AMA receptive fields. 
-Clearly, there exists a subspace along which the photoreceptor response separates according to the luminance level assigned to the target object. 
-Thus, the target LRV can be obtained by projecting the photoreceptor response along these AMA receptive fields. 
-We used such projections and a generalized Bayes' decoder (see methods) to estimate the luminance of the target objects in the test set stimuli. 
-Fig.~\ref{fig:case9Results} shows the estimated luminance v/s the actual luminance assigned to the target object for the test stimuli in condition 1. 
-We show the estimates obtained by AMA and two null models: a naive method that assigns the average target LRV across the training set to all images, and a linear model based on the photoreceptors corresponding to the center pixel on the target object (see Methods).
-As expected, in the absence of any external source of variation, the photoreceptor response is proportional to the luminance of the target object, and hence can be easily estimated by both AMA and linear regression.
-
-Each cloud in Fig.~\ref{fig:case1RFResponse} corresponds to the photoreceptor response to the images with target luminance level at a fixed value. 
-The variation within the cloud, between images that have the target object at same luminance values, is due to the difference in the relative shape of the target object reflectance spectra (difference in hue and saturation).
-The resulting variation dominates any variation coming from the noise in photoreceptor response or the noisy rendering of the images by the software.
-Fig.~\ref{fig:case0RFResponse} shows the projection of photoreceptor response corresponding to 1000 images where, in addition to the illumination and background spectra, we also fixed the relative shape of the target object surface reflectance.
-The variation resulting from the poisson nature of the photoreceptor response or due the image rendering software is small and can be ignored.
+Decoding performance for the test set is shown in Figure~\ref{fig:case1Results}.
+As expected, the LRV estimates obtained by decoding the AMA receptive field responses are veridical.
+Figure~\ref{fig:case1Results} also shows the performance of the baseline linear regression method, again trained
+on the training set and evaluated on the test set.
+For this condition, linear regression on the target object cone responses also leads to veridical LRV estimates.
 
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{RF response condition 0}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_c.pdf}
-        \label{fig:case0RFResponse}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.3 \textwidth}
         \caption{RF response condition 1}
@@
     \end{subfigure}    
-%    \begin{subfigure}[b]{0.33 \textwidth}   
- %       \includegraphics[width=\textwidth]{../Figures/resultsFigure/renderingNoise.pdf}
-%        \caption{Rendering noise}
-%        \label{fig:renderingNoise}
-%    \end{subfigure}
-            \begin{subfigure}[b]{0.297 \textwidth}
+            \begin{subfigure}[b]{0.3 \textwidth}
         \caption{Luminance Estimates}
         \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
-        \label{fig:case9Results}
+        \label{fig:case1Results}
     \end{subfigure}    
-    \caption{{\bf RF response and luminance estimates for condition 0 (baseline) and condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 0.
+    \caption{{\bf RF response and luminance estimates for condition 0 (baseline) and condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
 We show the response for the images in the training set.
@@
 The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(b) Photoreceptor response for images of condition 1.
-(c) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA.
+(b) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA.
 The estimates fall along the diagonal unit slope (blue dotted) line for both linear regression and AMA.
-The standard deviations are too small to be visible.}
-\label{fig:sourcesOfNoise}
+The standard deviations are too small to be visible.
+The relative error of estimation is XX (AMA) and YY(Linear regression).}
+\label{fig:Condition1}
 \end{figure}
@@
 
+% MOVE THIS TO DISCUSSION
+%This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
+Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the Discussion.
+% \cite{baker2011database}  \cite{kovacs17shading} \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}
+% Autonmous vehicle work - ask BAW
+
+% NOT SURE WE NEED ANY OF THIS.  PROBABLY NOT HERE IF WE DO
+%Even within the special case of luminance constancy, there are many scene manipulations that could be considered.
+The set of manipulations we focus on here are illustrated by Fig.~\ref{fig:introExampleFigure} and the three panels of Fig.~\ref{fig:studiedCases}.
+These conditions are: 1.
+variation in target object spectrum with fixed light source and background objects spectra (Fig.~\ref{fig:introExampleFigure}), 2.
+variation in target object spectrum and background objects spectra, with fixed light source  (Fig.~\ref{fig:backgroundVarying}), 3.
+variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.~\ref{fig:targetIlluminantVarying}), and 3.
+variations in all three types of spectra (target object, light source, and background objects) (Fig.~\ref{fig:allSpectraVarying}).
+Across real scenes, there will also be variations in the shape of the target object, its pose, eye position, etc.
+(see \nameref{Methods}).
+In this paper, we focus on the problem of luminance constancy within scene ensembles where these geometric factors are held fixed.
+%
+%We show that for conditions that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
+For variations only in target object reflectance spectra (Condition 1) or just the target and background objects reflectance spectra (Condition 2), LRV can be recovered directly from the light reflected off the target object.
+For Condition 3, where both the target object reflectance and light source spectra vary, LRV can be recovered from the contrast between the target and the background.
+When all the spectral features in the scene are allowed to change (Condition 4), the standard luminance can not be recovered simply from the cone response or the contrast.
+We have used AMA with a Bayesian estimator to estimate standard luminance of the target object.
+Using this method, we can recover the luminance of the target object with $\sim 15\%$ relative root mean square error.
+Our analysis shows that the optimal receptive fields for estimating the luminance of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
+Additionally, luminance estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
+Comparing the performance of the RFs learnt using  one condition on the cone response of other conditions shows that the receptive field of the complex conditions perform well on images of simpler conditions.
+We discuss the implications of such receptive fields on luminance constancy.
+
 \bibliography{references}

### 2018-04-16 Draft4/draft4.tex
reorganization

@@
 	\caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_a.png}
         \label{fig:introSchematic}
@@
         \caption{}    
-        \includegraphics[width=\textwidth]{../Figures/Figure1/Figure1_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.png}
         \label{fig:introExampleFigure}
@@
 		\caption{Condition 2}
-		\includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_a.png}
+		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
  		\label{fig:backgroundVarying}
@@
         \caption{Condition 3}	
-        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.png}
         \label{fig:targetIlluminantVarying}
@@
 	\caption{Condition 4}	
-        \includegraphics[width=\textwidth]{../Figures/Figure2/Figure2_c.png}        
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.png}        
         \label{fig:allSpectraVarying}
@@
         \caption{Library }
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_a.png}
         \label{fig:baseSceneLibrary}
@@
         \caption{Mill}    
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_b.png}
         \label{fig:baseSceneMill}
@@
         \caption{Table-Chairs}    
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_c.png}
         \label{fig:baseSceneTableChairs}
@@
         \caption{Indoor-plant}    
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_d.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_d.png}
         \label{fig:baseSceneIndoorPlant}
@@
         \caption{Warehouse}    
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_e.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_e.png}
         \label{fig:baseSceneWarehouse}
@@
         \caption{Checkerboard}    
-        \includegraphics[width=\textwidth]{../Figures/Figure3/Figure3_f.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_f.png}
         \label{fig:baseSceneCheckerBoard}
@@
         \caption{Big-ball}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_a.png}
         \label{fig:libraryWithBigBall}
@@
         \caption{Small-ball}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_b.png}
         \label{fig:libraryWithSmallBall}
@@
         \caption{Barrel}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_c.png}
         \label{fig:libraryWithBarrel}
@@
         \caption{Xylophone}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_d.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_d.png}
         \label{fig:libraryWithXylophone}
@@
         \caption{Ring toy}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_e.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_e.png}
         \label{fig:libraryWithRingToy}
@@
         \caption{Bottle}
-        \includegraphics[width=\textwidth]{../Figures/Figure4/Figure4_f.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_f.png}
         \label{fig:libraryWithChampagneBottle}
@@
         \caption{Target position}
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_d.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_d.png}
         \label{fig:targetPositionVariation}
@@
     \centering
-        \caption{Target Size/Orientation}
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_e.png}
+        \caption{Target size/Orientation}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_e.png}
         \label{fig:targetSizeOrientation}
@@
         \caption{Target spectra}
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_a.png}
         \label{fig:targetVariation}
@@
         \caption{Background spectra}
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_b.png}
         \label{fig:backGroundVariation}
@@
         \caption{Illumination spectra}
-        \includegraphics[width=\textwidth]{../Figures/Figure5/Figure5_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_c.png}
         \label{fig:illuminationVariation}
@@
 
+%% Fix the title capitalization in a and b
 \subsubsection{Illumination spectra}
@@
 	\caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_a.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_a.pdf}
         \label{fig:granadaData}
@@
         \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_b.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_b.pdf}
         \label{fig:illuminantSamples}
@@
         \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_c.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_c.pdf}
         \label{fig:xyDiagram}
@@
         \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure6/Figure6_d.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_d.pdf}
         \label{fig:sRGBIlluminant}
@@
 \subsubsection{Surface reflectance spectra}
-% Figure 7
+%% Fix the title capitalization in a and b
+% Figure 7 Surface Reflectance Data and Model
 \begin{figure}
@@
             \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_a.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_a.pdf}
         \label{fig:reflectanceSpectra}
@@
         \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_b.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_b.pdf}
         \label{fig:reflectanceSamples}
@@
     \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_c.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_c.pdf}
         \label{fig:xyChroReflectance}
@@
         \caption{}
-        \includegraphics[width=\textwidth]{../Figures/Figure7/Figure7_d.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_d.pdf}
         \label{fig:backgroundSwatches}
@@
 
+%Figure 8 Target Surface Reflectance Samples
 \begin{figure}
 \centering
-\includegraphics[width=0.3\textwidth]{../Figures/Figure7/Figure8.pdf}
+\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure8/Figure8.pdf}
 \caption{{\bf Target surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
@@
         \caption{sRGB rendering of a 3D scene}
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_a.png}
         \label{fig:3DScene}
@@
     \hspace{0.1 \textwidth}
-        \caption{Cropped Image}
+        \caption{Cropped image}
         \vspace{1.5mm}
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_b.png}
         \label{fig:croppedImage}
@@
     \hspace{0.1 \textwidth}
-        \caption{Optical Image}
+        \caption{Optical image}
         \vspace{1.5mm}
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_c.png}
         \label{fig:croppedImageWithMosaic}
@@
         \caption{LMS cone contrast}
-        \includegraphics[width=\textwidth]{../Figures/Figure8/Figure8_d.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_d.png}
         \label{fig:coneContrast}
@@
 
-%% Figure 9
+%% Figure 10: Results for Condition 1
 \begin{figure}
@@
         \caption{RF response condition 1}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_a.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure10/Figure10_a.pdf}
         \label{fig:case1RFResponse}
@@
             \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{Luminance Estimates}
-        \includegraphics[width=\textwidth]{../Figures/Figure9/Figure9_b.pdf}
+        \caption{LRV estimates}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure10/Figure10_b.pdf}
         \label{fig:case1Results}
     \end{subfigure}    
-    \caption{{\bf RF response and luminance estimates for condition 0 (baseline) and condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
+    \caption{{\bf RF response and luminance estimates for condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
 We show the response for the images in the training set.
@@
 
-\subsubsection{Condition 2: Target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable}
-When the light source emission spectrum is fixed, the naive expectation would be that the luminance of the target object would depend only on the surface reflectance of the target object. 
-Indeed, it is believed that the variation in the surface reflectance of the background has little effect on the reflected light from the target object  \cite{BrainardWandellRetinex}. 
-But our analysis shows that the secondary reflections from the target object, of the light coming indirectly after being reflected from the background objects, have a significant effect on the response of the photoreceptors corresponding to the target object.
-Fig.~{\ref{fig:case2RFResponse}} shows the projection of the photoreceptor response for the stimuli in condition 2 along the first two AMA receptive fields. 
-These receptive fields were learnt using the stimuli from the same condition (Condition 2). 
-The response projected along the first two optimal receptive fields do not separate as well compared to condition 1. 
-But the overlap is lower if the projection is considered in subspaces that have more AMA receptive fields. 
-Fig.~\ref{fig:ErrorVsNFilters} shows the relative error of luminance estimate as a function of the number of AMA receptive fields used for luminance estimation. 
-As expected, the relative error decreases with the number of receptive fields and converges to the minimum value around 8 receptive fields. 
-Fig.~\ref{fig:case2Estimates} shows the luminance estimates for the learning methods used in this work. 
-The mean estimates fall along the diagonal x=y line. 
-The variance in the estimates increases with assigned luminance. 
-This is because the isomerization noise is directly proportional to the light reflected from the target object and is higher at higher values of the target LRV.
-
-%% Figure condition 2
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.3	 \textwidth}   
-        \caption{RF response condition 2}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_a.pdf}
-        \label{fig:case2RFResponse}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{Luminance Estimates}
-        \includegraphics[width=\textwidth]{../Figures/Figure10/Figure10_b.pdf}
-        \label{fig:case2Estimates}
-    \end{subfigure}
-    \caption{{\bf Condition 2:} (a) Photoreceptor response projected along the first two AMA receptive fields.
-(b) Estimated v/s assigned target LRV for the image in condition 2.
-Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.}
-\label{fig:case2Results}
-\end{figure}
-
-%%% Figure 11: RMSE vs N Filters
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{../Figures/Figure11/Figure11.pdf}
-\caption{{\bf Performance with number of RFs used for estimation:} Relative error as a function of number of AMA receptive fields used for luminance estimation.
-While most of the information is captured by the first two filters, the relative error reduces as the number of receptive fields used for luminance estimation are increased.
-We have used the first 8 RFs for estimating the luminance.}
-\label{fig:ErrorVsNFilters}
-\end{figure}
-
-\subsubsection{Condition 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed}
-For the spectral variations of condition 3, the AMA receptive fields learnt on the photoreceptor response to the images does a very poor job in predicting the target LRV (Fig.~\ref{fig:isomerizationFails}).
+\subsubsection{Condition 2: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed}
+For the spectral variations of condition 2, the AMA receptive fields learnt on the photoreceptor response to the images does a very poor job in predicting the target LRV (Fig.~\ref{fig:isomerizationFails}).
 This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
@@
 
-%% Figure condition 3: Isomerization Fails
+%% Figure condition 2: Isomerization Fails
 \begin{figure}
 \centering
-    \begin{subfigure}[b]{0.3	 \textwidth}   
-        \caption{RFs learnt using photoreceptor response}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_a.pdf}
+    \begin{subfigure}[b]{0.22	 \textwidth}   
+        \caption{RF response (Isomerization)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_a.pdf}
         \label{fig:isomerizationFails}
     \end{subfigure}
-        \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{RFs learnt using contrast signal}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_b.pdf}
-        \label{fig:constrastWorks}
+        \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{LRV estimates (Isomerization)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_b.pdf}
+        \label{fig:IsomerizationResults}
     \end{subfigure}
-            \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{Luminance estimates}
-        \includegraphics[width=\textwidth]{../Figures/Figure12/Figure12_c.pdf}
-        \label{fig:case10Results}
+            \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{RF response (Contrast)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_c.pdf}
+        \label{fig:contrastWorks}
     \end{subfigure}
-    \caption{{\bf Condition 3: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
+            \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{LRV estimates (Contrast)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_d.pdf}
+        \label{fig:constrstResults}
+    \end{subfigure}
+    \caption{{\bf Condition 2: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
 (b) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
@@
 
-\subsubsection{Condition 4: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
-% Figure condition 4
+\subsubsection{Condition 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
+% Figure condition 3
 \begin{figure}
@@
     \begin{subfigure}[b]{0.3 \textwidth}   
-        \caption{AMA RF Response}
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_a.pdf}
+        \caption{RF response}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12_a.pdf}
         \label{fig:case12FiltersResponse}
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{Luminance Estimates}
-        \includegraphics[width=\textwidth]{../Figures/Figure13/Figure13_b.pdf}
+        \caption{LRV estimates}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12_b.pdf}
         \label{fig:case12Results}
@@
 	\caption{Condition 1}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_a.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure14/Figure14_a.pdf}
 	\label{fig:case1Filter}
@@
 	\caption{Condition 2}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_b.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure14/Figure14_b.pdf}
 	\label{fig:case2Filter}
@@
 	\caption{Condition 3}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_c.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure14/Figure14_c.pdf}
 	\label{fig:case3Filter}
@@
 	\caption{Condition 4}
-	\includegraphics[width=\textwidth]{../Figures/Figure14/Figure14_d.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure14/Figure14_d.pdf}
 	\label{fig:case4Filter}
@@
 	\caption{Condition 1}
-	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_a.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure15/Figure15_a.pdf}
 	\label{fig:case1Bar}
@@
 	\caption{Condition 2}
-	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_b.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure15/Figure15_b.pdf}
 	\label{fig:case2Bar}
@@
 	\caption{Condition 3}
-	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_c.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure15/Figure15_c.pdf}
 	\label{fig:case3Bar}
@@
 	\caption{Condition 4}
-	\includegraphics[width=\textwidth]{../Figures/Figure15/Figure15_d.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure15/Figure15_d.pdf}
 	\label{fig:case4Bar}

### 2018-04-16 Draft4/draft4.tex
more edits

@@
 For this condition, estimating LRV should be easy because the variation in target object reflectance that we introduced
-preserved LRV (which is calculated using a CIE D65 as the illumination.
-This in turn means that for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will
-vary minimally.
+preserved LRV (which is calculated using a CIE D65 as the illumination).
+This in turn means that for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
 In Condition 1, we used an illumination draw form our daylight sample and thus expect a reasonable degree of similarity to D65.
@@
 
-\subsubsection{Condition 2: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed}
-For the spectral variations of condition 2, the AMA receptive fields learnt on the photoreceptor response to the images does a very poor job in predicting the target LRV (Fig.~\ref{fig:isomerizationFails}).
+Next, we discuss Condition 2, where we varied the spectral power distribution function of the light sources in addition to the target object LRV and relative spectrum. 
+This is a more realistic condition, where the spectra of light sources change while the objects remain fixed, as in a naturalistic scene. 
+Similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
+First we trained and evaluated AMA on the cone responses to the image patches.
+Figure~\ref{fig:isomerizationFails} shows the responses of the first two receptive fields to all the image patches in the training set.
+For the spectral variations of condition 2, the AMA receptive fields learnt on the cone response to the images does a very poor job in predicting the target LRV.
 This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
-But, since the background surfaces are fixed in this condition, the ratio between the response of  photoreceptors corresponding to the target object and the background remains proportional to the target LRV.
+The decoding performance using these receptive fields for the test set is shown in Figure~\ref{fig:IsomerizationResults}.
+
+On the other hand, since the background surfaces are fixed in this condition, the ratio between the response of  photoreceptors corresponding to the target object and the background remains proportional to the target LRV.
 This is because a change in illuminant spectra produces the same effect in both the target object and the background object. 
-Thus, the AMA receptive fields learnt on the contrast normalized photoreceptor response (see Methods) can be used to predict the target LRV (Fig.~\ref{fig:constrastWorks}). 
-Fig.~\ref{fig:case10Results} shows the estimated target LRV v/s the assigned luminance for the images in condition 3 obtained using the contrast normalized representation. 
+Thus, the AMA receptive fields learnt on the contrast normalized cone response (see Methods) can be used to predict the target LRV (Fig.~\ref{fig:contrastWorks}). 
+Fig.~\ref{fig:contrastResults} shows the decoding performance for the test set in condition 2 obtained using the contrast normalized representation.
 AMA receptive fields provide excellent predictions of the target LRV. 
@@
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_d.pdf}
-        \label{fig:constrstResults}
+        \label{fig:contrastResults}
     \end{subfigure}
@@
 
-Again, similar to condition 2, the projection along the first two receptive fields shows an overlap between the stimuli at higher luminance values (Fig.~\ref{fig:constrastWorks}).
-But, the stimuli are better separated if the projection is considered within a subspace that has more receptive fields (Fig.~\ref{fig:ErrorVsNFilters}).
+Finally, we discuss Condition 3, where the spectral power distribution function of the light sources, the reflectance spectra of the background objects and the target object LRV and relative spectrum are allowed to vary.
+This is the most interesting and difficult condition.
+For this condition, we used AMA to learn a set of linear receptive fields using the contrast normalized cone response. 
+Fig.~\ref{fig:contrastResults} shows the decoding performance for the test set in condition 3 obtained using the contrast normalized representation.
 
@@
         \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{RF response}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12_a.pdf}
-        \label{fig:case12FiltersResponse}
-    \end{subfigure}    
-        \begin{subfigure}[b]{0.3 \textwidth}
         \caption{LRV estimates}
@@
     \end{subfigure}
-    \caption{{\bf Condition 3:} (a) Contrast normalized photoreceptor response projected along the first two AMA receptive fields.
-(b) Target LRV estimates v/s assigned luminance for images in condition 3.
-The AMA estimates are unbiased and have smaller relative error compared to linear model.}
+    \caption{{\bf Condition 3:} (a) Target LRV estimates v/s assigned luminance for images in condition 3. The AMA estimates are unbiased and have smaller relative error compared to linear model.}
     \label{fig:case12AllResults}

### 2018-04-18 Draft4/draft4.tex
added RMSE values for condition 1
small edits

@@
 The standard deviations are too small to be visible.
-The relative error of estimation is XX (AMA) and YY(Linear regression).}
+The relative error of estimation is 1.1\% (AMA) and 0.8\% (Linear regression).}
 \label{fig:Condition1}
@@
 
-Next, we discuss Condition 2, where we varied the spectral power distribution function of the light sources in addition to the target object LRV and relative spectrum. 
+Next we discuss Condition 2, where we varied the spectral power distribution function of the light sources in addition to the target object LRV and relative spectrum. 
 This is a more realistic condition, where the spectra of light sources change while the objects remain fixed, as in a naturalistic scene. 

### 2018-04-19 Draft4/draft4.tex
added figures for condition 2

@@
 
-To generate illumination spectra, we developed a statistical model of the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{peyvandi2016colorimetric} and sample randomly from the model.
+To generate illumination spectra, we developed a statistical model of the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{hernandez2001color} and sample randomly from the model.
 The overall intensity of the measurements spans approximately three orders of magnitude.
@@
 
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.22	 \textwidth}   
+        \caption{RF response (Isomerization)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_e.pdf}
+        \label{fig:isomerizationFails}
+    \end{subfigure}
+        \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{LRV estimates (Isomerization)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_f.pdf}
+        \label{fig:IsomerizationResults}
+    \end{subfigure}
+            \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{RF response (Contrast)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_g.pdf}
+        \label{fig:contrastWorks}
+    \end{subfigure}
+            \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{LRV estimates (Contrast)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_h.pdf}
+        \label{fig:contrastResults}
+    \end{subfigure}
+    \caption{{\bf Condition 2: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
+(b) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
+The receptive fields were calculated using the contrast normalized stimuli.
+The response at each luminance level separates much better in this representation.
+(c) Estimated v/s assigned target LRV for the image in condition 3.
+Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
+AMA estimates are much better compared to the null models.}
+\label{fig:importanceOfConstrast}
+\end{figure}
+
 Finally, we discuss Condition 3, where the spectral power distribution function of the light sources, the reflectance spectra of the background objects and the target object LRV and relative spectrum are allowed to vary.

### 2018-04-22 Draft4/draft4.tex
condition 2 figures and caption

@@
 \subsubsection*{Learning optimal filters}
-
-AMA 
-is a task specific Bayesian method for dimensionality reduction.
+AMA is a task specific Bayesian method for dimensionality reduction.
 When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of linear receptive fields.
@@
 We show the response for the images in the training set.
-Each response cloud represents the response of images corresponding to one luminance level.
+Each response cloud represents the response of images corresponding to one LRV.
 The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(b) Mean luminance estimates and standard deviations for the images in the test set obtained using the naive method, linear regression and AMA.
-The estimates fall along the diagonal unit slope (blue dotted) line for both linear regression and AMA.
+(b)  Estimated v/s assigned target LRV for the image in condition 1.
+Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
+Relative error of estimation is 0.8\% (Linear regression) and 1.1\% (AMA) .
+The diagonal unit slope (blue dotted) line is for reference.
 The standard deviations are too small to be visible.
-The relative error of estimation is 1.1\% (AMA) and 0.8\% (Linear regression).}
+}
 \label{fig:Condition1}
@@
     \caption{{\bf Condition 2: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
-(b) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
+(b) Mean LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA.
+The relative error of estimation is 41.4\% (Linear regression) and 31.3\% (AMA).
+(c) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
 The receptive fields were calculated using the contrast normalized stimuli.
 The response at each luminance level separates much better in this representation.
-(c) Estimated v/s assigned target LRV for the image in condition 3.
-Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
-AMA estimates are much better compared to the null models.}
-\label{fig:importanceOfConstrast}
-\end{figure}
-
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.22	 \textwidth}   
-        \caption{RF response (Isomerization)}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_e.pdf}
-        \label{fig:isomerizationFails}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{LRV estimates (Isomerization)}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_f.pdf}
-        \label{fig:IsomerizationResults}
-    \end{subfigure}
-            \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{RF response (Contrast)}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_g.pdf}
-        \label{fig:contrastWorks}
-    \end{subfigure}
-            \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{LRV estimates (Contrast)}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_h.pdf}
-        \label{fig:contrastResults}
-    \end{subfigure}
-    \caption{{\bf Condition 2: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
-(b) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
-The receptive fields were calculated using the contrast normalized stimuli.
-The response at each luminance level separates much better in this representation.
-(c) Estimated v/s assigned target LRV for the image in condition 3.
-Solid lines show the mean estimate, the filled region in light color  shows one standard deviation.
-AMA estimates are much better compared to the null models.}
+(d) Estimated v/s assigned target LRV for the image in condition 2.
+The relative error of estimation is 9.3\% (Linear regression) and 1.1\% (AMA).}
 \label{fig:importanceOfConstrast}

### 2018-04-24 Draft4/draft4.tex
more edits

@@
 
-Next we discuss Condition 2, where we varied the spectral power distribution function of the light sources in addition to the target object LRV and relative spectrum. 
-This is a more realistic condition, where the spectra of light sources change while the objects remain fixed, as in a naturalistic scene. 
-Similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
+Next we discuss Condition 2, where the spectral power distribution function of the light sources and the target object LRV and relative spectrum varies. 
+This is a more naturalistic condition compared to condition 1.
+Again, similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
 First we trained and evaluated AMA on the cone responses to the image patches.
@@
         \caption{LRV estimates}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12_b.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12_a.pdf}
         \label{fig:case12Results}
     \end{subfigure}
-    \caption{{\bf Condition 3:} (a) Target LRV estimates v/s assigned luminance for images in condition 3. The AMA estimates are unbiased and have smaller relative error compared to linear model.}
+    \caption{{\bf Condition 3:} Target LRV estimates v/s assigned luminance for images in test set of condition 3.
+The LRV estimates have been obtained using RFs learnt on contrast normalized images.
+The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.}
     \label{fig:case12AllResults}

### 2018-04-24 Draft4/draft4.tex
more edits

@@
 
-Finally, we discuss Condition 3, where the spectral power distribution function of the light sources, the reflectance spectra of the background objects and the target object LRV and relative spectrum are allowed to vary.
-This is the most interesting and difficult condition.
-For this condition, we used AMA to learn a set of linear receptive fields using the contrast normalized cone response. 
-Fig.~\ref{fig:contrastResults} shows the decoding performance for the test set in condition 3 obtained using the contrast normalized representation.
-
-\subsubsection{Condition 3: Target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable}
 % Figure condition 3
@@
         \caption{LRV estimates}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12_a.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12.pdf}
         \label{fig:case12Results}
@@
 
-Condition 4 is the most complex type of variation that we consider in this work.
-Here we allow all three types of spectra to change from image to image.
-In this condition, neither the photoreceptor response (as in condition 1 and 2), nor any simple transformation of the response (condition 3) can provide the target LRV.We used AMA to learn the receptive fields using the contrast normalized cone photoreceptor response from stimuli in condition 4.
-Fig.~\ref{fig:case12AllResults} shows the AMA receptive field response and the luminance estimates for the images in condition 4.
-We have used the first 8 receptive fields to estimate the luminance in this condition (see Fig.\ref{fig:ErrorVsNFilters}). 
-The AMA receptive fields do an excellent job of predicting the target LRV. 
-The estimates are unbiased with the mean estimates lying close the diagonal unit slope line (Fig.~\ref{fig:case12Results}). 
-The relative error of estimation is $\sim15\%$, which low compared to that of the naive model ($\sim42\%$) or the linear model on center pixel ($\sim21\%$).
+Finally, we discuss Condition 3, where the spectral power distribution function of the light sources, the reflectance spectra of the background objects and the target object LRV and relative spectrum are allowed to vary.
+This is the most interesting and difficult condition.
+For this condition, we used AMA to learn a set of linear receptive fields using the contrast normalized cone response. 
+Fig.~\ref{fig:case12AllResults} shows the decoding performance for the test set in condition 3 obtained using the contrast normalized representation.
 
@@
 	\caption{Condition 1}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure14/Figure14_a.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure13/Figure13_a.pdf}
 	\label{fig:case1Filter}
@@
     \begin{subfigure}{0.21 \textwidth}   
-	\caption{Condition 2}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure14/Figure14_b.pdf}
-	\label{fig:case2Filter}
+	\caption{Condition 2 isomerization}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure13/Figure13_b.pdf}
+	\label{fig:case2FilterI}
+    \end{subfigure}
+    ~ ~ ~
+        \begin{subfigure}{0.21 \textwidth}
+	\caption{Condition 2 contrast}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure13/Figure13_c.pdf}
+	\label{fig:case2FilterC}
     \end{subfigure}
@@
 	\caption{Condition 3}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure14/Figure14_c.pdf}
+	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure13/Figure13_d.pdf}
 	\label{fig:case3Filter}
-    \end{subfigure}
-    ~ ~ ~
-        \begin{subfigure}{0.21 \textwidth}
-	\caption{Condition 4}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure14/Figure14_d.pdf}
-	\label{fig:case4Filter}
     \end{subfigure}
@@
 The L and M filters have larger weight as luminance is essentially a function of the L and M cone isomerizations.
-The stereotypical pattern in the receptive fields of condition 4 is due to the fixed geometry of the images.}
+The stereotypical pattern in the receptive fields of condition 3 is due to the fixed geometry of the images.}
  \label{fig:AMAFilters}
@@
 The L, M and S components give the weights for the linear sum of the cone responses for the three cone types.
-The salient features are: the center surround structure of the RFs and the higher weights of the L and M cones, compared to the S cones.
+The salient features are: the center surround structure of the RFs, and the higher weights of the L and M cones, compared to the S cones.
 
 For condition 1, since the illuminant and the background are fixed, all the information is in the central target object reflectance. 
-Thus, the RFs weights are mostly concentrated around the center.
-For condition 2, where the target and the background spectra varies, most of the luminance information is still concentrated around the central target object.
-For condition 3, while the target and the illuminant spectra varies, the background object spectra is fixed.
-Hence, the luminance can be estimated by simply from the contrast between the response of the cones corresponding to the target and the background.
-Thus, while the RFs show a trend of weights concentrated at the center similar to condition 1, there is large negative contribution from the surround.
+Thus, the receptive fields weights are mostly concentrated around the center (Figure~\ref{fig:case1Filter}). 
+For condition 2, the illuminant spectra varies over several order of magnitude. 
+As a result the photoreceptor isomerizations vary wildly. 
+Thus, AMA receptive fields learnt on isomerizations do not show any clear pattern (Figure~\ref{fig:case2FilterI}). 
+But, since the background object spectra is fixed, the contrast between the response 
+of the cones corresponding to the target and the background carries the information about 
+the target object LRV. 
+The receptive fields learnt on the contrast signal shows this a trend. 
+The receptive field weights are concentrated at the center similar to condition 1, there is large negative contribution from the surround (Figure~\ref{fig:case2FilterC}).
 The spatial features of the RFs are due the stereotypical geometry of the images (see \nameref{Methods}). 
-Condition 4 has a similar center surround structure, but with more prominent features of the background since the spectra of the background objects are also varying.
+Condition 3 has a similar center surround structure, but with more prominent features of the background, since the spectra of the background objects are also varying (Figure~\ref{fig:case3Filter}). 
 Again, the spatial features are a result of the stereotypical geometry of the images.

### 2018-04-24 Draft4/draft4.tex
Today’s edits

@@
 
+Figure Blah [c] shows the first two AMA receptive fields.
+Each of these, in essence, takes a weighted sum of the L and M cone isomerizations at the target object location.
+The isomerizations in the background regions and the S cone isomerizations are largely ignored.
+These receptive fields make sense.
+For this condition, the background regions provide very little task relevant information: their only relevant effect is
+through light scattered from them onto the target.
+In addition, luminance is primarily determined by L and M cone isomerizations.
+
 %% Figure 10: Results for Condition 1
@@
 The diagonal unit slope (blue dotted) line is for reference.
-The standard deviations are too small to be visible.
-}
+The standard deviations are too small to be visible.}
 \label{fig:Condition1}
@@
 
-Next we discuss Condition 2, where the spectral power distribution function of the light sources and the target object LRV and relative spectrum varies. 
-This is a more naturalistic condition compared to condition 1.
-Again, similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
-First we trained and evaluated AMA on the cone responses to the image patches.
-Figure~\ref{fig:isomerizationFails} shows the responses of the first two receptive fields to all the image patches in the training set.
-For the spectral variations of condition 2, the AMA receptive fields learnt on the cone response to the images does a very poor job in predicting the target LRV.
-This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
-The decoding performance using these receptive fields for the test set is shown in Figure~\ref{fig:IsomerizationResults}.
+Next we discuss Condition 2, where we introduce variation in the spectral power distribution function of the light sources.
+This variation makes the task more difficult, because it causes more variation in cone isomerizations due to factors other than the target object LRV.
+%This is a more naturalistic condition compared to condition 1.
+%Again, similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
+%First we trained and evaluated AMA on the cone responses to the image patches.
+Figure~\ref{fig:isomerizationFails} [a and b] show the results when we learned and evaluated the performance of AMA on the cone isomerizations.
+Performance is poor.
+Indeed, on average the estimates track deviate considerably from the true LRV, as seen by the fact that the mean estimate
+(red line) does not lie along the positive diagonal and by the fact that there is large estimation variability for each
+value of the true LRV (asindicated by the width of the shaded red region).
+For this case, linear regression is also very poor. Indeed, the linear regression estimates are essentially the same as would be obtained
+by simply guessing the mean LRV of the training set (0.4).
 
-On the other hand, since the background surfaces are fixed in this condition, the ratio between the response of photoreceptors corresponding to the target object and the background remains proportional to the target LRV.
-This is because a change in illuminant spectra produces the same effect in both the target object and the background object. 
-Thus, the AMA receptive fields learnt on the contrast normalized cone response (see Methods) can be used to predict the target LRV (Fig.~\ref{fig:contrastWorks}). 
-Fig.~\ref{fig:contrastResults} shows the decoding performance for the test set in condition 2 obtained using the contrast normalized representation.
-AMA receptive fields provide excellent predictions of the target LRV. 
-The predictions are much better compared to that of a linear model that only considers the (contrast normalized) response of the photoreceptors corresponding to the center pixel of the target object.
+Recall that there are two qualitatively distinct aspects to the variation in light source spectra.
+One is a variation in relative spectral power distribution and the
+other is a variation in overall intensity.
+To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone isomerizations.
+Figure~\ref{fig:IsomerizationResults} [c and d] shows that performance improves greatly, and indeed is essentially perfect.
+This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
+contrast-based representations provide an effective vehicle for achieving color constancy (REFS).
+That same literature, however, shows that
+contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.
+
+In Condition 3, we introduced variation in the reflectance spectra of the background objects.
+This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
+We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations.
+Figure~\ref{fig:IsomerizationResults} [a] shows the results.
+The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions.
+None-the-less, the estimates provide useful information about the target LRV.
+Indeed, on average the estimates track the true LRV, as seen by the fact that the mean estimate
+(red line) tracks the positive diagonal.
+The increased estimation variability is indicated by the width of the shaded red region.
+Performance of baseline linear regression method (also for the contrast normalized isomerizations) is worse than that of the AMA-based estimates.
+
+Figure~\ref{fig:IsomerizationResults} [b] shows the responses of the first two AMA linear receptive fields for test [or training] stimuli.
+Here, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
+Recall, however, that performance is based on six rather than two receptive fields.
+Inclusion of more receptive fields reduces the ambiguity visible in the responses of just the first two.
+
+%This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
+%
+%responses of the first two receptive fields to all the image patches in the training set.
+%For the spectral variations of condition 2, the AMA receptive fields learnt on the cone response to the images does a very poor job in predicting the target LRV.
+%The decoding performance using these receptive fields for the test set is shown in .
+%
+%On the other hand, since the background surfaces are fixed in this condition, the ratio between the response of photoreceptors corresponding to the target object and the background remains proportional to the target LRV.
+%This is because a change in illuminant spectra produces the same effect in both the target object and the background object. 
+%Thus, the AMA receptive fields learnt on the contrast normalized cone response (see Methods) can be used to predict the target LRV (. 
+%Fig.~\ref{fig:contrastResults} shows the decoding performance for the test set in condition 2 obtained using the contrast normalized representation.
+%AMA receptive fields provide excellent predictions of the target LRV. 
+%The predictions are much better compared to that of a linear model that only considers the (contrast normalized) response of the photoreceptors corresponding to the center pixel of the target object.
 

### 2018-04-24 Draft4/draft4.tex
fixed figures and text

@@
 \section{Results} \label{Results}
+%% Figure 10: Results for Condition 1
+\begin{figure}
+\centering
+            \begin{subfigure}[b]{0.25 \textwidth}
+        \caption{LRV estimates}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft4/Figure10/Figure10_a.pdf}
+        \label{fig:case1Estimates}
+    \end{subfigure} 
+        \begin{subfigure}[b]{0.26 \textwidth}
+        \caption{Receptive field response}
+        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure10/Figure10_b.pdf}
+        \label{fig:case1RFResponse}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.28 \textwidth}
+	\caption{AMA receptive fields}
+	\includegraphics[width=1.07\textwidth, trim={0 -0.6cm 0 -0.3cm}]{../FiguresDraft4/Figure10/Figure10_c.pdf}
+	\label{fig:case1RFs}
+    \end{subfigure}   
+    \caption{{\bf RF response and luminance estimates for condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
+We show the response for the images in the training set.
+Each response cloud represents the response of images corresponding to one LRV.
+The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
+(b)  Estimated v/s assigned target LRV for the image in condition 1.
+Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
+Relative error of estimation is 0.8\% (Linear regression) and 1.1\% (AMA) .
+The diagonal unit slope (blue dotted) line is for reference.
+The standard deviations are too small to be visible.}
+\label{fig:Condition1}
+\end{figure}
+
+\begin{figure}
+\centering
+            \begin{subfigure}[b]{0.25 \textwidth}
+        \caption{LRV estimates}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft4/Figure10/Figure10_a.pdf}
+        \label{fig:case1Estimates}
+    \end{subfigure} 
+        \begin{subfigure}[b]{0.26 \textwidth}
+        \caption{Receptive field response}
+        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure10/Figure10_d.pdf}
+        \label{fig:case1RFResponse}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.28 \textwidth}
+	\caption{AMA receptive fields}
+	\includegraphics[width=1.07\textwidth, trim={0 -0.6cm 0 -0.3cm}]{../FiguresDraft4/Figure10/Figure10_c.pdf}
+	\label{fig:case1RFs}
+    \end{subfigure}   
+    \caption{{\bf RF response and luminance estimates for condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
+We show the response for the images in the training set.
+Each response cloud represents the response of images corresponding to one LRV.
+The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
+(b)  Estimated v/s assigned target LRV for the image in condition 1.
+Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
+Relative error of estimation is 0.8\% (Linear regression) and 1.1\% (AMA) .
+The diagonal unit slope (blue dotted) line is for reference.
+The standard deviations are too small to be visible.}
+\label{fig:Condition1}
+\end{figure}
 
@@
 
-Decoding performance for the test set is shown in Figure~\ref{fig:case1Results}.
+Decoding performance for the test set is shown in Figure~\ref{fig:case1Estimates}.
 As expected, the LRV estimates obtained by decoding the AMA receptive field responses are veridical.
-Figure~\ref{fig:case1Results} also shows the performance of the baseline linear regression method, again trained
+Figure~\ref{fig:case1Estimates} also shows the performance of the baseline linear regression method, again trained
 on the training set and evaluated on the test set.
@@
 
-Figure Blah [c] shows the first two AMA receptive fields.
+Figure~\ref{fig:case1RFs} shows the first two AMA receptive fields.
 Each of these, in essence, takes a weighted sum of the L and M cone isomerizations at the target object location.
@@
 
-%% Figure 10: Results for Condition 1
-\begin{figure}
-\centering
-        \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{RF response condition 1}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure10/Figure10_a.pdf}
-        \label{fig:case1RFResponse}
-    \end{subfigure}    
-            \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{LRV estimates}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure10/Figure10_b.pdf}
-        \label{fig:case1Results}
-    \end{subfigure}    
-    \caption{{\bf RF response and luminance estimates for condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
-We show the response for the images in the training set.
-Each response cloud represents the response of images corresponding to one LRV.
-The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(b)  Estimated v/s assigned target LRV for the image in condition 1.
-Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
-Relative error of estimation is 0.8\% (Linear regression) and 1.1\% (AMA) .
-The diagonal unit slope (blue dotted) line is for reference.
-The standard deviations are too small to be visible.}
-\label{fig:Condition1}
-\end{figure}
-
-Next we discuss Condition 2, where we introduce variation in the spectral power distribution function of the light sources.
-This variation makes the task more difficult, because it causes more variation in cone isomerizations due to factors other than the target object LRV.
-%This is a more naturalistic condition compared to condition 1.
-%Again, similar to condition 1, we used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
-%First we trained and evaluated AMA on the cone responses to the image patches.
-Figure~\ref{fig:isomerizationFails} [a and b] show the results when we learned and evaluated the performance of AMA on the cone isomerizations.
-Performance is poor.
-Indeed, on average the estimates track deviate considerably from the true LRV, as seen by the fact that the mean estimate
-(red line) does not lie along the positive diagonal and by the fact that there is large estimation variability for each
-value of the true LRV (asindicated by the width of the shaded red region).
-For this case, linear regression is also very poor. Indeed, the linear regression estimates are essentially the same as would be obtained
-by simply guessing the mean LRV of the training set (0.4).
-
-Recall that there are two qualitatively distinct aspects to the variation in light source spectra.
-One is a variation in relative spectral power distribution and the
-other is a variation in overall intensity.
-To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone isomerizations.
-Figure~\ref{fig:IsomerizationResults} [c and d] shows that performance improves greatly, and indeed is essentially perfect.
-This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
-contrast-based representations provide an effective vehicle for achieving color constancy (REFS).
-That same literature, however, shows that
-contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.
-
-In Condition 3, we introduced variation in the reflectance spectra of the background objects.
-This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
-We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations.
-Figure~\ref{fig:IsomerizationResults} [a] shows the results.
-The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions.
-None-the-less, the estimates provide useful information about the target LRV.
-Indeed, on average the estimates track the true LRV, as seen by the fact that the mean estimate
-(red line) tracks the positive diagonal.
-The increased estimation variability is indicated by the width of the shaded red region.
-Performance of baseline linear regression method (also for the contrast normalized isomerizations) is worse than that of the AMA-based estimates.
-
-Figure~\ref{fig:IsomerizationResults} [b] shows the responses of the first two AMA linear receptive fields for test [or training] stimuli.
-Here, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
-Recall, however, that performance is based on six rather than two receptive fields.
-Inclusion of more receptive fields reduces the ambiguity visible in the responses of just the first two.
-
-%This is because, since the illuminant spectra varies in this condition, the photoreceptor response is not directly proportional to the target object surface anymore. 
-%
-%responses of the first two receptive fields to all the image patches in the training set.
-%For the spectral variations of condition 2, the AMA receptive fields learnt on the cone response to the images does a very poor job in predicting the target LRV.
-%The decoding performance using these receptive fields for the test set is shown in .
-%
-%On the other hand, since the background surfaces are fixed in this condition, the ratio between the response of photoreceptors corresponding to the target object and the background remains proportional to the target LRV.
-%This is because a change in illuminant spectra produces the same effect in both the target object and the background object. 
-%Thus, the AMA receptive fields learnt on the contrast normalized cone response (see Methods) can be used to predict the target LRV (. 
-%Fig.~\ref{fig:contrastResults} shows the decoding performance for the test set in condition 2 obtained using the contrast normalized representation.
-%AMA receptive fields provide excellent predictions of the target LRV. 
-%The predictions are much better compared to that of a linear model that only considers the (contrast normalized) response of the photoreceptors corresponding to the center pixel of the target object.
-
 %% Figure condition 2: Isomerization Fails
@@
 \centering
-    \begin{subfigure}[b]{0.22	 \textwidth}   
+    \begin{subfigure}[b]{0.22\textwidth}   
         \caption{RF response (Isomerization)}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_a.pdf}
-        \label{fig:isomerizationFails}
+        \label{fig:case2IsomerizationEstimates}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_b.pdf}
-        \label{fig:IsomerizationResults}
+        \label{fig:case2RFResponseIsomer}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_c.pdf}
-        \label{fig:contrastWorks}
+        \label{fig:case2ContrastEstimates}
     \end{subfigure}
@@
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_d.pdf}
-        \label{fig:contrastResults}
+        \label{fig:case2RFResponseContrast}
     \end{subfigure}
@@
 The relative error of estimation is 9.3\% (Linear regression) and 1.1\% (AMA).}
-\label{fig:importanceOfConstrast}
+\label{fig:Condition2}
 \end{figure}
 
-% Figure condition 3
+Next we discuss Condition 2, where we introduce variation in the spectral power distribution function of the light sources.
+This variation makes the task more difficult, because it causes more variation in cone isomerizations due to factors other than the target object LRV.
+Figure~\ref{fig:Condition2}(a, b) show the results when we learned and evaluated the performance of AMA on the cone isomerizations.
+Performance is poor.
+Indeed, on average the estimates track deviate considerably from the true LRV, as seen by the fact that the mean estimate
+(red line) does not lie along the positive diagonal and by the fact that there is large estimation variability for each
+value of the true LRV (as indicated by the width of the shaded red region).
+For this case, linear regression is also very poor. Indeed, the linear regression estimates are essentially the same as would be obtained
+by simply guessing the mean LRV of the training set (0.4).
+
+Recall that there are two qualitatively distinct aspects to the variation in light source spectra.
+One is a variation in relative spectral power distribution and the
+other is a variation in overall intensity.
+To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone isomerizations.
+Figure~\ref{fig:Condition2}(c, d)shows that performance improves greatly, and indeed is essentially perfect.
+This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
+contrast-based representations provide an effective vehicle for achieving color constancy (REFS).
+That same literature, however, shows that
+contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.
+
+%% Figure 12: Results for Condition 3
 \begin{figure}
 \centering
-        \begin{subfigure}[b]{0.3 \textwidth}
+            \begin{subfigure}[b]{0.25 \textwidth}
         \caption{LRV estimates}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure12/Figure12.pdf}
-        \label{fig:case12Results}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft4/Figure12/Figure12_a.pdf}
+        \label{fig:case3Estimates}
     \end{subfigure} 
-    \caption{{\bf Condition 3:} Target LRV estimates v/s assigned luminance for images in test set of condition 3.
-The LRV estimates have been obtained using RFs learnt on contrast normalized images.
-The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.}
-    \label{fig:case12AllResults}
+        \begin{subfigure}[b]{0.26\textwidth}
+        \caption{Receptive field response}
+        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure12/Figure12_b.pdf}
+        \label{fig:case3RFResponse}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.28 \textwidth}
+	\caption{AMA receptive fields}
+	\includegraphics[width=1.07\textwidth, trim={0 -0.6cm 0 -0.5cm}]{../FiguresDraft4/Figure12/Figure12_c.pdf}
+	\label{fig:case3RFs}
+    \end{subfigure}       \caption{{\bf RF response and luminance estimates for condition 3:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
+We show the response for the images in the training set.
+Each response cloud represents the response of images corresponding to one LRV.
+The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
+(b)  Estimated v/s assigned target LRV for the image in condition 1.
+Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
+The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.
+The diagonal unit slope (blue dotted) line is for reference.
+The standard deviations are too small to be visible.}
+\label{fig:Condition3}
 \end{figure}
 
-Finally, we discuss Condition 3, where the spectral power distribution function of the light sources, the reflectance spectra of the background objects and the target object LRV and relative spectrum are allowed to vary.
-This is the most interesting and difficult condition.
-For this condition, we used AMA to learn a set of linear receptive fields using the contrast normalized cone response. 
-Fig.~\ref{fig:case12AllResults} shows the decoding performance for the test set in condition 3 obtained using the contrast normalized representation.
-
-\subsection{Optimal receptive fields for luminance estimation have a center surround structure}
-% Figure RFs 
+%% Figure 12: Results for Condition 3
 \begin{figure}
 \centering
-\begin{subfigure}{0.21 \textwidth}
-	\caption{Condition 1}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure13/Figure13_a.pdf}
-	\label{fig:case1Filter}
+            \begin{subfigure}[b]{0.25 \textwidth}
+        \caption{LRV estimates}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft4/Figure12/Figure12_a.pdf}
+        \label{fig:case3Estimates}
     \end{subfigure} 
-    ~ ~ ~
-    \begin{subfigure}{0.21 \textwidth}   
-	\caption{Condition 2 isomerization}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure13/Figure13_b.pdf}
-	\label{fig:case2FilterI}
+        \begin{subfigure}[b]{0.26\textwidth}
+        \caption{Receptive field response}
+        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure12/Figure12_d.pdf}
+        \label{fig:case3RFResponse}
     \end{subfigure}
-    ~ ~ ~
-        \begin{subfigure}{0.21 \textwidth}
-	\caption{Condition 2 contrast}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure13/Figure13_c.pdf}
-	\label{fig:case2FilterC}
-    \end{subfigure}
-    ~ ~ ~
-        \begin{subfigure}{0.21 \textwidth}
-	\caption{Condition 3}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure13/Figure13_d.pdf}
-	\label{fig:case3Filter}
-    \end{subfigure}
-\caption{{\bf AMA receptive fields:} The first two AMA receptive fields for the four conditions studied in this work.
-The receptive fields show a center surround structure.
-The L and M filters have larger weight as luminance is essentially a function of the L and M cone isomerizations.
-The stereotypical pattern in the receptive fields of condition 3 is due to the fixed geometry of the images.}
- \label{fig:AMAFilters}
+    ~
+    \begin{subfigure}[b]{0.28 \textwidth}
+	\caption{AMA receptive fields}
+	\includegraphics[width=1.07\textwidth, trim={0 -0.6cm 0 -0.5cm}]{../FiguresDraft4/Figure12/Figure12_c.pdf}
+	\label{fig:case3RFs}
+    \end{subfigure}       \caption{{\bf RF response and luminance estimates for condition 3:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
+We show the response for the images in the training set.
+Each response cloud represents the response of images corresponding to one LRV.
+The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
+(b)  Estimated v/s assigned target LRV for the image in condition 1.
+Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
+The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.
+The diagonal unit slope (blue dotted) line is for reference.
+The standard deviations are too small to be visible.}
+\label{fig:Condition3}
 \end{figure}
 
-Fig.~\ref{fig:AMAFilters} shows the first two AMA receptive fields that are optimal for estimating the target LRV for the four types of spectral variations studied in this work.
-The receptive fields are ranked in ascending order of the value of the cost function associated with them.
-Thus the first RF corresponds to the direction along which the projection of the data gives the minimum cost.
-The L, M and S components give the weights for the linear sum of the cone responses for the three cone types.
-The salient features are: the center surround structure of the RFs, and the higher weights of the L and M cones, compared to the S cones.
+In Condition 3, we introduced variation in the reflectance spectra of the background objects.
+This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
+We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations.
+Figure~\ref{fig:case3Estimates} shows the results.
+The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions.
+None-the-less, the estimates provide useful information about the target LRV.
+Indeed, on average the estimates track the true LRV, as seen by the fact that the mean estimate
+(red line) tracks the positive diagonal.
+The increased estimation variability is indicated by the width of the shaded red region.
+Performance of baseline linear regression method (also for the contrast normalized isomerizations) is worse than that of the AMA-based estimates.
 
-For condition 1, since the illuminant and the background are fixed, all the information is in the central target object reflectance. 
-Thus, the receptive fields weights are mostly concentrated around the center (Figure~\ref{fig:case1Filter}). 
-For condition 2, the illuminant spectra varies over several order of magnitude. 
-As a result the photoreceptor isomerizations vary wildly. 
-Thus, AMA receptive fields learnt on isomerizations do not show any clear pattern (Figure~\ref{fig:case2FilterI}). 
-But, since the background object spectra is fixed, the contrast between the response 
-of the cones corresponding to the target and the background carries the information about 
-the target object LRV. 
-The receptive fields learnt on the contrast signal shows this a trend. 
-The receptive field weights are concentrated at the center similar to condition 1, there is large negative contribution from the surround (Figure~\ref{fig:case2FilterC}).
-The spatial features of the RFs are due the stereotypical geometry of the images (see \nameref{Methods}). 
-Condition 3 has a similar center surround structure, but with more prominent features of the background, since the spectra of the background objects are also varying (Figure~\ref{fig:case3Filter}). 
-Again, the spatial features are a result of the stereotypical geometry of the images.
-
-\subsection{The receptive fields of complex condition generalize on simpler conditions}
-Fig.~\ref{fig:barGraphs} shows the relative error for the estimates of the target LRV obtained using the linear model and AMA.
-We show the relative error of the estimates obtained using the AMA receptive fields from all conditions.
-The receptive fields from a more complex condition perform at par on the stimuli from a simpler condition.
-The optimal AMA estimates are better than that of the linear model.
+Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA linear receptive fields for test [or training] stimuli.
+Here, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
+Recall, however, that performance is based on six rather than two receptive fields.
+Inclusion of more receptive fields reduces the ambiguity visible in the responses of just the first two.
 
@@
 \centering
-\begin{subfigure}{0.22 \textwidth}
-	\caption{Condition 1}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure15/Figure15_a.pdf}
-	\label{fig:case1Bar}
-    \end{subfigure}
-    ~ 
-    \begin{subfigure}{0.22 \textwidth}   
-	\caption{Condition 2}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure15/Figure15_b.pdf}
-	\label{fig:case2Bar}
-    \end{subfigure}
-    ~ 
-        \begin{subfigure}{0.22 \textwidth}
-	\caption{Condition 3}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure15/Figure15_c.pdf}
-	\label{fig:case3Bar}
-    \end{subfigure}
-    ~ 
-        \begin{subfigure}{0.22 \textwidth}
-	\caption{Condition 4}
-	\includegraphics[width=\textwidth]{../FiguresDraft4/Figure15/Figure15_d.pdf}
-	\label{fig:case4Bar}
-    \end{subfigure}
-\caption{{\bf Comparison of optimal RFs across cases:} Comparison of optimal AMA receptive fields from one condition on the images of other cases.
-Each panel shows the relative error estimates on the same set of images obtained using the receptive fields of the four cases (condition 1-4).
-(a) Error estimates for images of condition 1.
-The AMA receptive fields from all three cases perform well in this case.
-(b) Error estimates for images of condition 2.
-As expected, the best estimates are provided by the receptive fields of condition 2.
-(c) Error estimates for images of condition 3.
-(d) Error estimates for images of condition 4.}
+\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure13/Figure13_a.pdf}
+\caption{{\bf Comparison of LRV estimates:} Error estimates}
  \label{fig:barGraphs}

### 2018-04-25 Draft4/draft4.tex
Today’s edits

@@
 
-%\subsection{Performance evaluation}
-%
-%To evaluate the performance of our luminance constancy methods, we generated test sets as new random draws from our statistical models.
-%For each test image, we quant we summarized performance as the relative mean squared estimation error.
-%If $\hat{Y}$ is the estimated luminance corresponding to the assigned luminance $Y$, the error of the luminance estimates is quantified as the relative error ($E_{\rm rel}$) defined as: $E_{\rm rel}^2 = \left\langle\left((\hat{Y}-Y)/Y\right)^2\right\rangle$.
-
 \section{Results} \label{Results}
@@
 
+Figure~\ref{fig:barGraphs} summarizes luminance constancy performance across the conditions, for both AMA and linear regression. 
+We quantified overall performance in terms of overall relative root mean squared estimation error (relative RMSE) for the test set.
+If $\hat{Y}$ is the estimated LRV and $Y$ is the true LRV, the relative RMSE is ($E_{\rm rel}$) defined as $E_{\rm rel} = \sqrt{\left\langle\left((\hat{Y}-Y)/Y\right)^2\right\rangle}$,
+where the expectation is taken over all test stimuli at all LRVs.
+The height of each bar gives the relative RMSE for each method and condition.
+Note first that AMA improves upon linear regression for all conditions but the first, where performance for both methods is essentially perfect.
+This is expected since AMA makes optimal use of the stimulus information under a wider range
+of conditions than linear regression.
+Moreover, the linear regression method we use as a baseline here
+only has access to cone isomerizations at image locations corresponding to the target object, while AMA has access to isomerizations from the entire image patch.
+Second, the fact that performance for Condition 2 is very poor tells us that that when there is substantial intensity variation in the illuminant, achieving luminance constancy
+directly from the cone isomerizations is difficult.
+Performance improves greatly when we consider the same condition but when the cone isomerizations are contrast normalized. 
+Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
+Note, however, that Condition 2 does not include variation in the background surface reflectances.
+Such reflectances vary scene to scene in natural viewing.
+The results for Condition 3 show performance when we add such variation into the training and test sets.
+The error here represents the overall level of luminance constancy that our methods achieve for the
+most realistic condition that we tested.
+
 % Figure Error Bar Graphs
@@
 In this paper, we studied luminance constancy using naturalistic images.
-We used a software pipeline called  Virtual world color constancy (VWCC), which was developed for this work, to generate datasets of multispectral images labeled by the luminance of a target object in each image.
+We used a software pipeline, which was developed for this work, to render datasets of multispectral images from scene descriptions.
+Because we rendered the images, we were able to labeled each image by the luminance reflectance value (LRV) of a target object
+Across images, we varied the LRV of the target object and its relative surface reflectance spectrum, the spectral power distributions of the light sources, and the reflectance
+spectra of the background objects in the scene.
+This variation was based on statistical models of natural surface reflectance and illumination spectra.
+We used the labeled datasets to learn estimators for target object LRV.
+We studied the performance of these estimators as we systematically manipulated the spectral variations in the datasets.
+
+ima labeled by the luminance of a target object in each image.
 VWCC creates 2D multispectral images of 3D scenes based on information provided by the user.

### 2018-04-26 Draft4/draft4.tex
small edits

@@
 We used one fixed base scene and inserted a target object of fixed shape and size into this scene.
-We generated five distinct datasets: Conditions 0 through 4.
+We generated three distinct datasets: Conditions 1-3.
 Across these datasets the luminance constancy problem, estimating the target object LRV,
@@
 
-In Condition 0, the only source of stimulus variation was in the task relevant quantity, the target object LRV.
-Here, we fixed target object color (i.e. the relative reflectance spectrum of the target object),
-the reflectance spectra of the background objects, and the spectral power distributions of the light sources.
-We used 10 LRV values, equally spaced between 20 and 60.
-Condition 0 defines a baseline. In this condition, all images with the the same value of the LRV are identical.
+%In Condition 0, the only source of stimulus variation was in the task relevant quantity, the target object LRV.
+%Here, we fixed target object color (i.e. the relative reflectance spectrum of the target object),
+%the reflectance spectra of the background objects, and the spectral power distributions of the light sources.
+% Condition 0 defines a baseline. In this condition, all images with the same value of the LRV are identical.
 
-In the remaining conditions, we systematically introduced variation in scene factors other than the target object LRV.
-In Condition 1, we introduced variation in target object color but held the other factors fixed.
-
-Conditions 2, 3 and 4 each increase the variation relative to Condition 1.
-In Condition 2, in addition to the color of the target object,
-we varied the reflectance spectra of the background objects
-while holding the the spectral power distribution of the light sources
-constant.
-In Condition 3, in addition to the color of the target object,
-we varied the spectral power distribution of the light sources
-while holding the reflectance spectra of the background objects constant.
-Finally, in Condition 4 we varied all three factors (target object color,
-reflectance spectra of the background objects, spectral power distribution of the light sources).
+In Condition 1, we only varied the surface reflectance spectrum of the target object.
+The reflectance spectra of the background objects, and the spectral power distributions of the light sources were kept fixed.
+In Condition 2, in addition to the reflectance spectrum of the target object,
+we also varied the spectral power distribution of the light sources.
+Finally, in Condition 3 we varied all three factors (target object surface 
+reflectance spectrum, reflectance spectra of the background objects, 
+spectral power distribution of the light sources).
+We used 10 LRV values, equally spaced between 20 and 60 and generated 100 target surface reflectance spectra at these values. 
+The surface reflectance spectra at the same LRV could differ in their relative shape.
 The variation within our datasets captures the essence of the computational problem of lightness constancy

### 2018-04-26 Draft4/draft4.tex
edits and figures

@@
 But, the human visual system has the ability to stably perceive the object's color invariant of the context variations. 
-The mechanism of this behaviorally significant invariance detection ability remains largely unknown.
-To understand the computational principles that lead to such invariant perception, we study the perception of LRV under spectral variations in 3D scenes.
-Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the perceived luminance of an object.
-We have developed a software that generates naturalistic multispectral images of 3D scenes with precise control over the geometrical and spectral properties of the constituents that make a scene.
-We label these images with the luminance of a specific object in the scene.
-Next, we simulate the response of the retinal cones to these multispectral images using an accurate model of the early visual system.
-We then use supervised learning methods on these labeled cone responses to identify the computations that lead to accurate luminance estimation.
-We show that if only either target, or background, or illumination spectra are allowed to vary, the standard luminance can be estimated through simple transformations of the cone responses.
-When all the spectra vary simultaneously, while it is not easy to recover the luminance through simple transformations, a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and S cones can recover the luminance within about 15\% RMSE.}
+While this invariance detection ability is behaviorally very significant, its mechanism remains largely unknown. 
+To understand the computational principles that lead to invariant color perception, 
+here we study the perception of object light reflectance value (LRV) under variations in naturalistic scenes. 
+Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the 
+perceived LRV of a target object. 
+We have developed a software that renders naturalistic multispectral images of 3D scenes.
+The software provides precise control over the geometrical and spectral factors that make a scene. 
+We label the rendered images with the luminance of a specific object in the scene. 
+Next, we simulate the response of the retinal cones to these multispectral images using 
+an accurate model of the early visual system. 
+We then use supervised learning methods on these labeled cone responses to 
+identify the computations that lead to accurate LRV estimation under changes in spectral condition. 
+We show that if only either target or target and illumination spectra are allowed to vary, the standard luminance can be estimated through simple transformations of the cone responses. 
+When all the spectra vary simultaneously, while it is not easy to recover the luminance through simple transformations, 
+a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and  
+S cones can recover the luminance within about 13\% RMSE.}
 
@@
     \centering
-	\caption{}
+	\caption{Granada dataset}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_a.pdf}
@@
     \centering
-        \caption{}
+        \caption{Statistical model}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_b.pdf}
@@
     \centering
-        \caption{}
+        \caption{CIE xy chromaticity}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_c.pdf}
@@
     \centering
-        \caption{}
+        \caption{Color swatches}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_d.pdf}
@@
 To obtain illuminant spectra with intensity variation similar to the Granada dataset, we scaled each randomly generated relative spectrum.
-We obtained each scale factor by randomly sampling (with replacement) a spectrum from the Granda dataset and taking its mean. 
+The scale factors we sampled at random in the range 0.15 and 150.
 Color swatches of samples of illuminant spectra are shown in Figure~\ref{fig:sRGBIlluminant}.
@@
     \centering
-            \caption{}
+            \caption{Munsell and Vrhel dataset}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_a.pdf}
@@
     \centering
-        \caption{}
+        \caption{Statistical model}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_b.pdf}
@@
     \centering
-    \caption{}
+    \caption{CIE xy chromaticity}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_c.pdf}
@@
     \centering
-        \caption{}
+        \caption{Color swatches}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_d.pdf}
@@
 
-\begin{figure}
-\centering
-            \begin{subfigure}[b]{0.25 \textwidth}
-        \caption{LRV estimates}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft4/Figure10/Figure10_a.pdf}
-        \label{fig:case1Estimates}
-    \end{subfigure} 
-        \begin{subfigure}[b]{0.26 \textwidth}
-        \caption{Receptive field response}
-        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure10/Figure10_d.pdf}
-        \label{fig:case1RFResponse}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.28 \textwidth}
-	\caption{AMA receptive fields}
-	\includegraphics[width=1.07\textwidth, trim={0 -0.6cm 0 -0.3cm}]{../FiguresDraft4/Figure10/Figure10_c.pdf}
-	\label{fig:case1RFs}
-    \end{subfigure}   
-    \caption{{\bf RF response and luminance estimates for condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
-We show the response for the images in the training set.
-Each response cloud represents the response of images corresponding to one LRV.
-The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(b)  Estimated v/s assigned target LRV for the image in condition 1.
-Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
-Relative error of estimation is 0.8\% (Linear regression) and 1.1\% (AMA) .
-The diagonal unit slope (blue dotted) line is for reference.
-The standard deviations are too small to be visible.}
-\label{fig:Condition1}
-\end{figure}
-
 We start with Condition 1, where only the LRV and relative reflectance spectrum of the target object vary across scenes.
@@
 
-%% Figure 12: Results for Condition 3
-\begin{figure}
-\centering
-            \begin{subfigure}[b]{0.25 \textwidth}
-        \caption{LRV estimates}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft4/Figure12/Figure12_a.pdf}
-        \label{fig:case3Estimates}
-    \end{subfigure} 
-        \begin{subfigure}[b]{0.26\textwidth}
-        \caption{Receptive field response}
-        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure12/Figure12_d.pdf}
-        \label{fig:case3RFResponse}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.28 \textwidth}
-	\caption{AMA receptive fields}
-	\includegraphics[width=1.07\textwidth, trim={0 -0.6cm 0 -0.5cm}]{../FiguresDraft4/Figure12/Figure12_c.pdf}
-	\label{fig:case3RFs}
-    \end{subfigure}       \caption{{\bf RF response and luminance estimates for condition 3:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
-We show the response for the images in the training set.
-Each response cloud represents the response of images corresponding to one LRV.
-The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(b)  Estimated v/s assigned target LRV for the image in condition 1.
-Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
-The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.
-The diagonal unit slope (blue dotted) line is for reference.
-The standard deviations are too small to be visible.}
-\label{fig:Condition3}
-\end{figure}
-
 In Condition 3, we introduced variation in the reflectance spectra of the background objects.
@@
 Figure~\ref{fig:barGraphs} summarizes luminance constancy performance across the conditions, for both AMA and linear regression. 
-We quantified overall performance in terms of overall relative root mean squared estimation error (relative RMSE) for the test set.
-If $\hat{Y}$ is the estimated LRV and $Y$ is the true LRV, the relative RMSE is ($E_{\rm rel}$) defined as $E_{\rm rel} = \sqrt{\left\langle\left((\hat{Y}-Y)/Y\right)^2\right\rangle}$,
+We quantified overall performance in terms of overall relative root mean squared estimation error (relative RMSE) for the test set defined as:
+\begin{align}
+E_{\rm rel} = \sqrt{\left\langle\left(\frac{\rm{LRV_{Estimated}-LRV_{True}}}{\rm{LRV_{True}}}\right)^2\right\rangle}
+\label{eq:relRMSe}
+\end{align}
 where the expectation is taken over all test stimuli at all LRVs.
@@
 We used a software pipeline, which was developed for this work, to render datasets of multispectral images from scene descriptions.
-Because we rendered the images, we were able to labeled each image by the luminance reflectance value (LRV) of a target object
-Across images, we varied the LRV of the target object and its relative surface reflectance spectrum, the spectral power distributions of the light sources, and the reflectance
-spectra of the background objects in the scene.
-This variation was based on statistical models of natural surface reflectance and illumination spectra.
+Because we rendered the images, we were able to labeled each image by the luminance reflectance value (LRV) of a target object.
+Across images, we varied the LRV of the target object, its relative surface reflectance spectrum, 
+the spectral power distributions of the light sources, and the reflectance spectra of the background objects in the scene.
+These variations were based on statistical models of natural surface reflectance and illumination spectra.
 We used the labeled datasets to learn estimators for target object LRV.
-We studied the performance of these estimators as we systematically manipulated the spectral variations in the datasets.
+We studied the performance of these estimators as we systematically manipulated the 
+spectral variations in the datasets.
+We show that the target object LRV can be recovered almost perfectly if only the target 
+object spectrum or the target object spectrum and the illuminant spectra varies.
+In the first case, the LRV can be estimated from the cone isomerizations and in the second case 
+from the cone isomerization contrast between the target and the background objects.
+If, in addition, the background object spectra also vary, the cone contrast no longer 
+proportional to the target object LRV.
+In this case, the estimators can predict the LRV with relative RMSE ~13\%.
 
-ima labeled by the luminance of a target object in each image.
-VWCC creates 2D multispectral images of 3D scenes based on information provided by the user.
-Such information include the shape of the 3D space, the shape, size, position and material properties of the objects and light sources in the scene.
-In our work, we assigned these geometrical and spectral properties using random sampling from available databases of natural objects and light sources.
-Thus, we generated a large database of labeled hyper-spectral images, with naturalistic scene properties, where we have the ground truth information about every surface and light source.
-Such databases, of even a few images, are nearly impossible to obtain for natural scenes.
-This is because it is very hard to measure the surface reflectance and the illumination spectrum at every point in a scene, even for well controlled lab environments.
+The variability in the final condition results from changes in background object spectra.
+Change in background object spectra can affect the estimation in two ways.
+First, it will effect the estimation of average background isomerization in the contrast estimation.
+Second, it can also effect the total isomerization in cones corresponding to the target object through 
+secondary reflections from the background objects.
+While the first effect can be minimized by a better sampling of the background, 
+the effect of secondary reflections can not be removed through simple manipulations.
+This effect has largely been ignored in the field. 
+We show that such effects are significant.
 
-We used the software generated labeled images in a supervised manner to understand luminance constancy under four types of spectral manipulations (Fig.~\ref{fig:introExampleFigure}-Fig.~\ref{fig:studiedCases}).
-We found that target LRV can be recovered through simple manipulation of the retinal cone responses for cases where the spectral manipulations are restricted to at most two of the three possible sources of manipulations: the target object surface reflectance, the background object surface reflectances, or the light source illumination spectra.
-When variations are allowed only in the target object surface reflectance spectrum, or only the target object and the background objects surface reflectance spectra, the luminance can be estimated directly from the response of retinal cone photoreceptors.
-If the background spectra is fixed, but the target object reflectance spectrum and the light source illumination spectra are varying, the luminance can be obtained from the contrast between the cone response corresponding to the target and the background.
-When all three spectral variations are allowed simultaneously, one needs additional information to obtain the target LRV.
-
-Summary
-
-Effect of background. multiple reflection
-
-center surround RFs
-
-LM
+A major reason that such effects have been ignored in the study of color constancy is that we have 
+lacked tools through which their effects could be quantified.
+In this regard, a major contribution of this work has been to develop a computational package that
+produces naturalistic images with precise control over all factors that define the scene in the image.
+With this software we can systematically vary these factors and precisely quantify their effects on constancy.
 
@@
 
-% NOT SURE WE NEED ANY OF THIS.  PROBABLY NOT HERE IF WE DO
-%Even within the special case of luminance constancy, there are many scene manipulations that could be considered.
-The set of manipulations we focus on here are illustrated by Fig.~\ref{fig:introExampleFigure} and the three panels of Fig.~\ref{fig:studiedCases}.
-These conditions are: 1.
-variation in target object spectrum with fixed light source and background objects spectra (Fig.~\ref{fig:introExampleFigure}), 2.
-variation in target object spectrum and background objects spectra, with fixed light source  (Fig.~\ref{fig:backgroundVarying}), 3.
-variations in both the target object spectrum and the light source spectra, with fixed background object spectra (Fig.~\ref{fig:targetIlluminantVarying}), and 3.
-variations in all three types of spectra (target object, light source, and background objects) (Fig.~\ref{fig:allSpectraVarying}).
-Across real scenes, there will also be variations in the shape of the target object, its pose, eye position, etc.
-(see \nameref{Methods}).
-In this paper, we focus on the problem of luminance constancy within scene ensembles where these geometric factors are held fixed.
-%
-%We show that for conditions that have spectral variation only either in target object surface reflectance or background object surface reflectance or the power spectrum of the light sources, luminance can be estimated by simple transformations of the cone responses.
-For variations only in target object reflectance spectra (Condition 1) or just the target and background objects reflectance spectra (Condition 2), LRV can be recovered directly from the light reflected off the target object.
-For Condition 3, where both the target object reflectance and light source spectra vary, LRV can be recovered from the contrast between the target and the background.
-When all the spectral features in the scene are allowed to change (Condition 4), the standard luminance can not be recovered simply from the cone response or the contrast.
-We have used AMA with a Bayesian estimator to estimate standard luminance of the target object.
-Using this method, we can recover the luminance of the target object with $\sim 15\%$ relative root mean square error.
-Our analysis shows that the optimal receptive fields for estimating the luminance of the target object show a center surround structure, supporting a comparison between the light coming from the target object and its surround.
-Additionally, luminance estimation involves a weighted sum of the L, M and S cone responses where the receptive fields give more weight to the L and M cone responses compared to S cone responses.
-Comparing the performance of the RFs learnt using  one condition on the cone response of other conditions shows that the receptive field of the complex conditions perform well on images of simpler conditions.
-We discuss the implications of such receptive fields on luminance constancy.
-
 \bibliography{references}

### 2018-04-26 codeForFigures/codeToMakeFigures/illuminantGeneration.m

@@ -1,0 +1,156 @@
+% Illuminance Generation example
+
+% Clear
+clear; %close all;
+
+% Desired wl sampling
+nIlluminances = 100;
+
+S = [400 5 61];
+theWavelengths = SToWls(S);
+%% Load Granada Illumimace data
+load daylightGranadaLong
+daylightGranadaOriginal = SplineSrf(S_granada,daylightGranada,S);
+
+% Rescale spectrum by its mean
+meanDaylightGranada = mean(daylightGranadaOriginal);
+daylightGranadaRescaled = bsxfun(@rdivide,daylightGranadaOriginal,meanDaylightGranada);
+
+%% Center the data for PCA
+meandaylightGranadaRescaled = mean(daylightGranadaRescaled,2);
+daylightGranadaRescaledMeanSubtracted = bsxfun(@minus,daylightGranadaRescaled,meandaylightGranadaRescaled);
+
+%% Analyze with respect to a linear model
+B = FindLinMod(daylightGranadaRescaledMeanSubtracted,6);
+ill_granada_wgts = B\daylightGranadaRescaledMeanSubtracted;
+mean_wgts = mean(ill_granada_wgts,2);
+cov_wgts = cov(ill_granada_wgts');
+
+%% Generate some new illuminants
+nNewIlluminaces = nIlluminances;
+newIlluminance = zeros(S(3),nNewIlluminaces);
+newIndex = 1;
+
+scaling = 0;
+
+for i = 1:nNewIlluminaces
+    OK = false;
+    while (~OK)
+        ran_wgts = mvnrnd(mean_wgts',cov_wgts)';
+        ran_ill = B*ran_wgts+meandaylightGranadaRescaled;
+        if (all(ran_ill >= 0))
+            newIlluminance(:,newIndex) = ran_ill;
+            if scaling
+                newIlluminance(:,newIndex) = newIlluminance(:,newIndex)*...
+                        (meanDaylightGranada(randi(length(meanDaylightGranada))));
+            end
+            newIndex = newIndex+1;
+            OK = true;
+        end        
+    end
+%     filename = sprintf('illuminance_%03d.spd',i);
+%     fid = fopen(fullfile(folderToStore,filename),'w');
[…]

### 2018-04-26 codeForFigures/codeToMakeFigures/reflectanceGeneration.m

@@ -1,0 +1,167 @@
+% Clear
+clear;
+targetGenerationFigure;
+clearvars -except thetargetReflectanceImage TargetxyY targetSurfaces luminanceLevels
+
+% Desired wl sampling
+nSurfaces = 100;
+
+S = [400 5 61];
+theWavelengths = SToWls(S);
+% Munsell surfaces
+load sur_nickerson
+sur_nickerson = SplineSrf(S_nickerson,sur_nickerson,S);
+
+% Vhrel surfaces
+load sur_vrhel 
+sur_vrhel = SplineSrf(S_vrhel,sur_vrhel,S);
+
+% Put them together
+sur_all = [sur_nickerson sur_vrhel];
+sur_mean=mean(sur_all,2);
+sur_all_mean_centered = bsxfun(@minus,sur_all,sur_mean);
+
+%% Analyze with respect to a linear model
+B = FindLinMod(sur_all_mean_centered,6);
+sur_all_wgts = B\sur_all_mean_centered;
+mean_wgts = mean(sur_all_wgts,2);
+cov_wgts = cov(sur_all_wgts');
+
+%% Generate some new surfaces
+newSurfaces = zeros(S(3),nSurfaces);
+newIndex = 1;
+
+for i = 1:nSurfaces
+    OK = false;
+    while (~OK)
+        ran_wgts = mvnrnd(mean_wgts',cov_wgts)';
+        ran_sur = B*ran_wgts+sur_mean;
+        if (all(ran_sur >= 0) & all(ran_sur <= 1))
+            newSurfaces(:,newIndex) = ran_sur;
+            newIndex = newIndex+1;
+            OK = true;
+        end
+    end
+%     filename = sprintf('reflectance_%03d.spd',i);
+%     fid = fopen(fullfile(folderToStore,filename),'w');
+%     fprintf(fid,'%3d %3.6f\n',[theWavelengths,newSurfaces(:,i)]');
+%     f%close(fid);
+end    
+
+%% Load in the T_xyz1931 data for luminance sensitivity
+theXYZData = load('T_xyz1931');
+theLuminanceSensitivity = SplineCmf(theXYZData.S_xyz1931,theXYZData.T_xyz1931,theWavelengths);
[…]

### 2018-04-26 codeForFigures/codeToMakeFigures/targetGenerationFigure.m

@@ -1,0 +1,143 @@
+% Illuminance Generation example
+
+% Clear
+% clear; %close all;
+
+% Desired wl sampling
+luminanceLevels = [0.2:0.4/9:0.6];
+reflectanceNumbers = (1:10);
+nSurfaceAtEachLuminace = 10;
+
+S = [400 5 61];
+theWavelengths = SToWls(S);
+% Munsell surfaces
+load sur_nickerson
+sur_nickerson = SplineSrf(S_nickerson,sur_nickerson,S);
+
+% Vhrel surfaces
+load sur_vrhel 
+sur_vrhel = SplineSrf(S_vrhel,sur_vrhel,S);
+
+% Put them together
+sur_all = [sur_nickerson sur_vrhel];
+sur_mean=mean(sur_all,2);
+sur_all_mean_centered = bsxfun(@minus,sur_all,sur_mean);
+
+%% Analyze with respect to a linear model
+B = FindLinMod(sur_all_mean_centered,6);
+sur_all_wgts = B\sur_all_mean_centered;
+mean_wgts = mean(sur_all_wgts,2);
+cov_wgts = cov(sur_all_wgts');
+
+%% Load in the T_xyz1931 data for luminance sensitivity
+theXYZData = load('T_xyz1931');
+theLuminanceSensitivity = SplineCmf(theXYZData.S_xyz1931,theXYZData.T_xyz1931(2,:),theWavelengths);
+
+theIlluminantData = load('spd_D65');
+theIlluminant = SplineSpd(theIlluminantData.S_D65,theIlluminantData.spd_D65,theWavelengths);
+theIlluminant = theIlluminant/(theLuminanceSensitivity*theIlluminant);
+
+
+%% Generate new surfaces
+targetSurfaces = zeros(S(3),size(luminanceLevels,2)*nSurfaceAtEachLuminace);
+newIndex = 1;
+
+m=0;
+for i = 1:(size(luminanceLevels,2)*nSurfaceAtEachLuminace)
+    m=m+1;
+    OK = false;
+    while (~OK)
+        ran_wgts = mvnrnd(mean_wgts',cov_wgts)';
+        theReflectance = B*ran_wgts+sur_mean;
+        theLightToEye = theIlluminant.*theReflectance;
+        theLuminance = theLuminanceSensitivity*theLightToEye;
+        theLuminanceTarget = luminanceLevels(ceil(i/nSurfaceAtEachLuminace));
[…]

### 2018-04-30 Draft4/draft4.tex
more small edits

@@
 We used a software pipeline, which was developed for this work, to render datasets of multispectral images from scene descriptions.
-Because we rendered the images, we were able to labeled each image by the luminance reflectance value (LRV) of a target object.
+Because we rendered the images, we were able to label each image by the luminance reflectance value (LRV) of a target object.
 Across images, we varied the LRV of the target object, its relative surface reflectance spectrum, 
@@
 from the cone isomerization contrast between the target and the background objects.
-If, in addition, the background object spectra also vary, the cone contrast no longer 
+If, in addition, the background object spectra also vary, the cone contrast is no longer 
 proportional to the target object LRV.
-In this case, the estimators can predict the LRV with relative RMSE ~13\%.
+In this case, the AMA estimator we used in this work can predict the LRV to within ~13\% (relative RMSE).
 
-The variability in the final condition results from changes in background object spectra.
-Change in background object spectra can affect the estimation in two ways.
-First, it will effect the estimation of average background isomerization in the contrast estimation.
-Second, it can also effect the total isomerization in cones corresponding to the target object through 
-secondary reflections from the background objects.
-While the first effect can be minimized by a better sampling of the background, 
+The variability in the final condition results from changes in background object spectra, which affects the estimation in two ways.
+First, it effects the estimation of cone contrast due to the variability in the background.
+Second, it also effects the cone isomerizations corresponding to the target object through 
+variability in secondary reflections from the background objects.
+While the first effect can be minimized by a representative sampling of the background, 
 the effect of secondary reflections can not be removed through simple manipulations.
@@
 
-A major reason that such effects have been ignored in the study of color constancy is that we have 
-lacked tools through which their effects could be quantified.
-In this regard, a major contribution of this work has been to develop a computational package that
-produces naturalistic images with precise control over all factors that define the scene in the image.
+The reason such effects have been ignored is that we have lacked tools to quantify their effects.
+In this regard, a major contribution of this work is the development of a computational package to
+produce naturalistic images with precise control over factors defining the scene.
 With this software we can systematically vary these factors and precisely quantify their effects on constancy.

### 2018-05-01 Draft4/draft4.tex
relative RMSE definition in words

@@
 Figure~\ref{fig:barGraphs} summarizes luminance constancy performance across the conditions, for both AMA and linear regression. 
-We quantified overall performance in terms of overall relative root mean squared estimation error (relative RMSE) for the test set defined as:
-\begin{align}
-E_{\rm rel} = \sqrt{\left\langle\left(\frac{\rm{LRV_{Estimated}-LRV_{True}}}{\rm{LRV_{True}}}\right)^2\right\rangle}
-\label{eq:relRMSe}
-\end{align}
-where the expectation is taken over all test stimuli at all LRVs.
+We quantified overall performance in terms of overall relative root mean squared estimation error (relative RMSE) for the test set.
+The relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
+The mean is taken over all stimuli in the test set.
+%\begin{align}
+%E_{\rm rel} = \sqrt{\left\langle\left(\frac{\rm{LRV_{Estimated}-LRV_{True}}}{\rm{LRV_{True}}}\right)^2\right\rangle}
+%\label{eq:relRMSe}
+%\end{align}
+%where the expectation is taken over all test stimuli at all LRVs.
 The height of each bar gives the relative RMSE for each method and condition.

### 2018-05-01 Draft4/draft4.tex
Today’s edits, onwards to discussion!!!!!!!

--- 2018-04-30 Draft4/draft4.tex
@@
 
-Figure~\ref{fig:barGraphs} summarizes luminance constancy performance across the conditions, for both AMA and linear regression. 
-We quantified overall performance in terms of overall relative root mean squared estimation error (relative RMSE) for the test set defined as:
-\begin{align}
-E_{\rm rel} = \sqrt{\left\langle\left(\frac{\rm{LRV_{Estimated}-LRV_{True}}}{\rm{LRV_{True}}}\right)^2\right\rangle}
-\label{eq:relRMSe}
-\end{align}
-where the expectation is taken over all test stimuli at all LRVs.
-The height of each bar gives the relative RMSE for each method and condition.
-Note first that AMA improves upon linear regression for all conditions but the first, where performance for both methods is essentially perfect.
-This is expected since AMA makes optimal use of the stimulus information under a wider range
-of conditions than linear regression.
-Moreover, the linear regression method we use as a baseline here
-only has access to cone isomerizations at image locations corresponding to the target object, while AMA has access to isomerizations from the entire image patch.
-Second, the fact that performance for Condition 2 is very poor tells us that that when there is substantial intensity variation in the illuminant, achieving luminance constancy
-directly from the cone isomerizations is difficult.
-Performance improves greatly when we consider the same condition but when the cone isomerizations are contrast normalized. 
-Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
-Note, however, that Condition 2 does not include variation in the background surface reflectances.
-Such reflectances vary scene to scene in natural viewing.
-The results for Condition 3 show performance when we add such variation into the training and test sets.
-The error here represents the overall level of luminance constancy that our methods achieve for the
-most realistic condition that we tested.
+\section{Discussion} \label{Discussion}
 
-% Figure Error Bar Graphs
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure13/Figure13_a.pdf}
-\caption{{\bf Comparison of LRV estimates:} Error estimates}
- \label{fig:barGraphs}
-\end{figure}
+\subsection{Summary}
 
-\section{Discussion} \label{Discussion}
 In this paper, we studied luminance constancy using naturalistic images.
@@
 These variations were based on statistical models of natural surface reflectance and illumination spectra.
-We used the labeled datasets to learn estimators for target object LRV.
+We used the labeled datasets to learn estimators for the target object LRV.
 We studied the performance of these estimators as we systematically manipulated the 
 spectral variations in the datasets.
-We show that the target object LRV can be recovered almost perfectly if only the target 
-object spectrum or the target object spectrum and the illuminant spectra varies.
-In the first case, the LRV can be estimated from the cone isomerizations and in the second case 
-from the cone isomerization contrast between the target and the background objects.
-If, in addition, the background object spectra also vary, the cone contrast is no longer 
-proportional to the target object LRV.
-In this case, the AMA estimator we used in this work can predict the LRV to within ~13\% (relative RMSE).
+
+Figure~\ref{fig:barGraphs} summarizes our main findings by plotting the overall relative root mean squared estimation error (relative RMSE) for each condition. 
+In Condition 1, where only the relative target object spectrum varies, luminance constancy is an easy problem and performance is essentially perfect for both the baseline linear regression and AMA methods.
+In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
+Indeed, neither of our methods performs well when they directly process the cone isomerizations.
+Performance with both methods improves greatly when the cone isomerizations are contrast normalized. 
+Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
+Linear regression does less well, in part because it only has access to cone isomerizations at image locations
+corresponding to the target object.
+In addition, AMA makes optimal use of the stimulus information across a wider range
+of conditions than linear regression.
+Condition 2, however, does not include scene to scene variation in the background surface reflectances
+as occurs in natural viewing.
+The results for Condition 3 show performance when we add such variation.
+Performance here represents the overall level of luminance constancy that our methods achieve for the
+most realistic condition that we tested.
+In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.
+
+% Figure Error Bar Graphs
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure13/Figure13_a.pdf}
+\caption{{\bf Summary of luminance constancy performance:} The plot shows the relative RMSE estimation error for each method and condition.The relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
+The mean is taken over all stimuli in the test set.}
+ \label{fig:barGraphs}
+\end{figure}
+
+\subsection{Importance of Background Variation}
+
+\subsection{Use of Virtual Scenes}
+
+\subsection{Limitations Future Directions}
+Geometric variations
+Material and texture variation
+Other dimensions of color space
+
+\subsection{Linking to Human Performance}
+Constancy indices
+Weber fractions
+Experiments with virtual scenes
 
 The variability in the final condition results from changes in background object spectra, which affects the estimation in two ways.
-First, it effects the estimation of cone contrast due to the variability in the background.
+First, it affects the estimation of cone contrast due to the variability in the background.
 Second, it also effects the cone isomerizations corresponding to the target object through 

### 2018-05-02 Draft4/draft4.tex
small edits
Today’s edits in discussion.

@@
 
+% Figure Error Bar Graphs
+\begin{figure}
+\centering
+\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure13/Figure13_a.pdf}
+\caption{{\bf Summary of luminance constancy performance:} The plot shows the relative RMSE estimation error for each method and condition.The relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
+The mean is taken over all stimuli in the test set.}
+ \label{fig:barGraphs}
+\end{figure}
+
 Figure~\ref{fig:barGraphs} summarizes our main findings by plotting the overall relative root mean squared estimation error (relative RMSE) for each condition. 
@@
 In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.
+Note that introduction of variation in the background surfaces makes the luminance constancy problem substantially harder,
+because variation in the background surfaces reduces the reliability of the light reflected from these
+surfaces.
+%% READ THIS PART
 
-% Figure Error Bar Graphs
-\begin{figure}
-\centering
-\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure13/Figure13_a.pdf}
-\caption{{\bf Summary of luminance constancy performance:} The plot shows the relative RMSE estimation error for each method and condition.The relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
-The mean is taken over all stimuli in the test set.}
- \label{fig:barGraphs}
-\end{figure}
-
-\subsection{Importance of Background Variation}
+%\subsection{Importance of Background Variation}
+%
+%
+%The variability in the final condition results from changes in background object spectra, which affects the estimation in two ways.
+%First, it affects the estimation of cone contrast due to the variability in the background.
+%Second, it also effects the cone isomerizations corresponding to the target object through 
+%variability in secondary reflections from the background objects.
+%While the first effect can be minimized by a representative sampling of the background, 
+%the effect of secondary reflections can not be removed through simple manipulations.
+%This effect has largely been ignored in the field. 
+%Our work shows that such effects are significant.
+%
+%The reason such effects have been ignored is that we have lacked tools to quantify their effects.
+%In this regard, a major contribution of this work is the development of a computational package to
+%produce naturalistic images with precise control over factors defining the scene.
+%With this software we can systematically vary these factors and precisely quantify their effects on constancy.
 
@@
 
-\subsection{Limitations Future Directions}
-Geometric variations
-Material and texture variation
-Other dimensions of color space
+\subsection{Future Directions}
+
+In the work presented here, we incorporated spectral variation into our statistical model
+of naturalistic scenes.
+It is natural to begin with spectral variation, because this variation is at the heart of
+what makes luminance constancy a rich computational problem.
+In natural scenes, however, there are other sources of variation that add additional
+richness.
+These include variation in non-spectral properties of objects and lighting in the scene, including
+object texture, material, and shape as well as lighting geometry.
+The methods we developed here may be generalized to study the effects of variation
+in these factors.
+The basic approach would be to incorporate the variation into the generation of the
+scenes and again learn estimators from the corresponding labeled images.
+A challenge for this approach will be to thoughtfully control the increase in problem
+complexity both to keep compute time feasible and to ensure that it is possible to
+extract meaningful insight from the results.
+
+Luminance constancy is a special case of the more general problem of color constancy.
+The approach we developed here could easily be generalized to the estimation of additional
+surface reflectance descriptors, such as object hue or chroma.
+As with LRV these descriptors would be defined by the light reflected from an object 
+under a standard illuminant.
+A further advance would be to develop methods for learning receptive fields that are
+optimal for multivariate estimation problems.
+With such methods one could directly estimate three-dimensional color descriptors.
 
 \subsection{Linking to Human Performance}
-Constancy indices
-Weber fractions
-Experiments with virtual scenes
 
-The variability in the final condition results from changes in background object spectra, which affects the estimation in two ways.
-First, it affects the estimation of cone contrast due to the variability in the background.
-Second, it also effects the cone isomerizations corresponding to the target object through 
-variability in secondary reflections from the background objects.
-While the first effect can be minimized by a representative sampling of the background, 
-the effect of secondary reflections can not be removed through simple manipulations.
-This effect has largely been ignored in the field. 
-We show that such effects are significant.
-
-The reason such effects have been ignored is that we have lacked tools to quantify their effects.
-In this regard, a major contribution of this work is the development of a computational package to
-produce naturalistic images with precise control over factors defining the scene.
-With this software we can systematically vary these factors and precisely quantify their effects on constancy.
+An important motivation for studying the computational problem of luminance constancy
+is to gain insight about human vision.
+The approach we developed can be used to make predictions of how humans would
+perform in a psychophysical task that probes the visual representation of object LRV.
+For example, one could study discrimination thresholds for target LRV using the
+stimuli that were generated with the methods used
+here.
+For example, we could ask how LRV discrimination thresholds are impacted by 
+spectral variation in the illuminant, the background objects, and in the target object itself.
+Comparing human thresholds with the precision of AMA-based estimates would then
+allow inferences about how well human observers make use of the information available
+in the images for performing the LRV discrimination task.
+We think experiments and analyses along these lines represent an important future direction.
+By coupling the experiments and analyses, we hope to advance our understanding
+of how we see objects in the real world in a principled and controlled manner.
 

### 2018-05-02 Draft4/draft4.tex
small edits

@@
 To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone isomerizations.
-Figure~\ref{fig:Condition2}(c, d)shows that performance improves greatly, and indeed is essentially perfect.
+Figure~\ref{fig:Condition2}(c, d) shows that performance improves greatly, and indeed is essentially perfect.
 This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
@@
 This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
-We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations.
-Figure~\ref{fig:case3Estimates} shows the results.
+We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations 
+(Figure~\ref{fig:case3Estimates}).
 The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions.

### 2018-05-03 Draft4/draft4.tex
went over the whole draft

@@
 The perceived color of an object has important behavioral implications, since color helps to identify objects and their properties \cite{Mollon89, Jacobs81}.
-[THIS PERCEIVED COLOR DEPENDS ON THE SURFACE REFLECTANCE OF THE OBJECT.]
-Perceived object color is not sensed directly. Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
+The perceived color depends on the surface reflectance of the object, but it is not sensed directly. 
+Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
 The computational challenge underlying object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
@@
 The ability of a visual system to extract such a stable representation is called color constancy. 
-[DO WE NEED THIS LINE -] Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
+%Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
 In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eye to produce percepts well-correlated with object surface reflectance.
@@
 Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
-Subsequent computational work considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}; LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
+Subsequent computational work considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}.
+%LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
 A key insight from this computational work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.
@@
     \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the object's surface reflectance of the object and the illumination.
-It also depends on geometric factors, such as the object's shape, pose, and position relative to the observer.
+    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and the illumination under which it lies.
+Additionally, it also depends on geometric factors, such as the object's shape, pose, and position relative to the observer.
 The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable, an ability called color constancy.
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-		\caption{Condition 2}
-		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
+		\caption{Condition 1}
+%		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
+		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.png}
  		\label{fig:backgroundVarying}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-        \caption{Condition 3}	
+        \caption{Condition 2}	
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.png}
@@
 	\begin{subfigure}[b]{0.33 \textwidth}
-	\caption{Condition 4}	
+	\caption{Condition 3}	
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.png}        
@@
 5 images are shown at each luminance level.
-We studied four types of spectral variations.
-Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed, (Fig.~\ref{fig:introExampleFigure}).
-(a) Condition 2: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable, (b) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 4: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
-As in Fig.~\ref{fig:introExampleFigure}, the spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
-Moreover, across the four panels (Fig.~\ref{fig:introExampleFigure} \& Fig.~\ref{fig:studiedCases}), spheres in corresponding locations have the same surface reflectance.
-In all four panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+We studied three types of spectral variations.
+(a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
+%Condition 2: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable, 
+(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
+The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
+Moreover, across the three panels, spheres in corresponding locations have the same surface reflectance.
+In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
 The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
@@
 The LRV is a measure of the overall amount of light reflected by a surface (\citeauthor{astm1121477}).
-More precisely, the LRV is the luminance of the light that would
-be reflected to the eye from an object with the specified surface reflectance function when the object is illuminated by a reference illuminant,
+More precisely, the LRV is the luminance of the light that would be reflected to the eye from an object with the 
+specified surface reflectance function when the object is illuminated by a reference illuminant,
 normalized by the luminance of the reference illuminant itself.
@@
 First we generate a labeled set of training images.
-Second we use a model of the early visual system the compute the responses of the cone photoreceptor mosaic to the labeled images.
+Second we use a model of the early visual system to compute the responses of the cone photoreceptor mosaic to the labeled images.
 Third we apply AMA to the cone responses to learn task-optimal receptive fields (RFs).
@@
 \subsection{Labeled training data} \label{method:VirtualWorld}
+\subsubsection{Virtual naturalistic scenes}
+The light that reflects from objects to the eyes depends on many factors.
+These include the surface reflectance, texture, material and geometry of the objects, 
+the spectral power distribution function of the illuminants, and the position of the observer.
+We have developed a rendering package 
+(\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}, \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}) 
+that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
+The package harnesses an open-source computer graphics renderer 
+\cite{jakob2015mitsuba} to produce physically-accurate images from the scene models.
+Because each image is rendered from a known scene model, each image pixel can be labeled with 
+the surface reflectance of the corresponding scene object.
+By incorporating statistical models of the variation of object surface reflectance and daylight illumination, 
+the pipeline allows us to produce large labeled sets of images that capture much of the task-relevant 
+statistical structure of natural scenes.
+
 % Figure 3
@@
     \end{subfigure}
-    \caption{{\bf Example of base scenes form the VWCC library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.
-The reflectance spectra of the distinct surfaces in each scene has been assigned randomly (see below) using the VWCC software.
-The light source spectra were also assigned randomly to the default and inserted light source.}\label{fig:baseScenes}
+    \caption{{\bf Base scenes from the Virtual World Color Constancy (VWCC) library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.
+The reflectance spectra of the distinct surfaces and the spectral power distribution function of the light sources in each scene have been assigned randomly (see text).}\label{fig:baseScenes}
 \end{figure}
-
-\subsubsection{Virtual naturalistic scenes}
-
-The light that reflects from objects to the eyes depends on many factors.
-These include the surface reflectance, texture, material and geometry of the objects, the spectra of the illuminants, and the position of the observer.
-We developed a rendering package (\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}, \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}) that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
-The package harnesses an open-source computer graphics renderer  \cite{jakob2015mitsuba} to produce physically-accurate images from the scene models.
-Because each image is rendered from a known scene model, each image pixel can be labeled with the surface reflectance of the corresponding scene object.
-By incorporating statistical models of the variation of object surface reflectance and daylight illumination, the pipeline allows us to produce large labeled sets of images that capture much of the task-relevant statistical structure of natural scenes.
 
@@
     \end{subfigure}
-\caption{{\bf Library base scene with inserted objects.} The rendering package was used to insert different objects into the library base scene, with each panel showing a different object.
-The objects were inserted at a location in the image and then the camera was pointed at the object, so that the object's image is at the center of the rendered image.
-In the figure panels, the full rendered image is cropped so that the inserted object is more visually salient.
-We use this capability of our software pipeline to insert target objects into scenes.}\label{fig:libraryWithTarget}
+\caption{{\bf The library base scene with inserted objects.} The rendering package can be used to insert objects into the base scenes.
+The panels show different objects inserted in the library base scene.
+The objects were inserted at a user defined location in the image and then the camera was pointed at the object so that the object is at the center of the rendered image.
+In these panels, the full rendered image has been cropped so that the inserted object is more visually salient.}\label{fig:libraryWithTarget}
 \end{figure}
-
-Our rendering package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
-Base scenes specify an arrangement of objects and light sources.
-Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}).
-Once the position, size and pose of the inserted objects has been set, our package allows the assignment of a surface reflectance function to each object in the scene and a spectral power distribution to each light source (Fig.~\ref{fig:VWCCTransformations}).
-This provides a complete scene model which can be rendered from any specified viewpoint.
 
@@
     \end{subfigure}
-    \caption{{\bf Transformations of the scene.} The possible transformations of the properties of a scene can broadly be classified into two groups: Geometrical (a-b) and Spectral (c-e).
-VWCC provides control over such transformation as illustrated by the columns.
-(a) The three panels in the column have the target object at three different positions.
-The camera points to the center of the pixel.
-(b) The target object in the three panels are at different orientations.
-(c) The target object surface reflectance varies across the three panels of the column.
-(d) The surface reflectance of the background objects varies across the three panels.
-In each panel, the reflectances were assigned randomly.
-(e) The power spectrum of the light sources were assigned randomly in the three panels.
+    \caption{{\bf Transformations of the scene.} The properties of a visual scene can broadly be classified into two groups: Geometrical (a-b) and Spectral (c-e).
+VWCC provides control over such properties as illustrated by the columns.
+(a) Variation in inserted object positions.
+(b) Variation in orientations.
+(c) Variation is the surface reflectance of the target object.
+(d) Variation in surface reflectance of the background objects.
+The reflectances were assigned randomly in each panel.
+(e) Variation in the spectral power distribution function of the light sources.
 \label{fig:VWCCTransformations}}
 \end{figure}
+
+Our rendering package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
+Base scenes specify an arrangement of objects and light sources.
+Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}).
+Once the position, size and pose of the inserted objects has been set, 
+our package allows the assignment of a surface reflectance function to each object in the scene 
+and a spectral power distribution function to each light source (Fig.~\ref{fig:VWCCTransformations}).
+This provides a complete scene model which can be rendered from any specified viewpoint.
 
@@
 Each dataset consisted of 1000 scenes and corresponding images.
-
-%In Condition 0, the only source of stimulus variation was in the task relevant quantity, the target object LRV.
-%Here, we fixed target object color (i.e. the relative reflectance spectrum of the target object),
-%the reflectance spectra of the background objects, and the spectral power distributions of the light sources.
-% Condition 0 defines a baseline. In this condition, all images with the same value of the LRV are identical.
 
@@
 
-% 1000 each Condition
-%Condition 0: Baseline
-%Condition 1: Target Color Only Variation
-%Condition 2: Target Color and Background
-%Condition 3: Target Color and Illuminant
-%Condition 4a: Target Color, Background and Relative Illuminant
-%Condition 4: Everything
-
-For the primary results, we used the ``{\it Library}'' base scene and a spherical target object .
-The library base scene contains X area lights. We inserted one additional spherical spherical light source into the scene.
-The position and size of the inserted object, inserted light source and viewpoint were held fixed across all scenes in the database,
-as shown in Figure~\ref{fig:3DScene}.
-Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra.
-We describe these models below.
+For the primary results, we used the ``{\it Library}'' base scene and a spherical target object.
+The library base scene contains 2 area lights. 
+We inserted one additional spherical spherical light source into the scene.
+The position and size of the inserted object, inserted light source and viewpoint were held fixed across all 
+scenes in the database, as shown in Figure~\ref{fig:3DScene}.
+Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra as described below.
 Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
-
-%% Fix the title capitalization in a and b
 \subsubsection{Illumination spectra}
@@
 
-To generate illumination spectra, we developed a statistical model of the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{hernandez2001color} and sample randomly from the model.
+To generate illumination spectra, we developed a statistical model of the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{hernandez2001color} and sampled randomly from the model (see appendix).
 The overall intensity of the measurements spans approximately three orders of magnitude.
@@
 
-Our statistical model approximates these normalized shapes using their first 6 principle components, and models the variation in these components with
-a 6-dimensional Gaussian whose mean and covariance matrix match the dataset's sample mean and covariance of the weights on these components \cite{BrainardFreeman}.
+Our statistical model approximates these normalized shapes using their first 6 principle components.
+The variation in these components is modeled with a 6-dimensional Gaussian whose mean and covariance matrix 
+match the dataset's sample mean and covariance of the weights on these components \cite{BrainardFreeman}.
 To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
@@
 \subsubsection{Surface reflectance spectra}
-%% Fix the title capitalization in a and b
 % Figure 7 Surface Reflectance Data and Model
@@
     \end{subfigure}
-    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.(b) Representative samples of object surface reflectances.
+    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.(b) Representative samples of randomly generated object surface reflectances.
 (c) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (black) and samples of surface reflectances (red).
@@
 The figure shows 10 random samples at 10 equally spaced LRV levels in the range [0.2, 0.6].
-This range captures more than 90\% of the natural surface reflectances.
 Each row contains 10 random samples of reflectance spectra generated at the LRV shown on the left.}
@@
 We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
-measurements to create a database containing 632 reflectance spectra Figure~\ref{fig:reflectanceSpectra}.
-The Munsell database contains 462 spectra each measured at 5nm sampling intervals between 380nm and 780nm.
-The Vrhel dataset contains 170 spectra measured at 2nm sampling between 390nm and 730 nm.
-We resampled these spectra to 31 evenly-spaced wavelengths between $400$nm and $700$nm.
+measurements to create a database containing 632 reflectance spectra (Figure~\ref{fig:reflectanceSpectra}).
+The Munsell database contains 462 spectra each measured at 5 nm sampling intervals between 380nm and 780nm.
+The Vrhel dataset contains 170 spectra measured at 2 nm sampling between 390 nm and 730 nm.
+We resampled these spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
 Figure~\ref{fig:reflectanceSpectra} illustrates the spectra of draws obtained using this procedure.
@@
 
-For generating the target object reflectance at a particular luminance $(Y_{\rm T})$, the values in a generated spectrum were 
+For generating the target object reflectance at a particular luminance, the values in a generated spectrum were 
 scaled such that the LRV had the desired value (see appendix).
@@
 The target object is placed in the camera field of view.
-After assigning spectra to the light sources and other other objects in the scene, a multispectral image of the scene is rendered using the Mitsuba software package.
+After assigning spectra to the light sources and other objects in the scene, a multispectral image of the scene is rendered using the Mitsuba software package.
 (b) The central portion of the rendered image, which contains the target object, is cropped from the image.
-(c) The retinal image incident on the cone mosaic after optical blurring and the location and the identity of the cones (L cones: Red, M cones: Green, S cones: Blue).
+(c) The response of the cones in the retina are simulated using the retinal image incident on the cone mosaic.
+The figure shows the retinal image after optical blurring and the location and identity of the cones in the retinal mosaic (L cones: Red, M cones: Green, S cones: Blue).
 (d) The cone responses are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
@@
 \subsection{Model of early visual system} \label{method:Isetbio}
-
 The light entering the eye is blurred by the eye's optics.
@@
 We focussed our analysis on regions of the image local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
-This choice is motivated by the observation that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
+This choice is motivated by the observation that neural receptive fields in the early visual pathways (e.g., retina, primary visual cortex) pool information locally.
 In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle (REFS).
@@
 
-We modeled a visual system with a pupil diameter of 3 mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image (REF whatever optics model), spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (Brainard mosaic review; Fig.~\ref{fig:croppedImageWithMosaic}).
-The cone mosaic contained  L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard (REF).
-Cone isomerizations were computed assuming an integration time of 5 msec, and we modeled the Poisson nature of photopigment isomerization (REF Hecht et al).
-This modeling was implemented using the software infrastructure provided by ISETBio (REF).
+We modeled a visual system with a pupil diameter of 3 mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
+The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
+Cone isomerizations were computed assuming an integration time of 100 msec, and we modeled the Poisson nature of photopigment isomerization \cite{hecht1942energy}. 
+This modeling was implemented using the software infrastructure provided by ISETBio \cite{brainard2015isetbio}.
 
@@
 we processed the isomerizations as follows:
-First, we generated a response for each cone class at each pixel in the sampled retinal image, using bilinear interpolation separately for each cone class.
+First, we generated a response for each cone class at each pixel in the sampled retinal image, using linear interpolation separately for each cone class.
 This gives us a cone response image for each cone class.
@@
     \end{subfigure}   
-    \caption{{\bf RF response and luminance estimates for condition 1:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
-We show the response for the images in the training set.
-Each response cloud represents the response of images corresponding to one LRV.
-The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(b)  Estimated v/s assigned target LRV for the image in condition 1.
+    \caption{{\bf Luminance estimates, receptive fields and RF response for condition 1:} (a) Estimated v/s assigned target LRV for the test image in condition 1.
 Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
-Relative error of estimation is 0.8\% (Linear regression) and 1.1\% (AMA) .
-The diagonal unit slope (blue dotted) line is for reference.
-The standard deviations are too small to be visible.}
+The diagonal unit slope (dotted blue) line is for reference.
+The standard deviations are too small to be visible.
+Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.1\%  for AMA based estimation.
+(b) Cone isomerizations projected along the first two AMA receptive fields for training images of condition 1.
+Each cloud represents the image patches corresponding to one LRV.
+The clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
+(c) The first two AMA receptive fields learnt using the cone responses of stimuli in the training set.}
 \label{fig:Condition1}
@@
 This in turn means that for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
-In Condition 1, we used an illumination draw form our daylight sample and thus expect a reasonable degree of similarity to D65.
+In Condition 1, we used an illumination drawn form our daylight sample and thus expect a reasonable degree of similarity to D65.
 
@@
     \end{subfigure}
-    \caption{{\bf Condition 2: Luminance can be estimated using the contrast signal:} (a) Photoreceptor response projected on AMA receptive fields calculated using photoreceptor response.
-(b) Mean LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA.
-The relative error of estimation is 41.4\% (Linear regression) and 31.3\% (AMA).
-(c) The contrast normalized photoreceptor response projected along the first two AMA receptive fields.
-The receptive fields were calculated using the contrast normalized stimuli.
-The response at each luminance level separates much better in this representation.
-(d) Estimated v/s assigned target LRV for the image in condition 2.
-The relative error of estimation is 9.3\% (Linear regression) and 1.1\% (AMA).}
+    \caption{{\bf Condition 2:} (a) Mean LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA based estimators on the cone response.
+The relative RMSE is high (41.4\% for Linear regression and 31.3\% for AMA based estimation).
+(b) Cone isomerizations projected on AMA receptive fields calculated using photoreceptor response.
+(c) Estimated v/s assigned target LRV for the image in condition 2 learnt and evaluated on contrast normalized cone isomerizations.
+The relative RMSE of estimation is 9.3\% for linear regression and 1.1\% for AMA based estimator.
+(d) The contrast normalized cone isomerizations projected along the first two AMA receptive fields.
+The receptive fields were calculated using the contrast normalized cone isomerizations.
+For Condition 2, the response corresponding to individual image patches at each LRV level separates much better in this representation.}
 \label{fig:Condition2}
@@
 Performance is poor.
-Indeed, on average the estimates track deviate considerably from the true LRV, as seen by the fact that the mean estimate
+Indeed, on average the estimates deviate considerably from the true LRV, as seen by the fact that the mean estimate
 (red line) does not lie along the positive diagonal and by the fact that there is large estimation variability for each
@@
 	\label{fig:case3RFs}
-    \end{subfigure}       \caption{{\bf RF response and luminance estimates for condition 3:} (a) Photoreceptor response projected along the first two AMA receptive fields for images of condition 1.
-We show the response for the images in the training set.
-Each response cloud represents the response of images corresponding to one LRV.
-The response clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(b)  Estimated v/s assigned target LRV for the image in condition 1.
-Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
+    \end{subfigure}
+    \caption{{\bf Condition 3:} (a) Estimated v/s assigned target LRV for the test images in Condition 3.
 The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.
-The diagonal unit slope (blue dotted) line is for reference.
-The standard deviations are too small to be visible.}
+(b) Contrast normalized cone isomerizations projected along the first two AMA receptive fields.
+The receptive fields we learnt on the contrast normalized cone isomerizations corresponding to the image patches in the training set.
+(c) First two AMA receptive fields learnt using the contrast normalized cone isomerizations.}
 \label{fig:Condition3}
@@
 The increased estimation variability is indicated by the width of the shaded red region.
-Performance of baseline linear regression method (also for the contrast normalized isomerizations) is worse than that of the AMA-based estimates.
+Performance of baseline linear regression method (also evaluated using contrast normalized cone isomerizations) is worse than that of the AMA-based estimates.
 
-Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA linear receptive fields for test [or training] stimuli.
+Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA linear receptive fields for training stimuli.
 Here, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
@@
 
-Figure~\ref{fig:barGraphs} summarizes our main findings by plotting the overall relative root mean squared estimation error (relative RMSE) for each condition. 
+Figure~\ref{fig:barGraphs} summarizes our main findings by plotting the overall relative root mean squared estimation error (relative RMSE) for each condition (defined in Figure~\ref{fig:barGraphs}). 
 In Condition 1, where only the relative target object spectrum varies, luminance constancy is an easy problem and performance is essentially perfect for both the baseline linear regression and AMA methods.
@@
 %% READ THIS PART
-
-%\subsection{Importance of Background Variation}
-%
-%
-%The variability in the final condition results from changes in background object spectra, which affects the estimation in two ways.
-%First, it affects the estimation of cone contrast due to the variability in the background.
-%Second, it also effects the cone isomerizations corresponding to the target object through 
-%variability in secondary reflections from the background objects.
-%While the first effect can be minimized by a representative sampling of the background, 
-%the effect of secondary reflections can not be removed through simple manipulations.
-%This effect has largely been ignored in the field. 
-%Our work shows that such effects are significant.
-%
-%The reason such effects have been ignored is that we have lacked tools to quantify their effects.
-%In this regard, a major contribution of this work is the development of a computational package to
-%produce naturalistic images with precise control over factors defining the scene.
-%With this software we can systematically vary these factors and precisely quantify their effects on constancy.
-
 \subsection{Use of Virtual Scenes}
@@
 \subsection{Future Directions}
-
 In the work presented here, we incorporated spectral variation into our statistical model
@@
 surface reflectance descriptors, such as object hue or chroma.
-As with LRV these descriptors would be defined by the light reflected from an object 
+As with LRV, these descriptors would be defined by the light reflected from an object 
 under a standard illuminant.
@@
 here.
-For example, we could ask how LRV discrimination thresholds are impacted by 
+We could ask how LRV discrimination thresholds are impacted by 
 spectral variation in the illuminant, the background objects, and in the target object itself.

### 2018-05-04 Draft4/draft4.tex
Full Nth draft

@@
 %% READ THIS PART
+
 \subsection{Use of Virtual Scenes}
+
+AMA has been used in conjunction with database of labeled natural images to analyze the estimation of defocus blur,
+binocular disparity and retinal image motion (refs).
+Here we used labeled images rendered from virtual scene descriptions.
+The use of rendered images has advantages and disadvantages.
+
+As we noted in the introduction, supervised learning requires large labeled datasets and these are not readily available 
+for the study of how to estimate correlates of object surface reflectance.
+In particular, to obtain ground truth information about the reflectance of objects in a natural image, it is necessary to
+make an independent of the illumination impinging on each object.
+This can be done by inserting a small number of discretely spaced reflectance standards into the scene, but 
+interpolating to locations between such standards requires strong assumptions.
+The use of rendered images allows us to work with large numbers of labeled images where the reflectance
+and impinging illumination are known precisely at every pixel.
+
+A second advantage of using rendered images is that we can control the variation in distinct
+scene factors that might affect the difficulty of the estimation problem.
+This allows study of the individual effect of each factor as well as their joint effect.
+Here, we exploited this advantage to systematically introduce variation in the relative target object reflectance
+spectrum, the spectrum of the illumination, and the reflectance spectrum of the background objects.
+This allowed us to quantify how each of these variations limits LRV estimation.
+We believe this basic approach can be extended to include parametric control over the amount
+of variation of different factors as well as to include variation in additional factors (see below).
+
+At the same time, it is important to recognize that limitations of the approach.
+Virtual rendered scenes are not guaranteed to capture all of the task relevant
+variation that occurs in real scenes.
+Indeed, even casual inspection of our images reveals that they are rendered and
+not real.
+Computer graphics is getting better, however, and we expect that the gap between
+virtual and natural image databases will steadily close.
+Indeed, carefully constructed graphics images are now quite difficult to differentiate
+from real images.
+
+Our use of virtual images relies on datasets that characterize the statistical variation
+in object reflectance and natural illumination spectra.
+We believe these datasets provide reasonable approximations.
+None-the-less, they can be extended and improved.
+For example, the dataset of illuminations does not include the artificial illuminations
+that we now live much of our lives under.
+The surface reflectance datasets captures constraints on naturally occurring reflectance
+functions, but did not sample the environment in a manner that was intended to 
+characterize the relative frequency of occurrence of different reflectance spectra.
+Future work with virtual image datasets will benefit from targeted efforts to characterize
+the natural statistics of the scene components that are varied.
+Under the assumption that combination of different scene factors (e.g. surface reflectances
+and illuminations) is independent, the virtual image approach modularizes the study
+of variation in natural scenes.
+%Supervised learning requires large labeled data sets.
+Such data sets are not readily available for the study of color constancy.
+Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
+There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}; \citeauthor{davidPennHyperspectral}), but these are not large enough to drive supervised learning.
 

### 2018-05-09 Draft4/draft4.tex
DB editing pass through to results.

@@
 
+ \author{Cottaris}{Nicolas P.}
+ {}
+ {Department of Psychology, University of Pennsylvania, PA, USA}
+ {}{cottaris@sas.upenn.edu}
+
+ \author{Heasly}{Benjamin S.}
+ {}
+ {Department of Psychology, University of Pennsylvania, PA, USA}
+ {}{benjamin.heasly@gmail.com}
+
+ \author{Brainard}{David H.}
+ {}
+ {Department of Psychology, University of Pennsylvania, PA, USA}
+ {}{brainard@psych.upenn.edu}
+
+ \author{Burge}{Johannes}
+ {}
+ {Department of Psychology, University of Pennsylvania, PA, USA}
+ {}{jburge@psych.upenn.edu}
+
 \keywords{color constancy, luminance constancy, supervised learning}
@@
 The perceived color of an object has important behavioral implications, since color helps to identify objects and their properties \cite{Mollon89, Jacobs81}.
-The perceived color depends on the surface reflectance of the object, but it is not sensed directly. 
-Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
-The computational challenge underlying object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
-To produce a stable perceptual representation correlated with an object's surface reflectance the brain must account for these intrinsic factors on the reflected light.
-The ability of a visual system to extract such a stable representation is called color constancy. 
-%Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
+%The perceived color depends on the surface reflectance of the object, but it is not sensed directly. 
+%Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
+The computational challenge underlying object color perception is that the light reflected from an object depends not just on its surface reflectance, but also on object-extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
+To compute a perceptual representation of object color that is correlated with the object's physical surface reflectance, the brain must account for these object-extrinsic factors.
+The ability of a visual system to compute a representation of object color that is stable against variation in object-extrinsic scene factors is called color constancy. 
+Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
 In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eye to produce percepts well-correlated with object surface reflectance.
@@
 But, it is possible to obtain such descriptors by analyzing jointly the light reflected from all of the objects in the scene.
-As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant.
-Thus evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects \cite{BrainardWandellRetinex,BrainardFreeman}.
+As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant; evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects \cite{BrainardWandellRetinex,BrainardFreeman}.
 
@@
     \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and the illumination under which it lies.
-Additionally, it also depends on geometric factors, such as the object's shape, pose, and position relative to the observer.
-The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable, an ability called color constancy.
+    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination.
+Additionally, the reflected light also depends on geometric factors, such as the object's shape, pose, and position.
+The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable across such variations, an ability called color constancy.
 (b) {\bf Luminance Constancy:} Images of a sphere under a fixed illuminant.
-Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance spectrum held fixed.
-The relative spectrum (shape of reflectance spectrum) varies across each row.
+Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance function is held fixed.
+The relative reflectance function (i.e.
+the shape of the spectral reflectance function) varies across each row.
 Within each row, the light reflectance value (LRV) of the spheres is constant.
 The values on the left of each row provide the corresponding LRV.
-We cast the problem of computational luminance constancy to be that of estimating LRV from the image, across variation in other scene factors: variation in relative surface reflectance, variation in illumination, and variation in the reflectance of the other objects in the scene.}
+We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors.
+Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
  \end{figure}
 
-An alternative approach to computational color constancy, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors \cite{barron2015convolutional}.
+An alternative approach to computational color constancy, which has been less-well explored, is to use supervised machine learning to develop mappings between input images and stable color descriptors \cite{barron2015convolutional}.
 The use of supervised learning to understand perceptual capabilities for natural stimuli has enjoyed success in domains outside of color vision.
@@
 Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
-There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}; \citeauthor{davidPennHyperspectral}), but these are not large enough to drive supervised learning.
+There are a few databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}), but these are not large enough to drive supervised learning.
 
-% Figure 2: Conditions Studied
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.33 \textwidth}
-		\caption{Condition 1}
-%		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
-		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.png}
- 		\label{fig:backgroundVarying}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.33 \textwidth}
-        \caption{Condition 2}	
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.png}
-        \label{fig:targetIlluminantVarying}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.33 \textwidth}
-	\caption{Condition 3}	
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.png}        
-        \label{fig:allSpectraVarying}
-    \end{subfigure}    
-    \caption{{\bf Types of spectral variations studied in this work:} sRGB rendition of multispectral images similar to ones studied in our work.
-The numbers on the left indicate the standard luminance level of the target object.
-5 images are shown at each luminance level.
-We studied three types of spectral variations.
-(a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
-%Condition 2: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable, 
-(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
-The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
-Moreover, across the three panels, spheres in corresponding locations have the same surface reflectance.
-In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
-The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
-\label{fig:studiedCases}
-\end{figure}
+In this paper, we use high-quality computer graphics to generate large data sets of naturalistic images where the surface reflectance corresponding to each image pixel is known. 
+This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants.
+More specifically, we use this approach to tackle luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
 
-In this paper, we use high-quality computer graphics to generate large data sets of naturalistic images where the surface reflectance and illumination corresponding to each image pixel are known. 
-This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants.
-Here, we use this approach to tackle luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
-
-We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of an object's surface reflectance function.
+We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of a target object's surface reflectance function.
 The LRV is a measure of the overall amount of light reflected by a surface (\citeauthor{astm1121477}).
@@
 normalized by the luminance of the reference illuminant itself.
-Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function \cite{CIE86}.
-LRVs are typically expressed in percent, so that they range from 0 to 100.
+Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
+LRVs range from 0 to 1.
+%% DHB: The ASTM citation is not formatting well.  It should give a year.
 
@@
 Second we use a model of the early visual system to compute the responses of the cone photoreceptor mosaic to the labeled images.
-Third we apply AMA to the cone responses to learn task-optimal receptive fields (RFs).
+Third we apply AMA to the cone responses, as well as to a contrast normalized version of the cone responses, to learn task-optimal receptive fields (RFs).
 Fourth we evaluate how well the responses of the RFs may be decoded to achieve luminance constancy.
@@
 We have developed a rendering package 
-(\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}, \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}) 
+(\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{https://github.com/BrainardLab/VirtualWorldColorConstancy}) 
 that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
-The package harnesses an open-source computer graphics renderer 
+The package builds on our RenderToolblox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
+and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org})
 \cite{jakob2015mitsuba} to produce physically-accurate images from the scene models.
@@
 By incorporating statistical models of the variation of object surface reflectance and daylight illumination, 
-the pipeline allows us to produce large labeled sets of images that capture much of the task-relevant 
+the pipeline allows us to produce large labeled sets of images that capture key aspects of the task-relevant 
 statistical structure of natural scenes.
+%% DHB: Need to fix up citations in this paragraph. The URLs for RTB and Mitsuba should be inside the same paraneheses as the citations that
+% follow.
 
-% Figure 3
+% Figure 2
 \begin{figure}[t]
@@
     \end{subfigure}
+    \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional objects inserted.
+The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}
+\end{figure}
+%% DHB: We need to think about how to scale the images for display.  The Library scene is too dark, at least when printed.
 
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{Indoor-plant}    
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_d.png}
-        \label{fig:baseSceneIndoorPlant}
-    \end{subfigure}    
-    ~
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{Warehouse}    
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_e.png}
-        \label{fig:baseSceneWarehouse}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{Checkerboard}    
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_f.png}
-        \label{fig:baseSceneCheckerBoard}
-    \end{subfigure}
-    \caption{{\bf Base scenes from the Virtual World Color Constancy (VWCC) library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.
-The reflectance spectra of the distinct surfaces and the spectral power distribution function of the light sources in each scene have been assigned randomly (see text).}\label{fig:baseScenes}
-\end{figure}
-
-% Figure 4
+% Figure 3
 \begin{figure}
@@
     \begin{subfigure}[b]{0.14 \textwidth}
-        \caption{Small-ball}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_b.png}
-        \label{fig:libraryWithSmallBall}
-    \end{subfigure}
-    ~ 
-    \begin{subfigure}[b]{0.14 \textwidth}
         \caption{Barrel}
@@
         \label{fig:libraryWithBarrel}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.14 \textwidth}
-        \caption{Xylophone}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_d.png}
-        \label{fig:libraryWithXylophone}
          \end{subfigure}
@@
     \end{subfigure}
-\caption{{\bf The library base scene with inserted objects.} The rendering package can be used to insert objects into the base scenes.
+\caption{{\bf The library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
 The panels show different objects inserted in the library base scene.
-The objects were inserted at a user defined location in the image and then the camera was pointed at the object so that the object is at the center of the rendered image.
+The objects were inserted at a user defined location in the image.
+Then the rendering viewpoint was set so that the object is at the center of the rendered image.
 In these panels, the full rendered image has been cropped so that the inserted object is more visually salient.}\label{fig:libraryWithTarget}
 \end{figure}
+%% DHB: Can we render these examples at higher resolution, so that they look nicer?  The blurriness is distracting in the images.
 
-% Figure5
+% Figure 4
 \begin{figure}
@@
     \centering
+        \caption{Illumination spectra}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_c.png}
+        \label{fig:illuminationVariation}
+    \end{subfigure}
+          ~  
+    \begin{subfigure}[b]{0.18 \textwidth}
+    \centering
         \caption{Background spectra}
@@
     \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \caption{Illumination spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_c.png}
-        \label{fig:illuminationVariation}
-    \end{subfigure}
-    \caption{{\bf Transformations of the scene.} The properties of a visual scene can broadly be classified into two groups: Geometrical (a-b) and Spectral (c-e).
-VWCC provides control over such properties as illustrated by the columns.
+
+    \caption{{\bf Transformations of the scene.} The properties of a visual scene can broadly be classified into two groups: geometrical (a-b) and spectral (c-e).
+Our rendering package provides control over the properties illustrated by the columns of the figure.
 (a) Variation in inserted object positions.
-(b) Variation in orientations.
-(c) Variation is the surface reflectance of the target object.
-(d) Variation in surface reflectance of the background objects.
-The reflectances were assigned randomly in each panel.
-(e) Variation in the spectral power distribution function of the light sources.
+(b) Variation in object pose.
+(c) Variation in the surface reflectance of the target object.
+(d) Variation in the spectral power distributions of the light sources.
+(e) Variation in surface reflectance of the background objects.
 \label{fig:VWCCTransformations}}
 \end{figure}
+%% DHB: These are too dark in a printout.
+Let's review how they are scaled.
+Need to make sure we can see an effect of changing the illumination, might want to hand pick the illuminants used here to illustrate the effect.
+
+% Figure 5: Conditions Studied
+\begin{figure}
+\centering
+	\begin{subfigure}[b]{0.33 \textwidth}
+		\caption{Condition 1}
+%		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
+		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.png}
+ 		\label{fig:backgroundVarying}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.33 \textwidth}
+        \caption{Condition 2}	
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.png}
+        \label{fig:targetIlluminantVarying}
+    \end{subfigure}
+	\begin{subfigure}[b]{0.33 \textwidth}
+	\caption{Condition 3}	
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.png}        
+        \label{fig:allSpectraVarying}
+    \end{subfigure}    
+    \caption{{\bf Illustration of Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2 and 3.
+The numbers on the left indicate the standard luminance level of the target object.
+5 images are shown at each luminance level.
+We studied three types of spectral variations.
+(a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
+(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
+The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
+Across the three panels, spheres in corresponding locations have the same surface reflectance.
+In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+This smaller than the variation we studied, but allows us to show the variation within the dynamic range available for the figure.
+The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
+\label{fig:studiedCases}
+\end{figure}
+%% DHB: May also want to render these examples at a higher resolution
 
@@
 In the present work, we used our package to generate datasets of naturalistic scenes and corresponding images.
-We used one fixed base scene and inserted a target object of fixed shape and size into this scene.
-We generated three distinct datasets: Conditions 1-3.
+We used one fixed base scene and inserted a spherical target object of fixed shape and size into this scene.
+We generated three distinct datasets, which we refer to as Conditions 1-3 and describe below.
 Across these datasets the luminance constancy problem, estimating the target object LRV,
@@
 Each dataset consisted of 1000 scenes and corresponding images.
+%% DHB Need to decide how many images we really want for final version of the work.
 
@@
 spectral power distribution of the light sources).
-We used 10 LRV values, equally spaced between 20 and 60 and generated 100 target surface reflectance spectra at these values. 
+We used 10 LRV values, equally spaced between 0.2 and 0.6 and generated 100 target surface reflectance spectra at each of these values. 
 The surface reflectance spectra at the same LRV could differ in their relative shape.
@@
 The position and size of the inserted object, inserted light source and viewpoint were held fixed across all 
-scenes in the database, as shown in Figure~\ref{fig:3DScene}.
-Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra as described below.
+scenes in the database. The geometry is shown in Figure~\ref{fig:3DScene}.
+Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra, as described below.
 Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
@@
     \end{subfigure}
-    \caption{{\bf Illumination spectra:} (a) Granada dataset.
-The spectra are normalized by the mean over wavelength.
-(b) A representative sample of spectra generated using normalized Granada dataset.
-(c) CIE xy chromaticity diagram of the normalized dataset and the random samples.
-(d) sRGB renditions of the samples from Figure~\ref{fig:illuminantSamples}.}
+    \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset.
+Each spectrum is normalized by its mean (with mean taken over wavelength).
+(b) Sample spectra generated using the statistical model derived from normalized Granada dataset.
+(c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in b (red).
+F(d) sRGB renditions of the samples shown in b.}
 \label{fig:illuminant}
 \end{figure}
+%% DHB: The chromaticities in c and renderings in d are for the spectra in b, right?  I wrote the caption to say so, just checking.
 
-To generate illumination spectra, we developed a statistical model of the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{hernandez2001color} and sampled randomly from the model (see appendix).
+To generate illumination spectra, we developed a statistical model of the Granda daylight measurements (\href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) \cite{hernandez2001color} and sampled randomly from the model (see appendix).
 The overall intensity of the measurements spans approximately three orders of magnitude.
-Figure~\ref{fig:granadaData} plots the measurements in normalized form to make apparent the variation in the relative spectra. The spectra are normalized by their mean over wavelength.
+Figure~\ref{fig:granadaData} plots the measurements in normalized form to make apparent the variation in the relative spectra.
 
-Our statistical model approximates these normalized shapes using their first 6 principle components.
+Our statistical model approximates the normalized Granda spectra using their first 6 principle components.
 The variation in these components is modeled with a 6-dimensional Gaussian whose mean and covariance matrix 
-match the dataset's sample mean and covariance of the weights on these components \cite{BrainardFreeman}.
-To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
+match the sample mean and covariance of the weights on these components obtained from the normalized Granada spectra \cite{BrainardFreeman}.
+To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and then use the weights to generate the corresponding spectrum.
 Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
 Details of the statistical model for illumination are provided in the appendix.
+Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:xyDiagram} and ~\ref{fig:sRGBIlluminant}.
 
-Because our multivariate Gaussian model is based on the rescaled spectra, it does not embody the large variation in overall intensity of natural daylights.
+Because our multivariate Gaussian model is based on normalized spectra, it does not embody the large variation in overall intensity of natural daylights.
 To obtain illuminant spectra with intensity variation similar to the Granada dataset, we scaled each randomly generated relative spectrum.
-The scale factors we sampled at random in the range 0.15 and 150.
-Color swatches of samples of illuminant spectra are shown in Figure~\ref{fig:sRGBIlluminant}.
+The scale factors were sampled uniformly from range 0.15 and 150.
+%% DHB: Check that these values are right.  Linear spacing or log spacing?
 
@@
     \end{subfigure}
-    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.(b) Representative samples of randomly generated object surface reflectances.
-(c) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (black) and samples of surface reflectances (red).
-(d) sRGB renditions of the samples of object surface reflectance under CIE D65 daylight.}
+    \caption{{\bf Statistical model of surface reflectance:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.
+(b) Sample spectra generated using the surface reflectance statistical model.
+(c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances and samples shown in b (red).
+(d) sRGB renditions of the samples shown in b, rendered under the CIE D65 daylight.}
 \label{fig:surfaceReflectanceGeneration}
 \end{figure}
+%% DHB: The chromaticities in c and renderings in d are for the spectra in b, right?  I wrote the caption to say so, just checking.
 
@@
 \includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure8/Figure8.pdf}
-\caption{{\bf Target surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
+\caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
 The figure shows 10 random samples at 10 equally spaced LRV levels in the range [0.2, 0.6].
@@
 
-We generated random reflectance spectra using the same principles we applied to generate random illuminant spectra.
+We generated random reflectance spectra using the same principles we used to model illuminant spectral power distributions.
 We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
@@
 The Vrhel dataset contains 170 spectra measured at 2 nm sampling between 390 nm and 730 nm.
-We resampled these spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
-Figure~\ref{fig:reflectanceSpectra} illustrates the spectra of draws obtained using this procedure.
+We resampled these spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm (Figure~\ref{fig:reflectanceSpectra}).
 Details of the statistical model for surface reflectance spectra are provided in the appendix. 
+Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance draws obtained using the model.
 
@@
 scaled such that the LRV had the desired value (see appendix).
-Figure \ref{fig:targetSwatches} shows color swatches of target reflectance spectra rendered under CIE illuminant D65, for evenly spaced LRV values.
+Figure \ref{fig:targetSwatches} shows color renderings of target reflectance spectra under CIE illuminant D65, for the evenly spaced LRV values we studied.
+%% DHB: Note that this procedure is different than conditioning the statistical model on the target LRV.  We could switch to the latter if we wished.
 
@@
     \hspace{0.1 \textwidth}
-        \caption{Optical image}
+        \caption{Retinal image}
         \vspace{1.5mm}
@@
     \begin{subfigure}[b]{0.2 \textwidth}
-        \caption{LMS cone contrast}
+        \caption{LMS normalized cone contrast}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_d.png}
@@
     \label{fig:sceneWithCroppedImage}
-    \caption{{\bf Generating labeled dataset for computational analysis:}  For the supervised approach employed in this work, the labeled database is generated as follows: (a) A 3D virtual scene, containing a target object of known surface luminance is created.
-The target object is placed in the camera field of view.
-After assigning spectra to the light sources and other objects in the scene, a multispectral image of the scene is rendered using the Mitsuba software package.
-(b) The central portion of the rendered image, which contains the target object, is cropped from the image.
-(c) The response of the cones in the retina are simulated using the retinal image incident on the cone mosaic.
-The figure shows the retinal image after optical blurring and the location and identity of the cones in the retinal mosaic (L cones: Red, M cones: Green, S cones: Blue).
-(d) The cone responses are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
+    \caption{{\bf Pipeline for generating labeled datasets:}  For the supervised learning approach employed in this work, labeled images are generated as follows: (a) A 3D virtual scene, containing a target object is created.
+The rendering viewpoint is selected so that the target object is in the center of the image.
+Spectra are assigned to the target object, illuminants, and other objects in the scene using the statistical models described in the text.
+A multispectral image of the scene is then rendered.
+(b) The central portion of the rendered image, which contains the target object, is cropped.
+(c) The retinal image corresponding to the rendered image is computed, and this is used in turn to compute the excitations of the cone photoreceptors.
+The figure shows the a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).
+(d) The cone excitations are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
 Finally, the demosaiced images are contrast normalized separately for each cone type.}
@@
 The resulting retinal image is sampled by a mosaic of cone photoreceptors.
-The responses of these photoreceptors provide the information about the scene that is available to the neural visual system for further processing.
-Because we are interested in how well luminance constancy may be achieved by the human visual system, we simulated the cone responses
+The excitations of these photoreceptors provide the information about the scene that is available to the neural visual system for further processing.
+Because we are interested in how well luminance constancy may be achieved by the human visual system, we simulated the cone excitations
 to our scenes using a model of the early visual system.
@@
 In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle (REFS).
-% Johannes to provide his favorite citation or two.  Some review.
+%% DHB: Johannes to provide his favorite citation or two.  Some review.
 
-We modeled a visual system with a pupil diameter of 3 mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
+We modeled a visual system with a pupil diameter of 3 mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, and spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
 The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
-Cone isomerizations were computed assuming an integration time of 100 msec, and we modeled the Poisson nature of photopigment isomerization \cite{hecht1942energy}. 
-This modeling was implemented using the software infrastructure provided by ISETBio \cite{brainard2015isetbio}.
+Cone excitations were taken as isomerizations assuming an integration time of 100 msec, and we modeled the Poisson nature of photopigment isomerization \cite{hecht1942energy}. 
+This modeling was implemented using the software infrastructure provided by ISETBio (\href{https://isetbio.org}{https://isetbio.org}).
 
-% Details from Nicolas (TEXT IN CAPS IS FROM VIJAY)
-% Scene: 
-%- the default mean luminance was set to 200, but there is a key-value param that could have overriden this value. 
-%  I do not know if this were the case.
+%% Details on ISETBIO computations from Nicolas (TEXT IN CAPS IS FROM VIJAY)
+%% Scene: 
+%%- the default mean luminance was set to 200, but there is a key-value param that could have overriden this value. 
+%%  I do not know if this were the case.
+%%
+%% % MEAN LUMINANCE = 0, NO SCALING
 %
-% % MEAN LUMINANCE = 0, NO SCALING
+%%- The default FOV was 1 deg, but there is a key-value param that could have overriden this value.
+%%  I do not know if this were the case.
+%%
+%% % HORIZONTAL FOV = 1
+%%
+%%- Distance default is 1 meter, but there is  a key-value param that could have overriden this value.
+%%  I do not know if this were the case.
+%%
+%%% DISTANCE 1M
+%%
+%%Optics: 
+%%- 3 mm pupil, 17 mm focal length, with a spectro-spatial OTF described in  
+%%  (Marimont & Wandell (1994) J. Opt. Soc. Amer. A,  v. 11, p. 3113-3122), 
+%%   which includes axial chromatic aberration. However, there is key-value param o skip the OTF. 
+%%   Not sure if this was used.  It it was used, the optics was set to diffraction limited.
+%%
+%% % SKIP OTF OFF:  'skipOTF', false ...  
+%%
+%%Lens: 
+%%- not sure if the optical density is from Wyszecki&Stiles or from Stockman-Sharpe. 
+%%  The isetbio file commend only says it is from PTB. David do you know, or should I check
+%%  the data?
+%%
+%%Cone Mosaic: 
+%%- rectangular cone mosaic with 0.6:0.3:0.1 LMS densities
+%%- FOV was a key-value param, so I do not know what was used.
+%%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
+%%but there is a key-value param that could have overriden this value. I do not know what that parameter value was.
+%%
+%% CONE STRIDE = 3 'coneStride', 3, ... 
+%%
+%%
+%%- There is a key-value pair to also low-pass the optical image with default value to not do so.
+%%  If that was user-overriden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
+%%
+%% LOW PASS FILTER = MATCH CONE STRIDE : lowPassFilter = 'matchConeStride';      
+%%
+%%- IntegrationTime was not specified, so it was the default which is 5 msec.
+%%  The cone isomerization maps were also demosaiced using linear interpolation.
+%%- The default isomerization noise was set to none, but there is a key-value parameter
+%%  that can override it. I do not know what the value of that was.
+%%
+%% ISOMERIZATION NOISE = FROZEN, 'isomerizationNoise', 'frozen'
+%%
+%%-  Finally, there is a key-value param named 'coneEfficiencyBasedReponseScaling', which by default is set to 'none'
+%%   But if it was user-set to non 'none' the code scaled the responses to simulate equal quantal efficiencies 
+%%   for L , M and S coneEfficiencyBasedReponseScaling by undoing filtering by the lens and the macular pigment.
+%%   I do not know if this was used.
+%% 
+%% coneEfficiencyBasedReponseScaling = 'area'
 
-%- The default FOV was 1 deg, but there is a key-value param that could have overriden this value.
-%  I do not know if this were the case.
-%
-% % HORIZONTAL FOV = 1
+The cone excitations represent the first step of visual processing.
+To capture key properties of post-receptoral processing, such as contrast normalization \cite{heeger1992normalization,albrecht1991motion,carandini2012normalization},
+we processed the excitations as follows:
+First, we generated a response for each cone class at each pixel in the sampled retinal image, using linear interpolation separately for each cone class.
+This gives us a cone excitation image for each cone class.
+We also normalized each cone excitation image by the total area under the corresponding cone spectral sensitivity.
+This makes the magnitude of the cone excitation images similar across cone classes.
+These two processing steps do not alter the information in the cone excitation images.
 
-%- Distance default is 1 meter, but there is  a key-value param that could have overriden this value.
-%  I do not know if this were the case.
-%
-%% DISTANCE 1M
+To model contrast coding, we converted each cone excitation image to a corresponding cone contrast image.
+This was accomplished by computing the mean response over the three cone excitation images, and then subtracting off and dividing by this mean.
+To model contrast normalization, we divided the contrast images by the sum of squared contrasts taken over image pixels and cone classes.
 
-%
-%Optics: 
-%- 3 mm pupil, 17 mm focal length, with a spectro-spatial OTF described in  
-%  (Marimont & Wandell (1994) J. Opt. Soc. Amer. A,  v. 11, p. 3113-3122), 
-%   which includes axial chromatic aberration. However, there is key-value param o skip the OTF. 
-%   Not sure if this was used.  It it was used, the optics was set to diffraction limited.
-%
-% % SKIP OTF OFF:  'skipOTF', false ...
-
-%
-%Lens: 
-%- not sure if the optical density is from Wyszecki&Stiles or from Stockman-Sharpe. 
-%  The isetbio file commend only says it is from PTB. David do you know, or should I check
-%  the data?
-%
-%Cone Mosaic: 
-%- rectangular cone mosaic with 0.6:0.3:0.1 LMS densities
-%- FOV was a key-value param, so I do not know what was used.
-%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
-%but there is a key-value param that could have overriden this value. I do not know what that parameter value was.
-%
-% CONE STRIDE = 3 'coneStride', 3, ...
-
-%
-%- There is a key-value pair to also low-pass the optical image with default value to not do so.
-%  If that was user-overriden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
-%
-% LOW PASS FILTER = MATCH CONE STRIDE : lowPassFilter = 'matchConeStride';
-
-%- IntegrationTime was not specified, so it was the default which is 5 msec.
-%  The cone isomerization maps were also demosaiced using linear interpolation.
-%- The default isomerization noise was set to none, but there is a key-value parameter
-%  that can override it. I do not know what the value of that was.
-%
-% ISOMERIZATION NOISE = FROZEN, 'isomerizationNoise', 'frozen'
-
-%-  Finally, there is a key-value param named 'coneEfficiencyBasedReponseScaling', which by default is set to 'none'
-%   But if it was user-set to non 'none' the code scaled the responses to simulate equal quantal efficiencies 
-%   for L , M and S coneEfficiencyBasedReponseScaling by undoing filtering by the lens and the macular pigment.
-%   I do not know if this was used.
-% 
-% coneEfficiencyBasedReponseScaling = 'area'
-
-The cone isomerizations represent the first step of visual processing.
-To capture key properties of post-receptoral processing, such as contrast normalization \cite{heeger1992normalization,albrecht1991motion,carandini2012normalization},
-we processed the isomerizations as follows:
-First, we generated a response for each cone class at each pixel in the sampled retinal image, using linear interpolation separately for each cone class.
-This gives us a cone response image for each cone class.
-We also normalized each cone response image by the total area under the corresponding cone spectral sensitivity.
-This makes the magnitude of the cone response images similar across cone classes.
-These two processing steps do not alter the information in the cone response images.
-
-To model contrast coding, we converted each cone response image to a corresponding cone contrast image.
-This was accomplished by computing the mean response over the three cone contrast images, and then subtracting off and dividing by this mean.
-To model contrast normalization, we divided by the sum of squared contrasts over image pixels and cone classes.
+%% DHB: We meed to figure out and say something about how we scaled image intensities into a reasonable range.
 
 \subsection{Computational luminance constancy} \label{method:SupervisedLearning}
-We used our datasets to determine how well target object LRV can be estimated from cone responses and from normalized cone contrasts.
+We used our datasets to determine how well target object LRV can be estimated from cone excitations and from normalized cone contrasts.
 Studying both representations allows us to understand how early contrast coding and normalization affect how well luminance constancy can be achieved.
@@
 Then, we approximate these with multivariate Gaussian distributions.
-With the Gaussian approximation in hand, 
-to estimate the LRV of the target object in a test image, we use Bayes' rule to obtain the posterior distribution over LRV values given the filter responses.
+To estimate the LRV of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRV values given the filter responses.
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
+Here we use a squared error cost function, so that the optimal estimator is the posterior mean.
+%% DHB: Uniform prior, right? And posterior mean?  If not, correct prose above.
 
@@
 To provide baselines for evaluation of the estimation method described above, we used linear regression.
-First, we solved for the weights on the average L, M and S cone responses target object that best predicted the target LRV values.
-We took the average cone respones from a $3 \times 3$ region at the center of the target object.
+First, we solved for the weights on the average L, M and S cone excitations corresponding to the target object that best predicted the target LRV values.
+We took the average cone responses from a $3 \times 3$ region at the center of the target object.
 This baseline method disregards information carried the image regions corresponding to the background objects.
 We also performed regression on the contrast normalized version of the cone responses.
-This baseline method indirectly incorporates information carried the image regions corresponding to the background objects,
-through their effect on the contrast normalized responses from the target object. 
-We also evaluated the performance of a naive model that estimate the mean of the LRV values in the training set, irrespective
+This second baseline method indirectly incorporates information carried in the image regions corresponding to the background objects,
+through their effect on the contrast normalized responses at the center of the target object. 
+We also evaluated the performance of a naive model that estimates the mean of the LRV values in the training set, irrespective
 of the image data.

### 2018-05-11 Draft4/draft4.tex
Editing.

@@
     \label{introFigure}
-    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination.
+    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination.
 Additionally, the reflected light also depends on geometric factors, such as the object's shape, pose, and position.
 The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable across such variations, an ability called color constancy.
-(b) {\bf Luminance Constancy:} Images of a sphere under a fixed illuminant.
+(b) Images of a sphere under a fixed illuminant.
 Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance function is held fixed.
@@
     \end{subfigure}
-\caption{{\bf The library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
+\caption{{\b fLibrary base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
 The panels show different objects inserted in the library base scene.
@@
 
-    \caption{{\bf Transformations of the scene.} The properties of a visual scene can broadly be classified into two groups: geometrical (a-b) and spectral (c-e).
+    \caption{{\bf Scene transformations.} The properties of a visual scene can broadly be classified into two groups: geometrical (a-b) and spectral (c-e).
 Our rendering package provides control over the properties illustrated by the columns of the figure.
@@
     \end{subfigure}    
-    \caption{{\bf Illustration of Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2 and 3.
+    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2 and 3.
 The numbers on the left indicate the standard luminance level of the target object.

### 2018-05-11 Draft4/draft4.tex
This morning’s edits.  Through to “Use of virtual scenes”

@@
 (b) The central portion of the rendered image, which contains the target object, is cropped.
-(c) The retinal image corresponding to the rendered image is computed, and this is used in turn to compute the excitations of the cone photoreceptors.
+(c) The retinal image corresponding to the rendered image is computed, and this is used in turn to compute the excitations (taken as the number of photopigment isomerizations) of the cone photoreceptors.
 The figure shows the a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).
@@
 The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
-Cone excitations were taken as isomerizations assuming an integration time of 100 msec, and we modeled the Poisson nature of photopigment isomerization \cite{hecht1942energy}. 
+Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec, and we modeled the Poisson nature of photopigment isomerization \cite{hecht1942energy}.
 This modeling was implemented using the software infrastructure provided by ISETBio (\href{https://isetbio.org}{https://isetbio.org}).
@@
         \begin{subfigure}[b]{0.26 \textwidth}
-        \caption{Receptive field response}
+        \caption{RF responses}
         \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure10/Figure10_b.pdf}
@@
     \end{subfigure}   
-    \caption{{\bf Luminance estimates, receptive fields and RF response for condition 1:} (a) Estimated v/s assigned target LRV for the test image in condition 1.
-Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
-The diagonal unit slope (dotted blue) line is for reference.
+    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the cone excitations.
+Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation.
+The diagonal identity line (dotted blue) indicates veridical estimation.
 The standard deviations are too small to be visible.
 Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.1\%  for AMA based estimation.
-(b) Cone isomerizations projected along the first two AMA receptive fields for training images of condition 1.
+(b) Cone excitations projected along the first two AMA receptive fields for training images of Condition 1.
 Each cloud represents the image patches corresponding to one LRV.
-The clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
-(c) The first two AMA receptive fields learnt using the cone responses of stimuli in the training set.}
+The clouds are approximated by a multivariate Gaussians whose means and variances are approximated by the ellipses shown in the figure.
+(c) The first two AMA receptive fields learnt using the cone excitations of stimuli in the training set.}
 \label{fig:Condition1}
 \end{figure}
+
+\subsection{Condition 1}
 
@@
 In Condition 1, we used an illumination drawn form our daylight sample and thus expect a reasonable degree of similarity to D65.
+%% DHB: We need to say something about how similar.  Might explore different illuminants to dissect how sensitive the estimation
+% is to whether the fixed illuminant is D65 or something else.  Probably not very, but this is an example of something we can exploit
+% our graphics approach to understand, and we want to build up examples.
 
 We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
-For this condition, we trained and evaluated AMA on the cone responses to the image patches.
-Figure~\ref{fig:case1RFResponse} shows the responses of the first two receptive fields to all the image patches in the training set.
-Each individual point represents the receptive field responses to a single image patch.
-Each point is color coded according to the LRV corresponding to the target object in the patch.
-The responses segregate according to the target LRV.
-This means that the responses may be used to accurately decode LRV, confirming the intuition that computational
-luminance constancy is readily achieved for Condition 1.
-
+We trained and evaluated AMA on the cone excitations to the image patches.
 Decoding performance for the test set is shown in Figure~\ref{fig:case1Estimates}.
-As expected, the LRV estimates obtained by decoding the AMA receptive field responses are veridical.
+As expected, the LRV estimates obtained by decoding the AMA receptive field responses are essentially perfect.
 Figure~\ref{fig:case1Estimates} also shows the performance of the baseline linear regression method, again trained
@@
 
+Figure~\ref{fig:case1RFResponse} shows the responses of the first two receptive fields to all the image patches in the training set.
+Each individual point represents the receptive field responses to a single image patch.
+Each point is color coded according to the LRV corresponding to the target object in the patch.
+The responses segregate according to the target LRV, which is the feature required to support the high level 
+of estimation performance shown in Figure~\ref{fig:case1Estimates}.
+
 Figure~\ref{fig:case1RFs} shows the first two AMA receptive fields.
-Each of these, in essence, takes a weighted sum of the L and M cone isomerizations at the target object location.
-The isomerizations in the background regions and the S cone isomerizations are largely ignored.
+Each of these, in essence, takes a weighted sum of the L and M cone excitations at the target object location.
+The cone excitations in the background regions and the S cone excitations are largely ignored.
 These receptive fields make sense.
@@
 through light scattered from them onto the target.
-In addition, luminance is primarily determined by L and M cone isomerizations.
+In addition, luminance is primarily determined by L and M cone s, so the S cones should make little
+contribution.
+%% DHB: Can we add a color scale bar to the plots?
 
-%% Figure condition 2: Isomerization Fails
+%% Figure condition 2: Excitations Fail
 \begin{figure}
@@
     \begin{subfigure}[b]{0.22\textwidth}   
-        \caption{RF response (Isomerization)}
+        \caption{LRV estimates (excitations)}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_a.pdf}
@@
         \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{LRV estimates (Isomerization)}
+        \caption{RF responses (excitations)}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_b.pdf}
@@
             \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{RF response (Contrast)}
+        \caption{LRV estimates (Normalized contrast)}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_c.pdf}
@@
             \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{LRV estimates (Contrast)}
+        \caption{RF responses (Normalized contrast)}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_d.pdf}
@@
     \end{subfigure}
-    \caption{{\bf Condition 2:} (a) Mean LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA based estimators on the cone response.
-The relative RMSE is high (41.4\% for Linear regression and 31.3\% for AMA based estimation).
-(b) Cone isomerizations projected on AMA receptive fields calculated using photoreceptor response.
-(c) Estimated v/s assigned target LRV for the image in condition 2 learnt and evaluated on contrast normalized cone isomerizations.
+    \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the cone excitations.
+The relative RMSE is high (41.4\% for linear regression and 31.3\% for AMA based estimation).
+(b) Cone isomerizations projected on AMA receptive fields calculated using cone excitations.
+(c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the contrast normalized cone excitations.
 The relative RMSE of estimation is 9.3\% for linear regression and 1.1\% for AMA based estimator.
-(d) The contrast normalized cone isomerizations projected along the first two AMA receptive fields.
-The receptive fields were calculated using the contrast normalized cone isomerizations.
-For Condition 2, the response corresponding to individual image patches at each LRV level separates much better in this representation.}
+(d) The contrast normalized cone excitations projected along the first two AMA receptive fields.
+The receptive fields were learned using AMA and the contrast normalized cone excitations.
+For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is contrast normalized cone excitations rather than the cone excitations themselves.}
 \label{fig:Condition2}
 \end{figure}
+%% DHB: The labels above each panel wrap in unfortunate ways. Fix.
 
-Next we discuss Condition 2, where we introduce variation in the spectral power distribution function of the light sources.
-This variation makes the task more difficult, because it causes more variation in cone isomerizations due to factors other than the target object LRV.
-Figure~\ref{fig:Condition2}(a, b) show the results when we learned and evaluated the performance of AMA on the cone isomerizations.
+\subsection{Condition 2}
+
+Condition 2 introduces variation in the spectral power distribution of the light sources.
+This variation makes the task more difficult, because it causes more variation in cone excitations due to factors other than the target object LRV.
+Figure~\ref{fig:Condition2}a and b show the results when we learned and evaluated the performance of AMA on the cone excitations.
 Performance is poor.
@@
 other is a variation in overall intensity.
-To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone isomerizations.
-Figure~\ref{fig:Condition2}(c, d) shows that performance improves greatly, and indeed is essentially perfect.
+To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone excitations.
+Figure~\ref{fig:Condition2}(c, d) shows that performance improves greatly, and AMA performance is essentially perfect.
 This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
@@
 contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.
+%% DHB: Need to add REFS in paragraph above.
 
@@
     \end{subfigure}
-    \caption{{\bf Condition 3:} (a) Estimated v/s assigned target LRV for the test images in Condition 3.
-The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.
-(b) Contrast normalized cone isomerizations projected along the first two AMA receptive fields.
-The receptive fields we learnt on the contrast normalized cone isomerizations corresponding to the image patches in the training set.
-(c) First two AMA receptive fields learnt using the contrast normalized cone isomerizations.}
+    \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the contrast normalized cone excitations.
+The relative RMSE is 22.9\%  for linear regression and 13.0\% for AMA.
+(b) Contrast normalized cone excitations for the training set projected along the first two AMA receptive fields.
+(c) First two AMA receptive fields learnt using the contrast normalized cone excitations.}
 \label{fig:Condition3}
 \end{figure}
+%% Panel b shows training set projections, right?
 
-In Condition 3, we introduced variation in the reflectance spectra of the background objects.
+\subsection{Condition 3}
+
+Condition 3 introduces variation in the reflectance spectra of the background objects.
 This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
-We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations 
-(Figure~\ref{fig:case3Estimates}).
-The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions.
+We again trained and evaluated AMA for labeled images patches, using the contrast normalized cone excitations.
+The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions (Figure~\ref{fig:case3Estimates}).
 None-the-less, the estimates provide useful information about the target LRV.
 Indeed, on average the estimates track the true LRV, as seen by the fact that the mean estimate
-(red line) tracks the positive diagonal.
-The increased estimation variability is indicated by the width of the shaded red region.
-Performance of baseline linear regression method (also evaluated using contrast normalized cone isomerizations) is worse than that of the AMA-based estimates.
+(red line) lies along the positive diagonal.
+The increased estimation variability is indicated by the increased width of the shaded red region, relative to its width for the Condition 1 and 2 results.
+Performance of the baseline linear regression method (also evaluated using contrast normalized cone excitations) is worse than that of the AMA-based estimates.
 
 Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA linear receptive fields for training stimuli.
-Here, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
+Although the responses vary systematically with target object LRV, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
+This overlap is the combined effect of the variation in the illumination and background surface spectra.
 Recall, however, that performance is based on six rather than two receptive fields.
-Inclusion of more receptive fields reduces the ambiguity visible in the responses of just the first two.
+Inclusion of more receptive fields reduces the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
+%% DHB: It might be natural here to show a plot of relative RMSE versus number of receptive fields, and for the best number of receptive
+% fields of relative RMSE versus size of training set.  We want to persuade the reader that we are at asymptote.
+
+Figure~\ref{fig:case3RFs} shows the first two receptive fields learned for Condition 3.
+%% DHB: We need to write something interpretive about the RF structure shown in panel c.
+
+%% DHB; We were going to vary the number of secondary reflections modeled in the rendering for one of the conditions, to
+% separate the two possible sources of influence of the background surfaces.
 
@@
 Because we rendered the images, we were able to label each image by the luminance reflectance value (LRV) of a target object.
-Across images, we varied the LRV of the target object, its relative surface reflectance spectrum, 
+Across scenes, we varied the LRV of the target object, its relative surface reflectance spectrum, 
 the spectral power distributions of the light sources, and the reflectance spectra of the background objects in the scene.
@@
 We studied the performance of these estimators as we systematically manipulated the 
-spectral variations in the datasets.
+spectral variation in the datasets.
 
@@
 
-Figure~\ref{fig:barGraphs} summarizes our main findings by plotting the overall relative root mean squared estimation error (relative RMSE) for each condition (defined in Figure~\ref{fig:barGraphs}). 
-In Condition 1, where only the relative target object spectrum varies, luminance constancy is an easy problem and performance is essentially perfect for both the baseline linear regression and AMA methods.
+Figure~\ref{fig:barGraphs} summarizes our main findings.
+It plots the overall relative root mean squared estimation error (relative RMSE) for each condition. 
+In Condition 1, where only the relative target object spectrum varies, luminance constancy poses an easy computationsl problem,
+and performance is essentially perfect for both the baseline linear regression and AMA methods.
 In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
-Indeed, neither of our methods performs well when they directly process the cone isomerizations.
-Performance with both methods improves greatly when the cone isomerizations are contrast normalized. 
+Indeed, neither of our methods performs well when they directly act on the cone excitations.
+Performance with both methods improves greatly when the cone excitations are contrast normalized. 
 Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
-Linear regression does less well, in part because it only has access to cone isomerizations at image locations
+Linear regression does less well, in part because it only has access to cone excitations at image locations
 corresponding to the target object.
-In addition, AMA makes optimal use of the stimulus information across a wider range
-of conditions than linear regression.
-Condition 2, however, does not include scene to scene variation in the background surface reflectances
+Condition 2, however, does not include scene-to-scene variation in the background surface reflectances,
 as occurs in natural viewing.
@@
 because variation in the background surfaces reduces the reliability of the light reflected from these
-surfaces.
-%% READ THIS PART
+surfaces as a cue to the spectral power distribution of the illuminant.
 

### 2018-05-11 Draft4/draft4.tex
DHB finished with this pass.  Onto JB.

@@
 It plots the overall relative root mean squared estimation error (relative RMSE) for each condition. 
-In Condition 1, where only the relative target object spectrum varies, luminance constancy poses an easy computationsl problem,
+In Condition 1, where only the relative target object spectrum varies, luminance constancy poses an easy computational problem,
 and performance is essentially perfect for both the baseline linear regression and AMA methods.
@@
 
-As we noted in the introduction, supervised learning requires large labeled datasets and these are not readily available 
-for the study of how to estimate correlates of object surface reflectance.
+As we noted in the introduction, supervised learning requires large labeled datasets.
+These are not readily available  for the study of how to estimate correlates of object surface reflectance.
 In particular, to obtain ground truth information about the reflectance of objects in a natural image, it is necessary to
 make an independent of the illumination impinging on each object.
-This can be done by inserting a small number of discretely spaced reflectance standards into the scene, but 
+Although this can be done by inserting a small number of discretely spaced reflectance standards into the scene, 
 interpolating to locations between such standards requires strong assumptions.
-The use of rendered images allows us to work with large numbers of labeled images where the reflectance
-and impinging illumination are known precisely at every pixel.
+The use of rendered images allows us to work with large numbers of labeled images where object reflectance
+is precisely known at each pixel.
 
@@
 scene factors that might affect the difficulty of the estimation problem.
-This allows study of the individual effect of each factor as well as their joint effect.
-Here, we exploited this advantage to systematically introduce variation in the relative target object reflectance
+This allows study of the individual effect of each factor as well as their combined effect.
+Here, we exploited this to systematically introduce variation in the relative target object reflectance
 spectrum, the spectrum of the illumination, and the reflectance spectrum of the background objects.
 This allowed us to quantify how each of these variations limits LRV estimation.
-We believe this basic approach can be extended to include parametric control over the amount
+We believe the basic approach can be extended to include parametric control over the amount
 of variation of different factors as well as to include variation in additional factors (see below).
+%% DHB: Update if we add additional analyses as per some of the comments above.
 
-At the same time, it is important to recognize that limitations of the approach.
+At the same time, it is important to recognize limitations of the rendered image approach.
 Virtual rendered scenes are not guaranteed to capture all of the task relevant
 variation that occurs in real scenes.
-Indeed, even casual inspection of our images reveals that they are rendered and
-not real.
+Indeed, even casual inspection of our images reveals that they are rendered and not real.
 Computer graphics is getting better, however, and we expect that the gap between
@@
 from real images.
+%% DHB: Might be able to reference Farid's recent book on this point.
 
@@
 that we now live much of our lives under.
-The surface reflectance datasets captures constraints on naturally occurring reflectance
-functions, but did not sample the environment in a manner that was intended to 
-characterize the relative frequency of occurrence of different reflectance spectra.
+The surface reflectance datasets capture constraints on naturally occurring reflectance
+functions, but the surfaces in the datasets were not sample the environment in a manner that
+characterizes the relative frequency of different reflectance spectra in natural viewing.
 Future work with virtual image datasets will benefit from targeted efforts to characterize
@@
 A challenge for this approach will be to thoughtfully control the increase in problem
-complexity both to keep compute time feasible and to ensure that it is possible to
+complexity, both to keep compute time feasible and to ensure that it is possible to
 extract meaningful insight from the results.
@@
 Luminance constancy is a special case of the more general problem of color constancy.
-The approach we developed here could easily be generalized to the estimation of additional
+The approach we developed here could be generalized to the estimation of additional
 surface reflectance descriptors, such as object hue or chroma.
-As with LRV, these descriptors would be defined by the light reflected from an object 
-under a standard illuminant.
+As with LRV, these descriptors would be defined by the light reflected from an object's
+surface   under a standard illuminant.
 A further advance would be to develop methods for learning receptive fields that are
@@
 For example, one could study discrimination thresholds for target LRV using the
-stimuli that were generated with the methods used
-here.
-We could ask how LRV discrimination thresholds are impacted by 
+stimuli that were generated with the methods used here.
+More specfically, we could ask how LRV discrimination thresholds are impacted by 
 spectral variation in the illuminant, the background objects, and in the target object itself.
@@
 allow inferences about how well human observers make use of the information available
-in the images for performing the LRV discrimination task.
+in the images for performing LRV discrimination.
 We think experiments and analyses along these lines represent an important future direction.
-By coupling the experiments and analyses, we hope to advance our understanding
-of how we see objects in the real world in a principled and controlled manner.
+By coupling the experiments and analyses we hope to advance, in a principled and controlled manner,
+our understanding of how we see objects in the real world .
 

### 2018-05-12 Draft4/draft4.tex
answed some comments

@@
 Subsequent computational work considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}.
-%LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
 A key insight from this computational work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.
@@
 The package builds on our RenderToolblox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
-and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org})
-\cite{jakob2015mitsuba} to produce physically-accurate images from the scene models.
+and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org}, 
+\citeNP{jakob2015mitsuba}) to produce physically-accurate images from the scene models.
 Because each image is rendered from a known scene model, each image pixel can be labeled with 
@@
 statistical structure of natural scenes.
-%% DHB: Need to fix up citations in this paragraph. The URLs for RTB and Mitsuba should be inside the same paraneheses as the citations that
-% follow.
 
@@
 %% DHB: The chromaticities in c and renderings in d are for the spectra in b, right?  I wrote the caption to say so, just checking.
+%% VS: Yes
 
@@
 To obtain illuminant spectra with intensity variation similar to the Granada dataset, we scaled each randomly generated relative spectrum.
-The scale factors were sampled uniformly from range 0.15 and 150.
+The scale factors were sampled randomly on a log-uniform scale in the range [0.15, 150].
 %% DHB: Check that these values are right.  Linear spacing or log spacing?
+%% VS: Yes, log spacing, I have updated the text.
 
@@
 %% DHB: Note that this procedure is different than conditioning the statistical model on the target LRV.  We could switch to the latter if we wished.
+%% VS: I don't think it matters if we care about keeping only one color co-ordinate fixed.
 
@@
     \begin{subfigure}[b]{0.22\textwidth}   
-        \caption{LRV estimates (excitations)}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_a.pdf}
+        \caption{\centering{LRV estimates} \newline\centering{(Excitations)}}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_a.pdf}
         \label{fig:case2IsomerizationEstimates}
@@
         \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{RF responses (excitations)}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_b.pdf}
+        \caption{\centering{RF responses} \newline\centering{(Excitations)}}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_b.pdf}
         \label{fig:case2RFResponseIsomer}
@@
             \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{LRV estimates (Normalized contrast)}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_c.pdf}
+        \caption{\centering{LRV estimates}  \newline \centering{(Normalized contrast)}}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_c.pdf}
         \label{fig:case2ContrastEstimates}
@@
             \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{RF responses (Normalized contrast)}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_d.pdf}
+        \caption{\centering{RF responses}  \newline \centering{(Normalized contrast)}}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_d.pdf}
         \label{fig:case2RFResponseContrast}
@@
 \end{figure}
-%% DHB: The labels above each panel wrap in unfortunate ways. Fix.
 
@@
 This variation makes the task more difficult, because it causes more variation in cone excitations due to factors other than the target object LRV.
-Figure~\ref{fig:Condition2}a and b show the results when we learned and evaluated the performance of AMA on the cone excitations.
+Figure~\ref{fig:Condition2}(a,b) show the results when we learned and evaluated the performance of AMA on the cone excitations.
 Performance is poor.
@@
 To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone excitations.
-Figure~\ref{fig:Condition2}(c, d) shows that performance improves greatly, and AMA performance is essentially perfect.
+Figure~\ref{fig:Condition2}(c,d) shows that performance improves greatly, and AMA performance is essentially perfect.
 This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
@@
 %% Panel b shows training set projections, right?
+%% VS: Yes
 
@@
 of variation in natural scenes.
-%Supervised learning requires large labeled data sets.
-Such data sets are not readily available for the study of color constancy.
-Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
-There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}; \citeauthor{davidPennHyperspectral}), but these are not large enough to drive supervised learning.
 
@@
 
-% MOVE THIS TO DISCUSSION
-%This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
-Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the Discussion.
-% \cite{baker2011database}  \cite{kovacs17shading} \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}
-% Autonmous vehicle work - ask BAW
-
 \bibliography{references}

### 2018-05-14 Draft4/draft4.tex
added new library figure

@@
 We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of a target object's surface reflectance function.
-The LRV is a measure of the overall amount of light reflected by a surface (\citeauthor{astm1121477}).
+The LRV is a measure of the overall amount of light reflected by a surface \cite{astm1121477}.
 More precisely, the LRV is the luminance of the light that would be reflected to the eye from an object with the 
@@
 LRVs range from 0 to 1.
-%% DHB: The ASTM citation is not formatting well. It should give a year.
 
@@
     \end{subfigure}
-    \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional objects inserted.
+    \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional inserted objects.
 The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}
@@
     \end{subfigure}
-\caption{{\b fLibrary base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
+\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
 The panels show different objects inserted in the library base scene.

### 2018-05-15 Draft4/draft4.tex
changes in figures
changed cost function descripton

@@
         \caption{}    
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.pdf}
         \label{fig:introExampleFigure}
@@
     \begin{subfigure}[b]{0.14 \textwidth}
+        \caption{Xylophone}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_b.png}
+        \label{fig:libraryWithXylophone}
+    \end{subfigure}
+     ~ 
+    \begin{subfigure}[b]{0.14 \textwidth}
         \caption{Barrel}
@@
         \caption{Ring toy}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_e.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_d.png}
         \label{fig:libraryWithRingToy}
@@
         \caption{Bottle}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_f.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_e.png}
         \label{fig:libraryWithChampagneBottle}
@@
 Then the rendering viewpoint was set so that the object is at the center of the rendered image.
-In these panels, the full rendered image has been cropped so that the inserted object is more visually salient.}\label{fig:libraryWithTarget}
+In these panels, the full rendered image has been cropped so that the inserted object is visually salient.}\label{fig:libraryWithTarget}
 \end{figure}
@@
 %		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
-		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.png}
+		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.pdf}
  		\label{fig:backgroundVarying}
@@
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
-Here we use a squared error cost function, so that the optimal estimator is the posterior mean.
+Here we use a Kullback-Leibler divergence cost function, so that the optimal estimator is the maximum a posteriori estimate.
 %% DHB: Uniform prior, right? And posterior mean?  If not, correct prose above.

### 2018-05-15 Draft4/draft4.tex
some changes in RF figures

@@
 
-To generate illumination spectra, we developed a statistical model of the Granda daylight measurements (\href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) \cite{hernandez2001color} and sampled randomly from the model (see appendix).
+To generate illumination spectra, we developed a statistical model of the Granda daylight measurements (\citeNP{hernandez2001color}, \href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) and sampled randomly from the model (see appendix).
 The overall intensity of the measurements spans approximately three orders of magnitude.
@@
     \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.28 \textwidth}
+    \begin{subfigure}[b]{0.4 \textwidth}
 	\caption{AMA receptive fields}
-	\includegraphics[width=1.07\textwidth, trim={0 -0.6cm 0 -0.3cm}]{../FiguresDraft4/Figure10/Figure10_c.pdf}
+	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft4/Figure10/Figure10_c.pdf}
 	\label{fig:case1RFs}
@@
     \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.28 \textwidth}
+    \begin{subfigure}[b]{0.4 \textwidth}
 	\caption{AMA receptive fields}
-	\includegraphics[width=1.07\textwidth, trim={0 -0.6cm 0 -0.5cm}]{../FiguresDraft4/Figure12/Figure12_c.pdf}
+	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft4/Figure12/Figure12_c.pdf}
 	\label{fig:case3RFs}

### 2018-05-15 Draft4/draft4.tex
small edits

@@
         \caption{Condition 2}	
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.pdf}
         \label{fig:targetIlluminantVarying}
@@
 In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
-This smaller than the variation we studied, but allows us to show the variation within the dynamic range available for the figure.
+This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for the figure.
 The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
@@
 stimuli that were generated with the methods used here.
-More specfically, we could ask how LRV discrimination thresholds are impacted by 
+More specifically, we could ask how LRV discrimination thresholds are impacted by 
 spectral variation in the illuminant, the background objects, and in the target object itself.

### 2018-05-16 Draft4/draft4.0.tex
johannes edits… conflicts with vijay edits…
will have to debug

--- 2018-05-15 Draft4/draft4.tex
@@
 
- \author{Cottaris}{Nicolas P.}
- {}
- {Department of Psychology, University of Pennsylvania, PA, USA}
- {}{cottaris@sas.upenn.edu}
-
- \author{Heasly}{Benjamin S.}
- {}
- {Department of Psychology, University of Pennsylvania, PA, USA}
- {}{benjamin.heasly@gmail.com}
-
- \author{Brainard}{David H.}
- {}
- {Department of Psychology, University of Pennsylvania, PA, USA}
- {}{brainard@psych.upenn.edu}
-
- \author{Burge}{Johannes}
- {}
- {Department of Psychology, University of Pennsylvania, PA, USA}
- {}{jburge@psych.upenn.edu}
-
 \keywords{color constancy, luminance constancy, supervised learning}
@@
 \section{Introduction}
-The perceived color of an object has important behavioral implications, since color helps to identify objects and their properties \cite{Mollon89, Jacobs81}.
-%The perceived color depends on the surface reflectance of the object, but it is not sensed directly. 
-%Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
-The computational challenge underlying object color perception is that the light reflected from an object depends not just on its surface reflectance, but also on object-extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
-To compute a perceptual representation of object color that is correlated with the object's physical surface reflectance, the brain must account for these object-extrinsic factors.
-The ability of a visual system to compute a representation of object color that is stable against variation in object-extrinsic scene factors is called color constancy. 
-Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
+The perceived color of an object has important behavioral implications because it helps to identify objects and their material properties \cite{Mollon89, Jacobs81}.
+The perceived color depends on the surface reflectance of the object, but it is not sensed directly. 
+Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
+The computational challenge underlying object color perception is that this reflected light depends not just on the object's surface reflectance, but also on extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
+To produce a stable perceptual representation correlated with an object's surface reflectance the brain must account for these intrinsic factors on the reflected light.
+The ability of a visual system to extract such a stable representation is called color constancy. 
+%Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
 In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eye to produce percepts well-correlated with object surface reflectance.
@@
 Subsequent computational work considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}.
+%LET'S SEE IF WE CAN FIND SOME RECENT REVIEWS).
 A key insight from this computational work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.
 But, it is possible to obtain such descriptors by analyzing jointly the light reflected from all of the objects in the scene.
-As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant; evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects \cite{BrainardWandellRetinex,BrainardFreeman}.
+As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant.
+Thus evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects \cite{BrainardWandellRetinex,BrainardFreeman}.
 
@@
         \caption{}    
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.png}
         \label{fig:introExampleFigure}
@@
     \label{introFigure}
-    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination.
-Additionally, the reflected light also depends on geometric factors, such as the object's shape, pose, and position.
-The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable across such variations, an ability called color constancy.
-(b) Images of a sphere under a fixed illuminant.
-Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance function is held fixed.
-The relative reflectance function (i.e.
-the shape of the spectral reflectance function) varies across each row.
+    \caption{(a) {\bf Color Constancy:} The light reflected from an object to the eye depends both on the surface reflectance of the object and the illumination under which it lies.
+Additionally, it also depends on geometric factors, such as the object's shape, pose, and position relative to the observer.
+The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable, an ability called color constancy.
+(b) {\bf Luminance Constancy:} Images of a sphere under a fixed illuminant.
+Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance spectrum held fixed.
+The relative spectrum (shape of reflectance spectrum) varies across each row.
 Within each row, the light reflectance value (LRV) of the spheres is constant.
 The values on the left of each row provide the corresponding LRV.
-We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors.
-Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
+We cast the problem of computational luminance constancy to be that of estimating LRV from the image, across variation in other scene factors: variation in relative surface reflectance, variation in illumination, and variation in the reflectance of the other objects in the scene.}
  \end{figure}
 
-An alternative approach to computational color constancy, which has been less-well explored, is to use supervised machine learning to develop mappings between input images and stable color descriptors \cite{barron2015convolutional}.
+An alternative approach to computational color constancy, which has been less-well explored, is to use supervised machine learning techniques to develop mappings between input images and stable color descriptors \cite{barron2015convolutional}.
 The use of supervised learning to understand perceptual capabilities for natural stimuli has enjoyed success in domains outside of color vision.
@@
 Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
-There are a few databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}), but these are not large enough to drive supervised learning.
+There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}; \citeauthor{davidPennHyperspectral}), but these are not large enough to drive supervised learning.
 
-In this paper, we use high-quality computer graphics to generate large data sets of naturalistic images where the surface reflectance corresponding to each image pixel is known. 
+% Figure 2: Conditions Studied
+\begin{figure}
+\centering
+	\begin{subfigure}[b]{0.33 \textwidth}
+		\caption{Condition 1}
+%		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
+		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.png}
+ 		\label{fig:backgroundVarying}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.33 \textwidth}
+        \caption{Condition 2}	
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.png}
+        \label{fig:targetIlluminantVarying}
+    \end{subfigure}
+	\begin{subfigure}[b]{0.33 \textwidth}
+	\caption{Condition 3}	
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.png}        
+        \label{fig:allSpectraVarying}
+    \end{subfigure}    
+    \caption{{\bf Types of spectral variations studied in this work:} sRGB rendition of multispectral images similar to ones studied in our work.
+The numbers on the left indicate the standard luminance level of the target object.
+5 images are shown at each luminance level.
+We studied three types of spectral variations.
+(a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
+%Condition 2: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra variable, 
+(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
+The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
+Moreover, across the three panels, spheres in corresponding locations have the same surface reflectance.
+In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
+\label{fig:studiedCases}
+\end{figure}
+
+In this paper, we use high-quality computer graphics to generate large data sets of naturalistic images where the surface reflectance and illumination corresponding to each image pixel are known. 
 This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants.
-More specifically, we use this approach to tackle luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
+Here, we use this approach to tackle luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
 
-We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of a target object's surface reflectance function.
-The LRV is a measure of the overall amount of light reflected by a surface \cite{astm1121477}.
+We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of an object's surface reflectance function.
+The LRV is a measure of the overall amount of light reflected by a surface (\citeauthor{astm1121477}).
 More precisely, the LRV is the luminance of the light that would be reflected to the eye from an object with the 
@@
 normalized by the luminance of the reference illuminant itself.
-Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
-LRVs range from 0 to 1.
+Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function \cite{CIE86}.
+LRVs are typically expressed in percent, so that they range from 0 to 100.
 
@@
 Second we use a model of the early visual system to compute the responses of the cone photoreceptor mosaic to the labeled images.
-Third we apply AMA to the cone responses, as well as to a contrast normalized version of the cone responses, to learn task-optimal receptive fields (RFs).
+Third we apply AMA to the cone responses to learn task-optimal receptive fields (RFs).
 Fourth we evaluate how well the responses of the RFs may be decoded to achieve luminance constancy.
@@
 We have developed a rendering package 
-(\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{https://github.com/BrainardLab/VirtualWorldColorConstancy}) 
+(\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{Virtual World Color Constancy}, \href{http://rendertoolbox.org}{RenderToolbox4} \cite{heasly2014rendertoolbox3}) 
 that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
-The package builds on our RenderToolblox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
-and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org}, 
-\citeNP{jakob2015mitsuba}) to produce physically-accurate images from the scene models.
+The package harnesses an open-source computer graphics renderer 
+\cite{jakob2015mitsuba} to produce physically-accurate images from the scene models.
 Because each image is rendered from a known scene model, each image pixel can be labeled with 
@@
 By incorporating statistical models of the variation of object surface reflectance and daylight illumination, 
-the pipeline allows us to produce large labeled sets of images that capture key aspects of the task-relevant 
+the pipeline allows us to produce large labeled sets of images that capture much of the task-relevant 
 statistical structure of natural scenes.
 
-% Figure 2
+% Figure 3
 \begin{figure}[t]
@@
     \end{subfigure}
-    \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional inserted objects.
-The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}
+
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Indoor-plant}    
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_d.png}
+        \label{fig:baseSceneIndoorPlant}
+    \end{subfigure}    
+    ~
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Warehouse}    
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_e.png}
+        \label{fig:baseSceneWarehouse}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.22 \textwidth}
+        \caption{Checkerboard}    
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_f.png}
+        \label{fig:baseSceneCheckerBoard}
+    \end{subfigure}
+    \caption{{\bf Base scenes from the Virtual World Color Constancy (VWCC) library.} Each panel shows a rendering of one tamed base scene without additional objects inserted.
+The reflectance spectra of the distinct surfaces and the spectral power distribution function of the light sources in each scene have been assigned randomly (see text).}\label{fig:baseScenes}
 \end{figure}
-%% DHB: We need to think about how to scale the images for display.  The Library scene is too dark, at least when printed.
 
-% Figure 3
+% Figure 4
 \begin{figure}
@@
 \begin{subfigure}[b]{0.14 \textwidth}
-        \caption{Xylophone}
+        \caption{Small-ball}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_b.png}
-        \label{fig:libraryWithXylophone}
+        \label{fig:libraryWithSmallBall}
     \end{subfigure}
@@
     \end{subfigure}
+    \begin{subfigure}[b]{0.14 \textwidth}
+        \caption{Xylophone}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_d.png}
+        \label{fig:libraryWithXylophone}
+    \end{subfigure}
     ~
@@
         \caption{Ring toy}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_d.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_e.png}
         \label{fig:libraryWithRingToy}
@@
         \caption{Bottle}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_e.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_f.png}
         \label{fig:libraryWithChampagneBottle}
     \end{subfigure}
-\caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
+\caption{{\bf The library base scene with inserted objects.} The rendering package can be used to insert objects into the base scenes.
 The panels show different objects inserted in the library base scene.
-The objects were inserted at a user defined location in the image.
-Then the rendering viewpoint was set so that the object is at the center of the rendered image.
-In these panels, the full rendered image has been cropped so that the inserted object is visually salient.}\label{fig:libraryWithTarget}
+The objects were inserted at a user defined location in the image and then the camera was pointed at the object so that the object is at the center of the rendered image.
+In these panels, the full rendered image has been cropped so that the inserted object is more visually salient.}\label{fig:libraryWithTarget}
 \end{figure}
-%% DHB: Can we render these examples at higher resolution, so that they look nicer?  The blurriness is distracting in the images.
 
-% Figure 4
+% Figure5
 \begin{figure}
@@
     \centering
+        \caption{Background spectra}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_b.png}
+        \label{fig:backGroundVariation}
+    \end{subfigure}
+    ~
+    \begin{subfigure}[b]{0.18 \textwidth}
+    \centering
         \caption{Illumination spectra}
@@
     \end{subfigure}
-          ~  
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \caption{Background spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_b.png}
-        \label{fig:backGroundVariation}
-    \end{subfigure}
-
-    \caption{{\bf Scene transformations.} The properties of a visual scene can broadly be classified into two groups: geometrical (a-b) and spectral (c-e).
-Our rendering package provides control over the properties illustrated by the columns of the figure.
+    \caption{{\bf Transformations of the scene.} The properties of a visual scene can broadly be classified into two groups: Geometrical (a-b) and Spectral (c-e).
+VWCC provides control over such properties as illustrated by the columns.
 (a) Variation in inserted object positions.
-(b) Variation in object pose.
-(c) Variation in the surface reflectance of the target object.
-(d) Variation in the spectral power distributions of the light sources.
-(e) Variation in surface reflectance of the background objects.
+(b) Variation in orientations.
+(c) Variation is the surface reflectance of the target object.
+(d) Variation in surface reflectance of the background objects.
+The reflectances were assigned randomly in each panel.
+(e) Variation in the spectral power distribution function of the light sources.
 \label{fig:VWCCTransformations}}
 \end{figure}
-%% DHB: These are too dark in a printout.
-Let's review how they are scaled.
-Need to make sure we can see an effect of changing the illumination, might want to hand pick the illuminants used here to illustrate the effect.
-
-% Figure 5: Conditions Studied
-\begin{figure}
-\centering
-	\begin{subfigure}[b]{0.33 \textwidth}
-		\caption{Condition 1}
-%		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
-		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.pdf}
- 		\label{fig:backgroundVarying}
-	\end{subfigure}
-	\begin{subfigure}[b]{0.33 \textwidth}
-        \caption{Condition 2}	
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.png}
-        \label{fig:targetIlluminantVarying}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.33 \textwidth}
-	\caption{Condition 3}	
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.png}        
-        \label{fig:allSpectraVarying}
-    \end{subfigure}    
-    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2 and 3.
-The numbers on the left indicate the standard luminance level of the target object.
-5 images are shown at each luminance level.
-We studied three types of spectral variations.
-(a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
-(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
-The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
-Across the three panels, spheres in corresponding locations have the same surface reflectance.
-In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
-This smaller than the variation we studied, but allows us to show the variation within the dynamic range available for the figure.
-The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
-\label{fig:studiedCases}
-\end{figure}
-%% DHB: May also want to render these examples at a higher resolution
 
@@
 In the present work, we used our package to generate datasets of naturalistic scenes and corresponding images.
-We used one fixed base scene and inserted a spherical target object of fixed shape and size into this scene.
-We generated three distinct datasets, which we refer to as Conditions 1-3 and describe below.
+We used one fixed base scene and inserted a target object of fixed shape and size into this scene.
+We generated three distinct datasets: Conditions 1-3.
 Across these datasets the luminance constancy problem, estimating the target object LRV,
@@
 Each dataset consisted of 1000 scenes and corresponding images.
-%% DHB Need to decide how many images we really want for final version of the work.
 
@@
 spectral power distribution of the light sources).
-We used 10 LRV values, equally spaced between 0.2 and 0.6 and generated 100 target surface reflectance spectra at each of these values. 
+We used 10 LRV values, equally spaced between 20 and 60 and generated 100 target surface reflectance spectra at these values. 
 The surface reflectance spectra at the same LRV could differ in their relative shape.
@@
 The position and size of the inserted object, inserted light source and viewpoint were held fixed across all 
-scenes in the database. The geometry is shown in Figure~\ref{fig:3DScene}.
-Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra, as described below.
+scenes in the database, as shown in Figure~\ref{fig:3DScene}.
+Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra as described below.
 Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
@@
     \end{subfigure}
-    \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset.
-Each spectrum is normalized by its mean (with mean taken over wavelength).
-(b) Sample spectra generated using the statistical model derived from normalized Granada dataset.
-(c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in b (red).
-F(d) sRGB renditions of the samples shown in b.}
+    \caption{{\bf Illumination spectra:} (a) Granada dataset.
+The spectra are normalized by the mean over wavelength.
+(b) A representative sample of spectra generated using normalized Granada dataset.
+(c) CIE xy chromaticity diagram of the normalized dataset and the random samples.
+(d) sRGB renditions of the samples from Figure~\ref{fig:illuminantSamples}.}
 \label{fig:illuminant}
 \end{figure}
-%% DHB: The chromaticities in c and renderings in d are for the spectra in b, right?  I wrote the caption to say so, just checking.
-%% VS: Yes
 
-To generate illumination spectra, we developed a statistical model of the Granda daylight measurements (\href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) \cite{hernandez2001color} and sampled randomly from the model (see appendix).
+To generate illumination spectra, we developed a statistical model of the \href{http://colorimaginglab.ugr.es/pages/Data}{Granada daylight measurements} \cite{hernandez2001color} and sampled randomly from the model (see appendix).
 The overall intensity of the measurements spans approximately three orders of magnitude.
-Figure~\ref{fig:granadaData} plots the measurements in normalized form to make apparent the variation in the relative spectra.
+Figure~\ref{fig:granadaData} plots the measurements in normalized form to make apparent the variation in the relative spectra. The spectra are normalized by their mean over wavelength.
 
-Our statistical model approximates the normalized Granda spectra using their first 6 principle components.
+Our statistical model approximates these normalized shapes using their first 6 principle components.
 The variation in these components is modeled with a 6-dimensional Gaussian whose mean and covariance matrix 
-match the sample mean and covariance of the weights on these components obtained from the normalized Granada spectra \cite{BrainardFreeman}.
-To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and then use the weights to generate the corresponding spectrum.
+match the dataset's sample mean and covariance of the weights on these components \cite{BrainardFreeman}.
+To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and generate the corresponding spectrum.
 Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
 Details of the statistical model for illumination are provided in the appendix.
-Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:xyDiagram} and ~\ref{fig:sRGBIlluminant}.
 
-Because our multivariate Gaussian model is based on normalized spectra, it does not embody the large variation in overall intensity of natural daylights.
+Because our multivariate Gaussian model is based on the rescaled spectra, it does not embody the large variation in overall intensity of natural daylights.
 To obtain illuminant spectra with intensity variation similar to the Granada dataset, we scaled each randomly generated relative spectrum.
-The scale factors were sampled randomly on a log-uniform scale in the range [0.15, 150].
-%% DHB: Check that these values are right.  Linear spacing or log spacing?
-%% VS: Yes, log spacing, I have updated the text.
+The scale factors we sampled at random in the range 0.15 and 150.
+Color swatches of samples of illuminant spectra are shown in Figure~\ref{fig:sRGBIlluminant}.
 
@@
     \end{subfigure}
-    \caption{{\bf Statistical model of surface reflectance:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.
-(b) Sample spectra generated using the surface reflectance statistical model.
-(c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances and samples shown in b (red).
-(d) sRGB renditions of the samples shown in b, rendered under the CIE D65 daylight.}
+    \caption{{\bf Surface reflectance spectra:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.(b) Representative samples of randomly generated object surface reflectances.
+(c) CIE xy chromaticity diagram of the Munsell and Vrhel datasets (black) and samples of surface reflectances (red).
+(d) sRGB renditions of the samples of object surface reflectance under CIE D65 daylight.}
 \label{fig:surfaceReflectanceGeneration}
 \end{figure}
-%% DHB: The chromaticities in c and renderings in d are for the spectra in b, right?  I wrote the caption to say so, just checking.
-%% VS: Yes
 
@@
 \includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure8/Figure8.pdf}
-\caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
+\caption{{\bf Target surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
 The figure shows 10 random samples at 10 equally spaced LRV levels in the range [0.2, 0.6].
@@
 
-We generated random reflectance spectra using the same principles we used to model illuminant spectral power distributions.
+We generated random reflectance spectra using the same principles we applied to generate random illuminant spectra.
 We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
@@
 The Vrhel dataset contains 170 spectra measured at 2 nm sampling between 390 nm and 730 nm.
-We resampled these spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm (Figure~\ref{fig:reflectanceSpectra}).
+We resampled these spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
+Figure~\ref{fig:reflectanceSpectra} illustrates the spectra of draws obtained using this procedure.
 Details of the statistical model for surface reflectance spectra are provided in the appendix.
-Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance draws obtained using the model.
 
@@
 scaled such that the LRV had the desired value (see appendix).
-Figure \ref{fig:targetSwatches} shows color renderings of target reflectance spectra under CIE illuminant D65, for the evenly spaced LRV values we studied.
-%% DHB: Note that this procedure is different than conditioning the statistical model on the target LRV.  We could switch to the latter if we wished.
-%% VS: I don't think it matters if we care about keeping only one color co-ordinate fixed.
+Figure \ref{fig:targetSwatches} shows color swatches of target reflectance spectra rendered under CIE illuminant D65, for evenly spaced LRV values.
 
@@
     \hspace{0.1 \textwidth}
-        \caption{Retinal image}
+        \caption{Optical image}
         \vspace{1.5mm}
@@
     \begin{subfigure}[b]{0.2 \textwidth}
-        \caption{LMS normalized cone contrast}
+        \caption{LMS cone contrast}
         \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_d.png}
@@
     \label{fig:sceneWithCroppedImage}
-    \caption{{\bf Pipeline for generating labeled datasets:}  For the supervised learning approach employed in this work, labeled images are generated as follows: (a) A 3D virtual scene, containing a target object is created.
-The rendering viewpoint is selected so that the target object is in the center of the image.
-Spectra are assigned to the target object, illuminants, and other objects in the scene using the statistical models described in the text.
-A multispectral image of the scene is then rendered.
-(b) The central portion of the rendered image, which contains the target object, is cropped.
-(c) The retinal image corresponding to the rendered image is computed, and this is used in turn to compute the excitations (taken as the number of photopigment isomerizations) of the cone photoreceptors.
-The figure shows the a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).
-(d) The cone excitations are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
+    \caption{{\bf Generating labeled dataset for computational analysis:}  For the supervised approach employed in this work, the labeled database is generated as follows: (a) A 3D virtual scene, containing a target object of known surface luminance is created.
+The target object is placed in the camera field of view.
+After assigning spectra to the light sources and other objects in the scene, a multispectral image of the scene is rendered using the Mitsuba software package.
+(b) The central portion of the rendered image, which contains the target object, is cropped from the image.
+(c) The response of the cones in the retina are simulated using the retinal image incident on the cone mosaic.
+The figure shows the retinal image after optical blurring and the location and identity of the cones in the retinal mosaic (L cones: Red, M cones: Green, S cones: Blue).
+(d) The cone responses are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
 Finally, the demosaiced images are contrast normalized separately for each cone type.}
@@
 The resulting retinal image is sampled by a mosaic of cone photoreceptors.
-The excitations of these photoreceptors provide the information about the scene that is available to the neural visual system for further processing.
-Because we are interested in how well luminance constancy may be achieved by the human visual system, we simulated the cone excitations
+The responses of these photoreceptors provide the information about the scene that is available to the neural visual system for further processing.
+Because we are interested in how well luminance constancy may be achieved by the human visual system, we simulated the cone responses
 to our scenes using a model of the early visual system.
@@
 In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle (REFS).
-%% DHB: Johannes to provide his favorite citation or two.  Some review.
+% Johannes to provide his favorite citation or two.  Some review.
 
-We modeled a visual system with a pupil diameter of 3 mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, and spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
+We modeled a visual system with a pupil diameter of 3 mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
 The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
-Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec, and we modeled the Poisson nature of photopigment isomerization \cite{hecht1942energy}.
-This modeling was implemented using the software infrastructure provided by ISETBio (\href{https://isetbio.org}{https://isetbio.org}).
+Cone isomerizations were computed assuming an integration time of 100 msec, and we modeled the Poisson nature of photopigment isomerization \cite{hecht1942energy}. 
+This modeling was implemented using the software infrastructure provided by ISETBio \cite{brainard2015isetbio}.
 
-%% Details on ISETBIO computations from Nicolas (TEXT IN CAPS IS FROM VIJAY)
-%% Scene: 
-%%- the default mean luminance was set to 200, but there is a key-value param that could have overriden this value. 
-%%  I do not know if this were the case.
-%%
-%% % MEAN LUMINANCE = 0, NO SCALING
+% Details from Nicolas (TEXT IN CAPS IS FROM VIJAY)
+% Scene: 
+%- the default mean luminance was set to 200, but there is a key-value param that could have overriden this value. 
+%  I do not know if this were the case.
 %
-%%- The default FOV was 1 deg, but there is a key-value param that could have overriden this value.
-%%  I do not know if this were the case.
-%%
-%% % HORIZONTAL FOV = 1
-%%
-%%- Distance default is 1 meter, but there is  a key-value param that could have overriden this value.
-%%  I do not know if this were the case.
-%%
-%%% DISTANCE 1M
-%%
-%%Optics: 
-%%- 3 mm pupil, 17 mm focal length, with a spectro-spatial OTF described in  
-%%  (Marimont & Wandell (1994) J. Opt. Soc. Amer. A,  v. 11, p. 3113-3122), 
-%%   which includes axial chromatic aberration. However, there is key-value param o skip the OTF. 
-%%   Not sure if this was used.  It it was used, the optics was set to diffraction limited.
-%%
-%% % SKIP OTF OFF:  'skipOTF', false ...  
-%%
-%%Lens: 
-%%- not sure if the optical density is from Wyszecki&Stiles or from Stockman-Sharpe. 
-%%  The isetbio file commend only says it is from PTB. David do you know, or should I check
-%%  the data?
-%%
-%%Cone Mosaic: 
-%%- rectangular cone mosaic with 0.6:0.3:0.1 LMS densities
-%%- FOV was a key-value param, so I do not know what was used.
-%%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
-%%but there is a key-value param that could have overriden this value. I do not know what that parameter value was.
-%%
-%% CONE STRIDE = 3 'coneStride', 3, ... 
-%%
-%%
-%%- There is a key-value pair to also low-pass the optical image with default value to not do so.
-%%  If that was user-overriden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
-%%
-%% LOW PASS FILTER = MATCH CONE STRIDE : lowPassFilter = 'matchConeStride';      
-%%
-%%- IntegrationTime was not specified, so it was the default which is 5 msec.
-%%  The cone isomerization maps were also demosaiced using linear interpolation.
-%%- The default isomerization noise was set to none, but there is a key-value parameter
-%%  that can override it. I do not know what the value of that was.
-%%
-%% ISOMERIZATION NOISE = FROZEN, 'isomerizationNoise', 'frozen'
-%%
-%%-  Finally, there is a key-value param named 'coneEfficiencyBasedReponseScaling', which by default is set to 'none'
-%%   But if it was user-set to non 'none' the code scaled the responses to simulate equal quantal efficiencies 
-%%   for L , M and S coneEfficiencyBasedReponseScaling by undoing filtering by the lens and the macular pigment.
-%%   I do not know if this was used.
-%% 
-%% coneEfficiencyBasedReponseScaling = 'area'
+% % MEAN LUMINANCE = 0, NO SCALING
 
-The cone excitations represent the first step of visual processing.
+%- The default FOV was 1 deg, but there is a key-value param that could have overriden this value.
+%  I do not know if this were the case.
+%
+% % HORIZONTAL FOV = 1
+
+%- Distance default is 1 meter, but there is  a key-value param that could have overriden this value.
+%  I do not know if this were the case.
+%
+%% DISTANCE 1M
+
+%
+%Optics: 
+%- 3 mm pupil, 17 mm focal length, with a spectro-spatial OTF described in  
+%  (Marimont & Wandell (1994) J. Opt. Soc. Amer. A,  v. 11, p. 3113-3122), 
+%   which includes axial chromatic aberration. However, there is key-value param o skip the OTF. 
+%   Not sure if this was used.  It it was used, the optics was set to diffraction limited.
+%
+% % SKIP OTF OFF:  'skipOTF', false ...
+
+%
+%Lens: 
+%- not sure if the optical density is from Wyszecki&Stiles or from Stockman-Sharpe. 
+%  The isetbio file commend only says it is from PTB. David do you know, or should I check
+%  the data?
+%
+%Cone Mosaic: 
+%- rectangular cone mosaic with 0.6:0.3:0.1 LMS densities
+%- FOV was a key-value param, so I do not know what was used.
+%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
+%but there is a key-value param that could have overriden this value. I do not know what that parameter value was.
+%
+% CONE STRIDE = 3 'coneStride', 3, ...
+
+%
+%- There is a key-value pair to also low-pass the optical image with default value to not do so.
+%  If that was user-overriden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
+%
+% LOW PASS FILTER = MATCH CONE STRIDE : lowPassFilter = 'matchConeStride';
+
+%- IntegrationTime was not specified, so it was the default which is 5 msec.
+%  The cone isomerization maps were also demosaiced using linear interpolation.
+%- The default isomerization noise was set to none, but there is a key-value parameter
+%  that can override it. I do not know what the value of that was.
+%
+% ISOMERIZATION NOISE = FROZEN, 'isomerizationNoise', 'frozen'
+
+%-  Finally, there is a key-value param named 'coneEfficiencyBasedReponseScaling', which by default is set to 'none'
+%   But if it was user-set to non 'none' the code scaled the responses to simulate equal quantal efficiencies 
+%   for L , M and S coneEfficiencyBasedReponseScaling by undoing filtering by the lens and the macular pigment.
+%   I do not know if this was used.
+% 
+% coneEfficiencyBasedReponseScaling = 'area'
+
+The cone isomerizations represent the first step of visual processing.
 To capture key properties of post-receptoral processing, such as contrast normalization \cite{heeger1992normalization,albrecht1991motion,carandini2012normalization},
-we processed the excitations as follows:
+we processed the isomerizations as follows:
 First, we generated a response for each cone class at each pixel in the sampled retinal image, using linear interpolation separately for each cone class.
-This gives us a cone excitation image for each cone class.
-We also normalized each cone excitation image by the total area under the corresponding cone spectral sensitivity.
-This makes the magnitude of the cone excitation images similar across cone classes.
-These two processing steps do not alter the information in the cone excitation images.
+This gives us a cone response image for each cone class.
+We also normalized each cone response image by the total area under the corresponding cone spectral sensitivity.
+This makes the magnitude of the cone response images similar across cone classes.
+These two processing steps do not alter the information in the cone response images.
 
-To model contrast coding, we converted each cone excitation image to a corresponding cone contrast image.
-This was accomplished by computing the mean response over the three cone excitation images, and then subtracting off and dividing by this mean.
-To model contrast normalization, we divided the contrast images by the sum of squared contrasts taken over image pixels and cone classes.
-
-%% DHB: We meed to figure out and say something about how we scaled image intensities into a reasonable range.
+To model contrast coding, we converted each cone response image to a corresponding cone contrast image.
+This was accomplished by computing the mean response over the three cone contrast images, and then subtracting off and dividing by this mean.
+To model contrast normalization, we divided by the sum of squared contrasts over image pixels and cone classes.
 
 \subsection{Computational luminance constancy} \label{method:SupervisedLearning}
-We used our datasets to determine how well target object LRV can be estimated from cone excitations and from normalized cone contrasts.
+We used our datasets to determine how well target object LRV can be estimated from cone responses and from normalized cone contrasts.
 Studying both representations allows us to understand how early contrast coding and normalization affect how well luminance constancy can be achieved.
@@
 Then, we approximate these with multivariate Gaussian distributions.
-To estimate the LRV of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRV values given the filter responses.
+With the Gaussian approximation in hand, 
+to estimate the LRV of the target object in a test image, we use Bayes' rule to obtain the posterior distribution over LRV values given the filter responses.
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
-Here we use a Kullback-Leibler divergence cost function, so that the optimal estimator is the maximum a posteriori estimate.
-%% DHB: Uniform prior, right? And posterior mean?  If not, correct prose above.
 
@@
 To provide baselines for evaluation of the estimation method described above, we used linear regression.
-First, we solved for the weights on the average L, M and S cone excitations corresponding to the target object that best predicted the target LRV values.
-We took the average cone responses from a $3 \times 3$ region at the center of the target object.
+First, we solved for the weights on the average L, M and S cone responses target object that best predicted the target LRV values.
+We took the average cone respones from a $3 \times 3$ region at the center of the target object.
 This baseline method disregards information carried the image regions corresponding to the background objects.
 We also performed regression on the contrast normalized version of the cone responses.
-This second baseline method indirectly incorporates information carried in the image regions corresponding to the background objects,
-through their effect on the contrast normalized responses at the center of the target object. 
-We also evaluated the performance of a naive model that estimates the mean of the LRV values in the training set, irrespective
+This baseline method indirectly incorporates information carried the image regions corresponding to the background objects,
+through their effect on the contrast normalized responses from the target object. 
+We also evaluated the performance of a naive model that estimate the mean of the LRV values in the training set, irrespective
 of the image data.
@@
         \begin{subfigure}[b]{0.26 \textwidth}
-        \caption{RF responses}
+        \caption{Receptive field response}
         \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure10/Figure10_b.pdf}
@@
     \end{subfigure}   
-    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the cone excitations.
-Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation.
-The diagonal identity line (dotted blue) indicates veridical estimation.
+    \caption{{\bf Luminance estimates, receptive fields and RF response for condition 1:} (a) Estimated v/s assigned target LRV for the test image in condition 1.
+Solid lines show the mean estimate, the filled region in light color shows $\pm$ 1 standard deviation.
+The diagonal unit slope (dotted blue) line is for reference.
 The standard deviations are too small to be visible.
 Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.1\%  for AMA based estimation.
-(b) Cone excitations projected along the first two AMA receptive fields for training images of Condition 1.
+(b) Cone isomerizations projected along the first two AMA receptive fields for training images of condition 1.
 Each cloud represents the image patches corresponding to one LRV.
-The clouds are approximated by a multivariate Gaussians whose means and variances are approximated by the ellipses shown in the figure.
-(c) The first two AMA receptive fields learnt using the cone excitations of stimuli in the training set.}
+The clouds are approximated by a multivariate Gaussian whose mean and variance are approximated by the ellipses shown in the figure.
+(c) The first two AMA receptive fields learnt using the cone responses of stimuli in the training set.}
 \label{fig:Condition1}
 \end{figure}
-
-\subsection{Condition 1}
 
@@
 In Condition 1, we used an illumination drawn form our daylight sample and thus expect a reasonable degree of similarity to D65.
-%% DHB: We need to say something about how similar.  Might explore different illuminants to dissect how sensitive the estimation
-% is to whether the fixed illuminant is D65 or something else.  Probably not very, but this is an example of something we can exploit
-% our graphics approach to understand, and we want to build up examples.
 
 We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
-We trained and evaluated AMA on the cone excitations to the image patches.
+For this condition, we trained and evaluated AMA on the cone responses to the image patches.
+Figure~\ref{fig:case1RFResponse} shows the responses of the first two receptive fields to all the image patches in the training set.
+Each individual point represents the receptive field responses to a single image patch.
+Each point is color coded according to the LRV corresponding to the target object in the patch.
+The responses segregate according to the target LRV.
+This means that the responses may be used to accurately decode LRV, confirming the intuition that computational
+luminance constancy is readily achieved for Condition 1.
+
 Decoding performance for the test set is shown in Figure~\ref{fig:case1Estimates}.
-As expected, the LRV estimates obtained by decoding the AMA receptive field responses are essentially perfect.
+As expected, the LRV estimates obtained by decoding the AMA receptive field responses are veridical.
 Figure~\ref{fig:case1Estimates} also shows the performance of the baseline linear regression method, again trained
@@
 
-Figure~\ref{fig:case1RFResponse} shows the responses of the first two receptive fields to all the image patches in the training set.
-Each individual point represents the receptive field responses to a single image patch.
-Each point is color coded according to the LRV corresponding to the target object in the patch.
-The responses segregate according to the target LRV, which is the feature required to support the high level 
-of estimation performance shown in Figure~\ref{fig:case1Estimates}.
-
 Figure~\ref{fig:case1RFs} shows the first two AMA receptive fields.
-Each of these, in essence, takes a weighted sum of the L and M cone excitations at the target object location.
-The cone excitations in the background regions and the S cone excitations are largely ignored.
+Each of these, in essence, takes a weighted sum of the L and M cone isomerizations at the target object location.
+The isomerizations in the background regions and the S cone isomerizations are largely ignored.
 These receptive fields make sense.
@@
 through light scattered from them onto the target.
-In addition, luminance is primarily determined by L and M cone s, so the S cones should make little
-contribution.
-%% DHB: Can we add a color scale bar to the plots?
+In addition, luminance is primarily determined by L and M cone isomerizations.
 
-%% Figure condition 2: Excitations Fail
+%% Figure condition 2: Isomerization Fails
 \begin{figure}
@@
     \begin{subfigure}[b]{0.22\textwidth}   
-        \caption{\centering{LRV estimates} \newline\centering{(Excitations)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_a.pdf}
+        \caption{RF response (Isomerization)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_a.pdf}
         \label{fig:case2IsomerizationEstimates}
@@
         \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{\centering{RF responses} \newline\centering{(Excitations)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_b.pdf}
+        \caption{LRV estimates (Isomerization)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_b.pdf}
         \label{fig:case2RFResponseIsomer}
@@
             \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{\centering{LRV estimates}  \newline \centering{(Normalized contrast)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_c.pdf}
+        \caption{RF response (Contrast)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_c.pdf}
         \label{fig:case2ContrastEstimates}
@@
             \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{\centering{RF responses}  \newline \centering{(Normalized contrast)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_d.pdf}
+        \caption{LRV estimates (Contrast)}
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure11/Figure11_d.pdf}
         \label{fig:case2RFResponseContrast}
     \end{subfigure}
-    \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the cone excitations.
-The relative RMSE is high (41.4\% for linear regression and 31.3\% for AMA based estimation).
-(b) Cone isomerizations projected on AMA receptive fields calculated using cone excitations.
-(c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the contrast normalized cone excitations.
+    \caption{{\bf Condition 2:} (a) Mean LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA based estimators on the cone response.
+The relative RMSE is high (41.4\% for Linear regression and 31.3\% for AMA based estimation).
+(b) Cone isomerizations projected on AMA receptive fields calculated using photoreceptor response.
+(c) Estimated v/s assigned target LRV for the image in condition 2 learnt and evaluated on contrast normalized cone isomerizations.
 The relative RMSE of estimation is 9.3\% for linear regression and 1.1\% for AMA based estimator.
-(d) The contrast normalized cone excitations projected along the first two AMA receptive fields.
-The receptive fields were learned using AMA and the contrast normalized cone excitations.
-For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is contrast normalized cone excitations rather than the cone excitations themselves.}
+(d) The contrast normalized cone isomerizations projected along the first two AMA receptive fields.
+The receptive fields were calculated using the contrast normalized cone isomerizations.
+For Condition 2, the response corresponding to individual image patches at each LRV level separates much better in this representation.}
 \label{fig:Condition2}
@@
 
-\subsection{Condition 2}
-
-Condition 2 introduces variation in the spectral power distribution of the light sources.
-This variation makes the task more difficult, because it causes more variation in cone excitations due to factors other than the target object LRV.
-Figure~\ref{fig:Condition2}(a,b) show the results when we learned and evaluated the performance of AMA on the cone excitations.
+Next we discuss Condition 2, where we introduce variation in the spectral power distribution function of the light sources.
+This variation makes the task more difficult, because it causes more variation in cone isomerizations due to factors other than the target object LRV.
+Figure~\ref{fig:Condition2}(a, b) show the results when we learned and evaluated the performance of AMA on the cone isomerizations.
 Performance is poor.
@@
 other is a variation in overall intensity.
-To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone excitations.
-Figure~\ref{fig:Condition2}(c,d) shows that performance improves greatly, and AMA performance is essentially perfect.
+To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone isomerizations.
+Figure~\ref{fig:Condition2}(c, d) shows that performance improves greatly, and indeed is essentially perfect.
 This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
@@
 contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.
-%% DHB: Need to add REFS in paragraph above.
 
@@
     \end{subfigure}
-    \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the contrast normalized cone excitations.
-The relative RMSE is 22.9\%  for linear regression and 13.0\% for AMA.
-(b) Contrast normalized cone excitations for the training set projected along the first two AMA receptive fields.
-(c) First two AMA receptive fields learnt using the contrast normalized cone excitations.}
+    \caption{{\bf Condition 3:} (a) Estimated v/s assigned target LRV for the test images in Condition 3.
+The relative error of estimation is 22.9\%  for linear regression and 13.0\% for AMA.
+(b) Contrast normalized cone isomerizations projected along the first two AMA receptive fields.
+The receptive fields we learnt on the contrast normalized cone isomerizations corresponding to the image patches in the training set.
+(c) First two AMA receptive fields learnt using the contrast normalized cone isomerizations.}
 \label{fig:Condition3}
 \end{figure}
-%% Panel b shows training set projections, right?
-%% VS: Yes
 
-\subsection{Condition 3}
-
-Condition 3 introduces variation in the reflectance spectra of the background objects.
+In Condition 3, we introduced variation in the reflectance spectra of the background objects.
 This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
-We again trained and evaluated AMA for labeled images patches, using the contrast normalized cone excitations.
-The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions (Figure~\ref{fig:case3Estimates}).
+We again trained and evaluated AMA for labeled images patches in this condition using the contrast-normalized cone isomerizations 
+(Figure~\ref{fig:case3Estimates}).
+The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions.
 None-the-less, the estimates provide useful information about the target LRV.
 Indeed, on average the estimates track the true LRV, as seen by the fact that the mean estimate
-(red line) lies along the positive diagonal.
-The increased estimation variability is indicated by the increased width of the shaded red region, relative to its width for the Condition 1 and 2 results.
-Performance of the baseline linear regression method (also evaluated using contrast normalized cone excitations) is worse than that of the AMA-based estimates.
+(red line) tracks the positive diagonal.
+The increased estimation variability is indicated by the width of the shaded red region.
+Performance of baseline linear regression method (also evaluated using contrast normalized cone isomerizations) is worse than that of the AMA-based estimates.
 
 Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA linear receptive fields for training stimuli.
-Although the responses vary systematically with target object LRV, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
-This overlap is the combined effect of the variation in the illumination and background surface spectra.
+Here, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
 Recall, however, that performance is based on six rather than two receptive fields.
-Inclusion of more receptive fields reduces the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
-%% DHB: It might be natural here to show a plot of relative RMSE versus number of receptive fields, and for the best number of receptive
-% fields of relative RMSE versus size of training set.  We want to persuade the reader that we are at asymptote.
-
-Figure~\ref{fig:case3RFs} shows the first two receptive fields learned for Condition 3.
-%% DHB: We need to write something interpretive about the RF structure shown in panel c.
-
-%% DHB; We were going to vary the number of secondary reflections modeled in the rendering for one of the conditions, to
-% separate the two possible sources of influence of the background surfaces.
+Inclusion of more receptive fields reduces the ambiguity visible in the responses of just the first two.
 
@@
 Because we rendered the images, we were able to label each image by the luminance reflectance value (LRV) of a target object.
-Across scenes, we varied the LRV of the target object, its relative surface reflectance spectrum, 
+Across images, we varied the LRV of the target object, its relative surface reflectance spectrum, 
 the spectral power distributions of the light sources, and the reflectance spectra of the background objects in the scene.
@@
 We studied the performance of these estimators as we systematically manipulated the 
-spectral variation in the datasets.
+spectral variations in the datasets.
 
@@
 
-Figure~\ref{fig:barGraphs} summarizes our main findings.
-It plots the overall relative root mean squared estimation error (relative RMSE) for each condition. 
-In Condition 1, where only the relative target object spectrum varies, luminance constancy poses an easy computational problem,
-and performance is essentially perfect for both the baseline linear regression and AMA methods.
+Figure~\ref{fig:barGraphs} summarizes our main findings by plotting the overall relative root mean squared estimation error (relative RMSE) for each condition (defined in Figure~\ref{fig:barGraphs}). 
+In Condition 1, where only the relative target object spectrum varies, luminance constancy is an easy problem and performance is essentially perfect for both the baseline linear regression and AMA methods.
 In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
-Indeed, neither of our methods performs well when they directly act on the cone excitations.
-Performance with both methods improves greatly when the cone excitations are contrast normalized. 
+Indeed, neither of our methods performs well when they directly process the cone isomerizations.
+Performance with both methods improves greatly when the cone isomerizations are contrast normalized. 
 Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
-Linear regression does less well, in part because it only has access to cone excitations at image locations
+Linear regression does less well, in part because it only has access to cone isomerizations at image locations
 corresponding to the target object.
-Condition 2, however, does not include scene-to-scene variation in the background surface reflectances,
+In addition, AMA makes optimal use of the stimulus information across a wider range
+of conditions than linear regression.
+Condition 2, however, does not include scene to scene variation in the background surface reflectances
 as occurs in natural viewing.
@@
 because variation in the background surfaces reduces the reliability of the light reflected from these
-surfaces as a cue to the spectral power distribution of the illuminant.
+surfaces.
+%% READ THIS PART
 
@@
 
-As we noted in the introduction, supervised learning requires large labeled datasets.
-These are not readily available  for the study of how to estimate correlates of object surface reflectance.
+As we noted in the introduction, supervised learning requires large labeled datasets and these are not readily available 
+for the study of how to estimate correlates of object surface reflectance.
 In particular, to obtain ground truth information about the reflectance of objects in a natural image, it is necessary to
 make an independent of the illumination impinging on each object.
-Although this can be done by inserting a small number of discretely spaced reflectance standards into the scene, 
+This can be done by inserting a small number of discretely spaced reflectance standards into the scene, but 
 interpolating to locations between such standards requires strong assumptions.
-The use of rendered images allows us to work with large numbers of labeled images where object reflectance
-is precisely known at each pixel.
+The use of rendered images allows us to work with large numbers of labeled images where the reflectance
+and impinging illumination are known precisely at every pixel.
 
@@
 scene factors that might affect the difficulty of the estimation problem.
-This allows study of the individual effect of each factor as well as their combined effect.
-Here, we exploited this to systematically introduce variation in the relative target object reflectance
+This allows study of the individual effect of each factor as well as their joint effect.
+Here, we exploited this advantage to systematically introduce variation in the relative target object reflectance
 spectrum, the spectrum of the illumination, and the reflectance spectrum of the background objects.
 This allowed us to quantify how each of these variations limits LRV estimation.
-We believe the basic approach can be extended to include parametric control over the amount
+We believe this basic approach can be extended to include parametric control over the amount
 of variation of different factors as well as to include variation in additional factors (see below).
-%% DHB: Update if we add additional analyses as per some of the comments above.
 
-At the same time, it is important to recognize limitations of the rendered image approach.
+At the same time, it is important to recognize that limitations of the approach.
 Virtual rendered scenes are not guaranteed to capture all of the task relevant
 variation that occurs in real scenes.
-Indeed, even casual inspection of our images reveals that they are rendered and not real.
+Indeed, even casual inspection of our images reveals that they are rendered and
+not real.
 Computer graphics is getting better, however, and we expect that the gap between
@@
 from real images.
-%% DHB: Might be able to reference Farid's recent book on this point.
 
@@
 that we now live much of our lives under.
-The surface reflectance datasets capture constraints on naturally occurring reflectance
-functions, but the surfaces in the datasets were not sample the environment in a manner that
-characterizes the relative frequency of different reflectance spectra in natural viewing.
+The surface reflectance datasets captures constraints on naturally occurring reflectance
+functions, but did not sample the environment in a manner that was intended to 
+characterize the relative frequency of occurrence of different reflectance spectra.
 Future work with virtual image datasets will benefit from targeted efforts to characterize
@@
 of variation in natural scenes.
+%Supervised learning requires large labeled data sets.
+Such data sets are not readily available for the study of color constancy.
+Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
+There are some smaller databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}; \citeauthor{davidPennHyperspectral}), but these are not large enough to drive supervised learning.
 
@@
 A challenge for this approach will be to thoughtfully control the increase in problem
-complexity, both to keep compute time feasible and to ensure that it is possible to
+complexity both to keep compute time feasible and to ensure that it is possible to
 extract meaningful insight from the results.
@@
 Luminance constancy is a special case of the more general problem of color constancy.
-The approach we developed here could be generalized to the estimation of additional
+The approach we developed here could easily be generalized to the estimation of additional
 surface reflectance descriptors, such as object hue or chroma.
-As with LRV, these descriptors would be defined by the light reflected from an object's
-surface   under a standard illuminant.
+As with LRV, these descriptors would be defined by the light reflected from an object 
+under a standard illuminant.
 A further advance would be to develop methods for learning receptive fields that are
@@
 For example, one could study discrimination thresholds for target LRV using the
-stimuli that were generated with the methods used here.
-More specfically, we could ask how LRV discrimination thresholds are impacted by 
+stimuli that were generated with the methods used
+here.
+We could ask how LRV discrimination thresholds are impacted by 
 spectral variation in the illuminant, the background objects, and in the target object itself.
@@
 allow inferences about how well human observers make use of the information available
-in the images for performing LRV discrimination.
+in the images for performing the LRV discrimination task.
 We think experiments and analyses along these lines represent an important future direction.
-By coupling the experiments and analyses we hope to advance, in a principled and controlled manner,
-our understanding of how we see objects in the real world .
+By coupling the experiments and analyses, we hope to advance our understanding
+of how we see objects in the real world in a principled and controlled manner.
+
+% MOVE THIS TO DISCUSSION
+%This general approach has been adopted by other labs for the study of computational estimation of optical flow (Baker et al., 2011) and is becoming increasingly popular (Kovacs, Bell, Snavely, & Bala, 2017), as well as for the generation of stimuli for the study of human perception (e.g., Boyaci, Maloney, & Hersh, 2003; Todd & Mingolla, 1983; Arend & Reeves, 1986; Johnston, Cumming, & Parker, 1993).
+Of course, success within the domain of graphics images does not guarantee smooth generalization to real natural images, a point we return to in the Discussion.
+% \cite{baker2011database}  \cite{kovacs17shading} \citeNP{boyaci2003effect, todd1983perception, arend1986Simultaneous, johnston1993integration}
+% Autonmous vehicle work - ask BAW
 

### 2018-05-16 Draft4/draft4.tex
small edits
Today

@@
 \section{Introduction}
-The perceived color of an object has important behavioral implications, since color helps to identify objects and their properties \cite{Mollon89, Jacobs81}.
-%The perceived color depends on the surface reflectance of the object, but it is not sensed directly. 
-%Rather, it is computed by the brain starting with the retinal image of the light reflected from an object to the eye.
-The computational challenge underlying object color perception is that the light reflected from an object depends not just on its surface reflectance, but also on object-extrinsic factors such as the illumination, the object's pose, and the position of the observer (Fig.~\ref{fig:introSchematic}).
-To compute a perceptual representation of object color that is correlated with the object's physical surface reflectance, the brain must account for these object-extrinsic factors.
-The ability of a visual system to compute a representation of object color that is stable against variation in object-extrinsic scene factors is called color constancy. 
-Although human color constancy is by no means perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
-In this paper, we consider the computational problem of color constancy, that is, how in principle could a visual system process the light reflected to the eye to produce percepts well-correlated with object surface reflectance.
+The perceived color of an object has important behavioral implications because color helps to identify objects and their surface properties \cite{Mollon89, Jacobs81}.
+The computational challenge underlying object color perception is that the light reflected from an object depends not just on the object's surface reflectance, but also 
+on object-extrinsic factors such as the pose of the object, the illumination in the scene, and the position of the observer in the scene (Fig.~\ref{fig:introSchematic}).
+To compute a perceptual representation of object color that is correlated with the object's physical surface reflectance, the visual system must account for these object-extrinsic factors.
+The ability of a visual system to compute a representation of object color that is stable against variation in object-extrinsic factors is called color constancy. 
+Although human color constancy is not perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}. 
+In this paper, we consider the computational problem of color constancy.
+Specifically, we ask how a visual system should process the light entering the eye that has reflected off objects to produce percepts well-correlated with object surface reflectance.
 
 Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
-Subsequent computational work considered more complex geometries and incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{funt1988color, D'ZmuraConstancy3, barron2012color, D'ZmuraIversonSinger,BrainardFreeman}.
-A key insight from this computational work is that stable color descriptors of a target object cannot be obtained from the light reflected from the target object alone.
-But, it is possible to obtain such descriptors by analyzing jointly the light reflected from all of the objects in the scene.
-As a consequence, the performance of color constancy algorithms will be affected by variation in the surface reflectance of all of the objects in the scene \cite{BrainardWandellRetinex}, not just by variation in the illuminant; evaluation of constancy algorithms must include assessment of their performance with respect to both variation in the illumination and the surface reflectance of all of the scene objects \cite{BrainardWandellRetinex,BrainardFreeman}.
+Subsequent work incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{D'ZmuraConstancy3, D'ZmuraIversonSinger,BrainardFreeman}.
+A key insight from this computational work is that stable color descriptors of a target object cannot be obtained soley from the light reflected from that target object.
+But it is possible to obtain such descriptors by jointly analyzing the light reflected from multiple objects in the scene.
+As a consequence, the performance of color constancy algorithms will be affected both by variation in the illumination and in the surface reflectance of other objects in the scene and should therefore be evaluated with respect to both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}.
+There has also been work that generalizes to more complex viewing geometries \cite{funt1988color, barron2012color}.
 
@@
 
-An alternative approach to computational color constancy, which has been less-well explored, is to use supervised machine learning to develop mappings between input images and stable color descriptors \cite{barron2015convolutional}.
-The use of supervised learning to understand perceptual capabilities for natural stimuli has enjoyed success in domains outside of color vision.
+Recently, supervised statistical learning methods have been applied to the computational problem of color constancy.
+These methods use the joint statistics of labeled images and scene variables to learn mappings that extract stable surface color descriptors from image input \cite{barron2015convolutional}.
+This general statistical learning approach has been useful for other perceptual problems in early and mid-level vison. domains of vision. 
 For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal}.
-It has been used to develop ideal observers for speed, focus error, and disparity estimation that provide excellent models of human performance \cite{burge2011optimal, burge2014optimal, burge2015optimal}.
+It has been used to develop ideal observers for focus error, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2014optimal, burge2015optimal}.
 In this paper, we apply AMA to a special case of computational color constancy. 
+%% JDB: Please add 2012 reference that I will provide.
 
@@
 Such data sets are not readily available for the study of color constancy.
-Although there are databases of calibrated color images, these do not provide ground truth information about surface reflectance and illuminantion at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
+Although there are datasets of calibrated color images, these datasets do not provide ground truth information about surface reflectance and illumination at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
 There are a few databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}), but these are not large enough to drive supervised learning.
 
-In this paper, we use high-quality computer graphics to generate large data sets of naturalistic images where the surface reflectance corresponding to each image pixel is known. 
+In this paper, we use high-quality computer graphics to generate large datasets of naturalistic images where the surface reflectance corresponding to each image pixel is known. 
 This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants.
-More specifically, we use this approach to tackle luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
+We use this approach to tackle the specific problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
 
@@
 The LRV is a measure of the overall amount of light reflected by a surface \cite{astm1121477}.
-More precisely, the LRV is the luminance of the light that would be reflected to the eye from an object with the 
-specified surface reflectance function when the object is illuminated by a reference illuminant,
-normalized by the luminance of the reference illuminant itself.
+Computation of an LRV from a surface reflectance function proceeds in two steps.
+First, we computed the luminance of the light that would be reflected from the surface under a reference illuminant.
+Second, we normalize the result by the luminance of the reference illuminant itself.
 Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
-LRVs range from 0 to 1.
+Sometimes LRVs are expressed as a percentage.
+Here we express LRVs as proportion, so that they take on values between 0 and 1.
 
@@
 There are four key parts to our methods.
-First we generate a labeled set of training images.
-Second we use a model of the early visual system to compute the responses of the cone photoreceptor mosaic to the labeled images.
-Third we apply AMA to the cone responses, as well as to a contrast normalized version of the cone responses, to learn task-optimal receptive fields (RFs).
-Fourth we evaluate how well the responses of the RFs may be decoded to achieve luminance constancy.
-
-\subsection{Labeled training data} \label{method:VirtualWorld}
-\subsubsection{Virtual naturalistic scenes}
-The light that reflects from objects to the eyes depends on many factors.
-These include the surface reflectance, texture, material and geometry of the objects, 
-the spectral power distribution function of the illuminants, and the position of the observer.
-We have developed a rendering package 
-(\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{https://github.com/BrainardLab/VirtualWorldColorConstancy}) 
-that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
-The package builds on our RenderToolblox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
-and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org}, 
-\citeNP{jakob2015mitsuba}) to produce physically-accurate images from the scene models.
-Because each image is rendered from a known scene model, each image pixel can be labeled with 
-the surface reflectance of the corresponding scene object.
-By incorporating statistical models of the variation of object surface reflectance and daylight illumination, 
-the pipeline allows us to produce large labeled sets of images that capture key aspects of the task-relevant 
-statistical structure of natural scenes.
+First, we generate a labeled set of training images.
+Second, we use a model of the early visual system to compute the responses of the cone photoreceptor mosaic to the labeled images.
+Third, we apply AMA to the cone responses, as well as to a contrast normalized version of the cone responses, to learn task-optimal receptive fields (RFs).
+Fourth, we evaluate how well the responses of the RFs may be decoded to achieve luminance constancy.
 
@@
 %% DHB: We need to think about how to scale the images for display.  The Library scene is too dark, at least when printed.
+
+\subsection{Labeled training data} \label{method:VirtualWorld}
+\subsubsection{Virtual naturalistic scenes}
+The light that reflects from objects to the eyes depends on many factors.
+These include the surface reflectance, texture, material and geometry of the objects, 
+the spectral power distribution function of the illuminants, and the position of the observer.
+We have developed a rendering package 
+(\href{https://github.com/BrainardLab/VirtualWorldColorConstancy}{https://github.com/BrainardLab/VirtualWorldColorConstancy}) 
+that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
+The package builds on our RenderToolblox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
+and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org}, 
+\citeNP{jakob2015mitsuba}) to produce physically-accurate images from the scene models.
+Because each image is rendered from a known scene model, each image pixel can be labeled with 
+the surface reflectance of the corresponding scene object.
+By incorporating statistical models of the variation of object surface reflectance and daylight illumination, 
+the pipeline allows us to produce large labeled sets of images that capture key aspects of the task-relevant 
+statistical structure of natural scenes.
 
@@
 	\caption{Condition 3}	
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.png}        
+        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.pdf}        
         \label{fig:allSpectraVarying}
@@
 Base scenes specify an arrangement of objects and light sources.
-Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}).
-Once the position, size and pose of the inserted objects has been set, 
-our package allows the assignment of a surface reflectance function to each object in the scene 
-and a spectral power distribution function to each light source (Fig.~\ref{fig:VWCCTransformations}).
-This provides a complete scene model which can be rendered from any specified viewpoint.
+Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and additional light sources.
+Once the position, size and pose of the inserted objects and lightsources have been set, 
+a surface reflectance function can be assigned to each object in the scene, and a spectral power distribution function can be assigned to each light source (Fig.~\ref{fig:VWCCTransformations}).
+The resulting scene model can then be rendered from any specified viewpoint.
 
@@
 We generated three distinct datasets, which we refer to as Conditions 1-3 and describe below.
-Across these datasets the luminance constancy problem, estimating the target object LRV,
+Across these datasets the luminance constancy problem (i.e. estimating the target object LRV)
 becomes progressively more difficult (Fig.~\ref{fig:studiedCases}).
-Each dataset consisted of 1000 scenes and corresponding images.
+%Each dataset consisted of 1000 scenes and corresponding images, 100 for each of 10 LRV values.
 %% DHB Need to decide how many images we really want for final version of the work.
 
-In Condition 1, we only varied the surface reflectance spectrum of the target object.
-The reflectance spectra of the background objects, and the spectral power distributions of the light sources were kept fixed.
-In Condition 2, in addition to the reflectance spectrum of the target object,
-we also varied the spectral power distribution of the light sources.
-Finally, in Condition 3 we varied all three factors (target object surface 
-reflectance spectrum, reflectance spectra of the background objects, 
-spectral power distribution of the light sources).
-We used 10 LRV values, equally spaced between 0.2 and 0.6 and generated 100 target surface reflectance spectra at each of these values. 
-The surface reflectance spectra at the same LRV could differ in their relative shape.
 The variation within our datasets captures the essence of the computational problem of lightness constancy
 up to effects of scene geometry, an additional richness that we do not address in this paper.
+In Condition 1, the surface reflectance spectrum of the target object was the only source of scene variation other than the target object LRV..
+The reflectance spectra of the background objects, and the spectral power distributions of the light sources were kept fixed.
+In Condition 2, the spectral power distribution of the light sources varied in addition to the reflectance spectrum of the target object,
+Finally, in Condition 3 three distinct scene factors--target object surface 
+reflectance spectrum, reflectance spectra of the background objects, and
+spectral power distribution of the light sources--varied in addition to the target object LRV.
+Each condition had a corresponding dataset of 1000 scenes and images, 100 for each of 10 target object LRV values.
+The LRV values were equally spaced between 0.2 and 0.6.
+For each LRV value, a different target surface reflectance spectra for each of the 100 scenes.
+Thus, for each target object LRV value, the shape of the target object surface reflectance spectra could differ.
 
@@
 \end{figure}
-%% DHB: The chromaticities in c and renderings in d are for the spectra in b, right?  I wrote the caption to say so, just checking.
-%% VS: Yes
 
-To generate illumination spectra, we developed a statistical model of the Granda daylight measurements (\citeNP{hernandez2001color}, \href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) and sampled randomly from the model (see appendix).
-The overall intensity of the measurements spans approximately three orders of magnitude.
+To generate illumination spectra, we first developed a statistical model of the Granada daylight measurements (\href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) \cite{hernandez2001color} and then sampled randomly from the model (see appendix).
+To match the wavelength spacing we use in rendering, we resampled the wavelength spacing of the Granada spectra to
+to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
+
+The overall intensity of the Granada spectra spans approximately three orders of magnitude.
 Figure~\ref{fig:granadaData} plots the measurements in normalized form to make apparent the variation in the relative spectra.
+To normalize the spectra, we divided each spectrum by its mean power.
 
-Our statistical model approximates the normalized Granda spectra using their first 6 principle components.
-The variation in these components is modeled with a 6-dimensional Gaussian whose mean and covariance matrix 
-match the sample mean and covariance of the weights on these components obtained from the normalized Granada spectra \cite{BrainardFreeman}.
-To generate a random relative illuminant spectrum, we take a draw from this Gaussian to obtain weights and then use the weights to generate the corresponding spectrum.
+Our statistical model approximates the normalized Granada spectra using the first 6 principle components.
+The variation in the weights on these components is modeled with a 6-dimensional Gaussian.
+The mean and covariance matrix of the Gaussian match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
+% on these components obtained from the normalized Granada spectra 
+To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
 Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
@@
 Because our multivariate Gaussian model is based on normalized spectra, it does not embody the large variation in overall intensity of natural daylights.
-To obtain illuminant spectra with intensity variation similar to the Granada dataset, we scaled each randomly generated relative spectrum.
-The scale factors were sampled randomly on a log-uniform scale in the range [0.15, 150].
-%% DHB: Check that these values are right.  Linear spacing or log spacing?
-%% VS: Yes, log spacing, I have updated the text.
+To obtain illuminant spectra with intensity variation similar to the Granada dataset, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution in the range [0.15, 150].
+This procedure restores the three-order of magnitude intensity variation present in the original dataset.
 
@@
 \end{figure}
-%% DHB: The chromaticities in c and renderings in d are for the spectra in b, right?  I wrote the caption to say so, just checking.
-%% VS: Yes
 
@@
 
-We generated random reflectance spectra using the same principles we used to model illuminant spectral power distributions.
+To generate random reflectance spectra, we used the same principles we used to model illuminant spectral power distributions.
 We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
-measurements to create a database containing 632 reflectance spectra (Figure~\ref{fig:reflectanceSpectra}).
-The Munsell database contains 462 spectra each measured at 5 nm sampling intervals between 380nm and 780nm.
-The Vrhel dataset contains 170 spectra measured at 2 nm sampling between 390 nm and 730 nm.
-We resampled these spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm (Figure~\ref{fig:reflectanceSpectra}).
+measurements to create a database containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data) (Figure~\ref{fig:reflectanceSpectra}).
+We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm (Figure~\ref{fig:reflectanceSpectra}).
 Details of the statistical model for surface reflectance spectra are provided in the appendix. 
@@
 
-For generating the target object reflectance at a particular luminance, the values in a generated spectrum were 
+For generating the target object reflectance at a particular luminance, the generated reflectance spectrum was 
 scaled such that the LRV had the desired value (see appendix).
@@
 
-We focussed our analysis on regions of the image local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
-This choice is motivated by the observation that neural receptive fields in the early visual pathways (e.g., retina, primary visual cortex) pool information locally.
+We focussed our analysis on image regions local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
 In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle (REFS).
+The local analysis is thus motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
 %% DHB: Johannes to provide his favorite citation or two.  Some review.
 
-We modeled a visual system with a pupil diameter of 3 mm, optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, and spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
+We modeled a visual system limited by diffraction caused by a 3mm diameter pupil, optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, and spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
 The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
-Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec, and we modeled the Poisson nature of photopigment isomerization \cite{hecht1942energy}.
+Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec.
+The Poisson nature of the photopigment isomerization was also included \cite{hecht1942energy}.
 This modeling was implemented using the software infrastructure provided by ISETBio (\href{https://isetbio.org}{https://isetbio.org}).
@@
 
-The cone excitations represent the first step of visual processing.
+The cone excitations represent the first step of visual processing. % JDB: paragraph seems disjoint. Talk to David and Vijay.
+To put the computed cone excitations into a form for use in further processing, we demosaiced the excitations for each cone class using linear interpolation
+to obtain a cone excitation image for each cone class.
+The lens and macular pigment absorb more short than long wavelength light, so that the excitations of the S cones tend to be
+smaller than those of the L and M cones.
+To make the magnitude of the three cone excitation images similar across cone classes, we
+normalized each cone excitation image by the summed (over wavelength) quantal efficiency of the corresponding cone class.
+The demosaicing and normalization do not alter the information in the cone excitation images.
+
 To capture key properties of post-receptoral processing, such as contrast normalization \cite{heeger1992normalization,albrecht1991motion,carandini2012normalization}, 
 we processed the excitations as follows:
-First, we generated a response for each cone class at each pixel in the sampled retinal image, using linear interpolation separately for each cone class.
-This gives us a cone excitation image for each cone class.
-We also normalized each cone excitation image by the total area under the corresponding cone spectral sensitivity.
-This makes the magnitude of the cone excitation images similar across cone classes.
-These two processing steps do not alter the information in the cone excitation images.
-
 To model contrast coding, we converted each cone excitation image to a corresponding cone contrast image.
@@
 \subsubsection*{Learning optimal filters}
-AMA is a task specific Bayesian method for dimensionality reduction.
+AMA is a task-specific Bayesian method for dimensionality reduction.
 When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of linear receptive fields.
@@
 Here we use a Kullback-Leibler divergence cost function, so that the optimal estimator is the maximum a posteriori estimate.
+% JDB: I thought we were using a squared error cost function. See above?
 %% DHB: Uniform prior, right? And posterior mean?  If not, correct prose above.

### 2018-05-18 Draft4/draft4.tex
johannes edits complete
multiple comments added for future discussion. but nothing we shouldn’t be able to get through in our next session

@@
 It has been used to develop ideal observers for focus error, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2014optimal, burge2015optimal}.
+%% JDB: Please add 2012 reference that I will provide.
 In this paper, we apply AMA to a special case of computational color constancy.
-%% JDB: Please add 2012 reference that I will provide.
 
@@
 through their effect on the contrast normalized responses at the center of the target object. 
-We also evaluated the performance of a naive model that estimates the mean of the LRV values in the training set, irrespective
+We also evaluated the performance of a naive model that uses the mean of the LRV values in the training set as the estimate, irrespective
 of the image data.
@@
 
-We start with Condition 1, where only the LRV and relative reflectance spectrum of the target object vary across scenes.
-For this condition, estimating LRV should be easy because the variation in target object reflectance that we introduced
+In Condition 1, only the LRV and relative reflectance spectrum of the target object vary across scenes.
+For this condition, LRV estimation should be easy because the variation in target object reflectance that we introduced
 preserved LRV (which is calculated using a CIE D65 as the illumination).
-This in turn means that for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
-In Condition 1, we used an illumination drawn form our daylight sample and thus expect a reasonable degree of similarity to D65.
+% JDB: Isn't this true of all conditions? LRV is preserved for each set of images with the same LRV label for all conditions.
+Thus, for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
+In Condition 1, we used an illumination randomly sampled from our model of daylight illumination spectra (see Methods) and thus expect a reasonable degree of similarity to D65.
 %% DHB: We need to say something about how similar.  Might explore different illuminants to dissect how sensitive the estimation
@@
 % our graphics approach to understand, and we want to build up examples.
+% JDB: I agree. The statement in current form is unnecessarily vague. With a bit of additional analysis, we could also say that different random samples produce nearly identical results, etc. etc.
 
-We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
-We trained and evaluated AMA on the cone excitations to the image patches.
+We used accuracy maximization analysis (AMA) to learn a set of linear receptive fields that are optimal for estimating target LRV from the cone excitations to the image patches in this condition. 
+%We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
+%We trained and evaluated AMA on the cone excitations to the image patches.
 Decoding performance for the test set is shown in Figure~\ref{fig:case1Estimates}. 
-As expected, the LRV estimates obtained by decoding the AMA receptive field responses are essentially perfect.
-Figure~\ref{fig:case1Estimates} also shows the performance of the baseline linear regression method, again trained
-on the training set and evaluated on the test set.
-For this condition, linear regression on the target object cone responses also leads to veridical LRV estimates.
+Figure~\ref{fig:case1Estimates} also shows the performance of the baseline linear regression method. 
+Both methods are trained and tested on different image sets.
+As expected, the LRV estimates obtained from decoding the AMA receptive field responses the LRV estimates from linear regression are essentially perfect.
 
-Figure~\ref{fig:case1RFResponse} shows the responses of the first two receptive fields to all the image patches in the training set.
-Each individual point represents the receptive field responses to a single image patch.
-Each point is color coded according to the LRV corresponding to the target object in the patch.
-The responses segregate according to the target LRV, which is the feature required to support the high level 
+Figure~\ref{fig:case1RFResponse} shows the responses of the first two AMA receptive fields to all the image patches in the training set.
+Each individual point represents the receptive field responses to an individual image patch.
+Each point is color coded by the LRV corresponding to the target object in the patch.
+The responses segregate nearly completely according to the target LRV, which is the feature required to support the high level 
 of estimation performance shown in Figure~\ref{fig:case1Estimates}.
@@
 Figure~\ref{fig:case1RFs} shows the first two AMA receptive fields.
-Each of these, in essence, takes a weighted sum of the L and M cone excitations at the target object location.
-The cone excitations in the background regions and the S cone excitations are largely ignored.
+Each receptive field performs a weighted sum of the L, M, and S cone excitations.
+The L and M cone excitations at the target object location receive large weights.
+The L and M cone excitations at the background object locations and the S cone excitations at all locations receive small weights and are thus largely ignored. 
 These receptive fields make sense.
-For this condition, the background regions provide very little task relevant information: their only relevant effect is
-through light scattered from them onto the target.
-In addition, luminance is primarily determined by L and M cone s, so the S cones should make little
+For this condition, the background regions provide very little task-relevant information. 
+They are useful only because some light is scattered from them onto the target, and vice versa. 
+% JDB: Double check vice versa.
+In addition, luminance is primarily determined by L and M cones, so the S cones should make little
 contribution.
@@
 
-Condition 2 introduces variation in the spectral power distribution of the light sources.
-This variation makes the task more difficult, because it causes more variation in cone excitations due to factors other than the target object LRV.
-Figure~\ref{fig:Condition2}(a,b) show the results when we learned and evaluated the performance of AMA on the cone excitations.
+Condition 2 includes variation in the spectral power distribution of the light sources, in addition to the variation present in Condition 1. 
+This illumination variation makes the task more difficult because it causes additional variation in the cone excitations that is not due to target object LRV.
+This illumination variation makes the task more difficult because it causes additional variation in the cone excitations that is not due to target object LRV.
+We learned AMA receptive fields on the cone excitations to the images in this new condition, and again evaluated decoding performance (Fig.
+~\ref{fig:Condition2}(a,b)).
+%Figure~\ref{fig:Condition2}(a,b) show the results when we learned and evaluated the performance of AMA on the cone excitations.
 Performance is poor.
-Indeed, on average the estimates deviate considerably from the true LRV, as seen by the fact that the mean estimate
-(red line) does not lie along the positive diagonal and by the fact that there is large estimation variability for each
-value of the true LRV (as indicated by the width of the shaded red region).
+Indeed, the estimates deviate considerably from the true LRV, as seen by the fact that the mean estimate
+(red line) does not lie on the positive diagonal and by the fact that there is large estimation variability for each
+value of the true LRV.
 For this case, linear regression is also very poor. Indeed, the linear regression estimates are essentially the same as would be obtained
@@
 
-Recall that there are two qualitatively distinct aspects to the variation in light source spectra.
-One is a variation in relative spectral power distribution and the
-other is a variation in overall intensity.
-To separate the effect of these two aspects, we trained and evaluated AMA on the contrast normalized cone excitations.
-Figure~\ref{fig:Condition2}(c,d) shows that performance improves greatly, and AMA performance is essentially perfect.
-This observation is consistent with a large literature on computational color constancy that shows that when only illumination spectra are varied,
-contrast-based representations provide an effective vehicle for achieving color constancy (REFS).
-That same literature, however, shows that
-contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.
+Recall that there are two qualitatively distinct factors contributing to the variation in illumination spectra: changes in overall intensity, and changes in the shape of the spectral power distribution.
+To separate the effect of these two factors, we trained and evaluated AMA on the contrast normalized cone excitations. 
+By contrast normalizing the cone excitations, the contribution of overall intensity is essentially removed.
+Figure~\ref{fig:Condition2}(c,d) shows that performance improves greatly with contrast normalization. 
+Estimates obtained from the AMA receptive field reponses are essentially perfect. 
+Estimates obtained from linear regression are substantially improved.
+This observation is consistent with a large literature on computational color constancy that shows that 
+contrast-based representations are effective for supporting color constancy when only illumination spectra vary (REFS).
+However, the same literature shows that contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.
 %% DHB: Need to add REFS in paragraph above.
@@
 
-Condition 3 introduces variation in the reflectance spectra of the background objects.
-This condition models the full real-world spectral variation that is most relevant for the computational problem of luminance constancy.
+Condition 3 introduces variation in the reflectance spectra of the background objects, in addition to the sources of variation in Conditions 1 and 2.
+This condition models all the sources of real-world spectral variation that is most relevant for the computational problem of luminance constancy.
+% JDB: Folks are ok with "all the sources"?
 We again trained and evaluated AMA for labeled images patches, using the contrast normalized cone excitations.
 The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions (Figure~\ref{fig:case3Estimates}).
-None-the-less, the estimates provide useful information about the target LRV.
-Indeed, on average the estimates track the true LRV, as seen by the fact that the mean estimate
-(red line) lies along the positive diagonal.
+Nevertheless, the estimates provide useful information about the target LRV.
+Indeed, the estimates track the true LRV on average, as seen by the fact that the mean estimate (red line) lies along the positive diagonal.
 The increased estimation variability is indicated by the increased width of the shaded red region, relative to its width for the Condition 1 and 2 results.
@@
 
-Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA linear receptive fields for training stimuli.
+Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA receptive fields to the training stimuli.
 Although the responses vary systematically with target object LRV, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
-This overlap is the combined effect of the variation in the illumination and background surface spectra.
+This overlap is due to the combined effect of the variation in the illumination and background surface spectra.
 Recall, however, that performance is based on six rather than two receptive fields.
+% JDB: Have we said previously that performance is based on six RFs.
 Inclusion of more receptive fields reduces the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
@@
 % fields of relative RMSE versus size of training set.  We want to persuade the reader that we are at asymptote.
+% JDB: If we do this, it is probably best to put the evidence in the appendix. Otherwise, it will require a detour paragraph and figure subpanel.
 
@@
 We used a software pipeline, which was developed for this work, to render datasets of multispectral images from scene descriptions.
-Because we rendered the images, we were able to label each image by the luminance reflectance value (LRV) of a target object.
-Across scenes, we varied the LRV of the target object, its relative surface reflectance spectrum, 
+Because we rendered the images, we could label each image in the dataset by the luminance reflectance value (LRV) of the target object.
+We used the labeled datasets to learn estimators for the target object LRV.
+Across scenes, we varied the LRV of the target object, the relative surface reflectance spectrum of the target object, 
 the spectral power distributions of the light sources, and the reflectance spectra of the background objects in the scene.
-These variations were based on statistical models of natural surface reflectance and illumination spectra.
-We used the labeled datasets to learn estimators for the target object LRV.
-We studied the performance of these estimators as we systematically manipulated the 
-spectral variation in the datasets.
+These spectral variations were based on statistical models of natural surface reflectance spectra and natural illumination spectra.
+We studied the how the performance of the learned estimators changed with systematic manipulation of the spectral variation in the datasets.
 
@@
 
-Figure~\ref{fig:barGraphs} summarizes our main findings.
-It plots the overall relative root mean squared estimation error (relative RMSE) for each condition. 
-In Condition 1, where only the relative target object spectrum varies, luminance constancy poses an easy computational problem,
+Figure~\ref{fig:barGraphs} summarizes our main findings, by showing the overall relative root mean squared estimation error (relative RMSE; see Methods) for each condition. 
+In Condition 1, where only the relative target object spectrum varies, luminance constancy is an easy computational problem,
 and performance is essentially perfect for both the baseline linear regression and AMA methods.
 In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
-Indeed, neither of our methods performs well when they directly act on the cone excitations.
+Indeed, neither of our methods performs well when they operate directly on the cone excitations.
 Performance with both methods improves greatly when the cone excitations are contrast normalized. 
-Indeed, AMA performance for this case is, as in Condition 1, essentially perfect.
+Indeed, AMA performance for Condition 2 is essentially perfect, as it is in Condition 1.
 Linear regression does less well, in part because it only has access to cone excitations at image locations
@@
 In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.
-Note that introduction of variation in the background surfaces makes the luminance constancy problem substantially harder,
-because variation in the background surfaces reduces the reliability of the light reflected from these
-surfaces as a cue to the spectral power distribution of the illuminant.
+% JDB: Are we going to add in a constancy index, as we discussed doing a few meetings ago?
+Introducing variation in the surface reflectance spectra of the background objects makes the luminance constancy problem substantially more difficult.
+Variation in the reflectance spectra of the background objects surfaces reduces how reliably light reflected from those objects can be used a cue to the spectral power distribution of the illuminant.
+% JDB: Original concluding sentence very hard to read. I split into two and tried to simplify. Still not completely happy with it...
 
-\subsection{Use of Virtual Scenes}
-
-AMA has been used in conjunction with database of labeled natural images to analyze the estimation of defocus blur,
-binocular disparity and retinal image motion (refs).
-Here we used labeled images rendered from virtual scene descriptions.
-The use of rendered images has advantages and disadvantages.
-
-As we noted in the introduction, supervised learning requires large labeled datasets.
-These are not readily available  for the study of how to estimate correlates of object surface reflectance.
-In particular, to obtain ground truth information about the reflectance of objects in a natural image, it is necessary to
-make an independent of the illumination impinging on each object.
+\subsection{Images of Virtual vs. Real Scenes}
+% JDB: Completely rearranged opening of section. Previous version had a choppy opening paragraph that did not flow into second paragraph. Please see what you think.
+As noted in the introduction, supervised learning requires large labeled datasets.
+Large labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2014optimal, burge2015optimal}.
+%% JDB: Please add 2012 reference to citation list: Burge, J.
+& Geisler, W.
+S.
+(2012).
+Optimal defocus estimates from individual images for autofocusing a digital camera.
+Proceedings of the IS&T / SPIE.
+doi:10.1117/12.912066
+%%  JDB: Please also 2018 reference to citation list: Kim, S. & Burge, J. ?The lawful imprecision of human surface tilt estimation in natural scenes?. eLife. 7:31448. doi: 10.7554/eLife.31448
+Unfortunately, large labeled datasets that are useful studying how to estimate correlates of object surface reflectance are not readily available.
+To obtain ground truth information about the reflectance of objects in a natural image, it is necessary to make an independent of the illumination impinging on each object.
 Although this can be done by inserting a small number of discretely spaced reflectance standards into the scene, 
 interpolating to locations between such standards requires strong assumptions.
-The use of rendered images allows us to work with large numbers of labeled images where object reflectance
-is precisely known at each pixel.
 
-A second advantage of using rendered images is that we can control the variation in distinct
-scene factors that might affect the difficulty of the estimation problem.
-This allows study of the individual effect of each factor as well as their combined effect.
-Here, we exploited this to systematically introduce variation in the relative target object reflectance
-spectrum, the spectrum of the illumination, and the reflectance spectrum of the background objects.
-This allowed us to quantify how each of these variations limits LRV estimation.
-We believe the basic approach can be extended to include parametric control over the amount
-of variation of different factors as well as to include variation in additional factors (see below).
+Here we used labeled images rendered from virtual scene descriptions. 
+There are many advantages to using rendered images.
+One advantage is that they allow us to work with large numbers of labeled images where object reflectance is precisely known at each pixel.
+A second advantage is that we can control the variation in distinct scene factors that might affect the difficulty of the estimation problem.
+This flexibility allows study of the individual effect of each factor as well as their combined effects.
+Here, we exploited this flexibility to quantify how variation in the relative target object reflectance
+spectrum, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation..
+We believe this basic approach can be extended to include parametric control over the amount of variation of different factors as well as to include variation in additional factors (see below).
 %% DHB: Update if we add additional analyses as per some of the comments above.
+% % JDB: I don't understand what the the concluding sentence above is saying.
 
-At the same time, it is important to recognize limitations of the rendered image approach.
-Virtual rendered scenes are not guaranteed to capture all of the task relevant
-variation that occurs in real scenes.
-Indeed, even casual inspection of our images reveals that they are rendered and not real.
-Computer graphics is getting better, however, and we expect that the gap between
-virtual and natural image databases will steadily close.
-Indeed, carefully constructed graphics images are now quite difficult to differentiate
-from real images.
+There are also disadvantages associated with using rendered images. 
+Virtual rendered scenes are not guaranteed to capture all of the task relevant variation that occurs in real scenes.
+Casual inspection of our images reveals that they are rendered and not real.
+Computer graphics is getting better, however, and we expect that the gap between virtual and natural image databases will steadily close.
+Indeed, carefully constructed graphics images are now quite difficult to differentiate from real images.
 %% DHB: Might be able to reference Farid's recent book on this point.
 
-Our use of virtual images relies on datasets that characterize the statistical variation
-in object reflectance and natural illumination spectra.
-We believe these datasets provide reasonable approximations.
-None-the-less, they can be extended and improved.
-For example, the dataset of illuminations does not include the artificial illuminations
-that we now live much of our lives under.
-The surface reflectance datasets capture constraints on naturally occurring reflectance
-functions, but the surfaces in the datasets were not sample the environment in a manner that
-characterizes the relative frequency of different reflectance spectra in natural viewing.
-Future work with virtual image datasets will benefit from targeted efforts to characterize
-the natural statistics of the scene components that are varied.
-Under the assumption that combination of different scene factors (e.g. surface reflectances
-and illuminations) is independent, the virtual image approach modularizes the study
-of variation in natural scenes.
+To increase the representativeness of our rendered images, we used datasets of  natural surface reflectance spectra and natural daylight illumination spectra.
+Although we believe these datasets provide reasonable approximations of the statistical variation in reflectance and illumination spectra, they can be extended and improved.
+For example, the surface reflectance datasets capture constraints on naturally occurring reflectance functions, but the surfaces in the datasets were not sampled to reflect the relative frequency of different reflectance spectra in natural viewing.
+In addition, the dataset of illuminations does not include the artificial illuminations that we now live much of our lives under.
+% JDB: What are "constraints on naturally occuring reflectance functions"?
+Future work with virtual image datasets will benefit from targeted efforts to characterize the natural statistics of the scene components that are varied.
+% JDB: I think i understand what the previous sentence is trying to say, but i'm not sure. We should discuss.
+Under the assumption that combination of different scene factors (e.g.
+surface reflectances and illuminations) is independent, the virtual image approach modularizes the study of variation in natural scenes.
+% JDB: Confusing concluding sentence. Not sure the point will get across.
 
 \subsection{Future Directions}
-In the work presented here, we incorporated spectral variation into our statistical model
-of naturalistic scenes.
-It is natural to begin with spectral variation, because this variation is at the heart of
-what makes luminance constancy a rich computational problem.
-In natural scenes, however, there are other sources of variation that add additional
-richness.
-These include variation in non-spectral properties of objects and lighting in the scene, including
-object texture, material, and shape as well as lighting geometry.
-The methods we developed here may be generalized to study the effects of variation
-in these factors.
-The basic approach would be to incorporate the variation into the generation of the
-scenes and again learn estimators from the corresponding labeled images.
-A challenge for this approach will be to thoughtfully control the increase in problem
-complexity, both to keep compute time feasible and to ensure that it is possible to
-extract meaningful insight from the results.
+In the work presented here, we studied computational luminance constancy in virtual scenes with naturalistic spectral variation in light sources and in surface reflectance functions. 
+% JDB: Vet change to opening sentence w. vijay and david.
+
+It is natural to begin with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem.
+In natural scenes, however, there are other sources of variation that add additional richness and make the problem more difficult to solve.
+These include variation in non-spectral properties of objects and lighting in the scene, including object texture, material, and shape as well as lighting geometry. 
+The methods we developed here may be generalized to study the effects of variation in these factors.
+One could incorporate these other sources of variation into the generation of the scenes and again learn estimators from the corresponding labeled images. 
+A challenge for this approach will be to thoughtfully control the increase in problem complexity, both to keep compute time feasible and to ensure that it is possible to extract meaningful insight from the results.
 
 Luminance constancy is a special case of the more general problem of color constancy.
-The approach we developed here could be generalized to the estimation of additional
-surface reflectance descriptors, such as object hue or chroma.
-As with LRV, these descriptors would be defined by the light reflected from an object's
-surface   under a standard illuminant.
-A further advance would be to develop methods for learning receptive fields that are
-optimal for multivariate estimation problems.
+The approach we developed here could be generalized to the estimation of additional surface reflectance descriptors, such as object hue or chroma.
+As with LRV, these descriptors would be defined by the light reflected from an object's surface   under a standard illuminant.
+% JDB: Cut previous sentence. Seems like a niggly detail this close to the conclusion.
+A further advance would be to develop methods for learning receptive fields that are optimal for multivariate estimation problems. 
+% JDB: The right student could engage in this programming project.
 With such methods one could directly estimate three-dimensional color descriptors.
@@
 is to gain insight about human vision.
-The approach we developed can be used to make predictions of how humans would
-perform in a psychophysical task that probes the visual representation of object LRV.
-For example, one could study discrimination thresholds for target LRV using the
-stimuli that were generated with the methods used here.
-More specifically, we could ask how LRV discrimination thresholds are impacted by 
-spectral variation in the illuminant, the background objects, and in the target object itself.
-Comparing human thresholds with the precision of AMA-based estimates would then
-allow inferences about how well human observers make use of the information available
-in the images for performing LRV discrimination.
+The approach we developed can be used to make predictions of how humans would perform in a psychophysical task that probes the visual representation of object LRV.
+For example, one could study discrimination thresholds for target LRV using the stimuli that were generated with the methods used here.
+More specifically, we could ask how LRV discrimination thresholds are impacted by spectral variation in the illuminant, the background objects, and in the target object itself.
+Comparing human thresholds with the precision of AMA-based estimates would then allow inferences about how well human observers make use of the information available in the images for performing LRV discrimination.
 We think experiments and analyses along these lines represent an important future direction.
-By coupling the experiments and analyses we hope to advance, in a principled and controlled manner,
-our understanding of how we see objects in the real world .
+By coupling the experiments and analyses we hope to advance, in a principled and controlled manner, our understanding of how we see objects in the real world .
 

### 2018-05-18 Draft5/draft5.tex
restructured

--- 2018-05-18 Draft4/draft4.tex
@@
 	\caption{}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
         \label{fig:introSchematic}
@@
         \caption{}    
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
         \label{fig:introExampleFigure}
@@
 For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal}.
-It has been used to develop ideal observers for focus error, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2014optimal, burge2015optimal}.
-%% JDB: Please add 2012 reference that I will provide.
+It has been used to develop ideal observers for focus error, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
 In this paper, we apply AMA to a special case of computational color constancy.
@@
         \caption{Library }
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
         \label{fig:baseSceneLibrary}
@@
         \caption{Mill}    
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.png}
         \label{fig:baseSceneMill}
@@
         \caption{Table-Chairs}    
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure3/Figure3_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.png}
         \label{fig:baseSceneTableChairs}
@@
         \caption{Big-ball}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
         \label{fig:libraryWithBigBall}
@@
         \caption{Xylophone}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
         \label{fig:libraryWithXylophone}
@@
         \caption{Barrel}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
         \label{fig:libraryWithBarrel}
@@
         \caption{Ring toy}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_d.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
         \label{fig:libraryWithRingToy}
@@
         \caption{Bottle}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure4/Figure4_e.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
         \label{fig:libraryWithChampagneBottle}
@@
         \caption{Target position}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_d.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.png}
         \label{fig:targetPositionVariation}
@@
         \caption{Target size/Orientation}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_e.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.png}
         \label{fig:targetSizeOrientation}
@@
         \caption{Target spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.png}
         \label{fig:targetVariation}
@@
         \caption{Illumination spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.png}
         \label{fig:illuminationVariation}
@@
         \caption{Background spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure5/Figure5_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.png}
         \label{fig:backGroundVariation}
@@
 		\caption{Condition 1}
-%		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_a.png}
-		\includegraphics[width=\textwidth]{../FiguresDraft4/Figure1/Figure1_b.pdf}
+%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
+		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
  		\label{fig:backgroundVarying}
@@
         \caption{Condition 2}	
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_b.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
         \label{fig:targetIlluminantVarying}
@@
 	\caption{Condition 3}	
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure2/Figure2_c.pdf}        
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
         \label{fig:allSpectraVarying}
@@
 \end{figure}
-%% DHB: May also want to render these examples at a higher resolution
 
@@
 	\caption{Granada dataset}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_a.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_a.pdf}
         \label{fig:granadaData}
@@
         \caption{Statistical model}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_b.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_b.pdf}
         \label{fig:illuminantSamples}
@@
         \caption{CIE xy chromaticity}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_c.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_c.pdf}
         \label{fig:xyDiagram}
@@
         \caption{Color swatches}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure6/Figure6_d.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_d.pdf}
         \label{fig:sRGBIlluminant}
@@
 (c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in b (red).
-F(d) sRGB renditions of the samples shown in b.}
+(d) sRGB renditions of the samples shown in b.}
 \label{fig:illuminant}
@@
 
-To generate illumination spectra, we first developed a statistical model of the Granada daylight measurements (\href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) \cite{hernandez2001color} and then sampled randomly from the model (see appendix).
+To generate illumination spectra, we first developed a statistical model of the Granada daylight measurements (\citeNP{hernandez2001color}; \href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) and then sampled randomly from the model (see appendix).
 To match the wavelength spacing we use in rendering, we resampled the wavelength spacing of the Granada spectra to
@@
 The mean and covariance matrix of the Gaussian match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
-% on these components obtained from the normalized Granada spectra 
 To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
@@
             \caption{Munsell and Vrhel dataset}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_a.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_a.pdf}
         \label{fig:reflectanceSpectra}
@@
         \caption{Statistical model}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_b.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_b.pdf}
         \label{fig:reflectanceSamples}
@@
     \caption{CIE xy chromaticity}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_c.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_c.pdf}
         \label{fig:xyChroReflectance}
@@
         \caption{Color swatches}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure7/Figure7_d.pdf}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_d.pdf}
         \label{fig:backgroundSwatches}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure8/Figure8.pdf}
+\includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure8/Figure8.pdf}
 \caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
@@
 Figure \ref{fig:targetSwatches} shows color renderings of target reflectance spectra under CIE illuminant D65, for the evenly spaced LRV values we studied.
-%% DHB: Note that this procedure is different than conditioning the statistical model on the target LRV.  We could switch to the latter if we wished.
-%% VS: I don't think it matters if we care about keeping only one color co-ordinate fixed.
 
@@
         \caption{sRGB rendering of a 3D scene}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_a.png}
         \label{fig:3DScene}
@@
         \vspace{1.5mm}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_b.png}
         \label{fig:croppedImage}
@@
         \vspace{1.5mm}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_c.png}
         \label{fig:croppedImageWithMosaic}
@@
     \begin{subfigure}[b]{0.2 \textwidth}
-        \caption{LMS normalized cone contrast}
-        \includegraphics[width=\textwidth]{../FiguresDraft4/Figure9/Figure9_d.png}
+        \caption{Normalized cone contrast}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_d.png}
         \label{fig:coneContrast}
@@
 (d) The cone excitations are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
-Finally, the demosaiced images are contrast normalized separately for each cone type.}
+Finally, the demosaiced images are contrast normalized.}
 \end{figure}
@@
         \caption{LRV estimates}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft4/Figure10/Figure10_a.pdf}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
         \label{fig:case1Estimates}
@@
         \caption{RF responses}
-        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure10/Figure10_b.pdf}
+        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure10/Figure10_b.pdf}
         \label{fig:case1RFResponse}
@@
 	\caption{AMA receptive fields}
-	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft4/Figure10/Figure10_c.pdf}
+	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure10/Figure10_c.pdf}
 	\label{fig:case1RFs}
@@
 % JDB: Isn't this true of all conditions? LRV is preserved for each set of images with the same LRV label for all conditions.
+% VS: We should say, the only source of variation that we have introduced preserved LRV
 Thus, for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
@@
         \caption{\centering{LRV estimates} \newline\centering{(Excitations)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_a.pdf}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_a.pdf}
         \label{fig:case2IsomerizationEstimates}
@@
         \caption{\centering{RF responses} \newline\centering{(Excitations)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_b.pdf}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_b.pdf}
         \label{fig:case2RFResponseIsomer}
@@
         \caption{\centering{LRV estimates}  \newline \centering{(Normalized contrast)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_c.pdf}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_c.pdf}
         \label{fig:case2ContrastEstimates}
@@
         \caption{\centering{RF responses}  \newline \centering{(Normalized contrast)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft4/Figure11/Figure11_d.pdf}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_d.pdf}
         \label{fig:case2RFResponseContrast}
@@
 This illumination variation makes the task more difficult because it causes additional variation in the cone excitations that is not due to target object LRV. 
-We learned AMA receptive fields on the cone excitations to the images in this new condition, and again evaluated decoding performance (Fig.
-~\ref{fig:Condition2}(a,b)).
+We learned AMA receptive fields on the cone excitations to the images in this new condition, and again evaluated decoding performance (Fig. ~\ref{fig:Condition2}(a,b)). 
 %Figure~\ref{fig:Condition2}(a,b) show the results when we learned and evaluated the performance of AMA on the cone excitations.
@@
         \caption{LRV estimates}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft4/Figure12/Figure12_a.pdf}
+        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure12/Figure12_a.pdf}
         \label{fig:case3Estimates}
@@
         \caption{Receptive field response}
-        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft4/Figure12/Figure12_b.pdf}
+        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure12/Figure12_b.pdf}
         \label{fig:case3RFResponse}
@@
 	\caption{AMA receptive fields}
-	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft4/Figure12/Figure12_c.pdf}
+	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure12/Figure12_c.pdf}
 	\label{fig:case3RFs}
@@
 \end{figure}
-%% Panel b shows training set projections, right?
-%% VS: Yes
 
@@
 \centering
-\includegraphics[width=0.3\textwidth]{../FiguresDraft4/Figure13/Figure13_a.pdf}
+\includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure13/Figure13_a.pdf}
 \caption{{\bf Summary of luminance constancy performance:} The plot shows the relative RMSE estimation error for each method and condition.The relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
@@
 Introducing variation in the surface reflectance spectra of the background objects makes the luminance constancy problem substantially more difficult. 
-Variation in the reflectance spectra of the background objects surfaces reduces how reliably light reflected from those objects can be used a cue to the spectral power distribution of the illuminant.
+Variation in the reflectance spectra of the background objects surfaces reduces how reliably light reflected from those objects can be used a cue to estimate the spectral power distribution of the illuminant.
 % JDB: Original concluding sentence very hard to read. I split into two and tried to simplify. Still not completely happy with it...
@@
 As noted in the introduction, supervised learning requires large labeled datasets.
-Large labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2014optimal, burge2015optimal}.
-%% JDB: Please add 2012 reference to citation list: Burge, J.
-& Geisler, W.
-S.
-(2012).
-Optimal defocus estimates from individual images for autofocusing a digital camera.
-Proceedings of the IS&T / SPIE.
-doi:10.1117/12.912066
-%%  JDB: Please also 2018 reference to citation list: Kim, S. & Burge, J. ?The lawful imprecision of human surface tilt estimation in natural scenes?. eLife. 7:31448. doi: 10.7554/eLife.31448
+Large labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful}.
 Unfortunately, large labeled datasets that are useful studying how to estimate correlates of object surface reflectance are not readily available.

### 2018-05-24 Draft5/draft5.tex
small edits and changed 1 figure

@@
-%% Copyright (C) 2009 by Tobias Elze
-%% Journal of Vision LaTeX template version 1.0
-%% This document may be used freely for your own submissions.
-
 \documentclass{jov}
-\usepackage{graphicx} % needed for figures
+\usepackage{graphicx}
 \usepackage{subcaption}
@@
 Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the 
-perceived LRV of a target object. 
-We have developed a software that renders naturalistic multispectral images of 3D scenes.
-The software provides precise control over the geometrical and spectral factors that make a scene. 
-We label the rendered images with the luminance of a specific object in the scene. 
+perceived LRV of an object. 
+To do this, we have developed a software that renders naturalistic multispectral images of 3D scenes with 
+precise control over the geometrical and spectral factors that make a scene. 
+We label these images with the LRV of a specific object in the scene. 
 Next, we simulate the response of the retinal cones to these multispectral images using 
@@
 Subsequent work incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{D'ZmuraConstancy3, D'ZmuraIversonSinger,BrainardFreeman}.
-A key insight from this computational work is that stable color descriptors of a target object cannot be obtained soley from the light reflected from that target object.
+A key insight from this computational work is that stable color descriptors of a target object cannot be obtained solely from the light reflected from that target object.
 But it is possible to obtain such descriptors by jointly analyzing the light reflected from multiple objects in the scene.
@@
 (b) Images of a sphere under a fixed illuminant.  
-Down each column, the reflectance function of the sphere varies only by a scale factor; the relative reflectance function is held fixed.
-The relative reflectance function (i.e.
-the shape of the spectral reflectance function) varies across each row.
+Down each column, the reflectance function of the sphere varies only by a scale factor; the shape of the reflectance spectrum is held fixed.  
+The shape of the reflectance spectrum varies across each row.
 Within each row, the light reflectance value (LRV) of the spheres is constant. 
@@
 These methods use the joint statistics of labeled images and scene variables to learn mappings that extract stable surface color descriptors from image input \cite{barron2015convolutional}.
-This general statistical learning approach has been useful for other perceptual problems in early and mid-level vison. domains of vision. 
+This general statistical learning approach has been useful for other perceptual problems in early and mid-level vision. domains of vision. 
 For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal}.
-It has been used to develop ideal observers for focus error, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
+It has been used to develop ideal observers for defocus blur, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
 In this paper, we apply AMA to a special case of computational color constancy.
@@
 % Figure 2
-\begin{figure}[t]
+\begin{figure}
 \centering
@@
 %% DHB: We need to think about how to scale the images for display.  The Library scene is too dark, at least when printed.
+% % VS: Is it still dark?
 
@@
 \end{figure}
-%% DHB: Can we render these examples at higher resolution, so that they look nicer?  The blurriness is distracting in the images.
 
@@
 
+Our rendering package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
+Base scenes specify an arrangement of objects and light sources.
+Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and additional light sources.
+Once the position, size and pose of the inserted objects and light sources have been set, 
+a surface reflectance function can be assigned to each object in the scene, and a spectral power distribution function can be assigned to each light source (Fig.~\ref{fig:VWCCTransformations}).
+The resulting scene model can then be rendered from any specified viewpoint.
+
+In the present work, we used our package to generate datasets of naturalistic scenes and corresponding images.
+We used one fixed base scene and inserted a spherical target object of fixed shape and size into this scene.
+We generated three distinct datasets, which we refer to as Conditions 1-3 and describe below.
+Across these datasets the luminance constancy problem (i.e. estimating the target object LRV)
+becomes progressively more difficult (Fig.~\ref{fig:studiedCases}).
+
+The variation within our datasets captures the essence of the computational problem of lightness constancy
+up to effects of scene geometry, an additional richness that we do not address in this paper.
+In Condition 1, the surface reflectance spectrum of the target object was the only source of scene variation other than the target object LRV.
+The reflectance spectra of the background objects, and the spectral power distributions of the light sources were kept fixed.
+In Condition 2, the spectral power distribution of the light sources varied in addition to the reflectance spectrum of the target object,
+Finally, in Condition 3 three distinct scene factors--target object surface 
+reflectance spectrum, reflectance spectra of the background objects, and
+spectral power distribution of the light sources--varied in addition to the target object LRV.
+Each condition had a corresponding dataset of 1000 scenes and images, 100 for each of 10 target object LRV values.
+The LRV values were equally spaced between 0.2 and 0.6.
+For each LRV value, a different target surface reflectance spectra for each of the 100 scenes.
+Thus, for each target object LRV value, the shape of the target object surface reflectance spectra could differ.
+%% DHB Need to decide how many images we really want for final version of the work.
+
 % Figure 5: Conditions Studied
@@
 \end{figure}
-
-Our rendering package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
-Base scenes specify an arrangement of objects and light sources.
-Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and additional light sources.
-Once the position, size and pose of the inserted objects and lightsources have been set, 
-a surface reflectance function can be assigned to each object in the scene, and a spectral power distribution function can be assigned to each light source (Fig.~\ref{fig:VWCCTransformations}).
-The resulting scene model can then be rendered from any specified viewpoint.
-
-In the present work, we used our package to generate datasets of naturalistic scenes and corresponding images.
-We used one fixed base scene and inserted a spherical target object of fixed shape and size into this scene.
-We generated three distinct datasets, which we refer to as Conditions 1-3 and describe below.
-Across these datasets the luminance constancy problem (i.e. estimating the target object LRV)
-becomes progressively more difficult (Fig.~\ref{fig:studiedCases}).
-%Each dataset consisted of 1000 scenes and corresponding images, 100 for each of 10 LRV values.
-%% DHB Need to decide how many images we really want for final version of the work.
-
-The variation within our datasets captures the essence of the computational problem of lightness constancy
-up to effects of scene geometry, an additional richness that we do not address in this paper.
-In Condition 1, the surface reflectance spectrum of the target object was the only source of scene variation other than the target object LRV..
-The reflectance spectra of the background objects, and the spectral power distributions of the light sources were kept fixed.
-In Condition 2, the spectral power distribution of the light sources varied in addition to the reflectance spectrum of the target object,
-Finally, in Condition 3 three distinct scene factors--target object surface 
-reflectance spectrum, reflectance spectra of the background objects, and
-spectral power distribution of the light sources--varied in addition to the target object LRV.
-Each condition had a corresponding dataset of 1000 scenes and images, 100 for each of 10 target object LRV values.
-The LRV values were equally spaced between 0.2 and 0.6.
-For each LRV value, a different target surface reflectance spectra for each of the 100 scenes.
-Thus, for each target object LRV value, the shape of the target object surface reflectance spectra could differ.
 
@@
     \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset.
-Each spectrum is normalized by its mean (with mean taken over wavelength).
+Each spectrum is normalized by its mean power.
 (b) Sample spectra generated using the statistical model derived from normalized Granada dataset.
@@
 The mean and covariance matrix of the Gaussian match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
-To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
+To generate a random shape of the illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
 Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
@@
 In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle (REFS).
+%% VS: Needed a reference
 The local analysis is thus motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
@@
 Studying both representations allows us to understand how early contrast coding and normalization affect how well luminance constancy can be achieved.
+%% VS: This sentence does not read well.
 We applied accuracy maximization analysis (AMA) to learn the optimal receptive fields for estimating LRV,
@@
 assumption that all images in the training set are equally likely.
+% VS: This is not very clear.
 Moreover, the corresponding expected estimation cost may be explicitly computed.
 AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
-Here we used squared error as the cost function and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e. Poisson-like noise with a fano factor of 1.3).
+Here we used Kullback-Leibler divergence cost function and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e. Poisson-like noise with a fano factor of 1.3).
 Details of how AMA learns filters and the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
@@
 We took the average cone responses from a $3 \times 3$ region at the center of the target object.
-This baseline method disregards information carried the image regions corresponding to the background objects.
+This baseline method disregards information carried by the image regions corresponding to the background objects.
 We also performed regression on the contrast normalized version of the cone responses.
@@
 
-In Condition 1, only the LRV and relative reflectance spectrum of the target object vary across scenes.
+In Condition 1, only the LRV and the shape of the reflectance spectrum of the target object vary across scenes.
 For this condition, LRV estimation should be easy because the variation in target object reflectance that we introduced
@@
 % JDB: Isn't this true of all conditions? LRV is preserved for each set of images with the same LRV label for all conditions.
-% VS: We should say, the only source of variation that we have introduced preserved LRV
+% VS: We should say, "the variation that we introduced preserved LRV"
 Thus, for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
@@
 contribution.
-%% DHB: Can we add a color scale bar to the plots?
 
@@
 This illumination variation makes the task more difficult because it causes additional variation in the cone excitations that is not due to target object LRV. 
-This illumination variation makes the task more difficult because it causes additional variation in the cone excitations that is not due to target object LRV. 
-We learned AMA receptive fields on the cone excitations to the images in this new condition, and again evaluated decoding performance (Fig. ~\ref{fig:Condition2}(a,b)). 
-%Figure~\ref{fig:Condition2}(a,b) show the results when we learned and evaluated the performance of AMA on the cone excitations.
+We learned AMA receptive fields on the cone excitations to the images in this new condition, and again evaluated decoding performance (Fig.~\ref{fig:Condition2}(a,b)). 
 Performance is poor.
@@
 This overlap is due to the combined effect of the variation in the illumination and background surface spectra.
-Recall, however, that performance is based on six rather than two receptive fields.
+However, performance is based on six rather than two receptive fields.
 % JDB: Have we said previously that performance is based on six RFs.
+% VS: No
 Inclusion of more receptive fields reduces the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
@@
 Figure~\ref{fig:case3RFs} shows the first two receptive fields learned for Condition 3.
+Similar to Condition 1, the L and M cone excitations receive large weights, while the S cone excitations are largely ignored. 
+Additionally, the cone excitations at the target have opposite sign compared to background object locations.
+This make sense.
+As discussed earlier, luminance is primarily determined by L and M cones, so the S cones should make little
+contribution.
+Additionally, for this condition, the cone contrast needs to be compared across the target and background regions. 
+A center-surround receptive field facilitates such comparison.
+However, one should not interpret too much into the features that arise due to the specific geometry of the scene.
+
 %% DHB: We need to write something interpretive about the RF structure shown in panel c.
@@
 % separate the two possible sources of influence of the background surfaces.
+% % VS: On switching off secondary reflections, the performance (rel RMSE) remains essentially the same. Which means that this is not the primary source of variation.
+% % VS: To ensure that secondary reflections were switched off, I checked that the multispectral values of the central patch of the rendered image and the corresponding cone isoemrizations were the same for images that were generated with the same target and illuminant but different backgrounds.
+Then I performed the training and test as usual.
 
@@
 We used the labeled datasets to learn estimators for the target object LRV.
-Across scenes, we varied the LRV of the target object, the relative surface reflectance spectrum of the target object, 
+Across scenes, we varied the LRV of the target object, the shape of the reflectance spectrum of the target object, 
 the spectral power distributions of the light sources, and the reflectance spectra of the background objects in the scene.
@@
 
-Figure~\ref{fig:barGraphs} summarizes our main findings, by showing the overall relative root mean squared estimation error (relative RMSE; see Methods) for each condition. 
-In Condition 1, where only the relative target object spectrum varies, luminance constancy is an easy computational problem,
+Figure~\ref{fig:barGraphs} summarizes our main findings, by showing the overall relative root mean squared estimation error (relative RMSE; see Figure~\ref{fig:barGraphs} caption) for each condition. 
+In Condition 1, where only the shape of the reflectance spectrum of the target object varies, 
+luminance constancy is an easy computational problem,
 and performance is essentially perfect for both the baseline linear regression and AMA methods.
 In Condition 2, where the spectral power distribution of the illumination also varies, the problem of luminance constancy is more difficult.
-Indeed, neither of our methods performs well when they operate directly on the cone excitations.
+Indeed, neither of our methods perform well when they operate directly on the cone excitations.
 Performance with both methods improves greatly when the cone excitations are contrast normalized. 
@@
 % JDB: Are we going to add in a constancy index, as we discussed doing a few meetings ago?
-Introducing variation in the surface reflectance spectra of the background objects makes the luminance constancy problem substantially more difficult. 
-Variation in the reflectance spectra of the background objects surfaces reduces how reliably light reflected from those objects can be used a cue to estimate the spectral power distribution of the illuminant.
+Introducing variation in the surface reflectance spectra of the background objects makes 
+the luminance constancy problem substantially more difficult. 
+Variation in the reflectance spectra of the background objects surfaces reduces how 
+reliably light reflected from those objects can be used as a cue to estimate the spectral power distribution of the illuminant.
 % JDB: Original concluding sentence very hard to read. I split into two and tried to simplify. Still not completely happy with it...
@@
 Unfortunately, large labeled datasets that are useful studying how to estimate correlates of object surface reflectance are not readily available.
-To obtain ground truth information about the reflectance of objects in a natural image, it is necessary to make an independent of the illumination impinging on each object.
+To obtain ground truth information about the reflectance of objects in a natural image, it is necessary to make 
+an independent measurement of the illumination impinging on each object.
 Although this can be done by inserting a small number of discretely spaced reflectance standards into the scene, 
@@
 This flexibility allows study of the individual effect of each factor as well as their combined effects.
-Here, we exploited this flexibility to quantify how variation in the relative target object reflectance
-spectrum, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation..
+Here, we exploited this flexibility to quantify how variation in the shape of the reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation..
 We believe this basic approach can be extended to include parametric control over the amount of variation of different factors as well as to include variation in additional factors (see below).
@@
 Virtual rendered scenes are not guaranteed to capture all of the task relevant variation that occurs in real scenes.
-Casual inspection of our images reveals that they are rendered and not real.
+Casual inspection of our images reveals that they are rendered, and not real.
 Computer graphics is getting better, however, and we expect that the gap between virtual and natural image databases will steadily close.

### 2018-05-24 Draft5/draft5.tex
small edits

@@
 As noted in the introduction, supervised learning requires large labeled datasets.
-Large labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful}.
-Unfortunately, large labeled datasets that are useful studying how to estimate correlates of object surface reflectance are not readily available.
+Such datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful}.
+Unfortunately, such datasets are not readily available for studying correlates of object surface reflectance.
 To obtain ground truth information about the reflectance of objects in a natural image, it is necessary to make 
@@
 A second advantage is that we can control the variation in distinct scene factors that might affect the difficulty of the estimation problem.
-This flexibility allows study of the individual effect of each factor as well as their combined effects.
+This flexibility allows the study of individual scene factors as well as their combined effects.
 Here, we exploited this flexibility to quantify how variation in the shape of the reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation..
@@
 Casual inspection of our images reveals that they are rendered, and not real.
-Computer graphics is getting better, however, and we expect that the gap between virtual and natural image databases will steadily close.
+However, computer graphics is getting better and we expect that the gap between virtual and natural image databases will steadily close.
 Indeed, carefully constructed graphics images are now quite difficult to differentiate from real images.
@@
 The approach we developed here could be generalized to the estimation of additional surface reflectance descriptors, such as object hue or chroma.
-As with LRV, these descriptors would be defined by the light reflected from an object's surface under a standard illuminant.
-% JDB: Cut previous sentence. Seems like a niggly detail this close to the conclusion.
 A further advance would be to develop methods for learning receptive fields that are optimal for multivariate estimation problems. 

### 2018-05-25 Draft5/appendix.tex
edited SI

\documentclass[10pt,english]{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{lmodern}
\renewcommand{\sfdefault}{lmss}
\renewcommand{\ttdefault}{lmtt}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{amstext}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{babel}
\usepackage{mathtools}
%\usepackage{subfigure}
\usepackage{subcaption}

   \usepackage{multirow}
   \topmargin 0.0cm
   \oddsidemargin 0.5cm
   \evensidemargin 0.5cm
   \textwidth 16cm 
   \textheight 21cm

\date{}
\begin{document}
\title{Appendix: Luminance constancy under fixed geometry}

\author{Vijay Singh, Nicolas P. Cottaris, Benjamin S. Heasly, David H. Brainard, Johannes Burge}
\maketitle

% \begin{abstract}
% \end{abstract}

\section{Illumination Spectra}
Let us denote the $i$'th sample in the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset. 
Since the measured spectra vary over several orders of magnitude in overall intensity, we normalize each spectrum by dividing it by its mean power 
\begin{align}
I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}.
\end{align}
For simplicity of notation, we denote wavelength $\lambda$ as a continuous variable; in the actual calculations wavelength is discretely sampled and integrals are approximated by sums.

The Granada dataset was measured at 5 nm sampling intervals between 300 and 1100 nm.  
We subsampled the spectra to the 400-700 nm interval, 10 nm spacing representation used for rendering, and performed our calculations at this sampling.

The rescaled spectra $I_i^s(\lambda)$ were mean centered for PCA by subtracting out the sample mean ($\bar{I}^{s}(\lambda)$),  over all rescaled spectra in the dataset, 
\begin{align}
\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}.
\end{align} 
The mean centered dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$
was decomposed as:
\begin{align}
I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA},
\end{align}
where the $\hat{{\bf e}}_j^{PCA}$ are the PCA basis vectors obtained using
singular value decomposition (SVD) applied to $I_i^{MC}(\lambda)$, 
and $w_{ij}$ are the weights obtained by projecting each of $I_i^{MC}(\lambda)$ onto the basis vectors $\hat{{\bf e}}_j^{PCA}$ $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$.
We used the basis vectors corresponding to
the largest six SVD eigenvalues, so that $\{j \in [1,6]\}$.
For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance.

These steps can be summarized as follows:
\begin{align}
I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) \approx \sum_{j = 1}^6 w_{ij}\hat{{\bf e}}_j^{PCA}.
\end{align}

To get a random illuminant spectrum $\tilde{I}_i(\lambda)$, we sample random weights $\tilde{w}_{ij}$ from  
a multivariate Gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
and co-variance $\Sigma$ given as:
\begin{align}
\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right).
\end{align}
The corresponding spectrum is generated from these weights as $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right)$.
This spectrum can sometimes have values that are less than zero. 
In such cases, the weights are discarded and a new draw obtained, until
the condition $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, is satisfied for all $\lambda$.
The random illuminant spectrum is
\begin{align}
\tilde{I}_i(\lambda) = \left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right).
\end{align}

\section{Surface Reflectance Spectra}
Let us denote the $i$'th sample in the reflectance spectrum dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
and $M$ is the total number of spectra in the dataset. 
We first calculated the mean reflectance spectrum,
$\bar{R}(\lambda)$, by taking the sample mean over all spectra in the dataset
\begin{align}
\bar{R}(\lambda) = \frac{1}{M} \sum_{i=1}^M R_i(\lambda).\end{align} 
The dataset is then mean centered by subtracting the mean spectrum, $R_i^{\rm MC}(\lambda) =  R_i(\lambda)-\bar{R}(\lambda)$ 
and decomposed using PCA as:
\begin{align}
R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}},
\end{align} 
where ${\bf \hat{e}}_j^{\rm PCA}$ are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
and $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the basis vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. 
We used the basis vectors corresponding to the largest six SVD eigenvalues, which account for
more than $90\%$ of the variance in the combined Munsell and Vrhel datasets.

To get a random reflectance spectrum, we generate samples of weights ($\tilde{w}_{ij}$) drawn from the multivariate Gaussian 
distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. 
If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, the randomly generated reflectance spectrum is given as: 
\begin{align}
\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda).
\end{align}
Otherwise the draw is discarded and a new set of weights is drawn.

For generating the target object reflectance at a particular LRV $(Y_{\rm T})$, the values in a generated spectrum were 
scaled by 
\begin{align}
\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}
\end{align} 
with $\bar{y}(\lambda)$ being the CIE photopic luminosity (or luminous efficiency) function, which
describes the average spectral sensitivity of human visual 
perception of luminance. The target reflectance is then given by: 
\begin{align}
\tilde{R}^{\rm T}_i(\lambda) =\tilde{R}_i(\lambda) \cdot\left(\frac{Y_{\rm T}}{\int d\lambda \tilde{R}(\lambda) D_{65}(\lambda) \bar{y}(\lambda)}\right).
\end{align}

\bibliography{references}

\end{document}

### 2018-05-25 Draft5/draft5.tex
added another figure
Typo fixes

@@
 \title{Luminance constancy under fixed geometry}
+%% Luminance constancy in naturalistic scenes
+%% Learned luminance constancy: something
+%%
+
 \abstract{The light that reflects off an object surface and is captured by our eyes varies significantly with its context. 
@@
  \end{figure}
+ %% DHB: Add comment that resolution here (and maybe in some other figures) is higher than that used for AMA.
+ %% DHB: Add axis labels to (b).
 
@@
     \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional inserted objects.
-The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}
+The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}.
 \end{figure}
-%% DHB: We need to think about how to scale the images for display.  The Library scene is too dark, at least when printed.
-% % VS: Is it still dark?
+%% DHB: We need to say that each image in (a) was scaled and tone mapped individually to optimize the mapping into the available display gamut.
 
@@
 Thus, for each target object LRV value, the shape of the target object surface reflectance spectra could differ.
-%% DHB Need to decide how many images we really want for final version of the work.
+%% DHB Need to decide how many images we really want for final version of the work.  1000, 1000, 3000.
 
@@
 Figure~\ref{fig:Condition2}(c,d) shows that performance improves greatly with contrast normalization. 
-Estimates obtained from the AMA receptive field reponses are essentially perfect. 
+Estimates obtained from the AMA receptive field responses are essentially perfect. 
 Estimates obtained from linear regression are substantially improved.
@@
 Condition 3 introduces variation in the reflectance spectra of the background objects, in addition to the sources of variation in Conditions 1 and 2.
-This condition models all the sources of real-world spectral variation that is most relevant for the computational problem of luminance constancy.
-% JDB: Folks are ok with "all the sources"?
+This condition models the sources of real-world spectral variation that is most relevant for the computational problem of luminance constancy.
 We again trained and evaluated AMA for labeled images patches, using the contrast normalized cone excitations.
@@
 Inclusion of more receptive fields reduces the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
+
+% Figure Error Bar Graphs
+\begin{figure}
+\centering
+\includegraphics[width=0.6\textwidth]{../FiguresDraft5/FigureRMSEVsN/Figure14.pdf}
+\caption{{\bf Variation of relative RMSE with number of RFs and size of training set:} (a) Variation of relative RMSE for Condition 3 as the size of training set.
+The relative RMSE converges around 2000 images.
+(b) Variation of relative RMSE v/s the number of receptive fields used in estimation.
+The performance converges around 6 Rfs}
+ \label{fig:barGraphs}
+\end{figure}
 %% DHB: It might be natural here to show a plot of relative RMSE versus number of receptive fields, and for the best number of receptive
@@
 This flexibility allows the study of individual scene factors as well as their combined effects.
-Here, we exploited this flexibility to quantify how variation in the shape of the reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation..
+Here, we exploited this flexibility to quantify how variation in the shape of the reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation.
 We believe this basic approach can be extended to include parametric control over the amount of variation of different factors as well as to include variation in additional factors (see below).

### 2018-05-27 Draft5/draft5.tex
johannes is thru the captions

@@
     \label{introFigure}
-    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination. 
-Additionally, the reflected light also depends on geometric factors, such as the object's shape, pose, and position. 
-The human visual system is able to account for variations in the reflected light due to object-extrinsic factors and produce a percept of object color that is relatively stable across such variations, an ability called color constancy.
+    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination of the object. 
+The reflected light also depends on geometric factors, such as the object's shape, pose, and position. 
+The human visual system accounts for variations in the reflected light due to object-extrinsic factors and produces a percept of object color that is relatively stable across such variations, an ability called color constancy.
 (b) Images of a sphere under a fixed illuminant.  
-Down each column, the reflectance function of the sphere varies only by a scale factor; the shape of the reflectance spectrum is held fixed.  
-The shape of the reflectance spectrum varies across each row.
-Within each row, the light reflectance value (LRV) of the spheres is constant. 
-The values on the left of each row provide the corresponding LRV. 
+Down each column, the sphere's luminance reflectance value (LRV) varies, but the shape of the reflectance spectrum is held fixed.
+Across each row, the shape of the reflectance spectrum varies, but the LRV is held fixed.
 We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors. 
@@
     \end{subfigure}
-    \caption{{\bf Base scenes.} Each panel shows a rendering of one base scene without additional inserted objects.
-The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from models of naturally occurring spectra (see text).}\label{fig:baseScenes}.
+    \caption{{\bf Base scenes.} Each subplot shows a rendering of one base scene without additional inserted objects.
+The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from statistical models of naturally occurring spectra (see text).}\label{fig:baseScenes}.
 \end{figure}
@@
 \caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
-The panels show different objects inserted in the library base scene.
-The objects were inserted at a user defined location in the image.
-Then the rendering viewpoint was set so that the object is at the center of the rendered image.
-In these panels, the full rendered image has been cropped so that the inserted object is visually salient.}\label{fig:libraryWithTarget}
+The subplots show different objects inserted in the library base scene at a user specified location.
+Then the rendering viewpoint was set so that the object was at the center of the rendered image.
+In these subplots, the full rendered image has been cropped so that the inserted object is takes up a large proportion of the presented image patch.}\label{fig:libraryWithTarget}
 \end{figure}
@@
 
-    \caption{{\bf Scene transformations.} The properties of a visual scene can broadly be classified into two groups: geometrical (a-b) and spectral (c-e).
+    \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e).
 Our rendering package provides control over the properties illustrated by the columns of the figure.
@@
     \end{subfigure}    
-    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2 and 3.
-The numbers on the left indicate the standard luminance level of the target object.
-5 images are shown at each luminance level.
+    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2, and 3.
+Five images are shown for each luminance reflectance value (LRV).
+Each dataset had at least 100 images for each LRV.
 We studied three types of spectral variations.
-(a) Condition 1: target object relative surface reflectance spectrum variable, light source spectra fixed, background object spectra fixed (same as Fig.~\ref{fig:introExampleFigure}).
-(b) Condition 2: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra fixed, (c) Condition 3: target object relative surface reflectance spectrum variable, light source spectra variable, background object spectra variable.
-The spheres in each row of each panel have the same surface luminance, while the spheres in each column of each panel have the same relative surface reflectance.
-Across the three panels, spheres in corresponding locations have the same surface reflectance.
-In all three panels, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
-This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for the figure.
-The sRGB values for all three panels were normalized using a common scale factor prior to gamma correction.}
+(a) Condition 1: variable target object relative surface reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
+(b) Condition 2: variable target object relative surface reflectance spectrum, variable light source spectra, fixed background object spectra, (c) Condition 3: variable target object relative surface reflectance spectrum, variable light source spectra, variable background object spectra.
+The spheres in each row of subplots have the same LRV, while the spheres in each column of each subplot have the same relative surface reflectance.
+Across the three sets of subplots, spheres in corresponding locations have the same surface reflectance.
+In all three subplots, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for computer monitors and printed figures.
+The sRGB values for all three subplots were normalized using a common scale factor prior to gamma correction.}
 \label{fig:studiedCases}
 \end{figure}
+%%JDB: ADD "Luminance Reflectance Value (LRV) label to the left-most y-axis.
+%%JDB: DOUBLE CHECK FIRST SENTENCE ON SECOND LINE OF CAPTION: "Each dataset had at least 100 images for each LRV."
+%% JDB: "relative surface reflectance" AFTER CONDITION 3 IS DESCRIBED... CHANGE TO WHATEVER OUR STANDARD TERM IS... "shape of reflectance spectra"?
+%% JDB: I changed: "Across the subplots" to "Across the three sets of subplots"... DOUBLE CHECK THAT THE LANGUAGE IS CORRECT.
+%% JDB: update range [0.5, 1.5] so it is anchored to a luminance level...
+%% JDB: Changed "dynamic range available for computer monitors and printed figures" to "dynamic range available for computer monitors and printed figures".  OK WITH VIJAY AND DAVID?
 
@@
     \label{fig:sceneWithCroppedImage}
-    \caption{{\bf Pipeline for generating labeled datasets:}  For the supervised learning approach employed in this work, labeled images are generated as follows: (a) A 3D virtual scene, containing a target object is created.
+    \caption{{\bf Pipeline for generating labeled datasets:}  The labeled images used in this paper are generated as follows: (a) A 3D virtual scene, containing a target object is created.
 The rendering viewpoint is selected so that the target object is in the center of the image.
@@
 A multispectral image of the scene is then rendered.
-(b) The central portion of the rendered image, which contains the target object, is cropped.
-(c) The retinal image corresponding to the rendered image is computed, and this is used in turn to compute the excitations (taken as the number of photopigment isomerizations) of the cone photoreceptors.
-The figure shows the a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).
-(d) The cone excitations are interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
+(b) The central portion of the rendered image is cropped around the target object.
+(c) The retinal image corresponding to the rendered image is computed, which is then used to compute the number of photopigment isomerizations in the cone photoreceptors.
+The figure shows a rendering of the retinal image after optical blurring, with the location and identity of the cones indicated by an overlay (L cones: red, M cones: green, S cones: blue).
+(d) The cone excitations are linearly interpolated to estimate the responses of all the three types of cone at each location (demosaicing).
 Finally, the demosaiced images are contrast normalized.}
@@
 %% Scene: 
-%%- the default mean luminance was set to 200, but there is a key-value param that could have overriden this value. 
+%%- the default mean luminance was set to 200, but there is a key-value param that could have overridden this value. 
 %%  I do not know if this were the case.
@@
 %
-%%- The default FOV was 1 deg, but there is a key-value param that could have overriden this value.
+%%- The default FOV was 1 deg, but there is a key-value param that could have overridden this value.
 %%  I do not know if this were the case.
@@
 %%
-%%- Distance default is 1 meter, but there is  a key-value param that could have overriden this value.
+%%- Distance default is 1 meter, but there is  a key-value param that could have overridden this value.
 %%  I do not know if this were the case.
@@
 %%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
-%%but there is a key-value param that could have overriden this value. I do not know what that parameter value was.
+%%but there is a key-value param that could have overridden this value. I do not know what that parameter value was.
 %%
@@
 %%- There is a key-value pair to also low-pass the optical image with default value to not do so.
-%%  If that was user-overriden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
+%%  If that was user-overridden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
 %%
@@
     \end{subfigure}   
-    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the cone excitations.
+    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression on the cone excitations.
 Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation.
@@
 Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.1\%  for AMA based estimation.
-(b) Cone excitations projected along the first two AMA receptive fields for training images of Condition 1.
-Each cloud represents the image patches corresponding to one LRV.
-The clouds are approximated by a multivariate Gaussians whose means and variances are approximated by the ellipses shown in the figure.
-(c) The first two AMA receptive fields learnt using the cone excitations of stimuli in the training set.}
+(b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields.
+Each cluster of responses represents the image patches associated with a particular LRV, which is coded by color.
+The response clusters are approximated by a multivariate Gaussians whose mean and covariance matrices are represented by the ellipses shown in the figure.
+(c) The first two AMA receptive fields learned using the cone excitations of stimuli in the training set.}
 \label{fig:Condition1}
@@
     \end{subfigure}
-    \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the cone excitations.
+    \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
 The relative RMSE is high (41.4\% for linear regression and 31.3\% for AMA based estimation).
-(b) Cone isomerizations projected on AMA receptive fields calculated using cone excitations.
-(c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the contrast normalized cone excitations.
+(b) Cone excitations projected onto AMA receptive fields.
+(c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
 The relative RMSE of estimation is 9.3\% for linear regression and 1.1\% for AMA based estimator.
@@
 The receptive fields were learned using AMA and the contrast normalized cone excitations.
-For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is contrast normalized cone excitations rather than the cone excitations themselves.}
+For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is contrast normalized cone excitations than when the input is the raw cone excitations.}
 \label{fig:Condition2}
@@
     \end{subfigure}
-    \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using linear regression and AMA estimators, based on the contrast normalized cone excitations.
+    \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
 The relative RMSE is 22.9\%  for linear regression and 13.0\% for AMA.
-(b) Contrast normalized cone excitations for the training set projected along the first two AMA receptive fields.
-(c) First two AMA receptive fields learnt using the contrast normalized cone excitations.}
+(b) Contrast normalized cone excitations for the training set projected onto the first two AMA receptive fields.
+(c) First two AMA receptive fields learned using the contrast normalized cone excitations.}
 \label{fig:Condition3}
@@
 \includegraphics[width=0.6\textwidth]{../FiguresDraft5/FigureRMSEVsN/Figure14.pdf}
-\caption{{\bf Variation of relative RMSE with number of RFs and size of training set:} (a) Variation of relative RMSE for Condition 3 as the size of training set.
+\caption{{\bf Change of relative RMSE with number of receptive fields (RFs) and size of training set:} (a) Change of relative RMSE for Condition 3 with the size of training set.
 The relative RMSE converges around 2000 images.
-(b) Variation of relative RMSE v/s the number of receptive fields used in estimation.
-The performance converges around 6 Rfs}
+(b) Change of relative RMSE with the number of receptive fields.
+Performance converges around 6 RFs}
  \label{fig:barGraphs}
@@
 % % VS: On switching off secondary reflections, the performance (rel RMSE) remains essentially the same. Which means that this is not the primary source of variation.
-% % VS: To ensure that secondary reflections were switched off, I checked that the multispectral values of the central patch of the rendered image and the corresponding cone isoemrizations were the same for images that were generated with the same target and illuminant but different backgrounds.
+% % VS: To ensure that secondary reflections were switched off, I checked that the multispectral values of the central patch of the rendered image and the corresponding cone isomerizations were the same for images that were generated with the same target and illuminant but different backgrounds.
 Then I performed the training and test as usual.
@@
 \includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure13/Figure13_a.pdf}
-\caption{{\bf Summary of luminance constancy performance:} The plot shows the relative RMSE estimation error for each method and condition.The relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
+\caption{{\bf Summary of luminance constancy performance:} Relative RMSE estimation error for each method and condition.
+Relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
 The mean is taken over all stimuli in the test set.}
@@
 In addition, the dataset of illuminations does not include the artificial illuminations that we now live much of our lives under.
-% JDB: What are "constraints on naturally occuring reflectance functions"?
+% JDB: What are "constraints on naturally occurring reflectance functions"?
 Future work with virtual image datasets will benefit from targeted efforts to characterize the natural statistics of the scene components that are varied.

### 2018-05-27 Draft5/draft5.tex
pass through abstract

@@
 
-\abstract{The light that reflects off an object surface and is captured by our eyes varies significantly with its context. 
-But, the human visual system has the ability to stably perceive the object's color invariant of the context variations. 
-While this invariance detection ability is behaviorally very significant, its mechanism remains largely unknown. 
-To understand the computational principles that lead to invariant color perception, 
-here we study the perception of object light reflectance value (LRV) under variations in naturalistic scenes. 
-Specifically, we study the effects of variations in reflectance and illumination spectra in a scene on the 
-perceived LRV of an object. 
-To do this, we have developed a software that renders naturalistic multispectral images of 3D scenes with 
+\abstract{
+% JDB commented out: The light that reflects off an object surface and is captured by our eyes varies significantly with its context. 
+ % JDB addition:
+ The human visual system supports stable percepts of object color even though the light that reflects off object surfaces varies significantly with context.
+% JDB commented out: But, the human visual system has the ability to stably perceive the object's color invariant of the context variations. 
+% JDB commented out: While this invariance detection ability is behaviorally very significant, its mechanism remains largely unknown. 
+To understand the computations that support invariant color perception, 
+we study how the estimation of object light reflectance value (LRV) depends on variation in key properties of naturalistic scenes. 
+Specifically, we study how variation in target object reflectance, background object reflectance, and illumination spectra in a scene impact estimates of LRV. 
+To do this, we developed a software pipeline that renders naturalistic multispectral images of 3D scenes with 
 precise control over the geometrical and spectral factors that make a scene. 
@@
 an accurate model of the early visual system. 
-We then use supervised learning methods on these labeled cone responses to 
+We then use a supervised statistical learning methods on these labeled cone responses to 
 identify the computations that lead to accurate LRV estimation under changes in spectral condition. 
@@
 (b) Images of a sphere under a fixed illuminant.  
-Down each column, the sphere's luminance reflectance value (LRV) varies, but the shape of the reflectance spectrum is held fixed.
+Down each column, the sphere's light reflectance value (LRV) varies, but the shape of the reflectance spectrum is held fixed.
 Across each row, the shape of the reflectance spectrum varies, but the LRV is held fixed.
@@
     \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2, and 3.
-Five images are shown for each luminance reflectance value (LRV).
+Five images are shown for each light reflectance value (LRV).
 Each dataset had at least 100 images for each LRV.
@@
 \end{figure}
-%%JDB: ADD "Luminance Reflectance Value (LRV) label to the left-most y-axis.
+%%JDB: ADD "light reflectance value (LRV) label to the left-most y-axis.
 %%JDB: DOUBLE CHECK FIRST SENTENCE ON SECOND LINE OF CAPTION: "Each dataset had at least 100 images for each LRV."
@@
 We used a software pipeline, which was developed for this work, to render datasets of multispectral images from scene descriptions.
-Because we rendered the images, we could label each image in the dataset by the luminance reflectance value (LRV) of the target object.
+Because we rendered the images, we could label each image in the dataset by the light reflectance value (LRV) of the target object.
 We used the labeled datasets to learn estimators for the target object LRV.

### 2018-05-28 Draft5/draft5.tex
updated figures
small edits

@@
 Specifically, we study how variation in target object reflectance, background object reflectance, and illumination spectra in a scene impact estimates of LRV. 
-To do this, we developed a software pipeline that renders naturalistic multispectral images of 3D scenes with 
-precise control over the geometrical and spectral factors that make a scene. 
-We label these images with the LRV of a specific object in the scene. 
-Next, we simulate the response of the retinal cones to these multispectral images using 
-an accurate model of the early visual system. 
-We then use a supervised statistical learning methods on these labeled cone responses to 
-identify the computations that lead to accurate LRV estimation under changes in spectral condition. 
-We show that if only either target or target and illumination spectra are allowed to vary, the standard luminance can be estimated through simple transformations of the cone responses. 
-When all the spectra vary simultaneously, while it is not easy to recover the luminance through simple transformations, 
-a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and  
-S cones can recover the luminance within about 13\% RMSE.}
+To do this, we apply supervised statistical learning methods on the simulated response of human cone responses to labeled naturalistic images.
+We show that, under naturalistic variations in the spectral properties of the scene, a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and  S cones can recover the luminance within about 13\% RMSE.
+%To do this, we developed a software pipeline that renders naturalistic multispectral images of 3D scenes with 
+%precise control over the geometrical and spectral factors that make a scene. 
+%We label these images with the LRV of a specific object in the scene. 
+%Next, we simulate the response of the retinal cones to these multispectral images using 
+%an accurate model of the early visual system. 
+%We then use a supervised statistical learning methods on these labeled cone responses to 
+%identify the computations that lead to accurate LRV estimation under changes in spectral condition. 
+%We show that if only either target or target and illumination spectra are allowed to vary, the standard luminance can be estimated through simple transformations of the cone responses. 
+%When all the spectra vary simultaneously, while it is not easy to recover the luminance through simple transformations, 
+%a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and  
+%S cones can recover the luminance within about 13\% RMSE.
+}
 
@@
         \caption{Target position}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.pdf}
         \label{fig:targetPositionVariation}
@@
         \caption{Target size/Orientation}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
         \label{fig:targetSizeOrientation}
@@
         \caption{Target spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.pdf}
         \label{fig:targetVariation}
@@
         \caption{Illumination spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.pdf}
         \label{fig:illuminationVariation}
@@
         \caption{Background spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.pdf}
         \label{fig:backGroundVariation}
@@
 We studied three types of spectral variations.
-(a) Condition 1: variable target object relative surface reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
-(b) Condition 2: variable target object relative surface reflectance spectrum, variable light source spectra, fixed background object spectra, (c) Condition 3: variable target object relative surface reflectance spectrum, variable light source spectra, variable background object spectra.
+(a) Condition 1: variable shape of the target object reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
+(b) Condition 2: variable shape of the target object reflectance spectrum, variable light source spectra, fixed background object spectra, (c) Condition 3: variable shape of the target object reflectance spectrum, variable light source spectra, variable background object spectra.
 The spheres in each row of subplots have the same LRV, while the spheres in each column of each subplot have the same relative surface reflectance.
@@
 %% JDB: update range [0.5, 1.5] so it is anchored to a luminance level...
+%% VS: Range of mean Isomerization in central patch: 100-100,000
 %% JDB: Changed "dynamic range available for computer monitors and printed figures" to "dynamic range available for computer monitors and printed figures".  OK WITH VIJAY AND DAVID?
@@
 \centering
-\includegraphics[width=0.6\textwidth]{../FiguresDraft5/FigureRMSEVsN/Figure14.pdf}
+\includegraphics[width=0.6\textwidth]{../FiguresDraft5/Figure13/Figure13.pdf}
 \caption{{\bf Change of relative RMSE with number of receptive fields (RFs) and size of training set:} (a) Change of relative RMSE for Condition 3 with the size of training set.
@@
 (b) Change of relative RMSE with the number of receptive fields.
-Performance converges around 6 RFs}
+Performance converges around 6 RFs.}
  \label{fig:barGraphs}
@@
 \centering
-\includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure13/Figure13_a.pdf}
+\includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure14/Figure14.pdf}
 \caption{{\bf Summary of luminance constancy performance:} Relative RMSE estimation error for each method and condition.

### 2018-05-28 Draft5/draft5.tex
Today’s edits

@@
 \abstract{
-% JDB commented out: The light that reflects off an object surface and is captured by our eyes varies significantly with its context. 
- % JDB addition:
 The human visual system supports stable percepts of object color even though the light that reflects off object surfaces varies significantly with context.
-% JDB commented out: But, the human visual system has the ability to stably perceive the object's color invariant of the context variations. 
-% JDB commented out: While this invariance detection ability is behaviorally very significant, its mechanism remains largely unknown. 
 To understand the computations that support invariant color perception, 
-we study how the estimation of object light reflectance value (LRV) depends on variation in key properties of naturalistic scenes. 
+we study how the estimation of the light reflectance value of a target object (LRV; a measure of the light reflected from the object under a standard illuminant) depends on variation in key properties of naturalistic scenes.
 Specifically, we study how variation in target object reflectance, background object reflectance, and illumination spectra in a scene impact estimates of LRV. 
-To do this, we apply supervised statistical learning methods on the simulated response of human cone responses to labeled naturalistic images.
-We show that, under naturalistic variations in the spectral properties of the scene, a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and  S cones can recover the luminance within about 13\% RMSE.
-%To do this, we developed a software pipeline that renders naturalistic multispectral images of 3D scenes with 
-%precise control over the geometrical and spectral factors that make a scene. 
-%We label these images with the LRV of a specific object in the scene. 
-%Next, we simulate the response of the retinal cones to these multispectral images using 
-%an accurate model of the early visual system. 
-%We then use a supervised statistical learning methods on these labeled cone responses to 
-%identify the computations that lead to accurate LRV estimation under changes in spectral condition. 
-%We show that if only either target or target and illumination spectra are allowed to vary, the standard luminance can be estimated through simple transformations of the cone responses. 
-%When all the spectra vary simultaneously, while it is not easy to recover the luminance through simple transformations, 
-%a decoding scheme that compares the light from the target and the surround, and properly adds the response of the L,M and  
-%S cones can recover the luminance within about 13\% RMSE.
+To do this, we apply supervised statistical learning methods to the simulated excitations of human cone photoreceptors, obtained from labeled naturalistic images.
+The naturalistic images were obtained using computer graphics, where the scenes to be rendered were stochastically generated in conjunction with statistical models of natural spectral variation.
+We show that a decoding scheme that compares the light from the target and the surround can recover target object LRV to within about 13\% RMSE.
+%% DHB, VS: Maybe try to add a sentence saying why it is important.
 }
@@
 (b) Images of a sphere under a fixed illuminant.  
-Down each column, the sphere's light reflectance value (LRV) varies, but the shape of the reflectance spectrum is held fixed.
+Down each column, the sphere's light reflectance value (LRV) varies, but the relative reflectance spectrum (i.e. its spectral shape) is held fixed.
 Across each row, the shape of the reflectance spectrum varies, but the LRV is held fixed.
@@
  \end{figure}
- %% DHB: Add comment that resolution here (and maybe in some other figures) is higher than that used for AMA.
- %% DHB: Add axis labels to (b).
+%% DHB: Need to decide and then change with search through document: "relative reflectance spectrum" or "shape of reflectance spectrum".
+% I prefer relative, because "shape" in a vision paper generally refers to object shape.
+% And we found at least one instance where trying to use "shape" led to an awkward construction.
 
@@
     \caption{{\bf Base scenes.} Each subplot shows a rendering of one base scene without additional inserted objects.
-The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from statistical models of naturally occurring spectra (see text).}\label{fig:baseScenes}.
-\end{figure}
-%% DHB: We need to say that each image in (a) was scaled and tone mapped individually to optimize the mapping into the available display gamut.
+The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from statistical models of naturally occurring spectra (see text).
+The images in this figure have been scaled and tone mapped individually for illustrative purposes.}
+\label{fig:baseScenes}. \end{figure}
+%% DHB: Let's get the scaling and tone mapping used for these under control, so we know what it is.
+%% DHB: Maybe also say that the illumination scaling is much smaller than the range used in the study, so that it is possible to see it with common scaling.
 
@@
 \caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
-The subplots show different objects inserted in the library base scene at a user specified location.
-Then the rendering viewpoint was set so that the object was at the center of the rendered image.
-In these subplots, the full rendered image has been cropped so that the inserted object is takes up a large proportion of the presented image patch.}\label{fig:libraryWithTarget}
+Each image (a-e) shows a different object inserted into a user specified location in the library base scene.
+The rendering viewpoint was set so that the object was at the center of the rendered image.
+The full rendered image has been cropped here so that the inserted object is easily visible.}\label{fig:libraryWithTarget}
 \end{figure}
@@
 \end{figure}
-%% DHB: These are too dark in a printout.
-Let's review how they are scaled.
-Need to make sure we can see an effect of changing the illumination, might want to hand pick the illuminants used here to illustrate the effect.
+%% DHB: Need to generate these so that we display them all with a common scale factor and tone mapping. Then say so in the caption once it is done.
 
@@
 spectral power distribution of the light sources--varied in addition to the target object LRV.
-Each condition had a corresponding dataset of 1000 scenes and images, 100 for each of 10 target object LRV values.
+Conditions 1 and 2 had datasets consisting of 1000 scenes and images, 100 for each of 10 target object LRV values. 
+Condition 3 had a dataset consisting of 3000 scenes and images, 300 each for the 10 target LRV values.
 The LRV values were equally spaced between 0.2 and 0.6.
@@
 Thus, for each target object LRV value, the shape of the target object surface reflectance spectra could differ.
-%% DHB Need to decide how many images we really want for final version of the work.  1000, 1000, 3000.
 
@@
 Five images are shown for each light reflectance value (LRV).
-Each dataset had at least 100 images for each LRV.
 We studied three types of spectral variations.
 (a) Condition 1: variable shape of the target object reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
-(b) Condition 2: variable shape of the target object reflectance spectrum, variable light source spectra, fixed background object spectra, (c) Condition 3: variable shape of the target object reflectance spectrum, variable light source spectra, variable background object spectra.
-The spheres in each row of subplots have the same LRV, while the spheres in each column of each subplot have the same relative surface reflectance.
-Across the three sets of subplots, spheres in corresponding locations have the same surface reflectance.
-In all three subplots, the overall lights source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
-This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for computer monitors and printed figures.
+(b) Condition 2: variable shape of the target object reflectance spectrum, variable light source spectra, fixed background object spectra.
+(c) Condition 3: variable shape of the target object reflectance spectrum, variable light source spectra, variable background object spectra.
+The spheres in each row of each panel have the same LRV, while the spheres in each column of each panel have the same relative surface reflectance.
+Across panels a-c, spheres in corresponding locations have the same surface reflectance.
+In all three panels, the overall light source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for display in publication.
 The sRGB values for all three subplots were normalized using a common scale factor prior to gamma correction.}
@@
 \end{figure}
-%%JDB: ADD "light reflectance value (LRV) label to the left-most y-axis.
-%%JDB: DOUBLE CHECK FIRST SENTENCE ON SECOND LINE OF CAPTION: "Each dataset had at least 100 images for each LRV."
-%% JDB: "relative surface reflectance" AFTER CONDITION 3 IS DESCRIBED... CHANGE TO WHATEVER OUR STANDARD TERM IS... "shape of reflectance spectra"?
-%% JDB: I changed: "Across the subplots" to "Across the three sets of subplots"... DOUBLE CHECK THAT THE LANGUAGE IS CORRECT.
-%% JDB: update range [0.5, 1.5] so it is anchored to a luminance level...
-%% VS: Range of mean Isomerization in central patch: 100-100,000
-%% JDB: Changed "dynamic range available for computer monitors and printed figures" to "dynamic range available for computer monitors and printed figures".  OK WITH VIJAY AND DAVID?
 
@@
 This procedure restores the three-order of magnitude intensity variation present in the original dataset.
+We chose the particular scale factor range so that the mean number of cone isomerizations from the target object ranged from approximately 100 to 100,000 for the 100 msec cone integration time we used (see below).
+This range corresponds approximately to that for natural viewing.
 
@@
 In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle (REFS).
-%% VS: Needed a reference
-The local analysis is thus motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
+%% VS: Needed a reference from Johannes.
+The local analysis is thus motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally (REFS).
 %% DHB: Johannes to provide his favorite citation or two.  Some review.
@@
 %%
-%%- IntegrationTime was not specified, so it was the default which is 5 msec.
+%%- IntegrationTime was not specified, so it was the default which is 5 msec (note VS subsequently changed to 100 msec).
 %%  The cone isomerization maps were also demosaiced using linear interpolation.
@@
 
-The cone excitations represent the first step of visual processing. % JDB: paragraph seems disjoint. Talk to David and Vijay.
 To put the computed cone excitations into a form for use in further processing, we demosaiced the excitations for each cone class using linear interpolation
@@
 The demosaicing and normalization do not alter the information in the cone excitation images. 
+% JDB: paragraph seems disjoint. Talk to David and Vijay.
+% DHB and VS: We think it is fine but are leaving the comment so we can call remember to discuss.
 
@@
 
-%% DHB: We meed to figure out and say something about how we scaled image intensities into a reasonable range.
-
 \subsection{Computational luminance constancy} \label{method:SupervisedLearning}
 We used our datasets to determine how well target object LRV can be estimated from cone excitations and from normalized cone contrasts.
-Studying both representations allows us to understand how early contrast coding and normalization affect how well luminance constancy can be achieved.
-%% VS: This sentence does not read well.
+Studying both representations allows us to understand how early contrast coding and normalization affect luminance constancy.
 We applied accuracy maximization analysis (AMA) to learn the optimal receptive fields for estimating LRV,
@@
 AMA is a task-specific Bayesian method for dimensionality reduction.
-When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of linear receptive fields.
-Given a set of linear receptive fields and an explicit cost function, it is possible to determine the minimum-expected-cost estimator that maps responses to stimulus labels given the training set and the
-assumption that all images in the training set are equally likely.
-% VS: This is not very clear.
+When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of N linear receptive fields, where N is a parameter of the procedure.
+These receptive fields are chosen so that decoding their responses leads to minimum-expected-cost estimation, relative to any other choice of N linear receptive fields.
+This is possible because given a training set together with a set of N linear receptive fields and an explicit cost function, it is possible to determine the minimum-expected-cost estimator that maps the receptive field responses to the stimulus labels, on the assumption that all images in the training set are equally likely.
 Moreover, the corresponding expected estimation cost may be explicitly computed.
-AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
-Here we used Kullback-Leibler divergence cost function and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e. Poisson-like noise with a fano factor of 1.3).
-Details of how AMA learns filters and the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
+Thus, AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
+Here we used the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
+Poisson-like noise with a fano factor of 1.3).
+Details of how AMA learns filters and how the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
+For each condition, we learned the filters with a training set consisting of 90\% of the images.
 
@@
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
-Here we use a Kullback-Leibler divergence cost function, so that the optimal estimator is the maximum a posteriori estimate.
-% JDB: I thought we were using a squared error cost function. See above?
-%% DHB: Uniform prior, right? And posterior mean?  If not, correct prose above.
+Here we again used a Kullback-Leibler divergence cost function, so that the optimal estimator is the maximum a posteriori estimate.
+The Gaussian approximations were estimated using the same training set that was used to learn the receptive fields.
+Estimation performance was evaluated using a test set consisting of the 10\% of images that were not in the training set.
+For our primary results, estimation was based on 6 receptive fields.
+%% JDB: I thought we were using a squared error cost function. See above?
+%% DHB: Wouldn't it make more sense to use MSE and posterior mean for both learning and decoding, since we are reporting relative RMSE as our performance measure?
 
@@
 In Condition 1, only the LRV and the shape of the reflectance spectrum of the target object vary across scenes.
-For this condition, LRV estimation should be easy because the variation in target object reflectance that we introduced
-preserved LRV (which is calculated using a CIE D65 as the illumination).
-% JDB: Isn't this true of all conditions? LRV is preserved for each set of images with the same LRV label for all conditions.
-% VS: We should say, "the variation that we introduced preserved LRV"
-Thus, for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
-In Condition 1, we used an illumination randomly sampled from our model of daylight illumination spectra (see Methods) and thus expect a reasonable degree of similarity to D65.
-%% DHB: We need to say something about how similar.  Might explore different illuminants to dissect how sensitive the estimation
-% is to whether the fixed illuminant is D65 or something else.  Probably not very, but this is an example of something we can exploit
-% our graphics approach to understand, and we want to build up examples.
-% JDB: I agree. The statement in current form is unnecessarily vague. With a bit of additional analysis, we could also say that different random samples produce nearly identical results, etc. etc.
-
 We used accuracy maximization analysis (AMA) to learn a set of linear receptive fields that are optimal for estimating target LRV from the cone excitations to the image patches in this condition. 
-%We used AMA to learn a set of linear receptive fields that are optimal for estimating target LRV for this condition.
-%We trained and evaluated AMA on the cone excitations to the image patches.
 Decoding performance for the test set is shown in Figure~\ref{fig:case1Estimates}. 
@@
 For this condition, the background regions provide very little task-relevant information. 
-They are useful only because some light is scattered from them onto the target, and vice versa. 
-% JDB: Double check vice versa.
 In addition, luminance is primarily determined by L and M cones, so the S cones should make little
 contribution.
+
+The results in Figure {fig:Condition1} were obtained for one particular draw from our statistical model of illumination.
+We verified that performance remained excellent for other draws.
+
+%% DHB, VS: Maybe the above sentence is all we really need, and can delete what's below? Vijay's analysis did not actually use illuminants drawn
+% from the distribution, though.  Clarify?  Or actually do that?
+%
+%For this condition, LRV estimation should be easy because the variation in target object reflectance that we introduced
+%preserved LRV (which is calculated using a CIE D65 as the illumination).
+%Thus, for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
+%In Condition 1, we used an illumination randomly sampled from our model of daylight illumination spectra (see Methods).
+% and thus expect a reasonable degree of similarity to D65.
+%% DHB: We need to say something about how similar.  Might explore different illuminants to dissect how sensitive the estimation
+% is to whether the fixed illuminant is D65 or something else.  Probably not very, but this is an example of something we can exploit
+% our graphics approach to understand, and we want to build up examples.
+% JDB: I agree. The statement in current form is unnecessarily vague. With a bit of additional analysis, we could also say that different random samples produce nearly identical results, etc. etc.
 
@@
 Estimates obtained from linear regression are substantially improved.
-This observation is consistent with a large literature on computational color constancy that shows that 
-contrast-based representations are effective for supporting color constancy when only illumination spectra vary (REFS).
-However, the same literature shows that contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary.
-%% DHB: Need to add REFS in paragraph above.
+This observation is consistent with previous results on computational color constancy that show that 
+contrast-based representations are effective for supporting color constancy when only illumination spectra vary (e.g. REFS 1).
+However, contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary (e.g. REFS 2).
+%% REFS 1:
+% [1] Land, E.H. 1986 An alternative technique for the computation of the designator in the retinex theory of color vision. Proc. Natl. Acad. Sci. 83, 3078-3080.
+%
+% REFS 2:
+% [1] Brainard, D.H. & Wandell, B.A. 1986 Analysis of the retinex theory of color vision. Journal of the Optical Society of America A 3, 1651-1661.
 
@@
 This overlap is due to the combined effect of the variation in the illumination and background surface spectra.
-However, performance is based on six rather than two receptive fields.
-% JDB: Have we said previously that performance is based on six RFs.
-% VS: No
-Inclusion of more receptive fields reduces the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
+Recall, however, that the performance shown Figure~\ref{fig:case3Estimates} is based on six rather than two receptive fields;
+so that there is likely to be less overlap in the full six-dimensional response space.
+That is, inclusion of more receptive fields will in general reduce the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
+This effect is shown the right panel of Figure REF, which also illustrates the effect of training set size on estimation performance. 
+%% DHB: Check rewrite of last two sentences: OK?
+%% VS to add REF to last sentence above.
 
@@
 The relative RMSE converges around 2000 images.
-(b) Change of relative RMSE with the number of receptive fields.
+To make this plot, the 300 image test set for Condition 3 was used in each case, while the training set size varied between 300 to 2700 images.
+The number of receptive fields used was varied between 1 and 6.
+(b) Same data as in a, but plotted as a function of number of receptive fields.
 Performance converges around 6 RFs.}
@@
 \end{figure}
-%% DHB: It might be natural here to show a plot of relative RMSE versus number of receptive fields, and for the best number of receptive
-% fields of relative RMSE versus size of training set.  We want to persuade the reader that we are at asymptote.
-% JDB: If we do this, it is probably best to put the evidence in the appendix. Otherwise, it will require a detour paragraph and figure subpanel.
+%% DHB: Vijay to fix figure label
 

### 2018-05-29 Draft5/draft5.tex
small edits… added a couple citations

@@
 This general statistical learning approach has been useful for other perceptual problems in early and mid-level vision. domains of vision. 
-For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal}.
+For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
 It has been used to develop ideal observers for defocus blur, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
@@
 As noted in the introduction, supervised learning requires large labeled datasets.
-Such datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful}.
+Labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful}.
+%% JDB: ADD REFERENCE TO Burge, Fowlkes, Banks (2010).
+?Natural scene statistics predict how the figure-ground cue of convexity affects human depth perception?.
+Journal of Neuroscience, 30(21): 7269-7280.
+% JDB: ADD REFERENCE TO Girshick, Landy, Simoncelli (2011). Cardinal rules: visual orientation perception reflects knowledge of environmental statistics. Nature Neuroscience, 14(7), 926-932. 
+%% JDB: ADD REFERENCE TO Burge, McCann, Geisler (2016). Estimating 3D tilt from local image cues in natural scenes. Journal of Vision, 16(13):2, 1?25.
+%% JDB: ADD REFERNECE TO Goncalves & Welchman (2017).  "What Not?? Detectors Help the Brain See in Depth. Current Biology, 27, 1-10
+
 Unfortunately, such datasets are not readily available for studying correlates of object surface reflectance.

### 2018-05-29 Draft5/draft5.tex
still fixing figures
added references

--- 2018-05-28 Draft5/draft5.tex
@@
 These methods use the joint statistics of labeled images and scene variables to learn mappings that extract stable surface color descriptors from image input \cite{barron2015convolutional}.
-This general statistical learning approach has been useful for other perceptual problems in early and mid-level vision. domains of vision. 
-For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal}.
+This general statistical learning approach has been useful for other perceptual problems in early and mid-level vision.
+For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
 It has been used to develop ideal observers for defocus blur, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
@@
         \caption{Library }
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.pdf}
         \label{fig:baseSceneLibrary}
@@
         \caption{Mill}    
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.pdf}
         \label{fig:baseSceneMill}
@@
         \caption{Table-Chairs}    
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.png}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.pdf}
         \label{fig:baseSceneTableChairs}
@@
 
+Our rendering package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
+Base scenes specify an arrangement of objects and light sources.
+Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and additional light sources.
+Once the position, size and pose of the inserted objects and light sources have been set, 
+a surface reflectance function can be assigned to each object in the scene, and a spectral power distribution function can be assigned to each light source (Fig.~\ref{fig:VWCCTransformations}).
+The resulting scene model can then be rendered from any specified viewpoint.
+
 % Figure 4
@@
 (e) Variation in surface reflectance of the background objects.
+All panels in the figure have a common scale factor and tone mapping.
 \label{fig:VWCCTransformations}}
@@
 %% DHB: Need to generate these so that we display them all with a common scale factor and tone mapping. Then say so in the caption once it is done.
-
-Our rendering package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
-Base scenes specify an arrangement of objects and light sources.
-Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and additional light sources.
-Once the position, size and pose of the inserted objects and light sources have been set, 
-a surface reflectance function can be assigned to each object in the scene, and a spectral power distribution function can be assigned to each light source (Fig.~\ref{fig:VWCCTransformations}).
-The resulting scene model can then be rendered from any specified viewpoint.
 
@@
 up to effects of scene geometry, an additional richness that we do not address in this paper.
-In Condition 1, the surface reflectance spectrum of the target object was the only source of scene variation other than the target object LRV.
+In Condition 1, the relative reflectance spectrum of the target object was the only source of scene variation other than the target object LRV.
 The reflectance spectra of the background objects, and the spectral power distributions of the light sources were kept fixed.
-In Condition 2, the spectral power distribution of the light sources varied in addition to the reflectance spectrum of the target object,
-Finally, in Condition 3 three distinct scene factors--target object surface 
-reflectance spectrum, reflectance spectra of the background objects, and
+In Condition 2, the spectral power distribution of the light sources varied in addition to the relative reflectance spectrum of the target object,
+Finally, in Condition 3 three distinct scene factors--target object relative reflectance spectrum, reflectance spectra of the background objects, and
 spectral power distribution of the light sources--varied in addition to the target object LRV.
@@
 For each LRV value, a different target surface reflectance spectra for each of the 100 scenes.
-Thus, for each target object LRV value, the shape of the target object surface reflectance spectra could differ.
+Thus, for each target object LRV value, the relative reflectance spectrum of the target object could differ.
 
@@
 We studied three types of spectral variations.
-(a) Condition 1: variable shape of the target object reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
-(b) Condition 2: variable shape of the target object reflectance spectrum, variable light source spectra, fixed background object spectra.
-(c) Condition 3: variable shape of the target object reflectance spectrum, variable light source spectra, variable background object spectra.
+(a) Condition 1: variable target object relative reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
+(b) Condition 2: variable target object relative reflectance spectrum, variable light source spectra, fixed background object spectra.
+(c) Condition 3: variable target object relative reflectance spectrum, variable light source spectra, variable background object spectra.
 The spheres in each row of each panel have the same LRV, while the spheres in each column of each panel have the same relative surface reflectance.
@@
 The library base scene contains 2 area lights. 
-We inserted one additional spherical spherical light source into the scene.
+We inserted one additional spherical light source into the scene.
 The position and size of the inserted object, inserted light source and viewpoint were held fixed across all 
@@
 \subsection{Model of early visual system} \label{method:Isetbio}
-The light entering the eye is blurred by the eye's optics.
+The light entering the eye is blurred by the optics of the eye.
 The resulting retinal image is sampled by a mosaic of cone photoreceptors.
@@
 %% DHB: Wouldn't it make more sense to use MSE and posterior mean for both learning and decoding, since we are reporting relative RMSE as our performance measure?
+%% VS: The results are similar for both cost function. MSE estimates are biased at the ends.
+%% VS: For case 1 and 2, the first two RFs contain all the information and the performance is based on these two RFs.
 
@@
 
-In Condition 1, only the LRV and the shape of the reflectance spectrum of the target object vary across scenes.
+In Condition 1, only the LRV and the relative reflectance spectrum of the target object vary across scenes.
 We used accuracy maximization analysis (AMA) to learn a set of linear receptive fields that are optimal for estimating target LRV from the cone excitations to the image patches in this condition. 
@@
 This observation is consistent with previous results on computational color constancy that show that 
-contrast-based representations are effective for supporting color constancy when only illumination spectra vary (e.g. REFS 1).
-However, contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary (e.g. REFS 2).
-%% REFS 1:
-% [1] Land, E.H. 1986 An alternative technique for the computation of the designator in the retinex theory of color vision. Proc. Natl. Acad. Sci. 83, 3078-3080.
-%
-% REFS 2:
-% [1] Brainard, D.H. & Wandell, B.A. 1986 Analysis of the retinex theory of color vision. Journal of the Optical Society of America A 3, 1651-1661.
+contrast-based representations are effective for supporting color constancy when only illumination spectra vary (e.g. \citeNP{land1986alternative}).
+However, contrast-based representations are less effective at supporting constancy when the spectra of background objects in the scene vary (e.g. \citeNP{brainard1986analysis}).
 
@@
 That is, inclusion of more receptive fields will in general reduce the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
-This effect is shown the right panel of Figure REF, which also illustrates the effect of training set size on estimation performance. 
+This effect is shown the right panel of Figure~\ref{fig:RMSEvsRF}, which also illustrates the effect of training set size on estimation performance. 
 %% DHB: Check rewrite of last two sentences: OK?
@@
 
-% Figure Error Bar Graphs
+% Figure RMSE vs N RFs
 \begin{figure}
@@
 Performance converges around 6 RFs.}
- \label{fig:barGraphs}
+ \label{fig:RMSEvsRF}
 \end{figure}
-%% DHB: Vijay to fix figure label
+
+%% DHB: We need to write something interpretive about the RF structure shown in panel c.
 
@@
 However, one should not interpret too much into the features that arise due to the specific geometry of the scene.
-
-%% DHB: We need to write something interpretive about the RF structure shown in panel c.
 
@@
 As noted in the introduction, supervised learning requires large labeled datasets.
-Such datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful}.
+Labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful, burge2010natural, girshick2011cardinal, burge2016estimating, goncalves2017not}.
+
 Unfortunately, such datasets are not readily available for studying correlates of object surface reflectance.

### 2018-05-29 Draft5/draft5.tex
fixed results for condition 1

@@
 %% VS: The results are similar for both cost function. MSE estimates are biased at the ends.
-%% VS: For case 1 and 2, the first two RFs contain all the information and the performance is based on these two RFs.
 
@@
 The standard deviations are too small to be visible.
-Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.1\%  for AMA based estimation.
+Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.3\%  for AMA based estimation.
 (b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields.
@@
 (c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
-The relative RMSE of estimation is 9.3\% for linear regression and 1.1\% for AMA based estimator.
+The relative RMSE of estimation is 9.3\% for linear regression and 1.2\% for AMA based estimator.
 (d) The contrast normalized cone excitations projected along the first two AMA receptive fields.

### 2018-05-30 Draft5/draft5.tex
added some text

@@
 \end{figure}
-%% DHB: Need to generate these so that we display them all with a common scale factor and tone mapping. Then say so in the caption once it is done.
 
@@
 Thus, AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
-Here we used the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
+We used the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and means squared cost function (corresponding to mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
 Poisson-like noise with a fano factor of 1.3).
+Both, the Kullback-Leibler divergence cost function and mean squared cost function gave similar results.
+The results in this work are for the Kullback-Leibler divergence cost function (see below).
 Details of how AMA learns filters and how the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
@@
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
-Here we again used a Kullback-Leibler divergence cost function, so that the optimal estimator is the maximum a posteriori estimate.
-The Gaussian approximations were estimated using the same training set that was used to learn the receptive fields.
+Here we again used both Kullback-Leibler divergence cost function and mean square cost function, so that the optimal estimator is the maximum a posteriori estimate and the mean estimate respectively.
+The results in both cases were comparable.
+We present the results for the Kullback-Leibler divergence cost function case as the estimates obtained by the mean squared cost function have a bias near the lower and the upper limits of the LRV values used in our simulations.
+The bias results because the LRV values are bounded in the range [0.2, 0.6] in estimating the posterior.
+
+The Gaussian approximations for the posterior were estimated using the same training set that was used to learn the receptive fields.
 Estimation performance was evaluated using a test set consisting of the 10\% of images that were not in the training set.
@@
 
+%% VS added ->
+Our software allows us to compare the effect of background surface reflectances on target object LRV with and without secondary reflections from background objects. 
+Our analysis shows that the secondary reflections have minimal effect on LRV estimates.
+The estimates without secondary reflections are comparable to that with reflections.
+This shows that the primary source of the estimation error is due to the variability in the contrast estimation due to finite number of samples in the background and not due to secondary reflections.
+
 %% DHB; We were going to vary the number of secondary reflections modeled in the rendering for one of the conditions, to
 % separate the two possible sources of influence of the background surfaces.
-% % VS: On switching off secondary reflections, the performance (rel RMSE) remains essentially the same. Which means that this is not the primary source of variation.
-% % VS: To ensure that secondary reflections were switched off, I checked that the multispectral values of the central patch of the rendered image and the corresponding cone isomerizations were the same for images that were generated with the same target and illuminant but different backgrounds.
-Then I performed the training and test as usual.
 
@@
 We believe this basic approach can be extended to include parametric control over the amount of variation of different factors as well as to include variation in additional factors (see below).
+%% VS added ->
+For example, we could study the case without secondary of the light on the target object from background objects reflections in the scene, and show that such reflections have minimal effect on LRV estimation.
+Such analysis are not possible with real images.
 %% DHB: Update if we add additional analyses as per some of the comments above.

### 2018-05-31 Draft5/draft5.tex
small edits

@@
 Down each column, the sphere's light reflectance value (LRV) varies, but the relative reflectance spectrum (i.e. its spectral shape) is held fixed.
-Across each row, the shape of the reflectance spectrum varies, but the LRV is held fixed.
+Across each row, the relative reflectance spectrum varies, but the LRV is held fixed.
 We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors. 
@@
 \section*{Methods} \label{Methods}
-\subsection{Overview}
-There are four key parts to our methods.
-First, we generate a labeled set of training images.
-Second, we use a model of the early visual system to compute the responses of the cone photoreceptor mosaic to the labeled images.
-Third, we apply AMA to the cone responses, as well as to a contrast normalized version of the cone responses, to learn task-optimal receptive fields (RFs).
-Fourth, we evaluate how well the responses of the RFs may be decoded to achieve luminance constancy.
-
 % Figure 2
@@
 %% DHB: Maybe also say that the illumination scaling is much smaller than the range used in the study, so that it is possible to see it with common scaling.
+
+\subsection{Overview}
+There are four key parts to our methods.
+First, we generate a labeled set of training images.
+Second, we use a model of the early visual system to compute the responses of the cone photoreceptor mosaic to the labeled images.
+Third, we apply AMA to the cone responses, as well as to a contrast normalized version of the cone responses, to learn task-optimal receptive fields (RFs).
+Fourth, we evaluate how well the responses of the RFs may be decoded to achieve luminance constancy.
 
@@
 
-% Figure 4
-\begin{figure}
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \caption{Target position}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.pdf}
-        \label{fig:targetPositionVariation}
-    \end{subfigure}
-    ~
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \caption{Target size/Orientation}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
-        \label{fig:targetSizeOrientation}
-    \end{subfigure}
-~
-\centering
-	\begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \caption{Target spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.pdf}
-        \label{fig:targetVariation}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \caption{Illumination spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.pdf}
-        \label{fig:illuminationVariation}
-    \end{subfigure}
-          ~  
-    \begin{subfigure}[b]{0.18 \textwidth}
-    \centering
-        \caption{Background spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.pdf}
-        \label{fig:backGroundVariation}
-    \end{subfigure}
-
-    \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e).
-Our rendering package provides control over the properties illustrated by the columns of the figure.
-(a) Variation in inserted object positions.
-(b) Variation in object pose.
-(c) Variation in the surface reflectance of the target object.
-(d) Variation in the spectral power distributions of the light sources.
-(e) Variation in surface reflectance of the background objects.
-All panels in the figure have a common scale factor and tone mapping.
-\label{fig:VWCCTransformations}}
-\end{figure}
-
 In the present work, we used our package to generate datasets of naturalistic scenes and corresponding images.
@@
 
-% Figure 5: Conditions Studied
+% Figure 4
 \begin{figure}
+	\begin{subfigure}{0.18 \textwidth}
     \centering
-	\begin{subfigure}[b]{0.33 \textwidth}
-		\caption{Condition 1}
-%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
-		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
- 		\label{fig:backgroundVarying}
+        \caption{Target position}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.pdf}
+        \label{fig:targetPositionVariation}
     \end{subfigure}
-	\begin{subfigure}[b]{0.33 \textwidth}
-        \caption{Condition 2}	
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
-        \label{fig:targetIlluminantVarying}
+    ~
+	\begin{subfigure}{0.18 \textwidth}
+    \centering
+        \caption{Target size/Orientation}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
+        \label{fig:targetSizeOrientation}
     \end{subfigure}
-	\begin{subfigure}[b]{0.33 \textwidth}
-	\caption{Condition 3}	
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
-        \label{fig:allSpectraVarying}
+~
+\centering
+	\begin{subfigure}{0.18 \textwidth}
+    \centering
+        \caption{Target spectra}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.pdf}
+        \label{fig:targetVariation}
     \end{subfigure}
-    \caption{{\bf Dataset Conditions 1-3:} sRGB renderings of illustrative images from the datasets for Conditions 1, 2, and 3.
-Five images are shown for each light reflectance value (LRV).
-We studied three types of spectral variations.
-(a) Condition 1: variable target object relative reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
-(b) Condition 2: variable target object relative reflectance spectrum, variable light source spectra, fixed background object spectra.
-(c) Condition 3: variable target object relative reflectance spectrum, variable light source spectra, variable background object spectra.
-The spheres in each row of each panel have the same LRV, while the spheres in each column of each panel have the same relative surface reflectance.
-Across panels a-c, spheres in corresponding locations have the same surface reflectance.
-In all three panels, the overall light source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
-This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for display in publication.
-The sRGB values for all three subplots were normalized using a common scale factor prior to gamma correction.}
-\label{fig:studiedCases}
+    ~
+    \begin{subfigure}{0.18 \textwidth}
+    \centering
+        \caption{Illumination spectra}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.pdf}
+        \label{fig:illuminationVariation}
+    \end{subfigure}
+          ~  
+    \begin{subfigure}{0.18 \textwidth}
+    \centering
+        \caption{Background spectra}
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.pdf}
+        \label{fig:backGroundVariation}
+    \end{subfigure}
+
+    \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e).
+Our rendering package provides control over the properties illustrated by the columns of the figure.
+(a) Variation in inserted object positions.
+(b) Variation in object pose.
+(c) Variation in the surface reflectance of the target object.
+(d) Variation in the spectral power distributions of the light sources.
+(e) Variation in surface reflectance of the background objects.
+All panels in the figure have a common scale factor and tone mapping.
+\label{fig:VWCCTransformations}}
 \end{figure}
@@
 Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
+
+% Figure 5: Conditions Studied
+\begin{figure}
+\centering
+	\begin{subfigure}{0.33 \textwidth}
+		\caption{Condition 1}
+%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
+		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
+ 		\label{fig:backgroundVarying}
+	\end{subfigure}
+	\begin{subfigure}{0.33 \textwidth}
+        \caption{Condition 2}	
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
+        \label{fig:targetIlluminantVarying}
+    \end{subfigure}
+	\begin{subfigure}{0.33 \textwidth}
+	\caption{Condition 3}	
+        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
+        \label{fig:allSpectraVarying}
+    \end{subfigure}    
+    \caption{{\bf Conditions 1-3:} sRGB renderings of illustrative images for the three types of spectral variations studied in this paper.
+(a) Condition 1: variable target object relative reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
+(b) Condition 2: variable target object relative reflectance spectrum, variable light source spectra, fixed background object spectra.
+(c) Condition 3: variable target object relative reflectance spectrum, variable light source spectra, variable background object spectra.
+The spheres in each row of each panel have the same LRV, while the spheres in each column of each panel have the same relative surface reflectance.
+Across panels a-c, spheres in corresponding locations have the same surface reflectance.
+In all three panels, the overall light source spectra scale factors (see \nameref{Methods}) were drawn from a uniform distribution on the range [0.5, 1.5].
+This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for display in publication.
+The sRGB values for all three subplots were tone mapped and normalized using a common scale factor prior to gamma correction.}
+\label{fig:studiedCases}
+\end{figure}
+
 \subsubsection{Illumination spectra}
+To generate illumination spectra, we first developed a statistical model of the Granada daylight measurements (\citeNP{hernandez2001color}; \href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) and then sampled randomly from the model (see appendix).
+To match the wavelength spacing we use in rendering, we resampled the wavelength spacing of the Granada spectra to
+to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
+
 % Figure 6
@@
 \end{figure}
-
-To generate illumination spectra, we first developed a statistical model of the Granada daylight measurements (\citeNP{hernandez2001color}; \href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) and then sampled randomly from the model (see appendix).
-To match the wavelength spacing we use in rendering, we resampled the wavelength spacing of the Granada spectra to
-to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
-
-The overall intensity of the Granada spectra spans approximately three orders of magnitude.
-Figure~\ref{fig:granadaData} plots the measurements in normalized form to make apparent the variation in the relative spectra.
-To normalize the spectra, we divided each spectrum by its mean power.
 
@@
 We focussed our analysis on image regions local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
-In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle (REFS).
-%% VS: Needed a reference from Johannes.
-The local analysis is thus motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally (REFS).
-%% DHB: Johannes to provide his favorite citation or two.  Some review.
+In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}.
+The local analysis is thus motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
 
@@
 Thus, AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
-We used the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and means squared cost function (corresponding to mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
+We used the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and mean squared error cost function (corresponding to mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
 Poisson-like noise with a fano factor of 1.3).
-Both, the Kullback-Leibler divergence cost function and mean squared cost function gave similar results.
+Both, the Kullback-Leibler divergence cost function and mean squared error cost function gave similar results.
 The results in this work are for the Kullback-Leibler divergence cost function (see below).
@@
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
-Here we again used both Kullback-Leibler divergence cost function and mean square cost function, so that the optimal estimator is the maximum a posteriori estimate and the mean estimate respectively.
-The results in both cases were comparable.
-We present the results for the Kullback-Leibler divergence cost function case as the estimates obtained by the mean squared cost function have a bias near the lower and the upper limits of the LRV values used in our simulations.
+Here we again used both Kullback-Leibler divergence cost function and mean square error cost function, so that the optimal estimator is the maximum a posteriori estimate and the mean estimate, respectively.
+The performance (relative error) in both cases were comparable, but the results obtained using the mean square error cost function had a bias near the lower and the upper limits of the LRV values used in our simulations.
 The bias results because the LRV values are bounded in the range [0.2, 0.6] in estimating the posterior.
+For this reason, we present the results for the Kullback-Leibler divergence cost function.
 
@@
 %% DHB: Wouldn't it make more sense to use MSE and posterior mean for both learning and decoding, since we are reporting relative RMSE as our performance measure?
-%% VS: The results are similar for both cost function. MSE estimates are biased at the ends.
 
 \subsubsection*{Baseline methods}
-
 To provide baselines for evaluation of the estimation method described above, we used linear regression.
@@
 %% DHB: Check rewrite of last two sentences: OK?
-%% VS to add REF to last sentence above.
 
@@
 %% DHB: We need to write something interpretive about the RF structure shown in panel c.
-
+%% VS: added ->
 Figure~\ref{fig:case3RFs} shows the first two receptive fields learned for Condition 3.
@@
 
-%% VS added ->
+%% DHB; We were going to vary the number of secondary reflections modeled in the rendering for one of the conditions, to
+% separate the two possible sources of influence of the background surfaces.
+
+%% VS: added ->
 Our software allows us to compare the effect of background surface reflectances on target object LRV with and without secondary reflections from background objects. 
@@
 This shows that the primary source of the estimation error is due to the variability in the contrast estimation due to finite number of samples in the background and not due to secondary reflections.
-
-%% DHB; We were going to vary the number of secondary reflections modeled in the rendering for one of the conditions, to
-% separate the two possible sources of influence of the background surfaces.
 
@@
 We believe this basic approach can be extended to include parametric control over the amount of variation of different factors as well as to include variation in additional factors (see below).
+% % JDB: I don't understand what the the concluding sentence above is saying.
+%% DHB: Update if we add additional analyses as per some of the comments above.
 %% VS added ->
@@
 Such analysis are not possible with real images.
-%% DHB: Update if we add additional analyses as per some of the comments above.
-% % JDB: I don't understand what the the concluding sentence above is saying.
 
@@
 % JDB: Vet change to opening sentence w. vijay and david.
-
 It is natural to begin with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem.

### 2018-05-31 Draft5/draft5.tex
Today’s edits

@@
 We show that a decoding scheme that compares the light from the target and the surround can recover target object LRV to within about 13\% RMSE.
-%% DHB, VS: Maybe try to add a sentence saying why it is important.
-}
+Our work provides a framework for evaluating how different sources of scene variability limit performance on luminance constancy.}
 
@@
  \end{figure}
-%% DHB: Need to decide and then change with search through document: "relative reflectance spectrum" or "shape of reflectance spectrum".
-% I prefer relative, because "shape" in a vision paper generally refers to object shape.
-% And we found at least one instance where trying to use "shape" led to an awkward construction.
 
@@
 \label{fig:baseScenes}. \end{figure}
-%% DHB: Let's get the scaling and tone mapping used for these under control, so we know what it is.
-%% DHB: Maybe also say that the illumination scaling is much smaller than the range used in the study, so that it is possible to see it with common scaling.
 
@@
 (e) Variation in surface reflectance of the background objects.
-All panels in the figure have a common scale factor and tone mapping.
+All panels in this figure are rendered with a common scale factor and tone mapping.
 \label{fig:VWCCTransformations}}
@@
 The mean and covariance matrix of the Gaussian match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
-To generate a random shape of the illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
+To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
 Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
@@
 The demosaicing and normalization do not alter the information in the cone excitation images.
-% JDB: paragraph seems disjoint. Talk to David and Vijay.
-% DHB and VS: We think it is fine but are leaving the comment so we can call remember to discuss.
 
@@
 When provided with a labeled training set, a receptive field response model, a decoder that uses these responses to estimate the stimulus label, and a cost function, AMA returns a set of N linear receptive fields, where N is a parameter of the procedure.
-These receptive fields are chosen so that decoding their responses leads to minimum-expected-cost estimation, relative to any other choice of N linear receptive fields.
-This is possible because given a training set together with a set of N linear receptive fields and an explicit cost function, it is possible to determine the minimum-expected-cost estimator that maps the receptive field responses to the stimulus labels, on the assumption that all images in the training set are equally likely.
+These receptive fields are chosen so that decoding their responses leads to minimum expected-cost estimation, relative to any other choice of N linear receptive fields.
+This is possible because given a training set together with a set of N linear receptive fields and an explicit cost function, it is possible to determine the minimum expected-cost estimator that maps receptive field responses to the stimulus labels, on the assumption that all images in the training set are equally likely.
 Moreover, the corresponding expected estimation cost may be explicitly computed.
 Thus, AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
-We used the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and mean squared error cost function (corresponding to mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
+For each condition, we learned the filters with a training set consisting of 90\% of the images.
+
+In our implementation of AMA, we explored both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
 Poisson-like noise with a fano factor of 1.3).
-Both, the Kullback-Leibler divergence cost function and mean squared error cost function gave similar results.
-The results in this work are for the Kullback-Leibler divergence cost function (see below).
+Training with both cost functions yielded estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
+We chose this cost function because the estimates it yields at the edges of the stimulus range are less biased than those obtained with the mean squared error cost function.
+
 Details of how AMA learns filters and how the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
-For each condition, we learned the filters with a training set consisting of 90\% of the images.
 
@@
 
-Once the optimal receptive fields have been learned, we need to develop a general decoder that can be applied to arbitrary test stimuli.
+Once the optimal receptive fields have been learned, we need to develop a general decoder that can be applied to arbitrary test images.
 A general decoder is necessary because the decoder used to learn the receptive fields requires the response mean and response variance of the filters to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
-To proceed, first we use the AMA optimal receptive fields and the training dataset to find the conditional distributions of the receptive field responses, conditioned on the labelled target object LRVs.
+To proceed, first we use the AMA optimal receptive fields and the training dataset to find the conditional distributions of the receptive field responses, where the conditioning is on the labelled target object LRVs.
 Then, we approximate these with multivariate Gaussian distributions.
@@
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
-Here we again used both Kullback-Leibler divergence cost function and mean square error cost function, so that the optimal estimator is the maximum a posteriori estimate and the mean estimate, respectively.
-The performance (relative error) in both cases were comparable, but the results obtained using the mean square error cost function had a bias near the lower and the upper limits of the LRV values used in our simulations.
-The bias results because the LRV values are bounded in the range [0.2, 0.6] in estimating the posterior.
-For this reason, we present the results for the Kullback-Leibler divergence cost function.
+Here we again used the Kullback-Leibler divergence cost function for the result we report.
 
@@
 Estimation performance was evaluated using a test set consisting of the 10\% of images that were not in the training set.
-For our primary results, estimation was based on 6 receptive fields.
-%% JDB: I thought we were using a squared error cost function. See above?
-%% DHB: Wouldn't it make more sense to use MSE and posterior mean for both learning and decoding, since we are reporting relative RMSE as our performance measure?
+For our primary results, estimation was based on 6 learned receptive fields.
 
@@
 \end{figure}
+%% DHB, VS: In the new figure, RF1 is useless and RF2 is good.  Not the way we thought the ordering goes.  What's up?
 
@@
 
-The results in Figure {fig:Condition1} were obtained for one particular draw from our statistical model of illumination.
+The results in Figure~\ref{fig:Condition1} were obtained for one particular draw from our statistical model of illumination.
 We verified that performance remained excellent for other draws.
+% VS to try a few more cases to make sure.
 
 %% DHB, VS: Maybe the above sentence is all we really need, and can delete what's below? Vijay's analysis did not actually use illuminants drawn
-% from the distribution, though.  Clarify?  Or actually do that?
+% from the distribution, though.
+%
+%% Let's just run a version Condition 1 for some other draws of illumination.
 %
@@
 
-Recall that there are two qualitatively distinct factors contributing to the variation in illumination spectra: changes in overall intensity, and changes in the shape of the spectral power distribution.
+Recall that there are two qualitatively distinct factors contributing to the variation in illumination spectra: changes in overall intensity, and changes in the relative spectral power distribution. 
 To separate the effect of these two factors, we trained and evaluated AMA on the contrast normalized cone excitations. 
@@
 This effect is shown the right panel of Figure~\ref{fig:RMSEvsRF}, which also illustrates the effect of training set size on estimation performance. 
-%% DHB: Check rewrite of last two sentences: OK?
+%% DHB: Johannes, please check rewrite of last two sentences: OK?
 
@@
 
-%% DHB: We need to write something interpretive about the RF structure shown in panel c.
-%% VS: added ->
+Our software allows us to compare the effect of background surface reflectances on target object LRV with and without secondary reflections from background objects. 
+Our analysis shows that the secondary reflections have minimal effect on LRV estimates.
+The estimates without secondary reflections are comparable to that with reflections.
+This shows that the primary source of the estimation error is due to the variability in the normalized contrast of the target, due to the 
+finite number of samples in the background.
+
 Figure~\ref{fig:case3RFs} shows the first two receptive fields learned for Condition 3.
-Similar to Condition 1, the L and M cone excitations receive large weights, while the S cone excitations are largely ignored. 
+Similar to the receptive fields for Condition 1, the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
 Additionally, the cone excitations at the target have opposite sign compared to background object locations.
@@
 contribution.
-Additionally, for this condition, the cone contrast needs to be compared across the target and background regions. 
-A center-surround receptive field facilitates such comparison.
-However, one should not interpret too much into the features that arise due to the specific geometry of the scene.
-
-%% DHB; We were going to vary the number of secondary reflections modeled in the rendering for one of the conditions, to
-% separate the two possible sources of influence of the background surfaces.
-
-%% VS: added ->
-Our software allows us to compare the effect of background surface reflectances on target object LRV with and without secondary reflections from background objects. 
-Our analysis shows that the secondary reflections have minimal effect on LRV estimates.
-The estimates without secondary reflections are comparable to that with reflections.
-This shows that the primary source of the estimation error is due to the variability in the contrast estimation due to finite number of samples in the background and not due to secondary reflections.
+Additionally, for this condition, the optimal receptive fields compare normalized cone contrast between the target and background regions. 
+This comparison may serve to reduce the effect of light scattered from the background onto the target. 
+The specific geometry of the receptive fields should not be taken to be a general feature, as it arises as a consequence
+of the single scene geometry we studied.
+%% DHB: Let's look at RFs in case where secondary reflections are turned off, to see if what I drafted in this paragraph
+% about RF structure is plausible.
 
@@
 We used the labeled datasets to learn estimators for the target object LRV.
-Across scenes, we varied the LRV of the target object, the shape of the reflectance spectrum of the target object, 
+Across scenes, we varied the LRV of the target object, the relative reflectance spectrum of the target object, 
 the spectral power distributions of the light sources, and the reflectance spectra of the background objects in the scene.
@@
 Figure~\ref{fig:barGraphs} summarizes our main findings, by showing the overall relative root mean squared estimation error (relative RMSE; see Figure~\ref{fig:barGraphs} caption) for each condition. 
-In Condition 1, where only the shape of the reflectance spectrum of the target object varies, 
+In Condition 1, where only the relative reflectance spectrum of the target object varies, 
 luminance constancy is an easy computational problem,
@@
 In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.
-% JDB: Are we going to add in a constancy index, as we discussed doing a few meetings ago?
 Introducing variation in the surface reflectance spectra of the background objects makes 
@@
 reliably light reflected from those objects can be used as a cue to estimate the spectral power distribution of the illuminant.
-% JDB: Original concluding sentence very hard to read. I split into two and tried to simplify. Still not completely happy with it...
+% JDB: Are we going to add in a constancy index, as we discussed doing a few meetings ago?
+% DHB: I think it is time to submit this paper.
 
 \subsection{Images of Virtual vs. Real Scenes}
-% JDB: Completely rearranged opening of section. Previous version had a choppy opening paragraph that did not flow into second paragraph. Please see what you think.
 As noted in the introduction, supervised learning requires large labeled datasets.
@@
 This flexibility allows the study of individual scene factors as well as their combined effects.
-Here, we exploited this flexibility to quantify how variation in the shape of the reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation.
-We believe this basic approach can be extended to include parametric control over the amount of variation of different factors as well as to include variation in additional factors (see below).
-% % JDB: I don't understand what the the concluding sentence above is saying.
-%% DHB: Update if we add additional analyses as per some of the comments above.
-%% VS added ->
-For example, we could study the case without secondary of the light on the target object from background objects reflections in the scene, and show that such reflections have minimal effect on LRV estimation.
-Such analysis are not possible with real images.
+Here, we exploited this flexibility to quantify how variation in the relative reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation.
+We also exploited our use of rendered images to explore how the presence or absence of secondary reflections from background objects affected estimation
+of target object LRV.
+This type of question cannot be addressed using real images.
+The basic approach we use here can be extended to include parametric control over the amount of variation of different factors.
+For example, we could systematically vary the variances of the distribution over the weights that control the relative spectrum
+of the illumination.
 
@@
 Indeed, carefully constructed graphics images are now quite difficult to differentiate from real images.
-%% DHB: Might be able to reference Farid's recent book on this point.
 
@@
 Although we believe these datasets provide reasonable approximations of the statistical variation in reflectance and illumination spectra, they can be extended and improved.
-For example, the surface reflectance datasets capture constraints on naturally occurring reflectance functions, but the surfaces in the datasets were not sampled to reflect the relative frequency of different reflectance spectra in natural viewing.
+For example, the surface reflectance datasets capture regularities in naturally occurring reflectance functions, but the surfaces in the datasets were not sampled to reflect the relative frequency of different reflectance spectra in natural viewing.
 In addition, the dataset of illuminations does not include the artificial illuminations that we now live much of our lives under.
-% JDB: What are "constraints on naturally occurring reflectance functions"?
-Future work with virtual image datasets will benefit from targeted efforts to characterize the natural statistics of the scene components that are varied.
-% JDB: I think i understand what the previous sentence is trying to say, but i'm not sure. We should discuss.
-Under the assumption that combination of different scene factors (e.g.
-surface reflectances and illuminations) is independent, the virtual image approach modularizes the study of variation in natural scenes.
-% JDB: Confusing concluding sentence. Not sure the point will get across.
+Future work with virtual image datasets will benefit from targeted efforts to characterize additional features of the natural statistics of the scene components that are varied.
 
@@
 In the work presented here, we studied computational luminance constancy in virtual scenes with naturalistic spectral variation in light sources and in surface reflectance functions. 
-% JDB: Vet change to opening sentence w. vijay and david.
 It is natural to begin with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem.
@@
 A further advance would be to develop methods for learning receptive fields that are optimal for multivariate estimation problems. 
-% JDB: The right student could engage in this programming project.
 With such methods one could directly estimate three-dimensional color descriptors.

### 2018-06-03 Draft5/draft5.tex
updated figures

@@
 The standard deviations are too small to be visible.
-Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.8\% for linear regression and 1.3\%  for AMA based estimation.
+Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.7\% for linear regression and 1.1\%  for AMA based estimation.
 (b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields.
@@
     \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
-The relative RMSE is high (41.4\% for linear regression and 31.3\% for AMA based estimation).
+The relative RMSE is high (41.4\% for linear regression and 23.3\% for AMA based estimation).
 (b) Cone excitations projected onto AMA receptive fields.
@@
 (b) Same data as in a, but plotted as a function of number of receptive fields.
-Performance converges around 6 RFs.}
+Performance converges around 3 RFs.}
  \label{fig:RMSEvsRF}

### 2018-06-04 Draft5/draft5.tex
fixed some error numbers and margin widths

@@
     \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
-The relative RMSE is high (41.4\% for linear regression and 23.3\% for AMA based estimation).
+The relative RMSE is high (41.4\% for linear regression and 26.1\% for AMA based estimation).
 (b) Cone excitations projected onto AMA receptive fields.
 (c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
-The relative RMSE of estimation is 9.3\% for linear regression and 1.2\% for AMA based estimator.
+The relative RMSE of estimation is 9.3\% for linear regression and 1.6\% for AMA based estimator.
 (d) The contrast normalized cone excitations projected along the first two AMA receptive fields.
@@
     \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
-The relative RMSE is 22.9\%  for linear regression and 13.0\% for AMA.
+The relative RMSE is 24.0\%  for linear regression and 13.1\% for AMA.
 (b) Contrast normalized cone excitations for the training set projected onto the first two AMA receptive fields.

### 2018-06-08 Draft5/draft5.tex
small edits

@@
 The LRV values were equally spaced between 0.2 and 0.6.
-For each LRV value, a different target surface reflectance spectra for each of the 100 scenes.
+For each LRV value, we generated a different target surface reflectance spectra for each of the 100 scenes.
 Thus, for each target object LRV value, the relative reflectance spectrum of the target object could differ.
@@
 To match the wavelength spacing we use in rendering, we resampled the wavelength spacing of the Granada spectra to
-to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
+31 evenly-spaced wavelengths between 400 nm and 700 nm.
 
@@
 Poisson-like noise with a fano factor of 1.3).
-Training with both cost functions yielded estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
+Training with both cost functions yielded similar estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
 We chose this cost function because the estimates it yields at the edges of the stimulus range are less biased than those obtained with the mean squared error cost function.
@@
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
-Here we again used the Kullback-Leibler divergence cost function for the result we report.
+Here we again used the Kullback-Leibler divergence cost function for the results we report.
 
@@
 Both methods are trained and tested on different image sets.
-As expected, the LRV estimates obtained from decoding the AMA receptive field responses the LRV estimates from linear regression are essentially perfect.
+As expected, the LRV estimates obtained from decoding the AMA receptive field responses as well as the LRV estimates from linear regression are essentially perfect.
 

### 2018-06-08 Draft5/draft5.tex
small edits

@@
 This condition models the sources of real-world spectral variation that is most relevant for the computational problem of luminance constancy.
-We again trained and evaluated AMA for labeled images patches, using the contrast normalized cone excitations.
+We again trained and evaluated AMA for labeled image patches, using the contrast normalized cone excitations.
 The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions (Figure~\ref{fig:case3Estimates}).
@@
 That is, inclusion of more receptive fields will in general reduce the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
-This effect is shown the right panel of Figure~\ref{fig:RMSEvsRF}, which also illustrates the effect of training set size on estimation performance. 
+This effect is shown in the right panel of Figure~\ref{fig:RMSEvsRF}, which also illustrates the effect of training set size on estimation performance. 
 %% DHB: Johannes, please check rewrite of last two sentences: OK?
@@
 Relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
-The mean is taken over all stimuli in the test set.}
+The mean is taken over all stimuli in the test set.
+The dotted line represents the relative RMSE for a naive method that estimates the LRV of each image as the mean LRV over the images in the set (LRV = 0.4).}
  \label{fig:barGraphs}

### 2018-06-12 Draft5/draft5.tex
small edits. Cover letter

@@
 
-\title{Luminance constancy under fixed geometry}
+\title{Luminance constancy in naturalistic scenes}
 %% Luminance constancy in naturalistic scenes
@@
  {}{cottaris@sas.upenn.edu}
-
  \author{Heasly}{Benjamin S.}
@@
 We used one fixed base scene and inserted a spherical target object of fixed shape and size into this scene.
-We generated three distinct datasets, which we refer to as Conditions 1-3 and describe below.
+We generated three distinct datasets, which we refer to as Conditions 1-3. These are describe below.
 Across these datasets the luminance constancy problem (i.e. estimating the target object LRV)
@@
 The LRV values were equally spaced between 0.2 and 0.6.
-For each LRV value, we generated a different target surface reflectance spectra for each of the 100 scenes.
+For each LRV value, we generated a different target surface reflectance spectrum for each scene.
 Thus, for each target object LRV value, the relative reflectance spectrum of the target object could differ.
@@
     \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e).
-Our rendering package provides control over the properties illustrated by the columns of the figure.
+Our rendering package provides control over these properties as illustrated by the columns of the figure.
 (a) Variation in inserted object positions.
@@
 Indeed, the estimates track the true LRV on average, as seen by the fact that the mean estimate (red line) lies along the positive diagonal.
-The increased estimation variability is indicated by the increased width of the shaded red region, relative to its width for the Condition 1 and 2 results.
+The increased estimation variability is indicated by the increased width of the shaded red region, relative to its width for the results of Condition 1 and 2.
 Performance of the baseline linear regression method (also evaluated using contrast normalized cone excitations) is worse than that of the AMA-based estimates.

### 2018-06-18 Draft5/draft5.tex
DB’s edits on main paper
Some comments added in main text, search on DHB

@@
 
-\title{Luminance constancy in naturalistic scenes}
+\title{Luminance Constancy Learned from Labeled Naturalistic Images}
 %% Luminance constancy in naturalistic scenes
@@
 \abstract{
-The human visual system supports stable percepts of object color even though the light that reflects off object surfaces varies significantly with context.
-To understand the computations that support invariant color perception, 
+The human visual system supports stable percepts of object color even though the light that reflects from object surfaces varies significantly with the scene illumination.
+To understand the computations that support stable color perception, 
 we study how the estimation of the light reflectance value of a target object (LRV; a measure of the light reflected from the object under a standard illuminant) depends on variation in key properties of naturalistic scenes.
-Specifically, we study how variation in target object reflectance, background object reflectance, and illumination spectra in a scene impact estimates of LRV. 
-To do this, we apply supervised statistical learning methods to the simulated excitations of human cone photoreceptors, obtained from labeled naturalistic images.
-The naturalistic images were obtained using computer graphics, where the scenes to be rendered were stochastically generated in conjunction with statistical models of natural spectral variation.
-We show that a decoding scheme that compares the light from the target and the surround can recover target object LRV to within about 13\% RMSE.
+Specifically, we study how variation in target object reflectance, illumination spectra, and the reflectance of background objects in a scene impact estimation of a target object's LRV. 
+To do this, we applied supervised statistical learning methods to the simulated excitations of human cone photoreceptors, obtained from labeled naturalistic images.
+The naturalistic images were rendered with computer graphics, with the underlying scene descriptions generated stochastically using statistical models
+of natural spectral variation.
+We show that a decoding scheme used learned linear filters to process a contrast representation of the cone excitations can recover target object LRV to within about 13\% RMSE.
 Our work provides a framework for evaluating how different sources of scene variability limit performance on luminance constancy.}
@@
 The computational challenge underlying object color perception is that the light reflected from an object depends not just on the object's surface reflectance, but also 
-on object-extrinsic factors such as the pose of the object, the illumination in the scene, and the position of the observer in the scene (Fig.~\ref{fig:introSchematic}).
+on object-extrinsic factors such as the scene illumination, the pose of the object, and the viewpoint of the observer in the scene (Fig.~\ref{fig:introSchematic}).
 To compute a perceptual representation of object color that is correlated with the object's physical surface reflectance, the visual system must account for these object-extrinsic factors.
@@
 Although human color constancy is not perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}.
-In this paper, we consider the computational problem of color constancy.
-Specifically, we ask how a visual system should process the light entering the eye that has reflected off objects to produce percepts well-correlated with object surface reflectance.
 
-Early work on computational color constancy considered a simplified case with multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
+Early work on computational color constancy considered a simplified imaging model where where scenes consisted of multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
 Subsequent work incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{D'ZmuraConstancy3, D'ZmuraIversonSinger,BrainardFreeman}.
-A key insight from this computational work is that stable color descriptors of a target object cannot be obtained solely from the light reflected from that target object.
-But it is possible to obtain such descriptors by jointly analyzing the light reflected from multiple objects in the scene.
-As a consequence, the performance of color constancy algorithms will be affected both by variation in the illumination and in the surface reflectance of other objects in the scene and should therefore be evaluated with respect to both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}.
-There has also been work that generalizes to more complex viewing geometries \cite{funt1988color, barron2012color}.
+A key insight from these computational studies is that stable color descriptors of a target object cannot be obtained solely from the light reflected from that target object.
+It is possible, however, to obtain such descriptors by jointly analyzing the light reflected from multiple objects in the scene.
+As a consequence, the performance of color constancy algorithms will be affected both by variation in the illumination and in the surface reflectance of other objects in the scene,
+and thus algorithms need to be evaluated with respect to variation in both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}. 
+There has also been computational work that generalizes to more complex viewing geometries \cite{funt1988color, barron2012color}.
 
@@
     \label{introFigure}
-    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the illumination of the object. 
+    \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the scene illumination. 
 The reflected light also depends on geometric factors, such as the object's shape, pose, and position. 
-The human visual system accounts for variations in the reflected light due to object-extrinsic factors and produces a percept of object color that is relatively stable across such variations, an ability called color constancy.
+The human visual system accounts for variations in reflected light due to object-extrinsic factors and produces a percept of object color that is relatively stable across such variations. 
 (b) Images of a sphere under a fixed illuminant.  
-Down each column, the sphere's light reflectance value (LRV) varies, but the relative reflectance spectrum (i.e. its spectral shape) is held fixed.
+Down each column, the sphere's light reflectance value (LRV) varies, but its relative reflectance spectrum (i.e. its spectral shape) is held fixed.
 Across each row, the relative reflectance spectrum varies, but the LRV is held fixed.
@@
 For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
-It has been used to develop ideal observers for defocus blur, binocular disparity, and retinal motion estimation with natural stimuli that provide excellent predictions of neural and human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
-In this paper, we apply AMA to a special case of computational color constancy.
+It has been used to develop ideal observers for defocus blur, binocular disparity, and retinal motion estimation with natural stimuli.
+These ideal observers provide excellent predictions of human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
 
-Supervised learning requires large labeled data sets.
-Such data sets are not readily available for the study of color constancy.
-Although there are datasets of calibrated color images, these datasets do not provide ground truth information about surface reflectance and illumination at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
+Supervised learning requires large labeled datasets.
+Such datasets are not readily available for the study of color constancy.
+Although there are datasets of calibrated color images, these do not provide ground truth information about surface reflectance and illumination at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
 There are a few databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}), but these are not large enough to drive supervised learning.
@@
 This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants.
-We use this approach to tackle the specific problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
+We tackle the specific problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
 
@@
 Sometimes LRVs are expressed as a percentage.
-Here we express LRVs as proportion, so that they take on values between 0 and 1.
+Here we express LRVs as proportions, so that they take on values between 0 and 1.
 
@@
     \end{subfigure}
-    \caption{{\bf Base scenes.} Each subplot shows a rendering of one base scene without additional inserted objects.
-The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from statistical models of naturally occurring spectra (see text).
-The images in this figure have been scaled and tone mapped individually for illustrative purposes.}
+    \caption{{\bf Base scenes.} Each image shows a rendering of one base scene without additional inserted objects.
+The reflectance spectra of the distinct surfaces and the spectral power distributions of the light sources in each scene have been assigned randomly from statistical models of naturally occurring spectra.
+The images have been scaled and tone mapped individually for illustrative purposes.}
 \label{fig:baseScenes}. \end{figure}
@@
 These include the surface reflectance, texture, material and geometry of the objects, 
-the spectral power distribution function of the illuminants, and the position of the observer.
+the spectral power distribution of the illuminants, and the position of the observer.
 We have developed a rendering package 
@@
 that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
-The package builds on our RenderToolblox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
+The package builds on our RenderToolbox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
 and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org}, 
 \citeNP{jakob2015mitsuba}) to produce physically-accurate images from the scene models.
-Because each image is rendered from a known scene model, each image pixel can be labeled with 
-the surface reflectance of the corresponding scene object.
-By incorporating statistical models of the variation of object surface reflectance and daylight illumination, 
-the pipeline allows us to produce large labeled sets of images that capture key aspects of the task-relevant 
+Because the images are rendered from known scene models, each image pixel can be labeled with 
+the surface reflectance of the corresponding object.
+By incorporating statistical models of object surface reflectance and daylight illumination, 
+the package allows us to produce large labeled sets of images that capture key aspects of the task-relevant 
 statistical structure of natural scenes.
@@
 \caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
-Each image (a-e) shows a different object inserted into a user specified location in the library base scene.
-The rendering viewpoint was set so that the object was at the center of the rendered image.
-The full rendered image has been cropped here so that the inserted object is easily visible.}\label{fig:libraryWithTarget}
+Each image shows a different object inserted into the Library base scene.
+The rendering viewpoint was set so that the object was at the center of the images.
+The full rendered images have been croppedso that the inserted objects are easily visible.}\label{fig:libraryWithTarget}
 \end{figure}
@@
 Base scenes specify an arrangement of objects and light sources.
-Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and additional light sources.
+Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and by the insertion of additional light sources.
 Once the position, size and pose of the inserted objects and light sources have been set, 
@@
 In the present work, we used our package to generate datasets of naturalistic scenes and corresponding images.
-We used one fixed base scene and inserted a spherical target object of fixed shape and size into this scene.
-We generated three distinct datasets, which we refer to as Conditions 1-3. These are describe below.
+We used one fixed base scene and inserted a spherical target object of fixed size into this scene.
+We generated three distinct datasets, which we refer to as Conditions 1-3 (Fig.~\ref{fig:studiedCases}). These are described below.
 Across these datasets the luminance constancy problem (i.e. estimating the target object LRV)
-becomes progressively more difficult (Fig.~\ref{fig:studiedCases}).
+becomes progressively more difficult .
 
@@
 In Condition 1, the relative reflectance spectrum of the target object was the only source of scene variation other than the target object LRV.
-The reflectance spectra of the background objects, and the spectral power distributions of the light sources were kept fixed.
-In Condition 2, the spectral power distribution of the light sources varied in addition to the relative reflectance spectrum of the target object,
-Finally, in Condition 3 three distinct scene factors--target object relative reflectance spectrum, reflectance spectra of the background objects, and
-spectral power distribution of the light sources--varied in addition to the target object LRV.
-Conditions 1 and 2 had datasets consisting of 1000 scenes and images, 100 for each of 10 target object LRV values. 
-Condition 3 had a dataset consisting of 3000 scenes and images, 300 each for the 10 target LRV values.
+The reflectance spectra of the background objects and the spectral power distribution of the light sources were held fixed.
+In Condition 2, the spectral power distribution of the light sources varied in addition to the relative reflectance spectrum of the target object.
+Finally, in Condition 3 three distinct scene factors--target object relative reflectance spectrum, spectral power distribution of the light sources, and reflectance spectra of the background objects
+--varied in addition to the target object LRV.
+The datasets for Conditions 1 and 2 consiseted of 1000 scenes and images, 100 for each of 10 target object LRV values. 
+The dataset for Condition 3 consisted of 3000 scenes and images, 300 each for the 10 target LRV values.
 The LRV values were equally spaced between 0.2 and 0.6.
-For each LRV value, we generated a different target surface reflectance spectrum for each scene.
-Thus, for each target object LRV value, the relative reflectance spectrum of the target object could differ.
-
+For each LRV value, we generated a different relative target surface reflectance for each scene. 
 % Figure 4
@@
     \centering
-        \caption{Target size/Orientation}
+        \caption{Target size/pose}
         \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
@@
 (a) Variation in inserted object positions.
-(b) Variation in object pose.
+(b) Variation in object size and pose.
 (c) Variation in the surface reflectance of the target object.
@@
 (e) Variation in surface reflectance of the background objects.
-All panels in this figure are rendered with a common scale factor and tone mapping.
+All images in this figure are rendered with common scaling and tone mapping.
 \label{fig:VWCCTransformations}}
@@
 
-For the primary results, we used the ``{\it Library}'' base scene and a spherical target object.
-The library base scene contains 2 area lights. 
+We used the Library base scene and a spherical target object.
+The Library base scene contains 2 area lights. 
 We inserted one additional spherical light source into the scene.
 The position and size of the inserted object, inserted light source and viewpoint were held fixed across all 
-scenes in the database. The geometry is shown in Figure~\ref{fig:3DScene}.
-Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra, as described below.
+scenes in the datasets. The geometry is shown in Figure~\ref{fig:3DScene} below.
+Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra.
 Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
@@
     \end{subfigure}    
-    \caption{{\bf Conditions 1-3:} sRGB renderings of illustrative images for the three types of spectral variations studied in this paper.
+    \caption{{\bf Conditions 1-3:} Illustrative images for the three types of spectral variations studied in this paper.
 (a) Condition 1: variable target object relative reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
@@
 (c) Condition 3: variable target object relative reflectance spectrum, variable light source spectra, variable background object spectra.
-The spheres in each row of each panel have the same LRV, while the spheres in each column of each panel have the same relative surface reflectance.
+The spheres in each row of each panel have the same LRV, while the spheres in each column of each panel have the same relative surface reflectance spectrum.
 Across panels a-c, spheres in corresponding locations have the same surface reflectance.
@@
 This is smaller than the variation we studied, but allows us to show the variation within the dynamic range available for display in publication.
-The sRGB values for all three subplots were tone mapped and normalized using a common scale factor prior to gamma correction.}
+All images in this figure are rendered with common scaling and tone mapping.}
 \label{fig:studiedCases}
@@
 \subsubsection{Illumination spectra}
-To generate illumination spectra, we first developed a statistical model of the Granada daylight measurements (\citeNP{hernandez2001color}; \href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) and then sampled randomly from the model (see appendix).
+To generate illumination spectra, we developed a statistical model of the Granada daylight measurements (\citeNP{hernandez2001color}; \href{http://colorimaginglab.ugr.es/pages/Data}{http://colorimaginglab.ugr.es/pages/Data}) and then sampled randomly from the model.
 To match the wavelength spacing we use in rendering, we resampled the wavelength spacing of the Granada spectra to
@@
 
-Our statistical model approximates the normalized Granada spectra using the first 6 principle components.
-The variation in the weights on these components is modeled with a 6-dimensional Gaussian.
+Our statistical model approximates normalized spectra from the Granda dataset using the first 6 principle components of the normalized measurements from that dataset.
+The variation in the weights on these components is then modeled with a 6-dimensional Gaussian.
 The mean and covariance matrix of the Gaussian match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
@@
 Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
+Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:xyDiagram} and ~\ref{fig:sRGBIlluminant}.
 Details of the statistical model for illumination are provided in the appendix.
-Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:xyDiagram} and ~\ref{fig:sRGBIlluminant}.
 
@@
 We chose the particular scale factor range so that the mean number of cone isomerizations from the target object ranged from approximately 100 to 100,000 for the 100 msec cone integration time we used (see below).
-This range corresponds approximately to that for natural viewing.
+This range corresponds approximately to that of natural daylight viewing.
 
@@
 (b) Sample spectra generated using the surface reflectance statistical model.
-(c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances and samples shown in b (red).
+(c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances (black) and the sample spectra shown in b (red).
 (d) sRGB renditions of the samples shown in b, rendered under the CIE D65 daylight.}
@@
 measurements to create a database containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data) (Figure~\ref{fig:reflectanceSpectra}).
-We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm (Figure~\ref{fig:reflectanceSpectra}).
+We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
+Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance draws obtained using the model. 
 Details of the statistical model for surface reflectance spectra are provided in the appendix.
-Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance draws obtained using the model.
 
-For generating the target object reflectance at a particular luminance, the generated reflectance spectrum was 
-scaled such that the LRV had the desired value (see appendix).
+To generate the target object reflectance at a particular LRV, the generated reflectance spectrum was 
+scaled such that its LRV had the desired value (see appendix).
 Figure \ref{fig:targetSwatches} shows color renderings of target reflectance spectra under CIE illuminant D65, for the evenly spaced LRV values we studied.
@@
 \subsection{Model of early visual system} \label{method:Isetbio}
-The light entering the eye is blurred by the optics of the eye.
-The resulting retinal image is sampled by a mosaic of cone photoreceptors.
-The excitations of these photoreceptors provide the information about the scene that is available to the neural visual system for further processing.
+Lght entering the eye is focussed and blurred by eye's optics to form the retinal image.
+This image is then sampled by a mosaic of cone photoreceptors.
+The excitations of these photoreceptors provide the information available to the neural visual system for further processing.
 Because we are interested in how well luminance constancy may be achieved by the human visual system, we simulated the cone excitations
@@
 We focussed our analysis on image regions local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
-In foveal primary visual cortex, receptive fields have a spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}.
-The local analysis is thus motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
+The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally.
+In primary visual cortex, foveal receptive fields have a spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}.
 
-We modeled a visual system limited by diffraction caused by a 3mm diameter pupil, optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, and spatial sampling by an interleaved mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
+We modeled a visual system by typical optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, and spatial sampling by an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
 The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
@@
 
-To put the computed cone excitations into a form for use in further processing, we demosaiced the excitations for each cone class using linear interpolation
+To put the computed cone excitations into a form for further analysis, we demosaiced the excitations for each cone class using linear interpolation
 to obtain a cone excitation image for each cone class.
@@
 normalized each cone excitation image by the summed (over wavelength) quantal efficiency of the corresponding cone class.
-The demosaicing and normalization do not alter the information in the cone excitation images.
+The demosaicing and normalization do not alter the available information, relative to that carried by the cone excitations themselves.
 
 To capture key properties of post-receptoral processing, such as contrast normalization \cite{heeger1992normalization,albrecht1991motion,carandini2012normalization}, 
-we processed the excitations as follows:
-To model contrast coding, we converted each cone excitation image to a corresponding cone contrast image.
+we processed the cone excitation images as follows:
+We first converted each cone excitation image to a corresponding cone contrast image.
 This was accomplished by computing the mean response over the three cone excitation images, and then subtracting off and dividing by this mean.
-To model contrast normalization, we divided the contrast images by the sum of squared contrasts taken over image pixels and cone classes.
+To model contrast normalization, we then divided the contrast images by the sum of squared contrasts taken over image pixels and cone classes.
 
@@
 
-Once the optimal receptive fields have been learned, we need to develop a general decoder that can be applied to arbitrary test images.
-A general decoder is necessary because the decoder used to learn the receptive fields requires the response mean and response variance of the filters to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
-To proceed, first we use the AMA optimal receptive fields and the training dataset to find the conditional distributions of the receptive field responses, where the conditioning is on the labelled target object LRVs.
+Once the AMA receptive fields have been learned, we need to develop a general decoder that can be applied to arbitrary test images.
+A separate decoder is necessary because the decoder used to learn the receptive fields depends on the response mean and response variance of the filters to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
+To proceed, first we use the AMA receptive fields and the training dataset to find the conditional distributions of the receptive field responses, where the conditioning is on the labelled target object LRVs.
 Then, we approximate these with multivariate Gaussian distributions.
-To estimate the LRV of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRV values given the filter responses.
+To estimate the LRV of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRV values, given the filter responses.
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
-Here we again used the Kullback-Leibler divergence cost function for the results we report.
+For the results we report, we again used the Kullback-Leibler divergence cost function.
 
 The Gaussian approximations for the posterior were estimated using the same training set that was used to learn the receptive fields.
-Estimation performance was evaluated using a test set consisting of the 10\% of images that were not in the training set.
+Estimation performance was evaluated on a test set consisting of the 10\% of images in the dataset that were not in the training set.
 For our primary results, estimation was based on 6 learned receptive fields.
@@
 First, we solved for the weights on the average L, M and S cone excitations corresponding to the target object that best predicted the target LRV values.
-We took the average cone responses from a $3 \times 3$ region at the center of the target object.
+We took the average cone responses from a $3 \times 3$ pixel region at the center of the target object.
 This baseline method disregards information carried by the image regions corresponding to the background objects.
-We also performed regression on the contrast normalized version of the cone responses.
+We also performed regression on the contrast normalized version of the cone excitation images.
 This second baseline method indirectly incorporates information carried in the image regions corresponding to the background objects,
@@
 The standard deviations are too small to be visible.
-Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.7\% for linear regression and 1.1\%  for AMA based estimation.
+Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.7\% for linear regression and 1.1\%  for AMA-based estimation.
 (b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields.
-Each cluster of responses represents the image patches associated with a particular LRV, which is coded by color.
-The response clusters are approximated by a multivariate Gaussians whose mean and covariance matrices are represented by the ellipses shown in the figure.
-(c) The first two AMA receptive fields learned using the cone excitations of stimuli in the training set.}
+Each cluster of responses represents the image patches associated with a particular LRV.
+The response clusters are approximated by a multivariate Gaussians whose means and covariances are represented by the ellipses shown in the figure.
+(c) The first two AMA receptive fields.}
 \label{fig:Condition1}
 \end{figure}
-%% DHB, VS: In the new figure, RF1 is useless and RF2 is good.  Not the way we thought the ordering goes.  What's up?
+%% DHB: "Linear Model" in panel a) should be "Regression".  Also in Figures 11 and 12.
+%% DHB: It is really hard to see the ellipses in b), even if I increase the mag in the PDF.  Can you make them more salient?
+%% DHB: Show first three RFs in (c) here and in Figure 12, I think.  Otherwise it is hard to understand why the ones in 12 change.
 
@@
 In Condition 1, only the LRV and the relative reflectance spectrum of the target object vary across scenes.
-We used accuracy maximization analysis (AMA) to learn a set of linear receptive fields that are optimal for estimating target LRV from the cone excitations to the image patches in this condition. 
-Decoding performance for the test set is shown in Figure~\ref{fig:case1Estimates}. 
+We used accuracy maximization analysis (AMA) to learn a set of linear receptive fields that are optimal for estimating target LRV from the cone excitations in this condition. 
+Decoding performance is shown in Figure~\ref{fig:case1Estimates}. 
 Figure~\ref{fig:case1Estimates} also shows the performance of the baseline linear regression method. 
-Both methods are trained and tested on different image sets.
-As expected, the LRV estimates obtained from decoding the AMA receptive field responses as well as the LRV estimates from linear regression are essentially perfect.
+Both methods are trained on 90\% of the images in the dataset and tested on the remaining 10\%.
+The LRV estimates obtained for both methods are essentially perfect.
 
 Figure~\ref{fig:case1RFResponse} shows the responses of the first two AMA receptive fields to all the image patches in the training set.
-Each individual point represents the receptive field responses to an individual image patch.
-Each point is color coded by the LRV corresponding to the target object in the patch.
-The responses segregate nearly completely according to the target LRV, which is the feature required to support the high level 
+Each individual point represents the receptive field responses to an individual image patch and
+is color coded by target object LRV.
+The responses segregate according to the target LRV, which supports the high level 
 of estimation performance shown in Figure~\ref{fig:case1Estimates}.
@@
 contribution.
+%% DHB: We need to come back to this paragraph after we finalize the RFs to be shown in Figure 10c and 12c,
+% because the third RF does have S cone contribution.
 
@@
 We verified that performance remained excellent for other draws.
-% VS to try a few more cases to make sure.
+%% VS to try a few more cases to make sure.
 
@@
     \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
-The relative RMSE is high (41.4\% for linear regression and 26.1\% for AMA based estimation).
+The relative RMSE is high (41.4\% for linear regression and 26.1\% for AMA-based estimation).
 (b) Cone excitations projected onto AMA receptive fields.
 (c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
-The relative RMSE of estimation is 9.3\% for linear regression and 1.6\% for AMA based estimator.
+The relative RMSE of estimation is 9.3\% for linear regression and 1.6\% for the AMA-based estimator.
 (d) The contrast normalized cone excitations projected along the first two AMA receptive fields.
 The receptive fields were learned using AMA and the contrast normalized cone excitations.
-For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is contrast normalized cone excitations than when the input is the raw cone excitations.}
+For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is the contrast normalized cone excitations than when the input is the raw cone excitations.}
 \label{fig:Condition2}
@@
 Condition 2 includes variation in the spectral power distribution of the light sources, in addition to the variation present in Condition 1. 
-This illumination variation makes the task more difficult because it causes additional variation in the cone excitations that is not due to target object LRV. 
+This illumination variation makes the task more difficult because it causes variation in the cone excitations that is not due to target object LRV. 
 We learned AMA receptive fields on the cone excitations to the images in this new condition, and again evaluated decoding performance (Fig.~\ref{fig:Condition2}(a,b)). 
@@
 value of the true LRV.
-For this case, linear regression is also very poor. Indeed, the linear regression estimates are essentially the same as would be obtained
+For this case, linear regression also does poorly. Indeed, the linear regression estimates are essentially the same as would be obtained
 by simply guessing the mean LRV of the training set (0.4).
@@
 Condition 3 introduces variation in the reflectance spectra of the background objects, in addition to the sources of variation in Conditions 1 and 2.
-This condition models the sources of real-world spectral variation that is most relevant for the computational problem of luminance constancy.
+This condition models the sources of real-world spectral variation that are most relevant for the computational problem of luminance constancy.
 We again trained and evaluated AMA for labeled image patches, using the contrast normalized cone excitations.
@@
 Recall, however, that the performance shown Figure~\ref{fig:case3Estimates} is based on six rather than two receptive fields;
-so that there is likely to be less overlap in the full six-dimensional response space.
+there is likely to be less overlap in the full six-dimensional response space.
 That is, inclusion of more receptive fields will in general reduce the ambiguity that is seen when we visualize the responses of just the first two receptive fields.
-This effect is shown in the right panel of Figure~\ref{fig:RMSEvsRF}, which also illustrates the effect of training set size on estimation performance. 
-%% DHB: Johannes, please check rewrite of last two sentences: OK?
+This effect is shown in the right panel of Figure~\ref{fig:RMSEvsRF}.
+That figure also illustrates the effect of training set size on estimation performance.
 
@@
 
-Our software allows us to compare the effect of background surface reflectances on target object LRV with and without secondary reflections from background objects. 
-Our analysis shows that the secondary reflections have minimal effect on LRV estimates.
-The estimates without secondary reflections are comparable to that with reflections.
-This shows that the primary source of the estimation error is due to the variability in the normalized contrast of the target, due to the 
-finite number of samples in the background.
+Our rendering software allows us to compare the effect of background surface reflectances on target object LRV with and without simulation of secondary reflections of light from one object onto another
+Such secondary reflections were simulated for our primary results.
+When we turn off this feature of the rendering, we find (data not shown) that 
+that the secondary reflections have minimal effect on LRV estimation:
+the estimates without secondary reflections were similar to those with reflections.
+This suggests that the primary source of the estimation error in Condition 3 is caused by image-to-image variation in the reflectance of the background objects,
+which in turn affects the normalized contrast representation of the target.
 
@@
 This comparison may serve to reduce the effect of light scattered from the background onto the target. 
-The specific geometry of the receptive fields should not be taken to be a general feature, as it arises as a consequence
+The specific geometry of the receptive fields should not be taken to be a general feature of the human visual system, as the RF geometry arises as a consequence
 of the single scene geometry we studied.
@@
 
-Figure~\ref{fig:barGraphs} summarizes our main findings, by showing the overall relative root mean squared estimation error (relative RMSE; see Figure~\ref{fig:barGraphs} caption) for each condition. 
+Figure~\ref{fig:barGraphs} summarizes our main findings, by showing the overall relative root mean squared estimation error (relative RMSE) for each condition. 
 In Condition 1, where only the relative reflectance spectrum of the target object varies, 
@@
 To obtain ground truth information about the reflectance of objects in a natural image, it is necessary to make 
-an independent measurement of the illumination impinging on each object.
-Although this can be done by inserting a small number of discretely spaced reflectance standards into the scene, 
+an independent measurement of the of the reflectance function of each object (or of the illumination impinging on each object).
+Although this can be done at a small number of image locations by inserting discretely spaced reflectance standards into the scene, 
 interpolating to locations between such standards requires strong assumptions.
@@
 Virtual rendered scenes are not guaranteed to capture all of the task relevant variation that occurs in real scenes.
-Casual inspection of our images reveals that they are rendered, and not real.
+Even casual inspection of our images reveals that they are rendered, and not real.
 However, computer graphics is getting better and we expect that the gap between virtual and natural image databases will steadily close.
@@
 We think experiments and analyses along these lines represent an important future direction.
-By coupling the experiments and analyses we hope to advance, in a principled and controlled manner, our understanding of how we see objects in the real world .
 
@@
 \end{document}
+
+%% DHB: There are all sorts of problems with the citations.
+% a) Journal and book case should be (e.g.) "Journal of Vision" not (e.g.) "Journal of vision".  This is botched in many places.
+% b) In some cases we appear to be citing things that are one page long.  I think many of these are papers that have more than
+% one page, and those instances should be fixed.  In other cases, we may be citing abstracts and I would prefer not to cite those
+% unless there is a real need to.  
+% c) Sometimes page numbers are given by (e.g.) "112-173", other by (e.g.) ", yet others by (e.g.) "(pp. 112-173)".  Pick one style
+% and stick with it.
+% d) There are other glitches.  For example, the title of Goncalves and Welchman starts "?what not?".  Proofread carefully and fix up.

### 2018-06-18 Draft5/appendix.tex
Appendix edits, comments.

@@
 \section{Illumination Spectra}
-Let us denote the $i$'th sample in the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset. 
-Since the measured spectra vary over several orders of magnitude in overall intensity, we normalize each spectrum by dividing it by its mean power 
+Denote the $i$'th spectrum in the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset. 
+Since the measured spectra vary over several orders of magnitude in overall intensity, we normalize each spectrum by dividing it by its mean power to obtain what we refer to as rescaled spectra:
 \begin{align}
@@
 For simplicity of notation, we denote wavelength $\lambda$ as a continuous variable; in the actual calculations wavelength is discretely sampled and integrals are approximated by sums. 
-
 The Granada dataset was measured at 5 nm sampling intervals between 300 and 1100 nm.  
@@
 
-The rescaled spectra $I_i^s(\lambda)$ were mean centered for PCA by subtracting out the sample mean ($\bar{I}^{s}(\lambda)$),  over all rescaled spectra in the dataset, 
+The rescaled spectra $I_i^s(\lambda)$ were mean centered for PCA by subtracting out the mean ($\bar{I}^{s}(\lambda)$),  over all rescaled spectra in the dataset, 
 \begin{align}
@@
 For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance.
+%% DHB: Just before Eqn 3, there is an I_sub_s that should be I_sub_i_sup_s.
+%% DHB: The switch from function to vector notation with the e_hat_sub_j_sup_PCA doesn't really make sense - you can't have a lambda on the left of the equals without a lambda on the right.
+% I'd switch the e_hat's to be non-bolded functions of lamba throughout, I think.  Same under development for surface reflectance model.
 
-These steps can be summarized as follows:
-\begin{align}
-I^G_i(\lambda) \rightarrow I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)} \rightarrow I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda) \rightarrow I_i^{MC}(\lambda) \approx \sum_{j = 1}^6 w_{ij}\hat{{\bf e}}_j^{PCA}.
-\end{align}
+%% DHB.  I deleted the summary here, seemed completely redundant with the quite short description above.
 
@@
 a multivariate Gaussian distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-and co-variance $\Sigma$ given as:
+and covariance matrix $\Sigma$ given as:
 \begin{align}
@@
 \end{align}
+%% DHB: I'd add after "covariance matrix $\Sigma$ "whose j,j' th entry is \Sigma_{jj'}".  The Tex is too much for me to try to
+% do this myself, though.
 
 \section{Surface Reflectance Spectra}
-Let us denote the $i$'th sample in the reflectance spectrum dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
+Denote the $i$'th sample in the reflectance spectrum dataset as $R_i(\lambda)$, where $\{i \in [1,M]\}$ 
 and $M$ is the total number of spectra in the dataset. 
@@
 distribution with mean $\bar{w}_j = \frac{1}{M}\sum_i w_{ij}$, 
-and co-variance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. 
+and covariance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. 
 If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, the randomly generated reflectance spectrum is given as:
@@
 
-For generating the target object reflectance at a particular LRV $(Y_{\rm T})$, the values in a generated spectrum were 
+For generating the target object reflectance at a particular target LRV $(Y_{\rm T})$, the values in a generated spectrum were 
 scaled by 

### 2018-06-23 Draft5/draft5.tex
jdb edit done
a few more comments added to have a look at…
i think it is in good shape

@@
 To understand the computations that support stable color perception, 
-we study how the estimation of the light reflectance value of a target object (LRV; a measure of the light reflected from the object under a standard illuminant) depends on variation in key properties of naturalistic scenes.
+we study how estimating a target object's light reflectance value (LRV; a measure of the light reflected from the object under a standard illuminant) depends on variation in key properties of naturalistic scenes.
 Specifically, we study how variation in target object reflectance, illumination spectra, and the reflectance of background objects in a scene impact estimation of a target object's LRV. 
@@
 of natural spectral variation.
-We show that a decoding scheme used learned linear filters to process a contrast representation of the cone excitations can recover target object LRV to within about 13\% RMSE.
+Optimally decoding target object LRV from the responses of a small learned set of task-specific linear filters that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRV.
+% We show that a decoding scheme used learned linear filters to process a contrast representation of the cone excitations can recover target object LRV to within about 13\% RMSE.
+% JDB: WE DIDN'T DEFINE RMSE SO IT MIGHT BE BEST TO AVOID USING THE ACRONYM HERE.
 Our work provides a framework for evaluating how different sources of scene variability limit performance on luminance constancy.}
@@
  {Computational Neuroscience Initiative}
- {and Department of Physics, University of Pennsylvania, PA, USA}
+ {Department of Physics, University of Pennsylvania, PA, USA}
  {}{vsin@sas.upenn.edu}
@@
 A key insight from these computational studies is that stable color descriptors of a target object cannot be obtained solely from the light reflected from that target object.
-It is possible, however, to obtain such descriptors by jointly analyzing the light reflected from multiple objects in the scene.
-As a consequence, the performance of color constancy algorithms will be affected both by variation in the illumination and in the surface reflectance of other objects in the scene,
-and thus algorithms need to be evaluated with respect to variation in both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}. 
+It is possible, however, to obtain stable color descriptors by jointly analyzing the light reflected from multiple objects in the scene.
+As a consequence, color constancy will be affected both by variation in the illumination and by variation in the surface reflectance of other objects in the scene.
+Color constancy algorithms should therefore be evaluated with respect to variation in both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}.
 There has also been computational work that generalizes to more complex viewing geometries \cite{funt1988color, barron2012color}.
+% JDB: LAST SENTENCE DANGLES. HOW BOUT WE PUT IT LOWER DOWN IN THE MANUSCRIPT?
 
@@
 These methods use the joint statistics of labeled images and scene variables to learn mappings that extract stable surface color descriptors from image input \cite{barron2015convolutional}.
-This general statistical learning approach has been useful for other perceptual problems in early and mid-level vision.
+This general approach has been useful for other perceptual problems in early and mid-level vision.
 For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
-It has been used to develop ideal observers for defocus blur, binocular disparity, and retinal motion estimation with natural stimuli.
+AMA has been used to develop ideal observers for estimating defocus blur, binocular disparity, and retinal motion estimation with natural stimuli.
 These ideal observers provide excellent predictions of human performance \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal}.
@@
 Although there are datasets of calibrated color images, these do not provide ground truth information about surface reflectance and illumination at each image location \cite{ChakrabartiHyperspectral,NascimentoFoster2016,ParragaHyperspectralData,TkacikUpennHypersepctralData,skauli2013collection,olmos2004biologically}.
-There are a few databases consisting of images of posed scenes where object surface reflectances are measured individually (\citeNP{funt1988color,ciurea2003large}), but these are not large enough to drive supervised learning.
+There are a few databases consisting of images of posed scenes where surface reflectances of individual objects have been measured (\citeNP{funt1988color,ciurea2003large}), but these databases are not large enough to drive supervised learning.
 
@@
 The LRV is a measure of the overall amount of light reflected by a surface \cite{astm1121477}.
-Computation of an LRV from a surface reflectance function proceeds in two steps.
-First, we computed the luminance of the light that would be reflected from the surface under a reference illuminant.
-Second, we normalize the result by the luminance of the reference illuminant itself.
+Estimating the LRV from a surface reflectance function proceeds in two steps.
+First, one computes the luminance of the light that would be reflected from the surface under a reference illuminant.
+Second, one normalizes the result by the luminance of the reference illuminant itself.
 Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
@@
 \subsection{Overview}
-There are four key parts to our methods.
+There are four key steps to our methods.
 First, we generate a labeled set of training images.
@@
 that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
-The package builds on our RenderToolbox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
+The package builds on the RenderToolbox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
 and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org}, 
@@
 the surface reflectance of the corresponding object.
-By incorporating statistical models of object surface reflectance and daylight illumination, 
+By using statistical models of daylight illumination and object surface reflectance to guide the rendering of scenes, 
 the package allows us to produce large labeled sets of images that capture key aspects of the task-relevant 
@@
 
-Our rendering package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
+The RenderToolbox4 package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
+% JDB: THE ABOVE SENTENCE IS CORRECT?
 Base scenes specify an arrangement of objects and light sources.
 Base scenes may be enriched by the insertion of additional objects, chosen from an object library (Fig.~\ref{fig:libraryWithTarget}), and by the insertion of additional light sources.
-Once the position, size and pose of the inserted objects and light sources have been set, 
+Once the position, size, and pose of the inserted objects and light sources have been set, 
 a surface reflectance function can be assigned to each object in the scene, and a spectral power distribution function can be assigned to each light source (Fig.~\ref{fig:VWCCTransformations}).
@@
 --varied in addition to the target object LRV.
-The datasets for Conditions 1 and 2 consiseted of 1000 scenes and images, 100 for each of 10 target object LRV values. 
+The datasets for Conditions 1 and 2 consisted of 1000 scenes and images, 100 for each of 10 target object LRV values. 
 The dataset for Condition 3 consisted of 3000 scenes and images, 300 each for the 10 target LRV values.
 The LRV values were equally spaced between 0.2 and 0.6.
-For each LRV value, we generated a different relative target surface reflectance for each scene. 
+For each LRV value, we generated a different relative target object surface reflectance for each scene. 
 % Figure 4
@@
 We inserted one additional spherical light source into the scene.
-The position and size of the inserted object, inserted light source and viewpoint were held fixed across all 
-scenes in the datasets. The geometry is shown in Figure~\ref{fig:3DScene} below.
-Surface and illuminant spectra were drawn according to statistical models of naturally occurring spectra.
+The position and size of the inserted object, the inserted light source, and the viewpoint on the scene were held fixed across all 
+scenes. The geometry is shown in Figure~\ref{fig:3DScene} below.
+Surface and illuminant spectra were sampled according to statistical models of naturally occurring spectra.
 Multispectral images ($320 \times 240$ pixels) were rendered at 31 evenly-spaced wavelengths between $400$nm and $700$nm.
@@
 
-Our statistical model approximates normalized spectra from the Granda dataset using the first 6 principle components of the normalized measurements from that dataset.
+Our statistical model approximates normalized spectra from the Granada dataset using the first 6 principle components of the normalized measurements from that dataset.
 The variation in the weights on these components is then modeled with a 6-dimensional Gaussian.
@@
 
-Because our multivariate Gaussian model is based on normalized spectra, it does not embody the large variation in overall intensity of natural daylights.
-To obtain illuminant spectra with intensity variation similar to the Granada dataset, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution in the range [0.15, 150].
-This procedure restores the three-order of magnitude intensity variation present in the original dataset.
-We chose the particular scale factor range so that the mean number of cone isomerizations from the target object ranged from approximately 100 to 100,000 for the 100 msec cone integration time we used (see below).
-This range corresponds approximately to that of natural daylight viewing.
+The multivariate Gaussian model described above is based on normalized spectra. 
+Thus, it does not embody the large variation in overall intensity of natural daylights.
+To restore the overall intensity variation in the Granada dataset, which spans approximately three orders of magnitude, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution spanning three orders of magnitude.
+% JDB: THE NUMBERS [0.15, 150] ARE ARBITRARY. THE RELEVANT INFO IS THE NEXT SENTENCE.
+% To restore the overall intensity variation in the Granada dataset, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution in the range [0.15, 150].
+% This procedure restores the three-order of magnitude intensity variation present in the original dataset.
+The particular range of scale factors was chosen so that the mean number of cone isomerizations from the target object ranged from approximately 100 to 100,000, given a 100 ms cone integration time (see below).
+This range of cone isomerizations corresponds approximately to that of natural daylight viewing.
 
@@
 
-To generate random reflectance spectra, we used the same principles we used to model illuminant spectral power distributions.
-We combined the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance 
-measurements to create a database containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data) (Figure~\ref{fig:reflectanceSpectra}).
+To generate random reflectance spectra, we employed principles similar to those used to generate random illuminant spectral power distributions.
+We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data) (Figure~\ref{fig:reflectanceSpectra}).
 We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
-Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance draws obtained using the model. 
+Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance sampled obtained using the model. 
 Details of the statistical model for surface reflectance spectra are provided in the appendix.
 
-To generate the target object reflectance at a particular LRV, the generated reflectance spectrum was 
+To generate the target object reflectance at a particular LRV, the sampled reflectance spectrum was 
 scaled such that its LRV had the desired value (see appendix).
@@
 The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally. 
-In primary visual cortex, foveal receptive fields have a spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}.
+In primary visual cortex, foveal receptive fields have a maximum spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}.
 
-We modeled a visual system by typical optical blurring (including axial chromatic aberration) in the formation of the retinal image \cite{marimont1994matching}, and spatial sampling by an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
+We modeled a visual system having typical optical blurring (including axial chromatic aberration)\cite{marimont1994matching}, and typical spatial sampling with an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
 The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
 Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec. 
+% JDB: DO WE HAVE REFERENCE INDICATING THAT 100ms IS A REASONABLE INTEGRATION TIME TO ASSUME?
 The Poisson nature of the photopigment isomerization was also included \cite{hecht1942energy}. 
@@
 normalized each cone excitation image by the summed (over wavelength) quantal efficiency of the corresponding cone class.
-The demosaicing and normalization do not alter the available information, relative to that carried by the cone excitations themselves.
+The demosaicing and normalization do not alter the available information relative to that carried by the cone excitations themselves. 
+% JDB: SHOULD WE SWAP 'SIGNAL TO NOISE' FOR 'AVAILABLE INFORMATION'.
 
@@
 We applied accuracy maximization analysis (AMA) to learn the optimal receptive fields for estimating LRV,
-and evaluated the performance obtained when the output of these filters was optimally decoded.
+and evaluated the performance obtained when the responses of these filters are optimally decoded.
 
@@
 These receptive fields are chosen so that decoding their responses leads to minimum expected-cost estimation, relative to any other choice of N linear receptive fields.
-This is possible because given a training set together with a set of N linear receptive fields and an explicit cost function, it is possible to determine the minimum expected-cost estimator that maps receptive field responses to the stimulus labels, on the assumption that all images in the training set are equally likely.
-Moreover, the corresponding expected estimation cost may be explicitly computed.
+This is possible because given a training set together with a set of N linear receptive fields and an explicit cost function, it is possible to determine the minimum expected-cost estimator that maps receptive field responses to the stimulus labels.
+% , on the assumption that all images in the training set are equally likely.
+% JDB: CLAUSE SEEMS UNNECESSARY
+Moreover, a close approximation to the corresponding expected estimation cost may be explicitly computed.
 Thus, AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
@@
 Training with both cost functions yielded similar estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
-We chose this cost function because the estimates it yields at the edges of the stimulus range are less biased than those obtained with the mean squared error cost function.
+We chose this cost function because the estimates it yields at the boundaries of the LRV range are less biased than those obtained with the mean squared error cost function.
 
@@
 
-Once the AMA receptive fields have been learned, we need to develop a general decoder that can be applied to arbitrary test images.
-A separate decoder is necessary because the decoder used to learn the receptive fields depends on the response mean and response variance of the filters to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
-To proceed, first we use the AMA receptive fields and the training dataset to find the conditional distributions of the receptive field responses, where the conditioning is on the labelled target object LRVs.
-Then, we approximate these with multivariate Gaussian distributions.
+Once the AMA receptive fields have been learned, a general decoder is needed that can be used with arbitrary test images.
+A general decoder is necessary because the decoder used to learn the receptive fields can be used only with the training set.
+Specifically, the decoder used to learn the filters requires the response mean and response variance of each filters to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
+To proceed, first we use the AMA receptive fields and the training dataset to find the distributions of the receptive field responses conditional on the target object LRVs.
+Then, we model these conditional response distributions with multivariate Gaussians.
 To estimate the LRV of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRV values, given the filter responses.
@@
 Estimation performance was evaluated on a test set consisting of the 10\% of images in the dataset that were not in the training set.
-For our primary results, estimation was based on 6 learned receptive fields.
+For our primary results, estimation was based on six receptive fields.
 
@@
 through their effect on the contrast normalized responses at the center of the target object. 
-We also evaluated the performance of a naive model that uses the mean of the LRV values in the training set as the estimate, irrespective
-of the image data.
+We also evaluated the performance of a naive model that uses the mean LRV value in the training set as the estimate, irrespective
+of the image data; that is, the naive model always estimated the LRV to be equal to 0.4.
+% JDB: DOUBLE CHECK THAT THE ADDITIONIAL CLAUSE AT END OF LAST SENTENCE IS CORRECT.
 
@@
 %% DHB: Show first three RFs in (c) here and in Figure 12, I think.  Otherwise it is hard to understand why the ones in 12 change.
+%% JDB: VIJAY, If you recompute the reduction in AMA cost for RFs 1, 2, and 3 in order and then compute the reduction in AMA cost for RFs 1, 3, and 2 in order, which of the two orders gives lower cost with two filters?
 
@@
 % because the third RF does have S cone contribution.
+% % JDB: WE ALSO NEED TO WRITE SOMETHING SOMEWHERE ABOUT WHY THE RFs HAVE THE ODD LOOKING SHAPES THAT THEY DO.
 
@@
 This comparison may serve to reduce the effect of light scattered from the background onto the target. 
-The specific geometry of the receptive fields should not be taken to be a general feature of the human visual system, as the RF geometry arises as a consequence
-of the single scene geometry we studied.
+The specific geometry of the receptive fields should not be taken to be a general feature of the human visual system, as the RF geometry arises as a consequence of the fixed scene geometry used in the training set.
 %% DHB: Let's look at RFs in case where secondary reflections are turned off, to see if what I drafted in this paragraph
@@
 Although this can be done at a small number of image locations by inserting discretely spaced reflectance standards into the scene, 
-interpolating to locations between such standards requires strong assumptions.
+interpolating to locations between such standards requires strong assumptions that are often unjustified in real scenes.
 
@@
 Luminance constancy is a special case of the more general problem of color constancy.
-The approach we developed here could be generalized to the estimation of additional surface reflectance descriptors, such as object hue or chroma.
+The approach we developed here could also be generalized to the estimation of additional surface reflectance descriptors, such as object hue or chroma.
 A further advance would be to develop methods for learning receptive fields that are optimal for multivariate estimation problems. 
@@
 
-An important motivation for studying the computational problem of luminance constancy
-is to gain insight about human vision.
+An important motivation for studying the computational problem of luminance constancy is to gain insight about human vision.
 The approach we developed can be used to make predictions of how humans would perform in a psychophysical task that probes the visual representation of object LRV.

### 2018-06-23 Draft5/draft5.tex
frustating edits

@@
 \title{Luminance Constancy Learned from Labeled Naturalistic Images}
-%% Luminance constancy in naturalistic scenes
-%% Learned luminance constancy: something
-%%
 
@@
 Optimally decoding target object LRV from the responses of a small learned set of task-specific linear filters that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRV.
-% We show that a decoding scheme used learned linear filters to process a contrast representation of the cone excitations can recover target object LRV to within about 13\% RMSE.
-% JDB: WE DIDN'T DEFINE RMSE SO IT MIGHT BE BEST TO AVOID USING THE ACRONYM HERE.
 Our work provides a framework for evaluating how different sources of scene variability limit performance on luminance constancy.}
@@
  \author{Burge}{Johannes}
- {}
+ {Neuroscience Graduate Group}
  {Department of Psychology, University of Pennsylvania, PA, USA}
@@
 % JDB: LAST SENTENCE DANGLES. HOW BOUT WE PUT IT LOWER DOWN IN THE MANUSCRIPT?
+% Vijay: I agree
 
@@
 The rendering viewpoint was set so that the object was at the center of the images.
-The full rendered images have been croppedso that the inserted objects are easily visible.}\label{fig:libraryWithTarget}
+The full rendered images have been cropped so that the inserted objects are easily visible.}\label{fig:libraryWithTarget}
 \end{figure}
@@
 The RenderToolbox4 package includes a collection of base scenes (Fig.~\ref{fig:baseScenes}).
-% JDB: THE ABOVE SENTENCE IS CORRECT?
 Base scenes specify an arrangement of objects and light sources.
@@
 % This procedure restores the three-order of magnitude intensity variation present in the original dataset.
+% Vijay: This would needed by someone who wants to reproduce the results.
 The particular range of scale factors was chosen so that the mean number of cone isomerizations from the target object ranged from approximately 100 to 100,000, given a 100 ms cone integration time (see below).
@@
 % JDB: SHOULD WE SWAP 'SIGNAL TO NOISE' FOR 'AVAILABLE INFORMATION'.
+% Vijay: No.
 
@@
 This is possible because given a training set together with a set of N linear receptive fields and an explicit cost function, it is possible to determine the minimum expected-cost estimator that maps receptive field responses to the stimulus labels.
-% , on the assumption that all images in the training set are equally likely.
-% JDB: CLAUSE SEEMS UNNECESSARY
 Moreover, a close approximation to the corresponding expected estimation cost may be explicitly computed.
@@
 of the image data; that is, the naive model always estimated the LRV to be equal to 0.4.
-% JDB: DOUBLE CHECK THAT THE ADDITIONIAL CLAUSE AT END OF LAST SENTENCE IS CORRECT.
 
@@
 \centering
-            \begin{subfigure}[b]{0.25 \textwidth}
+            \begin{subfigure}[b]{0.3 \textwidth}
         \caption{LRV estimates}
@@
     \end{subfigure} 
-        \begin{subfigure}[b]{0.26 \textwidth}
+        \begin{subfigure}[b]{0.31 \textwidth}
         \caption{RF responses}
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.4 \textwidth}
+    \begin{subfigure}[b]{0.32 \textwidth}
 	\caption{AMA receptive fields}
@@
 \end{figure}
-%% DHB: "Linear Model" in panel a) should be "Regression".  Also in Figures 11 and 12.
-%% DHB: It is really hard to see the ellipses in b), even if I increase the mag in the PDF.  Can you make them more salient?
-%% DHB: Show first three RFs in (c) here and in Figure 12, I think.  Otherwise it is hard to understand why the ones in 12 change.
 %% JDB: VIJAY, If you recompute the reduction in AMA cost for RFs 1, 2, and 3 in order and then compute the reduction in AMA cost for RFs 1, 3, and 2 in order, which of the two orders gives lower cost with two filters?
+% Vijay: See my email.
 
@@
 %% VS to try a few more cases to make sure.
+% Vijay: Tried. Results are similar.
 
@@
     \end{subfigure} 
-        \begin{subfigure}[b]{0.26\textwidth}
+        \begin{subfigure}[b]{0.31\textwidth}
         \caption{Receptive field response}
@@
 The specific geometry of the receptive fields should not be taken to be a general feature of the human visual system, as the RF geometry arises as a consequence of the fixed scene geometry used in the training set.
-%% DHB: Let's look at RFs in case where secondary reflections are turned off, to see if what I drafted in this paragraph
-% about RF structure is plausible.
 
@@
 reliably light reflected from those objects can be used as a cue to estimate the spectral power distribution of the illuminant.
-% JDB: Are we going to add in a constancy index, as we discussed doing a few meetings ago?
-% DHB: I think it is time to submit this paper.
 
@@
 As noted in the introduction, supervised learning requires large labeled datasets.
-Labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, kim2018lawful, burge2010natural, girshick2011cardinal, burge2016estimating, goncalves2017not}.
+Labeled datasets of natural images have been useful for developing normative models of the estimation of defocus blur, binocular disparity, retinal image motion, and 3D surface orientation \cite{burge2011optimal, burge2012optimal, burge2014optimal, burge2015optimal, sebastian2015defocus, kim2018lawful, burge2010natural, girshick2011cardinal, burge2016estimating, goncalves2017not}.
 

### 2018-06-27 codeForFigures/codeToMakeFigures/estimatesVsActual.m
removed old codes for plotting

@@ -1,70 +1,0 @@
-% This script plots the lightness estimates vs the actual lighteness for 
-% the linear, SVD and AMA methods.
-%
-% Case 9 - Variable Target shape Fixed Background Fixed Illuminant
-% Case 10 - Variable Target shape Fixed Background Variable Illuminant
-% Case 12 - Variable Target shape Variable Background Variable Illuminant
-%
-% VS wrote this Oct7 2017
-
-% Make the directory where the figures will be stored
-if (~exist('estimatesVsActual','dir'))
-    mkdir('estimatesVsActual');
-end
-
-% Choose a case
-for caseNo = [ 9 10 12]
-
-% load the files containing the estimates
-loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'.mat']);
-loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'.mat']);
-loadTheSVDFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SVD/case',num2str(caseNo),'.mat']);
-
-% Define the colors to be used for each method
-naiveColor  = 'm';
-linearColor = 'k';   
-SVDColor    = 'g';
-AMAColor    = 'r';
-
-% Plot the contrast estimates
-fig = figure;
-set(fig,'units','pixels', 'Position', [1 1 500 500]);
-hold on;
-% plot the linear and svd response
-lNaive = plot(unique(loadTheAMAFile.XTest)',0.4*ones(size(unique(loadTheAMAFile.XTest)')),naiveColor,'linewidth',2);
-lLinear = plot(unique(loadTheAMAFile.XTest)',loadTheLinearFile.cNormMeanEstimateTest,linearColor,'linewidth',2);
-% errorbar(unique(loadTheLinearFile.labelsTest)',loadTheLinearFile.cMeanSvdEstimateTest,loadTheLinearFile.cStdSvdEstimateTest,SVDColor,'linewidth',2);
-xlim([0.15 0.65]);
-ylim([0.15 0.65]);
-xlabel('$Y$','interpreter','latex');
-ylabel('$\hat{Y}$','interpreter','latex');
-box on;
-
[…]

### 2018-06-27 codeForFigures/codeToMakeFigures/estimatesVsActualAMAOnly.m

@@ -1,75 +1,0 @@
-% This script plots the lightness estimates vs the actual lighteness for 
-% the linear, SVD and AMA methods.
-%
-% Case 9 - Variable Target shape Fixed Background Fixed Illuminant
-% Case 10 - Variable Target shape Fixed Background Variable Illuminant
-% Case 12 - Variable Target shape Variable Background Variable Illuminant
-%
-% VS wrote this Oct7 2017
-
-% Make the directory where the figures will be stored
-if (~exist('estimatesVsActualAMA','dir'))
-    mkdir('estimatesVsActualAMA');
-end
-
-% Choose a case
-for caseNo = [12]
-
-% load the files containing the estimates
-if (caseNo==9 || caseNo==11)
-    loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'_AMAIsomerization.mat']);
-    loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'_AMAIsomerization.mat']);
-else
-    loadTheLinearFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case',num2str(caseNo),'.mat']);
-    loadTheAMAFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SGD/case',num2str(caseNo),'.mat']);
-end
-% loadTheSVDFile = load(['/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/SVD/case',num2str(caseNo),'.mat']);
-
-% Define the colors to be used for each method
-naiveColor  = 'g';
-linearColor = 'k';   
-AMAColor    = 'r';
-
-% Plot the contrast estimates
-fig = figure;
-set(fig,'units','pixels', 'Position', [1 1 500 500]);
-hold on;
-% plot the linear and svd response
-lDiagonal = plot([0.15 0.65],[0.15 0.65],'b:','linewidth',1);
-lNaive = plot(unique(loadTheAMAFile.XTest)',0.4*ones(size(unique(loadTheAMAFile.XTest)')),naiveColor,'linewidth',2);
-if (caseNo==9 || caseNo==11)
[…]

### 2018-06-27 codeForFigures/codeToMakeFigures/filtersAndFilterResponses.m

@@ -1,150 +1,0 @@
-% filtersAndFilterResponses
-% This script can be used to plot AMA and SVD filters and filter responses.
-% This script first loads the results, plots the filters/response and saves
-% the figure as .pdf. The figures are made case by case. This is a really
-% dumb script. Everything needs to be typed manually.
-%
-% The data is stored in Johannes Burge's Ogle computer.
-%
-% VS wrote this Oct 7 2017
-
-% Make the directory where the figures will be stored
-if (~exist('filters','dir'))
-    mkdir('filters');
-end
-
-if (~exist('filterResponse','dir'))
-    mkdir('filterResponse');
-end
-
-%% Load AMA results struct
-clear;
-load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case11_AMAIsomerization.mat')
-plotFiltersJointResponsesModified(1,[1,2],case11Output.AMA.X,case11Output.AMA.s,case11Output.AMA.f,case11Output.AMA.ctgInd,[],[],[],[1:10])
-% save2pdf('/Users/vijaysingh_local/Documents/LightnessPaper/codeForFigures/codeToMakeFigures/filterResponse/case11FiltersResponse_AMAIsomerization.pdf',gcf,600);
-
-%% Load AMA results struct
-clear;
-load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat')
-plotFiltersJointResponsesModified(1,[1,2],case9Output.AMA.X,case9Output.AMA.s,case9Output.AMA.f,case9Output.AMA.ctgInd,[],[],[],[1:10])
-% Case11_AMAIsomerization
-
-%% Load AMA results struct
-clear;
-load('/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10_contrast.mat')
-plotFiltersJointResponsesModified(1,[1,2],case10Output.AMA.X,case10Output.AMA.s,case10Output.AMA.f,case10Output.AMA.ctgInd,[],[],[],[1:10])
[…]

### 2018-06-27 codeForFigures/codeToMakeFigures/plotBarGraphs.m

@@ -1,153 +1,0 @@
-% This script plots the RMSE bar graphs for the linear, SVD and AMA 
-% methods. 
-% Three bar graphs are produced.
-% 1. Comparison of Naive, Linear, SVD and AMA methods for each case.
-% 2. Performance of SVD Filters from one case on stimuli of other cases.
-% 3. Performance of AMA Filters from one case on stimuli of other cases.
-%
-% VS wrote this Oct 7 2017
-
-
-% Load the results for all cases
-% SVD Results
-clear;
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case9SVDResults.mat']);
-results9SVD = results.case9Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case10SVDResults.mat']);
-results10SVD = results.case10Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12SVDResults.mat']);
-results12SVD = results.case12Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12RotatedSVDResults.mat']);
-results12RSVD = results.case12Rotated;
-
-% AMA Results
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9.mat']);
-results9AMA = results.case9Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10.mat']);
-results10AMA = results.case10Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12.mat']);
-results12AMA = results.case12Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12Rotated.mat']);
-results12RAMA = results.case12Rotated;
-
-% Linear Results
-
-linearCase9 = load('/Users/vijaysingh_local/Dropbox (Personal)/dataForPoster/linear/Case9.mat');
[…]

### 2018-06-27 codeForFigures/codeToMakeFigures/plotBarGraphsAMAOnly.m

@@ -1,192 +1,0 @@
-% This script plots the RMSE bar graphs for the linear and AMA 
-% methods. 
-% Three bar graphs are produced.
-% 1. Case 1: Naive, Linear, AMA RF Case1 AMA RF Case2 AMA RF Case3
-% 2. Case 2: Naive, Linear, AMA RF Case1 AMA RF Case2 AMA RF Case3
-% 3. Case 3: Naive, Linear, AMA RF Case1 AMA RF Case2 AMA RF Case3
-%
-% VS wrote this Nov 8 2017
-
-
-% Load the results for all cases
-% SVD Results
-clear;
-% results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case9SVDResults.mat']);
-% results9SVD = results.case9Output;
-% 
-% results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case10SVDResults.mat']);
-% results10SVD = results.case10Output;
-% 
-% results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12SVDResults.mat']);
-% results12SVD = results.case12Output;
-% 
-% results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12RotatedSVDResults.mat']);
-% results12RSVD = results.case12Rotated;
-
-% AMA Results
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD2/Case9.mat']);
-results9AMA = results.case9Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD2/Case10.mat']);
-results10AMA = results.case10Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD2/Case11.mat']);
-results11AMA = results.case11Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD2/Case12.mat']);
-results12AMA = results.case12Output;
-
[…]

### 2018-06-27 codeForFigures/codeToMakeFigures/plotFiltersColor2D.m

@@ -1,62 +1,0 @@
-function plotFiltersColor2D(f,fSmp,figh,overallTitle,bsmoothing)
-
-% function plotFilters_Defocus(f,fSmp,figh)
-%
-%   example call: plotFilters_Defocus(f)
-%
-% plot filters for defocus estimation
-%
-% f:          filter weights
-% fSmp:       values at which filter weights are sampled
-% figh:       figure handle
-
-if ~exist('fSmp','var') || isempty(fSmp) fSmp = [0:(size(f,1)/2-1)]; fSmp = fSmp-max(fSmp)/2-1;  end
-if ~exist('figh','var') || isempty(figh) figh = []; end
-
-% HANDLE FIGURE
-if isempty(figh); figure;
-else              figure(figh);
-end
-set(gcf,'position',[991 973 500 300]);
-
-% PLOT
-for i = 1:size(f,2)
-    % SUBPLOT ORGANIZATION: <= 3 plot each row, 1 row for each filter
-    if ~bsmoothing        
-        fSmooth = zeros(size(f,1),size(f,2));
-        fSmooth(:,i) = f(:,i);
-    else
-        sizeOfGrid = sqrt(size(f,1)/3);
-        [X,Y] = meshgrid((1:sizeOfGrid),(1:sizeOfGrid));
-        [XX,YY] = meshgrid((1:0.25:sizeOfGrid),(1:0.25:sizeOfGrid));
-        fSmooth = zeros(length(XX(:)),size(f,2));
-        for kk = 1:3
-            fSmooth((kk-1)*length(XX(:))+1:kk*length(XX(:)),i) = ...
-                griddata(X(:),Y(:),f((kk-1)*length(X(:))+1:kk*length(X(:)),i),XX(:),YY(:));
-        end
-    end
-    fSqr = reshape(fSmooth(:,i),[sqrt(size(fSmooth,1)/3) sqrt(size(fSmooth,1)/3) 3]); 
-    for j = 1:3, 
-        subplot(size(fSmooth,2),3,(i-1)*3+j);         
-        imagesc(fSqr(:,:,j));
-        set(gca, 'XTick', []);
-        set(gca, 'YTick', []);
-        axis square;
-        
-        colormap(cmapBWR);
-        caxis([-.04 .04]); colormap(cmapBWR);        
-        switch j
-            case 1
-                channelName = ' L';
-            case 2
-                channelName = ' M';
-            case 3
-                channelName = ' S';
-        end
[…]

### 2018-06-27 codeForFigures/codeToMakeFigures/plotFiltersJointResponsesModified.m

@@ -1,113 +1,0 @@
-function plotFiltersJointResponsesModified(bPltRsp,fPairs,X,sTrn,fTrn,ctgIndTrn,sTst,fTst,ctgIndTst,ctg2plt,rMax,fano,var0,axisLims,bPLOTellipse)
-
-% function plotFiltersJointResponses(bPltRsp,fPairs,X,sTrn,fTrn,ctgIndTrn,sTst,fTst,ctgIndTst,ctg2plt,rMax,fano,var0,axisLims,bPLOTellipse)
-%
-%   example call: plotFiltersJointResponses(1,[1 2; 3 4],X,s,f,ctgInd)
-%
-% plot joint filter responses for specified filter pairs
-%
-% bPltRsp:      boolean indicating whether to scatter plot responses or not
-%               1 -> scatter plot responses
-%               0 -> don't (plots only rsp ellipses)
-% fPairs:       filter pairs to plot                 [ nPairs  x    2    ]
-% X:            category values                      [ 1       x  nCtg   ]
-% sTrn:         stimuli           (training set)     [ d       x nStmTrn ]
-% fTrn:         filters           (training set)     [ d       x    q    ]
-% ctgIndTrn:    category indices  (training set)     [ nStmTrn x    1    ]
-%               having nCtg unique values
-% sTst:         stimuli           (  test   set)     [ d       x nStmTst ]
-%               default = sTrn
-% fTst:         filters           (  test   set)     [ d       x    q    ] 
-%               default = fTrn
-% ctgIndTst:    category indices  (  test   set)     [ nStmTst x    1    ]
-%               default = ctgIndTrn
-% rMax:         response max
-% fano:         response fano factor
-% var0:         response baseline variance
-% axisLims:     manual control over axis limits (e.g. rMax*[-1 1 -1 1])
-% bPLOTellipse: plot ellipse or not
-%               1 -> plot 
-%               0 -> not
-
-% INPUT HANDLING
-if ~exist('sTst',        'var') || isempty(sTst)         sTst      = sTrn;              end
[…]

### 2018-06-27 codeForFigures/codeToMakeFigures/plotRMSEvsEigValSVD.m

@@ -1,89 +1,0 @@
-% This script plots the RMES v/s the number of eigenvalues used for 
-% lightness estimation. We plot the RMSE for AMA and SVD cases together in
-% one figure.
-% The script first loads all data and then plots the RMSE.
-%
-% VS wrote this Oct 7 2017.
-
-% Load the files
-clear all;
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case9SVDResults.mat']);
-results9SVD = results.case9Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case10SVDResults.mat']);
-results10SVD = results.case10Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12SVDResults.mat']);
-results12SVD = results.case12Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/SVDOutputs/case12RotatedSVDResults.mat']);
-results12RSVD = results.case12Rotated;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case9_AMAIsomerization.mat']);
-results9AMA = results.case9Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case10.mat']);
-results10AMA = results.case10Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case11_AMAIsomerization.mat']);
-results11AMA = results.case11Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12.mat']);
-results12AMA = results.case12Output;
-
-results = load(['/Users/vijaysingh_local/Desktop/codesAndData/Color/AMAOutputs/SGD/Case12Rotated.mat']);
-results12RAMA = results.case12Rotated;
-
-%%
-% Make the directory where the figures will be stored
-if (~exist('RMSEvsNEigVals','dir'))
-    mkdir('RMSEvsNEigVals');
-end
-
[…]

### 2018-06-27 Draft5/draft5.tex
Finalizing!

@@
 
-\title{Luminance Constancy Learned from Labeled Naturalistic Images}
+\title{Computational Luminance Constancy from Naturalistic Images}
 
@@
 
+ %% Possible reviewers:
+ %
+ %  Tom Serre, Brown
+ %  Bill Freeman, Google Research
+ %  Roland Fleming, Geissen
+ %  Kavita Bala, Cornell
+
 \keywords{color constancy, luminance constancy, supervised learning}
@@
 Color constancy algorithms should therefore be evaluated with respect to variation in both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}.
-There has also been computational work that generalizes to more complex viewing geometries \cite{funt1988color, barron2012color}.
-% JDB: LAST SENTENCE DANGLES. HOW BOUT WE PUT IT LOWER DOWN IN THE MANUSCRIPT?
-% Vijay: I agree
 
@@
 There are a few databases consisting of images of posed scenes where surface reflectances of individual objects have been measured (\citeNP{funt1988color,ciurea2003large}), but these databases are not large enough to drive supervised learning.
+Finally, recent work has applied crowd-sourcing techniques to annotate natural images with surface reflectance descriptors (REF).
+% Bala reference
 
@@
 Across these datasets the luminance constancy problem (i.e. estimating the target object LRV)
-becomes progressively more difficult .
+becomes progressively more difficult.
 
 The variation within our datasets captures the essence of the computational problem of lightness constancy
-up to effects of scene geometry, an additional richness that we do not address in this paper.
+up to effects of scene geometry, an additional richness that we do not address in this paper (see \citeNP{funt1988color, barron2012color}).
+
 In Condition 1, the relative reflectance spectrum of the target object was the only source of scene variation other than the target object LRV.
@@
 To restore the overall intensity variation in the Granada dataset, which spans approximately three orders of magnitude, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution spanning three orders of magnitude.
-% JDB: THE NUMBERS [0.15, 150] ARE ARBITRARY. THE RELEVANT INFO IS THE NEXT SENTENCE.
-% To restore the overall intensity variation in the Granada dataset, we scaled each randomly generated spectrum with a random number sampled from a log-uniform distribution in the range [0.15, 150].
-% This procedure restores the three-order of magnitude intensity variation present in the original dataset.
-% Vijay: This would needed by someone who wants to reproduce the results.
 The particular range of scale factors was chosen so that the mean number of cone isomerizations from the target object ranged from approximately 100 to 100,000, given a 100 ms cone integration time (see below).
@@
 % JDB: DO WE HAVE REFERENCE INDICATING THAT 100ms IS A REASONABLE INTEGRATION TIME TO ASSUME?
+% LEAVING HANGING FOR NOW.  MAYBE LOOK AT COHN TWO-FLASH DETECTION EXPERIMENTS OR TEMPORAL
+% SUMMATION.
 The Poisson nature of the photopigment isomerization was also included \cite{hecht1942energy}. 
@@
 The demosaicing and normalization do not alter the available information relative to that carried by the cone excitations themselves.
-% JDB: SHOULD WE SWAP 'SIGNAL TO NOISE' FOR 'AVAILABLE INFORMATION'.
-% Vijay: No.
 
@@
 The response clusters are approximated by a multivariate Gaussians whose means and covariances are represented by the ellipses shown in the figure.
-(c) The first two AMA receptive fields.}
+(c) The first three AMA receptive fields.}
 \label{fig:Condition1}
@@
 of estimation performance shown in Figure~\ref{fig:case1Estimates}.
+Note that even the responses of the first RF separate well (vertical lines would accurately
+distinguish the LRVs), so that that one receptive field is sufficient for accurately performing the task.
 
-Figure~\ref{fig:case1RFs} shows the first two AMA receptive fields.
+Figure~\ref{fig:case1RFs} shows the first three AMA receptive fields.
 Each receptive field performs a weighted sum of the L, M, and S cone excitations.
@@
 The L and M cone excitations at the background object locations and the S cone excitations at all locations receive small weights and are thus largely ignored. 
-These receptive fields make sense.
 For this condition, the background regions provide very little task-relevant information. 
 In addition, luminance is primarily determined by L and M cones, so the S cones should make little
-contribution.
-%% DHB: We need to come back to this paragraph after we finalize the RFs to be shown in Figure 10c and 12c,
-% because the third RF does have S cone contribution.
-% % JDB: WE ALSO NEED TO WRITE SOMETHING SOMEWHERE ABOUT WHY THE RFs HAVE THE ODD LOOKING SHAPES THAT THEY DO.
+direct contribution.
+The first three RFs are similar to each other, reflecting the fact that here the main benefit
+of multiple receptive fields is to reduce the impact of noise on estimation performance.
 
@@
 We verified that performance remained excellent for other draws.
-%% VS to try a few more cases to make sure.
-% Vijay: Tried. Results are similar.
-
-%% DHB, VS: Maybe the above sentence is all we really need, and can delete what's below? Vijay's analysis did not actually use illuminants drawn
-% from the distribution, though.
-%
-%% Let's just run a version Condition 1 for some other draws of illumination.
-%
-%For this condition, LRV estimation should be easy because the variation in target object reflectance that we introduced
-%preserved LRV (which is calculated using a CIE D65 as the illumination).
-%Thus, for fixed scene illuminants similar to D65, the luminance of the light reflected from the target object will vary minimally.
-%In Condition 1, we used an illumination randomly sampled from our model of daylight illumination spectra (see Methods).
-% and thus expect a reasonable degree of similarity to D65.
-%% DHB: We need to say something about how similar.  Might explore different illuminants to dissect how sensitive the estimation
-% is to whether the fixed illuminant is D65 or something else.  Probably not very, but this is an example of something we can exploit
-% our graphics approach to understand, and we want to build up examples.
-% JDB: I agree. The statement in current form is unnecessarily vague. With a bit of additional analysis, we could also say that different random samples produce nearly identical results, etc. etc.
+%% VS to try a few more cases to make sure. Vijay: Tried two more draws. Results are similar.
 
@@
 (b) Contrast normalized cone excitations for the training set projected onto the first two AMA receptive fields.
-(c) First two AMA receptive fields learned using the contrast normalized cone excitations.}
+(c) First three AMA receptive fields learned using the contrast normalized cone excitations.}
 \label{fig:Condition3}
@@
 
-Figure~\ref{fig:case3RFs} shows the first two receptive fields learned for Condition 3.
-Similar to the receptive fields for Condition 1, the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
+Figure~\ref{fig:case3RFs} shows the first three receptive fields learned for Condition 3.
+The first and third of these are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
 Additionally, the cone excitations at the target have opposite sign compared to background object locations.
-This make sense.
-As discussed earlier, luminance is primarily determined by L and M cones, so the S cones should make little
-contribution.
-Additionally, for this condition, the optimal receptive fields compare normalized cone contrast between the target and background regions. 
-This comparison may serve to reduce the effect of light scattered from the background onto the target. 
-The specific geometry of the receptive fields should not be taken to be a general feature of the human visual system, as the RF geometry arises as a consequence of the fixed scene geometry used in the training set.
+The specific geometry of the receptive fields, however, should not be taken to be a general feature of the human visual system,
+as the particular RF geometry arises partly as a consequence of the fixed scene geometry used in the training set.
+Indeed, aspects of the training image spatial structure can be seen in the RFs.
+The second receptive field weights the S cones most heavily.
+Although S cone signals do not contribute directly to luminance, for natural spectra S cone signals are correlated with
+those of L and M cones (REFS), so that S cone information can contribute to task performance.
+%% DHB: Cite [1] Burton, G.J. & Moorehead, I.R. 1987 Color and spatial structure in natural images. Applied Optics 26, 157-170.
+% Benson, N.C., Manning, J.R. & Brainard, D.H. 2014 Unsupervised learning of cone spectral classes from natural images. PLoS Comput Biol 10, e1003652.
 
@@
 Here we used labeled images rendered from virtual scene descriptions. 
-There are many advantages to using rendered images.
+There are many advantages to using rendered images (REF).
 One advantage is that they allow us to work with large numbers of labeled images where object reflectance is precisely known at each pixel.
@@
 of the illumination.
-
+% @inproceedings{Butler:ECCV:2012,
+%title = {A naturalistic open source movie for optical flow evaluation},
+%author = {Butler, D. J. and Wulff, J. and Stanley, G. B. and Black, M. J.},
+%booktitle = {European Conf. on Computer Vision (ECCV)},
+%editor = {{A. Fitzgibbon et al. (Eds.)}},
+%publisher = {Springer-Verlag},
+%series = {Part IV, LNCS 7577},
+%month = oct,
+%pages = {611--625},
+%year = {2012}
+%}
 There are also disadvantages associated with using rendered images. 

### 2018-06-27 Draft5/draft5.tex
more edits

@@
 
-\abstract{
-The human visual system supports stable percepts of object color even though the light that reflects from object surfaces varies significantly with the scene illumination.
+\abstract{The human visual system supports stable percepts of object color even though the light that reflects from object surfaces varies significantly with the scene illumination.
 To understand the computations that support stable color perception, 
@@
 of natural spectral variation.
-Optimally decoding target object LRV from the responses of a small learned set of task-specific linear filters that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRV.
+Optimally decoding target object LRV from the responses of a small learned set of task-specific linear receptive fields that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRV.
 Our work provides a framework for evaluating how different sources of scene variability limit performance on luminance constancy.}
@@
  {}{cottaris@sas.upenn.edu}
+
  \author{Heasly}{Benjamin S.}
@@
 
-Early work on computational color constancy considered a simplified imaging model where where scenes consisted of multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
+Early work on computational color constancy considered a simplified imaging model where scenes consisted of multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.
 Subsequent work incorporated probabilistic descriptions of the statistics of naturally occurring scenes \cite{D'ZmuraConstancy3, D'ZmuraIversonSinger,BrainardFreeman}.
@@
 This general approach has been useful for other perceptual problems in early and mid-level vision.
-For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear filters optimized for particular perceptual tasks \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
+For example, a recently developed technique called accuracy maximization analysis (AMA) learns linear receptive fields optimized for particular perceptual tasks \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
 AMA has been used to develop ideal observers for estimating defocus blur, binocular disparity, and retinal motion estimation with natural stimuli.
@@
 There are a few databases consisting of images of posed scenes where surface reflectances of individual objects have been measured (\citeNP{funt1988color,ciurea2003large}), but these databases are not large enough to drive supervised learning.
-Finally, recent work has applied crowd-sourcing techniques to annotate natural images with surface reflectance descriptors (REF).
-% Bala reference
+Finally, recent work has applied crowd-sourcing techniques to annotate natural images with surface reflectance descriptors \cite{kovacs17shading}.
 
@@
 (b) Sample spectra generated using the statistical model derived from normalized Granada dataset.
-(c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in b (red).
-(d) sRGB renditions of the samples shown in b.}
+(c) CIE xy chromaticities of the Granda dataset (black) and the samples shown in panel b (red).
+(d) sRGB renditions of the samples shown in panel b.}
 \label{fig:illuminant}
@@
 (b) Sample spectra generated using the surface reflectance statistical model.
-(c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances (black) and the sample spectra shown in b (red).
-(d) sRGB renditions of the samples shown in b, rendered under the CIE D65 daylight.}
+(c) CIE xy chromaticity diagram of the Munsell and Vrhel reflectances (black) and the sample spectra shown in panel b (red).
+(d) sRGB renditions of the samples shown in panel b, rendered under the CIE D65 daylight spectrum.}
 \label{fig:surfaceReflectanceGeneration}
 \end{figure}
+
+To generate random reflectance spectra, we employed principles similar to those used to generate random illuminant spectral power distributions.
+We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data) (Figure~\ref{fig:reflectanceSpectra}).
+We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
+Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance sampled obtained using the model. 
+Details of the statistical model for surface reflectance spectra are provided in the appendix.
 
@@
 
-To generate random reflectance spectra, we employed principles similar to those used to generate random illuminant spectral power distributions.
-We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data) (Figure~\ref{fig:reflectanceSpectra}).
-We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
-Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance sampled obtained using the model. 
-Details of the statistical model for surface reflectance spectra are provided in the appendix.
-
 To generate the target object reflectance at a particular LRV, the sampled reflectance spectrum was 
@@
 
-% Figure 8: Methods
+% Figure 9: Methods
 \begin{figure}
@@
         \caption{sRGB rendering of a 3D scene}
+                \vspace{1.2mm}
         \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_a.png}
@@
         \caption{Cropped image}
-        \vspace{1.5mm}
+        \vspace{2.5mm}
         \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_b.png}
@@
         \caption{Retinal image}
-        \vspace{1.5mm}
+        \vspace{2.5mm}
         \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_c.png}
@@
     ~
-    \begin{subfigure}[b]{0.2 \textwidth}
+    \begin{subfigure}[b]{0.205 \textwidth}
         \caption{Normalized cone contrast}        
@@
 \subsection{Model of early visual system} \label{method:Isetbio}
-Lght entering the eye is focussed and blurred by eye's optics to form the retinal image.
+Light entering the eye is focussed and blurred by eye's optics to form the retinal image.
 This image is then sampled by a mosaic of cone photoreceptors.
@@
 We applied accuracy maximization analysis (AMA) to learn the optimal receptive fields for estimating LRV,
-and evaluated the performance obtained when the responses of these filters are optimally decoded.
+and evaluated the performance obtained when the responses of these receptive fields are optimally decoded.
 
-\subsubsection*{Learning optimal filters}
+\subsubsection*{Learning optimal receptive fields}
 AMA is a task-specific Bayesian method for dimensionality reduction.
@@
 Thus, AMA searches over the space of linear receptive fields to find the set that minimizes the expected estimation cost.
-For each condition, we learned the filters with a training set consisting of 90\% of the images.
+For each condition, we learned the receptive fields with a training set consisting of 90\% of the images.
 
@@
 
-Details of how AMA learns filters and how the filter responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
+Details of how AMA learns receptive fields and how the receptive field responses are optimally decoded are provided in previously published work \cite{geisler2009optimal,burge2017accuracy,jaini2017linking}.
 
-\subsubsection*{Decoding optimal filters}
+\subsubsection*{Decoding optimal receptive fields}
 
@@
 A general decoder is necessary because the decoder used to learn the receptive fields can be used only with the training set.
-Specifically, the decoder used to learn the filters requires the response mean and response variance of each filters to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
+Specifically, the decoder used to learn the receptive fields requires the response mean and response variance of each receptive field to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
 To proceed, first we use the AMA receptive fields and the training dataset to find the distributions of the receptive field responses conditional on the target object LRVs.
 Then, we model these conditional response distributions with multivariate Gaussians.
-To estimate the LRV of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRV values, given the filter responses.
+To estimate the LRV of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRV values, given the receptive field responses.
 The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
@@
 \end{figure}
-%% JDB: VIJAY, If you recompute the reduction in AMA cost for RFs 1, 2, and 3 in order and then compute the reduction in AMA cost for RFs 1, 3, and 2 in order, which of the two orders gives lower cost with two filters?
-% Vijay: See my email.
 
 \subsection{Condition 1}
-
 In Condition 1, only the LRV and the relative reflectance spectrum of the target object vary across scenes.
@@
 We verified that performance remained excellent for other draws.
-%% VS to try a few more cases to make sure. Vijay: Tried two more draws. Results are similar.
 
@@
     \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
-The relative RMSE is high (41.4\% for linear regression and 26.1\% for AMA-based estimation).
+The relative RMSE is high (41.4\% for linear regression and 26.4\% for AMA-based estimation).
 (b) Cone excitations projected onto AMA receptive fields.
 (c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
-The relative RMSE of estimation is 9.3\% for linear regression and 1.6\% for the AMA-based estimator.
+The relative RMSE of estimation is 9.3\% for linear regression and 1.2\% for the AMA-based estimator.
 (d) The contrast normalized cone excitations projected along the first two AMA receptive fields.
@@
 Although S cone signals do not contribute directly to luminance, for natural spectra S cone signals are correlated with
-those of L and M cones (REFS), so that S cone information can contribute to task performance.
-%% DHB: Cite [1] Burton, G.J. & Moorehead, I.R. 1987 Color and spatial structure in natural images. Applied Optics 26, 157-170.
-% Benson, N.C., Manning, J.R. & Brainard, D.H. 2014 Unsupervised learning of cone spectral classes from natural images. PLoS Comput Biol 10, e1003652.
+those of L and M cones \cite{burton1987color, benson2014unsupervised}, so that S cone information can contribute to task performance.
 
@@
 \subsection{Summary}
-
 In this paper, we studied luminance constancy using naturalistic images.
@@
 Here we used labeled images rendered from virtual scene descriptions. 
-There are many advantages to using rendered images (REF).
-One advantage is that they allow us to work with large numbers of labeled images where object reflectance is precisely known at each pixel.
+There are many advantages to using rendered images \cite{Butler:ECCV:2012}.
+One advantage is that they allow us to work with large number of labeled images where object reflectance is precisely known at each pixel.
 A second advantage is that we can control the variation in distinct scene factors that might affect the difficulty of the estimation problem.
@@
 of the illumination.
-% @inproceedings{Butler:ECCV:2012,
-%title = {A naturalistic open source movie for optical flow evaluation},
-%author = {Butler, D. J. and Wulff, J. and Stanley, G. B. and Black, M. J.},
-%booktitle = {European Conf. on Computer Vision (ECCV)},
-%editor = {{A. Fitzgibbon et al. (Eds.)}},
-%publisher = {Springer-Verlag},
-%series = {Part IV, LNCS 7577},
-%month = oct,
-%pages = {611--625},
-%year = {2012}
-%}
+
 There are also disadvantages associated with using rendered images. 

### 2018-06-27 Draft5/draft5.tex
edits in condition 3

@@
     \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
-The relative RMSE is 24.0\%  for linear regression and 13.1\% for AMA.
+The relative RMSE is 23.9\%  for linear regression and 12.6\% for AMA.
 (b) Contrast normalized cone excitations for the training set projected onto the first two AMA receptive fields.
@@
 The number of receptive fields used was varied between 1 and 6.
-(b) Same data as in a, but plotted as a function of number of receptive fields.
+(b) Same data as in panel a, but plotted as a function of number of receptive fields.
 Performance converges around 3 RFs.}
@@
 
-Our rendering software allows us to compare the effect of background surface reflectances on target object LRV with and without simulation of secondary reflections of light from one object onto another
+Our rendering software allows us to compare the effect of background surface reflectances on target object LRV with and without simulation of secondary reflections of light from one object onto another.
 Such secondary reflections were simulated for our primary results.
@@
 Figure~\ref{fig:case3RFs} shows the first three receptive fields learned for Condition 3.
-The first and third of these are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
+These are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
 Additionally, the cone excitations at the target have opposite sign compared to background object locations.
@@
 Indeed, aspects of the training image spatial structure can be seen in the RFs.
-The second receptive field weights the S cones most heavily.
-Although S cone signals do not contribute directly to luminance, for natural spectra S cone signals are correlated with
-those of L and M cones \cite{burton1987color, benson2014unsupervised}, so that S cone information can contribute to task performance.
+% The second receptive field weights the S cones most heavily.
+% Although S cone signals do not contribute directly to luminance, for natural spectra S cone signals are correlated with
+% those of L and M cones \cite{burton1987color, benson2014unsupervised}, so that S cone information can contribute to task performance.
 

### 2018-06-28 Draft5/draft5.tex
Finalizing

@@
 (b) Same data as in panel a, but plotted as a function of number of receptive fields.
-Performance converges around 3 RFs.}
+Performance converges around 3 RFs.
+The error bars in each panel show +/- 1 SEM, with the variation taken across multiple runs with different sets if starting points for the numerical search used in our implementation of AMA.
+}
  \label{fig:RMSEvsRF}
 \end{figure}
+
+Figure~\ref{fig:case3RFs} shows the first three receptive fields learned for Condition 3.
+The first two are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
+In contrast to the Condition 1 RFs, there is also systematic contribution of cone excitations from background object locations, with both positive and negative
+contributions from background objects.
+The specific geometry of the receptive fields, however, should not be taken to be a general feature of the human visual system,
+as the particular RF geometry arises partly as a consequence of the fixed scene geometry used in the training set.
+Indeed, aspects of the training image spatial structure can be seen in the RFs.
+The third receptive field for Condition 3 places weight on the S cone excitations. 
+Although S cone signals do not contribute directly to luminance, for natural spectra S cone signals are correlated with
+those of L and M cones \cite{burton1987color, benson2014unsupervised}, so that S cone information can contribute to task performance.
+Finally, we note that there is some run-to-run variation in the structure of the optimal receptive fields that depends on the set of randomly-chosen starting
+points used for the numerical search used in our implementation of AMA.
+This variation also suggests that one should not over interpret details of the structure of the receptive fields.
+Such run-to-run RF variation leads only to very small changes in estimation error (see error bars in Figure~\ref{fig:RMSEvsRF}).
 
@@
 which in turn affects the normalized contrast representation of the target.
-
-Figure~\ref{fig:case3RFs} shows the first three receptive fields learned for Condition 3.
-These are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted. 
-Additionally, the cone excitations at the target have opposite sign compared to background object locations.
-The specific geometry of the receptive fields, however, should not be taken to be a general feature of the human visual system,
-as the particular RF geometry arises partly as a consequence of the fixed scene geometry used in the training set.
-Indeed, aspects of the training image spatial structure can be seen in the RFs.
-% The second receptive field weights the S cones most heavily.
-% Although S cone signals do not contribute directly to luminance, for natural spectra S cone signals are correlated with
-% those of L and M cones \cite{burton1987color, benson2014unsupervised}, so that S cone information can contribute to task performance.
 
@@
 
+\section{Acknowledgments} \label{Acknowledgments}
+
+Supported by RO1 EY100106 (DHB), Simons Foundation Collaboration on the Global Brain Grant 324759 (DHB) and the University of Pennsylvania Computational Neuroscience Initiative (VS).
+Prelminary versions of this work were presented at the Computational Cognitive Neuroscience Conference (2017) and the Annual Meeting of the Society for Neuroscience (2017).
+
 \bibliography{references}

### 2018-06-28 Draft5/draft5.tex
frustating citation edits

--- 2018-06-27 Draft5/draft5.tex
@@
 There are a few databases consisting of images of posed scenes where surface reflectances of individual objects have been measured (\citeNP{funt1988color,ciurea2003large}), but these databases are not large enough to drive supervised learning.
-Finally, recent work has applied crowd-sourcing techniques to annotate natural images with surface reflectance descriptors \cite{kovacs17shading}.
+Finally, recent work has applied crowd-sourcing techniques to annotate natural images with surface reflectance descriptors \cite{bell2014intrinsic}.
 
@@
 (b) Same data as in panel a, but plotted as a function of number of receptive fields.
-Performance converges around 3 RFs.}
+Performance converges around 3 RFs.
+The error bars in each panel show +/- 1 SEM, with the variation taken across multiple runs with different random initializations for the numerical search used in our implementation of AMA.}
  \label{fig:RMSEvsRF}
 \end{figure}
+
+Figure~\ref{fig:case3RFs} shows the first three receptive fields learned for Condition 3.
+The first two are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted.
+In contrast to the Condition 1 RFs, there is also systematic contribution of cone excitations from background object locations, with both positive and negative contributions from background objects. 
+The specific geometry of the receptive fields, however, should not be taken to be a strict prediction for receptive fields in the human visual system, as the particular RF geometry arises partly as a consequence of the fixed scene geometry used in the training set.
+Indeed, aspects of spatial structure of the training images can be seen in the RFs. 
+Also, the third receptive field for Condition 3 places weight on the S cone excitations.
+Although S cone signals do not contribute directly to luminance,  S cone responses are correlated with
+L and M cone responses to natural spectra \cite{burton1987color, benson2014unsupervised}.
+Information from the S cones can therefore contribute usefully to performance in the task. 
+Finally, we note that there is some run-to-run variation in the structure of the optimal receptive fields that depends on the random initialization of the numerical search used in our implementation of AMA.
+(The cost landscape is not convex so local minima are possible.) 
+However, such run-to-run RF variation leads only to very small changes in estimation error (see error bars in Figure~\ref{fig:RMSEvsRF}). 
+Furthermore, even if the order varies somewhat, the same set of RFs tends to be learned.
 
@@
 
+\section{Acknowledgments} \label{Acknowledgments}
+
+Supported by startup funds from the University of Pennsylvania (JB), NIH grant R01 EY028571 from the National Eye Institute and the Office of Behavioral and Social Science Research (JB), NIH grant RO1 EY100106 (DHB) from the National Eye Institute, Simons Foundation Collaboration on the Global Brain Grant 324759 (DHB), and the University of Pennsylvania Computational Neuroscience Initiative (VS).
+Preliminary versions of this work were presented at the Computational Cognitive Neuroscience Conference (2017) and the Annual Meeting of the Society for Neuroscience (2017).
+
 \bibliography{references}

### 2018-08-17 Draft6/appendix.tex
reviewer comments

--- 2018-06-18 Draft5/appendix.tex
@@
 \section{Illumination Spectra}
-Denote the $i$'th spectrum in the Granada dataset as $I^G_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset. 
+Denote the $i$'th spectrum in the Granada dataset as $I^{\rm G}_i(\lambda)$, where $\{i \in [1,M]\}$ and $M$ is the total number of spectra in the dataset. 
 Since the measured spectra vary over several orders of magnitude in overall intensity, we normalize each spectrum by dividing it by its mean power to obtain what we refer to as rescaled spectra:
 \begin{align}
-I_i^s(\lambda) = \frac{I^G_i(\lambda)}{\int d\lambda I^G_i(\lambda)}.
+I_i^{\rm S}(\lambda) = \frac{I^{\rm G}_i(\lambda)}{\int d\lambda I^{\rm G}_i(\lambda)}.
 \end{align}
@@
 
-The rescaled spectra $I_i^s(\lambda)$ were mean centered for PCA by subtracting out the mean ($\bar{I}^{s}(\lambda)$),  over all rescaled spectra in the dataset, 
+The rescaled spectra $I_i^{\rm S}(\lambda)$ were mean centered for PCA by subtracting out the mean ($\bar{I}^{\rm S}(\lambda)$),  over all rescaled spectra in the dataset, 
 \begin{align}
-\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^s(\lambda)}.
+\bar{I}^{s}(\lambda) = \frac{1}{M}\sum_i{I_i^{\rm S}(\lambda)}.
 \end{align} 
-The mean centered dataset, $I_i^{MC}(\lambda) = I_{s}(\lambda) - \bar{I}_{s}(\lambda)$
+The mean centered dataset, $I_i^{\rm MC}(\lambda) = I_{i}^{\rm S}(\lambda) - \bar{I}^{\rm S}(\lambda)$
 was decomposed as:
 \begin{align}
-I_i^{MC}(\lambda) = \sum_j w_{ij}\hat{{\bf e}}_j^{PCA},
+I_i^{\rm MC}(\lambda) = \sum_j w_{ij} e_j^{\rm PCA}(\lambda),
 \end{align}
-where the $\hat{{\bf e}}_j^{PCA}$ are the PCA basis vectors obtained using
-singular value decomposition (SVD) applied to $I_i^{MC}(\lambda)$, 
-and $w_{ij}$ are the weights obtained by projecting each of $I_i^{MC}(\lambda)$ onto the basis vectors $\hat{{\bf e}}_j^{PCA}$ $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$.
+where the $e_j^{\rm PCA}(\lambda)$ are the PCA basis vectors obtained using
+singular value decomposition (SVD) applied to $I_i^{\rm MC}(\lambda)$, 
+and $w_{ij}$ are the weights obtained by projecting each of $I_i^{\rm MC}(\lambda)$ onto the basis vectors $e_j^{\rm PCA}(\lambda)$ $\left( w_{ij} = I_i^{\rm MC}(\lambda)\cdot e_j^{\rm PCA}(\lambda)\right)$.
 We used the basis vectors corresponding to
@@
 For the rescaled Granada dataset, these six  eigenvalues account for more than $90\%$ of the variance.
-%% DHB: Just before Eqn 3, there is an I_sub_s that should be I_sub_i_sup_s.
-%% DHB: The switch from function to vector notation with the e_hat_sub_j_sup_PCA doesn't really make sense - you can't have a lambda on the left of the equals without a lambda on the right.
-% I'd switch the e_hat's to be non-bolded functions of lamba throughout, I think.  Same under development for surface reflectance model.
-
-%% DHB.  I deleted the summary here, seemed completely redundant with the quite short description above.
 
@@
 \end{align}
-The corresponding spectrum is generated from these weights as $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right)$.
+The corresponding spectrum is generated from these weights as $\left( \sum_j \tilde{w}_{ij} e_j^{\rm PCA}(\lambda) +  \bar{I}^{\rm S} (\lambda)\right)$.
 This spectrum can sometimes have values that are less than zero. 
 In such cases, the weights are discarded and a new draw obtained, until
-the condition $\left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right) > 0$, is satisfied for all $\lambda$.
+the condition $\left( \sum_j \tilde{w}_{ij} e_j^{\rm PCA}(\lambda)+  \bar{I}^{\rm S} (\lambda)\right) > 0$, is satisfied for all $\lambda$.
 The random illuminant spectrum is
 \begin{align}
-\tilde{I}_i(\lambda) = \left( \sum_j \tilde{w}_{ij} \hat{{\bf e}}_j^{PCA} +  \bar{I}_{s} (\lambda)\right).
+\tilde{I}_i(\lambda) = \left( \sum_j \tilde{w}_{ij} e_j^{\rm PCA}(\lambda) +  \bar{I}^{\rm S} (\lambda)\right).
 \end{align}
@@
 \begin{align}
-R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; {\bf \hat{e}}_j^{\rm PCA}},
+R_i^{\rm MC}(\lambda) = \sum_j{w_{ij} \; e_j^{\rm PCA}(\lambda)},
 \end{align} 
-where ${\bf \hat{e}}_j^{\rm PCA}$ are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
-and $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the basis vectors ${\bf \hat{e}}_j^{\rm PCA}$ 
-$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot {\bf \hat{e}}_j^{\rm PCA}\right)$. 
+where $e_j^{\rm PCA}(\lambda)$ are PCA basis vectors obtained using SVD applied to $R_i^{\rm MC}(\lambda)$
+and $w_{ij}$ are the weights obtained by projecting each of $R_i^{\rm MC}(\lambda)$ onto the basis vectors $e_j^{\rm PCA}(\lambda)$ 
+$\left( w_{ij} = R_i^{\rm MC}(\lambda)\cdot e_j^{\rm PCA}(\lambda)\right)$. 
 We used the basis vectors corresponding to the largest six SVD eigenvalues, which account for
@@
 and covariance $\Sigma_{jj'} = \frac{1}{M} \sum_i \left(w_{ij} -\bar{w}_j\right)\left(w_{ij'} -\bar{w}_{j'}\right) $. 
-If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda)<1\right) $ at every $\lambda$, the randomly generated reflectance spectrum is given as:
+If the randomly sampled weights satisfy the condition $\left( 0 < \sum_j \tilde{w}_{ij}e_j^{\rm PCA}(\lambda) + \bar{R}(\lambda)<1\right) $ at every $\lambda$, the randomly generated reflectance spectrum is given as:
 \begin{align}
-\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}{\bf \hat{e}}_j^{\rm PCA} + \bar{R}(\lambda).
+\tilde{R}_i(\lambda) =\sum_j \tilde{w}_{ij}e_j^{\rm PCA}(\lambda) + \bar{R}(\lambda).
 \end{align}

### 2018-08-17 Draft6/draft6.tex
reviewer comments

--- 2018-06-28 Draft5/draft5.tex
@@
 As a consequence, color constancy will be affected both by variation in the illumination and by variation in the surface reflectance of other objects in the scene.
-Color constancy algorithms should therefore be evaluated with respect to variation in both of these factors \cite{BrainardWandellRetinex,BrainardFreeman}.
+Color constancy algorithms should therefore be evaluated with respect to variation in both of these factors \cite{brainard1986analysis,BrainardFreeman}.
 

### 2018-08-28 Draft6/appendix.tex
added figure to appendix

@@
 
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.4 \textwidth}
+	\caption{Cone excitations}
+	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_a.pdf}
+	\label{fig:case1RFs}
+    \end{subfigure}   
+    \begin{subfigure}[b]{0.4 \textwidth}
+	\caption{Normalized contrast}
+	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_b.pdf}
+	\label{fig:case1RFs}
+    \end{subfigure}   
+    \caption{{\bf Condition 2 receptive fields:} The first three AMA receptive fields learnt on (a) Cone excitations (b) Normalized contrast.}
+\label{fig:Condition1}
+\end{figure}
+
 \bibliography{references}

### 2018-08-29 Revision1/draft6.tex
Rename directory.

--- 2018-08-17 Draft6/draft6.tex
@@
  {}
- {Department of Psychology, University of Pennsylvania, PA, USA}
+ {Department of sychology, University of Pennsylvania, PA, USA}
  {}{brainard@psych.upenn.edu}
@@
 
+The computational problem of color constancy may be framed as how to obtain stable descriptions of the spectral surface reflectance functions of the objects in a scene.
 Early work on computational color constancy considered a simplified imaging model where scenes consisted of multiple flat matte objects and a single spatially diffuse illuminant \cite{LandRetinex,Buchsbaum80,MaloneyWandell86}.

### 2018-08-29 Revision1/draft6.tex
JDB updates to response to reviewer doc.
Some accompanying changes to manuscript as well.

@@
 The LRV is a measure of the overall amount of light reflected by a surface \cite{astm1121477}.
-Estimating the LRV from a surface reflectance function proceeds in two steps.
+Defining the LRV from a surface reflectance function requires two steps.
 First, one computes the luminance of the light that would be reflected from the surface under a reference illuminant.
@@
 Sometimes LRVs are expressed as a percentage.
-Here we express LRVs as proportions, so that they take on values between 0 and 1.
+Here we express LRVs as proportions, so that they take on values between 0.0 and 1.0.
+An LRV of 0.0 means that none of the light from the reference illuminant is reflected from the surface.
+An LRV of 1.0 means that all of the light from the reference illuminant is reflected from the surface.
 
@@
 We applied accuracy maximization analysis (AMA) to learn the optimal receptive fields for estimating LRV,
-and evaluated the performance obtained when the responses of these receptive fields are optimally decoded.
+and evaluated performance when the responses of these receptive fields are optimally decoded.
 
@@
 
-In our implementation of AMA, we explored both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
+In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
 Poisson-like noise with a fano factor of 1.3).
@@
 Our rendering software allows us to compare the effect of background surface reflectances on target object LRV with and without simulation of secondary reflections of light from one object onto another.
-Such secondary reflections were simulated for our primary results.
-When we turn off this feature of the rendering, we find (data not shown) that 
-that the secondary reflections have minimal effect on LRV estimation:
-the estimates without secondary reflections were similar to those with reflections.
-This suggests that the primary source of the estimation error in Condition 3 is caused by image-to-image variation in the reflectance of the background objects,
-which in turn affects the normalized contrast representation of the target.
+These secondary reflections were included in the dataset from which we report our primary results. 
+When we turn off this feature of the rendering, we find (data not shown) that LRV estimation performance is essentially unchanged. 
+Estimates with and without secondary reflections are very similar.
+This result suggests that the primary source of the estimation error in Condition 3 is caused by image-to-image variation in the reflectance of the background objects.
 

### 2018-08-29 Revision1/Revision1.tex
edits, diff, renames

--- 2018-08-29 Revision1/draft6.tex
@@
 \DeclareMathOperator*{\argmin}{arg\,min}
-
+\usepackage{lineno}
+\linenumbers
 \begin{document}
@@
  {}
- {Department of sychology, University of Pennsylvania, PA, USA}
+ {Department of Psychology, University of Pennsylvania, PA, USA}
  {}{brainard@psych.upenn.edu}
@@
 
-We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of a target object's surface reflectance function.
+We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of a target object's surface reflectance function\footnote{We distinguish luminance constancy and LRV from lightness constancy and albedo, respectively, as the latter terms refer to achromatic stimuli.}.
 The LRV is a measure of the overall amount of light reflected by a surface \cite{astm1121477}.
@@
 We used one fixed base scene and inserted a spherical target object of fixed size into this scene.
+All surfaces in the scene model were matte and did not have specularities.
 We generated three distinct datasets, which we refer to as Conditions 1-3 (Fig.~\ref{fig:studiedCases}). These are described below.
@@
 The LRV values were equally spaced between 0.2 and 0.6.
+More than 90\% of the surface reflectance spectra (generated as described below) fell within this range.
 For each LRV value, we generated a different relative target object surface reflectance for each scene. 
@@
 We inserted one additional spherical light source into the scene.
+In condition 2 and 3, the overall intensity of the three light source illumination spectra were equal, while their relative shape varied.
+The overall intensity varied from scene to scene.
 The position and size of the inserted object, the inserted light source, and the viewpoint on the scene were held fixed across all 
@@
 In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
-Poisson-like noise with a fano factor of 1.3).
+Poisson-like noise with a fano factor of 1.3 \citeNP{geisler1997visual}).
 Training with both cost functions yielded similar estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
@@
 of the image data; that is, the naive model always estimated the LRV to be equal to 0.4.
+
+\subsubsection*{Quantifying estimation performance}
+We quantified the performance of AMA and the baseline methods at estimating LRV through relative root mean squared error (relative RMSE).
+Relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
+The mean is taken over all stimuli in the test set.
 
@@
 \caption{{\bf Summary of luminance constancy performance:} Relative RMSE estimation error for each method and condition.
-Relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
-The mean is taken over all stimuli in the test set.
 The dotted line represents the relative RMSE for a naive method that estimates the LRV of each image as the mean LRV over the images in the set (LRV = 0.4).}
@@
 of the illumination.
+Similarly, while the scenes rendered for this work were matte, 
+we could also introduce specularity and study interaction of its effect on luminance constancy.
 
@@
 In natural scenes, however, there are other sources of variation that add additional richness and make the problem more difficult to solve.
-These include variation in non-spectral properties of objects and lighting in the scene, including object texture, material, and shape as well as lighting geometry. 
+These include variation in non-spectral properties of objects and lighting in the scene, including object texture, material, specularity, and shape as well as lighting geometry. 
 The methods we developed here may be generalized to study the effects of variation in these factors.

### 2018-09-06 Revision1/Revision1.tex
added few citations
edited comments

@@
 
-\DeclareMathOperator*{\argmin}{arg\,min}
 \usepackage{lineno}
@@
 The ability of a visual system to compute a representation of object color that is stable against variation in object-extrinsic factors is called color constancy. 
-Although human color constancy is not perfect, it is often very good \cite{FosterColorConstancy, BrainardColorConstancy}.
+A well-studied special case of color constancy is when the stimuli are restricted to be achromatic. 
+This special case is called lightness constancy \cite{gilchrist2006seeing}. 
+Although human lightness and color constancy are not perfect, they are often very good \cite{FosterColorConstancy, BrainardColorConstancy,adelson2000,kingdom2011lightness}.
 
@@
 
-We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of a target object's surface reflectance function\footnote{We distinguish luminance constancy and LRV from lightness constancy and albedo, respectively, as the latter terms refer to achromatic stimuli.}.
-The LRV is a measure of the overall amount of light reflected by a surface \cite{astm1121477}.
-Defining the LRV from a surface reflectance function requires two steps.
+We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of a target object's surface reflectance function\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic.
+This condition does not apply to our work - we consider full spectral variation in the stimuli.
+We chose the term luminance constancy to denote the generalization from achromatic stimuli, while at the same time acknowledging that we are not studying the full problem of color constancy but rather the estimation of a luminance-based summary of surface spectral reflectance.}.
+The LRV is a measure of the overall amount of light reflected by a surface reflectance of the reference illuminant itself\footnote{LRV is related to albedo, but the concept of albedo does not incorporate the human luminosity function.
+It is also related to Munsell Value, but Munsell Value is defined with respect to a somewhat obsolete standard illuminant (CIE Illuminant C).} \cite{astm1121477}.
+Obtaining the LRV from a surface reflectance function requires two steps.
 First, one computes the luminance of the light that would be reflected from the surface under a reference illuminant.
@@
 All surfaces in the scene model were matte and did not have specularities.
+There were multiple light sources in the scene, and the rendering process simulated shadows as well as mutual reflection of light between nearby surfaces.
 We generated three distinct datasets, which we refer to as Conditions 1-3 (Fig.~\ref{fig:studiedCases}). These are described below.
@@
 
-We focussed our analysis on image regions local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
+We focused our analysis on image regions local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
 The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally. 
 In primary visual cortex, foveal receptive fields have a maximum spatial extent of approximately 1 degree of visual angle \cite{gattass1981visual, gattass1988visuotopic}. 
+We sought to understand how well responses from AMA-learned receptive fields at a similar scale could be used to achieve luminance constancy.
 
-We modeled a visual system having typical optical blurring (including axial chromatic aberration)\cite{marimont1994matching}, and typical spatial sampling with an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
-The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
+We modeled a visual system having typical optical blurring (including axial chromatic aberration, \citeNP{marimont1994matching}), and typical spatial sampling with an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
+The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 (1523 L cones, 801 M cones, 277 S cones) and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
 Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec. 
@@
 
-In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) and assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
+In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) to evaluate the accuracy of the AMA estimates of LRV.
+We also assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
 Poisson-like noise with a fano factor of 1.3  \citeNP{geisler1997visual}).
@@
 The diagonal identity line (dotted blue) indicates veridical estimation.
-The standard deviations are too small to be visible.
+The filled regions representing standard deviations are too small to be visible.
 Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.7\% for linear regression and 1.1\%  for AMA-based estimation.
@@
 The response clusters are approximated by a multivariate Gaussians whose means and covariances are represented by the ellipses shown in the figure.
-(c) The first three AMA receptive fields.}
+(c) The first three AMA receptive fields.
+These are specified over the same 1 x 1 degree patch as the stimuli.}
 \label{fig:Condition1}
@@
 
-Unfortunately, such datasets are not readily available for studying correlates of object surface reflectance.
-To obtain ground truth information about the reflectance of objects in a natural image, it is necessary to make 
-an independent measurement of the of the reflectance function of each object (or of the illumination impinging on each object).
-Although this can be done at a small number of image locations by inserting discretely spaced reflectance standards into the scene, 
-interpolating to locations between such standards requires strong assumptions that are often unjustified in real scenes.
+Large datasets of natural or posed scenes with ground truth information about illuminant and object surface reflectance are difficult to obtain, as independent measurement of illuminant and surface properties at each image location is painstaking.
+That noted, there are useful databases for evaluation of color constancy algorithms that provide information about illumination and/or surface reflectance (e.g., \citeNP{barnard2002data,ciurea2003large, cheng2014illuminant,NascimentoFoster2016}; see \href{http://colorconstancy.com}{http://colorconstancy.com}).
+Often the illumination is estimated through placement of a reflectance standard at a few image locations to allow estimation of the illumination impinging at those locations.
+This estimate is then interpolated/extrapolated across the image, an approximation whose quality is not yet well understood.
 
 Here we used labeled images rendered from virtual scene descriptions. 
+A similar approach has been used previously to study the perception of lightness and specularity \cite{toscani2013optimal,wiebel2015statistical,toscani2017lightness}; our work adds to this approach through the addition of variation in color.
 There are many advantages to using rendered images \cite{Butler:ECCV:2012}. 
@@
 Here, we exploited this flexibility to quantify how variation in the relative reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation.
-We also exploited our use of rendered images to explore how the presence or absence of secondary reflections from background objects affected estimation
-of target object LRV.
+We also exploited our use of rendered images to explore how the presence or absence of secondary reflections from background objects affected estimation of target object LRV.
 This type of question cannot be addressed using real images.
 The basic approach we use here can be extended to include parametric control over the amount of variation of different factors.
-For example, we could systematically vary the variances of the distribution over the weights that control the relative spectrum
-of the illumination.
-Similarly, while the scenes rendered for this work were matte, 
-we could also introduce specularity and study interaction of its effect on luminance constancy.
+For example, we could systematically vary the variances of the distribution over the weights that control the relative spectrum of the illumination.
 
@@
 Although we believe these datasets provide reasonable approximations of the statistical variation in reflectance and illumination spectra, they can be extended and improved.
-For example, the surface reflectance datasets capture regularities in naturally occurring reflectance functions, but the surfaces in the datasets were not sampled to reflect the relative frequency of different reflectance spectra in natural viewing.
-In addition, the dataset of illuminations does not include the artificial illuminations that we now live much of our lives under.
-Future work with virtual image datasets will benefit from targeted efforts to characterize additional features of the natural statistics of the scene components that are varied.
+For example, there are additional datasets of measured surface reflectances that could be incorporated into future analyses, with some of these focused on the reflectance of objects (e.g.
+fruit) that are thought to be important for the evolution of primate color vision (e.g., \citeNP{sumner2000catarrhine, regan2001fruits, barnard2002data, ennis2018hyperspectral}).
+Another issue, not addressed by these datasets, is the relative frequency of occcurance of different reflectance spectra in natural viewing.
+\citeNP{attewell2007distribution} made a systematic survey, and found that a beta distribution provided a better description of the distribution of an LRV-like quantity than did a truncated Gaussian.
+Generalizing these measurements to better characterize the distribution of full reflectance functions remains an interesting goal.
 
 \subsection{Future Directions}
-In the work presented here, we studied computational luminance constancy in virtual scenes with naturalistic spectral variation in light sources and in surface reflectance functions. 
-It is natural to begin with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem.
-In natural scenes, however, there are other sources of variation that add additional richness and make the problem more difficult to solve.
-These include variation in non-spectral properties of objects and lighting in the scene, including object texture, material, specularity, and shape as well as lighting geometry. 
+
+In the work presented here, we studied computational luminance constancy in virtual scenes with naturalistic spectral variation in light sources and in surface reflectance functions, with only matte surfaces in the scenes.
+It is natural to by studying with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem.
+In natural scenes, however, there are other sources of variation that add additional richness.
+These include variation in non-spectral properties of objects and lighting in the scene, including object texture, material (e.g.
+specularity), and shape as well as lighting geometry.
 The methods we developed here may be generalized to study the effects of variation in these factors.
-One could incorporate these other sources of variation into the generation of the scenes and again learn estimators from the corresponding labeled images. 
+That is, one could incorporate these other sources of variation into the generation of the scenes and again learn estimators from the corresponding labeled images.
 A challenge for this approach will be to thoughtfully control the increase in problem complexity, both to keep compute time feasible and to ensure that it is possible to extract meaningful insight from the results.
+Extending the work to include variation of material may provide insights not only about luminance constancy but also for computations that relate to material perception (see \citeNP{fleming2017material}); extending the work to include variation in object shape and lighting geometry may clarify the role of object boundaries versus object interiors for providing information that supports perception of object color and lightness (see \citeNP{land1971lightness, rudd2016retinex}).
+We also note that there is a literature on how increasing stimulus complexity along the various lines listed above affects human color and lightness perception (e.g.
+\citeNP{beck1964effect,yang2001illuminant, yang2002stereo,todd2004lightness, snyder2005illumination, boyaci2003effect, xiao2008surface, kingdom2011lightness, xiao2012color, anderson2015perceptual, toscani2017lightness}), as well as the computational problem of color and lightness constancy (e.g.
+\citeNP{lee1986method, d1986mechanisms, funt1988color, tominaga1989standard, barron2012color, barron2015convolutional, finlayson2018colour}).
+
+We studied the information available for LRV estimation using a 1°x1° image patch.
+As noted above this choice of size was motivated in part to use a spatial scale roughly commensurate with the scale of information integration in early visual cortex.
+Our general methods could be extended to study larger regions, and doing so would quantify the value of spatially remote information for luminance constancy.
 
@@
 \end{document}
-
-%% DHB: There are all sorts of problems with the citations.
-% a) Journal and book case should be (e.g.) "Journal of Vision" not (e.g.) "Journal of vision".  This is botched in many places.
-% b) In some cases we appear to be citing things that are one page long.  I think many of these are papers that have more than
-% one page, and those instances should be fixed.  In other cases, we may be citing abstracts and I would prefer not to cite those
-% unless there is a real need to.  
-% c) Sometimes page numbers are given by (e.g.) "112-173", other by (e.g.) ", yet others by (e.g.) "(pp. 112-173)".  Pick one style
-% and stick with it.
-% d) There are other glitches.  For example, the title of Goncalves and Welchman starts "?what not?".  Proofread carefully and fix up.

### 2018-09-08 Revision1/Revision1.tex
edited citations

@@
 To understand the computations that support stable color perception, 
-we study how estimating a target object's light reflectance value (LRV; a measure of the light reflected from the object under a standard illuminant) depends on variation in key properties of naturalistic scenes.
-Specifically, we study how variation in target object reflectance, illumination spectra, and the reflectance of background objects in a scene impact estimation of a target object's LRV. 
+we study how estimating a target object's luminous reflectance factor (LRF; a measure of the light reflected from the object under a standard illuminant) depends on variation in key properties of naturalistic scenes.
+Specifically, we study how variation in target object reflectance, illumination spectra, and the reflectance of background objects in a scene impact estimation of a target object's LRF. 
 To do this, we applied supervised statistical learning methods to the simulated excitations of human cone photoreceptors, obtained from labeled naturalistic images.
@@
 of natural spectral variation.
-Optimally decoding target object LRV from the responses of a small learned set of task-specific linear receptive fields that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRV.
+Optimally decoding target object LRF from the responses of a small learned set of task-specific linear receptive fields that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRF.
 Our work provides a framework for evaluating how different sources of scene variability limit performance on luminance constancy.}
@@
 (b) Images of a sphere under a fixed illuminant.  
-Down each column, the sphere's light reflectance value (LRV) varies, but its relative reflectance spectrum (i.e. its spectral shape) is held fixed.
-Across each row, the relative reflectance spectrum varies, but the LRV is held fixed.
-We cast the problem of computational luminance constancy to be that of estimating the LRV of a target object from the image, across variation in other scene factors. 
+Down each column, the sphere's luminous reflectance factor (LRF) varies, but its relative reflectance spectrum (i.e. its spectral shape) is held fixed.
+Across each row, the relative reflectance spectrum varies, but the LRF is held fixed.
+We cast the problem of computational luminance constancy to be that of estimating the LRF of a target object from the image, across variation in other scene factors. 
 Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
@@
 
-We define the computational problem of luminance constancy as that of estimating the light reflectance value (LRV) of a target object's surface reflectance function\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic.
+We define the computational problem of luminance constancy as that of estimating the luminous reflectance factor (LRF) of a target object's surface reflectance function\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic.
 This condition does not apply to our work - we consider full spectral variation in the stimuli.
 We chose the term luminance constancy to denote the generalization from achromatic stimuli, while at the same time acknowledging that we are not studying the full problem of color constancy but rather the estimation of a luminance-based summary of surface spectral reflectance.}.
-The LRV is a measure of the overall amount of light reflected by a surface reflectance of the reference illuminant itself\footnote{LRV is related to albedo, but the concept of albedo does not incorporate the human luminosity function.
-It is also related to Munsell Value, but Munsell Value is defined with respect to a somewhat obsolete standard illuminant (CIE Illuminant C).} \cite{astm1121477}.
-Obtaining the LRV from a surface reflectance function requires two steps.
+The LRF is a measure of the overall amount of light reflected by a surface luminance of the reference illuminant itself\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.} \cite{astm1121477}.
+Obtaining the LRF from a known surface reflectance function requires two steps.
 First, one computes the luminance of the light that would be reflected from the surface under a reference illuminant.
@@
 Here we use CIE daylight D65 as the reference illuminant and the CIE 1931 photopic luminosity function to compute luminance \cite{CIE86}.
-Sometimes LRVs are expressed as a percentage.
-Here we express LRVs as proportions, so that they take on values between 0.0 and 1.0. 
-An LRV of 0.0 means that none of the light from the reference illuminant is reflected from the surface. 
-An LRV of 1.0 means that all of the light from the reference illuminant is reflected from the surface.
+Sometimes LRFs are expressed as a percentage.
+Here we express LRFs as proportions, so that they take on values between 0.0 and 1.0. 
+An LRF of 0.0 means that none of the light from the reference illuminant is reflected from the surface. 
+An LRF of 1.0 means that all of the light from the reference illuminant is reflected from the surface.
 
@@
 that allows us to construct models of naturalistic scenes, with key scene factors under programmatic control.
-The package builds on the RenderToolbox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}) \cite{heasly2014rendertoolbox3},
+The package builds on the RenderToolbox4 package (\href{http://rendertoolbox.org}{http://rendertoolbox.org}; \citeNP{heasly2014rendertoolbox3}),
 and harnesses the open-source computer graphics renderer Mitsuba (\href{https://www.mitsuba-renderer.org}{https://www.mitsuba-renderer.org}, 
@@
 We generated three distinct datasets, which we refer to as Conditions 1-3 (Fig.~\ref{fig:studiedCases}). These are described below.
-Across these datasets the luminance constancy problem (i.e. estimating the target object LRV)
+Across these datasets the luminance constancy problem (i.e. estimating the target object LRF)
 becomes progressively more difficult.
@@
 
-In Condition 1, the relative reflectance spectrum of the target object was the only source of scene variation other than the target object LRV.
+In Condition 1, the relative reflectance spectrum of the target object was the only source of scene variation other than the target object LRF.
 The reflectance spectra of the background objects and the spectral power distribution of the light sources were held fixed.
@@
 Finally, in Condition 3 three distinct scene factors--target object relative reflectance spectrum, spectral power distribution of the light sources, and reflectance spectra of the background objects
---varied in addition to the target object LRV.
-The datasets for Conditions 1 and 2 consisted of 1000 scenes and images, 100 for each of 10 target object LRV values. 
-The dataset for Condition 3 consisted of 3000 scenes and images, 300 each for the 10 target LRV values.
-The LRV values were equally spaced between 0.2 and 0.6.
+--varied in addition to the target object LRF.
+The datasets for Conditions 1 and 2 consisted of 1000 scenes and images, 100 for each of 10 target object LRF values. 
+The dataset for Condition 3 consisted of 3000 scenes and images, 300 each for the 10 target LRF values.
+The LRF values were equally spaced between 0.2 and 0.6.
 More than 90\% of the surface reflectance spectra (generated as described below) fell within this range.
-For each LRV value, we generated a different relative target object surface reflectance for each scene. 
+For each LRF value, we generated a different relative target object surface reflectance for each scene. 
 % Figure 4
@@
 (c) Condition 3: variable target object relative reflectance spectrum, variable light source spectra, variable background object spectra.
-The spheres in each row of each panel have the same LRV, while the spheres in each column of each panel have the same relative surface reflectance spectrum.
+The spheres in each row of each panel have the same LRF, while the spheres in each column of each panel have the same relative surface reflectance spectrum.
 Across panels a-c, spheres in corresponding locations have the same surface reflectance.
@@
 To generate random reflectance spectra, we employed principles similar to those used to generate random illuminant spectral power distributions.
-We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data) (Figure~\ref{fig:reflectanceSpectra}).
+We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data; Figure~\ref{fig:reflectanceSpectra}).
 We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
@@
 \caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
-The figure shows 10 random samples at 10 equally spaced LRV levels in the range [0.2, 0.6].
-Each row contains 10 random samples of reflectance spectra generated at the LRV shown on the left.}
+The figure shows 10 random samples at 10 equally spaced LRF levels in the range [0.2, 0.6].
+Each row contains 10 random samples of reflectance spectra generated at the LRF shown on the left.}
 \label{fig:targetSwatches}
@@
 
-To generate the target object reflectance at a particular LRV, the sampled reflectance spectrum was 
-scaled such that its LRV had the desired value (see appendix).
-Figure \ref{fig:targetSwatches} shows color renderings of target reflectance spectra under CIE illuminant D65, for the evenly spaced LRV values we studied.
+To generate the target object reflectance at a particular LRF, the sampled reflectance spectrum was 
+scaled such that its LRF had the desired value (see appendix).
+Figure \ref{fig:targetSwatches} shows color renderings of target reflectance spectra under CIE illuminant D65, for the evenly spaced LRF values we studied.
 
@@
 We modeled a visual system having typical optical blurring (including axial chromatic aberration, \citeNP{marimont1994matching}), and typical spatial sampling with an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
-The cone mosaic contained L:M:S cones in the ratio 0.6:0.3:0.1 (1523 L cones, 801 M cones, 277 S cones) and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
+The cone mosaic contained L:M:S cones in approximately the ratio 0.6:0.3:0.1 (1523 L cones, 801 M cones, 277 S cones) and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
 Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec. 
@@
 \subsection{Computational luminance constancy} \label{method:SupervisedLearning}
-We used our datasets to determine how well target object LRV can be estimated from cone excitations and from normalized cone contrasts.
+We used our datasets to determine how well target object LRF can be estimated from cone excitations and from normalized cone contrasts.
 Studying both representations allows us to understand how early contrast coding and normalization affect luminance constancy.
-We applied accuracy maximization analysis (AMA) to learn the optimal receptive fields for estimating LRV,
+We applied accuracy maximization analysis (AMA) to learn the optimal receptive fields for estimating LRF,
 and evaluated performance when the responses of these receptive fields are optimally decoded.
@@
 
-In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) to evaluate the accuracy of the AMA estimates of LRV.
+In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) to evaluate the accuracy of the AMA estimates of LRF.
 We also assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
@@
 Training with both cost functions yielded similar estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
-We chose this cost function because the estimates it yields at the boundaries of the LRV range are less biased than those obtained with the mean squared error cost function.
+We chose this cost function because the estimates it yields at the boundaries of the LRF range are less biased than those obtained with the mean squared error cost function.
 
@@
 Specifically, the decoder used to learn the receptive fields requires the response mean and response variance of each receptive field to every labelled stimulus in the training set \cite{geisler2009optimal,burge2017accuracy}.
-To proceed, first we use the AMA receptive fields and the training dataset to find the distributions of the receptive field responses conditional on the target object LRVs.
+To proceed, first we use the AMA receptive fields and the training dataset to find the distributions of the receptive field responses conditional on the target object LRFs.
 Then, we model these conditional response distributions with multivariate Gaussians.
-To estimate the LRV of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRV values, given the receptive field responses.
-The optimal estimate is the LRV value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
+To estimate the LRF of the target object in a test image, we use Bayes' rule together with the Gaussian conditional distributions and a uniform prior to obtain the posterior distribution over LRF values, given the receptive field responses.
+The optimal estimate is the LRF value that minimizes the expected value of the cost function, where the expectation is taken over the posterior.
 For the results we report, we again used the Kullback-Leibler divergence cost function.
@@
 For our primary results, estimation was based on six receptive fields.
+The AMA analysis package is available at: \href{LuminanceConstancyAmaAnalysis
+}{https://github.com/vijaysoophie/LuminanceConstancyAmaAnalysis}.
 
@@
 To provide baselines for evaluation of the estimation method described above, we used linear regression.
-First, we solved for the weights on the average L, M and S cone excitations corresponding to the target object that best predicted the target LRV values.
+First, we solved for the weights on the average L, M and S cone excitations corresponding to the target object that best predicted the target LRF values.
 We took the average cone responses from a $3 \times 3$ pixel region at the center of the target object.
@@
 through their effect on the contrast normalized responses at the center of the target object. 
-We also evaluated the performance of a naive model that uses the mean LRV value in the training set as the estimate, irrespective
-of the image data; that is, the naive model always estimated the LRV to be equal to 0.4.
+We also evaluated the performance of a naive model that uses the mean LRF value in the training set as the estimate, irrespective
+of the image data; that is, the naive model always estimated the LRF to be equal to 0.4.
 
 \subsubsection*{Quantifying estimation performance}
-We quantified the performance of AMA and the baseline methods at estimating LRV through relative root mean squared error (relative RMSE).
-Relative RMSE is the square root of the mean of the squared difference between the estimated and true LRV divided by the true LRV.
+We quantified the performance of AMA and the baseline methods at estimating LRF through relative root mean squared error (relative RMSE).
+Relative RMSE is the square root of the mean of the squared difference between the estimated and true LRF divided by the true LRF.
 The mean is taken over all stimuli in the test set.
@@
             \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{LRV estimates}
+        \caption{LRF estimates}
         \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
@@
     \end{subfigure}   
-    \caption{{\bf Condition 1 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression on the cone excitations.
+    \caption{{\bf Condition 1 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression on the cone excitations.
 Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation.
@@
 (b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields.
-Each cluster of responses represents the image patches associated with a particular LRV.
+Each cluster of responses represents the image patches associated with a particular LRF.
 The response clusters are approximated by a multivariate Gaussians whose means and covariances are represented by the ellipses shown in the figure.
@@
 \subsection{Condition 1}
-In Condition 1, only the LRV and the relative reflectance spectrum of the target object vary across scenes.
-We used accuracy maximization analysis (AMA) to learn a set of linear receptive fields that are optimal for estimating target LRV from the cone excitations in this condition. 
+In Condition 1, only the LRF and the relative reflectance spectrum of the target object vary across scenes.
+We used accuracy maximization analysis (AMA) to learn a set of linear receptive fields that are optimal for estimating target LRF from the cone excitations in this condition. 
 Decoding performance is shown in Figure~\ref{fig:case1Estimates}. 
@@
 Both methods are trained on 90\% of the images in the dataset and tested on the remaining 10\%.
-The LRV estimates obtained for both methods are essentially perfect.
+The LRF estimates obtained for both methods are essentially perfect.
 
@@
 Each individual point represents the receptive field responses to an individual image patch and
-is color coded by target object LRV.
-The responses segregate according to the target LRV, which supports the high level 
-of estimation performance shown in Figure~\ref{fig:case1Estimates}.
+is color coded by target object LRF.
+The responses segregate according to the target LRF, which supports the high level 
+of estimation performance shown in Figure~\ref{fig:case1Estimates}.LRF
 Note that even the responses of the first RF separate well (vertical lines would accurately
-distinguish the LRVs), so that that one receptive field is sufficient for accurately performing the task.
+distinguish the LRFs), so that that one receptive field is sufficient for accurately performing the task.
 
@@
     \begin{subfigure}[b]{0.22\textwidth}   
-        \caption{\centering{LRV estimates} \newline\centering{(Excitations)}}
+        \caption{\centering{LRF estimates} \newline\centering{(Excitations)}}
         \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_a.pdf}
@@
             \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{\centering{LRV estimates}  \newline \centering{(Normalized contrast)}}
+        \caption{\centering{LRF estimates}  \newline \centering{(Normalized contrast)}}
         \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_c.pdf}
@@
     \end{subfigure}
-    \caption{{\bf Condition 2 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
+    \caption{{\bf Condition 2 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
 The relative RMSE is high (41.4\% for linear regression and 26.4\% for AMA-based estimation).
 (b) Cone excitations projected onto AMA receptive fields.
-(c) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
+(c) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
 The relative RMSE of estimation is 9.3\% for linear regression and 1.2\% for the AMA-based estimator.
@@
 The receptive fields were learned using AMA and the contrast normalized cone excitations.
-For Condition 2, the response corresponding to individual image patches at each LRV level separates much better when the input is the contrast normalized cone excitations than when the input is the raw cone excitations.}
+For Condition 2, the response corresponding to individual image patches at each LRF level separates much better when the input is the contrast normalized cone excitations than when the input is the raw cone excitations.}
 \label{fig:Condition2}
@@
 Condition 2 includes variation in the spectral power distribution of the light sources, in addition to the variation present in Condition 1. 
-This illumination variation makes the task more difficult because it causes variation in the cone excitations that is not due to target object LRV. 
+This illumination variation makes the task more difficult because it causes variation in the cone excitations that is not due to target object LRF. 
 We learned AMA receptive fields on the cone excitations to the images in this new condition, and again evaluated decoding performance (Fig.~\ref{fig:Condition2}(a,b)). 
 Performance is poor.
-Indeed, the estimates deviate considerably from the true LRV, as seen by the fact that the mean estimate
+Indeed, the estimates deviate considerably from the true LRF, as seen by the fact that the mean estimate
 (red line) does not lie on the positive diagonal and by the fact that there is large estimation variability for each
-value of the true LRV.
+value of the true LRF.
 For this case, linear regression also does poorly. Indeed, the linear regression estimates are essentially the same as would be obtained
-by simply guessing the mean LRV of the training set (0.4).
+by simply guessing the mean LRF of the training set (0.4).
 
@@
             \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{LRV estimates}
+        \caption{LRF estimates}
         \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure12/Figure12_a.pdf}
@@
     \end{subfigure}
-    \caption{{\bf Condition 3 results:} (a) Mean estimated LRV $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
+    \caption{{\bf Condition 3 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
 The relative RMSE is 23.9\%  for linear regression and 12.6\% for AMA.
@@
 We again trained and evaluated AMA for labeled image patches, using the contrast normalized cone excitations.
-The LRV estimates obtained via AMA are more variable and less accurate than for the previous conditions (Figure~\ref{fig:case3Estimates}).
-Nevertheless, the estimates provide useful information about the target LRV.
-Indeed, the estimates track the true LRV on average, as seen by the fact that the mean estimate (red line) lies along the positive diagonal.
+The LRF estimates obtained via AMA are more variable and less accurate than for the previous conditions (Figure~\ref{fig:case3Estimates}).
+Nevertheless, the estimates provide useful information about the target LRF.
+Indeed, the estimates track the true LRF on average, as seen by the fact that the mean estimate (red line) lies along the positive diagonal.
 The increased estimation variability is indicated by the increased width of the shaded red region, relative to its width for the results of Condition 1 and 2.
@@
 Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA receptive fields to the training stimuli.
-Although the responses vary systematically with target object LRV, there is considerable overlap in the receptive field responses for stimuli having different LRV values.
+Although the responses vary systematically with target object LRF, there is considerable overlap in the receptive field responses for stimuli having different LRF values.
 This overlap is due to the combined effect of the variation in the illumination and background surface spectra.
@@
 
-Our rendering software allows us to compare the effect of background surface reflectances on target object LRV with and without simulation of secondary reflections of light from one object onto another.
+Our rendering software allows us to compare the effect of background surface reflectances on target object LRF with and without simulation of secondary reflections of light from one object onto another.
 These secondary reflections were included in the dataset from which we report our primary results. 
-When we turn off this feature of the rendering, we find (data not shown) that LRV estimation performance is essentially unchanged. 
+When we turn off this feature of the rendering, we find (data not shown) that LRF estimation performance is essentially unchanged. 
 Estimates with and without secondary reflections are very similar. 
@@
 We used a software pipeline, which was developed for this work, to render datasets of multispectral images from scene descriptions.
-Because we rendered the images, we could label each image in the dataset by the light reflectance value (LRV) of the target object.
-We used the labeled datasets to learn estimators for the target object LRV.
-Across scenes, we varied the LRV of the target object, the relative reflectance spectrum of the target object, 
+Because we rendered the images, we could label each image in the dataset by the luminous reflectance factor (LRF) of the target object.
+We used the labeled datasets to learn estimators for the target object LRF.
+Across scenes, we varied the LRF of the target object, the relative reflectance spectrum of the target object, 
 the spectral power distributions of the light sources, and the reflectance spectra of the background objects in the scene.
@@
 \caption{{\bf Summary of luminance constancy performance:} Relative RMSE estimation error for each method and condition.
-The dotted line represents the relative RMSE for a naive method that estimates the LRV of each image as the mean LRV over the images in the set (LRV = 0.4).}
+The dotted line represents the relative RMSE for a naive method that estimates the LRF of each image as the mean LRF over the images in the set (LRF = 0.4).}
  \label{fig:barGraphs}
@@
 most realistic condition that we tested.
-In this case, AMA-based estimates of target object LRV are, on average, within 13\% (relative RMSE) of the true value.
+In this case, AMA-based estimates of target object LRF are, on average, within 13\% (relative RMSE) of the true value.
 Introducing variation in the surface reflectance spectra of the background objects makes 
@@
 Here we used labeled images rendered from virtual scene descriptions. 
-A similar approach has been used previously to study the perception of lightness and specularity \cite{toscani2013optimal,wiebel2015statistical,toscani2017lightness}; our work adds to this approach through the addition of variation in color.
+A similar approach has been used previously to study the perception of lightness and specularity \cite{toscani2013optimal,wiebel2015statistical,toscani2017lightness}. 
+Our work adds to this approach through the addition of variation in color. 
 There are many advantages to using rendered images \cite{Butler:ECCV:2012}. 
@@
 This flexibility allows the study of individual scene factors as well as their combined effects.
-Here, we exploited this flexibility to quantify how variation in the relative reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRV estimation.
-We also exploited our use of rendered images to explore how the presence or absence of secondary reflections from background objects affected estimation of target object LRV.
+Here, we exploited this flexibility to quantify how variation in the relative reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRF estimation.
+We also exploited our use of rendered images to explore how the presence or absence of secondary reflections from background objects affected estimation of target object LRF.
 This type of question cannot be addressed using real images.
@@
 Another issue, not addressed by these datasets, is the relative frequency of occcurance of different reflectance spectra in natural viewing.
-\citeNP{attewell2007distribution} made a systematic survey, and found that a beta distribution provided a better description of the distribution of an LRV-like quantity than did a truncated Gaussian.
+\citeNP{attewell2007distribution} made a systematic survey, and found that a beta distribution provided a better description of the distribution of an LRF-like quantity than did a truncated Gaussian.
 Generalizing these measurements to better characterize the distribution of full reflectance functions remains an interesting goal.
@@
 
-We studied the information available for LRV estimation using a 1°x1° image patch.
+We studied the information available for LRF estimation using a 1°x1° image patch.
 As noted above this choice of size was motivated in part to use a spatial scale roughly commensurate with the scale of information integration in early visual cortex.
@@
 An important motivation for studying the computational problem of luminance constancy is to gain insight about human vision.
-The approach we developed can be used to make predictions of how humans would perform in a psychophysical task that probes the visual representation of object LRV.
-For example, one could study discrimination thresholds for target LRV using the stimuli that were generated with the methods used here.
-More specifically, we could ask how LRV discrimination thresholds are impacted by spectral variation in the illuminant, the background objects, and in the target object itself.
-Comparing human thresholds with the precision of AMA-based estimates would then allow inferences about how well human observers make use of the information available in the images for performing LRV discrimination.
+The approach we developed can be used to make predictions of how humans would perform in a psychophysical task that probes the visual representation of object LRF.
+For example, one could study discrimination thresholds for target LRF using the stimuli that were generated with the methods used here.
+More specifically, we could ask how LRF discrimination thresholds are impacted by spectral variation in the illuminant, the background objects, and in the target object itself.
+Comparing human thresholds with the precision of AMA-based estimates would then allow inferences about how well human observers make use of the information available in the images for performing LRF discrimination.
 We think experiments and analyses along these lines represent an important future direction.

### 2018-09-08 codeForFigures/codeToMakeFigures/reflectanceGeneration.m
edited the TO DO list

@@ -93,6 +93,7 @@ ylimit=get(gca,'ylim');
 yticks([0:0.2:1]);
 yticklabels({'0.0' '0.2' '0.4' '0.6' '0.8' '1.0'});
 save2pdf('Figure7_a.pdf',fig,600);
+save2eps('Figure7_a.eps',fig,600);
 close;
 
 fig=figure;
@@ -112,6 +113,7 @@ set(gca,'FontSize',FS);
 % title('Statistical model','FontSize',FS);
 set(gca,'FontSize',FS);
 save2pdf('Figure7_b.pdf',fig,600);
+save2eps('Figure7_b.eps',fig,600);
 close;
 
 %%
@@ -128,6 +130,7 @@ set(gca,'FontSize',FS);
 legend({'Natural reflectance','Random samples'}, 'Location', 'southeast','FontSize',20);
 axis square;
 save2pdf('Figure7_c.pdf',fig,600);
+save2eps('Figure7_c.eps',fig,600);
 close;
 
 %%
@@ -142,6 +145,7 @@ ylim([0.5 10.5]);
 set(gca,'FontSize',FS);
 axis off;
 save2pdf('Figure7_d.pdf',fig,600);
+save2eps('Figure7_d.eps',fig,600);
 close;
 %%
 fig=figure;
@@ -161,7 +165,7 @@ yticks([1:10]);
 xticks([1:10]);
 currentaxes.YTickLabel={'0.20' '0.24' '0.29' '0.33' '0.38' '0.42' '0.47' '0.51' '0.56' '0.60'};
 xlabel('Sample Index');
-ylabel('LRV');
+ylabel('LRF');
 
 % save2pdf('Figure8.pdf',fig,600);
 %close;

### 2018-09-08 Revision1/Revision1.tex
edited the TO DO list
AMA link

@@
 For our primary results, estimation was based on six receptive fields.
-The AMA analysis package is available at: \href{LuminanceConstancyAmaAnalysis
-}{https://github.com/vijaysoophie/LuminanceConstancyAmaAnalysis}.
+The AMA analysis package is available at: \href{https://github.com/BrainardLab/LuminanceConstancyAmaAnalysis}{https://github.com/BrainardLab/LuminanceConstancyAmaAnalysis}.
 

### 2018-09-13 Revision1/Revision1.tex
edited a word in future directions

@@
 In the work presented here, we studied computational luminance constancy in virtual scenes with naturalistic spectral variation in light sources and in surface reflectance functions, with only matte surfaces in the scenes.
-It is natural to by studying with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem.
+It is natural to start with spectral variation, because this variation is at the heart of what makes luminance constancy a rich computational problem.
 In natural scenes, however, there are other sources of variation that add additional richness.

### 2018-09-14 Revision1/Revision1.tex
jdb updates

@@
 To do this, we applied supervised statistical learning methods to the simulated excitations of human cone photoreceptors, obtained from labeled naturalistic images.
-The naturalistic images were rendered with computer graphics, with the underlying scene descriptions generated stochastically using statistical models
-of natural spectral variation.
+The naturalistic images were rendered with computer graphics.
+The illumination spectra of the light sources and the reflectance spectra of the surfaces in the scene were generated using statistical models of natural spectral variation.
 Optimally decoding target object LRF from the responses of a small learned set of task-specific linear receptive fields that operate on a contrast representation of the cone excitations yields estimates that are within 13\% of the correct LRF.
@@
 This condition does not apply to our work - we consider full spectral variation in the stimuli.
-We chose the term luminance constancy to denote the generalization from achromatic stimuli, while at the same time acknowledging that we are not studying the full problem of color constancy but rather the estimation of a luminance-based summary of surface spectral reflectance.}.
-The LRF is a measure of the overall amount of light reflected by a surface luminance of the reference illuminant itself\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.} \cite{astm1121477}.
+We chose the term luminance constancy to denote the generalization from achromatic stimuli.
+At the same time, we acknowledge that we are not studying the full problem of color constancy.
+Rather, we are studying the estimation of a luminance-based summary of surface spectral reflectance.}.
+The LRF is a measure of the overall amount of light reflected by a surface relative to the reference illuminant itself\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.} \cite{astm1121477}.
 Obtaining the LRF from a known surface reflectance function requires two steps.
@@
 Second, we use a model of the early visual system to compute the responses of the cone photoreceptor mosaic to the labeled images.
-Third, we apply AMA to the cone responses, as well as to a contrast normalized version of the cone responses, to learn task-optimal receptive fields (RFs).
-Fourth, we evaluate how well the responses of the RFs may be decoded to achieve luminance constancy.
+Third, we learn the receptive fields (RFs) that extract the most useful information from the cone responses for the task.
+Fourth, we evaluate how well the responses of the receptive fields may be decoded to achieve luminance constancy.
 
@@
 Our statistical model approximates normalized spectra from the Granada dataset using the first 6 principle components of the normalized measurements from that dataset.
-The variation in the weights on these components is then modeled with a 6-dimensional Gaussian.
-The mean and covariance matrix of the Gaussian match the sample mean and covariance of the weights \cite{BrainardFreeman}. 
-To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components to generate the corresponding spectrum.
+The distribution of weights on these components is approximated with a 6-dimensional Gaussian, where the mean and covariance matrix match the sample mean and covariance of the weights \cite{BrainardFreeman}.
+To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components.
 Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
@@
 Cone excitations were taken as the number of photopigment isomerizations, assuming an integration time of 100 msec. 
-% JDB: DO WE HAVE REFERENCE INDICATING THAT 100ms IS A REASONABLE INTEGRATION TIME TO ASSUME?
-% LEAVING HANGING FOR NOW.  MAYBE LOOK AT COHN TWO-FLASH DETECTION EXPERIMENTS OR TEMPORAL
-% SUMMATION.
 The Poisson nature of the photopigment isomerization was also included \cite{hecht1942energy}. 
@@
 In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) to evaluate the accuracy of the AMA estimates of LRF.
-We also assumed that receptive field responses were corrupted by scaled Gaussian noise (i.e.
-Poisson-like noise with a fano factor of 1.3  \citeNP{geisler1997visual}).
 Training with both cost functions yielded similar estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
@@
 \subsubsection*{Quantifying estimation performance}
-We quantified the performance of AMA and the baseline methods at estimating LRF through relative root mean squared error (relative RMSE).
+We quantified the performance of AMA and the baseline methods at estimating LRF with relative root mean squared error (relative RMSE).
 Relative RMSE is the square root of the mean of the squared difference between the estimated and true LRF divided by the true LRF.
@@
 of estimation performance shown in Figure~\ref{fig:case1Estimates}.LRF
-Note that even the responses of the first RF separate well (vertical lines would accurately
+Note that even the responses of the first receptive field separate well (vertical lines would accurately
 distinguish the LRFs), so that that one receptive field is sufficient for accurately performing the task.
@@
 direct contribution.
-The first three RFs are similar to each other, reflecting the fact that here the main benefit
+The first three receptive fields are similar to each other, reflecting the fact that here the main benefit
 of multiple receptive fields is to reduce the impact of noise on estimation performance.
@@
 (b) Same data as in panel a, but plotted as a function of number of receptive fields.
-Performance converges around 3 RFs.
+Performance converges around three receptive fields (RFs).
 The error bars in each panel show +/- 1 SEM, with the variation taken across multiple runs with different random initializations for the numerical search used in our implementation of AMA.}
@@
 
-Figure~\ref{fig:case3RFs} shows the first three receptive fields learned for Condition 3.
+Figure~\ref{fig:case3RFs} shows the first three receptive fields (RFs) learned for Condition 3.
 The first two are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted.
-In contrast to the Condition 1 RFs, there is also systematic contribution of cone excitations from background object locations, with both positive and negative contributions from background objects. 
-The specific geometry of the receptive fields, however, should not be taken to be a strict prediction for receptive fields in the human visual system, as the particular RF geometry arises partly as a consequence of the fixed scene geometry used in the training set.
-Indeed, aspects of spatial structure of the training images can be seen in the RFs. 
+In contrast to the Condition 1 receptive fields, there is also systematic contribution of cone excitations from background object locations, with both positive and negative contributions from background objects.
+The specific geometry of the receptive fields, however, should not be taken to be a strict prediction for receptive fields in the human visual system, as the particular receptive field geometry arises partly as a consequence of the fixed scene geometry used in the training set.
+Indeed, aspects of spatial structure of the training images can be seen in the receptive fields. 
 Also, the third receptive field for Condition 3 places weight on the S cone excitations.
@@
 (The cost landscape is not convex so local minima are possible.) 
-However, such run-to-run RF variation leads only to very small changes in estimation error (see error bars in Figure~\ref{fig:RMSEvsRF}). 
-Furthermore, even if the order varies somewhat, the same set of RFs tends to be learned.
+However, such run-to-run receptive field variation leads only to very small changes in estimation error (see error bars in Figure~\ref{fig:RMSEvsRF}). 
+Furthermore, even if the order varies somewhat, the same set of receptive fields tends to be learned.
 
@@
 Large datasets of natural or posed scenes with ground truth information about illuminant and object surface reflectance are difficult to obtain, as independent measurement of illuminant and surface properties at each image location is painstaking.
-That noted, there are useful databases for evaluation of color constancy algorithms that provide information about illumination and/or surface reflectance (e.g., \citeNP{barnard2002data,ciurea2003large, cheng2014illuminant,NascimentoFoster2016}; see \href{http://colorconstancy.com}{http://colorconstancy.com}).
+That noted, there are databases for evaluation of color constancy algorithms that provide information about illumination and/or surface reflectance (e.g., \citeNP{barnard2002data,ciurea2003large, cheng2014illuminant,NascimentoFoster2016}; see \href{http://colorconstancy.com}{http://colorconstancy.com}).
 Often the illumination is estimated through placement of a reflectance standard at a few image locations to allow estimation of the illumination impinging at those locations.
-This estimate is then interpolated/extrapolated across the image, an approximation whose quality is not yet well understood.
+These illumination estimates are then interpolated/extrapolated across the image.
+However, the quality of this approximation cannot typically be evaluated.
 
-Here we used labeled images rendered from virtual scene descriptions. 
+Here we used labeled images rendered from descriptions of virtual scenes. 
 A similar approach has been used previously to study the perception of lightness and specularity \cite{toscani2013optimal,wiebel2015statistical,toscani2017lightness}. 
-Our work adds to this approach through the addition of variation in color. 
+Our work adds to this approach by introducing color variation. 
 There are many advantages to using rendered images \cite{Butler:ECCV:2012}. 
@@
 Although we believe these datasets provide reasonable approximations of the statistical variation in reflectance and illumination spectra, they can be extended and improved.
-For example, there are additional datasets of measured surface reflectances that could be incorporated into future analyses, with some of these focused on the reflectance of objects (e.g.
+For example, there are additional datasets of measured surface reflectances that could be incorporated into future analyses.
+Some of these datasets focused on the reflectance of objects (e.g.
 fruit) that are thought to be important for the evolution of primate color vision (e.g., \citeNP{sumner2000catarrhine, regan2001fruits, barnard2002data, ennis2018hyperspectral}).
-Another issue, not addressed by these datasets, is the relative frequency of occcurance of different reflectance spectra in natural viewing.
-\citeNP{attewell2007distribution} made a systematic survey, and found that a beta distribution provided a better description of the distribution of an LRF-like quantity than did a truncated Gaussian.
+Another issue, not addressed by these datasets, is relative frequency of different surface reflectivities in natural viewing.
+\citeNP{attewell2007distribution} performed a systematic survey, and report the distribution of an LRF-like quantity in natural scenes.
 Generalizing these measurements to better characterize the distribution of full reflectance functions remains an interesting goal.
@@
 In natural scenes, however, there are other sources of variation that add additional richness.
-These include variation in non-spectral properties of objects and lighting in the scene, including object texture, material (e.g.
-specularity), and shape as well as lighting geometry.
+These include variation in non-spectral properties of lighting and objects in the scene.
+Examples include lighting geometry, object texture, object material (e.g.
+specularity), and object shape.
 The methods we developed here may be generalized to study the effects of variation in these factors.
-That is, one could incorporate these other sources of variation into the generation of the scenes and again learn estimators from the corresponding labeled images.
+That is, one could incorporate these factors into the generation of the scenes and again learn estimators from the corresponding labeled images.
 A challenge for this approach will be to thoughtfully control the increase in problem complexity, both to keep compute time feasible and to ensure that it is possible to extract meaningful insight from the results.
-Extending the work to include variation of material may provide insights not only about luminance constancy but also for computations that relate to material perception (see \citeNP{fleming2017material}); extending the work to include variation in object shape and lighting geometry may clarify the role of object boundaries versus object interiors for providing information that supports perception of object color and lightness (see \citeNP{land1971lightness, rudd2016retinex}).
+Extending the work to include variation of material may provide insights not only about luminance constancy but also for computations that relate to material perception (see \citeNP{fleming2017material}).
+Extending the work to include variation in object shape and lighting geometry may clarify the role of object boundaries versus object interiors for providing information that supports perception of object color and lightness (see \citeNP{land1971lightness, rudd2016retinex}).
 We also note that there is a literature on how increasing stimulus complexity along the various lines listed above affects human color and lightness perception (e.g.
-\citeNP{beck1964effect,yang2001illuminant, yang2002stereo,todd2004lightness, snyder2005illumination, boyaci2003effect, xiao2008surface, kingdom2011lightness, xiao2012color, anderson2015perceptual, toscani2017lightness}), as well as the computational problem of color and lightness constancy (e.g.
+\citeNP{beck1964effect,yang2001illuminant, yang2002stereo,todd2004lightness, snyder2005illumination, boyaci2003effect, xiao2008surface, kingdom2011lightness, xiao2012color, anderson2015perceptual, toscani2017lightness}), and the computational problem of color and lightness constancy (e.g.
 \citeNP{lee1986method, d1986mechanisms, funt1988color, tominaga1989standard, barron2012color, barron2015convolutional, finlayson2018colour}).

### 2018-09-17 Revision1/Revision1.tex
final edits

@@
 \usepackage{comment}
+\usepackage{gensymb}
 
@@
 
-We define the computational problem of luminance constancy as that of estimating the luminous reflectance factor (LRF) of a target object's surface reflectance function\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic.
+We define the computational problem of luminance constancy\footnote{In the literature, the term lightness constancy is generally used to denote color constancy for the special case when stimuli are restricted to be achromatic.
 This condition does not apply to our work - we consider full spectral variation in the stimuli.
 We chose the term luminance constancy to denote the generalization from achromatic stimuli.
-At the same time, we acknowledge that we are not studying the full problem of color constancy.
-Rather, we are studying the estimation of a luminance-based summary of surface spectral reflectance.}.
+At the same time we acknowledge that we are not studying the full problem of color constancy.
+Rather, we are studying the estimation of a luminance-based summary of surface spectral reflectance.} as that of estimating the luminous reflectance factor (LRF) of a target object's surface reflectance function.
 The LRF is a measure of the overall amount of light reflected by a surface relative to the reference illuminant itself\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.} \cite{astm1121477}.
@@
 Sometimes LRFs are expressed as a percentage.
-Here we express LRFs as proportions, so that they take on values between 0.0 and 1.0. 
-An LRF of 0.0 means that none of the light from the reference illuminant is reflected from the surface. 
-An LRF of 1.0 means that all of the light from the reference illuminant is reflected from the surface.
+Here we express LRFs as proportions, so that they take on values between 0 and 1. 
+An LRF of 0 means that none of the light from the reference illuminant is reflected from the surface. 
+An LRF of 1 means that the luminance of the surface reflectance under the reference illuminant is the same as the luminance of a perfect reflector under that same illuminant.
 
@@
 We inserted one additional spherical light source into the scene.
-In condition 2 and 3, the overall intensity of the three light source illumination spectra were equal, while their relative shape varied.
+In Conditions 2 and 3, the overall intensities of the three light source illumination spectra were equal, while their relative shape varied. 
 The overall intensity varied from scene to scene.
@@
 
-We focused our analysis on image regions local to the target by cropping the rendered images to $1 \times 1$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
+We focused our analysis on image regions local to the target by cropping the rendered images to $1\degree \times 1\degree$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
 The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally. 
@@
 In our implementation of AMA, we used both the Kullback-Leibler divergence cost function (corresponding to the maximum a posteriori estimator) and the mean squared error cost function (corresponding to the posterior mean estimator) to evaluate the accuracy of the AMA estimates of LRF.
-Training with both cost functions yielded similar estimation performance; the results reported here are for the Kullback-Leibler divergence cost function.
+Training with both cost functions yielded similar estimation performance; the results reported here are for when the Kullback-Leibler divergence cost function was used in training.
 We chose this cost function because the estimates it yields at the boundaries of the LRF range are less biased than those obtained with the mean squared error cost function.
@@
 Estimates with and without secondary reflections are very similar. 
-This result suggests that the primary source of the estimation error in Condition 3 is caused by image-to-image variation in the reflectance of the background objects.
+This result suggests that the primary source of the estimation error in Condition 3 is caused by direct effects of image-to-image variation in the reflectance of the background objects on the AMA responses.
 
@@
 fruit) that are thought to be important for the evolution of primate color vision (e.g., \citeNP{sumner2000catarrhine, regan2001fruits, barnard2002data, ennis2018hyperspectral}).
-Another issue, not addressed by these datasets, is relative frequency of different surface reflectivities in natural viewing.
+Another issue, not addressed by these datasets, is relative frequency of different surface reflectances in natural viewing.
 \citeNP{attewell2007distribution} performed a systematic survey, and report the distribution of an LRF-like quantity in natural scenes.
@@
 
-We studied the information available for LRF estimation using a 1°x1° image patch.
+We studied the information available for LRF estimation using a $1\degree \times 1 \degree$ image patch.
 As noted above this choice of size was motivated in part to use a spatial scale roughly commensurate with the scale of information integration in early visual cortex.

### 2018-10-20 codeForFigures/codeToMakeFigures/illuminantGeneration.m
converted figures to eps

@@ -102,15 +102,16 @@ yticks([0 0.5 1 1.5 2]);
 yticklabels({'0.0' '0.5' '1.0' '1.5' '2.0'});
 axis square;
 save2pdf('Figure6_a.pdf',fig,1000);
+save2eps('Figure6_a.eps',fig,1000);
 close;
-
+%%
 % Figure 6 b
 fig=figure;
 box on; axis square; hold on;
 set(fig,'Position', [100, 100,550, 500]);
 for ii = 1 : size(newIlluminance,2)
     rescaledFig2 = plot(SToWls(S),newIlluminance(:,ii),'k');
-    rescaledFig2.Color(4)=0.3;
+    rescaledFig2.Color(4)=1;
 end
 ylim([0 2]);
 yticks([0 0.5 1 1.5 2]);
@@ -121,6 +122,7 @@ ylabel('Normalized Irradiance','FontSize',FS)
 set(gca,'FontSize',FS);
 axis square;
 save2pdf('Figure6_b.pdf',fig,600);
+save2eps('Figure6_b.eps',fig,600);
 close;
 
 % Figure 6 c
@@ -140,6 +142,7 @@ legend('Normalized dataset','Random samples','Location', 'northwest');
 set(gca,'FontSize',FS);
 axis square;
 save2pdf('Figure6_c.pdf',fig,600);
+save2eps('Figure6_c.eps',fig,600);
 close;
 
 % Figure 6d
@@ -151,6 +154,7 @@ image(theIlluminationImage);
 set(gca,'FontSize',FS);
 axis square;
 axis off;
-%save2pdf('Figure6_d.pdf',fig,600);
+save2pdf('Figure6_d.pdf',fig,600);
+save2eps('Figure6_d.eps',fig,600);
 % close;
 

### 2018-10-20 codeForFigures/codeToMakeFigures/reflectanceGeneration.m

@@ -81,8 +81,8 @@ set(fig,'Position', [100, 100,550, 500]);
 hold on;
 box on; axis square;
 for ii = 1 : size(sur_all,2)
-    rescaledFig = plot(SToWls(S),sur_all(:,ii),'k');
-    rescaledFig.Color(4)=0.2;
+    rescaledFig = plot(SToWls(S),sur_all(:,ii),'k','linewidth',0.1);
+    rescaledFig.Color(4)=0.6;
 end
 % title('Natural Surface Spectra','FontSize',FSTitle);
 xlabel('Wavelength (nm)','FontSize',FS);
@@ -92,8 +92,8 @@ set(gca,'FontSize',FS);
 ylimit=get(gca,'ylim');
 yticks([0:0.2:1]);
 yticklabels({'0.0' '0.2' '0.4' '0.6' '0.8' '1.0'});
-save2pdf('Figure7_a.pdf',fig,600);
-save2eps('Figure7_a.eps',fig,600);
+save2pdf('Figure7_a.pdf',fig,1000);
+save2eps('Figure7_a.eps',fig,1000);
 close;
 
 fig=figure;
@@ -102,7 +102,7 @@ hold on;
 box on; axis square;
 for ii = 1 : size(newSurfaces,2)
     rescaledFig = plot(SToWls(S),newSurfaces(:,ii),'k');
-    rescaledFig.Color(4)=0.4;
+    rescaledFig.Color(4)=0.8;
 end
 ylim([0 1]);
 yticks([0:0.2:1]);

### 2018-10-21 Production/Production.tex
editing figures for production

--- 2018-09-17 Revision1/Revision1.tex
@@
 
-\usepackage{lineno}
-\linenumbers
+% \usepackage{lineno}
+% \linenumbers
 \begin{document}
@@
 The computational challenge underlying object color perception is that the light reflected from an object depends not just on the object's surface reflectance, but also 
-on object-extrinsic factors such as the scene illumination, the pose of the object, and the viewpoint of the observer in the scene (Fig.~\ref{fig:introSchematic}).
+on object-extrinsic factors such as the scene illumination, the pose of the object, and the viewpoint of the observer in the scene (Fig.~\ref{fig:introFigure}a).
 To compute a perceptual representation of object color that is correlated with the object's physical surface reflectance, the visual system must account for these object-extrinsic factors.
@@
 \centering
-\begin{subfigure}{0.4 \textwidth}
-	\centering
-	\caption{}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
-        \label{fig:introSchematic}
-    \end{subfigure}
-    \begin{subfigure}{0.55 \textwidth}   
-        \caption{}    
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
-        \label{fig:introExampleFigure}
-    \end{subfigure}
-    \label{introFigure}
+%\begin{subfigure}{0.4 \textwidth}
+%	\centering
+%	\caption{}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
+%        \label{fig:introSchematic}
+%    \end{subfigure}
+%    \begin{subfigure}{0.55 \textwidth}   
+%        \caption{}    
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
+%        \label{fig:introExampleFigure}
+%    \end{subfigure}
+\includegraphics[width=\textwidth]{Figure1.eps}    
     \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the scene illumination. 
@@
 Specifically, we study variation in target object relative surface reflectance, variation in illumination spectrum, and variation in the surface reflectance of the other objects in the scene.}
+\label{fig:introFigure}
  \end{figure}
@@
 This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants.
-We tackle the specific problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introExampleFigure}).
+We tackle the specific problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introFigure}b).
 
@@
 \centering
-\begin{subfigure}[b]{0.22 \textwidth}
-        \caption{Library }
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.pdf}
-        \label{fig:baseSceneLibrary}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{Mill}    
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.pdf}
-        \label{fig:baseSceneMill}
-    \end{subfigure}    
-    ~
-    \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{Table-Chairs}    
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.pdf}
-        \label{fig:baseSceneTableChairs}
-    \end{subfigure}
+%\begin{subfigure}[b]{0.22 \textwidth}
+%        \caption{Library }
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.pdf}
+%        \label{fig:baseSceneLibrary}
+%    \end{subfigure}
+%    ~
+%    \begin{subfigure}[b]{0.22 \textwidth}
+%        \caption{Mill}    
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.pdf}
+%        \label{fig:baseSceneMill}
+%    \end{subfigure}    
+%    ~
+%    \begin{subfigure}[b]{0.22 \textwidth}
+%        \caption{Table-Chairs}    
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.pdf}
+%        \label{fig:baseSceneTableChairs}
+%    \end{subfigure}
+\includegraphics[width=\textwidth]{Figure2.eps}
     \caption{{\bf Base scenes.} Each image shows a rendering of one base scene without additional inserted objects.
@@
 The images have been scaled and tone mapped individually for illustrative purposes.}
-\label{fig:baseScenes}. \end{figure}
+\label{fig:baseScenes}
+\end{figure}
 
@@
 \centering
-    \begin{subfigure}[b]{0.14 \textwidth}
-        \caption{Big-ball}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
-        \label{fig:libraryWithBigBall}
-    \end{subfigure}
-     ~ 
-    \begin{subfigure}[b]{0.14 \textwidth}
-        \caption{Xylophone}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
-        \label{fig:libraryWithXylophone}
-    \end{subfigure}
-     ~ 
-    \begin{subfigure}[b]{0.14 \textwidth}
-        \caption{Barrel}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
-        \label{fig:libraryWithBarrel}
-         \end{subfigure}
-    ~
-	\begin{subfigure}[b]{0.14 \textwidth}
-        \caption{Ring toy}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
-        \label{fig:libraryWithRingToy}
-    \end{subfigure}
-        ~
-    	\begin{subfigure}[b]{0.14 \textwidth}
-        \caption{Bottle}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
-        \label{fig:libraryWithChampagneBottle}
-    \end{subfigure}
+%    \begin{subfigure}[b]{0.14 \textwidth}
+%        \caption{Big-ball}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
+%        \label{fig:libraryWithBigBall}
+%    \end{subfigure}
+%     ~ 
+%    \begin{subfigure}[b]{0.14 \textwidth}
+%        \caption{Xylophone}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
+%        \label{fig:libraryWithXylophone}
+%    \end{subfigure}
+%     ~ 
+%    \begin{subfigure}[b]{0.14 \textwidth}
+%        \caption{Barrel}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
+%        \label{fig:libraryWithBarrel}
+%         \end{subfigure}
+%    ~
+%	\begin{subfigure}[b]{0.14 \textwidth}
+%        \caption{Ring toy}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
+%        \label{fig:libraryWithRingToy}
+%    \end{subfigure}
+%        ~
+%    	\begin{subfigure}[b]{0.14 \textwidth}
+%        \caption{Bottle}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
+%        \label{fig:libraryWithChampagneBottle}
+%    \end{subfigure}
+\includegraphics[width=\textwidth]{Figure3.eps}
 \caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
@@
 \begin{figure}
-	\begin{subfigure}{0.18 \textwidth}
-    \centering
-        \caption{Target position}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.pdf}
-        \label{fig:targetPositionVariation}
-    \end{subfigure}
-    ~
-	\begin{subfigure}{0.18 \textwidth}
-    \centering
-        \caption{Target size/pose}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
-        \label{fig:targetSizeOrientation}
-    \end{subfigure}
-~
-\centering
-	\begin{subfigure}{0.18 \textwidth}
-    \centering
-        \caption{Target spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.pdf}
-        \label{fig:targetVariation}
-    \end{subfigure}
-    ~
-    \begin{subfigure}{0.18 \textwidth}
-    \centering
-        \caption{Illumination spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.pdf}
-        \label{fig:illuminationVariation}
-    \end{subfigure}
-          ~  
-    \begin{subfigure}{0.18 \textwidth}
-    \centering
-        \caption{Background spectra}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.pdf}
-        \label{fig:backGroundVariation}
-    \end{subfigure}
-
+%	\begin{subfigure}{0.18 \textwidth}
+%    \centering
+%        \caption{Target position}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.pdf}
+%        \label{fig:targetPositionVariation}
+%    \end{subfigure}
+%    ~
+%	\begin{subfigure}{0.18 \textwidth}
+%    \centering
+%        \caption{Target size/pose}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
+%        \label{fig:targetSizeOrientation}
+%    \end{subfigure}
+%~
+%\centering
+%	\begin{subfigure}{0.18 \textwidth}
+%    \centering
+%        \caption{Target spectra}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.pdf}
+%        \label{fig:targetVariation}
+%    \end{subfigure}
+%    ~
+%    \begin{subfigure}{0.18 \textwidth}
+%    \centering
+%        \caption{Illumination spectra}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.pdf}
+%        \label{fig:illuminationVariation}
+%    \end{subfigure}
+%          ~  
+%    \begin{subfigure}{0.18 \textwidth}
+%    \centering
+%        \caption{Background spectra}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.pdf}
+%        \label{fig:backGroundVariation}
+%    \end{subfigure}
+\includegraphics[width=\textwidth]{Figure4.eps}
     \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e).
@@
 The position and size of the inserted object, the inserted light source, and the viewpoint on the scene were held fixed across all 
-scenes. The geometry is shown in Figure~\ref{fig:3DScene} below.
+scenes. The geometry is shown in Figure~\ref{fig:figure9}a below.
 Surface and illuminant spectra were sampled according to statistical models of naturally occurring spectra.
@@
 \centering
-	\begin{subfigure}{0.33 \textwidth}
-		\caption{Condition 1}
-%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
-		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
- 		\label{fig:backgroundVarying}
-	\end{subfigure}
-	\begin{subfigure}{0.33 \textwidth}
-        \caption{Condition 2}	
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
-        \label{fig:targetIlluminantVarying}
-    \end{subfigure}
-	\begin{subfigure}{0.33 \textwidth}
-	\caption{Condition 3}	
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
-        \label{fig:allSpectraVarying}
-    \end{subfigure}    
+%	\begin{subfigure}{0.33 \textwidth}
+%		\caption{Condition 1}
+%%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
+%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
+% 		\label{fig:backgroundVarying}
+%	\end{subfigure}
+%	\begin{subfigure}{0.33 \textwidth}
+%        \caption{Condition 2}	
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
+%        \label{fig:targetIlluminantVarying}
+%    \end{subfigure}
+%	\begin{subfigure}{0.33 \textwidth}
+%	\caption{Condition 3}	
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
+%        \label{fig:allSpectraVarying}
+%    \end{subfigure}    
+\includegraphics[width=\textwidth]{Figure5.eps}        
     \caption{{\bf Conditions 1-3:} Illustrative images for the three types of spectral variations studied in this paper.
-(a) Condition 1: variable target object relative reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introExampleFigure}).
+(a) Condition 1: variable target object relative reflectance spectrum, fixed light source spectra, fixed background object spectra (same as Fig.~\ref{fig:introFigure}b).
 (b) Condition 2: variable target object relative reflectance spectrum, variable light source spectra, fixed background object spectra.
@@
 \centering
-    \begin{subfigure}[b]{0.24 \textwidth}
-    \centering
-	\caption{Granada dataset}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_a.pdf}
-        \label{fig:granadaData}
-    \end{subfigure}
-	\begin{subfigure}[b]{0.24 \textwidth}
-    \centering
-        \caption{Statistical model}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_b.pdf}
-        \label{fig:illuminantSamples}
-    \end{subfigure}
-      	\begin{subfigure}[b]{0.24 \textwidth}
-    \centering
-        \caption{CIE xy chromaticity}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_c.pdf}
-        \label{fig:xyDiagram}
-        \end{subfigure}
-      	\begin{subfigure}[b]{0.24 \textwidth}
-    \centering
-        \caption{Color swatches}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_d.pdf}
-        \label{fig:sRGBIlluminant}
-    \end{subfigure}
+%    \begin{subfigure}[b]{0.24 \textwidth}
+%    \centering
+%	\caption{Granada dataset}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_a.pdf}
+%        \label{fig:granadaData}
+%    \end{subfigure}
+%	\begin{subfigure}[b]{0.24 \textwidth}
+%    \centering
+%        \caption{Statistical model}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_b.pdf}
+%        \label{fig:illuminantSamples}
+%    \end{subfigure}
+%      	\begin{subfigure}[b]{0.24 \textwidth}
+%    \centering
+%        \caption{CIE xy chromaticity}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_c.pdf}
+%        \label{fig:xyDiagram}
+%        \end{subfigure}
+%      	\begin{subfigure}[b]{0.24 \textwidth}
+%    \centering
+%        \caption{Color swatches}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_d.pdf}
+%        \label{fig:sRGBIlluminant}
+%    \end{subfigure}
+\includegraphics[width=\textwidth]{Figure6.eps}
     \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset.
@@
 To generate a random relative illuminant spectrum, we sample weights randomly from this Gaussian and then perform a weighted sum of the components.
-Figure~\ref{fig:illuminantSamples} illustrates the relative spectra of draws obtained using this procedure.
-Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:xyDiagram} and ~\ref{fig:sRGBIlluminant}.
+Figure~\ref{fig:illuminant}b illustrates the relative spectra of draws obtained using this procedure.
+Chromaticities and rendered color renditions of these draws are shown in Figures~\ref{fig:illuminant}c and ~\ref{fig:illuminant}d.
 Details of the statistical model for illumination are provided in the appendix.
@@
 \centering
-	\begin{subfigure}{0.24 \textwidth}
-    \centering
-            \caption{Munsell and Vrhel dataset}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_a.pdf}
-        \label{fig:reflectanceSpectra}
-    \end{subfigure}
-    \begin{subfigure}{0.24 \textwidth}
-    \centering
-        \caption{Statistical model}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_b.pdf}
-        \label{fig:reflectanceSamples}
-    \end{subfigure}
-    \begin{subfigure}{0.24 \textwidth}
-    \centering
-    \caption{CIE xy chromaticity}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_c.pdf}
-        \label{fig:xyChroReflectance}
-    \end{subfigure}    
-    \centering
-	\begin{subfigure}{0.24 \textwidth}
-    \centering
-        \caption{Color swatches}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_d.pdf}
-        \label{fig:backgroundSwatches}
-    \end{subfigure}
+%	\begin{subfigure}{0.24 \textwidth}
+%    \centering
+%            \caption{Munsell and Vrhel dataset}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_a.pdf}
+%        \label{fig:reflectanceSpectra}
+%    \end{subfigure}
+%    \begin{subfigure}{0.24 \textwidth}
+%    \centering
+%        \caption{Statistical model}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_b.pdf}
+%        \label{fig:reflectanceSamples}
+%    \end{subfigure}
+%    \begin{subfigure}{0.24 \textwidth}
+%    \centering
+%    \caption{CIE xy chromaticity}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_c.pdf}
+%        \label{fig:xyChroReflectance}
+%    \end{subfigure}    
+%    \centering
+%	\begin{subfigure}{0.24 \textwidth}
+%    \centering
+%        \caption{Color swatches}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_d.pdf}
+%        \label{fig:backgroundSwatches}
+%    \end{subfigure}
+    \includegraphics[width=\textwidth]{Figure7.eps}
     \caption{{\bf Statistical model of surface reflectance:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.
@@
 To generate random reflectance spectra, we employed principles similar to those used to generate random illuminant spectral power distributions.
-We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data; Figure~\ref{fig:reflectanceSpectra}).
+We used measurements from the Munsell \cite{kelly1943tristimulus} and Vrhel \cite{vrhel1994measurement} surface reflectance datasets to create a dataset containing 632 reflectance spectra (462 from the Munsell data and 170 from the Vrhel data; Figure~\ref{fig:surfaceReflectanceGeneration}a).
 We resampled the spectra to 31 evenly-spaced wavelengths between 400 nm and 700 nm.
-Figures~\ref{fig:reflectanceSamples},~\ref{fig:xyChroReflectance}, and~\ref{fig:backgroundSwatches} illustrate reflectance sampled obtained using the model. 
+Figures~\ref{fig:surfaceReflectanceGeneration}b,~\ref{fig:surfaceReflectanceGeneration}c, and~\ref{fig:surfaceReflectanceGeneration}d illustrate reflectance sampled obtained using the model. 
 Details of the statistical model for surface reflectance spectra are provided in the appendix.
@@
 \centering
-\includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure8/Figure8.pdf}
+\includegraphics[width=0.3\textwidth]{Figure8.eps}
 \caption{{\bf Target object surface reflectance spectra:} sRGB renditions of the target object surface reflectance rendered under CIE D65 daylight spectrum.
@@
 \centering
-\begin{subfigure}[b]{0.25 \textwidth}
-		\centering
-        \caption{sRGB rendering of a 3D scene}
-                \vspace{1.2mm}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_a.png}
-        \label{fig:3DScene}
-    \end{subfigure}
-    ~ 
-    \begin{subfigure}[b]{0.19 \textwidth}   
-    \hspace{0.1 \textwidth}
-        \caption{Cropped image}
-        \vspace{2.5mm}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_b.png}
-        \label{fig:croppedImage}
-    \end{subfigure}
-    ~ 
-    \begin{subfigure}[b]{0.19 \textwidth}
-    \hspace{0.1 \textwidth}
-        \caption{Retinal image}
-        \vspace{2.5mm}
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_c.png}
-        \label{fig:croppedImageWithMosaic}
-    \end{subfigure}
-    ~
-    \begin{subfigure}[b]{0.205 \textwidth}
-        \caption{Normalized cone contrast}        
-        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_d.png}
-        \label{fig:coneContrast}
-    \end{subfigure}
+%\begin{subfigure}[b]{0.25 \textwidth}
+%		\centering
+%        \caption{sRGB rendering of a 3D scene}
+%                \vspace{1.2mm}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_a.png}
+%        \label{fig:3DScene}
+%    \end{subfigure}
+%    ~ 
+%    \begin{subfigure}[b]{0.19 \textwidth}   
+%    \hspace{0.1 \textwidth}
+%        \caption{Cropped image}
+%        \vspace{2.5mm}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_b.png}
+%        \label{fig:croppedImage}
+%    \end{subfigure}
+%    ~ 
+%    \begin{subfigure}[b]{0.19 \textwidth}
+%    \hspace{0.1 \textwidth}
+%        \caption{Retinal image}
+%        \vspace{2.5mm}
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_c.png}
+%        \label{fig:croppedImageWithMosaic}
+%    \end{subfigure}
+%    ~
+%    \begin{subfigure}[b]{0.205 \textwidth}
+%        \caption{Normalized cone contrast}        
+%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_d.png}
+%        \label{fig:coneContrast}
+%    \end{subfigure}
+    \includegraphics[width=\textwidth]{Figure9.eps}
     \label{fig:sceneWithCroppedImage}
@@
 Finally, the demosaiced images are contrast normalized.}
+\label{fig:figure9}
 \end{figure}
@@
 
-We focused our analysis on image regions local to the target by cropping the rendered images to $1\degree \times 1\degree$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:croppedImage}).
+We focused our analysis on image regions local to the target by cropping the rendered images to $1\degree \times 1\degree$ degrees of visual angle around the target object ($51 \times 51$ pixels; Figure~\ref{fig:figure9}b).
 The local analysis is motivated by the fact that neural receptive fields early in the visual pathways (e.g., retina, primary visual cortex) pool information locally. 
@@
 
-We modeled a visual system having typical optical blurring (including axial chromatic aberration, \citeNP{marimont1994matching}), and typical spatial sampling with an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:croppedImageWithMosaic}).
+We modeled a visual system having typical optical blurring (including axial chromatic aberration, \citeNP{marimont1994matching}), and typical spatial sampling with an interleaved rectangular mosaic of long (L), middle (M)  and short (S) wavelength-sensitive cones (\citeNP{brainard2015color}; Fig.~\ref{fig:figure9}c).
 The cone mosaic contained L:M:S cones in approximately the ratio 0.6:0.3:0.1 (1523 L cones, 801 M cones, 277 S cones) and with spectral sensitivities derived from the CIE physiological standard \cite{CIE86}.
@@
 This modeling was implemented using the software infrastructure provided by ISETBio (\href{https://isetbio.org}{https://isetbio.org}).
-
-%% Details on ISETBIO computations from Nicolas (TEXT IN CAPS IS FROM VIJAY)
-%% Scene: 
-%%- the default mean luminance was set to 200, but there is a key-value param that could have overridden this value. 
-%%  I do not know if this were the case.
-%%
-%% % MEAN LUMINANCE = 0, NO SCALING
-%
-%%- The default FOV was 1 deg, but there is a key-value param that could have overridden this value.
-%%  I do not know if this were the case.
-%%
-%% % HORIZONTAL FOV = 1
-%%
-%%- Distance default is 1 meter, but there is  a key-value param that could have overridden this value.
-%%  I do not know if this were the case.
-%%
-%%% DISTANCE 1M
-%%
-%%Optics: 
-%%- 3 mm pupil, 17 mm focal length, with a spectro-spatial OTF described in  
-%%  (Marimont & Wandell (1994) J. Opt. Soc. Amer. A,  v. 11, p. 3113-3122), 
-%%   which includes axial chromatic aberration. However, there is key-value param o skip the OTF. 
-%%   Not sure if this was used.  It it was used, the optics was set to diffraction limited.
-%%
-%% % SKIP OTF OFF:  'skipOTF', false ...  
-%%
-%%Lens: 
-%%- not sure if the optical density is from Wyszecki&Stiles or from Stockman-Sharpe. 
-%%  The isetbio file commend only says it is from PTB. David do you know, or should I check
-%%  the data?
-%%
-%%Cone Mosaic: 
-%%- rectangular cone mosaic with 0.6:0.3:0.1 LMS densities
-%%- FOV was a key-value param, so I do not know what was used.
-%%- Also the mosaic was subsampled  according to a cone-stride param, with a default of 15 cones
-%%but there is a key-value param that could have overridden this value. I do not know what that parameter value was.
-%%
-%% CONE STRIDE = 3 'coneStride', 3, ... 
-%%
-%%
-%%- There is a key-value pair to also low-pass the optical image with default value to not do so.
-%%  If that was user-overridden the OI was lowpass filtered using a Gaussian whose sigma was dependent on the cone-stride param.
-%%
-%% LOW PASS FILTER = MATCH CONE STRIDE : lowPassFilter = 'matchConeStride';      
-%%
-%%- IntegrationTime was not specified, so it was the default which is 5 msec (note VS subsequently changed to 100 msec).
-%%  The cone isomerization maps were also demosaiced using linear interpolation.
-%%- The default isomerization noise was set to none, but there is a key-value parameter
-%%  that can override it. I do not know what the value of that was.
-%%
-%% ISOMERIZATION NOISE = FROZEN, 'isomerizationNoise', 'frozen'
-%%
-%%-  Finally, there is a key-value param named 'coneEfficiencyBasedReponseScaling', which by default is set to 'none'
-%%   But if it was user-set to non 'none' the code scaled the responses to simulate equal quantal efficiencies 
-%%   for L , M and S coneEfficiencyBasedReponseScaling by undoing filtering by the lens and the macular pigment.
-%%   I do not know if this was used.
-%% 
-%% coneEfficiencyBasedReponseScaling = 'area'
 
@@
 \centering
-            \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{LRF estimates}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
-        \label{fig:case1Estimates}
-    \end{subfigure} 
-        \begin{subfigure}[b]{0.31 \textwidth}
-        \caption{RF responses}
-        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure10/Figure10_b.pdf}
-        \label{fig:case1RFResponse}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32 \textwidth}
-	\caption{AMA receptive fields}
-	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure10/Figure10_c.pdf}
-	\label{fig:case1RFs}
-    \end{subfigure}   
+%\begin{subfigure}[b]{0.3 \textwidth}
+%        \caption{LRF estimates}
+%        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
+%        \label{fig:case1Estimates}
+%    \end{subfigure} 
+%        \begin{subfigure}[b]{0.31 \textwidth}
+%        \caption{RF responses}
+%        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure10/Figure10_b.pdf}
+%        \label{fig:case1RFResponse}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.32 \textwidth}
+%	\caption{AMA receptive fields}
+%	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure10/Figure10_c.pdf}
+%	\label{fig:case1RFs}
+%    \end{subfigure}   
+\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{Figure10.eps}
     \caption{{\bf Condition 1 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression on the cone excitations.
@@
 We used accuracy maximization analysis (AMA) to learn a set of linear receptive fields that are optimal for estimating target LRF from the cone excitations in this condition. 
-Decoding performance is shown in Figure~\ref{fig:case1Estimates}. 
-Figure~\ref{fig:case1Estimates} also shows the performance of the baseline linear regression method. 
+Decoding performance is shown in Figure~\ref{fig:Condition1}a. 
+Figure~\ref{fig:Condition1}a also shows the performance of the baseline linear regression method. 
 Both methods are trained on 90\% of the images in the dataset and tested on the remaining 10\%.
@@
 
-Figure~\ref{fig:case1RFResponse} shows the responses of the first two AMA receptive fields to all the image patches in the training set.
+Figure~\ref{fig:Condition1}b shows the responses of the first two AMA receptive fields to all the image patches in the training set.
 Each individual point represents the receptive field responses to an individual image patch and
@@
 The responses segregate according to the target LRF, which supports the high level 
-of estimation performance shown in Figure~\ref{fig:case1Estimates}.LRF
+of estimation performance shown in Figure~\ref{fig:Condition1}a.LRF
 Note that even the responses of the first receptive field separate well (vertical lines would accurately
@@
 
-Figure~\ref{fig:case1RFs} shows the first three AMA receptive fields.
+Figure~\ref{fig:Condition1}c shows the first three AMA receptive fields.
 Each receptive field performs a weighted sum of the L, M, and S cone excitations.
@@
 \centering
-    \begin{subfigure}[b]{0.22\textwidth}   
-        \caption{\centering{LRF estimates} \newline\centering{(Excitations)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_a.pdf}
-        \label{fig:case2IsomerizationEstimates}
-    \end{subfigure}
-        \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{\centering{RF responses} \newline\centering{(Excitations)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_b.pdf}
-        \label{fig:case2RFResponseIsomer}
-    \end{subfigure}
-            \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{\centering{LRF estimates}  \newline \centering{(Normalized contrast)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_c.pdf}
-        \label{fig:case2ContrastEstimates}
-    \end{subfigure}
-            \begin{subfigure}[b]{0.22 \textwidth}
-        \caption{\centering{RF responses}  \newline \centering{(Normalized contrast)}}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_d.pdf}
-        \label{fig:case2RFResponseContrast}
-    \end{subfigure}
+%    \begin{subfigure}[b]{0.22\textwidth}   
+%        \caption{\centering{LRF estimates} \newline\centering{(Excitations)}}
+%        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_a.pdf}
+%        \label{fig:case2IsomerizationEstimates}
+%    \end{subfigure}
+%        \begin{subfigure}[b]{0.22 \textwidth}
+%        \caption{\centering{RF responses} \newline\centering{(Excitations)}}
+%        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_b.pdf}
+%        \label{fig:case2RFResponseIsomer}
+%    \end{subfigure}
+%            \begin{subfigure}[b]{0.22 \textwidth}
+%        \caption{\centering{LRF estimates}  \newline \centering{(Normalized contrast)}}
+%        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_c.pdf}
+%        \label{fig:case2ContrastEstimates}
+%    \end{subfigure}
+%            \begin{subfigure}[b]{0.22 \textwidth}
+%        \caption{\centering{RF responses}  \newline \centering{(Normalized contrast)}}
+%        \includegraphics[width=\textwidth, trim={0 0 0 1.5cm},clip]{../FiguresDraft5/Figure11/Figure11_d.pdf}
+%        \label{fig:case2RFResponseContrast}
+%    \end{subfigure}
+\includegraphics[width=\textwidth]{Figure11.eps}
     \caption{{\bf Condition 2 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
@@
 \centering
-            \begin{subfigure}[b]{0.3 \textwidth}
-        \caption{LRF estimates}
-        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure12/Figure12_a.pdf}
-        \label{fig:case3Estimates}
-    \end{subfigure} 
-        \begin{subfigure}[b]{0.31\textwidth}
-        \caption{Receptive field response}
-        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure12/Figure12_b.pdf}
-        \label{fig:case3RFResponse}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.32 \textwidth}
-	\caption{AMA receptive fields}
-	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure12/Figure12_c.pdf}
-	\label{fig:case3RFs}
-    \end{subfigure}
+%\begin{subfigure}[b]{0.3 \textwidth}
+%        \caption{LRF estimates}
+%        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure12/Figure12_a.pdf}
+%        \label{fig:case3Estimates}
+%    \end{subfigure} 
+%        \begin{subfigure}[b]{0.31\textwidth}
+%        \caption{Receptive field response}
+%        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure12/Figure12_b.pdf}
+%        \label{fig:case3RFResponse}
+%    \end{subfigure}
+%    \begin{subfigure}[b]{0.32 \textwidth}
+%	\caption{AMA receptive fields}
+%	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure12/Figure12_c.pdf}
+%	\label{fig:case3RFs}
+%    \end{subfigure}
+\includegraphics[width=1.0\textwidth]{Figure12.eps}
     \caption{{\bf Condition 3 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
@@
 We again trained and evaluated AMA for labeled image patches, using the contrast normalized cone excitations.
-The LRF estimates obtained via AMA are more variable and less accurate than for the previous conditions (Figure~\ref{fig:case3Estimates}).
+The LRF estimates obtained via AMA are more variable and less accurate than for the previous conditions (Figure~\ref{fig:Condition3}a).
 Nevertheless, the estimates provide useful information about the target LRF.
@@
 
-Figure~\ref{fig:case3RFResponse} shows the responses of the first two AMA receptive fields to the training stimuli.
+Figure~\ref{fig:Condition3}b shows the responses of the first two AMA receptive fields to the training stimuli.
 Although the responses vary systematically with target object LRF, there is considerable overlap in the receptive field responses for stimuli having different LRF values.
 This overlap is due to the combined effect of the variation in the illumination and background surface spectra.
-Recall, however, that the performance shown Figure~\ref{fig:case3Estimates} is based on six rather than two receptive fields;
+Recall, however, that the performance shown Figure~\ref{fig:Condition3}a is based on six rather than two receptive fields;
 there is likely to be less overlap in the full six-dimensional response space.
@@
 \centering
-\includegraphics[width=0.6\textwidth]{../FiguresDraft5/Figure13/Figure13.pdf}
+\includegraphics[width=\textwidth]{Figure13.eps}
 \caption{{\bf Change of relative RMSE with number of receptive fields (RFs) and size of training set:} (a) Change of relative RMSE for Condition 3 with the size of training set.
@@
 
-Figure~\ref{fig:case3RFs} shows the first three receptive fields (RFs) learned for Condition 3.
+Figure~\ref{fig:Condition3}c shows the first three receptive fields (RFs) learned for Condition 3.
 The first two are similar to the receptive fields for Condition 1, in that the L and M cone excitations receive large weights, while the S cone excitations are less heavily weighted.
@@
 \centering
-\includegraphics[width=0.3\textwidth]{../FiguresDraft5/Figure14/Figure14.pdf}
+\includegraphics[width=\textwidth]{Figure14.eps}
 \caption{{\bf Summary of luminance constancy performance:} Relative RMSE estimation error for each method and condition.
@@
 A second advantage is that we can control the variation in distinct scene factors that might affect the difficulty of the estimation problem.
-This flexibility allows the study of individual scene factors as well as their combined effects.
+This flexibility allows the impact of scene factors to be studied individually or in combination.
 Here, we exploited this flexibility to quantify how variation in the relative reflectance spectrum of the target object, the spectrum of the illumination, and the reflectance spectrum of the background objects limit LRF estimation.
@@
 Another issue, not addressed by these datasets, is relative frequency of different surface reflectances in natural viewing.
-\citeNP{attewell2007distribution} performed a systematic survey, and report the distribution of an LRF-like quantity in natural scenes.
+\citeNP{attewell2007distribution} performed a systematic survey, and reported the distribution of an LRF-like quantity in natural scenes.
 Generalizing these measurements to better characterize the distribution of full reflectance functions remains an interesting goal.

### 2018-10-22 Production/Production.tex
edited figures for the production draft
small updates

@@
  {Neuroscience Graduate Group}
+ %, Bioengineering Graduate Group
  {Department of Psychology, University of Pennsylvania, PA, USA}
  {}{jburge@psych.upenn.edu}
-
- %% Possible reviewers:
- %
- %  Tom Serre, Brown
- %  Bill Freeman, Google Research
- %  Roland Fleming, Geissen
- %  Kavita Bala, Cornell
 
@@
 \centering
-%\begin{subfigure}{0.4 \textwidth}
-%	\centering
-%	\caption{}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_a.png}
-%        \label{fig:introSchematic}
-%    \end{subfigure}
-%    \begin{subfigure}{0.55 \textwidth}   
-%        \caption{}    
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
-%        \label{fig:introExampleFigure}
-%    \end{subfigure}
-\includegraphics[width=\textwidth]{Figure1.eps}    
+\includegraphics{Figure1.eps}    
     \caption{{\bf Color and luminance constancy:} (a)  The light reflected from an object to the eye depends both on the surface reflectance of the object and on the scene illumination. 
@@
 This approach allows us to investigate computational color constancy with naturalistic stimuli, while retaining the ability to control the properties of objects and illuminants.
-We tackle the specific problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introFigure}b).
+We specifically tackle the problem of luminance constancy, a constitutive component of the more general color constancy problem (Fig.~\ref{fig:introFigure}b).
 
@@
 \centering
-%\begin{subfigure}[b]{0.22 \textwidth}
-%        \caption{Library }
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.pdf}
-%        \label{fig:baseSceneLibrary}
-%    \end{subfigure}
-%    ~
-%    \begin{subfigure}[b]{0.22 \textwidth}
-%        \caption{Mill}    
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_b.pdf}
-%        \label{fig:baseSceneMill}
-%    \end{subfigure}    
-%    ~
-%    \begin{subfigure}[b]{0.22 \textwidth}
-%        \caption{Table-Chairs}    
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_c.pdf}
-%        \label{fig:baseSceneTableChairs}
-%    \end{subfigure}
-\includegraphics[width=\textwidth]{Figure2.eps}
+\includegraphics{Figure2.eps}
     \caption{{\bf Base scenes.} Each image shows a rendering of one base scene without additional inserted objects.
@@
 \centering
-%    \begin{subfigure}[b]{0.14 \textwidth}
-%        \caption{Big-ball}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_a.png}
-%        \label{fig:libraryWithBigBall}
-%    \end{subfigure}
-%     ~ 
-%    \begin{subfigure}[b]{0.14 \textwidth}
-%        \caption{Xylophone}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_b.png}
-%        \label{fig:libraryWithXylophone}
-%    \end{subfigure}
-%     ~ 
-%    \begin{subfigure}[b]{0.14 \textwidth}
-%        \caption{Barrel}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_c.png}
-%        \label{fig:libraryWithBarrel}
-%         \end{subfigure}
-%    ~
-%	\begin{subfigure}[b]{0.14 \textwidth}
-%        \caption{Ring toy}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_d.png}
-%        \label{fig:libraryWithRingToy}
-%    \end{subfigure}
-%        ~
-%    	\begin{subfigure}[b]{0.14 \textwidth}
-%        \caption{Bottle}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure3/Figure3_e.png}
-%        \label{fig:libraryWithChampagneBottle}
-%    \end{subfigure}
-\includegraphics[width=\textwidth]{Figure3.eps}
+\includegraphics{Figure3.eps}
 \caption{{\bf Library base scene with inserted objects.} The rendering package can be used to insert objects into base scenes.
@@
 For each LRF value, we generated a different relative target object surface reflectance for each scene.
+
 % Figure 4
 \begin{figure}
-%	\begin{subfigure}{0.18 \textwidth}
-%    \centering
-%        \caption{Target position}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_a.pdf}
-%        \label{fig:targetPositionVariation}
-%    \end{subfigure}
-%    ~
-%	\begin{subfigure}{0.18 \textwidth}
-%    \centering
-%        \caption{Target size/pose}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_b.pdf}
-%        \label{fig:targetSizeOrientation}
-%    \end{subfigure}
-%~
-%\centering
-%	\begin{subfigure}{0.18 \textwidth}
-%    \centering
-%        \caption{Target spectra}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_c.pdf}
-%        \label{fig:targetVariation}
-%    \end{subfigure}
-%    ~
-%    \begin{subfigure}{0.18 \textwidth}
-%    \centering
-%        \caption{Illumination spectra}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_d.pdf}
-%        \label{fig:illuminationVariation}
-%    \end{subfigure}
-%          ~  
-%    \begin{subfigure}{0.18 \textwidth}
-%    \centering
-%        \caption{Background spectra}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure4/Figure4_e.pdf}
-%        \label{fig:backGroundVariation}
-%    \end{subfigure}
-\includegraphics[width=\textwidth]{Figure4.eps}
+\includegraphics{Figure4.eps}
     \caption{{\bf Scene transformations.} The properties of a visual scene can be broadly classified into two groups: geometrical (a-b) and spectral (c-e).
@@
 \centering   
-%	\begin{subfigure}{0.33 \textwidth}
-%		\caption{Condition 1}
-%%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure2/Figure2_a.png}
-%		\includegraphics[width=\textwidth]{../FiguresDraft5/Figure1/Figure1_b.pdf}
-% 		\label{fig:backgroundVarying}
-%	\end{subfigure}
-%	\begin{subfigure}{0.33 \textwidth}
-%        \caption{Condition 2}	
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_b.pdf}
-%        \label{fig:targetIlluminantVarying}
-%    \end{subfigure}
-%	\begin{subfigure}{0.33 \textwidth}
-%	\caption{Condition 3}	
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure5/Figure5_c.pdf}        
-%        \label{fig:allSpectraVarying}
-%    \end{subfigure}    
-\includegraphics[width=\textwidth]{Figure5.eps}        
+\includegraphics{Figure5.eps}        
     \caption{{\bf Conditions 1-3:} Illustrative images for the three types of spectral variations studied in this paper.
@@
 \centering
-%    \begin{subfigure}[b]{0.24 \textwidth}
-%    \centering
-%	\caption{Granada dataset}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_a.pdf}
-%        \label{fig:granadaData}
-%    \end{subfigure}
-%	\begin{subfigure}[b]{0.24 \textwidth}
-%    \centering
-%        \caption{Statistical model}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_b.pdf}
-%        \label{fig:illuminantSamples}
-%    \end{subfigure}
-%      	\begin{subfigure}[b]{0.24 \textwidth}
-%    \centering
-%        \caption{CIE xy chromaticity}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_c.pdf}
-%        \label{fig:xyDiagram}
-%        \end{subfigure}
-%      	\begin{subfigure}[b]{0.24 \textwidth}
-%    \centering
-%        \caption{Color swatches}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure6/Figure6_d.pdf}
-%        \label{fig:sRGBIlluminant}
-%    \end{subfigure}
-\includegraphics[width=\textwidth]{Figure6.eps}
+\includegraphics{Figure6.eps}
     \caption{{\bf Statistical model of illumination spectra:} (a) Normalized Granada dataset.
@@
 \centering
-%	\begin{subfigure}{0.24 \textwidth}
-%    \centering
-%            \caption{Munsell and Vrhel dataset}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_a.pdf}
-%        \label{fig:reflectanceSpectra}
-%    \end{subfigure}
-%    \begin{subfigure}{0.24 \textwidth}
-%    \centering
-%        \caption{Statistical model}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_b.pdf}
-%        \label{fig:reflectanceSamples}
-%    \end{subfigure}
-%    \begin{subfigure}{0.24 \textwidth}
-%    \centering
-%    \caption{CIE xy chromaticity}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_c.pdf}
-%        \label{fig:xyChroReflectance}
-%    \end{subfigure}    
-%    \centering
-%	\begin{subfigure}{0.24 \textwidth}
-%    \centering
-%        \caption{Color swatches}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure7/Figure7_d.pdf}
-%        \label{fig:backgroundSwatches}
-%    \end{subfigure}
-    \includegraphics[width=\textwidth]{Figure7.eps}
+    \includegraphics{Figure7.eps}
     \caption{{\bf Statistical model of surface reflectance:} (a) Surface reflectance spectra from the Munsell and Vrhel datasets.
@@
 \centering
-%\begin{subfigure}[b]{0.25 \textwidth}
-%		\centering
-%        \caption{sRGB rendering of a 3D scene}
-%                \vspace{1.2mm}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_a.png}
-%        \label{fig:3DScene}
-%    \end{subfigure}
-%    ~ 
-%    \begin{subfigure}[b]{0.19 \textwidth}   
-%    \hspace{0.1 \textwidth}
-%        \caption{Cropped image}
-%        \vspace{2.5mm}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_b.png}
-%        \label{fig:croppedImage}
-%    \end{subfigure}
-%    ~ 
-%    \begin{subfigure}[b]{0.19 \textwidth}
-%    \hspace{0.1 \textwidth}
-%        \caption{Retinal image}
-%        \vspace{2.5mm}
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_c.png}
-%        \label{fig:croppedImageWithMosaic}
-%    \end{subfigure}
-%    ~
-%    \begin{subfigure}[b]{0.205 \textwidth}
-%        \caption{Normalized cone contrast}        
-%        \includegraphics[width=\textwidth]{../FiguresDraft5/Figure9/Figure9_d.png}
-%        \label{fig:coneContrast}
-%    \end{subfigure}
-    \includegraphics[width=\textwidth]{Figure9.eps}
+    \includegraphics{Figure9.eps}
     \label{fig:sceneWithCroppedImage}
@@
 \centering
-%\begin{subfigure}[b]{0.3 \textwidth}
-%        \caption{LRF estimates}
-%        \includegraphics[width=\textwidth, trim={0 0 0 1.3cm},clip]{../FiguresDraft5/Figure10/Figure10_a.pdf}
-%        \label{fig:case1Estimates}
-%    \end{subfigure} 
-%        \begin{subfigure}[b]{0.31 \textwidth}
-%        \caption{RF responses}
-%        \includegraphics[width=\textwidth, trim={0 3mm 0 15mm},clip]{../FiguresDraft5/Figure10/Figure10_b.pdf}
-%        \label{fig:case1RFResponse}
-%    \end{subfigure}
-%    \begin{subfigure}[b]{0.32 \textwidth}
-%	\caption{AMA receptive fields}
-%	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/Figure10/Figure10_c.pdf}
-%	\label{fig:case1RFs}
-%    \end{subfigure}   
-\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{Figure10.eps}
+\includegraphics{Figure10.eps}
     \caption{{\bf Condition 1 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression on the cone excitations.
@@
 %    \end{subfigure}
-\includegraphics[width=\textwidth]{Figure11.eps}
+\includegraphics{Figure11.eps}
     \caption{{\bf Condition 2 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the cone excitations.
@@
 %    \end{subfigure}
-\includegraphics[width=1.0\textwidth]{Figure12.eps}
+\includegraphics{Figure12.eps}
     \caption{{\bf Condition 3 results:} (a) Mean estimated LRF $\pm$ 1 standard deviation for images in the test set obtained using the AMA-based estimator and linear regression from the contrast normalized cone excitations.
@@
 \centering
-\includegraphics[width=\textwidth]{Figure13.eps}
+\includegraphics{Figure13.eps}
 \caption{{\bf Change of relative RMSE with number of receptive fields (RFs) and size of training set:} (a) Change of relative RMSE for Condition 3 with the size of training set.
@@
 \centering
-\includegraphics[width=\textwidth]{Figure14.eps}
+\includegraphics{Figure14.eps}
 \caption{{\bf Summary of luminance constancy performance:} Relative RMSE estimation error for each method and condition.

### 2018-10-22 codeForFigures/codeToMakeFigures/illuminantGeneration.m
small edits

@@ -101,8 +101,9 @@ ylim([0 2]);
 yticks([0 0.5 1 1.5 2]);
 yticklabels({'0.0' '0.5' '1.0' '1.5' '2.0'});
 axis square;
-save2pdf('Figure6_a.pdf',fig,1000);
-save2eps('Figure6_a.eps',fig,1000);
+fig.CurrentAxes.LineWidth = 1;
+save2pdf('Figure6_a.pdf',fig,600);
+save2eps('Figure6_a.eps',fig,600);
 close;
 %%
 % Figure 6 b

### 2018-10-22 Production/Production.tex
small edits
small edits and typos

@@
  \author{Burge}{Johannes}
- {Neuroscience Graduate Group}
- %, Bioengineering Graduate Group
+ {Neuroscience Graduate Group, Bioengineering Graduate Group}
  {Department of Psychology, University of Pennsylvania, PA, USA}
@@
 Solid lines show the mean estimate, the filled region in lighter color shows $\pm$ 1 standard deviation.
-The diagonal identity line (dotted blue) indicates veridical estimation.
+The diagonal identity line (dotted black) indicates veridical estimation.
 The filled regions representing standard deviations are too small to be visible.
-Relative RMSE (see Fig.\ref{fig:barGraphs}) is 0.7\% for linear regression and 1.1\%  for AMA-based estimation.
+Relative RMSE (see Methods: Quantifying estimation performance) is 0.7\% for linear regression and 1.1\%  for AMA-based estimation.
 (b) Training image cone excitations in Condition 1 projected onto the first two AMA receptive fields.
@@
 The responses segregate according to the target LRF, which supports the high level 
-of estimation performance shown in Figure~\ref{fig:Condition1}a.LRF
+of estimation performance shown in Figure~\ref{fig:Condition1}a.
 Note that even the responses of the first receptive field separate well (vertical lines would accurately
@@
 These spectral variations were based on statistical models of natural surface reflectance spectra and natural illumination spectra.
-We studied the how the performance of the learned estimators changed with systematic manipulation of the spectral variation in the datasets.
+We studied how the performance of the learned estimators changed with systematic manipulation of the spectral variation in the datasets.
 

### 2018-10-22 codeForFigures/codeToMakeFigures/illuminantGeneration.m

@@ -101,9 +101,8 @@ ylim([0 2]);
 yticks([0 0.5 1 1.5 2]);
 yticklabels({'0.0' '0.5' '1.0' '1.5' '2.0'});
 axis square;
-fig.CurrentAxes.LineWidth = 1;
-save2pdf('Figure6_a.pdf',fig,600);
-save2eps('Figure6_a.eps',fig,600);
+save2pdf('Figure6_a.pdf',fig,1000);
+save2eps('Figure6_a.eps',fig,1000);
 close;
 %%
 % Figure 6 b

### 2018-10-24 Production/Production.tex
david’s comments edited in

@@
 Rather, we are studying the estimation of a luminance-based summary of surface spectral reflectance.} as that of estimating the luminous reflectance factor (LRF) of a target object's surface reflectance function.
-The LRF is a measure of the overall amount of light reflected by a surface relative to the reference illuminant itself\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.} \cite{astm1121477}.
+The LRF is a measure of the overall amount of light reflected by a surface relative to the reference illuminant itself.\footnote{LRF is related to albedo, but the concept of albedo does not incorporate the human luminosity function.
+The terminology surrounding LRF and the related concept light reflectance value (LRV) varies somewhat in the literature.
+Here we follow the definition of LRF given by the \citeNP{astm1121477}.}
 Obtaining the LRF from a known surface reflectance function requires two steps.

### 2018-10-24 Production/appendix.tex
editing figures for production
david’s comments edited in

--- 2018-08-28 Draft6/appendix.tex
@@
 \begin{document}
-\title{Appendix: Luminance constancy under fixed geometry}
+\title{Appendix: Computational Luminance Constancy from Naturalistic Images}
 
@@
     \begin{subfigure}[b]{0.4 \textwidth}
-	\caption{Normalized contrast}
+	\caption{Contrast normalized}
 	\includegraphics[width=1.0\textwidth, trim={0.2cm -0.cm 0 0.3cm}]{../FiguresDraft5/FigureSI/SI_Figure1_b.pdf}
@@
     \end{subfigure}   
-    \caption{{\bf Condition 2 receptive fields:} The first three AMA receptive fields learnt on (a) Cone excitations (b) Normalized contrast.}
+    \caption{{\bf Condition 2 receptive fields:} The first three AMA receptive fields learnt on (a) Cone excitations (b) Contrast normalized.}
 \label{fig:Condition1}

### 2018-10-26 Production copy/Production.tex
making new copies

--- 2018-10-24 Production/Production.tex
@@
 The terminology surrounding LRF and the related concept light reflectance value (LRV) varies somewhat in the literature.
-Here we follow the definition of LRF given by the \citeNP{astm1121477}.}
+Here we follow the definition of LRF given by the American Society for Testing and Materials \citeyear{astm1121477}.}
 Obtaining the LRF from a known surface reflectance function requires two steps.
